### 2019-08-02 main.tex
Add content

\documentclass[twocolumn]{aastex62}
\usepackage{natbib}
\usepackage[colorinlistoftodos]{todonotes}
%\usepackage{academicons}
%\definecolor{orcidlogocol}{HTML}{A6CE39}
\bibliographystyle{apj}

\begin{document}

\title{COLLISION RATES OF PLANETESIMALS NEAR MEAN-MOTION RESONANCES}

\author{Spencer C. Wallace}
\affiliation{Astronomy Department, University of Washington, Seattle, WA 98195}

\author{Aaron C. Boley}
\affiliation{Department of Physics and Astronomy, University of British Columbia, Vancouver BC, Canada}

\author{Thomas R. Quinn}
\affiliation{Astronomy Department, University of Washington, Seattle, WA 98195}

\begin{abstract}
A perturbing planes can leave a lasting imprint a debris disk near the locations of mean motion resonances (MMRs). Unfortunately, the planetesimal-sized objects that make up the majority of these disks are extremely difficult to directly observe. Dust created from collisions between planetesimals may be a much better way to constrain the structure of these disks. We use a direct N-body model to measure planetesimal collision rates in a dynamically cold debris disk composed of 150 km bodies. Even though the eccentricities are pumped at the nominal resonance locations, conservation of the Jacobi energy pushes planetesimals inward and enhances the collision rate adjacent to the resonances. In addition, we find that the collision rate is severely throttled near the 3:1 MMR and that a tightly wound spiral wave is launched from this location.
\end{abstract}

\section{Introduction} \label{sec:intro}

Recent observations of circumstellar disks by ALMA have revealed a rich variety of substructure in the millimeter wavelength contiunuum emission. Features such as gaps and asymmetries \citep{2015ApJ...808L...3A, 2016Sci...353.1519P, PhysRevLett.117.251101, 2016ApJ...820L..40A, 2016Natur.535..258C} in the emission provide diagnostics for the physical processes that drive the evolution of the disks. At these wavelengths, much of this light is produced by second-generation debris generated through collisional grinding of planetesimals \citep[see][]{2008ARA&A..46..339W}.

In some cases, these gap features are argued to be an indicator for the presence of a giant planet, either embedded in the disk \citep{2015MNRAS.453L..73D} or orbiting externally. An giant perturber can influence the structure of the dust emission in a number of ways. A misaligned giant planet can produce nonaxisymmetric features such as warps \citep{2001A&A...370..447A}. Highly eccentric perturbers can produce even more complicated structures through secular perturbations \citep{2014MNRAS.443.2541P, 2015MNRAS.448.3679P}. Mean motion resonances have been shown to open gaps as well \citep{2015ApJ...798...83N, 2016ApJ...818..159T, 2018ApJ...857....3T}.

The dynamics that give rise to second-generation dust in debris disks are not well understood. Add more text about this and some references. Should maybe discuss planet migration and resonant trapping here (and why we are ignoring it in our simulations)?

In this study, we will examine the dynamical effects that give rise to collisions between planetesimals under the influence of an external giant planet. Near mean motion resonances (MMRs), the surface density and eccentricity dispersion of planetesimals becomes significantly altered \citep{2000Icar..143...45R, 2017ApJ...850..103B}. The effect that this has on the behavior of collisional grinding in these regions is not well understood. The way in which planetesimals move and interact in the vicinity of MMRs is extremely nonlinear and is best studied with N-body methods. Collision detection in an N-body simulation is extremely computationally expensive. So far, most studies of planetesimal dynamics near MMRs have involved either collisionless test particles \citep{2017ApJ...850..103B, 2016ApJ...818..159T, 2018ApJ...857....3T} or severely limited integration times \citep{2000Icar..143...45R}. Also see \citep{2001A&A...373..683C}. The only exception to this are a series of N-body studies of a Jupiter sized planet embedded in a disk of colliding planetesimals \citep{2013ApJ...777L..31D, 2016ApJ...820...29D}. In these simulations, the close proximity of the planetesimals to the planet produces a significant population of high eccentricity bodies, diluting the dynamical and collisional features near MMRs.

This paragraph is an outline of the paper

\begin{figure}
    \includegraphics[width=\columnwidth]{figures/test.eps}
    \caption{Caption goes here.
    \label{fig:test}}
\end{figure}

%In this study, we will consider the effects that an external perturber has on the dynamical evolution and collision rates of planetesimals in a circumstellar disk. Planetesimals are too small to reflect much star light and are of too low mass to have any significant amount of thermal inertial. However, the large amounts of dust produced by collisional grinding can be used to infer where planetesimals are interacting \citep{2005Natur.436..363S, 2015ApJ...806...23L}. Although the behavior of the small dust grains can strongly depend on the hydrodynamic behavior of the gas \citep{2015ApJ...813L..14B}, the evolution of the planetesimals (km sized and larger) should be well decoupled from the gas. This means that results of this study should be applicable to both gas rich protoplanetary disks such as HL Tau and TW Hya, along with dusty debris disks such as Fomalhut \citep{2017ApJ...842....8M}.

%The intermediate stages of planet formation are incredibly difficult to observe. Planetesimals, which are the building blocks of planets, are too small to reflect any significant amount of star light and are of too low mass to carry much thermal inertia. However, large volumes of dust produced through collisional grinding of planetesimals can be used to infer where planetesimals are interacting

%In the Solar System, the formation of Jupiter is thought to have destabilized the orbits of nearby planetesimals and triggered a short and intense period of bombardment. In addition to triggering a cascade of collisional grinding \citep{2012ApJ...750....8T}, the formation of Jupiter is thought to have facilitated the mixing of volatiles in the inner Solar System \citep{2017Icar..297..134R}.

%From an outsider's perspective, the most easily observable property of the Solar System is the infrared emission from small dust grains. Outside the Solar System, infrared excess has also been tied to the presence of dust (citation needed). Recent high resolution images from ALMA have shown that the structure of these dusty disks around other stars can have rather complicated structures.

%Talk about observed gaps in ALMA images of PPDs. Many different explanations for rings and gaps \citep{2019arXiv190103680V}. One possible explanation is resonances with outer companion. \citet{2017ApJ...850..103B} examined this possibility, but used massless test particles to represent the planetesimals. Although this provided some information about how the planetesimals move under the influence of a mean motion resonance, it did not say anything about where the collisions and dust production would occur.

%Talk about specific PPDs where MMRs might be producing some of the structure (HL Tau, TW Hya)

%Talk about dynamics in MMRs. Resonances tend to push particles away from the perturber. Mention study by \citet{2016ApJ...818..159T, 2018ApJ...857....3T}. Massive disk can move resonance locations (see eq 10 or \citet{2015ApJ...805..100T}). Looks like we are getting a spiral wave being launched from the 3:1 MMR (see section 5.6 in \citet{2016ApJ...818..159T}). Study by \citet{2018MNRAS.473.3547R} used collisionless N-body sim to examine production of cavity in debris disk, assume paricles trace mm sized objects which should be observable.

%See \citet{1984prin.conf..513S} for a fantastic discussion of spiral waves in a planetary context.

\section{Simulations}\label{sec:sims}

Overview of ChaNGa and collision code

Talk about initial conditions, meant to be similar to case B in \citet{2000Icar..143...45R}.

We use equation 12 from kokubo and ida 2002 to set initial free eccentricites and inclinations for particles, in equilibrium with gas drag. These would be about twice as big if we instead used vrandom = vesc, which is the point at which grav stirring stops being very effective. Forced eccentricity and varpi set by secular perturbations by Jupiter, as done by Tabeshian and Weigert.

%Scattering of planetesimals by giant planet does not depend on migration, so we ignore this process \citet{2017Icar..297..134R}.

\section{Results}\label{sec:results}

Figures to include:

\begin{itemize}
    \item a-e evolution of particles
    \item a-e closeup of resonance (do we need to pick more than one?)
    \item azimuthally averaged profile of collision rates
    \item temporal evolution of collision rates inside and outside resonance
\end{itemize}

Need to expain waves in a-e plots. This is from the free eccentricity cycling through phase space.

Might be useful to compare Aaron's estimate of collsion rates from velocity dispersion in 2017 paper to the actual collision rates that we measure. Collision rates tend to be supressed outside of MMRs compared to Safronov rate. Im guessing this has to do with the fact that precession rates are high inside MMRs and so orbits are not aligned and more likely to cross. For a discussion of secular precession rates due to a giant planet, see \citet{2009MNRAS.399.1403M}.

\bibliography{references}

\clearpage

\end{document}

### 2019-08-02 makeFig.py

@@ -1,0 +1,22 @@
+#/bin/bash
+
+import matplotlib.pylab as plt
+import numpy as np
+
+# Regenerate existing plots?
+clobber = False
+
+import os
+def make_test():
+    file_str = 'figures/test.eps'
+    if not clobber and os.path.exists(file_str):
+        return
+
+    x = np.linspace(0, 2*np.pi)
+    y = np.sin(x)
+
+    fig, axes = plt.subplots(figsize=(8,8))
+    axes.plot(x, y)
+    plt.savefig(file_str, format='eps', bbox_inches='tight')
+
+make_test()

### 2019-08-06 main.tex
Add text to intro

@@
 \begin{abstract}
-A perturbing planes can leave a lasting imprint a debris disk near the locations of mean motion resonances (MMRs).
+A perturbing planet can leave a lasting imprint a debris disk near the locations of mean motion resonances (MMRs).
 Unfortunately, the planetesimal-sized objects that make up the majority of these disks are extremely difficult to directly observe.
@@
 Highly eccentric perturbers can produce even more complicated structures through secular perturbations \citep{2014MNRAS.443.2541P, 2015MNRAS.448.3679P}.
-Mean motion resonances have been shown to open gaps as well \citep{2015ApJ...798...83N, 2016ApJ...818..159T, 2018ApJ...857....3T}.
+Mean motion resonances (MMRs) have been shown to open gaps as well \citep{2015ApJ...798...83N, 2016ApJ...818..159T, 2018ApJ...857....3T}.
 
-The dynamics that give rise to second-generation dust in debris disks are not well understood.
-Add more text about this and some references.
-Should maybe discuss planet migration and resonant trapping here (and why we are ignoring it in our simulations)?
+The dynamics governing the motion of bodies near MMRs is extremely nonlinear, as is determining what the collision rates between planetesimals should look like in these regions.
+For a collection of bodies massive enough to experience the effects of gravitational focusing, a large eccentricity dispersion tends to reduce the probability of collision, while enhancements in surface density tends to increase it.
+Due to conservation of the Jacobi energy, MMRs simultaneously enhance the local eccentricity dispersion and also enhance the surface density adjacent to the resonance \citep{2000Icar..143...45R, 2017ApJ...850..103B}.
+
+Because the second generation dust production is driven by the planetesimal collision rate, it is crucial to understand how the dynamics that drive collisions works.
+In particular, it is not obvious how to link the readily observable thermal emission from dust in protoplanetary disks to the presence of a perturbing giant planet.
+Due to its nonlinearity, this problem is best studied with N-body simulations.
+Unfortunately, collision detection in an N-body simulation is extremely computationally expensive.
+So far, studies of planetesimal dynamics near MMRs have involved either collisionless test particles \citep{2017ApJ...850..103B, 2016ApJ...818..159T, 2018ApJ...857....3T} or severely limited integration times \citep{2000Icar..143...45R}.
+
+To further elucidate this subject, we use the tree based N-body code {\sc ChaNGa} \citep{2008IEEEpds...ChaNGa, 2015AphCom..2..1} to follow the collisional evolution of a planetesimal disk under the gravitational influence of a Jupiter sized body.
+Because particle positions are sorted into a tree structure, neighbor finding and collision detection can be done quickly and efficiently.
+This considerably relaxes the constraints on resolution and integration time.
+With this toolset, we explore the collision rate structure of the planetesimal disk in the vicinity of mean motion resonances.
+
+This work is organized in the following way.
 

### 2019-08-07 main.tex
Finish intro, outline sections

@@
 This work is organized in the following way.
+In section \ref{sec:dynamics} we provide an overview of the dynamics that drive the evolution of a planetesimal disk under the gravitational influence of an external perturber.
+In section \ref{sec:setup} we describe the N-body code we use and describe how we constructed the initial conditions for the two simulations that are run: one with a perturber on a circular orbit and one with an eccentric perturber.
+Section \ref{sec:results} goes on to explore the results of the two, with particular focus on the radial variation in the collision rates.
+In section \ref{sec:dust}, we use the positions of the collision events to construct a map of second generation dust emission, under the assumption that dust grains produced by collisions will immediately couple to the gas and circularize their orbits.
+Finally, we assess the observability of features in the dust emission due to mean motion resonances and conclude in section \ref{sec:discuss}.
 
-In this study, we will examine the dynamical effects that give rise to collisions between planetesimals under the influence of an external giant planet.
-Near mean motion resonances (MMRs), the surface density and eccentricity dispersion of planetesimals becomes significantly altered \citep{2000Icar..143...45R, 2017ApJ...850..103B}.
-The effect that this has on the behavior of collisional grinding in these regions is not well understood.
-The way in which planetesimals move and interact in the vicinity of MMRs is extremely nonlinear and is best studied with N-body methods.
-Collision detection in an N-body simulation is extremely computationally expensive.
-So far, most studies of planetesimal dynamics near MMRs have involved either collisionless test particles \citep{2017ApJ...850..103B, 2016ApJ...818..159T, 2018ApJ...857....3T} or severely limited integration times \citep{2000Icar..143...45R}.
-Also see \citep{2001A&A...373..683C}.
-The only exception to this are a series of N-body studies of a Jupiter sized planet embedded in a disk of colliding planetesimals \citep{2013ApJ...777L..31D, 2016ApJ...820...29D}.
-In these simulations, the close proximity of the planetesimals to the planet produces a significant population of high eccentricity bodies, diluting the dynamical and collisional features near MMRs.
+\section{Collisions and Mean Motion Resonances} \label{sec:dynamics}
 
-This paragraph is an outline of the paper
+\section{Simulation Setup} \label{sec:setup}
+
+We use equation 12 from kokubo and ida 2002 to set initial free eccentricites and inclinations for particles, in equilibrium with gas drag.
+These would be about twice as big if we instead used vrandom = vesc, which is the point at which grav stirring stops being very effective.
+Forced eccentricity and varpi set by secular perturbations by Jupiter, as done by Tabeshian and Weigert.
+
+\section{Results} \label{sec:results}
+
+\section{Dust Emission} \label{sec:results}
+
+\section{Summary and Discussion} \label{sec:discuss}
 
@@
 
-\section{Simulations}\label{sec:sims}
-
-Overview of ChaNGa and collision code
-
-Talk about initial conditions, meant to be similar to case B in \citet{2000Icar..143...45R}.
-
-We use equation 12 from kokubo and ida 2002 to set initial free eccentricites and inclinations for particles, in equilibrium with gas drag.
-These would be about twice as big if we instead used vrandom = vesc, which is the point at which grav stirring stops being very effective.
-Forced eccentricity and varpi set by secular perturbations by Jupiter, as done by Tabeshian and Weigert.
-
 %Scattering of planetesimals by giant planet does not depend on migration, so we ignore this process \citet{2017Icar..297..134R}.
-
-\section{Results}\label{sec:results}
 

### 2019-08-08 main.tex
Add text to section 2

@@
 
-\section{Collisions and Mean Motion Resonances} \label{sec:dynamics}
+\section{Overview of Relavant Dynamics} \label{sec:dynamics}
+
+\subsection{Collisions}
+
+We begin by making the assumption that a typical encounter between planetesimals in a disk is well-described by two-body dynamics.
+So long as the random velocities of planetesimals $v_{p}$ are large compared to the Hill velocity of a planetesimal $v_{h} = \sqrt{G m_{p} / r_{h}}$, where $r_{h}$ is the Hill radius, the gravitational field of the central star will play an insignificant role and can be safely ignored.
+In this case and assuming equal mass bodies, the collision rate is given by \citep{1967SvA....10..650S}
+
+\begin{equation}\label{eq:safronov}
+	\sigma v = \pi r_{p}^2 \left( 1 + v_{esc}^2/v_{p}^2 \right) v_{p},
+\end{equation}
+
+\noindent where $r_{p}$ is the radius of a planetesimal and $v_{esc}$ is the mutual escape velocity of two planetesimals in contact.
+The $v_{esc}^2/v_{p}^2$ term describes the factor above which the collision cross section is enhanced due to gravitational focusing.
+For a dynamically cold planetesimal disk, $v_{p}$ is small relative to $v_{esc}$ and the collision rate becomes strongly enhanced.
+
+In the absence of a proper treatment of collision detection, equation \ref{eq:safronov} can be used to make a local estimate of the collision rate in an N-body simulation using only the positions and velocities of particles.
+This has been done in other studies \citep{2017ApJ...850..103B} (any other examples?), but requires bulk averaging of the phase space properties of particles, which may mask important information and blur out features.
+We will revisit equation \ref{eq:safronov} in section \ref{sec:results} to test how well the collision rate near mean motion resonances is described by this framework.
+
+\subsection{Mean Motion Resonances}
 
@@
 
-\section{Dust Emission} \label{sec:results}
+\section{Dust Emission} \label{sec:dust}
 

### 2019-08-09 main.tex
Add text to section 2

@@
 
+\subsection{Secular Forcing}
+
+The most direct and widespread effect that a giant perturber will have on a planetesimal disk is through secular forcing of the eccentricities of the planetesimals.
+This will cause the complex eccentricities of the planetesimals to take on a time independent forced value, given by \citep{1999ApJ...527..918W} as
+
+\begin{equation}\label{eq:eforced}
+	z_{f} = \frac{b^{2}_{3/2} (\alpha)}{b^{1}_{3/2} (\alpha)} e_{g} ~ \mathrm{exp} ~ i \omega_{g}.
+\end{equation}
+
+\noindent Here, $\alpha = a_{g} / a$ where $a_{g}$ and $a$ are the semi-major axes of the giant planet and the planetesimal, respectively.
+$e_{g}$ and $\omega_{g}$ are the eccentricity and longitude of pericenter of the giant and $b^{j}_{s} (\alpha)$ is a Laplace coefficient given by \citep{2000ssd..book.....M} as
+
+\begin{equation}\label{eq:lap}
+	b_{s}^{j}(\alpha) = \frac{1}{2 \pi} \int_{0}^{2 \pi} \frac{cos \, j \theta \, d \theta}{\left( 1 - 2 \alpha \, cos \theta + \alpha^2 \right)^{s}}.
+\end{equation}
+
+Ignoring secular and mean motion resonances, equation \ref{eq:eforced} will completely describe the eccentricities and pericenter orientations of the orbits of the planetesimals.
+Additional forces due to two-body scattering between planetesimals, along with aerodynamic gas drag will add an additional free component to the complex eccentricity, which will be randomly oriented.
+The magnitude of the free eccentricity describes how dynamically hot the planetesimal disk is and sets the random encounter speeds of planetesimals.
+When the dynamical excitation of the disk is driven by gravitational stirring, the magnitude of the free eccentricity can be described by a Rayleigh distribution \citep{1992Icar...96..107I}.
+
 \subsection{Mean Motion Resonances}

### 2019-08-12 main.tex
Finish section 2

@@
 
+In regions where there are commensurabilities between frequencies, secular theory breaks down and bodies are subject to strong perturbations.
+For the purposes of this study, we will ignore secular resonances, which generally occur on rather large timescales and will focus on mean motion resonances (MMRs).
+A MMR occurs  when the orbital period ratio between two bodies is sufficiently close to
+
+\begin{equation}\label{eq:per_mmr}
+	\frac{P}{P'} = \frac{p + q}{p},
+\end{equation}
+
+\noindent where  $p$ and $q$ are integers $>$ 0 and the unprimed and primed quantities correspond to the perturber and the body being perturbed, respectively.
+If the gravitational potential of the system is dominated by the central star, the condition for MMR is set by the semi-major axes of the two bodies by
+
+\begin{equation}\label{eq:a_mmr}
+	\frac{a}{a'} = \left( \frac{p}{p + q} \right)^{2/3}.
+\end{equation}
+
+Under the effect of MMR, a body will undergo oscillations in semi-major axis and eccentricity.
+So long as the gravitational force on the body is dominated by the central star and the perturbing body, the amplitude of the oscillations in semi-major axis can be described using the pendulum approximation (see equation 6 in \citet{2018arXiv181007201W}).
+This amplitude can be thought of as the 'width' over which the perturbations of the resonance are effective.
+Variations in eccentricity follow the semi-major axis variations according to the Tisserand relation
+
+\begin{equation}\label{eq:tiss}
+	\frac{de}{da} = \frac{a^{3/2} - 1}{2 a^{5/2} e}.
+\end{equation}
+
+The net result of this is that isolated MMRs will produce 'spikes' in the semi-major axis vs eccentricity distribution of a planetesimal disk.
+Following equation \ref{eq:tiss}, these spikes will tend to slightly curve away from the perturbing body.
+As planetesimals undergo two-body scattering events with other bodies, the variations in semi-major axis and eccentricity due to resonances can become permanent.
+This tends to lower the surface density of the disk near the locations of resonances, while producing a pileup of eccentric bodies adjacent to the MMR.
+The enhanced surface density will increase the collision rate, while the large eccentricity dispersion will lower it due to the decreased effectiveness of gravitational focusing.
+Due to these competing effects, along with the complicated dynamics that are likely at play near the edge of the resonant region, we turn to a direct N-body treatment to better understand how the collision rate varies in the vicinity of a MMR.
+
 \section{Simulation Setup} \label{sec:setup}

### 2019-08-14 main.tex
Start adding text to section 3

@@
 
-\section{Simulation Setup} \label{sec:setup}
+\section{Simulations} \label{sec:sims}
+
+\subsection{Numerical Methods}\label{sec:methods}
+
+To follow the dynamical and collisional evolution of a planetesimal disk, we use the highly parallel N-body code {\sc ChaNGa} \footnote{A public version of {\sc ChaNGa} can be downloaded from \url{http://www-hpcc.astro.washington.edu/tools/ChaNGa.html}}.
+This code, which is written in the {\sc CHARM++} parallel programming language, was originally designed for cosmology simulations and has been shown to perform well on up to half a million processors \citep{2015AphCom..2..1}.
+{\sc ChaNGa} calculates gravitational forces using a modified Barnes-Hut \citep{1986Natur.324..446B} tree with hexadecapole expansions of the moments.
+All of the simulations we perform use a node opening criterion of $\theta_{BH}$ = 0.7.
+More information about the code can be found in \citet{2008IEEEpds...ChaNGa}.
+We have also recently modified {\sc ChaNGa} to handle solid-body collisions.
+A full description of the collision module implementation can be found in \citet{2018arXiv181007201W}.
+
+\subsection{Initial Conditions}\label{sec:ics}
+
+Two simulations are run, which are loosely based off of 'Model B' in \citet{2000Icar..143...45R}.
+In both cases, a Jupiter mass planet is placed on a 5.2 AU orbit around a 1 $M_{\odot}$ star with a disk of planetesimals placed interior.
+In the first case, Jupiter is given a mildly eccentric (e = 0.05) orbit.
+In the second case, Jupiter is placed on a circular orbit.
+We will refer to these simulations as EJ and CJ, respectively.
+
+In both cases, the planetesimal disk extends from 2.2 to 3.8 AU.
+This range of semi-major axes covers a number of prominent interior mean motion resonances with Jupiter, including the 3:1, the 5:2, the 2:1 and the 5:3.
+The planetesimal disk follows a minimum-mass solar nebula surface density profile \citep{1981PThPS..70...35H}
+
+\begin{equation}\label{eq:surf_den}
+	\Sigma = \Sigma_{0} r^{-\alpha},
+\end{equation}
+
+\noindent with $\alpha$ = 3/2 and $\Sigma_{0}$ = 10 g cm$^{-2}$.
+Planetesimals are given a bulk density of 2 g cm$^{-3}$ and a diameter of 300 km.
+This corresponds to a disk containing slightly less than 500,000 planetesimals.
+
+In the CJ simulation, there is no secular forcing from Jupiter and so the mean longitudes and mean anomalies are randomly assigned values between 0 and 2$\pi$.
+The distribution of eccentricities and inclinations of the planetesimals are chosen so that the effects of viscous stirring and gas drag from the solar nebula are in balance.
+This occurs when eccentricities are described by a Rayleigh distribution with a mode given by equation 12 in \citet{2002ApJ...581..666K}.
+The inclination distribution is described by this same function, with a mode that is a factor of 2 smaller \citep{1993MNRAS.263..875I}.
 

### 2019-08-15 main.tex
Finish section 3

@@
 In both cases, a Jupiter mass planet is placed on a 5.2 AU orbit around a 1 $M_{\odot}$ star with a disk of planetesimals placed interior.
-In the first case, Jupiter is given a mildly eccentric (e = 0.05) orbit.
-In the second case, Jupiter is placed on a circular orbit.
-We will refer to these simulations as EJ and CJ, respectively.
+In the first case, Jupiter is placed on a circular orbit.
+In the second case, Jupiter is placed on a mildly eccentric (e = 0.05) orbit.
+We will refer to these simulations as CJ and EJ, respectively.
 
@@
 This corresponds to a disk containing slightly less than 500,000 planetesimals.
+Both simulations are evolved for 10,000 years, which is about 800 Jupiter orbits.
 
@@
 The inclination distribution is described by this same function, with a mode that is a factor of 2 smaller \citep{1993MNRAS.263..875I}.
+
+For simulation EJ, the effects of secular forcing by Jupiter are applied to the initial conditions.
+This is done by first assigning Kepler orbital elements to the planetesimals in the same way as simulation CJ and then adding a forced component to the eccentricity vectors $z_{i} = \left( h_{i}, k_{i} \right)$, described by equation \ref{eq:eforced}.
+For simplicity, a coordinate system is chosen so that $\omega_{g}$ = 0.
+This allows us to simply add a scalar value to each $h_{i}$, which depends only on the semi-major axis of a planetesimal and Jupiter, along with the eccentricity of Jupiter.
+
+\subsection{Time Stepping Scheme}\label{sec:timestep}
+
+For the purposes of the integrator, there are two relevant timescales in this system.
+The first is the orbital dynamical time $\sqrt{a^3/G M_{\odot}}$.
+All particles are placed on a fixed time step of $\Delta T$ = 0.01 yr.
+This is roughly 3\% of an orbital dynamical time at the inner edge of the planetesimal disk, which is a reasonable time step size for a leapfrog integrator (reference?).
+The time step for collisions is determined by the planetesimal dynamical timescale ($\sim 1/\sqrt{G \rho}$), which is about 45 minutes.
+To resolve both of these timescales simultaneously, we use a two-tiered time stepping scheme.
+At the beginning of each time step, all bodies are placed on the orbital time step.
+A first pass of collision detection is then run in which the radii of all bodies are inflated by a factor of 2.5.
+Any bodies with imminent collisions predicted using the inflated radii are placed on a time step that is a factor of 16 smaller than the orbital time step.
+The purpose of two-tiered scheme is to properly resolve the gravitational interactions between any bodies that will undergo a close encounter.
+This prevents the coarser base time step from reducing the effectiveness of gravitational focusing, while minimizing the additional computational expense.
 

### 2019-08-22 main.tex
Outline figures to show

@@
 
+Outline for this section:
+\begin{list}
+\li Time evolution of disk surface density for circ and ecc
+\li Time evolution of sma vs ecc
+\li Number of collisions as a function of sma and radial distance
+\li Number of collisions as a function of mean anomaly and delta mean anomaly
+\li Comparison between safronov rate and actual collision statistics
+\end{list}
+
 \section{Dust Emission} \label{sec:dust}
+
+\begin{list}
+\li Show CASA images
+\end{list}
 

### 2019-08-24 main.tex
Add first few figures

--- 2019-08-15 main.tex
@@
-\documentclass[twocolumn]{aastex62}
+\documentclass[twocolumn]{aastex63}
 \usepackage{natbib}
-\usepackage[colorinlistoftodos]{todonotes}
-%\usepackage{academicons}
 %\definecolor{orcidlogocol}{HTML}{A6CE39}
-\bibliographystyle{apj}
+\bibliographystyle{aasjournal}
 
@@
 
+\begin{figure*}
+    \includegraphics[width=\textwidth]{figures/rtheta.png}
+    \caption{Caption goes here.\label{fig:rtheta}}
+\end{figure*}
+
+\begin{figure*}
+    \includegraphics[width=\textwidth]{figures/ae.png}
+    \caption{Caption goes here.\label{fig:ae}}
+\end{figure*}
+
+\begin{figure}
+    \includegraphics[width=\columnwidth]{figures/long_ph.png}
+    \caption{Caption goes here.\label{fig:long_ph}}
+\end{figure}
+
 \section{Results} \label{sec:results}
+
+Outline for this section:
+\begin{itemize}
+\item Time evolution of disk surface density for circ and ecc
+\item Time evolution of sma vs ecc
+\item Number of collisions as a function of sma and radial distance
+\item Number of collisions as a function of mean anomaly and delta mean anomaly
+\item Comparison between safronov rate and actual collision statistics
+\end{itemize}
 
@@
 
+\begin{itemize}
+\item Show CASA images
+\end{itemize}
+
 \section{Summary and Discussion} \label{sec:discuss}
-
-\begin{figure}
-    \includegraphics[width=\columnwidth]{figures/test.eps}
-    \caption{Caption goes here.
-    \label{fig:test}}
-\end{figure}
 

### 2019-08-24 makeFig.py

@@ -1,22 +1,96 @@
 #/bin/bash
-
 import matplotlib.pylab as plt
+import matplotlib as mpl
 import numpy as np
+import pandas as pd
+import pynbody as pb
+import natsort as ns
+import glob as gl
+import os
+
+from astropy import units as u
+from astropy.constants import G
+simT = u.year/(2*np.pi)
+simV = u.AU / simT
+
+import sys
+sys.path.insert(0, '../OrbitTools/')
+import OrbitTools
+
+mpl.rcParams.update({'font.size': 18, 'font.family': 'STIXGeneral', 'mathtext.fontset': 'stix',
+                            'image.cmap': 'viridis'})
+
+simT = u.year/(2*np.pi)
+simV = u.AU/simT
+path = '../files/research/planetFormation/jupResonance/data/'
+s_c_files = np.array([path + 'hkshiftfullJupCirc/hkshiftfullJupCirc.ic']+ \
+	                  ns.natsorted(gl.glob(path + 'hkshiftfullJupCirc/*.[0-9]*[0-9]')))
+s_e_files = np.array([path + 'hkshiftfull/hkshiftfull.ic']+ \
+	                  ns.natsorted(gl.glob(path + 'hkshiftfull/*.[0-9]*[0-9]')))
+
+a_in, a_out = 2.2, 3.8
 
 # Regenerate existing plots?
-clobber = False
+clobber = True
+fmt = 'png'
+s = 0.005
 
-import os
-def make_test():
-    file_str = 'figures/test.eps'
-    if not clobber and os.path.exists(file_str):
-        return
+def make_rtheta():
+	file_str = 'figures/rtheta.' + fmt
+	if not clobber and os.path.exists(file_str):
+		return
+	s_c, s_e = pb.load(s_c_files[-1]), pb.load(s_e_files[-26])
+	pl_c, pl_e = OrbitTools.orb_params(s_c), OrbitTools.orb_params(s_e)
+	x_c, y_c = pl_c['pos'][:,0], pl_c['pos'][:,1]
+	r_c, theta_c = np.sqrt(x_c**2 + y_c**2), np.arctan2(y_c, x_c) + np.pi
+	x_e, y_e = pl_e['pos'][:,0], pl_e['pos'][:,1]
[…]

### 2019-08-29 makeFig.py
Add more figures

@@ -22,11 +22,87 @@ mpl.rcParams.update({'font.size': 18, 'font.family': 'STIXGeneral', 'mathtext.fo
 
 simT = u.year/(2*np.pi)
 simV = u.AU/simT
+
 path = '../files/research/planetFormation/jupResonance/data/'
+
+# Resonances
+res_dist = [2.5, 3.27, 3.7]
+res_label = ['3:1', '2:1', '5:3']
+res_p = [1, 1, 3]
+res_q = [2, 1, 2]
+
+# Width of a resonance with jupiter (in AU)
+# Assume body has an eccentricity of e_forced
+def res_width_jup(p, q):
+    m, m_c = 9.54e-4, 1
+    a_jup = 5.2
+    ecc_jup = 0.048
+    j1 = p + q
+    j2 = -p
+    alpha = (-j2/j1)**(2./3.)
+    ecc = OrbitTools.lap(2, 3/2, alpha)/OrbitTools.lap(1, 3/2, alpha)*ecc_jup
+    dist = alpha*a_jup
+    rw = OrbitTools.res_width(m, m_c, ecc, j1, j2)*dist
+    return rw
+
+def plot_res(axis, res=-1, vertical=True, show_widths=False):
+	xmin, xmax = axis.get_xlim()
+	ymin, ymax = axis.get_ylim()
+	if res == -1:
+		for idx, dist in enumerate(res_dist):
+			if vertical:
+				axis.vlines(dist, ymin, ymax, linestyles='-')
+				axis.text(dist, ymax, res_label[idx])
+				if show_widths:
+					width = res_width_jup(res_p[idx], res_q[idx])
+					axis.vlines(res_dist[idx] - width, ymin, ymax, linestyle='--')
+					axis.vlines(res_dist[idx] + width, ymin, ymax, linestyle='--')
+			else:
+				axis.hlines(dist, xmin, xmax, linestyles='-')
+				axis.text(xmax, dist, res_label[idx])
+				if show_widths:
+					width = res_width_jup(res_p[idx], res_q[idx])
+					axis.hlines(res_dist[idx] - width, xmin, xmax, linestyle='--')
[…]

### 2019-09-05 main.tex
Add more figures
Discussion of figure 1

@@
 The distribution of eccentricities and inclinations of the planetesimals are chosen so that the effects of viscous stirring and gas drag from the solar nebula are in balance.
-This occurs when eccentricities are described by a Rayleigh distribution with a mode given by equation 12 in \citet{2002ApJ...581..666K}.
-The inclination distribution is described by this same function, with a mode that is a factor of 2 smaller \citep{1993MNRAS.263..875I}.
+This occurs when eccentricities are described by a Rayleigh distribution with a scale parameter given by equation 12 in \citet{2002ApJ...581..666K}.
+The inclination distribution is described by this same function, with a scale parameter that is half as large.
+This is typical for a sufficiently dynamically heated disk of particles in a Kepler potential \citep{1993MNRAS.263..875I}.
 
@@
 
-We use equation 12 from kokubo and ida 2002 to set initial free eccentricites and inclinations for particles, in equilibrium with gas drag.
-These would be about twice as big if we instead used vrandom = vesc, which is the point at which grav stirring stops being very effective.
-Forced eccentricity and varpi set by secular perturbations by Jupiter, as done by Tabeshian and Weigert.
-
 \begin{figure*}
@@
 
+\begin{figure*}
+    \includegraphics[width=\textwidth]{figures/coll_hist_a.png}
+    \caption{Caption goes here.\label{fig:coll_hist_a}}
+\end{figure*}
+
+\begin{figure*}
+    \includegraphics[width=\textwidth]{figures/coll_hist_r.png}
+    \caption{Caption goes here.\label{fig:coll_hist_r}}
+\end{figure*}
+
+\begin{figure*}
+    \includegraphics[width=\textwidth]{figures/m_hist.png}
+    \caption{Caption goes here.\label{fig:coll_hist_r}}
+\end{figure*}
+
 \section{Results} \label{sec:results}
+
+A side-by-side comparison of the final distribution in cylindrical coordinates of planetesimals from the CJ and EJ simulations is shown in figure \ref{fig:rtheta}.
+Gaps produced by the 3:1, 2:1 and 5:3 MMR with Jupiter are visible in both frames.
+In the EJ simulation, a gap in the vicinity of the 5:2 MMR is also visible.
+The non-axisymmetric character of the gaps reflects the fact that the planetesimals in the vicinity of the resonances (especially the 2:1) are having their eccentricities significantly pumped.
+(I don't think there should be any azimuthal structure to the gaps in the CJ simulation.
+This is probably a reflection of the fact that we need to run with smaller timesteps.) Although examining the spatial distribution of planetesimals near MMR in debris disks may be a viable way to detect unseen planets, we will not focus on this topic any longer as it has already been covered in detail in other studies \citep{2016ApJ...818..159T, 2018ApJ...857....3T}.
+It is worth noting, however that the spatial distribution of planetesimals shown in figure \ref{fig:rtheta} appears qualitatively similar to figures 3 and 4 in \citep{2016ApJ...818..159T}.
 

### 2019-09-06 main.tex
Add discussion of fig 2

@@
 
+The location of the mean motion resonances with Jupiter is most clearly visible when examining the semimajor axis-eccentricity distribution of the planetesimals.
+This is shown in figure \ref{fig:ae}, with the final snapshot from the CJ simulation shown on the left and EJ on the right.
+The solid vertical lines indicate the nominal locations of the mean motion resonances.
+Away from the resonance locations, the eccentricity dispersion grows via viscous stirring as energy from the Keplerian shearing of the disk is gradually transferred to random motions of planetesimals.
+The slight inward curving of the eccentricity peaks near the resonances is a consequence of the conservation of the Jacobi energy.
+As the semimajor axis of a planetesimal in MMR librates, the corresponding change in eccentricity is given by equation \ref{eq:tiss}.
+
+In the EJ simulation, the eccentricity remains enhanced between the MMRs due to the secular forcing effect of Jupiter.
+This also has the consequence of making the eccentricity spikes due to the 5:2 and (what's the MMR at 3.6 AU?) more prominent.
+The reason for this is that the libration width of a resonance generally scales with the eccentricity of the particle being perturbed.
+In a secularly forced disk, the eccentricity of particles affected by resonance is larger, which increases the resonance width and allows a larger region of the disk to be affected by a given resonance.
+Also visible in the EJ snapshot in figure \ref{fig:ae} are eccentricity spikes that extend below the background eccentricity distribution.
+This is a clear sign that planetesimals in the MMRs are librating.
+The phase of the libration is set by the resonant argument (maybe I should add an equation for the resonant argument in section 2).
+
 Outline for this section:

### 2019-09-10 main.tex
Add discussion of figure 3

@@
 
-\subsection{Secular Forcing}
+\subsection{Secular Forcing}\label{sec:sec_force}
 
@@
 
+An additional effect that the MMRs have on the orbits of planetesimals is visible in figure \ref{fig:long_ph}.
+This shows the semimajor axis distribution of planetesimals as a function of longitude of perihelion in the EJ simulation.
+As discussed in section \ref{sec:sec_force}, the eccentric orbit of Jupiter causes the perihelia of the planetesimal orbits to align with the giant perturber.
+The mean motion resonances, however, drive the rather vigorous precession of the orbits of planetesimals in their vicinity.
+Because the timescale of the resonances is much shorter than the timescale for secular forcing, the longitudinal orientations of orbits close to the MMRs are effectively randomized.
+The dashed horizontal lines in figure \ref{fig:long_ph} indicate the libration width of the MMRs at the forced eccentricity (given by the magnitude of equation \ref{eq:eforced}.
+The size of the zone of vigorous precession roughly matches the libration width of the MMRs.
+As will be discussed in the next session, the relative longitudinal orientation of the orbits has important implications for where and when planetesimal collisions occur at a given semimajor axis.
+
 Outline for this section:

### 2019-10-08 main.tex
Add discussion of figure 4, update plots with newly run EJ simulation

@@
 The size of the zone of vigorous precession roughly matches the libration width of the MMRs.
-As will be discussed in the next session, the relative longitudinal orientation of the orbits has important implications for where and when planetesimal collisions occur at a given semimajor axis.
+As will be discussed shortly, the relative longitudinal orientation of the orbits has important implications for where and when planetesimal collisions occur at a given semimajor axis.
+Not shown is the longitude of perihelia and semimajor axes of the bodies in the CJ simulation.
+Due to the lack of secular forcing, the orientations of the orbits of these bodes are effectively random.
+
+Next, we move on to examine the statistics of the collisions that occur.
+Figure \ref{fig:coll_hist_a} shows the distribution of semimajor axes of every collision that is resolved.
+Here, the semimajor axis of a collision is defined as the semimajor axis of the first body participating in the collision at the moment that it occurs.
+During a collision, the determination of which body is first and which is second is determined by the collision search tree in {\sc ChaNGa}.
+To ensure that this does not introduce any bias, we also constructed figure \ref{fig:coll_hist_a} using the orbital parameters of the second body and found no qualitative difference.
+By examining the semimajor axis distribution of the collisions, it is easy to see how the MMRs affect the collision rates.
+The dashed lines again represent the libration width of each resonance and are meant to show its range of influence.
+In both the circular and eccentric Jupiter simulations, the collision rate is clearly enhanced interior to the 2:1 MMR.
+Interestingly, the 3:1 MMR only appears to have a noticeable influence on the collision rate in the EJ simulation.
+(Better check if this is still true when I rerun CJ with smaller steps).
+In both cases, the 5:3 MMR appears to slightly enhance the collision rate interior to the nominal resonance location.
+It is important to keep in mind, however that the libration width of sufficiently eccentric particles near the 5:3 MMR may extend beyond the outer edge of the disk and introduce nonphysical boundary effects.
 

### 2019-10-08 makeFig.py

@@ -83,11 +83,19 @@ coll_dist_c1 = np.sqrt(x_c_c1**2 + y_c_c1**2)
 a_c_c1, e_c_c1, inc_c_c1, Omega_c_c1, omega_c_c1, M_c_c1 = \
     OrbitTools.cart2kepX(x_c_c1, y_c_c1, z_c_c1, vx_c_c1, vy_c_c1, vz_c_c1, mc_c, m1_c)
 x_c_c2, y_c_c2, z_c_c2 = coll_c['x2x'], coll_c['x2y'], coll_c['x2z']
-vx_c_c2, vy_c_c2, vz_c_c2 = coll_c['v2x'], coll_c['v2y'], coll_c['v2z']
+#vx_c_c2, vy_c_c2, vz_c_c2 = coll_c['v2x'], coll_c['v2y'], coll_c['v2z']
+
+# Oops, the ChaNGa output for collider 2's velocity is messed up. Fortunately, we can
+# get the correct value from v1 and vNew
+vx_c_c2 = (coll_c['m1']*coll_c['v1x'] - (coll_c['m1'] + coll_c['m2'])*coll_c['vNewx'])/coll_c['m2']
+vy_c_c2 = (coll_c['m1']*coll_c['v1y'] - (coll_c['m1'] + coll_c['m2'])*coll_c['vNewy'])/coll_c['m2']
+vz_c_c2 = (coll_c['m1']*coll_c['v1z'] - (coll_c['m1'] + coll_c['m2'])*coll_c['vNewz'])/coll_c['m2']
+
 m2_c = coll_c['m2']
 coll_dist_c2 = np.sqrt(x_c_c2**2 + y_c_c2**2)
 a_c_c2, e_c_c2, inc_c_c2, Omega_c_c2, omega_c_c2, M_c_c2 = \
     OrbitTools.cart2kepX(x_c_c2, y_c_c2, z_c_c2, vx_c_c2, vy_c_c2, vz_c_c2, mc_c, m2_c)
+
 coll_e = pd.read_csv(path + 'hkshiftfull/collisions')
 coll_e = coll_e[coll_e['time']/(2*np.pi) <= 10000]
 mc_e = s0_e['mass'][0]
@@ -98,7 +106,13 @@ coll_dist_e1 = np.sqrt(x_c_e1**2 + y_c_e1**2)
 a_c_e1, e_c_e1, inc_c_e1, Omega_c_e1, omega_c_e1, M_c_e1 = \
[…]

### 2019-10-08 main.tex
Add discusion of figure 5

@@
     \includegraphics[width=\textwidth]{figures/m_hist.png}
-    \caption{Caption goes here.\label{fig:coll_hist_r}}
+    \caption{Caption goes here.\label{fig:m_hist}}
 \end{figure*}
@@
 In both the circular and eccentric Jupiter simulations, the collision rate is clearly enhanced interior to the 2:1 MMR.
-Interestingly, the 3:1 MMR only appears to have a noticeable influence on the collision rate in the EJ simulation.
+Interestingly, the 3:1 MMR only appears to have a noticemable influence on the collision rate in the EJ simulation.
 (Better check if this is still true when I rerun CJ with smaller steps).
@@
 It is important to keep in mind, however that the libration width of sufficiently eccentric particles near the 5:3 MMR may extend beyond the outer edge of the disk and introduce nonphysical boundary effects.
+
+Although the semimajor axis of a particle at the moment of collision provides useful information about how the mean motion resonances affect the collision rate in the disk, this information alone is not enough to predict where the second generation dust that is produced will end up.
+To do so, we will operate under the assumption that dust grains produced by collision events will quickly couple to the gas and attain a circular orbit.
+This assumption, which will be further justified in section \ref{sec:dust}, allows to map the radial variation in the dust surface density to the radial position of the collisions.
+This is shown in figure \ref{fig:coll_hist_r}, where the histograms indicate the x and y coordinates of a body at the moment that it undergoes a collision.
+Most notably, many of the prominent features visible in figure \ref{fig:coll_hist_a} no longer appear.
+This is due to the fact that the orbits of colliding bodies have a wide range of eccentricities.
+In the CJ simulation, there are prominent dips in the collision rate centered around the 2:1 and 3:1 MMR.
+Although still visible in the EJ simulation, these dips are much wider and shallower.
+This is due to the fact that particles near the edge of the region of influence of the MMRs have a higher eccentricity in the secularly forced disk.
+Because a larger eccentricity allows collisions to happen over a broader range of radial distances, the sharp, well-defined edges of the trough centered around the resonances becomes washed out.
 

### 2019-10-09 main.tex
Add discussion of figure 6

@@
 
+As is seen in figure \ref{fig:long_ph}, the relatively fast precession rates induced by the mean motion resonances overpower the secular forcing by Jupiter and randomize the orientation of orbits near the nominal resonance locations.
+Of course, this difference in longitude of perihelion of bodies inside and outside of resonance is only present in the EJ simulation because the Jupiter imposes zero forced eccentricity on the disk when it has a circular orbit.
+Figure \ref{fig:m_hist} provides another view of the difference in collision statistics inside and outside and of resonance.
+The top row shows the mean anomaly of bodies at the moment that they undergo a collision.
+The left side corresponds to collisions that occur inside of the 2:1 MMR and the right side corresponds to collisions that occur with a semimajor axis between 2.7 and 2.8 AU, which is meant to well away from the influence of any resonances.
+The semimajor axis window size in the right hand panel is chosen so that both histograms contain the same total number of collisions.
+The bottom row shows the difference in the mean anomaly between pairs of bodies at the moment that they collide.
+
+In this figure, the most notable difference between the collision statistics inside and outside of resonance is that collisions inside of resonance preferentially happen at perhielion.
+In addition, the two bodies that collide tend to be at a similar orbital phase.
+Outside of resonance, however, there are no significant trends in the mean anomaly at collision or in the mean anomaly difference.
+The difference in collision statistics between these two regions of the disk can be explained in the following way: for $\approx$ 100 km bodies, gravitational focusing plays a significant role in controlling the collision rate.
+In this regime, the collision rate is given by equation \ref{eq:safronov}, is larger for small relative velocities $v_{p}$ between planetesimals.
+At perihelion, relative velocities between planetesimals are largest (wait, this is backwards, why do collisions tend to happen at perihelion?).
+When the longitude of perhelia for adjacent orbits are aligned, which is true away from the resonances, bodies will always tend to have similar relative velocities, regardless of orbital phase.
+Therefore, the collision rate should no longer vary with mean anomaly, which is exactly what is shown in the top right panel of figure \ref{fig:m_hist}.
+(But shouldnt you see points clustered around deltaM = 0 in the bottom right panel then?)
+
+\subsection{Comparison With Analytic Safronov Collision Rate}\label{sec:saf}
+
 Outline for this section:

### 2019-10-10 main.tex
Update figure 6 and explanation

--- 2019-10-08 main.tex
@@
 
+As is seen in figure \ref{fig:long_ph}, the relatively fast precession rates induced by the mean motion resonances overpower the secular forcing by Jupiter and randomize the orientation of orbits near the nominal resonance locations.
+Of course, this difference in longitude of perihelion of bodies inside and outside of resonance is only present in the EJ simulation because the Jupiter imposes zero forced eccentricity on the disk when it has a circular orbit.
+Figure \ref{fig:m_hist} provides another view of the difference in collision statistics inside and outside and of resonance.
+This shows the mean anomalies of bodies at the moment that they undergo a collision.
+The top row corresponds to the EJ simulation and the bottom rom corresponds to the CJ simulation.
+The left panels correspond to collisions that occur inside of the 2:1 MMR and the right panels are for collisions that occur with a semimajor axis between 2.7 and 2.8 AU, which is meant to well away from the influence of any resonances.
+The semimajor axis window size in the right hand panel is chosen so that both histograms contain the same total number of collisions.
+
+The qualitative differences between these four panels can be explained in the following way: for $\approx$ 100 km bodies, gravitational focusing plays a significant role in setting the collision rate.
+In regions of the disk where the rms eccentricity is small (which corresponds to a small velocity dispersion), the collision rate should be enhanced (see equation \ref{eq:safronov}).
+Inside of resonances, planetesimals undergo large amplitude libration which pumps up the eccentricity dispersion.
+This effect is visible in figure \ref{fig:ae} for both the EJ and CJ simulation.
+This implies that the collision rate should be geometric, and not depend on the velocity dispersion near resonances.
+When this is true, collisions should preferentially occur near perihelion.
+The reason for this is that in the geometric limit, the collision probability scales with the ratio between the geometric cross section of the two planetesimals and the surface area of a sphere with radius $r$, where $r$ is the distance between the bodies and the central star.
+This ratio, and therefore the collision probability, is largest when $r$ is minimized (see \citet{2003AJ....125.2692L}).
+The fact both of the left-hand panels in figure \ref{fig:m_hist} show a distinct lack of collisions near aphelion is consistent with this explanation.
+
+Note that this trend is not present in the right-hand panels of figure \ref{fig:m_hist}.
+In the case with Jupiter on a circular orbit (bottom right panel), there is a spike in the collision rate both at perihelion and aphelion.
+The perihelion spike is still due to the geometric argument presented in the previous paragraph.
+The aphelion spike is due to the effect of gravitational focusing.
+At aphelion, bodies achieve their minimum speed.
+This lowers the relative velocity between planetesimals, which according to equation \ref{eq:safronov} should enhance the collision rate.
+Note that the collision rate does not exhibit much dependence on mean anomaly outside of resonance in the case with Jupiter on an eccentric orbit (top right panel).
+This is due to the secular forcing by Jupiter, which aligns the longitude of perihelia of adjacent planetesimals.
+The result of this is that bodies maintain similar relative speeds over the course of an orbit, even though the orbit is eccentric.
+This lack of variation in the relative speeds makes collisions equally likely at any orbital phase.
+
+\subsection{Comparison With Analytic Safronov Collision Rate}\label{sec:saf}
+
 Outline for this section:

### 2019-10-10 makeFig.py

@@ -263,23 +263,23 @@ def make_m_hist():
 	ax[0,1].set_ylim(0, np.max(hist)*1.1)
 	ax[0,1].set_title(str(a21) + ' < a < ' + str(a22) + ' (' + str(len(M_c_e1[mask])) + ' coll)')
 
-	mask = np.logical_and(a_c_e1 > a11, a_c_e1 < a12)
-	hist, bins = np.histogram(ang_diff(M_c_e1[mask], M_c_e2[mask]), 
-	                          bins=np.linspace(-np.pi, np.pi, num=20))
+	mask = np.logical_and(a_c_c1 > a11, a_c_c1 < a12)
+	hist, bins = np.histogram(M_c_c1[mask], bins=np.linspace(0, 2*np.pi, num=20))
 	bins = 0.5*(bins[1:] + bins[:-1])
 	ax[1,0].plot(bins, hist, linestyle='steps-mid')
-	ax[1,0].set_xlabel(r'$\Delta$M')
+	ax[1,0].set_xlabel('Mean Anomaly')
 	ax[1,0].set_ylabel('Number of Collisions')
 	ax[1,0].set_ylim(0, np.max(hist)*1.1)
+	ax[1,0].set_title(str(a11) + ' < a < ' + str(a12) + ' (' + str(len(M_c_c1[mask])) + ' coll)')
 
-	mask = np.logical_and(a_c_e1 > a21, a_c_e1 < a22)
-	hist, bins = np.histogram(ang_diff(M_c_e1[mask], M_c_e2[mask]), 
-	                          bins=np.linspace(-np.pi, np.pi, num=20))
+	mask = np.logical_and(a_c_c1 > a21, a_c_c1 < a22)
+	hist, bins = np.histogram(M_c_c1[mask], bins=np.linspace(0, 2*np.pi, num=20))
 	bins = 0.5*(bins[1:] + bins[:-1])
 	ax[1,1].plot(bins, hist, linestyle='steps-mid')
-	ax[1,1].set_xlabel(r'$\Delta$M')
+	ax[1,1].set_xlabel('Mean Anomaly')
 	ax[1,1].set_ylabel('Number of Collisions')
 	ax[1,1].set_ylim(0, np.max(hist)*1.1)
+	ax[1,1].set_title(str(a21) + ' < a < ' + str(a22) + ' (' + str(len(M_c_c1[mask])) + ' coll)')
 	plt.savefig(file_str, format=fmt, bbox_inches='tight')
 
 make_rtheta()

### 2019-11-18 makeFig.py
Update figures to reflect finished simulations

@@ -219,7 +219,7 @@ def make_coll_hist_r():
 	coll_hist_r_e, coll_bins_r_e = np.histogram(coll_dist_e1, bins=np.linspace(a_in, a_out, num=60))
 	coll_bins_r_e = 0.5*(coll_bins_r_e[1:] + coll_bins_r_e[:-1])
 
-	fig, (ax1, ax2) = plt.subplots(figsize=(16,6), nrows=1, ncols=2, sharey=True)
+	fig, (ax1, ax2) = plt.subplots(figsize=(16,6), nrows=1, ncols=2, sharey=False)
 	ax1.plot(coll_bins_r_c, coll_hist_r_c, linestyle='steps-mid')
 	plot_res(ax1)
 	ax1.set_xlabel('Heliocentric Distance [AU]')

### 2019-11-18 main.tex
Update reference to our paper

@@
 Under the effect of MMR, a body will undergo oscillations in semi-major axis and eccentricity.
-So long as the gravitational force on the body is dominated by the central star and the perturbing body, the amplitude of the oscillations in semi-major axis can be described using the pendulum approximation (see equation 6 in \citet{2018arXiv181007201W}).
+So long as the gravitational force on the body is dominated by the central star and the perturbing body, the amplitude of the oscillations in semi-major axis can be described using the pendulum approximation (see equation 6 in \citet{2019MNRAS.489.2159W}).
 This amplitude can be thought of as the 'width' over which the perturbations of the resonance are effective.
@@
 We have also recently modified {\sc ChaNGa} to handle solid-body collisions.
-A full description of the collision module implementation can be found in \citet{2018arXiv181007201W}.
+A full description of the collision module implementation can be found in \citet{2019MNRAS.489.2159W}.
 

### 2019-11-27 main.tex
Update discussion of figures 4 and 5

@@
 In both the circular and eccentric Jupiter simulations, the collision rate is clearly enhanced interior to the 2:1 MMR.
-Interestingly, the 3:1 MMR only appears to have a noticemable influence on the collision rate in the EJ simulation.
-(Better check if this is still true when I rerun CJ with smaller steps).
-In both cases, the 5:3 MMR appears to slightly enhance the collision rate interior to the nominal resonance location.
-It is important to keep in mind, however that the libration width of sufficiently eccentric particles near the 5:3 MMR may extend beyond the outer edge of the disk and introduce nonphysical boundary effects.
+The 3:1 MMR only appears to have a noticeable influence on the collision rate in the EJ simulation.
+In both cases, although the 5:3 MMR has a clear influence on the on the semimajor-axis eccentricity distribution, it does not leave a measureable imprint on the collision rate.
+It is important to point out, however, that the libration width of sufficiently eccentric particles near the 5:3 MMR may extend beyond the outer edge of the disk and introduce boundary effects.
 
@@
 This is shown in figure \ref{fig:coll_hist_r}, where the histograms indicate the x and y coordinates of a body at the moment that it undergoes a collision.
-Most notably, many of the prominent features visible in figure \ref{fig:coll_hist_a} no longer appear.
-This is due to the fact that the orbits of colliding bodies have a wide range of eccentricities.
-In the CJ simulation, there are prominent dips in the collision rate centered around the 2:1 and 3:1 MMR.
-Although still visible in the EJ simulation, these dips are much wider and shallower.
-This is due to the fact that particles near the edge of the region of influence of the MMRs have a higher eccentricity in the secularly forced disk.
-Because a larger eccentricity allows collisions to happen over a broader range of radial distances, the sharp, well-defined edges of the trough centered around the resonances becomes washed out.
+
+Most notably, the prominent features visible in figure \ref{fig:coll_hist_a} adjacent to the 2:1 MMR no longer appear.
+This is due to the fact that the orbits of bodies in the 2:1 MMR have a wide range of eccentricities and therefore have the potential to undergo collisions at a wide range of heliocentric distances.
+In the CJ simulation, there is a prominent dip in the collision rate near the 2:1 MMR.
+This feature is still moderately visible in the EJ simulation, but the dip is much wider and shallower.
+The random orientations of the orbits inside of the resonance (see figure \ref{fig:long_ph}), combined with the forced eccentricites of planetesimals adjacent to the resonance weakens the dip near the 2:1 MMR seen in the left hand panel of figure \ref{fig:coll_hist_a}.
+Additionally, there is a double-pronged feature in the collision rate near the 3:1 MMR in the EJ simulation.
+The radial distance of these two prongs corresponds to the maximum radial excursion that a planetesimal at the 3:1 MMR with an eccentricity set by secular forcing with Jupiter undergoes.
+(Need more explanation of why this happens)
 

### 2019-11-29 makeFig.py
Add todo comments to document, ignore collisions during first few hundred Jupiter orbits

@@ -13,6 +13,8 @@ from astropy.constants import G
 simT = u.year/(2*np.pi)
 simV = u.AU / simT
 
+from scipy import stats
+
 import sys
 sys.path.insert(0, '../OrbitTools/')
 import OrbitTools
@@ -72,9 +74,22 @@ s_e_files = np.array([path + 'hkshiftfull/hkshiftfull.ic']+ \
 	                  ns.natsorted(gl.glob(path + 'hkshiftfull/*.[0-9]*[0-9]')))
 s0_e = pb.load(s_e_files[0])
 
+# Skip the first 2000 years of the collision output. There is a transient feature interior
+# to the 3:1 MMR in the EJ simulation before this time.
+t_skip = 2000
+t_max = 5000
+
+a_in, a_out = 2.2, 3.8
+nbins = 30
+
+# Regenerate existing plots?
+clobber = True
+fmt = 'png'
+s = 0.005
+
 # Collision data
 coll_c = pd.read_csv(path + 'hkshiftfullJupCirc/collisions')
-coll_c = coll_c[coll_c['time']/(2*np.pi) <= 10000]
+coll_c = coll_c[np.logical_and(coll_c['time']/(2*np.pi) <= t_max, coll_c['time']/(2*np.pi) >= t_skip)]
 mc_c = s0_c['mass'][0]
 x_c_c1, y_c_c1, z_c_c1 = coll_c['x1x'], coll_c['x1y'], coll_c['x1z']
 vx_c_c1, vy_c_c1, vz_c_c1 = coll_c['v1x'], coll_c['v1y'], coll_c['v1z']
@@ -97,7 +112,7 @@ a_c_c2, e_c_c2, inc_c_c2, Omega_c_c2, omega_c_c2, M_c_c2 = \
     OrbitTools.cart2kepX(x_c_c2, y_c_c2, z_c_c2, vx_c_c2, vy_c_c2, vz_c_c2, mc_c, m2_c)
 
 coll_e = pd.read_csv(path + 'hkshiftfull/collisions')
-coll_e = coll_e[coll_e['time']/(2*np.pi) <= 10000]
+coll_e = coll_e[np.logical_and(coll_e['time']/(2*np.pi) <= t_max, coll_e['time']/(2*np.pi) >= t_skip)]
 mc_e = s0_e['mass'][0]
 x_c_e1, y_c_e1, z_c_e1 = coll_e['x1x'], coll_e['x1y'], coll_e['x1z']
[…]

### 2019-12-04 main.tex
Add todo comments to document, ignore collisions during first few hundred Jupiter orbits
Break paragraphs up into multiple lines

@@
 \begin{abstract}
-A perturbing planet can leave a lasting imprint a debris disk near the locations of mean motion resonances (MMRs).
-Unfortunately, the planetesimal-sized objects that make up the majority of these disks are extremely difficult to directly observe.
-Dust created from collisions between planetesimals may be a much better way to constrain the structure of these disks.
-We use a direct N-body model to measure planetesimal collision rates in a dynamically cold debris disk composed of 150 km bodies.
-Even though the eccentricities are pumped at the nominal resonance locations, conservation of the Jacobi energy pushes planetesimals inward and enhances the collision rate adjacent to the resonances.
-In addition, we find that the collision rate is severely throttled near the 3:1 MMR and that a tightly wound spiral wave is launched from this location.
+A perturbing planet can leave a lasting imprint a debris disk near the locations of mean motion resonances (MMRs). Unfortunately,
+the planetesimal-sized objects that make up the majority of these disks are extremely difficult to directly observe. Dust created from
+collisions between planetesimals may be a much better way to constrain the structure of these disks. We use a direct N-body model
+to measure planetesimal collision rates in a dynamically cold debris disk composed of 150 km bodies. Even though the eccentricities
+are pumped at the nominal resonance locations, conservation of the Jacobi energy pushes planetesimals inward and enhances the
+collision rate adjacent to the resonances. In addition, we find that the collision rate is severely throttled near the 3:1 MMR and that a
+tightly wound spiral wave is launched from this location.
 \end{abstract}
@@
 
-Recent observations of circumstellar disks by ALMA have revealed a rich variety of substructure in the millimeter wavelength contiunuum emission.
-Features such as gaps and asymmetries \citep{2015ApJ...808L...3A, 2016Sci...353.1519P, PhysRevLett.117.251101, 2016ApJ...820L..40A, 2016Natur.535..258C} in the emission provide diagnostics for the physical processes that drive the evolution of the disks.
-At these wavelengths, much of this light is produced by second-generation debris generated through collisional grinding of planetesimals \citep[see][]{2008ARA&A..46..339W}.
+%Things to change/do:
+%    Transient feature in EJ collision rate before 2000 years. Only want to look at collisions after this time. Justify the cutoff (maybe something to do with precession in 3:1 MMR?)
+%    Safronov and Nbody collision rates. Not matching up well near resonance. The 'wings' from the resonances mess up calculation of velocity dispersion. Maybe do comparison
+%       no grav focusing?
+%    Get Aaron to make some dust emission makes from the Nbody collision histograms
+%    Can we scale these results to any size system? Get rid of units. How to justify planetesimal size?
 
-In some cases, these gap features are argued to be an indicator for the presence of a giant planet, either embedded in the disk \citep{2015MNRAS.453L..73D} or orbiting externally.
-An giant perturber can influence the structure of the dust emission in a number of ways.
-A misaligned giant planet can produce nonaxisymmetric features such as warps \citep{2001A&A...370..447A}.
-Highly eccentric perturbers can produce even more complicated structures through secular perturbations \citep{2014MNRAS.443.2541P, 2015MNRAS.448.3679P}.
-Mean motion resonances (MMRs) have been shown to open gaps as well \citep{2015ApJ...798...83N, 2016ApJ...818..159T, 2018ApJ...857....3T}.
+Recent observations of circumstellar disks by ALMA have revealed a rich variety of substructure in the millimeter wavelength
+contiunuum emission. Features such as gaps and asymmetries 
+\citep{2015ApJ...808L...3A, 2016Sci...353.1519P, PhysRevLett.117.251101, 2016ApJ...820L..40A, 2016Natur.535..258C} in the 
+emission provide diagnostics for the physical processes that drive the evolution of the disks. At these wavelengths, much of this light 
+is produced by second-generation debris generated through collisional grinding of planetesimals
+\citep[see][]{2008ARA&A..46..339W}.
 
-The dynamics governing the motion of bodies near MMRs is extremely nonlinear, as is determining what the collision rates between planetesimals should look like in these regions.
-For a collection of bodies massive enough to experience the effects of gravitational focusing, a large eccentricity dispersion tends to reduce the probability of collision, while enhancements in surface density tends to increase it.
-Due to conservation of the Jacobi energy, MMRs simultaneously enhance the local eccentricity dispersion and also enhance the surface density adjacent to the resonance \citep{2000Icar..143...45R, 2017ApJ...850..103B}.
+In some cases, these gap features are argued to be an indicator for the presence of a giant planet, either embedded in the disk 
+\citep{2015MNRAS.453L..73D} or orbiting externally. An giant perturber can influence the structure of the dust emission in a number 
+of ways. A misaligned giant planet can produce nonaxisymmetric features such as warps \citep{2001A&A...370..447A}. Highly 
+eccentric perturbers can produce even more complicated structures through secular perturbations \citep{2014MNRAS.443.2541P, 
+2015MNRAS.448.3679P}. Mean motion resonances (MMRs) have been shown to open gaps as well
+\citep{2015ApJ...798...83N, 2016ApJ...818..159T, 2018ApJ...857....3T}.
 
-Because the second generation dust production is driven by the planetesimal collision rate, it is crucial to understand how the dynamics that drive collisions works.
-In particular, it is not obvious how to link the readily observable thermal emission from dust in protoplanetary disks to the presence of a perturbing giant planet.
-Due to its nonlinearity, this problem is best studied with N-body simulations.
-Unfortunately, collision detection in an N-body simulation is extremely computationally expensive.
-So far, studies of planetesimal dynamics near MMRs have involved either collisionless test particles \citep{2017ApJ...850..103B, 2016ApJ...818..159T, 2018ApJ...857....3T} or severely limited integration times \citep{2000Icar..143...45R}.
+The dynamics governing the motion of bodies near MMRs is extremely nonlinear, as is determining what the collision rates between 
+planetesimals should look like in these regions. For a collection of bodies massive enough to experience the effects of gravitational 
+focusing, a large eccentricity dispersion tends to reduce the probability of collision, while enhancements in surface density tends to 
+increase it. Due to conservation of the Jacobi energy, MMRs simultaneously enhance the local eccentricity dispersion and also 
+enhance the surface density adjacent to the resonance \citep{2000Icar..143...45R, 2017ApJ...850..103B}.
 
-To further elucidate this subject, we use the tree based N-body code {\sc ChaNGa} \citep{2008IEEEpds...ChaNGa, 2015AphCom..2..1} to follow the collisional evolution of a planetesimal disk under the gravitational influence of a Jupiter sized body.
-Because particle positions are sorted into a tree structure, neighbor finding and collision detection can be done quickly and efficiently.
-This considerably relaxes the constraints on resolution and integration time.
-With this toolset, we explore the collision rate structure of the planetesimal disk in the vicinity of mean motion resonances.
+Because the second generation dust production is driven by the planetesimal collision rate, it is crucial to understand how the 
+dynamics that drive collisions works. In particular, it is not obvious how to link the readily observable thermal emission from dust in 
+protoplanetary disks to the presence of a perturbing giant planet. Due to its nonlinearity, this problem is best studied with N-body 
+simulations. Unfortunately, collision detection in an N-body simulation is extremely computationally expensive. So far, studies of 
+planetesimal dynamics near MMRs have involved either collisionless test particles \citep{2017ApJ...850..103B, 2016ApJ...818..159T, 
+2018ApJ...857....3T} or severely limited integration times \citep{2000Icar..143...45R}.
 
-This work is organized in the following way.
-In section \ref{sec:dynamics} we provide an overview of the dynamics that drive the evolution of a planetesimal disk under the gravitational influence of an external perturber.
-In section \ref{sec:setup} we describe the N-body code we use and describe how we constructed the initial conditions for the two simulations that are run: one with a perturber on a circular orbit and one with an eccentric perturber.
-Section \ref{sec:results} goes on to explore the results of the two, with particular focus on the radial variation in the collision rates.
-In section \ref{sec:dust}, we use the positions of the collision events to construct a map of second generation dust emission, under the assumption that dust grains produced by collisions will immediately couple to the gas and circularize their orbits.
-Finally, we assess the observability of features in the dust emission due to mean motion resonances and conclude in section \ref{sec:discuss}.
+To further elucidate this subject, we use the tree based N-body code {\sc ChaNGa}
+\citep{2008IEEEpds...ChaNGa, 2015AphCom..2..1} to follow the collisional evolution of a planetesimal disk under the gravitational 
+influence of a Jupiter sized body. Because particle positions are sorted into a tree structure, neighbor finding and collision detection 
+can be done quickly and efficiently. This considerably relaxes the constraints on resolution and integration time. With this toolset, we 
+explore the collision rate structure of the planetesimal disk in the vicinity of mean motion resonances.
+
+This work is organized in the following way. In section \ref{sec:dynamics} we provide an overview of the dynamics that drive the 
+evolution of a planetesimal disk under the gravitational influence of an external perturber. In section \ref{sec:setup} we describe the 
+N-body code we use and describe how we constructed the initial conditions for the two simulations that are run: one with a perturber 
+on a circular orbit and one with an eccentric perturber. Section \ref{sec:results} goes on to explore the results of the two, with 
+particular focus on the radial variation in the collision rates. In section \ref{sec:dust}, we use the positions of the collision events to 
+construct a map of second generation dust emission, under the assumption that dust grains produced by collisions will immediately 
+couple to the gas and circularize their orbits. Finally, we assess the observability of features in the dust emission due to mean motion 
+resonances and conclude in section \ref{sec:discuss}.
 
@@
 
-We begin by making the assumption that a typical encounter between planetesimals in a disk is well-described by two-body dynamics.
-So long as the random velocities of planetesimals $v_{p}$ are large compared to the Hill velocity of a planetesimal $v_{h} = \sqrt{G m_{p} / r_{h}}$, where $r_{h}$ is the Hill radius, the gravitational field of the central star will play an insignificant role and can be safely ignored.
-In this case and assuming equal mass bodies, the collision rate is given by \citep{1967SvA....10..650S}
+We begin by making the assumption that a typical encounter between planetesimals in a disk is well-described by two-body 
+dynamics. So long as the random velocities of planetesimals $v_{p}$ are large compared to the Hill velocity of a planetesimal $v_{h} 
+= \sqrt{G m_{p} / r_{h}}$, where $r_{h}$ is the Hill radius, the gravitational field of the central star will play an insignificant role and 
+can be safely ignored. In this case and assuming equal mass bodies, the collision rate is given by \citep{1967SvA....10..650S}
 
@@
 
-In the absence of a proper treatment of collision detection, equation \ref{eq:safronov} can be used to make a local estimate of the collision rate in an N-body simulation using only the positions and velocities of particles.
-This has been done in other studies \citep{2017ApJ...850..103B} (any other examples?), but requires bulk averaging of the phase space properties of particles, which may mask important information and blur out features.
-We will revisit equation \ref{eq:safronov} in section \ref{sec:results} to test how well the collision rate near mean motion resonances is described by this framework.
+In the absence of a proper treatment of collision detection, equation \ref{eq:safronov} can be used to make a local estimate of the 
+collision rate in an N-body simulation using only the positions and velocities of particles. This has been done in other studies 
+\citep{2017ApJ...850..103B} (any other examples?), but requires bulk averaging of the phase space properties of particles, which 
+may mask important information and blur out features. We will revisit equation \ref{eq:safronov} in section \ref{sec:results} to test 
+how well the collision rate near mean motion resonances is described by this framework.
 
@@
 
-The most direct and widespread effect that a giant perturber will have on a planetesimal disk is through secular forcing of the eccentricities of the planetesimals.
-This will cause the complex eccentricities of the planetesimals to take on a time independent forced value, given by \citep{1999ApJ...527..918W} as
+The most direct and widespread effect that a giant perturber will have on a planetesimal disk is through secular forcing of the 
+eccentricities of the planetesimals. This will cause the complex eccentricities of the planetesimals to take on a time independent 
+forced value, given by \citep{1999ApJ...527..918W} as
 
@@
 
-\noindent Here, $\alpha = a_{g} / a$ where $a_{g}$ and $a$ are the semi-major axes of the giant planet and the planetesimal, respectively.
-$e_{g}$ and $\omega_{g}$ are the eccentricity and longitude of pericenter of the giant and $b^{j}_{s} (\alpha)$ is a Laplace coefficient given by \citep{2000ssd..book.....M} as
+\noindent Here, $\alpha = a_{g} / a$ where $a_{g}$ and $a$ are the semi-major axes of the giant planet and the planetesimal, 
+respectively. $e_{g}$ and $\omega_{g}$ are the eccentricity and longitude of pericenter of the giant and $b^{j}_{s} (\alpha)$ is a 
+Laplace coefficient given by \citep{2000ssd..book.....M} as
 
@@
 
-Ignoring secular and mean motion resonances, equation \ref{eq:eforced} will completely describe the eccentricities and pericenter orientations of the orbits of the planetesimals.
-Additional forces due to two-body scattering between planetesimals, along with aerodynamic gas drag will add an additional free component to the complex eccentricity, which will be randomly oriented.
-The magnitude of the free eccentricity describes how dynamically hot the planetesimal disk is and sets the random encounter speeds of planetesimals.
-When the dynamical excitation of the disk is driven by gravitational stirring, the magnitude of the free eccentricity can be described by a Rayleigh distribution \citep{1992Icar...96..107I}.
+Ignoring secular and mean motion resonances, equation \ref{eq:eforced} will completely describe the eccentricities and pericenter 
+orientations of the orbits of the planetesimals. Additional forces due to two-body scattering between planetesimals, along with 
+aerodynamic gas drag will add an additional free component to the complex eccentricity, which will be randomly oriented. The 
+magnitude of the free eccentricity describes how dynamically hot the planetesimal disk is and sets the random encounter speeds of 
+planetesimals. When the dynamical excitation of the disk is driven by gravitational stirring, the magnitude of the free eccentricity can 
+be described by a Rayleigh distribution \citep{1992Icar...96..107I}.
 
@@
 
-In regions where there are commensurabilities between frequencies, secular theory breaks down and bodies are subject to strong perturbations.
-For the purposes of this study, we will ignore secular resonances, which generally occur on rather large timescales and will focus on mean motion resonances (MMRs).
-A MMR occurs  when the orbital period ratio between two bodies is sufficiently close to
+In regions where there are commensurabilities between frequencies, secular theory breaks down and bodies are subject to strong 
+perturbations. For the purposes of this study, we will ignore secular resonances, which generally occur on rather large timescales 
+and will focus on mean motion resonances (MMRs). A MMR occurs  when the orbital period ratio between two bodies is sufficiently 
+close to
 
@@
 
-\noindent where  $p$ and $q$ are integers $>$ 0 and the unprimed and primed quantities correspond to the perturber and the body being perturbed, respectively.
-If the gravitational potential of the system is dominated by the central star, the condition for MMR is set by the semi-major axes of the two bodies by
+\noindent where  $p$ and $q$ are integers $>$ 0 and the unprimed and primed quantities correspond to the perturber and the body 
+being perturbed, respectively. If the gravitational potential of the system is dominated by the central star, the condition for MMR is set 
+by the semi-major axes of the two bodies by
 
@@
 
-Under the effect of MMR, a body will undergo oscillations in semi-major axis and eccentricity.
-So long as the gravitational force on the body is dominated by the central star and the perturbing body, the amplitude of the oscillations in semi-major axis can be described using the pendulum approximation (see equation 6 in \citet{2019MNRAS.489.2159W}).
-This amplitude can be thought of as the 'width' over which the perturbations of the resonance are effective.
-Variations in eccentricity follow the semi-major axis variations according to the Tisserand relation
+Under the effect of MMR, a body will undergo oscillations in semi-major axis and eccentricity. So long as the gravitational force on 
+the body is dominated by the central star and the perturbing body, the amplitude of the oscillations in semi-major axis can be 
+described using the pendulum approximation (see equation 6 in \citet{2019MNRAS.489.2159W}). This amplitude can be thought of 
+as the 'width' over which the perturbations of the resonance are effective. Variations in eccentricity follow the semi-major axis 
+variations according to the Tisserand relation
 
@@
 
-The net result of this is that isolated MMRs will produce 'spikes' in the semi-major axis vs eccentricity distribution of a planetesimal disk.
-Following equation \ref{eq:tiss}, these spikes will tend to slightly curve away from the perturbing body.
-As planetesimals undergo two-body scattering events with other bodies, the variations in semi-major axis and eccentricity due to resonances can become permanent.
-This tends to lower the surface density of the disk near the locations of resonances, while producing a pileup of eccentric bodies adjacent to the MMR.
-The enhanced surface density will increase the collision rate, while the large eccentricity dispersion will lower it due to the decreased effectiveness of gravitational focusing.
-Due to these competing effects, along with the complicated dynamics that are likely at play near the edge of the resonant region, we turn to a direct N-body treatment to better understand how the collision rate varies in the vicinity of a MMR.
+The net result of this is that isolated MMRs will produce 'spikes' in the semi-major axis vs eccentricity distribution of a planetesimal 
+disk. Following equation \ref{eq:tiss}, these spikes will tend to slightly curve away from the perturbing body. As planetesimals 
+undergo two-body scattering events with other bodies, the variations in semi-major axis and eccentricity due to resonances can 
+become permanent. This tends to lower the surface density of the disk near the locations of resonances, while producing a pileup of 
+eccentric bodies adjacent to the MMR. The enhanced surface density will increase the collision rate, while the large eccentricity 
+dispersion will lower it due to the decreased effectiveness of gravitational focusing. Due to these competing effects, along with the 
+complicated dynamics that are likely at play near the edge of the resonant region, we turn to a direct N-body treatment to better 
+understand how the collision rate varies in the vicinity of a MMR.
 
@@
 
-To follow the dynamical and collisional evolution of a planetesimal disk, we use the highly parallel N-body code {\sc ChaNGa} \footnote{A public version of {\sc ChaNGa} can be downloaded from \url{http://www-hpcc.astro.washington.edu/tools/ChaNGa.html}}.
-This code, which is written in the {\sc CHARM++} parallel programming language, was originally designed for cosmology simulations and has been shown to perform well on up to half a million processors \citep{2015AphCom..2..1}.
-{\sc ChaNGa} calculates gravitational forces using a modified Barnes-Hut \citep{1986Natur.324..446B} tree with hexadecapole expansions of the moments.
-All of the simulations we perform use a node opening criterion of $\theta_{BH}$ = 0.7.
-More information about the code can be found in \citet{2008IEEEpds...ChaNGa}.
-We have also recently modified {\sc ChaNGa} to handle solid-body collisions.
-A full description of the collision module implementation can be found in \citet{2019MNRAS.489.2159W}.
+To follow the dynamical and collisional evolution of a planetesimal disk, we use the highly parallel N-body code {\sc ChaNGa} 
+\footnote{A public version of {\sc ChaNGa} can be downloaded from \url{http://www-hpcc.astro.washington.edu/tools/ChaNGa.html}}. 
+This code, which is written in the {\sc CHARM++} parallel programming language, was originally designed for cosmology simulations 
+and has been shown to perform well on up to half a million processors \citep{2015AphCom..2..1}. {\sc ChaNGa} calculates 
+gravitational forces using a modified Barnes-Hut \citep{1986Natur.324..446B} tree with hexadecapole expansions of the moments. 
+All of the simulations we perform use a node opening criterion of $\theta_{BH}$ = 0.7. More information about the code can be found 
+in \citet{2008IEEEpds...ChaNGa}. We have also recently modified {\sc ChaNGa} to handle solid-body collisions. A full description of 
+the collision module implementation can be found in \citet{2019MNRAS.489.2159W}.
 
@@
 
-Two simulations are run, which are loosely based off of 'Model B' in \citet{2000Icar..143...45R}.
-In both cases, a Jupiter mass planet is placed on a 5.2 AU orbit around a 1 $M_{\odot}$ star with a disk of planetesimals placed interior.
-In the first case, Jupiter is placed on a circular orbit.
-In the second case, Jupiter is placed on a mildly eccentric (e = 0.05) orbit.
-We will refer to these simulations as CJ and EJ, respectively.
+Two simulations are run, which are loosely based off of 'Model B' in \citet{2000Icar..143...45R}. In both cases, a Jupiter mass planet 
+is placed on a 5.2 AU orbit around a 1 $M_{\odot}$ star with a disk of planetesimals placed interior. In the first case, Jupiter is placed 
+on a circular orbit. In the second case, Jupiter is placed on a mildly eccentric (e = 0.05) orbit. We will refer to these simulations as CJ 
+and EJ, respectively.
 
-In both cases, the planetesimal disk extends from 2.2 to 3.8 AU.
-This range of semi-major axes covers a number of prominent interior mean motion resonances with Jupiter, including the 3:1, the 5:2, the 2:1 and the 5:3.
-The planetesimal disk follows a minimum-mass solar nebula surface density profile \citep{1981PThPS..70...35H}
+In both cases, the planetesimal disk extends from 2.2 to 3.8 AU. This range of semi-major axes covers a number of prominent 
+interior mean motion resonances with Jupiter, including the 3:1, the 5:2, the 2:1 and the 5:3. The planetesimal disk follows a 
+minimum-mass solar nebula surface density profile \citep{1981PThPS..70...35H}
 
@@
 
-\noindent with $\alpha$ = 3/2 and $\Sigma_{0}$ = 10 g cm$^{-2}$.
-Planetesimals are given a bulk density of 2 g cm$^{-3}$ and a diameter of 300 km.
-This corresponds to a disk containing slightly less than 500,000 planetesimals.
-Both simulations are evolved for 10,000 years, which is about 800 Jupiter orbits.
+\noindent with $\alpha$ = 3/2 and $\Sigma_{0}$ = 10 g cm$^{-2}$. Planetesimals are given a bulk density of 2 g cm$^{-3}$ and a 
+diameter of 300 km. This corresponds to a disk containing slightly less than 500,000 planetesimals. Both simulations are evolved for 
+10,000 years, which is about 800 Jupiter orbits.
 
-In the CJ simulation, there is no secular forcing from Jupiter and so the mean longitudes and mean anomalies are randomly assigned values between 0 and 2$\pi$.
-The distribution of eccentricities and inclinations of the planetesimals are chosen so that the effects of viscous stirring and gas drag from the solar nebula are in balance.
-This occurs when eccentricities are described by a Rayleigh distribution with a scale parameter given by equation 12 in \citet{2002ApJ...581..666K}.
-The inclination distribution is described by this same function, with a scale parameter that is half as large.
-This is typical for a sufficiently dynamically heated disk of particles in a Kepler potential \citep{1993MNRAS.263..875I}.
+In the CJ simulation, there is no secular forcing from Jupiter and so the mean longitudes and mean anomalies are randomly 
+assigned values between 0 and 2$\pi$. The distribution of eccentricities and inclinations of the planetesimals are chosen so that the 
+effects of viscous stirring and gas drag from the solar nebula are in balance. This occurs when eccentricities are described by a 
+Rayleigh distribution with a scale parameter given by equation 12 in \citet{2002ApJ...581..666K}. The inclination distribution is 
+described by this same function, with a scale parameter that is half as large. This is typical for a sufficiently dynamically heated disk 
+of particles in a Kepler potential \citep{1993MNRAS.263..875I}.
 
-For simulation EJ, the effects of secular forcing by Jupiter are applied to the initial conditions.
-This is done by first assigning Kepler orbital elements to the planetesimals in the same way as simulation CJ and then adding a forced component to the eccentricity vectors $z_{i} = \left( h_{i}, k_{i} \right)$, described by equation \ref{eq:eforced}.
-For simplicity, a coordinate system is chosen so that $\omega_{g}$ = 0.
-This allows us to simply add a scalar value to each $h_{i}$, which depends only on the semi-major axis of a planetesimal and Jupiter, along with the eccentricity of Jupiter.
+For simulation EJ, the effects of secular forcing by Jupiter are applied to the initial conditions. This is done by first assigning Kepler 
+orbital elements to the planetesimals in the same way as simulation CJ and then adding a forced component to the eccentricity 
+vectors $z_{i} = \left( h_{i}, k_{i} \right)$, described by equation \ref{eq:eforced}. For simplicity, a coordinate system is chosen so that 
+$\omega_{g}$ = 0. This allows us to simply add a scalar value to each $h_{i}$, which depends only on the semi-major axis of a 
+planetesimal and Jupiter, along with the eccentricity of Jupiter.
 
@@
 
-For the purposes of the integrator, there are two relevant timescales in this system.
-The first is the orbital dynamical time $\sqrt{a^3/G M_{\odot}}$.
-All particles are placed on a fixed time step of $\Delta T$ = 0.01 yr.
-This is roughly 3\% of an orbital dynamical time at the inner edge of the planetesimal disk, which is a reasonable time step size for a leapfrog integrator (reference?).
-The time step for collisions is determined by the planetesimal dynamical timescale ($\sim 1/\sqrt{G \rho}$), which is about 45 minutes.
-To resolve both of these timescales simultaneously, we use a two-tiered time stepping scheme.
-At the beginning of each time step, all bodies are placed on the orbital time step.
-A first pass of collision detection is then run in which the radii of all bodies are inflated by a factor of 2.5.
-Any bodies with imminent collisions predicted using the inflated radii are placed on a time step that is a factor of 16 smaller than the orbital time step.
-The purpose of two-tiered scheme is to properly resolve the gravitational interactions between any bodies that will undergo a close encounter.
-This prevents the coarser base time step from reducing the effectiveness of gravitational focusing, while minimizing the additional computational expense.
+For the purposes of the integrator, there are two relevant timescales in this system. The first is the orbital dynamical time $\sqrt{a^3/
+G M_{\odot}}$. All particles are placed on a fixed time step of $\Delta T$ = 0.01 yr. This is roughly 3\% of an orbital dynamical time at 
+the inner edge of the planetesimal disk, which is a reasonable time step size for a leapfrog integrator (reference?). The time step for 
+collisions is determined by the planetesimal dynamical timescale ($\sim 1/\sqrt{G \rho}$), which is about 45 minutes. To resolve both 
+of these timescales simultaneously, we use a two-tiered time stepping scheme. At the beginning of each time step, all bodies are 
+placed on the orbital time step. A first pass of collision detection is then run in which the radii of all bodies are inflated by a factor of 
+2.5. Any bodies with imminent collisions predicted using the inflated radii are placed on a time step that is a factor of 16 smaller than 
+the orbital time step. The purpose of two-tiered scheme is to properly resolve the gravitational interactions between any bodies that 
+will undergo a close encounter. This prevents the coarser base time step from reducing the effectiveness of gravitational focusing, 
+while minimizing the additional computational expense.
 
@@
 
-A side-by-side comparison of the final distribution in cylindrical coordinates of planetesimals from the CJ and EJ simulations is shown in figure \ref{fig:rtheta}.
-Gaps produced by the 3:1, 2:1 and 5:3 MMR with Jupiter are visible in both frames.
-In the EJ simulation, a gap in the vicinity of the 5:2 MMR is also visible.
-The non-axisymmetric character of the gaps reflects the fact that the planetesimals in the vicinity of the resonances (especially the 2:1) are having their eccentricities significantly pumped.
-(I don't think there should be any azimuthal structure to the gaps in the CJ simulation.
-This is probably a reflection of the fact that we need to run with smaller timesteps.) Although examining the spatial distribution of planetesimals near MMR in debris disks may be a viable way to detect unseen planets, we will not focus on this topic any longer as it has already been covered in detail in other studies \citep{2016ApJ...818..159T, 2018ApJ...857....3T}.
-It is worth noting, however that the spatial distribution of planetesimals shown in figure \ref{fig:rtheta} appears qualitatively similar to figures 3 and 4 in \citep{2016ApJ...818..159T}.
+A side-by-side comparison of the final distribution in cylindrical coordinates of planetesimals from the CJ and EJ simulations is shown 
+in figure \ref{fig:rtheta}. Gaps produced by the 3:1, 2:1 and 5:3 MMR with Jupiter are visible in both frames. In the EJ simulation, a 
+gap in the vicinity of the 5:2 MMR is also visible. The non-axisymmetric character of the gaps reflects the fact that the planetesimals 
+in the vicinity of the resonances (especially the 2:1) are having their eccentricities significantly pumped. (I don't think there should be 
+any azimuthal structure to the gaps in the CJ simulation. This is probably a reflection of the fact that we need to run with smaller 
+timesteps.) Although examining the spatial distribution of planetesimals near MMR in debris disks may be a viable way to detect 
+unseen planets, we will not focus on this topic any longer as it has already been covered in detail in other studies
+\citep{2016ApJ...818..159T, 2018ApJ...857....3T}. It is worth noting, however that the spatial distribution of planetesimals shown in 
+figure \ref{fig:rtheta} appears qualitatively similar to figures 3 and 4 in \citep{2016ApJ...818..159T}.
 
-The location of the mean motion resonances with Jupiter is most clearly visible when examining the semimajor axis-eccentricity distribution of the planetesimals.
-This is shown in figure \ref{fig:ae}, with the final snapshot from the CJ simulation shown on the left and EJ on the right.
-The solid vertical lines indicate the nominal locations of the mean motion resonances.
-Away from the resonance locations, the eccentricity dispersion grows via viscous stirring as energy from the Keplerian shearing of the disk is gradually transferred to random motions of planetesimals.
-The slight inward curving of the eccentricity peaks near the resonances is a consequence of the conservation of the Jacobi energy.
-As the semimajor axis of a planetesimal in MMR librates, the corresponding change in eccentricity is given by equation \ref{eq:tiss}.
+The location of the mean motion resonances with Jupiter is most clearly visible when examining the semimajor axis-eccentricity 
+distribution of the planetesimals. This is shown in figure \ref{fig:ae}, with the final snapshot from the CJ simulation shown on the left 
+and EJ on the right. The solid vertical lines indicate the nominal locations of the mean motion resonances. Away from the resonance 
+locations, the eccentricity dispersion grows via viscous stirring as energy from the Keplerian shearing of the disk is gradually 
+transferred to random motions of planetesimals. The slight inward curving of the eccentricity peaks near the resonances is a 
+consequence of the conservation of the Jacobi energy. As the semimajor axis of a planetesimal in MMR librates, the corresponding 
+change in eccentricity is given by equation \ref{eq:tiss}.
 
-In the EJ simulation, the eccentricity remains enhanced between the MMRs due to the secular forcing effect of Jupiter.
-This also has the consequence of making the eccentricity spikes due to the 5:2 and (what's the MMR at 3.6 AU?) more prominent.
-The reason for this is that the libration width of a resonance generally scales with the eccentricity of the particle being perturbed.
-In a secularly forced disk, the eccentricity of particles affected by resonance is larger, which increases the resonance width and allows a larger region of the disk to be affected by a given resonance.
-Also visible in the EJ snapshot in figure \ref{fig:ae} are eccentricity spikes that extend below the background eccentricity distribution.
-This is a clear sign that planetesimals in the MMRs are librating.
-The phase of the libration is set by the resonant argument (maybe I should add an equation for the resonant argument in section 2).
+In the EJ simulation, the eccentricity remains enhanced between the MMRs due to the secular forcing effect of Jupiter. This also has 
+the consequence of making the eccentricity spikes due to the 5:2 and (what's the MMR at 3.6 AU?) more prominent. The reason for 
+this is that the libration width of a resonance generally scales with the eccentricity of the particle being perturbed. In a secularly 
+forced disk, the eccentricity of particles affected by resonance is larger, which increases the resonance width and allows a larger 
+region of the disk to be affected by a given resonance. Also visible in the EJ snapshot in figure \ref{fig:ae} are eccentricity spikes that 
+extend below the background eccentricity distribution. This is a clear sign that planetesimals in the MMRs are librating. The phase of 
+the libration is set by the resonant argument (maybe I should add an equation for the resonant argument in section 2).
 
-An additional effect that the MMRs have on the orbits of planetesimals is visible in figure \ref{fig:long_ph}.
-This shows the semimajor axis distribution of planetesimals as a function of longitude of perihelion in the EJ simulation.
-As discussed in section \ref{sec:sec_force}, the eccentric orbit of Jupiter causes the perihelia of the planetesimal orbits to align with the giant perturber.
-The mean motion resonances, however, drive the rather vigorous precession of the orbits of planetesimals in their vicinity.
-Because the timescale of the resonances is much shorter than the timescale for secular forcing, the longitudinal orientations of orbits close to the MMRs are effectively randomized.
-The dashed horizontal lines in figure \ref{fig:long_ph} indicate the libration width of the MMRs at the forced eccentricity (given by the magnitude of equation \ref{eq:eforced}.
-The size of the zone of vigorous precession roughly matches the libration width of the MMRs.
-As will be discussed shortly, the relative longitudinal orientation of the orbits has important implications for where and when planetesimal collisions occur at a given semimajor axis.
-Not shown is the longitude of perihelia and semimajor axes of the bodies in the CJ simulation.
-Due to the lack of secular forcing, the orientations of the orbits of these bodes are effectively random.
+An additional effect that the MMRs have on the orbits of planetesimals is visible in figure \ref{fig:long_ph}. This shows the semimajor 
+axis distribution of planetesimals as a function of longitude of perihelion in the EJ simulation. As discussed in section 
+\ref{sec:sec_force}, the eccentric orbit of Jupiter causes the perihelia of the planetesimal orbits to align with the giant perturber. The 
+mean motion resonances, however, drive the rather vigorous precession of the orbits of planetesimals in their vicinity. Because the 
+timescale of the resonances is much shorter than the timescale for secular forcing, the longitudinal orientations of orbits close to the 
+MMRs are effectively randomized. The dashed horizontal lines in figure \ref{fig:long_ph} indicate the libration width of the MMRs at 
+the forced eccentricity (given by the magnitude of equation \ref{eq:eforced}. The size of the zone of vigorous precession roughly 
+matches the libration width of the MMRs. As will be discussed shortly, the relative longitudinal orientation of the orbits has important 
+implications for where and when planetesimal collisions occur at a given semimajor axis. Not shown is the longitude of perihelia and 
+semimajor axes of the bodies in the CJ simulation. Due to the lack of secular forcing, the orientations of the orbits of these bodes are 
+effectively random.
 
-Next, we move on to examine the statistics of the collisions that occur.
-Figure \ref{fig:coll_hist_a} shows the distribution of semimajor axes of every collision that is resolved.
-Here, the semimajor axis of a collision is defined as the semimajor axis of the first body participating in the collision at the moment that it occurs.
-During a collision, the determination of which body is first and which is second is determined by the collision search tree in {\sc ChaNGa}.
-To ensure that this does not introduce any bias, we also constructed figure \ref{fig:coll_hist_a} using the orbital parameters of the second body and found no qualitative difference.
-By examining the semimajor axis distribution of the collisions, it is easy to see how the MMRs affect the collision rates.
-The dashed lines again represent the libration width of each resonance and are meant to show its range of influence.
-In both the circular and eccentric Jupiter simulations, the collision rate is clearly enhanced interior to the 2:1 MMR.
-The 3:1 MMR only appears to have a noticeable influence on the collision rate in the EJ simulation.
-In both cases, although the 5:3 MMR has a clear influence on the on the semimajor-axis eccentricity distribution, it does not leave a measureable imprint on the collision rate.
-It is important to point out, however, that the libration width of sufficiently eccentric particles near the 5:3 MMR may extend beyond the outer edge of the disk and introduce boundary effects.
+Next, we move on to examine the statistics of the collisions that occur. Figure \ref{fig:coll_hist_a} shows the distribution of semimajor 
+axes of every collision that is resolved. Here, the semimajor axis of a collision is defined as the semimajor axis of the first body 
+participating in the collision at the moment that it occurs. During a collision, the determination of which body is first and which is 
+second is determined by the collision search tree in {\sc ChaNGa}. To ensure that this does not introduce any bias, we also 
+constructed figure \ref{fig:coll_hist_a} using the orbital parameters of the second body and found no qualitative difference. By 
+examining the semimajor axis distribution of the collisions, it is easy to see how the MMRs affect the collision rates. The dashed lines 
+again represent the libration width of each resonance and are meant to show its range of influence. In both the circular and eccentric 
+Jupiter simulations, the collision rate is clearly enhanced interior to the 2:1 MMR. The 3:1 MMR only appears to have a noticeable 
+influence on the collision rate in the EJ simulation. In both cases, although the 5:3 MMR has a clear influence on the on the 
+semimajor-axis eccentricity distribution, it does not leave a measureable imprint on the collision rate. It is important to point out, 
+however, that the libration width of sufficiently eccentric particles near the 5:3 MMR may extend beyond the outer edge of the disk 
+and introduce boundary effects.
 
-Although the semimajor axis of a particle at the moment of collision provides useful information about how the mean motion resonances affect the collision rate in the disk, this information alone is not enough to predict where the second generation dust that is produced will end up.
-To do so, we will operate under the assumption that dust grains produced by collision events will quickly couple to the gas and attain a circular orbit.
-This assumption, which will be further justified in section \ref{sec:dust}, allows to map the radial variation in the dust surface density to the radial position of the collisions.
-This is shown in figure \ref{fig:coll_hist_r}, where the histograms indicate the x and y coordinates of a body at the moment that it undergoes a collision.
+Although the semimajor axis of a particle at the moment of collision provides useful information about how the mean motion 
+resonances affect the collision rate in the disk, this information alone is not enough to predict where the second generation dust that 
+is produced will end up. To do so, we will operate under the assumption that dust grains produced by collision events will quickly 
+couple to the gas and attain a circular orbit. This assumption, which will be further justified in section \ref{sec:dust}, allows to map the 
+radial variation in the dust surface density to the radial position of the collisions. This is shown in figure \ref{fig:coll_hist_r}, where the 
+histograms indicate the x and y coordinates of a body at the moment that it undergoes a collision.
 
-Most notably, the prominent features visible in figure \ref{fig:coll_hist_a} adjacent to the 2:1 MMR no longer appear.
-This is due to the fact that the orbits of bodies in the 2:1 MMR have a wide range of eccentricities and therefore have the potential to undergo collisions at a wide range of heliocentric distances.
-In the CJ simulation, there is a prominent dip in the collision rate near the 2:1 MMR.
-This feature is still moderately visible in the EJ simulation, but the dip is much wider and shallower.
-The random orientations of the orbits inside of the resonance (see figure \ref{fig:long_ph}), combined with the forced eccentricites of planetesimals adjacent to the resonance weakens the dip near the 2:1 MMR seen in the left hand panel of figure \ref{fig:coll_hist_a}.
-Additionally, there is a double-pronged feature in the collision rate near the 3:1 MMR in the EJ simulation.
-The radial distance of these two prongs corresponds to the maximum radial excursion that a planetesimal at the 3:1 MMR with an eccentricity set by secular forcing with Jupiter undergoes.
-(Need more explanation of why this happens)
+Most notably, the prominent features visible in figure \ref{fig:coll_hist_a} adjacent to the 2:1 MMR no longer appear. This is due to the 
+fact that the orbits of bodies in the 2:1 MMR have a wide range of eccentricities and therefore have the potential to undergo 
+collisions at a wide range of heliocentric distances. In the CJ simulation, there is a prominent dip in the collision rate near the 2:1 
+MMR. This feature is still moderately visible in the EJ simulation, but the dip is much wider and shallower. The random orientations of 
+the orbits inside of the resonance (see figure \ref{fig:long_ph}), combined with the forced eccentricites of planetesimals adjacent to 
+the resonance weakens the dip near the 2:1 MMR seen in the left hand panel of figure \ref{fig:coll_hist_a}. Additionally, there is a 
+double-pronged feature in the collision rate near the 3:1 MMR in the EJ simulation. The radial distance of these two prongs 
+corresponds to the maximum radial excursion that a planetesimal at the 3:1 MMR with an eccentricity set by secular forcing with 
+Jupiter undergoes. (Need more explanation of why this happens)
 
-As is seen in figure \ref{fig:long_ph}, the relatively fast precession rates induced by the mean motion resonances overpower the secular forcing by Jupiter and randomize the orientation of orbits near the nominal resonance locations.
-Of course, this difference in longitude of perihelion of bodies inside and outside of resonance is only present in the EJ simulation because the Jupiter imposes zero forced eccentricity on the disk when it has a circular orbit.
-Figure \ref{fig:m_hist} provides another view of the difference in collision statistics inside and outside and of resonance.
-This shows the mean anomalies of bodies at the moment that they undergo a collision.
-The top row corresponds to the EJ simulation and the bottom rom corresponds to the CJ simulation.
-The left panels correspond to collisions that occur inside of the 2:1 MMR and the right panels are for collisions that occur with a semimajor axis between 2.7 and 2.8 AU, which is meant to well away from the influence of any resonances.
-The semimajor axis window size in the right hand panel is chosen so that both histograms contain the same total number of collisions.
+As is seen in figure \ref{fig:long_ph}, the relatively fast precession rates induced by the mean motion resonances overpower the 
+secular forcing by Jupiter and randomize the orientation of orbits near the nominal resonance locations. Of course, this difference in 
+longitude of perihelion of bodies inside and outside of resonance is only present in the EJ simulation because the Jupiter imposes 
+zero forced eccentricity on the disk when it has a circular orbit. Figure \ref{fig:m_hist} provides another view of the difference in 
+collision statistics inside and outside and of resonance. This shows the mean anomalies of bodies at the moment that they undergo a 
+collision. The top row corresponds to the EJ simulation and the bottom rom corresponds to the CJ simulation. The left panels 
+correspond to collisions that occur inside of the 2:1 MMR and the right panels are for collisions that occur with a semimajor axis 
+between 2.7 and 2.8 AU, which is meant to well away from the influence of any resonances. The semimajor axis window size in the 
+right hand panel is chosen so that both histograms contain the same total number of collisions.
 
-The qualitative differences between these four panels can be explained in the following way: for $\approx$ 100 km bodies, gravitational focusing plays a significant role in setting the collision rate.
-In regions of the disk where the rms eccentricity is small (which corresponds to a small velocity dispersion), the collision rate should be enhanced (see equation \ref{eq:safronov}).
-Inside of resonances, planetesimals undergo large amplitude libration which pumps up the eccentricity dispersion.
-This effect is visible in figure \ref{fig:ae} for both the EJ and CJ simulation.
-This implies that the collision rate should be geometric, and not depend on the velocity dispersion near resonances.
-When this is true, collisions should preferentially occur near perihelion.
-The reason for this is that in the geometric limit, the collision probability scales with the ratio between the geometric cross section of the two planetesimals and the surface area of a sphere with radius $r$, where $r$ is the distance between the bodies and the central star.
-This ratio, and therefore the collision probability, is largest when $r$ is minimized (see \citet{2003AJ....125.2692L}).
-The fact both of the left-hand panels in figure \ref{fig:m_hist} show a distinct lack of collisions near aphelion is consistent with this explanation.
+The qualitative differences between these four panels can be explained in the following way: for $\approx$ 100 km bodies, 
+gravitational focusing plays a significant role in setting the collision rate. In regions of the disk where the rms eccentricity is small 
+(which corresponds to a small velocity dispersion), the collision rate should be enhanced (see equation \ref{eq:safronov}). Inside of 
+resonances, planetesimals undergo large amplitude libration which pumps up the eccentricity dispersion. This effect is visible in 
+figure \ref{fig:ae} for both the EJ and CJ simulation. This implies that the collision rate should be geometric, and not depend on the 
+velocity dispersion near resonances. When this is true, collisions should preferentially occur near perihelion. The reason for this is 
+that in the geometric limit, the collision probability scales with the ratio between the geometric cross section of the two planetesimals 
+and the surface area of a sphere with radius $r$, where $r$ is the distance between the bodies and the central star. This ratio, and 
+therefore the collision probability, is largest when $r$ is minimized (see \citet{2003AJ....125.2692L}). The fact both of the left-hand 
+panels in figure \ref{fig:m_hist} show a distinct lack of collisions near aphelion is consistent with this explanation.
 

### 2019-12-08 main.tex
Rework outline and figures

@@
 
-\begin{figure*}
-    \includegraphics[width=\textwidth]{figures/ae.png}
+\begin{figure}
+    \includegraphics[width=\columnwidth]{figures/ae.png}
     \caption{Caption goes here.\label{fig:ae}}
-\end{figure*}
+\end{figure}
 
@@
 
-\begin{figure*}
-    \includegraphics[width=\textwidth]{figures/coll_hist_a.png}
+\begin{figure}
+    \includegraphics[width=\columnwidth]{figures/coll_hist_a.png}
     \caption{Caption goes here.\label{fig:coll_hist_a}}
-\end{figure*}
+\end{figure}
 
@@
 
-\begin{figure*}
-    \includegraphics[width=\textwidth]{figures/m_hist.png}
-    \caption{Caption goes here.\label{fig:m_hist}}
-\end{figure*}
+\section{Results} \label{sec:results}
 
-\section{Results} \label{sec:results}
+Discuss figures 1 through 4 here.
 
@@
 gap in the vicinity of the 5:2 MMR is also visible. The non-axisymmetric character of the gaps reflects the fact that the planetesimals 
-in the vicinity of the resonances (especially the 2:1) are having their eccentricities significantly pumped. (I don't think there should be 
-any azimuthal structure to the gaps in the CJ simulation. This is probably a reflection of the fact that we need to run with smaller 
-timesteps.) Although examining the spatial distribution of planetesimals near MMR in debris disks may be a viable way to detect 
-unseen planets, we will not focus on this topic any longer as it has already been covered in detail in other studies
-\citep{2016ApJ...818..159T, 2018ApJ...857....3T}. It is worth noting, however that the spatial distribution of planetesimals shown in 
-figure \ref{fig:rtheta} appears qualitatively similar to figures 3 and 4 in \citep{2016ApJ...818..159T}.
+in the vicinity of the resonances (especially the 2:1) are having their eccentricities significantly pumped.
+Although examining the spatial distribution of planetesimals near MMR in debris disks may be a viable way to detect  unseen planets, we will not focus on this topic any longer as it has already been covered in detail in other studies \citep{2016ApJ...818..159T, 2018ApJ...857....3T}.
+It is worth noting, however that the spatial distribution of planetesimals shown in  figure \ref{fig:rtheta} appears qualitatively similar to figures 3 and 4 in \citep{2016ApJ...818..159T}.
 
@@
 
-\subsection{Comparison With Analytic Safronov Collision Rate}\label{sec:saf}
+\section{Radial Collision Rates}\label{sec:rad_coll}
 
-Outline for this section:
-\begin{itemize}
-\item Time evolution of disk surface density for circ and ecc
-\item Time evolution of sma vs ecc
-\item Number of collisions as a function of sma and radial distance
-\item Number of collisions as a function of mean anomaly and delta mean anomaly
-\item Comparison between safronov rate and actual collision statistics
-\end{itemize}
+Motivate the assumption that dust produced in collisions immediately goes onto circular orbit
 
-\section{Dust Emission} \label{sec:dust}
+Discuss figure 5, hilight differences between surface density distribution and collision histogram.
+Calculation of safronov rate is hard because velocity distribution is bimodal in many places.
+Key features to point out: 2:1 MMR shows up well in CJ.
+Much more washed out in EJ, while 3:1 becomes more prominent.
+Also both features in EJ are shifted to the right of resonance location by a factor of (1+$e_{forced}$.
+This could be a viable way to measure ecc of the perturber.
 
-\begin{itemize}
-\item Show CASA images
-\end{itemize}
+\section{Observability of Collisions} \label{sec:dust}
+
+Have aaron make a CASA dust emission map for the two histograms in figure 5.
+Fit a gaussian to the radial features and see if we can back out the eccentricity of the perturber and its mass.
+Also make 2d histogram showing how the perturbers eccentricity (which sets the forced eccentricity) and mass sets the libration width.
 
@@
 
-Figures to include:
-
-\begin{itemize}
-    \item a-e evolution of particles
-    \item a-e closeup of resonance (do we need to pick more than one?)
-    \item azimuthally averaged profile of collision rates
-    \item temporal evolution of collision rates inside and outside resonance
-\end{itemize}
-
-Need to expain waves in a-e plots. This is from the free eccentricity cycling through phase space.
-
-Might be useful to compare Aaron's estimate of collsion rates from velocity dispersion in 2017 paper to the actual collision rates that we measure.
-Collision rates tend to be supressed outside of MMRs compared to Safronov rate.
-Im guessing this has to do with the fact that precession rates are high inside MMRs and so orbits are not aligned and more likely to cross.
-For a discussion of secular precession rates due to a giant planet, see \citet{2009MNRAS.399.1403M}.
-
 \bibliography{references}

### 2019-12-08 makeFig.py

@@ -133,16 +133,17 @@ coll_dist_e2 = np.sqrt(x_c_e2**2 + y_c_e2**2)
 a_c_e2, e_c_e2, inc_c_e2, Omega_c_e2, omega_c_e2, M_c_e2 = \
     OrbitTools.cart2kepX(x_c_e2, y_c_e2, z_c_e2, vx_c_e2, vy_c_e2, vz_c_e2, mc_e, m2_e)
 
+s_c, s_e = pb.load(s_c_files[-1]), pb.load(s_e_files[-1])
+pl_c, pl_e = OrbitTools.orb_params(s_c), OrbitTools.orb_params(s_e)
+x_c, y_c = pl_c['pos'][:,0], pl_c['pos'][:,1]
+r_c, theta_c = np.sqrt(x_c**2 + y_c**2), np.arctan2(y_c, x_c) + np.pi
+x_e, y_e = pl_e['pos'][:,0], pl_e['pos'][:,1]
+r_e, theta_e = np.sqrt(x_e**2 + y_e**2), np.arctan2(y_e, x_e) + np.pi
+
 def make_rtheta():
 	file_str = 'figures/rtheta.' + fmt
 	if not clobber and os.path.exists(file_str):
 		return
-	s_c, s_e = pb.load(s_c_files[-1]), pb.load(s_e_files[-1])
-	pl_c, pl_e = OrbitTools.orb_params(s_c), OrbitTools.orb_params(s_e)
-	x_c, y_c = pl_c['pos'][:,0], pl_c['pos'][:,1]
-	r_c, theta_c = np.sqrt(x_c**2 + y_c**2), np.arctan2(y_c, x_c) + np.pi
-	x_e, y_e = pl_e['pos'][:,0], pl_e['pos'][:,1]
-	r_e, theta_e = np.sqrt(x_e**2 + y_e**2), np.arctan2(y_e, x_e) + np.pi
 
 	fig, (ax1, ax2) = plt.subplots(figsize=(16,6), nrows=1, ncols=2)
 	ax1.scatter(theta_c, r_c, s=s)
@@ -159,30 +160,27 @@ def make_ae():
 	file_str = 'figures/ae.' + fmt
 	if not clobber and os.path.exists(file_str):
 		return
-	s_c, s_e = pb.load(s_c_files[-1]), pb.load(s_e_files[-26])
[…]

### 2019-12-09 main.tex
Rework overview of paper at end of introduction

@@
 can be done quickly and efficiently. This considerably relaxes the constraints on resolution and integration time. With this toolset, we 
-explore the collision rate structure of the planetesimal disk in the vicinity of mean motion resonances.
+explore the collision rate structure of the planetesimal disk in the vicinity of mean motion resonances. In particular, we would like to 
+determine: 1. whether MMRs leave a detectable signature in the collisionally-generated dust. 2. If these signatures can be used to determine the orbital properties of the perturbing planet.
 
-This work is organized in the following way. In section \ref{sec:dynamics} we provide an overview of the dynamics that drive the 
-evolution of a planetesimal disk under the gravitational influence of an external perturber. In section \ref{sec:setup} we describe the 
-N-body code we use and describe how we constructed the initial conditions for the two simulations that are run: one with a perturber 
-on a circular orbit and one with an eccentric perturber. Section \ref{sec:results} goes on to explore the results of the two, with 
-particular focus on the radial variation in the collision rates. In section \ref{sec:dust}, we use the positions of the collision events to 
-construct a map of second generation dust emission, under the assumption that dust grains produced by collisions will immediately 
-couple to the gas and circularize their orbits. Finally, we assess the observability of features in the dust emission due to mean motion 
-resonances and conclude in section \ref{sec:discuss}.
+This work is organized in the following way: In section \ref{sec:dynamics}, we provide an overview of the relevant dynamics that drive 
+the evolution of a planetesimal disk under the gravitational influence of an external perturber.
+We also highlight the shortcomings of secular theory in trying to predict the radial collision rate and motivate the need for N-body simulations with massive, collisional particles.
+In section \ref{sec:sims} we describe the N-body code that we use and detail the initial conditions that are used for two simulations: one in which the perturber is on a circular orbit and another in which the perturber is given a mildly eccentric orbit.
+Section \ref{sec:results} presents the results of the two simulations.
+Next, we generate dust emission maps in section \ref{sec:dust}, under the assumption that collisionally-generated dust will quickly couple with the gas and circularize, and show that radial structure is produced in the vicinity of the MMRs.
+Using the dust emission maps, section \ref{sec:fitting} explores the feasibility of measuring properties of the perturbing planet from the MMR features in the dust.
+We then conclude in section \ref{sec:discuss}.
 
@@
 
-\section{Radial Collision Rates}\label{sec:rad_coll}
-
 Motivate the assumption that dust produced in collisions immediately goes onto circular orbit
@@
 
+\section{Measuring Properties of the Perturber} \label{sec:fitting}
+
 \section{Summary and Discussion} \label{sec:discuss}
-
-%In this study, we will consider the effects that an external perturber has on the dynamical evolution and collision rates of planetesimals in a circumstellar disk.
-Planetesimals are too small to reflect much star light and are of too low mass to have any significant amount of thermal inertial.
-However, the large amounts of dust produced by collisional grinding can be used to infer where planetesimals are interacting \citep{2005Natur.436..363S, 2015ApJ...806...23L}.
-Although the behavior of the small dust grains can strongly depend on the hydrodynamic behavior of the gas \citep{2015ApJ...813L..14B}, the evolution of the planetesimals (km sized and larger) should be well decoupled from the gas.
-This means that results of this study should be applicable to both gas rich protoplanetary disks such as HL Tau and TW Hya, along with dusty debris disks such as Fomalhut \citep{2017ApJ...842....8M}.
-
-%The intermediate stages of planet formation are incredibly difficult to observe.
-Planetesimals, which are the building blocks of planets, are too small to reflect any significant amount of star light and are of too low mass to carry much thermal inertia.
-However, large volumes of dust produced through collisional grinding of planetesimals can be used to infer where planetesimals are interacting
-
-%In the Solar System, the formation of Jupiter is thought to have destabilized the orbits of nearby planetesimals and triggered a short and intense period of bombardment.
-In addition to triggering a cascade of collisional grinding \citep{2012ApJ...750....8T}, the formation of Jupiter is thought to have facilitated the mixing of volatiles in the inner Solar System \citep{2017Icar..297..134R}.
-
-%From an outsider's perspective, the most easily observable property of the Solar System is the infrared emission from small dust grains.
-Outside the Solar System, infrared excess has also been tied to the presence of dust (citation needed).
-Recent high resolution images from ALMA have shown that the structure of these dusty disks around other stars can have rather complicated structures.
-
-%Talk about observed gaps in ALMA images of PPDs.
-Many different explanations for rings and gaps \citep{2019arXiv190103680V}.
-One possible explanation is resonances with outer companion.
-\citet{2017ApJ...850..103B} examined this possibility, but used massless test particles to represent the planetesimals.
-Although this provided some information about how the planetesimals move under the influence of a mean motion resonance, it did not say anything about where the collisions and dust production would occur.
-
-%Talk about specific PPDs where MMRs might be producing some of the structure (HL Tau, TW Hya)
-
-%Talk about dynamics in MMRs.
-Resonances tend to push particles away from the perturber.
-Mention study by \citet{2016ApJ...818..159T, 2018ApJ...857....3T}.
-Massive disk can move resonance locations (see eq 10 or \citet{2015ApJ...805..100T}).
-Looks like we are getting a spiral wave being launched from the 3:1 MMR (see section 5.6 in \citet{2016ApJ...818..159T}).
-Study by \citet{2018MNRAS.473.3547R} used collisionless N-body sim to examine production of cavity in debris disk, assume paricles trace mm sized objects which should be observable.
-
-%See \citet{1984prin.conf..513S} for a fantastic discussion of spiral waves in a planetary context.
-
-%Scattering of planetesimals by giant planet does not depend on migration, so we ignore this process \citet{2017Icar..297..134R}.
 

### 2019-12-10 main.tex
Update timestepping description

@@
 the body is dominated by the central star and the perturbing body, the amplitude of the oscillations in semi-major axis can be 
-described using the pendulum approximation (see equation 6 in \citet{2019MNRAS.489.2159W}). This amplitude can be thought of 
+described using the pendulum approximation (see equation 8.76 in \citet{2000ssd..book.....M}). This amplitude can be thought of 
 as the 'width' over which the perturbations of the resonance are effective. Variations in eccentricity follow the semi-major axis 
@@
 \noindent with $\alpha$ = 3/2 and $\Sigma_{0}$ = 10 g cm$^{-2}$. Planetesimals are given a bulk density of 2 g cm$^{-3}$ and a 
-diameter of 300 km. This corresponds to a disk containing slightly less than 500,000 planetesimals. Both simulations are evolved for 
-10,000 years, which is about 800 Jupiter orbits.
+diameter of 300 km. This corresponds to a disk containing roughly 500,000 planetesimals. Both simulations are evolved for 
+5,000 years, which is about 400 Jupiter orbits.
 
@@
 Rayleigh distribution with a scale parameter given by equation 12 in \citet{2002ApJ...581..666K}. The inclination distribution is 
-described by this same function, with a scale parameter that is half as large. This is typical for a sufficiently dynamically heated disk 
+described by this same function, with a scale parameter that is half as large. This is typical for a dynamically heated disk 
 of particles in a Kepler potential \citep{1993MNRAS.263..875I}.
 
-For simulation EJ, the effects of secular forcing by Jupiter are applied to the initial conditions. This is done by first assigning Kepler 
+For simulation EJ, the effects of secular forcing by Jupiter are built in to the initial conditions. This is done by first assigning Kepler 
 orbital elements to the planetesimals in the same way as simulation CJ and then adding a forced component to the eccentricity 
@@
 G M_{\odot}}$. All particles are placed on a fixed time step of $\Delta T$ = 0.01 yr. This is roughly 3\% of an orbital dynamical time at 
-the inner edge of the planetesimal disk, which is a reasonable time step size for a leapfrog integrator (reference?). The time step for 
-collisions is determined by the planetesimal dynamical timescale ($\sim 1/\sqrt{G \rho}$), which is about 45 minutes. To resolve both 
-of these timescales simultaneously, we use a two-tiered time stepping scheme. At the beginning of each time step, all bodies are 
-placed on the orbital time step. A first pass of collision detection is then run in which the radii of all bodies are inflated by a factor of 
-2.5. Any bodies with imminent collisions predicted using the inflated radii are placed on a time step that is a factor of 16 smaller than 
-the orbital time step. The purpose of two-tiered scheme is to properly resolve the gravitational interactions between any bodies that 
-will undergo a close encounter. This prevents the coarser base time step from reducing the effectiveness of gravitational focusing, 
-while minimizing the additional computational expense.
+the inner edge of the planetesimal disk. From numerical tests with {\sc ChaNGa}, we have found that this time step size preserves 
+the symplectic nature of the integration without being too computationally expensive. Although using $\Delta T$ = 0.01 yr keeps the 
+integration symplectic, we find that a small amount of artificial precession is produced, which is particularly noticable in the EJ 
+simulation. We reduce the base time step size by an additional factor of 4 to the keep longitude of perihelia of planetesimals near the 
+inner edge of the disk from drifting too far over the course of our integration.
+
+An additional timescale is set by the dynamical time of the planetesimals ($\sim 1/\sqrt{G \rho}$), which is about 45 minutes. To 
+resolve the base time step and the dynamical timescale of planetesimals simultaneously, we use a two-tiered time stepping scheme. 
+At the beginning of each time step, all bodies are placed on the orbital time step. A first pass of collision detection is then run in 
+which the radii of all bodies are inflated by a factor of 2.5. Any bodies with imminent collisions predicted using the inflated radii are 
+placed on a time step that is a factor of 16 smaller than the orbital time step. The purpose of two-tiered scheme is to properly resolve 
+the gravitational interactions between any bodies that will undergo a close encounter. This prevents the coarser base time step from 
+reducing the effectiveness of gravitational focusing, while minimizing the additional computational expense.
 

### 2019-12-12 main.tex
Rework discussion of figures 1 and 2

@@
 placed on a time step that is a factor of 16 smaller than the orbital time step. The purpose of two-tiered scheme is to properly resolve 
-the gravitational interactions between any bodies that will undergo a close encounter. This prevents the coarser base time step from 
+the gravitational interactions between any bodies that undergo a close encounter. This prevents the coarser base time step from 
 reducing the effectiveness of gravitational focusing, while minimizing the additional computational expense.
@@
 
-Discuss figures 1 through 4 here.
+We begin by examining the spatial distribution of planetesimals in both simulations. The polar position of the planetesimals at the 
+end of the CJ and EJ simulations are shown in the left and right hand panels of  figure \ref{fig:rtheta}, respectively. Gaps produced by 
+the 3:1, 2:1 and 5:3 MMR with Jupiter are visible in both cases. In the EJ case, a gap in the vicinity of the 5:2 MMR is also visible. 
+The non-axisymmetric shape of the gaps reflects the fact that planetesimals in the vicinity of the resonances have been excited onto 
+non-circular orbits. Although examining the spatial distribution of planetesimals near MMR in debris disks may be a viable way to 
+detect unseen planets, we will not focus on this topic here, as it has already been covered in detail by other studies 
+\citep{2016ApJ...818..159T, 2018ApJ...857....3T}.
 
-A side-by-side comparison of the final distribution in cylindrical coordinates of planetesimals from the CJ and EJ simulations is shown 
-in figure \ref{fig:rtheta}. Gaps produced by the 3:1, 2:1 and 5:3 MMR with Jupiter are visible in both frames. In the EJ simulation, a 
-gap in the vicinity of the 5:2 MMR is also visible. The non-axisymmetric character of the gaps reflects the fact that the planetesimals 
-in the vicinity of the resonances (especially the 2:1) are having their eccentricities significantly pumped.
+The MMRs are most clearly visible when viewing the semimajor axis and eccentricity distribution of the planetesimals. The top panel 
+of figure \ref{fig:ae} corresponds to the CJ simulation and the bottom panel corresponds to EJ. The solid vertical lines in this plot 
+represent the nominal locations of the resonances. Near the nominal resonance locations, the a-e distribution of the planetesimals 
+exhibits well-defined spikes which curve slightly inward due to conservation of the Jacobi energy. In the EJ simulation, the 
+eccentricity distribution of bodies near resonance extends below the initial forced value. This is a reflection of the fact that these 
+bodies are undergoing libration, which drives periodic oscillations in both semimajor axis and eccentricity. The coupling between 
+these two quantities is described by equation \ref{eq:tiss}.
+
+% old stuff
+%A side-by-side comparison of the final distribution in cylindrical coordinates of planetesimals from the CJ and EJ simulations is shown in figure \ref{fig:rtheta}.
+Gaps produced by the 3:1, 2:1 and 5:3 MMR with Jupiter are visible in both frames.
+In the EJ simulation, a gap in the vicinity of the 5:2 MMR is also visible.
+The non-axisymmetric character of the gaps reflects the fact that the planetesimals in the vicinity of the resonances (especially the 2:1) are having their eccentricities significantly pumped.
 Although examining the spatial distribution of planetesimals near MMR in debris disks may be a viable way to detect  unseen planets, we will not focus on this topic any longer as it has already been covered in detail in other studies \citep{2016ApJ...818..159T, 2018ApJ...857....3T}.
@@
 
-The location of the mean motion resonances with Jupiter is most clearly visible when examining the semimajor axis-eccentricity 
-distribution of the planetesimals. This is shown in figure \ref{fig:ae}, with the final snapshot from the CJ simulation shown on the left 
-and EJ on the right. The solid vertical lines indicate the nominal locations of the mean motion resonances. Away from the resonance 
-locations, the eccentricity dispersion grows via viscous stirring as energy from the Keplerian shearing of the disk is gradually 
-transferred to random motions of planetesimals. The slight inward curving of the eccentricity peaks near the resonances is a 
-consequence of the conservation of the Jacobi energy. As the semimajor axis of a planetesimal in MMR librates, the corresponding 
-change in eccentricity is given by equation \ref{eq:tiss}.
+%The location of the mean motion resonances with Jupiter is most clearly visible when examining the semimajor axis-eccentricity distribution of the planetesimals.
+This is shown in figure \ref{fig:ae}, with the final snapshot from the CJ simulation shown on the left and EJ on the right.
+The solid vertical lines indicate the nominal locations of the mean motion resonances.
+Away from the resonance locations, the eccentricity dispersion grows via viscous stirring as energy from the Keplerian shearing of the disk is gradually transferred to random motions of planetesimals.
+The slight inward curving of the eccentricity peaks near the resonances is a consequence of the conservation of the Jacobi energy.
+As the semimajor axis of a planetesimal in MMR librates, the corresponding change in eccentricity is given by equation \ref{eq:tiss}.
 

### 2019-12-16 main.tex
Finish discussion of figure 2, rewrite discussion of figure 3

@@
 %Things to change/do:
-%    Transient feature in EJ collision rate before 2000 years. Only want to look at collisions after this time. Justify the cutoff (maybe something to do with precession in 3:1 MMR?)
+%    Transient feature in EJ collision rate before 2000 years.
+Only want to look at collisions after this time.
+Mention this when discussing figure 4.
+Justify the cutoff (maybe something to do with precession in 3:1 MMR?)
 %    Safronov and Nbody collision rates. Not matching up well near resonance. The 'wings' from the resonances mess up calculation of velocity dispersion. Maybe do comparison
@@
 The non-axisymmetric shape of the gaps reflects the fact that planetesimals in the vicinity of the resonances have been excited onto 
-non-circular orbits. Although examining the spatial distribution of planetesimals near MMR in debris disks may be a viable way to 
+non-circular orbits. Although the spatial distribution of planetesimals near MMR in debris disks may provide clues to 
 detect unseen planets, we will not focus on this topic here, as it has already been covered in detail by other studies 
@@
 
-The MMRs are most clearly visible when viewing the semimajor axis and eccentricity distribution of the planetesimals. The top panel 
-of figure \ref{fig:ae} corresponds to the CJ simulation and the bottom panel corresponds to EJ. The solid vertical lines in this plot 
-represent the nominal locations of the resonances. Near the nominal resonance locations, the a-e distribution of the planetesimals 
-exhibits well-defined spikes which curve slightly inward due to conservation of the Jacobi energy. In the EJ simulation, the 
-eccentricity distribution of bodies near resonance extends below the initial forced value. This is a reflection of the fact that these 
+The MMRs are most clearly visible when viewing the semimajor axis and eccentricity distribution of the planetesimals. This is shown 
+in figure \ref{fig:ae}. The top panel corresponds to the CJ simulation and the bottom panel corresponds to EJ. The solid vertical lines 
+in this plot represent the nominal locations of the resonances. Near the nominal resonance locations, the a-e distribution of the 
+planetesimals exhibits well-defined spikes which curve slightly inward due to conservation of the Jacobi energy. In the EJ simulation, 
+the eccentricity distribution of bodies near resonance extends below the initial forced value. This is a reflection of the fact that these 
 bodies are undergoing libration, which drives periodic oscillations in both semimajor axis and eccentricity. The coupling between 
-these two quantities is described by equation \ref{eq:tiss}.
+these two quantities is described by equation \ref{eq:tiss}. In the EJ simulation, the eccentricity remains enhanced between the 
+MMRs due to the secular forcing by Jupiter. This also has the consequence of making the eccentricity spikes more prominent. The 
+reason for this is that the resonant perturbations scale with the eccentricity of the body in resonance $e$. This scaling is linear for a 
+first order MMR, while the scaling is quadratic for a second order MMR. This results in a greater relative prominence of the features 
+in figure \ref{fig:ae} of the 5:3 and 3:1 MMRs relative to the 2:1 in the EJ simulation.
 
-% old stuff
-%A side-by-side comparison of the final distribution in cylindrical coordinates of planetesimals from the CJ and EJ simulations is shown in figure \ref{fig:rtheta}.
-Gaps produced by the 3:1, 2:1 and 5:3 MMR with Jupiter are visible in both frames.
-In the EJ simulation, a gap in the vicinity of the 5:2 MMR is also visible.
-The non-axisymmetric character of the gaps reflects the fact that the planetesimals in the vicinity of the resonances (especially the 2:1) are having their eccentricities significantly pumped.
-Although examining the spatial distribution of planetesimals near MMR in debris disks may be a viable way to detect  unseen planets, we will not focus on this topic any longer as it has already been covered in detail in other studies \citep{2016ApJ...818..159T, 2018ApJ...857....3T}.
-It is worth noting, however that the spatial distribution of planetesimals shown in  figure \ref{fig:rtheta} appears qualitatively similar to figures 3 and 4 in \citep{2016ApJ...818..159T}.
-
-%The location of the mean motion resonances with Jupiter is most clearly visible when examining the semimajor axis-eccentricity distribution of the planetesimals.
-This is shown in figure \ref{fig:ae}, with the final snapshot from the CJ simulation shown on the left and EJ on the right.
-The solid vertical lines indicate the nominal locations of the mean motion resonances.
-Away from the resonance locations, the eccentricity dispersion grows via viscous stirring as energy from the Keplerian shearing of the disk is gradually transferred to random motions of planetesimals.
-The slight inward curving of the eccentricity peaks near the resonances is a consequence of the conservation of the Jacobi energy.
-As the semimajor axis of a planetesimal in MMR librates, the corresponding change in eccentricity is given by equation \ref{eq:tiss}.
-
-In the EJ simulation, the eccentricity remains enhanced between the MMRs due to the secular forcing effect of Jupiter. This also has 
-the consequence of making the eccentricity spikes due to the 5:2 and (what's the MMR at 3.6 AU?) more prominent. The reason for 
-this is that the libration width of a resonance generally scales with the eccentricity of the particle being perturbed. In a secularly 
-forced disk, the eccentricity of particles affected by resonance is larger, which increases the resonance width and allows a larger 
-region of the disk to be affected by a given resonance. Also visible in the EJ snapshot in figure \ref{fig:ae} are eccentricity spikes that 
-extend below the background eccentricity distribution. This is a clear sign that planetesimals in the MMRs are librating. The phase of 
-the libration is set by the resonant argument (maybe I should add an equation for the resonant argument in section 2).
-
-An additional effect that the MMRs have on the orbits of planetesimals is visible in figure \ref{fig:long_ph}. This shows the semimajor 
-axis distribution of planetesimals as a function of longitude of perihelion in the EJ simulation. As discussed in section 
-\ref{sec:sec_force}, the eccentric orbit of Jupiter causes the perihelia of the planetesimal orbits to align with the giant perturber. The 
-mean motion resonances, however, drive the rather vigorous precession of the orbits of planetesimals in their vicinity. Because the 
-timescale of the resonances is much shorter than the timescale for secular forcing, the longitudinal orientations of orbits close to the 
-MMRs are effectively randomized. The dashed horizontal lines in figure \ref{fig:long_ph} indicate the libration width of the MMRs at 
-the forced eccentricity (given by the magnitude of equation \ref{eq:eforced}. The size of the zone of vigorous precession roughly 
-matches the libration width of the MMRs. As will be discussed shortly, the relative longitudinal orientation of the orbits has important 
-implications for where and when planetesimal collisions occur at a given semimajor axis. Not shown is the longitude of perihelia and 
-semimajor axes of the bodies in the CJ simulation. Due to the lack of secular forcing, the orientations of the orbits of these bodes are 
-effectively random.
+The MMRs have one important additional effect, which is to drive precession of the longitude of perihelia of planetesimals near 
+resonance. This effect becomes important in the EJ simulation, in which the orbits of bodies are initially aligned with that of Jupiter 
+(see section \ref{sec:sec_force}). As is shown in figure \ref{fig:long_ph}, the strong precession induced by the MMRs overcomes the 
+secular forcing and randomizes the orbital orientations of bodies near the resonances. The dashed horizontal lines in figure 
+\ref{fig:long_ph} indicate the libration width of a planetesimal with an eccentricity of $e_{forced}$ at each resonance, which 
+approximately shows the zone of influence of each MMR. When looking at the collision rates in the disk, this difference in the orbital 
+orientations inside and outside of resonance will have an important effect on the radial structure of the second-generation dust, which 
+will be discussed shortly.  Although this fast precession is also present in the CJ simulation, the longitude of perihelia of 
+planetesimals in the disk exhibit no preferred direction, and so the precession from the MMRs produces no discernible difference in 
+the orbital structure of the disk.
 

### 2019-12-16 main.tex
Add intro to section 4.1

@@
 
+\subsection{Collision Rates}\label{sec:coll_rates}
+
+The Safronov collision rate given by equation \ref{eq:safronov} can be a viable way to predict the collision rates of planetesimals 
+using only their positions and velocities \citep{2017ApJ...850..103B}, but suffers from some limitations. First, the Safronov collision 
+rate is constructed from the assumption that the planetesimal disk is azimuthally symmetric. This is not the case for the EJ 
+simulation, in which the disk between resonances exhibits a well defined pericenter orientation. Although the strong precession 
+induced by the MMRs does randomize the orientations of orbits near the resonances, the phase space distribution of bodies at the 
+edges of the resonances becomes extremely complex and is best studied using a full N-body treatment. Secondly, as we will show 
+below, the velocity distribution of planetesimals takes on a bimodal distribution near the MMRs. This makes the rms velocity of 
+planetesimals not well-defined and therefore predicting the collision rate using a statistical approach becomes difficult.
+
 Next, we move on to examine the statistics of the collisions that occur. Figure \ref{fig:coll_hist_a} shows the distribution of semimajor 
@@
 
+%Explanation of offset of feature near 3:1 in EJ: orbital orientations randomized near MMR, most bodies have ecc of e_forced, even in resonance.
+Geometrically, less overlap at apo, so surface density drops and so does coll rate.
 Most notably, the prominent features visible in figure \ref{fig:coll_hist_a} adjacent to the 2:1 MMR no longer appear. This is due to the 

### 2019-12-17 main.tex
Rework discussion of figure 4

@@
 
-Next, we move on to examine the statistics of the collisions that occur. Figure \ref{fig:coll_hist_a} shows the distribution of semimajor 
-axes of every collision that is resolved. Here, the semimajor axis of a collision is defined as the semimajor axis of the first body 
-participating in the collision at the moment that it occurs. During a collision, the determination of which body is first and which is 
-second is determined by the collision search tree in {\sc ChaNGa}. To ensure that this does not introduce any bias, we also 
-constructed figure \ref{fig:coll_hist_a} using the orbital parameters of the second body and found no qualitative difference. By 
-examining the semimajor axis distribution of the collisions, it is easy to see how the MMRs affect the collision rates. The dashed lines 
-again represent the libration width of each resonance and are meant to show its range of influence. In both the circular and eccentric 
-Jupiter simulations, the collision rate is clearly enhanced interior to the 2:1 MMR. The 3:1 MMR only appears to have a noticeable 
-influence on the collision rate in the EJ simulation. In both cases, although the 5:3 MMR has a clear influence on the on the 
-semimajor-axis eccentricity distribution, it does not leave a measureable imprint on the collision rate. It is important to point out, 
-however, that the libration width of sufficiently eccentric particles near the 5:3 MMR may extend beyond the outer edge of the disk 
-and introduce boundary effects.
+Figure \ref{fig:coll_hist_a} shows the semimajor axis of collisions resolved in the CJ (top) and EJ simulations (bottom). The 
+'semimajor axis of a collision' is defined as the semimajor axis of the first of the two planetesimals participating in a collision at the 
+moment that it happens. To ensure that the definition of the first and second collider chosen by {\sc ChaNGa} does not influence 
+these results, we also tried constructing figure \ref{fig:coll_hist_a} using the second collider and found no qualitative differences. 
+Although both simulations were integrated and collisions were resolved for 5,000 years, we only show collisions that occurred during 
+the last 3,000 years of the simulations. Before this time, the resonant features in the semimajor axis-eccentricity distribution (see 
+figure \ref{fig:ae}) were still developing and had not yet reached a steady state. This results in transient features appearing in the 
+collision profiles early on, which we exclude from figure \ref{fig:coll_hist_a} and all subsequent figures.
 
-Although the semimajor axis of a particle at the moment of collision provides useful information about how the mean motion 
-resonances affect the collision rate in the disk, this information alone is not enough to predict where the second generation dust that 
-is produced will end up. To do so, we will operate under the assumption that dust grains produced by collision events will quickly 
-couple to the gas and attain a circular orbit. This assumption, which will be further justified in section \ref{sec:dust}, allows to map the 
-radial variation in the dust surface density to the radial position of the collisions. This is shown in figure \ref{fig:coll_hist_r}, where the 
-histograms indicate the x and y coordinates of a body at the moment that it undergoes a collision.
+Most notably, the MMRs appear to have a measurable effect on the local collision rates. Slightly interior to the 2:1 resonance, the 
+collision rate increases by a factor of roughly 2. In the EJ simulation, there is a significant deficiency in the number of collisions near 
+the 3:1 MMR. We attribute this to the fact that the strength of a second order MMR scales as $e^{2}$, while a first order MMR scales 
+linearly. Therefore, one would expect the 3:1 resonance to have more of an influence on the collision rate in a secularly perturbed 
+disk. Although viewing the collision rate as a function of semimajor axis allows one to see a clear connection between the 
+resonances and the collision rate, this does not immediately indicate where the dust generated by collisions will end up in the disk.
+
+%Next, we move on to examine the statistics of the collisions that occur.
+Figure \ref{fig:coll_hist_a} shows the distribution of semimajor axes of every collision that is resolved.
+Here, the semimajor axis of a collision is defined as the semimajor axis of the first body participating in the collision at the moment that it occurs.
+During a collision, the determination of which body is first and which is second is determined by the collision search tree in {\sc ChaNGa}.
+To ensure that this does not introduce any bias, we also constructed figure \ref{fig:coll_hist_a} using the orbital parameters of the second body and found no qualitative difference.
+By examining the semimajor axis distribution of the collisions, it is easy to see how the MMRs affect the collision rates.
+The dashed lines again represent the libration width of each resonance and are meant to show its range of influence.
+In both the circular and eccentric Jupiter simulations, the collision rate is clearly enhanced interior to the 2:1 MMR.
+The 3:1 MMR only appears to have a noticeable influence on the collision rate in the EJ simulation.
+In both cases, although the 5:3 MMR has a clear influence on the on the semimajor-axis eccentricity distribution, it does not leave a measureable imprint on the collision rate.
+It is important to point out, however, that the libration width of sufficiently eccentric particles near the 5:3 MMR may extend beyond the outer edge of the disk and introduce boundary effects.
+
+%Although the semimajor axis of a particle at the moment of collision provides useful information about how the mean motion resonances affect the collision rate in the disk, this information alone is not enough to predict where the second generation dust that is produced will end up.
+To do so, we will operate under the assumption that dust grains produced by collision events will quickly couple to the gas and attain a circular orbit.
+This assumption, which will be further justified in section \ref{sec:dust}, allows to map the radial variation in the dust surface density to the radial position of the collisions.
+This is shown in figure \ref{fig:coll_hist_r}, where the histograms indicate the x and y coordinates of a body at the moment that it undergoes a collision.
 

### 2019-12-18 main.tex
Add motivation for dust circularizing

@@
 
+To construct a radial dust profile, we begin by making the assumption that any dust generated by collisions is strongly coupled to the 
+gas. For a dust grain larger than the mean free path of the gas particles, the timescale to damp its eccentricity is given by 
+\citep{1976PThPh..56.1756A}
+
+\begin{equation}\label{eq:t_edamp}
+    t_{e, damp} = \frac{8 s \rho}{3 e C_{D} \rho_{g} v_{th}}.
+\end{equation}
+
+where $m$, $e$ and $s$ are the mass, eccentricity and radius of the dust grain. $C_{D}$ is a drag coefficient which is of order unity, $
+\rho_{g}$ is the local density of the gas and $v_{th}$ is its thermal speed. At 3 AU, the gaseous component of the solar nebula has a 
+density of $4 \times 10^{-10}$ g cm$^{-3}$ and a typical thermal speed of $10^{5}$ cm s$^{-1}$ \citep{1981PThPS..70...35H}. For a 1 
+mm dust grain with a density of 1 g cm$^{-3}$ and an eccentricity of 0.05, the damping timescale is $4 \times 10^{-3}$ years. This is 
+orders of magnitude smaller than the collision timescale, therefore we expect that collisionally generated dust grains will immediately 
+couple to the gas.
+
+Operating under this assumption, a map of the relative concentration of second-generation dust can be constructed from simply the cylindrical distance at which the collisions occur.
+This is shown in the top panels of figure \ref{fig:coll_hist_r}, where the left side corresponds to the CJ simulation and the right side corresponds to EJ.
+
 %Next, we move on to examine the statistics of the collisions that occur.

### 2019-12-18 main.tex
Add discussion of figure 5

@@
 This is shown in the top panels of figure \ref{fig:coll_hist_r}, where the left side corresponds to the CJ simulation and the right side corresponds to EJ.
+As in the semimajor axis projection, features appear near the 2:1 and 3:1 MMRs in both simulations, although the shape of the features are qualitatively different here.
+Near the 2:1 resonance, the radial collision rate is noticably suppressed.
+This is mainly due to the reduced surface density of planetesimals near the center of the resonance, shown in the second row of figure \ref{fig:coll_hist_r}.
+The surface density in the EJ simulation near this resonance is less suppressed than the CJ simulation due to the enhanced eccentricity of planetesimals in the vicinity.
+This also has the effect of washing out the feature created in the collision rate profile due to the 2:1 MMR.
+
+Additionally, a sharp, well-defined feature appears just exterior to the 3:1 MMR in the EJ simulation.
+A corresponding dip in the surface density at this same location suggests that the variation in the collision rate here is due to a lack of planetesimals in this location.
+Upon closer inspection, we find that the center of this feature lies at a a radial distance of $(1+e_{forced})a_{3:1}$, where $a_{3:1}$ is the nominal location of the 3:1 MMR and $e_{forced}$ is the forced eccentricity of a planetesimal at $a_{3:1}$.
+This distance corresponds to the aphelion distance of a planetesimal with these orbital parameters.
+Physically, the drop in the surface density here can be explained as follows: bodies near the 3:1 MMR experience strong precession, which randomizes their orbits and undergo libration which produces a large spread in their relative velocities.
+For a collection of randomly oriented eccentric orbits, there is less geometric overlap at aphelion, which lowers the surface density at this distance.
+Given the clear connection between the offset of this feature and the local forced eccentricity, we will examine the feasibility of using this feature to measure the eccentricity of the perturbing planet in section \ref{sec:dust} after we construct a dust emission map from the collision rate profile.
+
+The bottom row of figure \ref{fig:coll_hist_r} demonstrates the difficulty with calculating the collision rate from the position and velocity distribution of particles.
+Typically, the rms velocity is defined as $\sqrt(\left<e^2\right> + \left<i^2\right>)$.
+In this case, the wings extending off of the resonances in the distance-eccentricity distribution makes the eccentricity dispersion distinctly bimodal and not well defined at nearly all radial distances.
+A naive calculation of the Safronov rate here would predict a collision rate near the resonances that is smaller than the actual value.
 

### 2020-04-11 makeFig.py
Update orbit and collision library calls in makeFig, change paper to onecolumn style

@@ -1,6 +1,10 @@
 #/bin/bash
 import matplotlib.pylab as plt
 import matplotlib as mpl
+
+mpl.rcParams.update({'font.size': 18, 'font.family': 'STIXGeneral', 'mathtext.fontset': 'stix',
+                            'image.cmap': 'viridis'})
+
 import numpy as np
 import pandas as pd
 import pynbody as pb
@@ -14,18 +18,13 @@ simT = u.year/(2*np.pi)
 simV = u.AU / simT
 
 from scipy import stats
-
-import sys
-sys.path.insert(0, '../OrbitTools/')
-import OrbitTools
-
-mpl.rcParams.update({'font.size': 18, 'font.family': 'STIXGeneral', 'mathtext.fontset': 'stix',
-                            'image.cmap': 'viridis'})
+import KeplerOrbit as ko
+import CollisionTools as coll
 
 simT = u.year/(2*np.pi)
 simV = u.AU/simT
 
-path = '../files/research/planetFormation/jupResonance/data/'
+path = 'data/'
 
 # Resonances
 res_dist = [2.5, 3.27, 3.7]
@@ -42,9 +41,9 @@ def res_width_jup(p, q):
     j1 = p + q
     j2 = -p
     alpha = (-j2/j1)**(2./3.)
-    ecc = OrbitTools.lap(2, 3/2, alpha)/OrbitTools.lap(1, 3/2, alpha)*ecc_jup
+    ecc = ko.lap(2, 3/2, alpha)/ko.lap(1, 3/2, alpha)*ecc_jup
     dist = alpha*a_jup
-    rw = OrbitTools.res_width(m, m_c, ecc, j1, j2)*dist
+    rw = ko.res_width(m, m_c, ecc, j1, j2)*dist
     return rw
 
 def plot_res(axis, res=-1, vertical=True, show_widths=False):
@@ -74,8 +73,8 @@ s_e_files = np.array([path + 'hkshiftfull/hkshiftfull.ic']+ \
 	                  ns.natsorted(gl.glob(path + 'hkshiftfull/*.[0-9]*[0-9]')))
 s0_e = pb.load(s_e_files[0])
 
[…]

### 2020-04-13 main.tex
Update orbit and collision library calls in makeFig, change paper to onecolumn style
Update text and figures

@@
-\documentclass[twocolumn]{aastex63}
+\documentclass[onecolumn]{aastex63}
 \usepackage{natbib}
@@
 
-\subsection{Collisions}
+\subsection{Collision Rates of Massive Bodies}
 
@@
 
-\noindent where $r_{p}$ is the radius of a planetesimal and $v_{esc}$ is the mutual escape velocity of two planetesimals in contact. 
-The $v_{esc}^2/v_{p}^2$ term describes the factor above which the collision cross section is enhanced due to gravitational focusing. 
-For a dynamically cold planetesimal disk, $v_{p}$ is small relative to $v_{esc}$ and the collision rate becomes strongly enhanced.
+\noindent where $r_{p}$ is the radius of a planetesimal, $v_{esc}$ is the mutual escape velocity of two planetesimals in contact and 
+$v_{p}$ is the typical encounter velocity between planetesimals. The $v_{esc}^2/v_{p}^2$ term describes the factor above which the 
+collision cross section is enhanced due to gravitational focusing. For a dynamically cold planetesimal disk, $v_{p}$ is small relative to 
+$v_{esc}$ and the collision rate becomes strongly enhanced.
 
-In the absence of a proper treatment of collision detection, equation \ref{eq:safronov} can be used to make a local estimate of the 
-collision rate in an N-body simulation using only the positions and velocities of particles. This has been done in other studies 
+In the absence of collision detection, equation \ref{eq:safronov} can be used to make a local estimate of the 
+collision rate in an N-body simulation using only the positions, velocities and masses of particles. This has been done in other studies 
 \citep{2017ApJ...850..103B} (any other examples?), but requires bulk averaging of the phase space properties of particles, which 
-may mask important information and blur out features. We will revisit equation \ref{eq:safronov} in section \ref{sec:results} to test 
-how well the collision rate near mean motion resonances is described by this framework.
+may mask important information and blur out features. As we will show in section \ref{sec:results}, the complex dynamical behavior of 
+planetesimals near mean-motion resonance makes it difficult to represent the typical encounter velocity $v_{p}$ with a single value. We will 
+revisit equation \ref{eq:safronov} in section \ref{sec:results} to test how well the collision rate near mean-motion resonances is described by 
+this framework.
 
@@
 
-Ignoring secular and mean motion resonances, equation \ref{eq:eforced} will completely describe the eccentricities and pericenter 
-orientations of the orbits of the planetesimals. Additional forces due to two-body scattering between planetesimals, along with 
+Without any nearby secular or mean motion resonances, equation \ref{eq:eforced} will completely describe the eccentricities longitude of  pericenter orientations of the planetesimals.
+Additional forces due to two-body scattering between planetesimals, along with
 aerodynamic gas drag will add an additional free component to the complex eccentricity, which will be randomly oriented. The 
@@
 
-Under the effect of MMR, a body will undergo oscillations in semi-major axis and eccentricity. So long as the gravitational force on 
-the body is dominated by the central star and the perturbing body, the amplitude of the oscillations in semi-major axis can be 
-described using the pendulum approximation (see equation 8.76 in \citet{2000ssd..book.....M}). This amplitude can be thought of 
-as the 'width' over which the perturbations of the resonance are effective. Variations in eccentricity follow the semi-major axis 
+Under the effect of MMR, a body will undergo oscillations in semi-major axis and eccentricity. For sufficiently small perturbations,
+the amplitude of the oscillations in semi-major axis can be 
+described using the pendulum approximation (see equation 8.58 and 8.76 in \citet{2000ssd..book.....M}). This amplitude can be thought of 
+as the 'width' over which resonant perturbations are effective. Changes in eccentricity are correlated with changes in semi-major axis 
 variations according to the Tisserand relation
@@
 The net result of this is that isolated MMRs will produce 'spikes' in the semi-major axis vs eccentricity distribution of a planetesimal 
-disk. Following equation \ref{eq:tiss}, these spikes will tend to slightly curve away from the perturbing body. As planetesimals 
-undergo two-body scattering events with other bodies, the variations in semi-major axis and eccentricity due to resonances can 
-become permanent. This tends to lower the surface density of the disk near the locations of resonances, while producing a pileup of 
-eccentric bodies adjacent to the MMR. The enhanced surface density will increase the collision rate, while the large eccentricity 
-dispersion will lower it due to the decreased effectiveness of gravitational focusing. Due to these competing effects, along with the 
-complicated dynamics that are likely at play near the edge of the resonant region, we turn to a direct N-body treatment to better 
-understand how the collision rate varies in the vicinity of a MMR.
+disk. Following equation \ref{eq:tiss}, these spikes will tend to slightly curve away from the perturbing body. This tends to lower the surface 
+density of the disk near the locations of resonances, while producing a pileup of bodies on eccentric orbits adjacent to the MMR. The 
+enhanced surface density will increase the collision rate, while the larger eccentricites will lower it due to the decreased effectiveness of 
+gravitational focusing. In addition, the MMRs will drive fast precession of the orbiting planetesimals, which effectively randomizes their 
+longitudes of perihelion. In the case of a secularly forced disk, there will be an interface between aligned and randomly oriented orbits at 
+the edge of the resonance. Due to the complicated dynamics that are likely at play near the edge of the resonant region, we turn to a direct 
+N-body treatment to better understand how the collision rate varies in the vicinity of a MMR.
 
@@
 simulation. We reduce the base time step size by an additional factor of 4 to the keep longitude of perihelia of planetesimals near the 
-inner edge of the disk from drifting too far over the course of our integration.
+inner edge of the disk from drifting too far over the course of our integrations.
 
@@
 \begin{figure*}
-    \includegraphics[width=\textwidth]{figures/rtheta.png}
-    \caption{Caption goes here.\label{fig:rtheta}}
+    \includegraphics[width=\textwidth]{figures/xy.png}
+    \caption{Caption goes here.\label{fig:xy}}
 \end{figure*}
@@
 \begin{figure}
-    \includegraphics[width=\columnwidth]{figures/ae.png}
+    \begin{center}
+    \includegraphics[width=0.4\columnwidth]{figures/ae.png}
     \caption{Caption goes here.\label{fig:ae}}
+    \end{center}
 \end{figure}
@@
 \begin{figure}
-    \includegraphics[width=\columnwidth]{figures/long_ph.png}
+    \begin{center}
+    \includegraphics[width=0.4\columnwidth]{figures/long_ph.png}
     \caption{Caption goes here.\label{fig:long_ph}}
+    \end{center}
 \end{figure}
@@
 \begin{figure}
-    \includegraphics[width=\columnwidth]{figures/coll_hist_a.png}
+    \begin{center}
+    \includegraphics[width=0.4\columnwidth]{figures/coll_hist_a.png}
     \caption{Caption goes here.\label{fig:coll_hist_a}}
+    \end{center}
 \end{figure}
-
-\begin{figure*}
-    \includegraphics[width=\textwidth]{figures/coll_hist_r.png}
-    \caption{Caption goes here.\label{fig:coll_hist_r}}
-\end{figure*}
 
@@
 
-We begin by examining the spatial distribution of planetesimals in both simulations. The polar position of the planetesimals at the 
-end of the CJ and EJ simulations are shown in the left and right hand panels of  figure \ref{fig:rtheta}, respectively. Gaps produced by 
-the 3:1, 2:1 and 5:3 MMR with Jupiter are visible in both cases. In the EJ case, a gap in the vicinity of the 5:2 MMR is also visible. 
-The non-axisymmetric shape of the gaps reflects the fact that planetesimals in the vicinity of the resonances have been excited onto 
-non-circular orbits. Although the spatial distribution of planetesimals near MMR in debris disks may provide clues to 
-detect unseen planets, we will not focus on this topic here, as it has already been covered in detail by other studies 
-\citep{2016ApJ...818..159T, 2018ApJ...857....3T}.
+We begin by examining the spatial distribution of planetesimals in the CJ and EJ simulations. The cylindrical position of the planetesimals 
+in the the CJ and EJ simulations after 5000 years of integration are shown in the left and right hand panels of  figure \ref{fig:xy}, 
+respectively. In the circular Jupiter case, a gap produced by the 2:1 MMR is visible, while the 3:1 and 5:3 MMR gaps are visible with an 
+eccentric Jupiter. The non-axisymmetric nature of the gaps is due to the fact that planetesimals in the vicinity of the resonances have been 
+excited onto non-circular orbits. Although the spatial distribution of planetesimals near MMR in debris disks may provide clues to detect 
+unseen planets, we will not focus on this topic here, as it has already been covered in detail by other studies \citep{2016ApJ...818..159T, 
+2018ApJ...857....3T}.
 
@@
 these two quantities is described by equation \ref{eq:tiss}. In the EJ simulation, the eccentricity remains enhanced between the 
-MMRs due to the secular forcing by Jupiter. This also has the consequence of making the eccentricity spikes more prominent. The 
-reason for this is that the resonant perturbations scale with the eccentricity of the body in resonance $e$. This scaling is linear for a 
-first order MMR, while the scaling is quadratic for a second order MMR. This results in a greater relative prominence of the features 
-in figure \ref{fig:ae} of the 5:3 and 3:1 MMRs relative to the 2:1 in the EJ simulation.
+MMRs due to the secular forcing by Jupiter. Because the strength of the resonances scales with the initial eccentricity of the planetesimals, 
+the eccentricity spikes are larger in the EJ simulation. Additionally, the relative size of the 3:1 and 5:3 MMR spikes also grows because the 
+strength of a MMR scales as $e^{k}$, where $k$ is the order of the resonance (citation needed).
 
-The MMRs have one important additional effect, which is to drive precession of the longitude of perihelia of planetesimals near 
+The MMRs have one more effect, which is to drive precession of the longitudes of perihelion of planetesimals near 
 resonance. This effect becomes important in the EJ simulation, in which the orbits of bodies are initially aligned with that of Jupiter 
@@
 \ref{fig:long_ph} indicate the libration width of a planetesimal with an eccentricity of $e_{forced}$ at each resonance, which 
-approximately shows the zone of influence of each MMR. When looking at the collision rates in the disk, this difference in the orbital 
-orientations inside and outside of resonance will have an important effect on the radial structure of the second-generation dust, which 
-will be discussed shortly.  Although this fast precession is also present in the CJ simulation, the longitude of perihelia of 
-planetesimals in the disk exhibit no preferred direction, and so the precession from the MMRs produces no discernible difference in 
-the orbital structure of the disk.
+approximately shows the zone of influence of each MMR. It is important to note that the collision rate predicted by equation
+\ref{eq:safronov} assumes that the orbits of bodies are randomly oriented. Near the interface of the resonances, the N-body collision rate, 
+which we will examine next, is likely not well-described by the Safronov rate.
 
@@
 
-The Safronov collision rate given by equation \ref{eq:safronov} can be a viable way to predict the collision rates of planetesimals 
-using only their positions and velocities \citep{2017ApJ...850..103B}, but suffers from some limitations. First, the Safronov collision 
-rate is constructed from the assumption that the planetesimal disk is azimuthally symmetric. This is not the case for the EJ 
-simulation, in which the disk between resonances exhibits a well defined pericenter orientation. Although the strong precession 
-induced by the MMRs does randomize the orientations of orbits near the resonances, the phase space distribution of bodies at the 
-edges of the resonances becomes extremely complex and is best studied using a full N-body treatment. Secondly, as we will show 
-below, the velocity distribution of planetesimals takes on a bimodal distribution near the MMRs. This makes the rms velocity of 
-planetesimals not well-defined and therefore predicting the collision rate using a statistical approach becomes difficult.
+As we have already discussed, the Safronov collision rate given by equation \ref{eq:safronov} suffers from two important limitations. The
+first is that the orbits of colliding bodies exhibit no preferred orientation. Second, as we will show below, the velocities of planetesimals 
+near the MMRs follows a bimodal distribution. This makes it difficult to characterize the planetesimals with a single 'typical' encounter 
+velocity and therefore predicting the collision rate using a statistical approach is far from straightforward.
 
-Figure \ref{fig:coll_hist_a} shows the semimajor axis of collisions resolved in the CJ (top) and EJ simulations (bottom). The 
-'semimajor axis of a collision' is defined as the semimajor axis of the first of the two planetesimals participating in a collision at the 
+Figure \ref{fig:coll_hist_a} shows the semimajor axis of collisions resolved in the CJ (top) and EJ simulations (bottom). We define 
+'semimajor axis of a collision' as the semimajor axis of the first of the two planetesimals participating in a collision at the 
 moment that it happens. To ensure that the definition of the first and second collider chosen by {\sc ChaNGa} does not influence 
@@
 the last 3,000 years of the simulations. Before this time, the resonant features in the semimajor axis-eccentricity distribution (see 
-figure \ref{fig:ae}) were still developing and had not yet reached a steady state. This results in transient features appearing in the 
-collision profiles early on, which we exclude from figure \ref{fig:coll_hist_a} and all subsequent figures.
+figure \ref{fig:ae}) were still developing and had not yet reached a steady state (the libration timescale of the MMRs we are interested in turns out to be about 2,000 years).
+This results in transient features appearing in the collision profiles early on, which we exclude from figure \ref{fig:coll_hist_a} and all subsequent figures.
 
-Most notably, the MMRs appear to have a measurable effect on the local collision rates. Slightly interior to the 2:1 resonance, the 
-collision rate increases by a factor of roughly 2. In the EJ simulation, there is a significant deficiency in the number of collisions near 
-the 3:1 MMR. We attribute this to the fact that the strength of a second order MMR scales as $e^{2}$, while a first order MMR scales 
-linearly. Therefore, one would expect the 3:1 resonance to have more of an influence on the collision rate in a secularly perturbed 
-disk. Although viewing the collision rate as a function of semimajor axis allows one to see a clear connection between the 
-resonances and the collision rate, this does not immediately indicate where the dust generated by collisions will end up in the disk.
+We find that the features present in figure \ref{fig:coll_hist_a} are highly sensitive to the choice of binning when constructing a standard histogram and instead model the occurrence of collisions as a function of semimajor axis using a kernel density estimate (KDE).
+We use the {\sc neighbors.KernelDensity} function from the {\sc sklearn} \citep{scikit-learn} package to construct our KDEs.
+For our kernel, we use a tophat function with a bandwidth of 0.01 AU.
+
+Most notably, the MMRs appear to have a measurable effect on the local collision rates. This is in contrast to \citet{2000Icar..143...45R}, 
+who simulated a similar setup and found no discernible features near the MMRs. We attribute the difference to a more careful treatment of 
+timestepping in our simulations. Slightly interior to the 2:1 resonance, the collision rate increases by a factor of roughly 2. In the EJ 
+simulation, there is a significant deficiency in the number of collisions near the 3:1 MMR. We attribute this to the fact that the strength of a 
+second order MMR scales as $e^{2}$, while a first order MMR scales linearly with $e$. One would therefore expect the 3:1 resonance to 
+have more of an influence on the collision rate in a secularly perturbed disk. Although viewing the collision rate as a function of semimajor 
+axis demonstrates a clear connection between the resonances and the collision rate, this does not immediately indicate where the dust 
+generated by collisions will end up in the disk.
 
@@
 mm dust grain with a density of 1 g cm$^{-3}$ and an eccentricity of 0.05, the damping timescale is $4 \times 10^{-3}$ years. This is 
-orders of magnitude smaller than the collision timescale, therefore we expect that collisionally generated dust grains will immediately 
+orders of magnitude smaller than the collision timescale, therefore we conclude that collisionally generated dust grains will immediately 
 couple to the gas.
 
-Operating under this assumption, a map of the relative concentration of second-generation dust can be constructed from simply the cylindrical distance at which the collisions occur.
+Operating under this assumption, a map of the relative concentration of second-generation dust can be constructed from the cylindrical distance at which the collisions occur.
 This is shown in the top panels of figure \ref{fig:coll_hist_r}, where the left side corresponds to the CJ simulation and the right side corresponds to EJ.
-As in the semimajor axis projection, features appear near the 2:1 and 3:1 MMRs in both simulations, although the shape of the features are qualitatively different here.
+As in figure \ref{fig:coll_hist_a}, a kernel density estimate of the number of collisions is constructed using a tophat kernel with a bandwidth of 0.01 AU.
+Features again appear near the 2:1 and 3:1 MMRs in both simulations, although the shape of the features are qualitatively different from figure \ref{fig:coll_hist_a}.
 Near the 2:1 resonance, the radial collision rate is noticably suppressed.
@@
 A naive calculation of the Safronov rate here would predict a collision rate near the resonances that is smaller than the actual value.
+
+\begin{figure*}
+    \includegraphics[width=\textwidth]{figures/coll_hist_r.png}
+    \caption{Caption goes here.\label{fig:coll_hist_r}}
+\end{figure*}
 

### 2020-04-13 makeFig.py

@@ -32,6 +32,22 @@ res_label = ['3:1', '2:1', '5:3']
 res_p = [1, 1, 3]
 res_q = [2, 1, 2]
 
+# Build a PDF from a series of data points using a KDE
+from sklearn.neighbors import KernelDensity
+def kde(qty, bw=0.01):
+    bins = np.linspace(np.log10(np.min(qty)), np.log10(np.max(qty)))
+    
+    def kde_helper(x, x_grid, **kwargs):
+        kde_skl = KernelDensity(kernel='tophat', bandwidth=bw, **kwargs)
+        kde_skl.fit(x[:, np.newaxis])
+        log_pdf = kde_skl.score_samples(x_grid[:, np.newaxis])
+        return np.exp(log_pdf)
+    
+    pdf = kde_helper(np.log10(qty), bins)
+    cum_df = np.cumsum(pdf[::-1])[::-1]
+    
+    return 10.**bins, pdf
+
 # Width of a resonance with jupiter (in AU)
 # Assume body has an eccentricity of e_forced
 def res_width_jup(p, q):
@@ -113,6 +129,34 @@ r_c, theta_c = np.sqrt(x_c**2 + y_c**2), np.arctan2(y_c, x_c) + np.pi
 x_e, y_e = pl_e['pos'][:,0], pl_e['pos'][:,1]
 r_e, theta_e = np.sqrt(x_e**2 + y_e**2), np.arctan2(y_e, x_e) + np.pi
 
+def make_xy():
+	file_str = 'figures/xy.' + fmt
+	if not clobber and os.path.exists(file_str):
+		return
+
+	# Rotate so that jupiter is at theta =0
+	theta_jup_c = np.arctan2(pl_c['pos'][0][1], pl_c['pos'][0][0])
+	x_c_rot = x_c*np.cos(-theta_jup_c) - y_c*np.sin(-theta_jup_c)
+	y_c_rot = x_c*np.sin(-theta_jup_c) + y_c*np.cos(-theta_jup_c)
+	theta_jup_e = np.arctan2(pl_e['pos'][0][1], pl_e['pos'][0][0])
+	x_e_rot = x_e*np.cos(-theta_jup_e) - y_e*np.sin(-theta_jup_e)
[…]

### 2020-04-13 main.tex
Add citation for resonance order and strength

@@
 the eccentricity spikes are larger in the EJ simulation. Additionally, the relative size of the 3:1 and 5:3 MMR spikes also grows because the 
-strength of a MMR scales as $e^{k}$, where $k$ is the order of the resonance (citation needed).
+strength of a MMR scales as $e^{q}$, where $q$ is the order of the resonance \citep{1994PhyD...77..289M}.
 
@@
 the last 3,000 years of the simulations. Before this time, the resonant features in the semimajor axis-eccentricity distribution (see 
-figure \ref{fig:ae}) were still developing and had not yet reached a steady state (the libration timescale of the MMRs we are interested in turns out to be about 2,000 years).
-This results in transient features appearing in the collision profiles early on, which we exclude from figure \ref{fig:coll_hist_a} and all subsequent figures.
+figure \ref{fig:ae}) were still developing and had not yet reached a steady state (the libration timescale of the MMRs we are interested in 
+turns out to be about 2,000 years). This results in transient features appearing in the collision profiles early on, which we exclude from 
+figure \ref{fig:coll_hist_a} and all subsequent figures.
 
-We find that the features present in figure \ref{fig:coll_hist_a} are highly sensitive to the choice of binning when constructing a standard histogram and instead model the occurrence of collisions as a function of semimajor axis using a kernel density estimate (KDE).
-We use the {\sc neighbors.KernelDensity} function from the {\sc sklearn} \citep{scikit-learn} package to construct our KDEs.
-For our kernel, we use a tophat function with a bandwidth of 0.01 AU.
+We find that the features present in figure \ref{fig:coll_hist_a} are highly sensitive to the choice of binning when constructing a standard 
+histogram and instead model the occurrence of collisions as a function of semimajor axis using a kernel density estimate (KDE). We use 
+the {\sc neighbors.KernelDensity} function from the {\sc sklearn} \citep{scikit-learn} package to construct our KDEs. For our kernel, we use 
+a tophat function with a bandwidth of 0.01 AU.
 
@@
 simulation, there is a significant deficiency in the number of collisions near the 3:1 MMR. We attribute this to the fact that the strength of a 
-second order MMR scales as $e^{2}$, while a first order MMR scales linearly with $e$. One would therefore expect the 3:1 resonance to 
-have more of an influence on the collision rate in a secularly perturbed disk. Although viewing the collision rate as a function of semimajor 
-axis demonstrates a clear connection between the resonances and the collision rate, this does not immediately indicate where the dust 
-generated by collisions will end up in the disk.
+second order MMR scales as $e^{2}$, while a first order MMR scales linearly with $e$ \citep{1994PhyD...77..289M}. One would therefore 
+expect the 3:1 resonance to have more of an influence on the collision rate in a secularly perturbed disk. Although viewing the collision rate 
+as a function of semimajor axis demonstrates a clear connection between the resonances and the collision rate, this does not immediately 
+indicate where the dust generated by collisions will end up in the disk.
 

### 2020-04-13 main.tex
Finish results section

--- 2020-04-13 main.tex
@@
 dynamics. So long as the random velocities of planetesimals $v_{p}$ are large compared to the Hill velocity of a planetesimal $v_{h} 
-= \sqrt{G m_{p} / r_{h}}$, where $r_{h}$ is the Hill radius, the gravitational field of the central star will play an insignificant role and 
-can be safely ignored. In this case and assuming equal mass bodies, the collision rate is given by \citep{1967SvA....10..650S}
+= \sqrt{G m_{p} / r_{h}}$, where $r_{h}$ is the Hill radius, the gravitational field of the central star will play an insignificant role during a 
+encounter and can be safely ignored. In this case and assuming equal mass bodies, the collision rate is given by 
+\citep{1967SvA....10..650S}
 
@@
 The net result of this is that isolated MMRs will produce 'spikes' in the semi-major axis vs eccentricity distribution of a planetesimal 
-disk. Following equation \ref{eq:tiss}, these spikes will tend to slightly curve away from the perturbing body. This tends to lower the surface 
+disk. Equation \ref{eq:tiss} predicts that these spikes will tend to slightly curve away from the perturbing body. This lowers the surface 
 density of the disk near the locations of resonances, while producing a pileup of bodies on eccentric orbits adjacent to the MMR. The 
 enhanced surface density will increase the collision rate, while the larger eccentricites will lower it due to the decreased effectiveness of 
-gravitational focusing. In addition, the MMRs will drive fast precession of the orbiting planetesimals, which effectively randomizes their 
-longitudes of perihelion. In the case of a secularly forced disk, there will be an interface between aligned and randomly oriented orbits at 
-the edge of the resonance. Due to the complicated dynamics that are likely at play near the edge of the resonant region, we turn to a direct 
-N-body treatment to better understand how the collision rate varies in the vicinity of a MMR.
+gravitational focusing. In addition, the MMRs cause the orbits of planetesimals to precess on relatively short timescales, which effectively 
+randomizes their longitudes of perihelion. In a secularly forced disk, there will be an interface between aligned and randomly oriented orbits 
+at the edge of the resonance. Due to the complicated dynamics that are at play in this region, we turn to a direct N-body treatment to better 
+understand how the collision rate varies in the vicinity of a MMR.
 
@@
 
+\section{Results} \label{sec:results}
+
+We begin by examining the spatial distribution of planetesimals in the CJ and EJ simulations. The cylindrical position of the planetesimals 
+in the the CJ and EJ simulations after 5000 years of integration are shown in the left and right hand panels of  figure \ref{fig:xy}, 
+respectively. In the circular Jupiter case, a gap produced by the 2:1 MMR is visible, while the 3:1 and 5:3 MMR gaps are visible with an 
+eccentric Jupiter. The non-axisymmetric nature of the gaps is due to the fact that planetesimals in the vicinity of the resonances have been 
+excited onto non-circular orbits. Although the spatial distribution of planetesimals near MMR in debris disks may provide clues to detect 
+unseen planets, we will not focus on this topic here, as it has already been covered in detail by other studies \citep{2016ApJ...818..159T, 
+2018ApJ...857....3T}.
+
+The MMRs are most clearly visible when viewing the semimajor axis and eccentricity distribution of the planetesimals. This is shown 
+in figure \ref{fig:ae}. The top panel corresponds to the CJ simulation and the bottom panel corresponds to EJ. The solid vertical lines 
+in this plot represent the nominal locations of the resonances. Near the nominal resonance locations, the a-e distribution of the 
+planetesimals exhibits well-defined spikes which curve slightly inward due to conservation of the Jacobi energy. In the EJ simulation, 
+the eccentricity distribution of bodies near resonance extends below the initial forced value. This is a reflection of the fact that the resonant 
+angles of these bodies are undergoing libration, which drives periodic oscillations in both semimajor axis and eccentricity. The coupling 
+between these two quantities is described by equation \ref{eq:tiss}. Because the strength of the resonances scales with the initial 
+eccentricity of the planetesimals, the eccentricity spikes are larger in the EJ simulation. Additionally, the relative size of the 3:1 and 5:3 
+MMR spikes also grows because the strength of a MMR scales as $e^{q}$, where $q$ is the order of the resonance 
+\citep{1994PhyD...77..289M}.
+
 \begin{figure}
@@
 \end{figure}
+
+The MMRs have an additional important effect, which is to drive precession of the longitudes of perihelion of planetesimals. 
+This effect becomes important in the EJ simulation because the orbits of bodies are initially aligned with that of Jupiter 
+(see section \ref{sec:sec_force}). As is shown in figure \ref{fig:long_ph}, the strong precession induced by the MMRs overcomes the 
+secular forcing and randomizes the orbital orientations of bodies near the resonances. The dashed horizontal lines in figure 
+\ref{fig:long_ph} indicate the libration width (should probably show the equation I used to calculate this) of a planetesimal with an 
+eccentricity of $e_{forced}$ at each resonance, which approximately shows the zone of influence of each MMR.
 
@@
 
-\section{Results} \label{sec:results}
-
-We begin by examining the spatial distribution of planetesimals in the CJ and EJ simulations. The cylindrical position of the planetesimals 
-in the the CJ and EJ simulations after 5000 years of integration are shown in the left and right hand panels of  figure \ref{fig:xy}, 
-respectively. In the circular Jupiter case, a gap produced by the 2:1 MMR is visible, while the 3:1 and 5:3 MMR gaps are visible with an 
-eccentric Jupiter. The non-axisymmetric nature of the gaps is due to the fact that planetesimals in the vicinity of the resonances have been 
-excited onto non-circular orbits. Although the spatial distribution of planetesimals near MMR in debris disks may provide clues to detect 
-unseen planets, we will not focus on this topic here, as it has already been covered in detail by other studies \citep{2016ApJ...818..159T, 
-2018ApJ...857....3T}.
-
-The MMRs are most clearly visible when viewing the semimajor axis and eccentricity distribution of the planetesimals. This is shown 
-in figure \ref{fig:ae}. The top panel corresponds to the CJ simulation and the bottom panel corresponds to EJ. The solid vertical lines 
-in this plot represent the nominal locations of the resonances. Near the nominal resonance locations, the a-e distribution of the 
-planetesimals exhibits well-defined spikes which curve slightly inward due to conservation of the Jacobi energy. In the EJ simulation, 
-the eccentricity distribution of bodies near resonance extends below the initial forced value. This is a reflection of the fact that these 
-bodies are undergoing libration, which drives periodic oscillations in both semimajor axis and eccentricity. The coupling between 
-these two quantities is described by equation \ref{eq:tiss}. In the EJ simulation, the eccentricity remains enhanced between the 
-MMRs due to the secular forcing by Jupiter. Because the strength of the resonances scales with the initial eccentricity of the planetesimals, 
-the eccentricity spikes are larger in the EJ simulation. Additionally, the relative size of the 3:1 and 5:3 MMR spikes also grows because the 
-strength of a MMR scales as $e^{k}$, where $k$ is the order of the resonance (citation needed).
-
-The MMRs have one more effect, which is to drive precession of the longitudes of perihelion of planetesimals near 
-resonance. This effect becomes important in the EJ simulation, in which the orbits of bodies are initially aligned with that of Jupiter 
-(see section \ref{sec:sec_force}). As is shown in figure \ref{fig:long_ph}, the strong precession induced by the MMRs overcomes the 
-secular forcing and randomizes the orbital orientations of bodies near the resonances. The dashed horizontal lines in figure 
-\ref{fig:long_ph} indicate the libration width of a planetesimal with an eccentricity of $e_{forced}$ at each resonance, which 
-approximately shows the zone of influence of each MMR. It is important to note that the collision rate predicted by equation
-\ref{eq:safronov} assumes that the orbits of bodies are randomly oriented. Near the interface of the resonances, the N-body collision rate, 
-which we will examine next, is likely not well-described by the Safronov rate.
-
 \subsection{Collision Rates}\label{sec:coll_rates}
 
-As we have already discussed, the Safronov collision rate given by equation \ref{eq:safronov} suffers from two important limitations. The
-first is that the orbits of colliding bodies exhibit no preferred orientation. Second, as we will show below, the velocities of planetesimals 
-near the MMRs follows a bimodal distribution. This makes it difficult to characterize the planetesimals with a single 'typical' encounter 
-velocity and therefore predicting the collision rate using a statistical approach is far from straightforward.
+A prediction of the collision rate using the Safronov equation (eq \ref{eq:safronov}) and the positions and velocities of the planetesimals
+suffers from an important limitation. As we will show below, the velocities of planetesimals near the MMRs does not follow a unimodal 
+distribution. This makes it difficult to characterize the motion of the planetesimals with a single encounter velocity $v_{p}$ and so predicting 
+the collision rate using a statistical approach is far from straightforward. This operation becomes even more complicated with a secularly 
+perturbed disk where there is a transition between aligned and randomly oriented orbits near the interface of the resonances (see figure 
+\ref{fig:long_ph}.
 
 Figure \ref{fig:coll_hist_a} shows the semimajor axis of collisions resolved in the CJ (top) and EJ simulations (bottom). We define 
-'semimajor axis of a collision' as the semimajor axis of the first of the two planetesimals participating in a collision at the 
+the semimajor axis of a collision as the semimajor axis of the first of the two planetesimals participating in a collision at the 
 moment that it happens. To ensure that the definition of the first and second collider chosen by {\sc ChaNGa} does not influence 
-these results, we also tried constructing figure \ref{fig:coll_hist_a} using the second collider and found no qualitative differences. 
-Although both simulations were integrated and collisions were resolved for 5,000 years, we only show collisions that occurred during 
-the last 3,000 years of the simulations. Before this time, the resonant features in the semimajor axis-eccentricity distribution (see 
-figure \ref{fig:ae}) were still developing and had not yet reached a steady state (the libration timescale of the MMRs we are interested in turns out to be about 2,000 years).
-This results in transient features appearing in the collision profiles early on, which we exclude from figure \ref{fig:coll_hist_a} and all subsequent figures.
+these results, we also tried constructing figure \ref{fig:coll_hist_a} using the properties of the second collider and found no qualitative 
+differences. Although both simulations were integrated and collisions were resolved for 5,000 years, we only show collisions that occurred 
+during the last 3,000 years of the simulations. Before this time, the resonant features in the semimajor axis-eccentricity distribution (see 
+figure \ref{fig:ae}) were still developing and had not yet reached a steady state (the libration timescale of the MMRs we are interested in 
+turns out to be about 2,000 years). This results in transient features appearing in the collision profiles early on, which we exclude from 
+figure \ref{fig:coll_hist_a} and all subsequent figures.
 
-We find that the features present in figure \ref{fig:coll_hist_a} are highly sensitive to the choice of binning when constructing a standard histogram and instead model the occurrence of collisions as a function of semimajor axis using a kernel density estimate (KDE).
-We use the {\sc neighbors.KernelDensity} function from the {\sc sklearn} \citep{scikit-learn} package to construct our KDEs.
-For our kernel, we use a tophat function with a bandwidth of 0.01 AU.
+We find that the features present in figure \ref{fig:coll_hist_a} are highly sensitive to the choice of binning when constructing a standard 
+histogram and instead model the occurrence of collisions as a function of semimajor axis using a kernel density estimate (KDE). We use 
+the {\sc neighbors.KernelDensity} function from the {\sc sklearn} \citep{scikit-learn} package to construct our KDEs. For the kernel, we use 
+a tophat function with a bandwidth of 0.01 AU.
 
-Most notably, the MMRs appear to have a measurable effect on the local collision rates. This is in contrast to \citet{2000Icar..143...45R}, 
-who simulated a similar setup and found no discernible features near the MMRs. We attribute the difference to a more careful treatment of 
-timestepping in our simulations. Slightly interior to the 2:1 resonance, the collision rate increases by a factor of roughly 2. In the EJ 
-simulation, there is a significant deficiency in the number of collisions near the 3:1 MMR. We attribute this to the fact that the strength of a 
-second order MMR scales as $e^{2}$, while a first order MMR scales linearly with $e$. One would therefore expect the 3:1 resonance to 
-have more of an influence on the collision rate in a secularly perturbed disk. Although viewing the collision rate as a function of semimajor 
-axis demonstrates a clear connection between the resonances and the collision rate, this does not immediately indicate where the dust 
-generated by collisions will end up in the disk.
+Near some of the MMRs, there are noticeable suppressions or enhancements of the local collision rate. This contrasts with the findings of 
+\citet{2000Icar..143...45R}, who simulated a similar setup and found no discernible features near the MMRs. We attribute the differences to 
+a more careful treatment of timestepping in our simulations. Just interior to the 2:1 resonance, the collision rate is strongly enhanced. In the 
+EJ simulation, there is a significant deficiency in the number of collisions near the 3:1 MMR. This feature, although still present, is much 
+weaker in the CJ simulation. We attribute this to the fact that the strength of a second-order MMR scales as $e^{2}$, while a first order 
+MMR scales with $e$ \citep{1994PhyD...77..289M}. One would therefore expect the 3:1 resonance to have more of an influence on the 
+collision rate in a more eccentric disk. Although viewing the collision rate as a function of semimajor axis demonstrates a clear connection 
+between the resonances and the collision rate, this does not immediately indicate where the dust generated by collisions will end up in the 
+disk. (Why is the feature around the 3:1 MMR so different than the 2:1?)
+
+\subsection{Where Does the Dust End Up?}
 
@@
 
-Operating under this assumption, a map of the relative concentration of second-generation dust can be constructed from the cylindrical distance at which the collisions occur.
-This is shown in the top panels of figure \ref{fig:coll_hist_r}, where the left side corresponds to the CJ simulation and the right side corresponds to EJ.
-As in figure \ref{fig:coll_hist_a}, a kernel density estimate of the number of collisions is constructed using a tophat kernel with a bandwidth of 0.01 AU.
-Features again appear near the 2:1 and 3:1 MMRs in both simulations, although the shape of the features are qualitatively different from figure \ref{fig:coll_hist_a}.
-Near the 2:1 resonance, the radial collision rate is noticably suppressed.
-This is mainly due to the reduced surface density of planetesimals near the center of the resonance, shown in the second row of figure \ref{fig:coll_hist_r}.
-The surface density in the EJ simulation near this resonance is less suppressed than the CJ simulation due to the enhanced eccentricity of planetesimals in the vicinity.
-This also has the effect of washing out the feature created in the collision rate profile due to the 2:1 MMR.
+Operating under this assumption, a map of the relative concentration of second-generation dust can be constructed from the cylindrical 
+distance at which the collisions occur. This is shown in the top panels of figure \ref{fig:coll_hist_r}, where the left side corresponds to the CJ 
+simulation and the right side corresponds to EJ. As in figure \ref{fig:coll_hist_a}, a KDE of the collision rate is constructed using a tophat 
+kernel with a bandwidth of 0.01 AU.
 
-Additionally, a sharp, well-defined feature appears just exterior to the 3:1 MMR in the EJ simulation.
-A corresponding dip in the surface density at this same location suggests that the variation in the collision rate here is due to a lack of planetesimals in this location.
-Upon closer inspection, we find that the center of this feature lies at a a radial distance of $(1+e_{forced})a_{3:1}$, where $a_{3:1}$ is the nominal location of the 3:1 MMR and $e_{forced}$ is the forced eccentricity of a planetesimal at $a_{3:1}$.
-This distance corresponds to the aphelion distance of a planetesimal with these orbital parameters.
-Physically, the drop in the surface density here can be explained as follows: bodies near the 3:1 MMR experience strong precession, which randomizes their orbits and undergo libration which produces a large spread in their relative velocities.
-For a collection of randomly oriented eccentric orbits, there is less geometric overlap at aphelion, which lowers the surface density at this distance.
-Given the clear connection between the offset of this feature and the local forced eccentricity, we will examine the feasibility of using this feature to measure the eccentricity of the perturbing planet in section \ref{sec:dust} after we construct a dust emission map from the collision rate profile.
+In contrast to what was seen in figure \ref{fig:coll_hist_a}, the radial collision rate is now suppressed near the 2:1 MMR. The spike in the 
+collision rate at semimajor axes interior to this location becomes washed out when viewed instead by cylindrical distance because the 
+spread in the eccentricities of the colliding planetesimals is so large. Although many of the collisions happen at the same semimajor axis, 
+they occur at very different distances from the central star. The second row of figure \ref{fig:coll_hist_r} shows the azimuthally averaged 
+surface density of the planetesimal disk at the end of the simulations. These profiles were calculated using the {\sc PYNBODY} analysis 
+package \citep{2013ascl.soft05002P}.
 
-The bottom row of figure \ref{fig:coll_hist_r} demonstrates the difficulty with calculating the collision rate from the position and velocity distribution of particles.
-Typically, the rms velocity is defined as $\sqrt(\left<e^2\right> + \left<i^2\right>)$.
-In this case, the wings extending off of the resonances in the distance-eccentricity distribution makes the eccentricity dispersion distinctly bimodal and not well defined at nearly all radial distances.
-A naive calculation of the Safronov rate here would predict a collision rate near the resonances that is smaller than the actual value.
+In both the CJ and EJ simulations, the local minima in the surface density profiles match well with the minima in the collision rates. 
+Additionally, the minima in the EJ simulation are offset from the centers of the resonances. This can be explained as follows: for 
+planetesimals affected by the MMRs, the typical encounter velocity is large and gravitational focusing is suppressed. Here, the collision 
+cross section is geometric. In this limit, the collision probability scales with the ratio between the geometric cross section of the 
+planetesimals and the surface area of a sphere with radius $r$, where $r$ is the distance between the bodies and the central star. This 
+ratio, and therefore the collision probability, is largest when $r$ is minimized (see \citet{2003AJ....125.2692L}). Therefore, the collision 
+probability for planetesimals affected by resonance is smallest at aphelion. This is also consistent with the reduced surface density exterior 
+to the resonances.
+
+Finally, the bottom row of figure \ref{fig:coll_hist_r} demonstrates the difficulty with calculating the collision rate from the position and velocity 
+distribution of particles. At a given distance from the central star, the distribution of velocities (using eccentricity as a proxy for typical encounter 
+velocity), is not unimodal. In addition, the wings extending off of the resonances in these plots show that planetesimals can interact and collide 
+with bodies far from the centers of the resonances. The bump seen in the collision rate in the EJ simulation around 2.7 AU is like a result of the 
+complicated interaction between planetesimals in the 3:1, 5:2 and 2:1 resonances.
+
+So far, we have shown that mean-motion resonances with a perturbing giant planet will produce measureable radial variations in the collision rates across a disk of planetesimals, which should give rise to variations in the dust profile.
+In addition, distinctly different features are produced if the giant planet is on an eccentric, rather than a circular orbit.
+In the next section, we would like to determine whether these features can be used to place any constraints on the mass and eccentricity of the planet.
 
@@
 
-%Next, we move on to examine the statistics of the collisions that occur.
-Figure \ref{fig:coll_hist_a} shows the distribution of semimajor axes of every collision that is resolved.
-Here, the semimajor axis of a collision is defined as the semimajor axis of the first body participating in the collision at the moment that it occurs.
-During a collision, the determination of which body is first and which is second is determined by the collision search tree in {\sc ChaNGa}.
-To ensure that this does not introduce any bias, we also constructed figure \ref{fig:coll_hist_a} using the orbital parameters of the second body and found no qualitative difference.
-By examining the semimajor axis distribution of the collisions, it is easy to see how the MMRs affect the collision rates.
-The dashed lines again represent the libration width of each resonance and are meant to show its range of influence.
-In both the circular and eccentric Jupiter simulations, the collision rate is clearly enhanced interior to the 2:1 MMR.
-The 3:1 MMR only appears to have a noticeable influence on the collision rate in the EJ simulation.
-In both cases, although the 5:3 MMR has a clear influence on the on the semimajor-axis eccentricity distribution, it does not leave a measureable imprint on the collision rate.
-It is important to point out, however, that the libration width of sufficiently eccentric particles near the 5:3 MMR may extend beyond the outer edge of the disk and introduce boundary effects.
+\section{Influence of Jupiter's Mass and Eccentricity on the Radial Dust Profile}
 
-%Although the semimajor axis of a particle at the moment of collision provides useful information about how the mean motion resonances affect the collision rate in the disk, this information alone is not enough to predict where the second generation dust that is produced will end up.
-To do so, we will operate under the assumption that dust grains produced by collision events will quickly couple to the gas and attain a circular orbit.
-This assumption, which will be further justified in section \ref{sec:dust}, allows to map the radial variation in the dust surface density to the radial position of the collisions.
-This is shown in figure \ref{fig:coll_hist_r}, where the histograms indicate the x and y coordinates of a body at the moment that it undergoes a collision.
+\section{Observability of Dust} \label{sec:dust}
 
-%Explanation of offset of feature near 3:1 in EJ: orbital orientations randomized near MMR, most bodies have ecc of e_forced, even in resonance.
-Geometrically, less overlap at apo, so surface density drops and so does coll rate.
-Most notably, the prominent features visible in figure \ref{fig:coll_hist_a} adjacent to the 2:1 MMR no longer appear. This is due to the 
-fact that the orbits of bodies in the 2:1 MMR have a wide range of eccentricities and therefore have the potential to undergo 
-collisions at a wide range of heliocentric distances. In the CJ simulation, there is a prominent dip in the collision rate near the 2:1 
-MMR. This feature is still moderately visible in the EJ simulation, but the dip is much wider and shallower. The random orientations of 
-the orbits inside of the resonance (see figure \ref{fig:long_ph}), combined with the forced eccentricites of planetesimals adjacent to 
-the resonance weakens the dip near the 2:1 MMR seen in the left hand panel of figure \ref{fig:coll_hist_a}. Additionally, there is a 
-double-pronged feature in the collision rate near the 3:1 MMR in the EJ simulation. The radial distance of these two prongs 
-corresponds to the maximum radial excursion that a planetesimal at the 3:1 MMR with an eccentricity set by secular forcing with 
-Jupiter undergoes. (Need more explanation of why this happens)
-
-As is seen in figure \ref{fig:long_ph}, the relatively fast precession rates induced by the mean motion resonances overpower the 
-secular forcing by Jupiter and randomize the orientation of orbits near the nominal resonance locations. Of course, this difference in 
-longitude of perihelion of bodies inside and outside of resonance is only present in the EJ simulation because the Jupiter imposes 
-zero forced eccentricity on the disk when it has a circular orbit. Figure \ref{fig:m_hist} provides another view of the difference in 
-collision statistics inside and outside and of resonance. This shows the mean anomalies of bodies at the moment that they undergo a 
-collision. The top row corresponds to the EJ simulation and the bottom rom corresponds to the CJ simulation. The left panels 
-correspond to collisions that occur inside of the 2:1 MMR and the right panels are for collisions that occur with a semimajor axis 
-between 2.7 and 2.8 AU, which is meant to well away from the influence of any resonances. The semimajor axis window size in the 
-right hand panel is chosen so that both histograms contain the same total number of collisions.
-
-The qualitative differences between these four panels can be explained in the following way: for $\approx$ 100 km bodies, 
-gravitational focusing plays a significant role in setting the collision rate. In regions of the disk where the rms eccentricity is small 
-(which corresponds to a small velocity dispersion), the collision rate should be enhanced (see equation \ref{eq:safronov}). Inside of 
-resonances, planetesimals undergo large amplitude libration which pumps up the eccentricity dispersion. This effect is visible in 
-figure \ref{fig:ae} for both the EJ and CJ simulation. This implies that the collision rate should be geometric, and not depend on the 
-velocity dispersion near resonances. When this is true, collisions should preferentially occur near perihelion. The reason for this is 
-that in the geometric limit, the collision probability scales with the ratio between the geometric cross section of the two planetesimals 
-and the surface area of a sphere with radius $r$, where $r$ is the distance between the bodies and the central star. This ratio, and 
-therefore the collision probability, is largest when $r$ is minimized (see \citet{2003AJ....125.2692L}). The fact both of the left-hand 
-panels in figure \ref{fig:m_hist} show a distinct lack of collisions near aphelion is consistent with this explanation.
-
-Note that this trend is not present in the right-hand panels of figure \ref{fig:m_hist}.
-In the case with Jupiter on a circular orbit (bottom right panel), there is a spike in the collision rate both at perihelion and aphelion.
-The perihelion spike is still due to the geometric argument presented in the previous paragraph.
-The aphelion spike is due to the effect of gravitational focusing.
-At aphelion, bodies achieve their minimum speed.
-This lowers the relative velocity between planetesimals, which according to equation \ref{eq:safronov} should enhance the collision rate.
-Note that the collision rate does not exhibit much dependence on mean anomaly outside of resonance in the case with Jupiter on an eccentric orbit (top right panel).
-This is due to the secular forcing by Jupiter, which aligns the longitude of perihelia of adjacent planetesimals.
-The result of this is that bodies maintain similar relative speeds over the course of an orbit, even though the orbit is eccentric.
-This lack of variation in the relative speeds makes collisions equally likely at any orbital phase.
-
-Motivate the assumption that dust produced in collisions immediately goes onto circular orbit
-
-Discuss figure 5, hilight differences between surface density distribution and collision histogram.
-Calculation of safronov rate is hard because velocity distribution is bimodal in many places.
-Key features to point out: 2:1 MMR shows up well in CJ.
-Much more washed out in EJ, while 3:1 becomes more prominent.
-Also both features in EJ are shifted to the right of resonance location by a factor of (1+$e_{forced}$.
-This could be a viable way to measure ecc of the perturber.
-
-\section{Observability of Collisions} \label{sec:dust}
-
-Have aaron make a CASA dust emission map for the two histograms in figure 5.
-Fit a gaussian to the radial features and see if we can back out the eccentricity of the perturber and its mass.
-Also make 2d histogram showing how the perturbers eccentricity (which sets the forced eccentricity) and mass sets the libration width.
-
-\section{Measuring Properties of the Perturber} \label{sec:fitting}
+Aaron's CASA images go here
 

### 2020-04-13 makeFig.py

@@ -147,12 +147,14 @@ def make_xy():
 	ax1.scatter(x_c_rot[0], y_c_rot[0], color='r')
 	ax1.set_xlabel('X [AU]')
 	ax1.set_ylabel('Y [AU]')
+	ax1.set_title('Circular Jupiter')
 	ax1.set_xlim(-5.5, 5.5)
 	ax1.set_ylim(-5.5, 5.5)
 	ax2.scatter(x_e_rot, y_e_rot, s=s)
 	ax2.scatter(x_e_rot[0], y_e_rot[0], color='r')
 	ax2.set_xlabel('X [AU]')
 	ax2.set_ylabel('Y [AU]')
+	ax2.set_title('Eccentric Jupiter')
 	plt.savefig(file_str, format=fmt, bbox_inches='tight')
 
 	plt.savefig(file_str, format=fmt, bbox_inches='tight')
@@ -180,18 +182,20 @@ def make_ae():
 
 	# Libration width varies with eccentricity so it doesn't make much sense
 	# to do show_widths=True here
-	fig, (ax1, ax2) = plt.subplots(figsize=(8,8), nrows=2, ncols=1, sharex=True)
+	fig, (ax1, ax2) = plt.subplots(figsize=(8,8), nrows=2, ncols=1, sharex=True, sharey=True)
 	ax1.scatter(pl_c['a'], pl_c['e'], s=s)
 	plot_res(ax1, show_widths=False)
 	ax1.set_ylabel('Eccentricity')
+	ax1.set_title('Circular Jupiter')
 	ax2.scatter(pl_e['a'], pl_e['e'], s=s)
 	plot_res(ax2, show_widths=False)
 	ax2.set_xlim(2, 4)
 	ax2.set_xlabel('Semimajor Axis [AU]')
 	ax2.set_ylabel('Eccentricity')
+	ax2.set_title('Eccentric Jupiter')
 	# sharey=true hides the tick labels
 	ax2.yaxis.set_tick_params(labelleft=True)
-	plt.tight_layout(h_pad=0)
+	#plt.tight_layout(h_pad=0)
 	plt.savefig(file_str, format=fmt, bbox_inches='tight')
 
 def make_long_ph():
@@ -219,13 +223,15 @@ def make_coll_hist_a():
 	ax1.plot(coll_bins_a_c, coll_pdf_a_c, linestyle='steps-mid')
[…]

### 2020-04-15 main.tex
Add figure captions, add new figure showing change in collision rate with ejup and mjup

@@
 \section{Introduction} \label{sec:intro}
-
-%Things to change/do:
-%    Transient feature in EJ collision rate before 2000 years.
-Only want to look at collisions after this time.
-Mention this when discussing figure 4.
-Justify the cutoff (maybe something to do with precession in 3:1 MMR?)
-%    Safronov and Nbody collision rates. Not matching up well near resonance. The 'wings' from the resonances mess up calculation of velocity dispersion. Maybe do comparison
-%       no grav focusing?
-%    Get Aaron to make some dust emission makes from the Nbody collision histograms
-%    Can we scale these results to any size system? Get rid of units. How to justify planetesimal size?
 
@@
     \includegraphics[width=\textwidth]{figures/xy.png}
-    \caption{Caption goes here.\label{fig:xy}}
+    \caption{The positions of remaining planetesimals at the end of the CJ (left) and EJ (right) simulations. Jupiter's position is
+    indicated by a red dot. Nonaxisymmetric features due to mean motion resonances are clearly visible in both cases. Higher
+    order resonances are visible in the EJ case.\label{fig:xy}}
 \end{figure*}
@@
     \includegraphics[width=0.4\columnwidth]{figures/ae.png}
-    \caption{Caption goes here.\label{fig:ae}}
+    \caption{The semimajor axis - eccentricity state of the remaining planetesimals are shown at the end of the CJ (top) and EJ (bottom) 
+    simulations. The vertical bars mark the nominal locations of prominent resonances. Planetesimals affected by resonance with Jupiter gain
+     eccentricity, and due to conservation of the Jacobi energy, reduce their semimajor axes. This produces the curved fingerlike structure 
+     extending off of the resonances. In the EJ case, some bodies in resonance take on eccentricities smaller than their initial forced values as 
+     they undergo libration.\label{fig:ae}}
     \end{center}
@@
     \includegraphics[width=0.4\columnwidth]{figures/long_ph.png}
-    \caption{Caption goes here.\label{fig:long_ph}}
+    \caption{The semimajor axis and pericenter orientation of remaining planetesimals at the end of the EJ simulation. All bodies start with their 
+    pericenters closely aligned with Jupiter's ($\varpi = \pi$). Near the resonances, bodies undergo strong precession which randomizes their 
+    orbital orientations. Two-body interactions between the planetesimals in resonance and nearby non-resonant planetesimals drags their 
+    longitude of perihelia along with.\label{fig:long_ph}}
     \end{center}
@@
     \includegraphics[width=0.4\columnwidth]{figures/coll_hist_a.png}
-    \caption{Caption goes here.\label{fig:coll_hist_a}}
+    \caption{A kernel density estimate (KDE) of the collision rate as a function of semimajor axis in the CJ (top) and EJ (bottom) simulations. 
+    There are measureable changes in the collision rate near 2:1 and 3:1 MMRs, each of which produce qualitatively different changes in the 
+    collision rate. The vertical bars mark the nominal locations of prominent resonances.\label{fig:coll_hist_a}}
     \end{center}
@@
 disk. (Why is the feature around the 3:1 MMR so different than the 2:1?)
+
+\begin{figure*}
+    \includegraphics[width=\textwidth]{figures/coll_hist_r.png}
+    \caption{\textit{Top:} A KDE of the collision rate in the CJ (left) and EJ (right) simulations as a function of cylindrical distance from the central 
+    star. Vertical lines mark the nominal locations of the MMRs. Variations in the collision rate are visible near the MMRs, but are distinctly 
+    different than the feature that appeared in figure \ref{fig:coll_hist_a}. \textit{Middle:} The azimuthally-averaged surface density of remaining 
+    planetesimals. \textit{Bottom:} The cylindrical distance and eccentricities of remaining planetesimals. The cones extending upward from the 
+    resonance locations are due to the fact that eccentric planetesimals explore a wide range of physical space over the course of an orbit.\label{fig:coll_hist_r}}
+\end{figure*}
 
@@
 Finally, the bottom row of figure \ref{fig:coll_hist_r} demonstrates the difficulty with calculating the collision rate from the position and velocity 
-distribution of particles. At a given distance from the central star, the distribution of velocities (using eccentricity as a proxy for typical encounter 
+distribution of particles. At a given distance from the central star, the distribution of velocities (using eccentricity as a proxy for encounter 
 velocity), is not unimodal. In addition, the wings extending off of the resonances in these plots show that planetesimals can interact and collide 
-with bodies far from the centers of the resonances. The bump seen in the collision rate in the EJ simulation around 2.7 AU is like a result of the 
-complicated interaction between planetesimals in the 3:1, 5:2 and 2:1 resonances.
+with bodies far from the centers of the resonances.
+The bump seen in the collision rate in the EJ simulation around 2.7 AU is like a result of interaction between planetesimals in the 3:1, 5:2 and 2:1 resonances.
 
@@
 
+\section{Influence of Jupiter's Mass and Eccentricity on the Radial Dust Profile}
+
 \begin{figure*}
-    \includegraphics[width=\textwidth]{figures/coll_hist_r.png}
-    \caption{Caption goes here.\label{fig:coll_hist_r}}
+    \includegraphics[width=0.4\textwidth]{figures/coll_hist_e_and_m.png}
+    \caption{Caption goes here.\label{fig:coll_hist_e_and_m}}
 \end{figure*}
-
-\section{Influence of Jupiter's Mass and Eccentricity on the Radial Dust Profile}
 

### 2020-04-15 makeFig.py

@@ -100,13 +100,13 @@ nbins = 30
 # Regenerate existing plots?
 clobber = True
 fmt = 'png'
-s = 0.005
+s = 0.0001
 
 # Collision log data
 
 # Circular Jupiter case
-mc_c = s0_c['mass'][0]
-coll_c_log = coll.CollisionLog(path + 'hkshiftfullJupCirc/collisions', mc_c)
+mc = s0_c['mass'][0]
+coll_c_log = coll.CollisionLog(path + 'hkshiftfullJupCirc/collisions', mc)
 coll_c = coll_c_log.coll
 # The v2y output in the collision log is messed up. Fortunately, we can recover it from
 # v1y and vNewy
@@ -115,11 +115,41 @@ coll_c = coll_c[np.logical_and(coll_c['time']/(2*np.pi) <= t_max, coll_c['time']
 
 # Eccentric Jupiter case
 mc_e = s0_e['mass'][0]
-coll_e_log = coll.CollisionLog(path + 'hkshiftfull/collisions', mc_e)
+coll_e_log = coll.CollisionLog(path + 'hkshiftfull/collisions', mc)
 coll_e = coll_e_log.coll
 # Fix the v2y output again
 coll_e['v2y'] = (coll_e['m1']*coll_e['v1y'] - (coll_e['m1'] + coll_e['m2'])*coll_e['vNewy'])/coll_e['m2']
 coll_e = coll_e[np.logical_and(coll_e['time']/(2*np.pi) <= t_max, coll_e['time']/(2*np.pi) >= t_skip)]
+
+# Low eccentricity Jupiter
+mc_e = s0_e['mass'][0]
+coll_e1_log = coll.CollisionLog(path + 'e1/collisions', mc)
+coll_e1 = coll_e1_log.coll
+# Fix the v2y output again
+coll_e1['v2y'] = (coll_e1['m1']*coll_e1['v1y'] - (coll_e1['m1'] + coll_e1['m2'])*coll_e1['vNewy'])/coll_e1['m2']
+
+# High eccentricity Jupiter
+mc_e = s0_e['mass'][0]
+coll_e2_log = coll.CollisionLog(path + 'e2/collisions', mc)
+coll_e2 = coll_e2_log.coll
[…]

### 2020-04-15 makeFig.py
Add additional semimajor axis panels to fig 6

@@ -315,7 +315,13 @@ def make_coll_hist_e_and_m():
 	if not clobber and os.path.exists(file_str):
 		return
 
-	fig, (ax1, ax2) = plt.subplots(figsize=(8,8), nrows=2, ncols=1, sharex=True, sharey=True)
+	fig, ax = plt.subplots(figsize=(16,12), nrows=2, ncols=2, sharex=True, sharey=True)
+
+	coll_bins_a_e1, coll_pdf_a_e1 = kde(coll_e1['a1'])
+	coll_bins_a_e, coll_pdf_a_e = kde(coll_e['a1'])
+	coll_bins_a_e2, coll_pdf_a_e2 = kde(coll_e2['a1'])
+	coll_bins_a_m1, coll_pdf_a_m1 = kde(coll_m1['a1'])
+	coll_bins_a_m2, coll_pdf_a_m2 = kde(coll_m2['a1'])
 
 	coll_dist_e1 = np.sqrt(coll_e1['x1x']**2 + coll_e1['x1y']**2)
 	coll_bins_r_e1, coll_pdf_r_e1 = kde(coll_dist_e1)
@@ -328,26 +334,36 @@ def make_coll_hist_e_and_m():
 	coll_dist_m2 = np.sqrt(coll_m2['x1x']**2 + coll_m2['x1y']**2)
 	coll_bins_r_m2, coll_pdf_r_m2 = kde(coll_dist_m2)
 
-	ax1.plot(coll_bins_r_e1, coll_pdf_r_e1, label=r'e$_{pl}$ = 1/2 e$_{jup}$', linestyle='steps-mid')
-	ax1.plot(coll_bins_r_e, coll_pdf_r_e, label=r'e$_{pl}$ = e$_{jup}$', linestyle='steps-mid')
-	ax1.plot(coll_bins_r_e2, coll_pdf_r_e2, label=r'e$_{pl}$ = 2 e$_{jup}$', linestyle='steps-mid')
+	ax[0][0].plot(coll_bins_a_e1, coll_pdf_a_e1, label=r'e$_{pl}$ = 1/2 e$_{jup}$', linestyle='steps-mid')
+	ax[0][0].plot(coll_bins_a_e, coll_pdf_a_e, label=r'e$_{pl}$ = e$_{jup}$', linestyle='steps-mid')
[…]

### 2020-04-15 main.tex
Add additional semimajor axis panels to fig 6
Add libration width and surface density figure

@@
 \begin{figure*}
-    \includegraphics[width=0.4\textwidth]{figures/coll_hist_e_and_m.png}
+    \includegraphics[width=\textwidth]{figures/coll_hist_e_and_m.png}
     \caption{Caption goes here.\label{fig:coll_hist_e_and_m}}
+\end{figure*}
+
+\begin{figure*}
+    \begin{center}
+    \includegraphics[width=0.4\textwidth]{figures/e_and_m_surf_den.png}
+    \caption{Caption goes here.\label{fig:e_and_m_surf_den}}
+    \end{center}
+\end{figure*}
+
+\begin{figure*}
+    \includegraphics[width=\textwidth]{figures/lib_width.png}
+    \caption{Caption goes here.\label{fig:lib_width}}
 \end{figure*}

### 2020-04-15 makeFig.py

@@ -32,6 +32,11 @@ res_label = ['3:1', '2:1', '5:3']
 res_p = [1, 1, 3]
 res_q = [2, 1, 2]
 
+mc = 1
+m_jup = 9.54e-4
+a_jup = 5.2
+ecc_jup = 0.048
+
 # Build a PDF from a series of data points using a KDE
 from sklearn.neighbors import KernelDensity
 def kde(qty, bw=0.01):
@@ -48,18 +53,18 @@ def kde(qty, bw=0.01):
     
     return 10.**bins, pdf
 
+def e_forced(a, ecc_jup):
+	return ko.lap(2, 3/2, a/a_jup)/ko.lap(1, 3/2, a/a_jup)*ecc_jup
+
 # Width of a resonance with jupiter (in AU)
 # Assume body has an eccentricity of e_forced
-def res_width_jup(p, q):
-    m, m_c = 9.54e-4, 1
-    a_jup = 5.2
-    ecc_jup = 0.048
+def res_width_jup(p, q, ecc_jup=ecc_jup, m_jup=m_jup):
     j1 = p + q
     j2 = -p
     alpha = (-j2/j1)**(2./3.)
-    ecc = ko.lap(2, 3/2, alpha)/ko.lap(1, 3/2, alpha)*ecc_jup
     dist = alpha*a_jup
-    rw = ko.res_width(m, m_c, ecc, j1, j2)*dist
+    ecc = e_forced(dist, ecc_jup)
+    rw = ko.res_width(m_jup, mc, ecc, j1, j2)*dist
     return rw
 
 def plot_res(axis, res=-1, vertical=True, show_widths=False):
@@ -88,6 +93,26 @@ s0_c = pb.load(s_c_files[0])
 s_e_files = np.array([path + 'hkshiftfull/hkshiftfull.ic']+ \
 	                  ns.natsorted(gl.glob(path + 'hkshiftfull/*.[0-9]*[0-9]')))
 s0_e = pb.load(s_e_files[0])
+s_c, s_e = pb.load(s_c_files[-1]), pb.load(s_e_files[-1])
+pl_c, pl_e = ko.orb_params(s_c), ko.orb_params(s_e)
+
+s_m1_files = np.array([path + 'm1/m1.ic']+ \
+	                  ns.natsorted(gl.glob(path + 'm1/m1_coll.[0-9]*[0-9]')))
+s0_m1 = pb.load(s_m1_files[0])
[…]

### 2020-04-15 main.tex
Dont build plots when compiling LaTeX, update abstract

@@
 \begin{abstract}
-A perturbing planet can leave a lasting imprint a debris disk near the locations of mean motion resonances (MMRs). Unfortunately,
-the planetesimal-sized objects that make up the majority of these disks are extremely difficult to directly observe. Dust created from
-collisions between planetesimals may be a much better way to constrain the structure of these disks. We use a direct N-body model
-to measure planetesimal collision rates in a dynamically cold debris disk composed of 150 km bodies. Even though the eccentricities
-are pumped at the nominal resonance locations, conservation of the Jacobi energy pushes planetesimals inward and enhances the
-collision rate adjacent to the resonances. In addition, we find that the collision rate is severely throttled near the 3:1 MMR and that a
-tightly wound spiral wave is launched from this location.
+In circumstellar disks, collisional grinding of planetesimals produces second-generation dust, which can be observed through thermal 
+emission. While it remains unclear when second-generation dust first becomes a major component of the total dust content, the presence of 
+such dust and potentially the substructure within it can be used to explore a disk's physical conditions. A perturbing planet has been shown to 
+produce nonaxisymmetric structures, as well as gaps in disks, regardless of the origin of the dust. However, small grains will have very 
+different dynamics compared with planetesimals when in the presence of gas, and as such, the collisional evolution of planetesimals could 
+create dusty disk structures that would not exist otherwise. In particular, mean motion resonances (MMRs) are extremely nonlinear and could 
+drive disk morphologies. We use a direct N-body model to track collision rates in a planetesimal disk under the gravitational influence of an 
+external Jupiter-sized planet. We show that a perturbing planet can produce significant variations in the collision rate of planetesimals near the 
+MMRs and we explore how the mass and eccentricity of the perturbing planet alters this structure. Finally, we use the CASA image simulator to 
+predict what the dust emission sturcture should look like with ALMA and the NG-VLA. Although the dust structure produced by MMRs cannot 
+be used to directly measure the properties of the perturbing planet, we show that it can be used to place constraints on its mass and 
+eccentricity.
 \end{abstract}
@@
 velocity), is not unimodal. In addition, the wings extending off of the resonances in these plots show that planetesimals can interact and collide 
-with bodies far from the centers of the resonances.
-The bump seen in the collision rate in the EJ simulation around 2.7 AU is like a result of interaction between planetesimals in the 3:1, 5:2 and 2:1 resonances.
+with bodies far from the centers of the resonances. The bump seen in the collision rate in the EJ simulation around 2.7 AU is like a result of 
+interaction between planetesimals in the 3:1, 5:2 and 2:1 resonances.
 
-So far, we have shown that mean-motion resonances with a perturbing giant planet will produce measureable radial variations in the collision rates across a disk of planetesimals, which should give rise to variations in the dust profile.
-In addition, distinctly different features are produced if the giant planet is on an eccentric, rather than a circular orbit.
-In the next section, we would like to determine whether these features can be used to place any constraints on the mass and eccentricity of the planet.
+So far, we have shown that mean-motion resonances with a perturbing giant planet will produce measureable radial variations in the collision 
+rates across a disk of planetesimals, which should give rise to variations in the dust profile. In addition, distinctly different features are 
+produced if the giant planet is on an eccentric, rather than a circular orbit. In the next section, we would like to determine whether these 
+features can be used to place any constraints on the mass and eccentricity of the planet.
 

### 2020-04-22 main.tex
Add figures explaining bumps and dips in a and r collision distributions

@@
     \begin{center}
-    \includegraphics[width=0.4\textwidth]{figures/e_and_m_surf_den.png}
-    \caption{Caption goes here.\label{fig:e_and_m_surf_den}}
+    \includegraphics[width=\textwidth]{figures/coll_hist_hot_cold_a.png}
+    \caption{Caption goes here.\label{fig:coll_hist_hot_cold_a}}
     \end{center}
@@
 \begin{figure*}
-    \includegraphics[width=\textwidth]{figures/lib_width.png}
-    \caption{Caption goes here.\label{fig:lib_width}}
+    \begin{center}
+    \includegraphics[width=0.4\textwidth]{figures/coll_gf_vary.png}
+    \caption{Caption goes here.\label{fig:coll_gf_varg}}
+    \end{center}
+\end{figure*}
+
+\begin{figure*}
+    \begin{center}
+    \includegraphics[width=\textwidth]{figures/coll_hist_r_inout_res.png}
+    \caption{Caption goes here.\label{fig:coll_hist_r_inout_res}}
+    \end{center}
+\end{figure*}
+
+\begin{figure*}
+    \begin{center}
+    \includegraphics[width=\textwidth]{figures/wander_res_scale.png}
+    \caption{Caption goes here.\label{fig:wander_res_scale}}
+    \end{center}
 \end{figure*}

### 2020-04-22 makeFig.py

@@ -39,8 +39,8 @@ ecc_jup = 0.048
 
 # Build a PDF from a series of data points using a KDE
 from sklearn.neighbors import KernelDensity
-def kde(qty, bw=0.01):
-    bins = np.linspace(np.log10(np.min(qty)), np.log10(np.max(qty)))
+def kde(qty, bw=0.1):
+    bins = np.linspace(np.min(qty), np.max(qty))
     
     def kde_helper(x, x_grid, **kwargs):
         kde_skl = KernelDensity(kernel='tophat', bandwidth=bw, **kwargs)
@@ -48,10 +48,9 @@ def kde(qty, bw=0.01):
         log_pdf = kde_skl.score_samples(x_grid[:, np.newaxis])
         return np.exp(log_pdf)
     
-    pdf = kde_helper(np.log10(qty), bins)
-    cum_df = np.cumsum(pdf[::-1])[::-1]
+    pdf = kde_helper(qty, bins)
     
-    return 10.**bins, pdf
+    return bins, pdf
 
 def e_forced(a, ecc_jup):
 	return ko.lap(2, 3/2, a/a_jup)/ko.lap(1, 3/2, a/a_jup)*ecc_jup
@@ -59,13 +58,13 @@ def e_forced(a, ecc_jup):
 # Width of a resonance with jupiter (in AU)
 # Assume body has an eccentricity of e_forced
 def res_width_jup(p, q, ecc_jup=ecc_jup, m_jup=m_jup):
-    j1 = p + q
-    j2 = -p
-    alpha = (-j2/j1)**(2./3.)
-    dist = alpha*a_jup
-    ecc = e_forced(dist, ecc_jup)
-    rw = ko.res_width(m_jup, mc, ecc, j1, j2)*dist
-    return rw
+	j1 = p + q
+	j2 = -p
+	alpha = (-j2/j1)**(2./3.)
+	ecc = ko.lap(2, 3/2, alpha)/ko.lap(1, 3/2, alpha)*ecc_jup
+	dist = alpha*a_jup
+	rw = ko.res_width(m_jup, mc, ecc, j1, j2)*dist
+	return rw
 
 def plot_res(axis, res=-1, vertical=True, show_widths=False):
 	xmin, xmax = axis.get_xlim()
[…]

### 2020-04-22 main.tex
Clean up normalization of PDFs in later figures, add more captions

@@
     \includegraphics[width=\textwidth]{figures/coll_hist_e_and_m.png}
-    \caption{Caption goes here.\label{fig:coll_hist_e_and_m}}
+    \caption{\textit{Top}: KDE of the number of collisions at each semimajor axis (left) and heliocentric distance (right) as the eccentricity of of the perturbing planet is varied.
+\textit{Bottom}:  Same as top row, except the perturber's eccentricity is set to $e_{jup}$ and the mass is now varied.
+In all plots, the PDF is normalized to the ($e_{jup}, m_{jup}$) case.
+Characteristic bumps or dips appear near the 2:1 and 3:1 MMRs, the presence of which depends on the mass and eccentricity of the perturber.
+\label{fig:coll_hist_e_and_m}}
 \end{figure*}
@@
     \includegraphics[width=\textwidth]{figures/coll_hist_hot_cold_a.png}
-    \caption{Caption goes here.\label{fig:coll_hist_hot_cold_a}}
+    \caption{KDE of the number of collisions at each semimajor axis for the lowest eccentricity case (left) and highest eccentricity case (right).
+To elucidate why a bump forms at the 2:1 while a dip forms at the 3:1 MMR, we split the resolved collisions into hot and cold categories.
+A bump is produced when the hot collision rate increases, while a dip is produced when the cold collision rate decreases.\label{fig:coll_hist_hot_cold_a}}
     \end{center}
@@
     \includegraphics[width=0.4\textwidth]{figures/coll_gf_vary.png}
-    \caption{Caption goes here.\label{fig:coll_gf_varg}}
+    \caption{The collision rate of a population of 300 km planetesimals as a function of the rms eccentricity in the vicinity of the 3:1 and 2:1 MMRs, relative to the value at $\left< e^{1/2} \right>^{2}$ = $10^{-3}$.
+The resonances will act to dynamically heat the local planetesimal population.
+The local minimum corresponds to the rms eccentricity at which the typical planetesimal encounter velocity is $v_{esc}$.
+If the planetesimals are heated by a small amount, gravitational focusing is suppressed and the collision rate decreases.
+Stronger dynamical heating will increase the encounter rate enough to overcome the lack of gravitational focusing.\label{fig:coll_gf_varg}}
     \end{center}
@@
     \includegraphics[width=\textwidth]{figures/coll_hist_r_inout_res.png}
-    \caption{Caption goes here.\label{fig:coll_hist_r_inout_res}}
+    \caption{KDE of the number of collisions at a given heliocentric distance for planetesimals inside (left) and outside (right) of the 2:1 MMR.
+In the $e_{pl} = 2 e_{jup}$ case, a bump, rather than a dip appears near the 2:1 MMR (see figure \ref{fig:coll_hist_e_and_m}).
+This bump is produced by non-resonant planetesimals undergoing collisions near the center of the 2:1 MMR.\label{fig:coll_hist_r_inout_res}}
     \end{center}
@@
     \includegraphics[width=\textwidth]{figures/wander_res_scale.png}
-    \caption{Caption goes here.\label{fig:wander_res_scale}}
+    \caption{The radial excursion distance of a planetesimal $\delta r_{ex}$ =  ($a_{pl} (1 + e_{f}$) (solid lines) near the resonance and full libration width $\delta r_{res}$ (dashed lines) of that resonance for the 3:1 (left) and 2:1 (right) MMR.
+For the 2:1 MMR, $\delta r_{ex} < \delta r _{res}$ near the resonance for $e_{pl} = 1/2 e_{jup}$ and $e_{pl} = e_{jup}$.
+In these case, a dip, rather than a bump appears near the resonance in the bottom right panel of figure \ref{fig:coll_hist_e_and_m}.
+\label{fig:wander_res_scale}}
     \end{center}

### 2020-04-22 makeFig.py

@@ -39,7 +39,7 @@ ecc_jup = 0.048
 
 # Build a PDF from a series of data points using a KDE
 from sklearn.neighbors import KernelDensity
-def kde(qty, bw=0.1):
+def kde(qty, bw=0.05):
     bins = np.linspace(np.min(qty), np.max(qty))
     
     def kde_helper(x, x_grid, **kwargs):
@@ -264,11 +264,11 @@ def make_coll_hist_a():
 	coll_bins_a_e, coll_pdf_a_e = kde(coll_e['a1'])
 
 	fig, (ax1, ax2) = plt.subplots(figsize=(8,8), nrows=2, ncols=1, sharex=True)
-	ax1.plot(coll_bins_a_c, coll_pdf_a_c, linestyle='steps-mid')
+	ax1.plot(coll_bins_a_c, coll_pdf_a_c)
 	plot_res(ax1, show_widths=False)
 	ax1.set_ylabel('dN/da')
 	ax1.set_title('Circular Jupiter')
-	ax2.plot(coll_bins_a_e, coll_pdf_a_e, linestyle='steps-mid')
+	ax2.plot(coll_bins_a_e, coll_pdf_a_e)
 	plot_res(ax2, show_widths=False)
 	ax2.set_xlabel('Semimajor Axis [AU]')
 	ax2.set_ylabel('dN/da')
@@ -297,7 +297,7 @@ def make_coll_hist_r():
 
 	fig, ax = plt.subplots(figsize=(16,12), nrows=3, ncols=2, sharey='row', sharex='col')
 	
-	ax[0][0].plot(coll_bins_r_c, coll_pdf_r_c, linestyle='steps-mid')
+	ax[0][0].plot(coll_bins_r_c, coll_pdf_r_c)
 	plot_res(ax[0][0])
 	ax[0][0].set_ylabel('dN/dr')
 	ax[0][0].set_title('Circular Jupiter')
@@ -310,7 +310,7 @@ def make_coll_hist_r():
 	ax[2][0].set_xlim(a_in, a_out)
 	ax[2][0].set_ylim(-0.02, 0.35)
 
-	ax[0][1].plot(coll_bins_r_e, coll_pdf_r_e, linestyle='steps-mid')
[…]

### 2020-04-27 main.tex
Start looking at effect of pericenter precession near resonances

@@
 determine: 1. whether MMRs leave a detectable signature in the collisionally-generated dust. 2. If these signatures can be used to determine the orbital properties of the perturbing planet.
+
+Also mention \citet{2020A&A...635A..10S}, looked at dust trapping in resonances with terrestrial SS planets. Also mention 
+\citet{2020arXiv200408736G}, detection of a planetesimal collision around Fomalhut.
 
@@
     \includegraphics[width=0.4\columnwidth]{figures/ae.png}
-    \caption{The semimajor axis - eccentricity state of the remaining planetesimals are shown at the end of the CJ (top) and EJ (bottom) 
-    simulations. The vertical bars mark the nominal locations of prominent resonances. Planetesimals affected by resonance with Jupiter gain
-     eccentricity, and due to conservation of the Jacobi energy, reduce their semimajor axes. This produces the curved fingerlike structure 
-     extending off of the resonances. In the EJ case, some bodies in resonance take on eccentricities smaller than their initial forced values as 
-     they undergo libration.\label{fig:ae}}
+    \caption{The semimajor axis and eccentricities of planetesimals at the end of the eccentric Jupiter simulations.
+Near the location of mean motion resonances, the resonant angle librates and drives corresponding oscillations in eccentricity.
+Due to the conservation of the Jacobi energy, these changes in eccentricity also drive slight, inward changes in semimajor axis.\label{fig:ae}}
     \end{center}
@@
     \begin{center}
-    \includegraphics[width=0.4\columnwidth]{figures/long_ph.png}
-    \caption{The semimajor axis and pericenter orientation of remaining planetesimals at the end of the EJ simulation. All bodies start with their 
-    pericenters closely aligned with Jupiter's ($\varpi = \pi$). Near the resonances, bodies undergo strong precession which randomizes their 
-    orbital orientations. Two-body interactions between the planetesimals in resonance and nearby non-resonant planetesimals drags their 
-    longitude of perihelia along with.\label{fig:long_ph}}
+    \includegraphics[width=\columnwidth]{figures/long_ph.png}
+    \caption{The semimajor axis and pericenter orientation of remaining planetesimals at the end of the eccentric Jupiter simulations.
+When the forced eccentricity of the planetesimal disk is large, planetesimals near the edge of the mean motion resonances become more resistant to precession induced by the resonances.\label{fig:long_ph}}
     \end{center}
@@
 In the $e_{pl} = 2 e_{jup}$ case, a bump, rather than a dip appears near the 2:1 MMR (see figure \ref{fig:coll_hist_e_and_m}).
-This bump is produced by non-resonant planetesimals undergoing collisions near the center of the 2:1 MMR.\label{fig:coll_hist_r_inout_res}}
+This bump is produced by non-resonant planetesimals undergoing collisions near the center of the 2:1 MMR.
+In the right panel, the dashed curves represent collisions where the longitude of perihelion of either collider was strongly misaligned with Jupiter.
+In the high eccentricity case, bodies near the edge of the resonance with randomly oriented orbits can reach across the resonance and collide with planetesimals on the other side.\label{fig:coll_hist_r_inout_res}}
     \end{center}

### 2020-04-27 makeFig.py

@@ -226,19 +226,28 @@ def make_ae():
 
 	# Libration width varies with eccentricity so it doesn't make much sense
 	# to do show_widths=True here
-	fig, (ax1, ax2) = plt.subplots(figsize=(8,8), nrows=2, ncols=1, sharex=True, sharey=True)
-	ax1.scatter(pl_c['a'], pl_c['e'], s=s)
-	plot_res(ax1, show_widths=False)
-	ax1.set_ylabel('Eccentricity')
-	ax1.set_title('Circular Jupiter')
-	ax2.scatter(pl_e['a'], pl_e['e'], s=s)
-	plot_res(ax2, show_widths=False)
-	ax2.set_xlim(2, 4)
-	ax2.set_xlabel('Semimajor Axis [AU]')
-	ax2.set_ylabel('Eccentricity')
-	ax2.set_title('Eccentric Jupiter')
+	fig, ax = plt.subplots(figsize=(8,12), nrows=3, ncols=1, sharex=True, sharey=True)
+	ax[0].scatter(pl_e1['a'], pl_e1['e'], s=s)
+	#plot_res(ax[0], show_widths=False)
+	ax[0].set_ylabel('Eccentricity')
+	ax[0].set_title(r'e$_{pl}$ = 1/2 e$_{jup}$')
+
+	ax[1].scatter(pl_e['a'], pl_e['e'], s=s)
+	#plot_res(ax[1], show_widths=False)
+	ax[1].set_ylabel('Eccentricity')
+	ax[1].set_title(r'e$_{pl}$ = e$_{jup}$')
+
+	ax[2].scatter(pl_e2['a'], pl_e2['e'], s=s)
+	#plot_res(ax[2], show_widths=False)
+	ax[2].set_ylabel('Eccentricity')
+	ax[2].set_title(r'e$_{pl}$ = 2 e$_{jup}$')
+
+	ax[2].set_xlabel('Semimajor Axis [AU')
+
 	# sharey=true hides the tick labels
-	ax2.yaxis.set_tick_params(labelleft=True)
+	ax[2].yaxis.set_tick_params(labelleft=True)
+	ax[2].set_xlim(2, 4)
+	ax[2].set_ylim(-0.001, 0.2)
 	#plt.tight_layout(h_pad=0)
 	plt.savefig(file_str, format=fmt, bbox_inches='tight')
 
@@ -247,12 +256,22 @@ def make_long_ph():
[…]

### 2020-05-12 main.tex
Add new figures and reorder

--- 2020-04-22 main.tex
@@
 
+Also mention \citet{2020A&A...635A..10S}, looked at dust trapping in resonances with terrestrial SS planets. Also mention 
+\citet{2020arXiv200408736G}, detection of a planetesimal collision around Fomalhut.
+
 This work is organized in the following way: In section \ref{sec:dynamics}, we provide an overview of the relevant dynamics that drive 
@@
 
-We begin by making the assumption that a typical encounter between planetesimals in a disk is well-described by two-body 
-dynamics. So long as the random velocities of planetesimals $v_{p}$ are large compared to the Hill velocity of a planetesimal $v_{h} 
-= \sqrt{G m_{p} / r_{h}}$, where $r_{h}$ is the Hill radius, the gravitational field of the central star will play an insignificant role during a 
-encounter and can be safely ignored. In this case and assuming equal mass bodies, the collision rate is given by 
-\citep{1967SvA....10..650S}
-
-\begin{equation}\label{eq:safronov}
-	\sigma v = \pi r_{p}^2 \left( 1 + v_{esc}^2/v_{p}^2 \right) v_{p},
-\end{equation}
-
-\noindent where $r_{p}$ is the radius of a planetesimal, $v_{esc}$ is the mutual escape velocity of two planetesimals in contact and 
-$v_{p}$ is the typical encounter velocity between planetesimals. The $v_{esc}^2/v_{p}^2$ term describes the factor above which the 
-collision cross section is enhanced due to gravitational focusing. For a dynamically cold planetesimal disk, $v_{p}$ is small relative to 
-$v_{esc}$ and the collision rate becomes strongly enhanced.
-
-In the absence of collision detection, equation \ref{eq:safronov} can be used to make a local estimate of the 
-collision rate in an N-body simulation using only the positions, velocities and masses of particles. This has been done in other studies 
-\citep{2017ApJ...850..103B} (any other examples?), but requires bulk averaging of the phase space properties of particles, which 
-may mask important information and blur out features. As we will show in section \ref{sec:results}, the complex dynamical behavior of 
-planetesimals near mean-motion resonance makes it difficult to represent the typical encounter velocity $v_{p}$ with a single value. We will 
-revisit equation \ref{eq:safronov} in section \ref{sec:results} to test how well the collision rate near mean-motion resonances is described by 
-this framework.
-
-\subsection{Secular Forcing}\label{sec:sec_force}
-
-The most direct and widespread effect that a giant perturber will have on a planetesimal disk is through secular forcing of the 
-eccentricities of the planetesimals. This will cause the complex eccentricities of the planetesimals to take on a time independent 
-forced value, given by \citep{1999ApJ...527..918W} as
-
-\begin{equation}\label{eq:eforced}
-	z_{f} = \frac{b^{2}_{3/2} (\alpha)}{b^{1}_{3/2} (\alpha)} e_{g} ~ \mathrm{exp} ~ i \omega_{g}.
-\end{equation}
-
-\noindent Here, $\alpha = a_{g} / a$ where $a_{g}$ and $a$ are the semi-major axes of the giant planet and the planetesimal, 
-respectively. $e_{g}$ and $\omega_{g}$ are the eccentricity and longitude of pericenter of the giant and $b^{j}_{s} (\alpha)$ is a 
-Laplace coefficient given by \citep{2000ssd..book.....M} as
-
-\begin{equation}\label{eq:lap}
-	b_{s}^{j}(\alpha) = \frac{1}{2 \pi} \int_{0}^{2 \pi} \frac{cos \, j \theta \, d \theta}{\left( 1 - 2 \alpha \, cos \theta + \alpha^2 \right)^{s}}.
-\end{equation}
-
-Without any nearby secular or mean motion resonances, equation \ref{eq:eforced} will completely describe the eccentricities longitude of  pericenter orientations of the planetesimals.
-Additional forces due to two-body scattering between planetesimals, along with
-aerodynamic gas drag will add an additional free component to the complex eccentricity, which will be randomly oriented. The 
-magnitude of the free eccentricity describes how dynamically hot the planetesimal disk is and sets the random encounter speeds of 
-planetesimals. When the dynamical excitation of the disk is driven by gravitational stirring, the magnitude of the free eccentricity can 
-be described by a Rayleigh distribution \citep{1992Icar...96..107I}.
-
 \subsection{Mean Motion Resonances}
-
-In regions where there are commensurabilities between frequencies, secular theory breaks down and bodies are subject to strong 
-perturbations. For the purposes of this study, we will ignore secular resonances, which generally occur on rather large timescales 
-and will focus on mean motion resonances (MMRs). A MMR occurs  when the orbital period ratio between two bodies is sufficiently 
-close to
-
-\begin{equation}\label{eq:per_mmr}
-	\frac{P}{P'} = \frac{p + q}{p},
-\end{equation}
-
-\noindent where  $p$ and $q$ are integers $>$ 0 and the unprimed and primed quantities correspond to the perturber and the body 
-being perturbed, respectively. If the gravitational potential of the system is dominated by the central star, the condition for MMR is set 
-by the semi-major axes of the two bodies by
-
-\begin{equation}\label{eq:a_mmr}
-	\frac{a}{a'} = \left( \frac{p}{p + q} \right)^{2/3}.
-\end{equation}
-
-Under the effect of MMR, a body will undergo oscillations in semi-major axis and eccentricity. For sufficiently small perturbations,
-the amplitude of the oscillations in semi-major axis can be 
-described using the pendulum approximation (see equation 8.58 and 8.76 in \citet{2000ssd..book.....M}). This amplitude can be thought of 
-as the 'width' over which resonant perturbations are effective. Changes in eccentricity are correlated with changes in semi-major axis 
-variations according to the Tisserand relation
-
-\begin{equation}\label{eq:tiss}
-	\frac{de}{da} = \frac{a^{3/2} - 1}{2 a^{5/2} e}.
-\end{equation}
-
-The net result of this is that isolated MMRs will produce 'spikes' in the semi-major axis vs eccentricity distribution of a planetesimal 
-disk. Equation \ref{eq:tiss} predicts that these spikes will tend to slightly curve away from the perturbing body. This lowers the surface 
-density of the disk near the locations of resonances, while producing a pileup of bodies on eccentric orbits adjacent to the MMR. The 
-enhanced surface density will increase the collision rate, while the larger eccentricites will lower it due to the decreased effectiveness of 
-gravitational focusing. In addition, the MMRs cause the orbits of planetesimals to precess on relatively short timescales, which effectively 
-randomizes their longitudes of perihelion. In a secularly forced disk, there will be an interface between aligned and randomly oriented orbits 
-at the edge of the resonance. Due to the complicated dynamics that are at play in this region, we turn to a direct N-body treatment to better 
-understand how the collision rate varies in the vicinity of a MMR.
 
@@
 
-To follow the dynamical and collisional evolution of a planetesimal disk, we use the highly parallel N-body code {\sc ChaNGa} 
-\footnote{A public version of {\sc ChaNGa} can be downloaded from \url{http://www-hpcc.astro.washington.edu/tools/ChaNGa.html}}. 
-This code, which is written in the {\sc CHARM++} parallel programming language, was originally designed for cosmology simulations 
-and has been shown to perform well on up to half a million processors \citep{2015AphCom..2..1}. {\sc ChaNGa} calculates 
-gravitational forces using a modified Barnes-Hut \citep{1986Natur.324..446B} tree with hexadecapole expansions of the moments. 
-All of the simulations we perform use a node opening criterion of $\theta_{BH}$ = 0.7. More information about the code can be found 
-in \citet{2008IEEEpds...ChaNGa}. We have also recently modified {\sc ChaNGa} to handle solid-body collisions. A full description of 
-the collision module implementation can be found in \citet{2019MNRAS.489.2159W}.
-
 \subsection{Initial Conditions}\label{sec:ics}
-
-Two simulations are run, which are loosely based off of 'Model B' in \citet{2000Icar..143...45R}. In both cases, a Jupiter mass planet 
-is placed on a 5.2 AU orbit around a 1 $M_{\odot}$ star with a disk of planetesimals placed interior. In the first case, Jupiter is placed 
-on a circular orbit. In the second case, Jupiter is placed on a mildly eccentric (e = 0.05) orbit. We will refer to these simulations as CJ 
-and EJ, respectively.
-
-In both cases, the planetesimal disk extends from 2.2 to 3.8 AU. This range of semi-major axes covers a number of prominent 
-interior mean motion resonances with Jupiter, including the 3:1, the 5:2, the 2:1 and the 5:3. The planetesimal disk follows a 
-minimum-mass solar nebula surface density profile \citep{1981PThPS..70...35H}
-
-\begin{equation}\label{eq:surf_den}
-	\Sigma = \Sigma_{0} r^{-\alpha},
-\end{equation}
-
-\noindent with $\alpha$ = 3/2 and $\Sigma_{0}$ = 10 g cm$^{-2}$. Planetesimals are given a bulk density of 2 g cm$^{-3}$ and a 
-diameter of 300 km. This corresponds to a disk containing roughly 500,000 planetesimals. Both simulations are evolved for 
-5,000 years, which is about 400 Jupiter orbits.
-
-In the CJ simulation, there is no secular forcing from Jupiter and so the mean longitudes and mean anomalies are randomly 
-assigned values between 0 and 2$\pi$. The distribution of eccentricities and inclinations of the planetesimals are chosen so that the 
-effects of viscous stirring and gas drag from the solar nebula are in balance. This occurs when eccentricities are described by a 
-Rayleigh distribution with a scale parameter given by equation 12 in \citet{2002ApJ...581..666K}. The inclination distribution is 
-described by this same function, with a scale parameter that is half as large. This is typical for a dynamically heated disk 
-of particles in a Kepler potential \citep{1993MNRAS.263..875I}.
-
-For simulation EJ, the effects of secular forcing by Jupiter are built in to the initial conditions. This is done by first assigning Kepler 
-orbital elements to the planetesimals in the same way as simulation CJ and then adding a forced component to the eccentricity 
-vectors $z_{i} = \left( h_{i}, k_{i} \right)$, described by equation \ref{eq:eforced}. For simplicity, a coordinate system is chosen so that 
-$\omega_{g}$ = 0. This allows us to simply add a scalar value to each $h_{i}$, which depends only on the semi-major axis of a 
-planetesimal and Jupiter, along with the eccentricity of Jupiter.
 
@@
 
-For the purposes of the integrator, there are two relevant timescales in this system. The first is the orbital dynamical time $\sqrt{a^3/
-G M_{\odot}}$. All particles are placed on a fixed time step of $\Delta T$ = 0.01 yr. This is roughly 3\% of an orbital dynamical time at 
-the inner edge of the planetesimal disk. From numerical tests with {\sc ChaNGa}, we have found that this time step size preserves 
-the symplectic nature of the integration without being too computationally expensive. Although using $\Delta T$ = 0.01 yr keeps the 
-integration symplectic, we find that a small amount of artificial precession is produced, which is particularly noticable in the EJ 
-simulation. We reduce the base time step size by an additional factor of 4 to the keep longitude of perihelia of planetesimals near the 
-inner edge of the disk from drifting too far over the course of our integrations.
-
-An additional timescale is set by the dynamical time of the planetesimals ($\sim 1/\sqrt{G \rho}$), which is about 45 minutes. To 
-resolve the base time step and the dynamical timescale of planetesimals simultaneously, we use a two-tiered time stepping scheme. 
-At the beginning of each time step, all bodies are placed on the orbital time step. A first pass of collision detection is then run in 
-which the radii of all bodies are inflated by a factor of 2.5. Any bodies with imminent collisions predicted using the inflated radii are 
-placed on a time step that is a factor of 16 smaller than the orbital time step. The purpose of two-tiered scheme is to properly resolve 
-the gravitational interactions between any bodies that undergo a close encounter. This prevents the coarser base time step from 
-reducing the effectiveness of gravitational focusing, while minimizing the additional computational expense.
+\section{Results} \label{sec:results}
 
 \begin{figure*}
+\begin{center}
     \includegraphics[width=\textwidth]{figures/xy.png}
-    \caption{The positions of remaining planetesimals at the end of the CJ (left) and EJ (right) simulations. Jupiter's position is
-    indicated by a red dot. Nonaxisymmetric features due to mean motion resonances are clearly visible in both cases. Higher
-    order resonances are visible in the EJ case.\label{fig:xy}}
+    \caption{Non axisymmetric gaps and rings appear near MMRs. More features appear at higher eccentricities. Gap features
+    at $\theta$ = 0 and $\theta = \pi$ follow the giant planet in its orbit.\label{fig:xy}}
+\end{center}
 \end{figure*}
-
-\section{Results} \label{sec:results}
-
-We begin by examining the spatial distribution of planetesimals in the CJ and EJ simulations. The cylindrical position of the planetesimals 
-in the the CJ and EJ simulations after 5000 years of integration are shown in the left and right hand panels of  figure \ref{fig:xy}, 
-respectively. In the circular Jupiter case, a gap produced by the 2:1 MMR is visible, while the 3:1 and 5:3 MMR gaps are visible with an 
-eccentric Jupiter. The non-axisymmetric nature of the gaps is due to the fact that planetesimals in the vicinity of the resonances have been 
-excited onto non-circular orbits. Although the spatial distribution of planetesimals near MMR in debris disks may provide clues to detect 
-unseen planets, we will not focus on this topic here, as it has already been covered in detail by other studies \citep{2016ApJ...818..159T, 
-2018ApJ...857....3T}.
-
-The MMRs are most clearly visible when viewing the semimajor axis and eccentricity distribution of the planetesimals. This is shown 
-in figure \ref{fig:ae}. The top panel corresponds to the CJ simulation and the bottom panel corresponds to EJ. The solid vertical lines 
-in this plot represent the nominal locations of the resonances. Near the nominal resonance locations, the a-e distribution of the 
-planetesimals exhibits well-defined spikes which curve slightly inward due to conservation of the Jacobi energy. In the EJ simulation, 
-the eccentricity distribution of bodies near resonance extends below the initial forced value. This is a reflection of the fact that the resonant 
-angles of these bodies are undergoing libration, which drives periodic oscillations in both semimajor axis and eccentricity. The coupling 
-between these two quantities is described by equation \ref{eq:tiss}. Because the strength of the resonances scales with the initial 
-eccentricity of the planetesimals, the eccentricity spikes are larger in the EJ simulation. Additionally, the relative size of the 3:1 and 5:3 
-MMR spikes also grows because the strength of a MMR scales as $e^{q}$, where $q$ is the order of the resonance 
-\citep{1994PhyD...77..289M}.
 
@@
 \begin{center}
-    \includegraphics[width=0.4\columnwidth]{figures/ae.png}
-    \caption{The semimajor axis - eccentricity state of the remaining planetesimals are shown at the end of the CJ (top) and EJ (bottom) 
-    simulations. The vertical bars mark the nominal locations of prominent resonances. Planetesimals affected by resonance with Jupiter gain
-     eccentricity, and due to conservation of the Jacobi energy, reduce their semimajor axes. This produces the curved fingerlike structure 
-     extending off of the resonances. In the EJ case, some bodies in resonance take on eccentricities smaller than their initial forced values as 
-     they undergo libration.\label{fig:ae}}
+    \includegraphics[width=0.5\textwidth]{figures/ae.png}
+    \caption{The MMRs produce spikes in the a-e plane. Between resonances, the nonzero eccentricity is caused by secular
+    forcing by the planet. At larger eccentricities, the higher order resonances become more prominent because of the steeper
+    scaling with $e$.\label{fig:ae}}
 \end{center}
@@
 
-The MMRs have an additional important effect, which is to drive precession of the longitudes of perihelion of planetesimals. 
-This effect becomes important in the EJ simulation because the orbits of bodies are initially aligned with that of Jupiter 
-(see section \ref{sec:sec_force}). As is shown in figure \ref{fig:long_ph}, the strong precession induced by the MMRs overcomes the 
-secular forcing and randomizes the orbital orientations of bodies near the resonances. The dashed horizontal lines in figure 
-\ref{fig:long_ph} indicate the libration width (should probably show the equation I used to calculate this) of a planetesimal with an 
-eccentricity of $e_{forced}$ at each resonance, which approximately shows the zone of influence of each MMR.
+\begin{figure*}
+\begin{center}
+    \includegraphics[width=\textwidth]{figures/long_ph.png}
+    \caption{The MMRs also induce precession which overpowers the secular forcing. Inside of the resonances, orbits of
+    planetesimals are effectively randomized.\label{fig:long_ph}}
+\end{center}
+\end{figure*}
 
@@
 \begin{center}
-    \includegraphics[width=0.4\columnwidth]{figures/long_ph.png}
-    \caption{The semimajor axis and pericenter orientation of remaining planetesimals at the end of the EJ simulation. All bodies start with their 
-    pericenters closely aligned with Jupiter's ($\varpi = \pi$). Near the resonances, bodies undergo strong precession which randomizes their 
-    orbital orientations. Two-body interactions between the planetesimals in resonance and nearby non-resonant planetesimals drags their 
-    longitude of perihelia along with.\label{fig:long_ph}}
+    \includegraphics[width=0.5\textwidth]{figures/coll_hist_a.png}
+    \caption{In semimajor axis space, prominent features appear near the 3:1 and 2:1 MMRs. Near the 3:1, the collision
+    rate decreases, while it gets enhanced near the 2:1. This is because gravitational focusing is already suppressed
+    near the 2:1. Additional heating by the resonance increases the encounter rate.\label{fig:coll_hist_a}}
 \end{center}
@@
 \begin{center}
-    \includegraphics[width=0.4\columnwidth]{figures/coll_hist_a.png}
-    \caption{A kernel density estimate (KDE) of the collision rate as a function of semimajor axis in the CJ (top) and EJ (bottom) simulations. 
-    There are measureable changes in the collision rate near 2:1 and 3:1 MMRs, each of which produce qualitatively different changes in the 
-    collision rate. The vertical bars mark the nominal locations of prominent resonances.\label{fig:coll_hist_a}}
+    \includegraphics[width=0.5\textwidth]{figures/coll_hist_r.png}
+    \caption{The features near resonance that appear in cylindrical distance space appear qualitatively different.
+    The orange curve shows collisions with bodies inside the 2:1 and 3:1 MMR excluded. This does not qualitatively
+    change any of the plots, and we infer that the features seen here are produced by bodies outside of resonance.
+    Most interestingly,  the highest eccentricity planet simulation produces bumps, rather than dips near the 2:1 and
+    3:1 MMR.\label{fig:coll_hist_r}}
+\end{center}
+\end{figure}
+
+\begin{figure*}
+    \includegraphics[width=\textwidth]{figures/coll_polar_e.png}
+    \caption{The features in the previous figure appear to match with the pileups of bodies near the edges of the
+    resonances. The dashed and solid lines show the perihelion and aphelion distances for bodies at the inner
+    and outer edges of the 2:1 and 3:1 resonances. The dip vs bump features seen in the previous figure appear
+    to depend on whether the aphelia of bodies at the inner edge and perihelia of bodies at the outer edge of a
+    resonance cross. When this does not occur, a cavity persists at the center of the resonance, which reduces the
+    collision rate in that region. When the two distances overlap, bodies from both edges of the resonance spend some
+    time in the middle, producing a bump in the collision rate.\label{fig:coll_polar_e}}
+\end{figure*}
+
+\begin{figure*}
+    \includegraphics[width=\textwidth]{figures/coll_polar_m.png}
+    \caption{Similar to the previous figure, except the eccentricity of the planet is kept constant and the mass is varied.
+    This has the effect of changing the width of the resonances, without altering the relative apo or peri distances of
+    bodies near the edges.\label{fig:coll_polar_m}}
+\end{figure*}
+
+\begin{figure}
+\begin{center}
+    \includegraphics[width=0.5\textwidth]{figures/bump_dip_diag.png}
+    \caption{The presence of a dip or bump near the resonances can be used to constrain the mass and eccentricity
+    of the perturbing planet. A simultaneous dip and the 2:1 MMR, combined with a bump at the 3:1 MMR can be
+    used to place even more restrictive constraints.\label{fig:bump_dip_diag}}
 \end{center}
@@
 
-A prediction of the collision rate using the Safronov equation (eq \ref{eq:safronov}) and the positions and velocities of the planetesimals
-suffers from an important limitation. As we will show below, the velocities of planetesimals near the MMRs does not follow a unimodal 
-distribution. This makes it difficult to characterize the motion of the planetesimals with a single encounter velocity $v_{p}$ and so predicting 
-the collision rate using a statistical approach is far from straightforward. This operation becomes even more complicated with a secularly 
-perturbed disk where there is a transition between aligned and randomly oriented orbits near the interface of the resonances (see figure 
-\ref{fig:long_ph}.
-
-Figure \ref{fig:coll_hist_a} shows the semimajor axis of collisions resolved in the CJ (top) and EJ simulations (bottom). We define 
-the semimajor axis of a collision as the semimajor axis of the first of the two planetesimals participating in a collision at the 
-moment that it happens. To ensure that the definition of the first and second collider chosen by {\sc ChaNGa} does not influence 
-these results, we also tried constructing figure \ref{fig:coll_hist_a} using the properties of the second collider and found no qualitative 
-differences. Although both simulations were integrated and collisions were resolved for 5,000 years, we only show collisions that occurred 
-during the last 3,000 years of the simulations. Before this time, the resonant features in the semimajor axis-eccentricity distribution (see 
-figure \ref{fig:ae}) were still developing and had not yet reached a steady state (the libration timescale of the MMRs we are interested in 
-turns out to be about 2,000 years). This results in transient features appearing in the collision profiles early on, which we exclude from 
-figure \ref{fig:coll_hist_a} and all subsequent figures.
-
-We find that the features present in figure \ref{fig:coll_hist_a} are highly sensitive to the choice of binning when constructing a standard 
-histogram and instead model the occurrence of collisions as a function of semimajor axis using a kernel density estimate (KDE). We use 
-the {\sc neighbors.KernelDensity} function from the {\sc sklearn} \citep{scikit-learn} package to construct our KDEs. For the kernel, we use 
-a tophat function with a bandwidth of 0.01 AU.
-
-Near some of the MMRs, there are noticeable suppressions or enhancements of the local collision rate. This contrasts with the findings of 
-\citet{2000Icar..143...45R}, who simulated a similar setup and found no discernible features near the MMRs. We attribute the differences to 
-a more careful treatment of timestepping in our simulations. Just interior to the 2:1 resonance, the collision rate is strongly enhanced. In the 
-EJ simulation, there is a significant deficiency in the number of collisions near the 3:1 MMR. This feature, although still present, is much 
-weaker in the CJ simulation. We attribute this to the fact that the strength of a second-order MMR scales as $e^{2}$, while a first order 
-MMR scales with $e$ \citep{1994PhyD...77..289M}. One would therefore expect the 3:1 resonance to have more of an influence on the 
-collision rate in a more eccentric disk. Although viewing the collision rate as a function of semimajor axis demonstrates a clear connection 
-between the resonances and the collision rate, this does not immediately indicate where the dust generated by collisions will end up in the 
-disk. (Why is the feature around the 3:1 MMR so different than the 2:1?)
-
-\begin{figure*}
-    \includegraphics[width=\textwidth]{figures/coll_hist_r.png}
-    \caption{\textit{Top:} A KDE of the collision rate in the CJ (left) and EJ (right) simulations as a function of cylindrical distance from the central 
-    star. Vertical lines mark the nominal locations of the MMRs. Variations in the collision rate are visible near the MMRs, but are distinctly 
-    different than the feature that appeared in figure \ref{fig:coll_hist_a}. \textit{Middle:} The azimuthally-averaged surface density of remaining 
-    planetesimals. \textit{Bottom:} The cylindrical distance and eccentricities of remaining planetesimals. The cones extending upward from the 
-    resonance locations are due to the fact that eccentric planetesimals explore a wide range of physical space over the course of an orbit.\label{fig:coll_hist_r}}
-\end{figure*}
-
 \subsection{Where Does the Dust End Up?}
 
-To construct a radial dust profile, we begin by making the assumption that any dust generated by collisions is strongly coupled to the 
-gas. For a dust grain larger than the mean free path of the gas particles, the timescale to damp its eccentricity is given by 
-\citep{1976PThPh..56.1756A}
-
-\begin{equation}\label{eq:t_edamp}
-    t_{e, damp} = \frac{8 s \rho}{3 e C_{D} \rho_{g} v_{th}}.
-\end{equation}
-
-where $m$, $e$ and $s$ are the mass, eccentricity and radius of the dust grain. $C_{D}$ is a drag coefficient which is of order unity, $
-\rho_{g}$ is the local density of the gas and $v_{th}$ is its thermal speed. At 3 AU, the gaseous component of the solar nebula has a 
-density of $4 \times 10^{-10}$ g cm$^{-3}$ and a typical thermal speed of $10^{5}$ cm s$^{-1}$ \citep{1981PThPS..70...35H}. For a 1 
-mm dust grain with a density of 1 g cm$^{-3}$ and an eccentricity of 0.05, the damping timescale is $4 \times 10^{-3}$ years. This is 
-orders of magnitude smaller than the collision timescale, therefore we conclude that collisionally generated dust grains will immediately 
-couple to the gas.
-
-Operating under this assumption, a map of the relative concentration of second-generation dust can be constructed from the cylindrical 
-distance at which the collisions occur. This is shown in the top panels of figure \ref{fig:coll_hist_r}, where the left side corresponds to the CJ 
-simulation and the right side corresponds to EJ. As in figure \ref{fig:coll_hist_a}, a KDE of the collision rate is constructed using a tophat 
-kernel with a bandwidth of 0.01 AU.
-
-In contrast to what was seen in figure \ref{fig:coll_hist_a}, the radial collision rate is now suppressed near the 2:1 MMR. The spike in the 
-collision rate at semimajor axes interior to this location becomes washed out when viewed instead by cylindrical distance because the 
-spread in the eccentricities of the colliding planetesimals is so large. Although many of the collisions happen at the same semimajor axis, 
-they occur at very different distances from the central star. The second row of figure \ref{fig:coll_hist_r} shows the azimuthally averaged 
-surface density of the planetesimal disk at the end of the simulations. These profiles were calculated using the {\sc PYNBODY} analysis 
-package \citep{2013ascl.soft05002P}.
-
-In both the CJ and EJ simulations, the local minima in the surface density profiles match well with the minima in the collision rates. 
-Additionally, the minima in the EJ simulation are offset from the centers of the resonances. This can be explained as follows: for 
-planetesimals affected by the MMRs, the typical encounter velocity is large and gravitational focusing is suppressed. Here, the collision 
-cross section is geometric. In this limit, the collision probability scales with the ratio between the geometric cross section of the 
-planetesimals and the surface area of a sphere with radius $r$, where $r$ is the distance between the bodies and the central star. This 
-ratio, and therefore the collision probability, is largest when $r$ is minimized (see \citet{2003AJ....125.2692L}). Therefore, the collision 
-probability for planetesimals affected by resonance is smallest at aphelion. This is also consistent with the reduced surface density exterior 
-to the resonances.
-
-Finally, the bottom row of figure \ref{fig:coll_hist_r} demonstrates the difficulty with calculating the collision rate from the position and velocity 
-distribution of particles. At a given distance from the central star, the distribution of velocities (using eccentricity as a proxy for encounter 
-velocity), is not unimodal. In addition, the wings extending off of the resonances in these plots show that planetesimals can interact and collide 
-with bodies far from the centers of the resonances. The bump seen in the collision rate in the EJ simulation around 2.7 AU is like a result of 
-interaction between planetesimals in the 3:1, 5:2 and 2:1 resonances.
-
-So far, we have shown that mean-motion resonances with a perturbing giant planet will produce measureable radial variations in the collision 
-rates across a disk of planetesimals, which should give rise to variations in the dust profile. In addition, distinctly different features are 
-produced if the giant planet is on an eccentric, rather than a circular orbit. In the next section, we would like to determine whether these 
-features can be used to place any constraints on the mass and eccentricity of the planet.
-
 \section{Influence of Jupiter's Mass and Eccentricity on the Radial Dust Profile}
-
-\begin{figure*}
-    \includegraphics[width=\textwidth]{figures/coll_hist_e_and_m.png}
-    \caption{Caption goes here.\label{fig:coll_hist_e_and_m}}
-\end{figure*}
-
-\begin{figure*}
-    \begin{center}
-    \includegraphics[width=\textwidth]{figures/coll_hist_hot_cold_a.png}
-    \caption{Caption goes here.\label{fig:coll_hist_hot_cold_a}}
-    \end{center}
-\end{figure*}
-
-\begin{figure*}
-    \begin{center}
-    \includegraphics[width=0.4\textwidth]{figures/coll_gf_vary.png}
-    \caption{Caption goes here.\label{fig:coll_gf_varg}}
-    \end{center}
-\end{figure*}
-
-\begin{figure*}
-    \begin{center}
-    \includegraphics[width=\textwidth]{figures/coll_hist_r_inout_res.png}
-    \caption{Caption goes here.\label{fig:coll_hist_r_inout_res}}
-    \end{center}
-\end{figure*}
-
-\begin{figure*}
-    \begin{center}
-    \includegraphics[width=\textwidth]{figures/wander_res_scale.png}
-    \caption{Caption goes here.\label{fig:wander_res_scale}}
-    \end{center}
-\end{figure*}
 

### 2020-05-12 makeFig.py

@@ -27,7 +27,6 @@ simV = u.AU/simT
 path = 'data/'
 
 # Resonances
-res_dist = [2.5, 3.27, 3.7]
 res_label = ['3:1', '2:1', '5:3']
 res_p = [1, 1, 3]
 res_q = [2, 1, 2]
@@ -37,10 +36,17 @@ m_jup = 9.54e-4
 a_jup = 5.2
 ecc_jup = 0.048
 
+res_dist = []
+for idx in range(len(res_p)):
+    j1 = res_p[idx] + res_q[idx]
+    j2 = -res_p[idx]
+    alpha = (-j2/j1)**(2./3.)
+    res_dist.append(a_jup*alpha)
+
 # Build a PDF from a series of data points using a KDE
 from sklearn.neighbors import KernelDensity
-def kde(qty, bw=0.05):
-    bins = np.linspace(np.min(qty), np.max(qty))
+def kde(qty, bw=0.03):
+    bins = np.linspace(2, 4, (4-2)/bw)
     
     def kde_helper(x, x_grid, **kwargs):
         kde_skl = KernelDensity(kernel='tophat', bandwidth=bw, **kwargs)
@@ -52,14 +58,24 @@ def kde(qty, bw=0.05):
     
     return bins, pdf
 
+def coll_hist(coll, key, nbins=60):
+	bins = np.linspace(2, 4, nbins)
+
+	hist, bins = np.histogram(coll[key], bins=bins)
+	bins = 0.5*(bins[1:] + bins[:-1])
+
+	bins, hist = kde(coll[key])
+
+	return bins, hist
+
 def e_forced(a, ecc_jup):
 	return ko.lap(2, 3/2, a/a_jup)/ko.lap(1, 3/2, a/a_jup)*ecc_jup
 
 # Width of a resonance with jupiter (in AU)
 # Assume body has an eccentricity of e_forced
-def res_width_jup(p, q, ecc_jup=ecc_jup, m_jup=m_jup):
-	j1 = p + q
-	j2 = -p
+def res_width_jup(res_idx, ecc_jup=ecc_jup, m_jup=m_jup):
+	j1 = res_p[res_idx] + res_q[res_idx]
+	j2 = -res_p[res_idx]
 	alpha = (-j2/j1)**(2./3.)
[…]

### 2020-05-13 main.tex
Add new bump vs dip diagnostic figure

@@
 
-\begin{figure}
+\begin{figure*}
 \begin{center}
-    \includegraphics[width=0.5\textwidth]{figures/bump_dip_diag.png}
+    \includegraphics[width=\textwidth]{figures/bump_dip_diag.png}
     \caption{The presence of a dip or bump near the resonances can be used to constrain the mass and eccentricity
-    of the perturbing planet. A simultaneous dip and the 2:1 MMR, combined with a bump at the 3:1 MMR can be
-    used to place even more restrictive constraints.\label{fig:bump_dip_diag}}
+    of the perturbing planet. The color scale indicates the relative strength of the features, while the dashed lines
+    indicate boundaries in parameter space where a dip or a bump will be produced at the resonance.\label{fig:bump_dip_diag}}
 \end{center}
-\end{figure}
+\end{figure*}
 

### 2020-05-13 makeFig.py

@@ -1,6 +1,8 @@
 #/bin/bash
 import matplotlib.pylab as plt
 import matplotlib as mpl
+from matplotlib import cm
+import matplotlib.colors as colors
 
 mpl.rcParams.update({'font.size': 18, 'font.family': 'STIXGeneral', 'mathtext.fontset': 'stix',
                             'image.cmap': 'viridis'})
@@ -45,11 +47,11 @@ for idx in range(len(res_p)):
 
 # Build a PDF from a series of data points using a KDE
 from sklearn.neighbors import KernelDensity
-def kde(qty, bw=0.03):
+def kde(qty, bw=0.02):
     bins = np.linspace(2, 4, (4-2)/bw)
     
     def kde_helper(x, x_grid, **kwargs):
-        kde_skl = KernelDensity(kernel='tophat', bandwidth=bw, **kwargs)
+        kde_skl = KernelDensity(kernel='gaussian', bandwidth=bw, **kwargs)
         kde_skl.fit(x[:, np.newaxis])
         log_pdf = kde_skl.score_samples(x_grid[:, np.newaxis])
         return np.exp(log_pdf)
@@ -239,7 +241,7 @@ def make_coll_polar_e():
 	ax00.invert_xaxis()
 
 	ax00.plot(coll_hist_e1, coll_bins_e1, linestyle='steps-mid')
-	ax01.scatter(theta_e1, r_e1, s=s)
+	ax01.scatter(theta_e1, r_e1, s=s*10)
 
 	ax00.axhline(outer_peri_31)
 	ax00.axhline(outer_apo_31, linestyle='--')
@@ -263,7 +265,7 @@ def make_coll_polar_e():
 	ax00.set_ylim(rmin, rmax)
 	ax01.set_xlim(-np.pi, np.pi)
 	ax01.set_ylim(rmin, rmax)
-	ax00.set_xlabel('Number of Collisions')
+	ax00.set_xlabel('Rel. # of Collisions')
 	ax01.set_xlabel('Azimuth')
 	ax00.set_ylabel('Cylindrical Distance [AU]')
 	ax01.set_title(r'e$_{g}$ = 1/2 e$_{jup}$')
@@ -291,7 +293,7 @@ def make_coll_polar_e():
 	ax10.invert_xaxis()
 
[…]

### 2020-05-14 main.tex
Add resonance width equations to section 2, update initial conditions section

@@
 drive disk morphologies. We use a direct N-body model to track collision rates in a planetesimal disk under the gravitational influence of an 
-external Jupiter-sized planet. We show that a perturbing planet can produce significant variations in the collision rate of planetesimals near the 
+external giant planet. We show that a perturbing planet can produce significant variations in the collision rate of planetesimals near the 
 MMRs and we explore how the mass and eccentricity of the perturbing planet alters this structure. Finally, we use the CASA image simulator to 
@@
 
+Also mention \citet{2020A&A...635A..10S}, looked at dust trapping in resonances with terrestrial SS planets. Also mention 
+\citet{2020arXiv200408736G}, detection of a planetesimal collision around Fomalhut.
+
 The dynamics governing the motion of bodies near MMRs is extremely nonlinear, as is determining what the collision rates between 
@@
 explore the collision rate structure of the planetesimal disk in the vicinity of mean motion resonances. In particular, we would like to 
-determine: 1. whether MMRs leave a detectable signature in the collisionally-generated dust. 2. If these signatures can be used to determine the orbital properties of the perturbing planet.
-
-Also mention \citet{2020A&A...635A..10S}, looked at dust trapping in resonances with terrestrial SS planets. Also mention 
-\citet{2020arXiv200408736G}, detection of a planetesimal collision around Fomalhut.
+determine: 1.
+whether MMRs leave a detectable signature in the collisionally-generated dust.
+2.
+If these signatures can be used to determine or constrain the orbital properties of the perturbing planet.
 
@@
 
-\subsection{Collision Rates of Massive Bodies}
+\subsection{Secular Forcing}\label{sec:sec_force}
+
+The most direct and widespread effect that a giant perturber will have on a planetesimal disk is through secular forcing of the 
+eccentricities of the planetesimals. This will cause the complex eccentricities of the planetesimals to take on a time independent 
+forced value, given by \citep{1999ApJ...527..918W} as
+
+\begin{equation}\label{eq:eforced}
+	z_{f} = \frac{b^{2}_{3/2} (\alpha)}{b^{1}_{3/2} (\alpha)} e_{g} ~ \mathrm{exp} ~ i \omega_{g}.
+\end{equation}
+
+\noindent Here, $\alpha = a_{g} / a$ where $a_{g}$ and $a$ are the semi-major axes of the giant planet and the planetesimal, 
+respectively. $e_{g}$ and $\omega_{g}$ are the eccentricity and longitude of pericenter of the giant and $b^{j}_{s} (\alpha)$ is a 
+Laplace coefficient given by \citep{2000ssd..book.....M} as
+
+\begin{equation}\label{eq:lap}
+	b_{s}^{j}(\alpha) = \frac{1}{2 \pi} \int_{0}^{2 \pi} \frac{cos \, j \theta \, d \theta}{\left( 1 - 2 \alpha \, cos \theta + \alpha^2 \right)^{s}}.
+\end{equation}
+
+Without any nearby secular or mean motion resonances, equation \ref{eq:eforced} will completely describe the eccentricities and longitude of  
+pericenter orientations of the planetesimals. Additional forces due to two-body scattering between planetesimals, along with 
+aerodynamic gas drag will add an additional free component to the complex eccentricity, which will be randomly oriented. The 
+magnitude of the free eccentricity describes how dynamically hot the planetesimal disk is and sets the random encounter speeds of 
+planetesimals. When the dynamical excitation of the disk is driven by gravitational stirring, the magnitude of the free eccentricity can 
+be described by a Rayleigh distribution \citep{1992Icar...96..107I}.
 
 \subsection{Mean Motion Resonances}
+
+In regions where there are commensurabilities between frequencies, secular theory breaks down and bodies are subject to strong 
+perturbations. For the purposes of this study, we will ignore secular resonances, which generally occur on rather large timescales 
+and will focus on mean motion resonances (MMRs). A MMR occurs  when the orbital period ratio between two bodies is sufficiently 
+close to
+
+\begin{equation}\label{eq:per_mmr}
+	\frac{P}{P'} = \frac{p + q}{p},
+\end{equation}
+
+\noindent where  $p$ and $q$ are integers $>$ 0 and the unprimed and primed quantities correspond to the perturber and the body 
+being perturbed, respectively. If the perturber is much more massive than the other body, the condition for MMR is set  by the semi-major 
+axes of the two bodies by
+
+\begin{equation}\label{eq:a_mmr}
+	\frac{a}{a'} = \left( \frac{p}{p + q} \right)^{2/3}.
+\end{equation}
+
+If we further assume that the two bodies are orbiting in the same plane, the behavior of the bodies near resonance is determined by the
+behavior of a critical angle
+
+\begin{equation}\label{eq:phi_crit}
+	\phi = (p + q) \lambda' - q \lambda - (2 p + q) \varpi,
+\end{equation}
+
+\noindent where $\lambda = \varpi + M$ is the mean longitude of a body. For bodies in resonance, the critical angle will librate around an 
+equlibrium value, while this angle will circulate outside of resonance. This behavior is analogous to the motion of a pendulum. Changes in the 
+critical angle are coupled to changes in the mean motion and semimajor axis \citet{2000ssd..book.....M}. An important point to note, which will 
+become important later, is that the circulation frequency approaches zero near the edge of a resonance. The width of a resonance can be 
+defined by determining the largest variation in semimajor axis that permits librational, rather than circulatory motion of the pendulum. For 
+second and higher order resonances, the maximum libration width is given by
+
+\begin{equation}\label{eq:res_so}
+	\frac{\delta a}{a} = \left( \frac{16}{3} \frac{\left| C_{r} \right|}{n} e^{\left| 2 p + q \right|} \right)^{1/2},
+\end{equation}
+
+\noindent where n, a and e are the mean motion, semimajor axis and eccentricity of the unperturbed body.
+$C_{r}$ is a constant defined by $m'/m_{c} n \alpha f_{d}(\alpha)$, where $\alpha$ = $a/a'$ and $f_{d}$ is the resonant part of the disturbing function.
+For an interior second-order resonance,
+
+\begin{equation}\label{eq:fd_so}
+	f_{d} (\alpha) = \frac{1}{8} \left[ -5(p+q) + 4(p+q)^{2} - 2 \alpha D + 4(p+q) \alpha D + \alpha^{2} D^{2} \right] b^{p+q}_{1/2},
+\end{equation}
+
+\noindent where $D b^{j}_{s}$ is the first derivative with respect to $\alpha$ of the Laplace coefficient defined in equation \ref{eq:lap}. This can 
+be written as
+
+\begin{equation}\label{eq:lap_d}
+	\frac{d b_{s}^{j}}{d \alpha} = s \left( b_{s+1}^{j-1} - 2 \alpha b_{s+1}^{j} + b_{s+1}^{j+1} \right).
+\end{equation}
+
+For a first order resonance, the associated disturbing function terms are slightly simpler
+
+\begin{equation}\label{eq:fd_fo}
+	f_{d}(\alpha) = (p+q) b_{1/2}^{p+q} + \frac{\alpha}{2} D b_{1/2}^{p+q},
+\end{equation}
+
+\noindent and there is an additional contribution to the motion of the critical angle by the pericenter precession rate such that
+
+\begin{equation}\label{eq:res_fo}
+	\frac{\delta a}{a} = \pm \left(\frac{16}{3} \frac{\left| C_{r} \right|}{n} e \right)^{1/2} \left(  1 + \frac{1}{27 p^2 e^3} \frac{\left| C_{r} \right|}{n} 
+	\right)^{1/2} - \frac{2}{9 p e}  \frac{\left| C_{r} \right|}{n}.
+\end{equation}
+
+Changes in eccentricity are correlated with changes in semimajor axis variations according to the Tisserand relation
+
+\begin{equation}\label{eq:tiss}
+	\frac{de}{da} = \frac{a^{3/2} - 1}{2 a^{5/2} e}.
+\end{equation}
+
+The net result of this is that MMRs will produce 'spikes' in the semimajor axis - eccentricity distribution of a planetesimal disk. In order to 
+preserve the Jacobi energy, equation \ref{eq:tiss} predicts that these spikes will tend to curve away from the perturbing body. This lowers the 
+surface density of the disk near the locations of resonances, while producing a pileup of bodies on eccentric orbits adjacent to the MMR. The 
+enhanced surface density will increase the collision rate. At the same time, the large eccentricites will either lower it due to the decreased 
+effectiveness of gravitational focusing, or raise it due to the more vigorous encounter rate, depending on how large the encounter velocity gets 
+compared to the escape velocity of the planetesimals. In addition, the MMRs cause the orbits of planetesimals to precess on relatively short 
+timescales, which effectively randomizes their longitudes of perihelion. In a secularly forced disk, there will be an interface between aligned 
+and randomly oriented orbits at the edge of the resonance. Due to the complicated dynamics that are at play in this region, we turn to a direct 
+N-body treatment to better understand how the collision rate varies in the vicinity of a MMR.
 
@@
 
+To follow the dynamical and collisional evolution of a planetesimal disk, we use the highly parallel N-body code {\sc ChaNGa} 
+\footnote{A public version of {\sc ChaNGa} can be downloaded from \url{http://www-hpcc.astro.washington.edu/tools/ChaNGa.html}}. 
+This code, which is written in the {\sc CHARM++} parallel programming language, was originally designed for cosmology simulations 
+and has been shown to perform well on up to half a million processors \citep{2015AphCom..2..1}. {\sc ChaNGa} calculates 
+gravitational forces using a modified Barnes-Hut \citep{1986Natur.324..446B} tree with hexadecapole expansions of the moments. 
+All of the simulations we perform use a node opening criterion of $\theta_{BH}$ = 0.7. More information about the code can be found 
+in \citet{2008IEEEpds...ChaNGa}. We have also recently modified {\sc ChaNGa} to handle solid-body collisions. A full description of 
+the collision module implementation can be found in \citet{2019MNRAS.489.2159W}.
+
 \subsection{Initial Conditions}\label{sec:ics}
 
+In total, five simulations are run. The first is a 'nominal' case, in which the perturbing planet's mass and eccentricity are set to that of Jupiter's. 
+In the other four cases, the mass (eccentricity) is increased or decreased by a factor of two, while the mass (eccentricity) is held at the nominal 
+value. In all cases, the perturbing giant is placed on a 5.2 AU orbit around a 1 $M_{\odot}$ star. The planetesimal disk extends from 2.2 to 3.8 
+AU, which covers the two most prominent mean motion resonances with the giant planet, the 2:1 at 3.27 AU and the 3:1 at 2.5 AU.The 
+planetesimal disk follows a minimum-mass solar nebula surface density profile \citep{1981PThPS..70...35H}
+
+\begin{equation}\label{eq:surf_den}
+	\Sigma = \Sigma_{0} r^{-\alpha},
+\end{equation}
+
+\noindent with $\alpha$ = 3/2 and $\Sigma_{0}$ = 10 g cm$^{-2}$. Planetesimals are given a bulk density of 2 g cm$^{-3}$ and a diameter of 
+300 km. This corresponds to a disk containing roughly 500,000 bodies. Each simulation is evolved for 5,000 years, which is about 400 Jupiter 
+orbits.
+
+The dynamical effects of secular forcing by the giant planet, along with  the effects of viscous stirring and gas drag on the planetesimals, are 
+built into the initial conditions. This is done by first calculating the equilibirum eccentricity $e_{eq}$ due to viscous stirring and gas drag as a 
+function of semimajor axis according to equation 12 of \citet{2002ApJ...581..666K}. Although {\sc ChaNGa} does not account for the effects of 
+gas drag on the planetesimals, the viscous stirring timescale is long compared to our integration time and should not cause the velocity 
+distribution to significantly evolve. The eccentricities of the bodies are drawn randomly from a Rayleigh distribution with a mode of $e_{eq}$, 
+while the inclinations are drawn from a similar distribution with a mode of $e_{eq}$/2 \citep{1993MNRAS.263..875I}. The longitude of perihelia 
+$\omega$ and the mean anomalies $M$ of the bodies are drawn from a uniform polar distribution.
+
+To account for the effects of secular forcing, the eccentricity vectors of the planetesimals are first decomposed into real and imaginary 
+components:
+
+\begin{equation}\label{eq:hk}
+	z = (h, k) = e \, exp(i \omega)
+\end{equation}
+
+\noindent and a forced component is added to $h$ according to equation \ref{eq:eforced} (where we have set $\omega_{g}$ = 0).
+
 \subsection{Time Stepping Scheme}\label{sec:timestep}
+
+For the purposes of the integrator, there are two relevant timescales in this system. The first is the orbital dynamical time $\sqrt{a^3/
+G M_{\odot}}$. All particles are placed on a fixed time step of $\Delta T$ = 0.01 yr. This is roughly 3\% of an orbital dynamical time at 
+the inner edge of the planetesimal disk. From numerical tests with {\sc ChaNGa}, we have found that this time step size preserves 
+the symplectic nature of the integration without being too computationally expensive. Although using $\Delta T$ = 0.01 yr keeps the 
+integration symplectic, we find that a small amount of artificial precession is produced. We reduce the base time step size by an additional 
+factor of 4 to the keep longitude of perihelia of planetesimals near the inner edge of the disk from drifting too far over the course of our 
+integrations.
+
+An additional timescale is set by the dynamical time of the planetesimals ($\sim 1/\sqrt{G \rho}$), which is about 45 minutes. To 
+resolve the base time step and the dynamical timescale of planetesimals simultaneously, we use a two-tiered time stepping scheme. 
+At the beginning of each time step, all bodies are placed on the orbital time step. A first pass of collision detection is then run in 
+which the radii of all bodies are inflated by a factor of 2.5. Any bodies with imminent collisions predicted using the inflated radii are 
+placed on a time step that is a factor of 16 smaller than the orbital time step. The purpose of two-tiered scheme is to properly resolve 
+the gravitational interactions between any bodies that undergo a close encounter. This prevents the coarser base time step from 
+reducing the effectiveness of gravitational focusing, while minimizing the additional computational expense.
 

### 2020-05-15 main.tex
Fill out text for figures 3 4 5 and 6. Add an additional figure showing hk state of bodies near edge of resonance

@@
 \begin{equation}\label{eq:res_so}
-	\frac{\delta a}{a} = \left( \frac{16}{3} \frac{\left| C_{r} \right|}{n} e^{\left| 2 p + q \right|} \right)^{1/2},
+	\frac{\delta a}{a} = \pm \left( \frac{16}{3} \frac{\left| C_{r} \right|}{n} e^{\left| 2 p + q \right|} \right)^{1/2},
 \end{equation}
@@
 \begin{equation}\label{eq:hk}
-	z = (h, k) = e \, exp(i \omega)
+	z = (h, ik) = e \, exp(i \omega)
 \end{equation}
@@
 
+All five simulations are evolved for 5,000 years, which is roughly 400 orbits of the perturbing planet.
+Because the effects of the mean motion resonances are not built into the initial conditions, the simulations must be run long enough for the distribution of orbital elements to reach equilibrium near the resonances before the collision rate is measured.
+The libration timescale, which describes how long the critical angle (and also the semimajor axis and eccentricity) of a planetesimal in resonance takes to undergo a full oscillation is given by
+
+\begin{equation}\label{eq:lib_time}
+	T_{lib} = \frac{2 \pi}{3 q^{2} C_{r} n e^{\left| 2p + q \right|}},
+\end{equation}
+
+\noindent for small-amplitude librations.
+For all five sets of initial conditions used, $T_{lib} \sim$ 1,000 - 2,000 years for the 3:1 and 2:1 resonances.
+For this reason, we allow each simulation to run for 2,000 years before we begin tracking any collision statistics.
+
+Add justification for the dust circularizing here as well.
+
+\subsection{Varying the Eccentricity}
+
+We begin by examining simulations $e_{lo}$, $n$ and $e_{hi}$.
+The positions of the planetesimals in the x-y plane after 5,000 years of integration is shown in figure \ref{fig:xy}.
+In all cases, the coordinate system is rotated so that the giant planet lies at $\theta = 0$ and the longitude of perihelion of the planet is shown by the dashed line.
+Resonances with the perturbing planet are visible via axisymmetric gaps.
+Upon close inspection of the last few simulation snapshots, these gaps appear to follow the planet in its orbit, rather than aligning themselves with the longitude of perihelion.
+A similar substructure reveals itself in \citet{2000Icar..143...45R} (see bottom panel of figure 3) and \citet{2016ApJ...818..159T} (figure 3).
+It is worth noting that \citet{2000Icar..143...45R} started with a completely cold planetesimal disk and a Jupiter mass planet on a circular, coplanar orbit.
+The presence of these features seems robust to the choice of initial conditions.
+
+The effects of the resonances become much more apparent in semimajor axis-eccentricity space, which is shown in figure \ref{fig:ae}.
+In all cases, the 3:1, 2:1 and 5:3 resonances are readily visible as 'spikes' in the eccentricity that bend slightly inward (due to the conservation of $E_{J}$).
+In the $e_{hi}$ simulation, features also appear near the 5:2, 7:3 and 5:3 resonances.
+The absence of these features from the $e_{low}$ simulation can be explained by the fact that the strength of a resonance scales with $e^{q}$ \citep{1994PhyD...77..289M}.
+
+Another important effect of the resonances is visible in figure \ref{fig:long_ph}, which shows the orientation of the longitude of perihelia of planetesimals in the disk.
+Inside of the resonances, orbits of planetesimals quickly precess and their orientations are effectively randomized.
+An important point to note is that this strong precession effect quickly disappears beyond the boundaries of the resonance.
+This turns out to be important to explain the nonaxisymmetric structure seen in figure \ref{fig:xy}, which will be addressed in more detail below.
+
+Next, we examine the statistics of collisions resolved in each of the simulations.
+The 3D positions and velocities of the two colliding bodies are recorded to a table at the moment of impact.
+From these quantities, we also derive the Keplerian orbital elements of a collision from these quantities.
+First, we examine the semimajor axis of the first particle participating in each collision.
+During a collision, the 'first' particle is defined as the more massive of the two.
+However, nearly all of the collisions happen between the initial, equal-mass planetesimals.
+In this case, the distinction is set by the collision search algorithm and is rather arbitrary.
+In all of the plots where we show collision statistics, we have verified that using the 'first' or 'second' collider does not qualitatively change any of the features.
+
+Figure \ref{fig:coll_hist_a} shows the semimajor axis distribution of the resolved collisions.
+We find that some of the features present in this and subsequent figures are highly sensitive to the number of bins and the location of the bin edges.
+For this reason, we construct a PDF of the collisions using a Kernel Density Estimate (KDE).
+We use the {\sc neighbors.KernelDensity} function from the {\sc sklearn} \citep{scikit-learn} package to construct our KDEs.
+For the kernel, we use a tophat function with a bandwidth of 0.02 AU.
+
+Near some of the resonances, there are noticeable suppressions or enhancements of the local collision rate.
+This contrasts with the findings of \citet{2000Icar..143...45R}, who simulated a similar setup and found no discernible features near the MMRs.
+We attribute the differences to  a more conservative timestepping criterion in our simulations.
+The most prominent features appear as an enhancement to the collision rate near the 2:1 MMR and a decrease near the 3:1 MMR.
+At higher forced eccentricities, features near the 5:2, 7:3 and 5:3 resonances are also visible, due to the steeper sensitivity of higher order resonances to eccentricity \citep{1994PhyD...77..289M}.
+
+We attribute the production of a bump vs a dip at certain resonances to changes in the gravitational focusing factor during two-body encounters.
+Closer to the star, the planetesimal disk starts off dynamically colder.
+Here, additional heating from the resonance acts to suppress the gravitational focusing cross section, which reduces the collision rate from the non-perturbed value.
+Further out in the disk, where the encounter velocity is already higher, the gravitational focusing cross section is already minimized.
+Any additional heating instead acts to simply increase the encounter rate between bodies, which enhances the collision rate.
+This explains the relative drop in the collision rate near the 3:1 MMR and the bumps that form near the 2:1 and 5:3 resonance.
+Although this could potentially serve as a useful diagnostic of the planetesimal size in a disk (because the mutual escape velocity sets how dynamically hot the bodies can get before gravitational focusing is suppressed), a direct measurement of the semimajor axes of the planetesimals is not possible.
+In addition, as will demonstrate next, collisions due to bodies in resonance end up having an insignificant effect on the final shape of the radial dust distribution.
+
+Operating under the assumption that any dust produced in a collision will couple to the gas and circularize on a short timescale, we use the cylindrical distance at which a collision occurs to predict the radial structure of the dust profile.
+This is shown in figure \ref{fig:coll_hist_r}, which was constructed in a similar way to figure \ref{fig:coll_hist_a}.
+Most strikingly, the bump that was present near the 2:1 resonance is no longer present in cylindrical distance space, although it suddenly appears again in the $e_{hi}$ simulation.
+The dip that is present near the 3:1 MMR also disappears and instead presents as a bump in the $e_{hi}$ case.
+To determine how the resonant bodies actually contribute to the radial collision profile, we excluded collisions that fall between $2.495 < a < 2.505$ AU (near the 3:1 resonance) and between $3.2 < a < 3.35$ AU (near the 2:1 resonance), which is shown by the orange curve.
+Qualitatively, none of the bump or dip features present are changed by making this exclusion.
+This suggests that the features near resonance seen in semimajor axis space become 'smeared out' in cylindrical distance space due to the large spread in eccentricity and orbital orientation.
+
+This also suggests that the features seen in figure \ref{fig:coll_hist_r} are being produced by bodies outside of resonance.
+To further understand this, we revisit the axisymmetric structure seen in figure \ref{fig:xy}.
+In figure \ref{fig:coll_polar_e}, we compare the radial collision profile to the polar structure seen in the $e_{low}$, $n$ and $e_{hi}$ simulations.
+In the lowest forced eccentricity case, the pileups near the edges of the resonances line up with the boundaries of the dip feature seen in the radial collision profile.
+This is especially prominent for the 2:1 resonance.
+As discussed previously, the pileups and gaps seen in polar coordinates follow the position of the giant planet in its orbit.
+
+Although the axisymmetric pileup of bodies near the edges of resonances has been seen previously \citep{2000Icar..143...45R, 2016ApJ...818..159T}, we could not find a satisfactory explanation for why it happens and will provide one here.
+As mentioned previously, the circulation frequency of the critical angle slows as one approaches the edge of the resonance from the outside.
+Following the pendulum analogy, this is equivalent to reaching the point where the pendulum becomes suspended in the vertical position.
+When the critical angle stays relatively stationary during an encounter, the net torque will drive the longitude of pericenter towards the point of conjunction \citep{1976ARA&A..14..215P}.
+This is the basic mechanism that causes isolated resonance to be stable.
+Inside of resonance, the critical angles librates about some value and this configuration is maintained.
+Just outside of resonance, however, the critical angle slowly drifts away, with the drift direction changing sign across the resonance.
+The net result of this is that bodies near the edge of the resonance experience a torque from that planet that temporarily aligns their pericenters with the orbital phase of the planet.
+After the encounter ends, differential rotation of the disk slowly destroys the configuration over part of an orbit.
+This explains why the concentration of planetesimals appears to 'follow' the the planet.
+
+In a disk with no secular forcing, this dynamical phenomena would produce a 'dip' near the center of the resonance and a 'bump' at each edge in cylindrical distance space.
+When a forced eccentricity is introduced, the edges of the resonance, where the pileups are located, are able to explore a wider range of radii.
+If the the aphelion distance of the inner edge and the perihelion distance of the outer edge cross, we should expect to see the central dip feature in the collision profile start to disappear.
+This is exactly what appears to be happening in the middle panel of figure \ref{fig:coll_polar_e}.
+As the forced eccentricity is increased further, a region forms at the center of the resonance where planetesimals from both sides of the resonance spend time (although not simultaneously).
+When this occurs, a bump feature forms in the collision profile at this region.
+This is apparent in the bottom panel of figure \ref{fig:coll_polar_e}.
+
 \begin{figure*}
@@
     \caption{Non axisymmetric gaps and rings appear near MMRs. More features appear at higher eccentricities. Gap features
-    at $\theta$ = 0 and $\theta = \pi$ follow the giant planet in its orbit.\label{fig:xy}}
+    at $\theta$ = 0 and $\theta = \pi$ follow the giant planet in its orbit. (Update this to show long of peri of Jupiter)\label{fig:xy}}
 \end{center}
@@
 
-\begin{figure*}
-\begin{center}
-    \includegraphics[width=\textwidth]{figures/bump_dip_diag.png}
-    \caption{The presence of a dip or bump near the resonances can be used to constrain the mass and eccentricity
-    of the perturbing planet. The color scale indicates the relative strength of the features, while the dashed lines
-    indicate boundaries in parameter space where a dip or a bump will be produced at the resonance.\label{fig:bump_dip_diag}}
-\end{center}
-\end{figure*}
-
 \subsection{Collision Rates}\label{sec:coll_rates}

### 2020-05-15 makeFig.py

@@ -110,7 +110,8 @@ s0_c = pb.load(s_c_files[0])
 s_e_files = np.array([path + 'hkshiftfull/hkshiftfull.ic']+ \
 	                  ns.natsorted(gl.glob(path + 'hkshiftfull/*.[0-9]*[0-9]')))
 s0_e = pb.load(s_e_files[0])
-s_c, s_e = pb.load(s_c_files[-1]), pb.load(s_e_files[-1])
+s_c, s_e = pb.load(s_c_files[-1]), pb.load(s_e_files[-2])
+print(s_e_files[-2])
 pl_c, pl_e = ko.orb_params(s_c), ko.orb_params(s_e)
 
 s_m1_files = np.array([path + 'm1/m1.ic']+ \
@@ -891,6 +892,71 @@ def make_coll_hist_r():
 
 	plt.savefig(file_str, format=fmt, bbox_inches='tight')
 
+def make_polar_hk_plots():
+	file_str = 'figures/polar_hk.' + fmt
+	if not clobber and os.path.exists(file_str):
+		return
+
+	a211, a212 = 3.16, 3.2
+	a211a, a212a = 3.38, 3.43
+
+	fig = plt.figure(figsize=(8, 8), constrained_layout=True)
+	gs = fig.add_gridspec(2, 2)
+
+	ax1 = fig.add_subplot(gs[0, :])
+	theta1, theta2 = np.pi-0.1, np.pi+0.1
+	theta1a, theta2a = 3*np.pi/2-0.1, 3*np.pi/2+0.1
+	pl = pl_e
+	x, y = pl['pos'][:,0], pl['pos'][:,1]
+	theta_jup = np.arctan2(y[0], x[0])
+	rad, theta = np.sqrt(x**2 + y**2), (np.arctan2(y, x) - theta_jup)%(2*np.pi)
+	mask_21 = np.logical_and(np.logical_and(pl['a'] > a211, pl['a'] < a212), \
+	                         np.logical_and(theta > theta1, theta < theta2))
+	mask_21a = np.logical_and(np.logical_and(pl['a'] > a211a, pl['a'] < a212a), \
+	                          np.logical_and(theta > theta1, theta < theta2))
+	mask_a21 = np.logical_and(np.logical_and(pl['a'] > a211, pl['a'] < a212), \
+	                         np.logical_and(theta > theta1a, theta < theta2a))
[…]

### 2020-05-16 main.tex
Outline rest of paper, add discussion of varying mass

@@
 In all cases, the coordinate system is rotated so that the giant planet lies at $\theta = 0$ and the longitude of perihelion of the planet is shown by the dashed line.
-Resonances with the perturbing planet are visible via axisymmetric gaps.
+Resonances with the perturbing planet are visible via nonaxisymmetric gaps.
 Upon close inspection of the last few simulation snapshots, these gaps appear to follow the planet in its orbit, rather than aligning themselves with the longitude of perihelion.
@@
 This also suggests that the features seen in figure \ref{fig:coll_hist_r} are being produced by bodies outside of resonance.
-To further understand this, we revisit the axisymmetric structure seen in figure \ref{fig:xy}.
+To further understand this, we revisit the nonaxisymmetric structure seen in figure \ref{fig:xy}.
 In figure \ref{fig:coll_polar_e}, we compare the radial collision profile to the polar structure seen in the $e_{low}$, $n$ and $e_{hi}$ simulations.
@@
 
-Although the axisymmetric pileup of bodies near the edges of resonances has been seen previously \citep{2000Icar..143...45R, 2016ApJ...818..159T}, we could not find a satisfactory explanation for why it happens and will provide one here.
+Although the nonaxisymmetric pileup of bodies near the edges of resonances has been seen previously \citep{2000Icar..143...45R, 2016ApJ...818..159T}, we could not find a satisfactory explanation for why it happens and will provide one here.
 As mentioned previously, the circulation frequency of the critical angle slows as one approaches the edge of the resonance from the outside.
@@
 In a disk with no secular forcing, this dynamical phenomena would produce a 'dip' near the center of the resonance and a 'bump' at each edge in cylindrical distance space.
-When a forced eccentricity is introduced, the edges of the resonance, where the pileups are located, are able to explore a wider range of radii.
-If the the aphelion distance of the inner edge and the perihelion distance of the outer edge cross, we should expect to see the central dip feature in the collision profile start to disappear.
+When a forced eccentricity is introduced, the edges of the resonance (indicated by the solid and dashed lines in figure \ref{fig:coll_polar_e}), where the pileups are located, begin to explore a wider range of radii.
+If the the aphelion distance of the inner edge and the perihelion distance of the outer edge cross, we should expect to see the central dip feature in the collision profile disappear.
 This is exactly what appears to be happening in the middle panel of figure \ref{fig:coll_polar_e}.
 As the forced eccentricity is increased further, a region forms at the center of the resonance where planetesimals from both sides of the resonance spend time (although not simultaneously).
-When this occurs, a bump feature forms in the collision profile at this region.
+When this occurs, a bump feature forms in the collision profile near the center of the resonance.
 This is apparent in the bottom panel of figure \ref{fig:coll_polar_e}.
+
+Although the same phenomenon appears to be happening near the 3:1 MMR, the pileups at the edges of the resonance are not as well defined.
+We attribute this to the longer synodic period, compared to the 2:1 MMR.
+In addition, a number of other nearby resonances, including the 7:2 (at 2.25 AU), the 10:3 (at 2.33 AU), the 8:3 (at 2.71 AU) and the 5:3 (at 2.82 AU) also likely are contributing to the collision profile in cylindrical distance space near the 3:1.
+The width of the 3:1 MMR is also much narrower than the 2:1, which means that any dip or bump features produced by it would require much higher resolution observations.
+For these reasons, we focus on the 2:1 MMR as the main diagnostic indicator.
+
+\subsection{Varying the Mass}
+
+The dynamical effects on the planetesimal disk of varying the mass of the planet of varying the mass are much simpler, in that it doing so does not affect the forced eccentricity.
+The width of a first order resonance scales with $m$ (see equation \ref{eq:res_so}), while the leading order terms in the resonant part of the disturbing function, which set the strength of the resonance, also scale as $m$.
+For the 2:1 MMR, this dynamics near resonance are equally sensitive to changes in eccentricity and mass.
+
+We show the polar structure of the $m_{low}$, $n$ and $m_{hi}$ simulations in figure \ref{fig:coll_polar_m} alongside the radial collision profile.
+In all three cases, the eccentricity of the perturbing planet is set to $e_{jup}$ and so the forced eccentricity does not change.
+Changes in the apocenter and pericenter distances of the edges of the resonances are entirely due to changes in the libration width of the resonances here.
+For the $m_{low}$ and $n$ simulations, the inner apocenter and outer pericenter distances near the 2:1 MMR are quite similar and no strong features appear in the collision profile near this region.
+For the $m_{hi}$ case, the edges of the resonances are sufficiently far apart to allow a gap near the center of the 2:1 resonance to appear in the collision profile.
+As seen in the previous section, the collision profile does not appear to follow the simple dip vs bump behavior.
+
+\section{Constraining the Mass and Eccentricity of the Planet}
+
+\subsection{Simulated ALMA Observations}
+
+Aaron's stuff goes here.
+Can the bumps and dips near the 2:1 MMR actually be resolved?
+What does the 3:1 resonance look like?
+Although we might not be able to use the 3:1 MMR to constrain mass or eccentricity, at least two resonances must be identified to determine where the 2:1 MMR actually is.
+
+\subsection{Implications of a Bump vs Dip at the 2:1 MMR}
+
+Show figure \ref{fig:bump_dip_diag} here.
+The presence of a dip or a bump at the 2:1 MMR can be used to determine which side of the eccentricity-mass plane we are on.
+Resonance strength scales with $m$ and $e$, so this will generally work better up and to the right on this diagram.
+Parameter combinations that lie between the dashed lines mean that the inner apo - outer peri distance is smaller than the resonance width.
+In this case, there won't really be much of a feature.
+
+\section{Discussion and Summary}
 
@@
 
-\subsection{Collision Rates}\label{sec:coll_rates}
-
-\subsection{Where Does the Dust End Up?}
-
-\section{Influence of Jupiter's Mass and Eccentricity on the Radial Dust Profile}
-
-\section{Observability of Dust} \label{sec:dust}
-
-Aaron's CASA images go here
-
-\section{Summary and Discussion} \label{sec:discuss}
+\begin{figure*}
+\begin{center}
+    \includegraphics[width=\textwidth]{figures/bump_dip_diag.png}
+    \caption{The presence of a dip or bump near the resonances can be used to constrain the mass and eccentricity
+    of the perturbing planet. The color scale indicates the relative strength of the features, while the dashed lines
+    indicate boundaries in parameter space where a dip or a bump will be produced at the resonance.\label{fig:bump_dip_diag}}
+\end{center}
+\end{figure*}
 

### 2020-05-17 main.tex
Clean up resonance labels in figures,, finish outlining paper

@@
 
-Add justification for the dust circularizing here as well.
-
 \subsection{Varying the Eccentricity}
@@
 
-Operating under the assumption that any dust produced in a collision will couple to the gas and circularize on a short timescale, we use the cylindrical distance at which a collision occurs to predict the radial structure of the dust profile.
-This is shown in figure \ref{fig:coll_hist_r}, which was constructed in a similar way to figure \ref{fig:coll_hist_a}.
+\subsection{Where Does the Dust End Up?}
+
+To construct a radial dust profile from the collision statistics, we begin by making the assumption that any dust generated by collisions is strongly coupled to the gas.
+For a dust grain larger than the mean free path of the gas particles, the timescale to damp its eccentricity is given by \citep{1976PThPh..56.1756A}
+
+\begin{equation}\label{eq:t_edamp}
+    t_{e, damp} = \frac{8 s \rho}{3 e C_{D} \rho_{g} v_{th}}.
+\end{equation}
+
+\noindent where $m$, $e$ and $s$ are the mass, eccentricity and radius of the dust grain.
+$C_{D}$ is a drag coefficient which is of order unity, $\rho_{g}$ is the local density of the gas and $v_{th}$ is its thermal speed.
+At 3 AU, the gaseous component of the solar nebula has a density of $4 \times 10^{-10}$ g cm$^{-3}$ and a typical thermal speed of $10^{5}$ cm s$^{-1}$ \citep{1981PThPS..70...35H}.
+For a 1 mm dust grain with a density of 1 g cm$^{-3}$ and an eccentricity of 0.05, the damping timescale is $4 \times 10^{-3}$ years.
+This is orders of magnitude smaller than the collision timescale, therefore we conclude that collisionally generated dust grains will immediately couple to the gas.
+
+Operating under this assumption, a map of the relative concentration of second-generation dust can be constructed from the cylindrical 
+distance at which the collisions occur.
+This is shown in figure \ref{fig:coll_hist_r}.
+Similar to figure \ref{fig:coll_hist_a}, we use a KDE with a bandwidth of 0.02 AU to assemble the collision locations into a radial distribution.
 Most strikingly, the bump that was present near the 2:1 resonance is no longer present in cylindrical distance space, although it suddenly appears again in the $e_{hi}$ simulation.
@@
 When the critical angle stays relatively stationary during an encounter, the net torque will drive the longitude of pericenter towards the point of conjunction \citep{1976ARA&A..14..215P}.
-This is the basic mechanism that causes isolated resonance to be stable.
+This is the basic mechanism that causes isolated resonances to be stable.
 Inside of resonance, the critical angles librates about some value and this configuration is maintained.
 Just outside of resonance, however, the critical angle slowly drifts away, with the drift direction changing sign across the resonance.
-The net result of this is that bodies near the edge of the resonance experience a torque from that planet that temporarily aligns their pericenters with the orbital phase of the planet.
+The net result of this is that bodies near the edge of the resonance experience a torque from that planet that temporarily drives their pericenters toward the current orbital position of the planet.
 After the encounter ends, differential rotation of the disk slowly destroys the configuration over part of an orbit.
@@
 
-In a disk with no secular forcing, this dynamical phenomena would produce a 'dip' near the center of the resonance and a 'bump' at each edge in cylindrical distance space.
+\citet{2016ApJ...818..159T} provides a different explanation for this phenomenon.
+Instead, the nonaxisymmetric structure is claimed to be a product of the path that a resonant test particle takes in a frame co-rotating with the planet (see figure 8.4 of \citet{2000ssd..book.....M}).
+This explanation, however, does not hold for a large collection of planetesimals, especially when there is no forced eccentricity.
+In such a case, the orbits of planetesimals near resonance would be randomly aligned, and the axisymmetric structure should become washed out.
+In the case with a perturbing planet planet on a circular orbit, this structure is still present (see figure 3 of \citet{2016ApJ...818..159T}).
+
+With no secular forcing, this dynamical phenomena would produce a 'dip' in the radial surface density profile near the center of the resonance and a 'bump' at each edge in cylindrical distance space.
 When a forced eccentricity is introduced, the edges of the resonance (indicated by the solid and dashed lines in figure \ref{fig:coll_polar_e}), where the pileups are located, begin to explore a wider range of radii.
@@
 We attribute this to the longer synodic period, compared to the 2:1 MMR.
-In addition, a number of other nearby resonances, including the 7:2 (at 2.25 AU), the 10:3 (at 2.33 AU), the 8:3 (at 2.71 AU) and the 5:3 (at 2.82 AU) also likely are contributing to the collision profile in cylindrical distance space near the 3:1.
+In addition, a number of other nearby resonances, including the 7:2 (at 2.25 AU), the 10:3 (at 2.33 AU), the 8:3 (at 2.71 AU) and the 5:2 (at 2.82 AU) also likely are contributing to the collision profile in cylindrical distance space near the 3:1.
 The width of the 3:1 MMR is also much narrower than the 2:1, which means that any dip or bump features produced by it would require much higher resolution observations.
 For these reasons, we focus on the 2:1 MMR as the main diagnostic indicator.
+
+\subsection{Observability of the Dust}
+
+Orange curves in figure \ref{fig:coll_polar_e} show the simulated ALMA flux profiles generated with {\sc CASA} \citep{2007ASPC..376..127M}.
+Have Aaron add in some more text here describing exactly how the profiles were created.
 
@@
 
-\subsection{Simulated ALMA Observations}
-
-Aaron's stuff goes here.
 Can the bumps and dips near the 2:1 MMR actually be resolved?
@@
 Although we might not be able to use the 3:1 MMR to constrain mass or eccentricity, at least two resonances must be identified to determine where the 2:1 MMR actually is.
-
-\subsection{Implications of a Bump vs Dip at the 2:1 MMR}
 
@@
 
-\section{Discussion and Summary}
+\section{Conclusions and Summary}
+
+Gap features take on a different structure for exterior resonances \citet{2016ApJ...818..159T}, which might make this bump vs dip diagnostic only useful for the interior 2:1 MMR.
 
@@
 
-\begin{figure*}
+\begin{figure}
 \begin{center}
-    \includegraphics[width=\textwidth]{figures/bump_dip_diag.png}
+    \includegraphics[width=0.5\textwidth]{figures/bump_dip_diag.png}
     \caption{The presence of a dip or bump near the resonances can be used to constrain the mass and eccentricity
@@
 \end{center}
-\end{figure*}
+\end{figure}
 

### 2020-05-17 makeFig.py

@@ -29,9 +29,9 @@ simV = u.AU/simT
 path = 'data/'
 
 # Resonances
-res_label = ['3:1', '2:1', '5:3']
-res_p = [1, 1, 3]
-res_q = [2, 1, 2]
+res_label = ['7:2', '10:3', '3:1', '8:3', '5:2', '2:1', '5:3']
+res_p = [2, 3, 1, 3, 2, 1, 3]
+res_q = [5, 7, 2, 4, 3, 1, 2]
 
 mc = 1
 m_jup = 9.54e-4
@@ -84,25 +84,28 @@ def res_width_jup(res_idx, ecc_jup=ecc_jup, m_jup=m_jup):
 	rw = ko.res_width(m_jup, mc, ecc, j1, j2)*dist
 	return rw
 
-def plot_res(axis, res=-1, vertical=True, show_widths=False):
+def plot_res(axis, res=-1, vertical=True, show_widths=False, all=False):
 	xmin, xmax = axis.get_xlim()
 	ymin, ymax = axis.get_ylim()
+	res_ind = range(len(res_dist))
+	if all == False:
+		res_ind = [2, 5]
 	if res == -1:
-		for idx, dist in enumerate(res_dist):
+		for idx, val in enumerate(res_ind):
 			if vertical:
-				axis.vlines(dist, ymin, ymax, linestyles='-')
-				axis.text(dist, ymax, res_label[idx])
+				axis.vlines(res_dist[val], ymin, ymax, linestyles='--', lw=0.5)
+				axis.text(res_dist[val], ymax, res_label[val], verticalalignment='top', fontsize=12)
 				if show_widths:
-					width = res_width_jup(idx)
-					axis.vlines(res_dist[idx] - width, ymin, ymax, linestyle='--')
-					axis.vlines(res_dist[idx] + width, ymin, ymax, linestyle='--')
+					width = res_width_jup(val)
+					axis.vlines(res_dist[val] - width, ymin, ymax, linestyle='-', lw=0.5)
+					axis.vlines(res_dist[val] + width, ymin, ymax, linestyle='-', lw=0.5)
 			else:
-				axis.hlines(dist, xmin, xmax, linestyles='-')
[…]

### 2020-05-20 main.tex
Add table summarizing simulations run, fill out most of summary and conclusions section

@@
 
+\begin{table}
+\begin{center}
+\caption{Summary of Simulations Run}
+\begin{tabular}{lllll} \hline \hline
+Name     & Mass of Planet [$M_{jup}$] & Eccentricity of Planet [$e_{jup}$] &  &  \\ \hline
+$e_{lo}$ & 1                      & 0.5                            &  &  \\
+nom      & 1                      & 1                              &  &  \\
+$e_{hi}$ & 1                      & 2                              &  &  \\
+$m_{lo}$ & 0.5                    & 1                              &  &  \\
+$m_{hi}$ & 2                      & 1                              &  &  \\ \hline
+\end{tabular}
+\label{tab:sims}
+\end{center}
+\end{table}
+
 \subsection{Time Stepping Scheme}\label{sec:timestep}
@@
 reducing the effectiveness of gravitational focusing, while minimizing the additional computational expense.
+
+Add a table describing the parameters of the 5 simulations that are run.
 
@@
 
-With no secular forcing, this dynamical phenomena would produce a 'dip' in the radial surface density profile near the center of the resonance and a 'bump' at each edge in cylindrical distance space.
-When a forced eccentricity is introduced, the edges of the resonance (indicated by the solid and dashed lines in figure \ref{fig:coll_polar_e}), where the pileups are located, begin to explore a wider range of radii.
-If the the aphelion distance of the inner edge and the perihelion distance of the outer edge cross, we should expect to see the central dip feature in the collision profile disappear.
+With no secular forcing, this dynamical phenomena would produce an underdensity in the radial surface density profile near the center of the resonance and an overdensity at each edge in cylindrical distance space.
+When a forced eccentricity is introduced, the edges of the resonance (indicated by the solid and dashed lines in figure \ref{fig:coll_polar_e}), where the pileups are located, begin to explore a wider range of radii over the course of a single orbit.
+If the the aphelion distance of the inner edge becomes comparable to the perihelion distance of the outer edge, the overdense regions on each side of the resonance meet and we should expect to see the central dip feature in the collision profile disappear.
 This is exactly what appears to be happening in the middle panel of figure \ref{fig:coll_polar_e}.
@@
 The width of the 3:1 MMR is also much narrower than the 2:1, which means that any dip or bump features produced by it would require much higher resolution observations.
-For these reasons, we focus on the 2:1 MMR as the main diagnostic indicator.
+For these reasons, we will focus on the 2:1 MMR as the main diagnostic indicator.
 
@@
 
-The dynamical effects on the planetesimal disk of varying the mass of the planet of varying the mass are much simpler, in that it doing so does not affect the forced eccentricity.
+The dynamical effects of varying the mass of the planet are somewhat simpler, in that doing so does not affect the forced eccentricity of the planetesimal disk.
+Instead, only the width of the resonances changes.
 The width of a first order resonance scales with $m$ (see equation \ref{eq:res_so}), while the leading order terms in the resonant part of the disturbing function, which set the strength of the resonance, also scale as $m$.
-For the 2:1 MMR, this dynamics near resonance are equally sensitive to changes in eccentricity and mass.
+For the 2:1 MMR, the dynamics near the resonance are equally sensitive to changes in eccentricity and mass.
 
 We show the polar structure of the $m_{low}$, $n$ and $m_{hi}$ simulations in figure \ref{fig:coll_polar_m} alongside the radial collision profile.
-In all three cases, the eccentricity of the perturbing planet is set to $e_{jup}$ and so the forced eccentricity does not change.
-Changes in the apocenter and pericenter distances of the edges of the resonances are entirely due to changes in the libration width of the resonances here.
+In all three cases, the eccentricity of the perturbing planet is set to $e_{jup}$.
+Changes in the apocenter and pericenter distances of the edges of the resonances are entirely due to changes in the libration width here.
 For the $m_{low}$ and $n$ simulations, the inner apocenter and outer pericenter distances near the 2:1 MMR are quite similar and no strong features appear in the collision profile near this region.
 For the $m_{hi}$ case, the edges of the resonances are sufficiently far apart to allow a gap near the center of the 2:1 resonance to appear in the collision profile.
-As seen in the previous section, the collision profile does not appear to follow the simple dip vs bump behavior.
 
@@
 
-Can the bumps and dips near the 2:1 MMR actually be resolved?
-What does the 3:1 resonance look like?
-Although we might not be able to use the 3:1 MMR to constrain mass or eccentricity, at least two resonances must be identified to determine where the 2:1 MMR actually is.
+The simple 'bump' vs 'dip' structure that we expect to reveal itself in the dust emission from colliding planetesimals in near-resonance with a giant planet could potentially be used to place constraints on the mass and eccentricity of the planet.
+Near the 2:1 MMR, the central dip feature is only produced when bodies at the edges of the resonance stay sufficiently separated in cylindrical distance over the course of an orbit.
+This is achieved when either the resonance width is large and the forced eccentricity is small.
+Conversely, the bump feature is produced when there is a sufficiently large amount of overlap between the apocenters and pericenters of the inner and outer edges of the resonance, respectively.
+This is achieved when the resonance is narrow and the forced eccentricity is large.
 
-Show figure \ref{fig:bump_dip_diag} here.
-The presence of a dip or a bump at the 2:1 MMR can be used to determine which side of the eccentricity-mass plane we are on.
-Resonance strength scales with $m$ and $e$, so this will generally work better up and to the right on this diagram.
-Parameter combinations that lie between the dashed lines mean that the inner apo - outer peri distance is smaller than the resonance width.
-In this case, there won't really be much of a feature.
+In figure \ref{fig:bump_dip_diag}, we show the constraints that the presence of a bump or a dip places on the values of $(m_{g}, e_{g})$.
+A dip is produced by sufficiently low eccentricity and high mass planets, while a bump is produced by a low mass or high eccentricity planet.
+The parameter choices for the five simulations presented in the previous section are shown by the black dots.
+Between the two dashed lines, the overlap between the aphelion and perihelion distances of the inner and outer edges of the resonance is smaller than the width of the resonance.
+In this region, the overdense regions on each side of the resonance spend roughly equal amounts of time at all possible cylindrical distances, and no strong feature appears in the collision profile.
 
-\section{Conclusions and Summary}
+Because the strength of the 2:1 resonance scales with $e_{g}$ and  $m_{g}$, a sufficiently low mass and low eccentricity planet will not induce enough of a perturbation in the planetesimal disk to produce a detectable bump or dip feature.
+The colored contours in figure \ref{fig:bump_dip_diag} indicate the relative strength of the resonance as these quantities are varied.
+Although the resonance strength is equally sensitive to changes in mass and eccentricity, the peri - apocenter overlap of the resonance edges is more sensitive to changes in eccentricity.
+This is also consistent with what was seen in figure \ref{fig:coll_polar_m}, where changing $m_{g}$ by a factor of 4 produced very minimal changes to the resulting dust profile.
 
-Gap features take on a different structure for exterior resonances \citet{2016ApJ...818..159T}, which might make this bump vs dip diagnostic only useful for the interior 2:1 MMR.
+In order to actually identify the 2:1 MMR in the dust emission, at least one other resonance must be visible.
+Assuming the gravitational field in the disk is near-Keplerian, the distance ratios between two features can be used to determine period ratios, which can be used to confirm whether the features seen are indeed resonances.
+Although the 3:1 MMR does not appear to follow the simple bump vs dip dichotomy described above, its presence should be marginally detectable in all of the cases shown above.
+
+\section{Summary and Conclusions}
+
+In this work, we have shown that mean-motion resonances with a perturbing planet produce significant variations in the collision rate of a planetesimal disk.
+In contrast to \citet{2000Icar..143...45R}, we find that the more prominent interior MMRs, including the 2:1, 3:1 and 5:3, all produce structures in the collision profile as a function of semimajor axis.
+Furthermore, we found a series of distinctly different features that appear when collisions are grouped by cylindrical distance from the central star.
+If enough gas from the protoplanetary disk is still present, dust generated from planetesimals collisions will immediately couple to it and fall onto a circular orbit.
+In this case, variations in the radial collision profile will match the radial dust emission profile, which can potentially be observed in the sub-mm.
+
+Near the interior 2:1 MMR, we find that a distinct bump or dip feature is generated in the dust profile.
+The presence of either of these structures can used to constrain the mass and eccentricity of the perturbing planet.
+For a high mass, low eccentricity planet, a dip will form in the dust profile because the edges of the resonance, where many collisions occur, stay sufficiently separated.
+If the planet has a low enough mass (which shrinks the size of the resonance) or is sufficiently eccentric (which decreases the separation between the apocenter and pericenter distances of the inner and outer edges of the resonance), a bump will instead form.
+We tested this hypothesis for five different combinations of the planet's mass and eccentricity and found that this diagnostic is useful as long as the planet is sufficiently far from the dividing line in parameter space.
+This diagnostic is more clear for massive, eccentric planets, because the strength of the resonant perturbations scale linearly with both of these quantities.
+
+The results presented here appear to be broadly consistent with \citet{2016ApJ...818..159T}, which used collisionless, massless test particles to model a planetesimal disk perturbed by a planet.
+In their case, a dip feature appeared in the azimuthally averaged surface density profile was seen, although they did use a high enough eccentricity planet in any of their simulations to produce a bump.
+Another thing to note is that the gap morphology seen by \citet{2016ApJ...818..159T} was markedly different for the 2:1 exterior MMR.
+Whether this would alter the radial collision profile for the exterior, rather then the interior 2:1 resonance, is not immediately clear.
+Given that the solid surface density diminishes with distance ($\sim r^{3/2}$ for the MMSN \citep{1981PThPS..70...35H}), exterior resonances may not be quite as useful for this type of measurement.
+
+Our conclusion that the bodies in resonance do not significantly contribute to the radial collision profile (see figure \ref{fig:coll_hist_a}) does appear support the simplifying assumptions made by \citet{2017ApJ...850..103B}, in which dynamically cold, low eccentricity regions of test particles were assumed to trace the regions of second-generation dust production.
+Besides the corotation regions, nonaxisymmetric structure near resonances does not appear to be present in \citet{2017ApJ...850..103B}.
+This makes it difficult to determine whether a simpler model in which test particles 'trace' the collision rate can be used to generate a dust profile.
+
+Resolving these structures is really pushing the capabilities of observatories like ALMA. Mention NG-VLA. Also {\sc Frankenstein} \citep{2020arXiv200507709J}.
 

### 2020-05-20 main.tex
Finalize draft

@@
-\documentclass[onecolumn]{aastex63}
+\documentclass[twocolumn]{aastex63}
 \usepackage{natbib}
@@
 
+\author{Thomas R. Quinn}
+\affiliation{Astronomy Department, University of Washington, Seattle, WA 98195}
+
 \author{Aaron C. Boley}
@@
 
-\author{Thomas R. Quinn}
-\affiliation{Astronomy Department, University of Washington, Seattle, WA 98195}
-
 \begin{abstract}
-In circumstellar disks, collisional grinding of planetesimals produces second-generation dust, which can be observed through thermal 
+In circumstellar disks, collisional grinding of planetesimals produces second-generation dust which can be observed through thermal 
 emission. While it remains unclear when second-generation dust first becomes a major component of the total dust content, the presence of 
@@
 different dynamics compared with planetesimals when in the presence of gas, and as such, the collisional evolution of planetesimals could 
-create dusty disk structures that would not exist otherwise. In particular, mean motion resonances (MMRs) are extremely nonlinear and could 
-drive disk morphologies. We use a direct N-body model to track collision rates in a planetesimal disk under the gravitational influence of an 
-external giant planet. We show that a perturbing planet can produce significant variations in the collision rate of planetesimals near the 
-MMRs and we explore how the mass and eccentricity of the perturbing planet alters this structure. Finally, we use the CASA image simulator to 
-predict what the dust emission sturcture should look like with ALMA and the NG-VLA. Although the dust structure produced by MMRs cannot 
-be used to directly measure the properties of the perturbing planet, we show that it can be used to place constraints on its mass and 
-eccentricity.
+create dusty disk structures that would not exist otherwise. Previous studies have shown that morphological differences in the collisional dust 
+corotating with a giant planet can be used to determine whether the planet's eccentricity is large or small. Going further, we investigate the 
+production of second-generation dust near prominent mean-motion resonances with the planet using N-body simulations that directly resolve 
+collisions between planetesimals. We find that a distinct over- or under-density in the dust emission is produced at the interior 2:1 mean motion 
+resonance, depending on the mass and eccentricity of the planet. The presence of one of these two features can be used to place simultaneous 
+upper or lower limits on the mass and eccentricity of the perturbing body.
 \end{abstract}
@@
 
-Recent observations of circumstellar disks by ALMA have revealed a rich variety of substructure in the millimeter wavelength
-contiunuum emission. Features such as gaps and asymmetries 
-\citep{2015ApJ...808L...3A, 2016Sci...353.1519P, PhysRevLett.117.251101, 2016ApJ...820L..40A, 2016Natur.535..258C} in the 
-emission provide diagnostics for the physical processes that drive the evolution of the disks. At these wavelengths, much of this light 
-is produced by second-generation debris generated through collisional grinding of planetesimals
-\citep[see][]{2008ARA&A..46..339W}.
-
-In some cases, these gap features are argued to be an indicator for the presence of a giant planet, either embedded in the disk 
-\citep{2015MNRAS.453L..73D} or orbiting externally. An giant perturber can influence the structure of the dust emission in a number 
-of ways. A misaligned giant planet can produce nonaxisymmetric features such as warps \citep{2001A&A...370..447A}. Highly 
-eccentric perturbers can produce even more complicated structures through secular perturbations \citep{2014MNRAS.443.2541P, 
-2015MNRAS.448.3679P}. Mean motion resonances (MMRs) have been shown to open gaps as well
+Recent observations of circumstellar disks by ALMA have revealed a rich variety of substructure in the millimeter contiunuum emission. Features 
+such as gaps and asymmetries 
+\citep{2015ApJ...808L...3A, 2016Sci...353.1519P, PhysRevLett.117.251101, 2016ApJ...820L..40A, 2016Natur.535..258C} in the emission provide 
+diagnostics for the physical processes that drive the evolution of the disks. In some cases, these gap features are argued to be an indicator for the 
+presence of a giant planet, either embedded in the disk \citep{2015MNRAS.453L..73D} or orbiting externally. A giant perturber can influence the 
+structure of the continuum emission in a number of ways. A misaligned giant planet can produce nonaxisymmetric features such as warps 
+\citep{2001A&A...370..447A}. Highly eccentric perturbers can produce even more complicated structures through secular perturbations 
+\citep{2014MNRAS.443.2541P, 2015MNRAS.448.3679P}. Mean motion resonances (MMRs) have been shown to open gaps as well 
 \citep{2015ApJ...798...83N, 2016ApJ...818..159T, 2018ApJ...857....3T}.
 
-Also mention \citet{2020A&A...635A..10S}, looked at dust trapping in resonances with terrestrial SS planets. Also mention 
-\citet{2020arXiv200408736G}, detection of a planetesimal collision around Fomalhut.
+Collisions between planetesimals are thought to be a significant source of dust for many young circumstellar disks 
+\citep[see][]{2008ARA&A..46..339W}. An expanding debris cloud from a planetesimal collision was recently detected through scattered light in the 
+Fomalhut system \citep{2020PNAS..117.9712G}. Although some amount of primordial dust is likely still present during the planet formation process, 
+ongoing collisions between small bodies will augment this and could be used to trace the underlying dynamical activity of the planetesimals. 
+\citet{2013ApJ...777L..31D} showed that collisional dust generated near the gap formed by a giant planet in a planetesimal disk should produce a 
+distinctly observable marker that could be used to infer the presence of the planet. In a followup study, it was found that morphological differences in 
+the dust emission could be used to distinguish between a low and high eccentricity planet \citep{2016ApJ...820...29D}.
 
-The dynamics governing the motion of bodies near MMRs is extremely nonlinear, as is determining what the collision rates between 
-planetesimals should look like in these regions. For a collection of bodies massive enough to experience the effects of gravitational 
-focusing, a large eccentricity dispersion tends to reduce the probability of collision, while enhancements in surface density tends to 
-increase it. Due to conservation of the Jacobi energy, MMRs simultaneously enhance the local eccentricity dispersion and also 
-enhance the surface density adjacent to the resonance \citep{2000Icar..143...45R, 2017ApJ...850..103B}.
+Although more difficult to spatially resolve, substructure due to mean-motion resonances (MMRs) with a giant planet may hold additional clues which 
+could be used to constrain the properties of the planet.  The width of a resonance is set by both the mass of the perturbing planet, along with the 
+unperturbed eccentricity of the planetesimals, which is in turn set by the eccentricity of the planet through secular forcing. Therefore, the structure of 
+second generation dust produced near MMRs may hold information about both the mass and eccentricity of the planet.
 
-Because the second generation dust production is driven by the planetesimal collision rate, it is crucial to understand how the 
-dynamics that drive collisions works. In particular, it is not obvious how to link the readily observable thermal emission from dust in 
-protoplanetary disks to the presence of a perturbing giant planet. Due to its nonlinearity, this problem is best studied with N-body 
-simulations. Unfortunately, collision detection in an N-body simulation is extremely computationally expensive. So far, studies of 
-planetesimal dynamics near MMRs have involved either collisionless test particles \citep{2017ApJ...850..103B, 2016ApJ...818..159T, 
-2018ApJ...857....3T} or severely limited integration times \citep{2000Icar..143...45R}.
+The dynamics governing the motion of bodies near MMRs is extremely nonlinear, as is determining what the collision rates between planetesimals 
+should look like in these regions. For a collection of bodies massive enough to experience the effects of gravitational focusing, a large eccentricity 
+dispersion tends to reduce the probability of collision, while enhancements in surface density tends to increase it. Due to conservation of the Jacobi 
+energy, MMRs simultaneously enhance the local eccentricity dispersion and also enhance the surface density adjacent to the resonance 
+\citep{2000Icar..143...45R, 2017ApJ...850..103B}. Unfortunately, collision detection in an N-body simulation is extremely computationally expensive. 
+So far, studies of planetesimal dynamics near MMRs have involved either collisionless test particles 
+\citep{2017ApJ...850..103B, 2016ApJ...818..159T, 2018ApJ...857....3T} or severely limited integration times \citep{2000Icar..143...45R}.
 
@@
 explore the collision rate structure of the planetesimal disk in the vicinity of mean motion resonances. In particular, we would like to 
-determine: 1.
-whether MMRs leave a detectable signature in the collisionally-generated dust.
-2.
-If these signatures can be used to determine or constrain the orbital properties of the perturbing planet.
+determine: 1. whether MMRs leave a detectable signature in the collisionally-generated dust. 2. If these signatures can be used to determine or 
+constrain the orbital properties of the perturbing planet.
 
-This work is organized in the following way: In section \ref{sec:dynamics}, we provide an overview of the relevant dynamics that drive 
-the evolution of a planetesimal disk under the gravitational influence of an external perturber.
-We also highlight the shortcomings of secular theory in trying to predict the radial collision rate and motivate the need for N-body simulations with massive, collisional particles.
-In section \ref{sec:sims} we describe the N-body code that we use and detail the initial conditions that are used for two simulations: one in which the perturber is on a circular orbit and another in which the perturber is given a mildly eccentric orbit.
-Section \ref{sec:results} presents the results of the two simulations.
-Next, we generate dust emission maps in section \ref{sec:dust}, under the assumption that collisionally-generated dust will quickly couple with the gas and circularize, and show that radial structure is produced in the vicinity of the MMRs.
-Using the dust emission maps, section \ref{sec:fitting} explores the feasibility of measuring properties of the perturbing planet from the MMR features in the dust.
-We then conclude in section \ref{sec:discuss}.
+This work is organized in the following way: In section \ref{sec:dynamics}, we provide an overview of the relevant dynamics that drive the evolution 
+of a planetesimal disk under the gravitational influence of an external perturber. In section \ref{sec:sims} we provide an overview of the N-body code 
+that we use and describe the initial conditions that are used for five simulations in which a perturbing giant planet is given is given various masses 
+and eccentricities. Section \ref{sec:results} presents the results of these five simulations and we use the collision statistics to generate synthetic dust 
+emission profiles that would be detected with observing facilities like ALMA. Next, we show in section \ref{sec:constrain} that a characteristic bump 
+or dip feature appears in the dust emission near the interior 2:1 MMR, the presence of which depends on the mass and eccentricity of the perturbing 
+planet. We discuss the potential of using this feature to place and upper or lower on the mass and eccentricity of the planet and conclude in section 
+\ref{sec:conclusions}.
 
-\section{Overview of Relavant Dynamics} \label{sec:dynamics}
+\section{Overview of Relevant Dynamics} \label{sec:dynamics}
 
@@
 
-\noindent where n, a and e are the mean motion, semimajor axis and eccentricity of the unperturbed body.
-$C_{r}$ is a constant defined by $m'/m_{c} n \alpha f_{d}(\alpha)$, where $\alpha$ = $a/a'$ and $f_{d}$ is the resonant part of the disturbing function.
-For an interior second-order resonance,
+\noindent where n, a and e are the mean motion, semimajor axis and eccentricity of the unperturbed body. $C_{r}$ is a constant defined by 
+$m'/m_{c} n \alpha f_{d}(\alpha)$, where $\alpha$ = $a/a'$ and $f_{d}$ is the resonant part of the disturbing function. For an interior second-order 
+resonance,
 
@@
 
+\begin{table}
+\begin{center}
+\caption{Summary of Simulations Run}
+\begin{tabular}{lllll} \hline \hline
+Name     & Mass of Planet & Eccentricity of Planet &  &  \\ \hline
+e1m2 & 1.0 $M_{jup}$                     & 0.5 $e_{jup}$                            &  &  \\
+e2m2      & 1.0 $M_{jup}$                     & 1.0 $e_{jup}$                             &  &  \\
+e3m2 & 1.0 $M_{jup}$                     & 2.0 $e_{jup}$                             &  &  \\
+e2m1 & 0.5 $M_{jup}$                   & 1.0 $e_{jup}$                             &  &  \\
+e2m3 & 2.0 $M_{jup}$                     & 1.0 $e_{jup}$                             &  &  \\ \hline
+\end{tabular}
+\label{tab:sims}
+\end{center}
+\end{table}
+
 \subsection{Initial Conditions}\label{sec:ics}
@@
 
-\begin{table}
-\begin{center}
-\caption{Summary of Simulations Run}
-\begin{tabular}{lllll} \hline \hline
-Name     & Mass of Planet [$M_{jup}$] & Eccentricity of Planet [$e_{jup}$] &  &  \\ \hline
-$e_{lo}$ & 1                      & 0.5                            &  &  \\
-nom      & 1                      & 1                              &  &  \\
-$e_{hi}$ & 1                      & 2                              &  &  \\
-$m_{lo}$ & 0.5                    & 1                              &  &  \\
-$m_{hi}$ & 2                      & 1                              &  &  \\ \hline
-\end{tabular}
-\label{tab:sims}
-\end{center}
-\end{table}
-
 \subsection{Time Stepping Scheme}\label{sec:timestep}
@@
 resolve the base time step and the dynamical timescale of planetesimals simultaneously, we use a two-tiered time stepping scheme. 
-At the beginning of each time step, all bodies are placed on the orbital time step. A first pass of collision detection is then run in 
+To start, all bodies are placed on the orbital time step. A first pass of collision detection is then run in 
 which the radii of all bodies are inflated by a factor of 2.5. Any bodies with imminent collisions predicted using the inflated radii are 
@@
 
-Add a table describing the parameters of the 5 simulations that are run.
-
-\section{Results} \label{sec:results}
-
-All five simulations are evolved for 5,000 years, which is roughly 400 orbits of the perturbing planet.
-Because the effects of the mean motion resonances are not built into the initial conditions, the simulations must be run long enough for the distribution of orbital elements to reach equilibrium near the resonances before the collision rate is measured.
-The libration timescale, which describes how long the critical angle (and also the semimajor axis and eccentricity) of a planetesimal in resonance takes to undergo a full oscillation is given by
-
-\begin{equation}\label{eq:lib_time}
-	T_{lib} = \frac{2 \pi}{3 q^{2} C_{r} n e^{\left| 2p + q \right|}},
-\end{equation}
-
-\noindent for small-amplitude librations.
-For all five sets of initial conditions used, $T_{lib} \sim$ 1,000 - 2,000 years for the 3:1 and 2:1 resonances.
-For this reason, we allow each simulation to run for 2,000 years before we begin tracking any collision statistics.
-
-\subsection{Varying the Eccentricity}
-
-We begin by examining simulations $e_{lo}$, $n$ and $e_{hi}$.
-The positions of the planetesimals in the x-y plane after 5,000 years of integration is shown in figure \ref{fig:xy}.
-In all cases, the coordinate system is rotated so that the giant planet lies at $\theta = 0$ and the longitude of perihelion of the planet is shown by the dashed line.
-Resonances with the perturbing planet are visible via nonaxisymmetric gaps.
-Upon close inspection of the last few simulation snapshots, these gaps appear to follow the planet in its orbit, rather than aligning themselves with the longitude of perihelion.
-A similar substructure reveals itself in \citet{2000Icar..143...45R} (see bottom panel of figure 3) and \citet{2016ApJ...818..159T} (figure 3).
-It is worth noting that \citet{2000Icar..143...45R} started with a completely cold planetesimal disk and a Jupiter mass planet on a circular, coplanar orbit.
-The presence of these features seems robust to the choice of initial conditions.
-
-The effects of the resonances become much more apparent in semimajor axis-eccentricity space, which is shown in figure \ref{fig:ae}.
-In all cases, the 3:1, 2:1 and 5:3 resonances are readily visible as 'spikes' in the eccentricity that bend slightly inward (due to the conservation of $E_{J}$).
-In the $e_{hi}$ simulation, features also appear near the 5:2, 7:3 and 5:3 resonances.
-The absence of these features from the $e_{low}$ simulation can be explained by the fact that the strength of a resonance scales with $e^{q}$ \citep{1994PhyD...77..289M}.
-
-Another important effect of the resonances is visible in figure \ref{fig:long_ph}, which shows the orientation of the longitude of perihelia of planetesimals in the disk.
-Inside of the resonances, orbits of planetesimals quickly precess and their orientations are effectively randomized.
-An important point to note is that this strong precession effect quickly disappears beyond the boundaries of the resonance.
-This turns out to be important to explain the nonaxisymmetric structure seen in figure \ref{fig:xy}, which will be addressed in more detail below.
-
-Next, we examine the statistics of collisions resolved in each of the simulations.
-The 3D positions and velocities of the two colliding bodies are recorded to a table at the moment of impact.
-From these quantities, we also derive the Keplerian orbital elements of a collision from these quantities.
-First, we examine the semimajor axis of the first particle participating in each collision.
-During a collision, the 'first' particle is defined as the more massive of the two.
-However, nearly all of the collisions happen between the initial, equal-mass planetesimals.
-In this case, the distinction is set by the collision search algorithm and is rather arbitrary.
-In all of the plots where we show collision statistics, we have verified that using the 'first' or 'second' collider does not qualitatively change any of the features.
-
-Figure \ref{fig:coll_hist_a} shows the semimajor axis distribution of the resolved collisions.
-We find that some of the features present in this and subsequent figures are highly sensitive to the number of bins and the location of the bin edges.
-For this reason, we construct a PDF of the collisions using a Kernel Density Estimate (KDE).
-We use the {\sc neighbors.KernelDensity} function from the {\sc sklearn} \citep{scikit-learn} package to construct our KDEs.
-For the kernel, we use a tophat function with a bandwidth of 0.02 AU.
-
-Near some of the resonances, there are noticeable suppressions or enhancements of the local collision rate.
-This contrasts with the findings of \citet{2000Icar..143...45R}, who simulated a similar setup and found no discernible features near the MMRs.
-We attribute the differences to  a more conservative timestepping criterion in our simulations.
-The most prominent features appear as an enhancement to the collision rate near the 2:1 MMR and a decrease near the 3:1 MMR.
-At higher forced eccentricities, features near the 5:2, 7:3 and 5:3 resonances are also visible, due to the steeper sensitivity of higher order resonances to eccentricity \citep{1994PhyD...77..289M}.
-
-We attribute the production of a bump vs a dip at certain resonances to changes in the gravitational focusing factor during two-body encounters.
-Closer to the star, the planetesimal disk starts off dynamically colder.
-Here, additional heating from the resonance acts to suppress the gravitational focusing cross section, which reduces the collision rate from the non-perturbed value.
-Further out in the disk, where the encounter velocity is already higher, the gravitational focusing cross section is already minimized.
-Any additional heating instead acts to simply increase the encounter rate between bodies, which enhances the collision rate.
-This explains the relative drop in the collision rate near the 3:1 MMR and the bumps that form near the 2:1 and 5:3 resonance.
-Although this could potentially serve as a useful diagnostic of the planetesimal size in a disk (because the mutual escape velocity sets how dynamically hot the bodies can get before gravitational focusing is suppressed), a direct measurement of the semimajor axes of the planetesimals is not possible.
-In addition, as will demonstrate next, collisions due to bodies in resonance end up having an insignificant effect on the final shape of the radial dust distribution.
-
-\subsection{Where Does the Dust End Up?}
-
-To construct a radial dust profile from the collision statistics, we begin by making the assumption that any dust generated by collisions is strongly coupled to the gas.
-For a dust grain larger than the mean free path of the gas particles, the timescale to damp its eccentricity is given by \citep{1976PThPh..56.1756A}
-
-\begin{equation}\label{eq:t_edamp}
-    t_{e, damp} = \frac{8 s \rho}{3 e C_{D} \rho_{g} v_{th}}.
-\end{equation}
-
-\noindent where $m$, $e$ and $s$ are the mass, eccentricity and radius of the dust grain.
-$C_{D}$ is a drag coefficient which is of order unity, $\rho_{g}$ is the local density of the gas and $v_{th}$ is its thermal speed.
-At 3 AU, the gaseous component of the solar nebula has a density of $4 \times 10^{-10}$ g cm$^{-3}$ and a typical thermal speed of $10^{5}$ cm s$^{-1}$ \citep{1981PThPS..70...35H}.
-For a 1 mm dust grain with a density of 1 g cm$^{-3}$ and an eccentricity of 0.05, the damping timescale is $4 \times 10^{-3}$ years.
-This is orders of magnitude smaller than the collision timescale, therefore we conclude that collisionally generated dust grains will immediately couple to the gas.
-
-Operating under this assumption, a map of the relative concentration of second-generation dust can be constructed from the cylindrical 
-distance at which the collisions occur.
-This is shown in figure \ref{fig:coll_hist_r}.
-Similar to figure \ref{fig:coll_hist_a}, we use a KDE with a bandwidth of 0.02 AU to assemble the collision locations into a radial distribution.
-Most strikingly, the bump that was present near the 2:1 resonance is no longer present in cylindrical distance space, although it suddenly appears again in the $e_{hi}$ simulation.
-The dip that is present near the 3:1 MMR also disappears and instead presents as a bump in the $e_{hi}$ case.
-To determine how the resonant bodies actually contribute to the radial collision profile, we excluded collisions that fall between $2.495 < a < 2.505$ AU (near the 3:1 resonance) and between $3.2 < a < 3.35$ AU (near the 2:1 resonance), which is shown by the orange curve.
-Qualitatively, none of the bump or dip features present are changed by making this exclusion.
-This suggests that the features near resonance seen in semimajor axis space become 'smeared out' in cylindrical distance space due to the large spread in eccentricity and orbital orientation.
-
-This also suggests that the features seen in figure \ref{fig:coll_hist_r} are being produced by bodies outside of resonance.
-To further understand this, we revisit the nonaxisymmetric structure seen in figure \ref{fig:xy}.
-In figure \ref{fig:coll_polar_e}, we compare the radial collision profile to the polar structure seen in the $e_{low}$, $n$ and $e_{hi}$ simulations.
-In the lowest forced eccentricity case, the pileups near the edges of the resonances line up with the boundaries of the dip feature seen in the radial collision profile.
-This is especially prominent for the 2:1 resonance.
-As discussed previously, the pileups and gaps seen in polar coordinates follow the position of the giant planet in its orbit.
-
-Although the nonaxisymmetric pileup of bodies near the edges of resonances has been seen previously \citep{2000Icar..143...45R, 2016ApJ...818..159T}, we could not find a satisfactory explanation for why it happens and will provide one here.
-As mentioned previously, the circulation frequency of the critical angle slows as one approaches the edge of the resonance from the outside.
-Following the pendulum analogy, this is equivalent to reaching the point where the pendulum becomes suspended in the vertical position.
-When the critical angle stays relatively stationary during an encounter, the net torque will drive the longitude of pericenter towards the point of conjunction \citep{1976ARA&A..14..215P}.
-This is the basic mechanism that causes isolated resonances to be stable.
-Inside of resonance, the critical angles librates about some value and this configuration is maintained.
-Just outside of resonance, however, the critical angle slowly drifts away, with the drift direction changing sign across the resonance.
-The net result of this is that bodies near the edge of the resonance experience a torque from that planet that temporarily drives their pericenters toward the current orbital position of the planet.
-After the encounter ends, differential rotation of the disk slowly destroys the configuration over part of an orbit.
-This explains why the concentration of planetesimals appears to 'follow' the the planet.
-
-\citet{2016ApJ...818..159T} provides a different explanation for this phenomenon.
-Instead, the nonaxisymmetric structure is claimed to be a product of the path that a resonant test particle takes in a frame co-rotating with the planet (see figure 8.4 of \citet{2000ssd..book.....M}).
-This explanation, however, does not hold for a large collection of planetesimals, especially when there is no forced eccentricity.
-In such a case, the orbits of planetesimals near resonance would be randomly aligned, and the axisymmetric structure should become washed out.
-In the case with a perturbing planet planet on a circular orbit, this structure is still present (see figure 3 of \citet{2016ApJ...818..159T}).
-
-With no secular forcing, this dynamical phenomena would produce an underdensity in the radial surface density profile near the center of the resonance and an overdensity at each edge in cylindrical distance space.
-When a forced eccentricity is introduced, the edges of the resonance (indicated by the solid and dashed lines in figure \ref{fig:coll_polar_e}), where the pileups are located, begin to explore a wider range of radii over the course of a single orbit.
-If the the aphelion distance of the inner edge becomes comparable to the perihelion distance of the outer edge, the overdense regions on each side of the resonance meet and we should expect to see the central dip feature in the collision profile disappear.
-This is exactly what appears to be happening in the middle panel of figure \ref{fig:coll_polar_e}.
-As the forced eccentricity is increased further, a region forms at the center of the resonance where planetesimals from both sides of the resonance spend time (although not simultaneously).
-When this occurs, a bump feature forms in the collision profile near the center of the resonance.
-This is apparent in the bottom panel of figure \ref{fig:coll_polar_e}.
-
-Although the same phenomenon appears to be happening near the 3:1 MMR, the pileups at the edges of the resonance are not as well defined.
-We attribute this to the longer synodic period, compared to the 2:1 MMR.
-In addition, a number of other nearby resonances, including the 7:2 (at 2.25 AU), the 10:3 (at 2.33 AU), the 8:3 (at 2.71 AU) and the 5:2 (at 2.82 AU) also likely are contributing to the collision profile in cylindrical distance space near the 3:1.
-The width of the 3:1 MMR is also much narrower than the 2:1, which means that any dip or bump features produced by it would require much higher resolution observations.
-For these reasons, we will focus on the 2:1 MMR as the main diagnostic indicator.
-
-\subsection{Observability of the Dust}
-
-Orange curves in figure \ref{fig:coll_polar_e} show the simulated ALMA flux profiles generated with {\sc CASA} \citep{2007ASPC..376..127M}.
-Have Aaron add in some more text here describing exactly how the profiles were created.
-
-\subsection{Varying the Mass}
-
-The dynamical effects of varying the mass of the planet are somewhat simpler, in that doing so does not affect the forced eccentricity of the planetesimal disk.
-Instead, only the width of the resonances changes.
-The width of a first order resonance scales with $m$ (see equation \ref{eq:res_so}), while the leading order terms in the resonant part of the disturbing function, which set the strength of the resonance, also scale as $m$.
-For the 2:1 MMR, the dynamics near the resonance are equally sensitive to changes in eccentricity and mass.
-
-We show the polar structure of the $m_{low}$, $n$ and $m_{hi}$ simulations in figure \ref{fig:coll_polar_m} alongside the radial collision profile.
-In all three cases, the eccentricity of the perturbing planet is set to $e_{jup}$.
-Changes in the apocenter and pericenter distances of the edges of the resonances are entirely due to changes in the libration width here.
-For the $m_{low}$ and $n$ simulations, the inner apocenter and outer pericenter distances near the 2:1 MMR are quite similar and no strong features appear in the collision profile near this region.
-For the $m_{hi}$ case, the edges of the resonances are sufficiently far apart to allow a gap near the center of the 2:1 resonance to appear in the collision profile.
-
-\section{Constraining the Mass and Eccentricity of the Planet}
-
-The simple 'bump' vs 'dip' structure that we expect to reveal itself in the dust emission from colliding planetesimals in near-resonance with a giant planet could potentially be used to place constraints on the mass and eccentricity of the planet.
-Near the 2:1 MMR, the central dip feature is only produced when bodies at the edges of the resonance stay sufficiently separated in cylindrical distance over the course of an orbit.
-This is achieved when either the resonance width is large and the forced eccentricity is small.
-Conversely, the bump feature is produced when there is a sufficiently large amount of overlap between the apocenters and pericenters of the inner and outer edges of the resonance, respectively.
-This is achieved when the resonance is narrow and the forced eccentricity is large.
-
-In figure \ref{fig:bump_dip_diag}, we show the constraints that the presence of a bump or a dip places on the values of $(m_{g}, e_{g})$.
-A dip is produced by sufficiently low eccentricity and high mass planets, while a bump is produced by a low mass or high eccentricity planet.
-The parameter choices for the five simulations presented in the previous section are shown by the black dots.
-Between the two dashed lines, the overlap between the aphelion and perihelion distances of the inner and outer edges of the resonance is smaller than the width of the resonance.
-In this region, the overdense regions on each side of the resonance spend roughly equal amounts of time at all possible cylindrical distances, and no strong feature appears in the collision profile.
-
-Because the strength of the 2:1 resonance scales with $e_{g}$ and  $m_{g}$, a sufficiently low mass and low eccentricity planet will not induce enough of a perturbation in the planetesimal disk to produce a detectable bump or dip feature.
-The colored contours in figure \ref{fig:bump_dip_diag} indicate the relative strength of the resonance as these quantities are varied.
-Although the resonance strength is equally sensitive to changes in mass and eccentricity, the peri - apocenter overlap of the resonance edges is more sensitive to changes in eccentricity.
-This is also consistent with what was seen in figure \ref{fig:coll_polar_m}, where changing $m_{g}$ by a factor of 4 produced very minimal changes to the resulting dust profile.
-
-In order to actually identify the 2:1 MMR in the dust emission, at least one other resonance must be visible.
-Assuming the gravitational field in the disk is near-Keplerian, the distance ratios between two features can be used to determine period ratios, which can be used to confirm whether the features seen are indeed resonances.
-Although the 3:1 MMR does not appear to follow the simple bump vs dip dichotomy described above, its presence should be marginally detectable in all of the cases shown above.
-
-\section{Summary and Conclusions}
-
-In this work, we have shown that mean-motion resonances with a perturbing planet produce significant variations in the collision rate of a planetesimal disk.
-In contrast to \citet{2000Icar..143...45R}, we find that the more prominent interior MMRs, including the 2:1, 3:1 and 5:3, all produce structures in the collision profile as a function of semimajor axis.
-Furthermore, we found a series of distinctly different features that appear when collisions are grouped by cylindrical distance from the central star.
-If enough gas from the protoplanetary disk is still present, dust generated from planetesimals collisions will immediately couple to it and fall onto a circular orbit.
-In this case, variations in the radial collision profile will match the radial dust emission profile, which can potentially be observed in the sub-mm.
-
-Near the interior 2:1 MMR, we find that a distinct bump or dip feature is generated in the dust profile.
-The presence of either of these structures can used to constrain the mass and eccentricity of the perturbing planet.
-For a high mass, low eccentricity planet, a dip will form in the dust profile because the edges of the resonance, where many collisions occur, stay sufficiently separated.
-If the planet has a low enough mass (which shrinks the size of the resonance) or is sufficiently eccentric (which decreases the separation between the apocenter and pericenter distances of the inner and outer edges of the resonance), a bump will instead form.
-We tested this hypothesis for five different combinations of the planet's mass and eccentricity and found that this diagnostic is useful as long as the planet is sufficiently far from the dividing line in parameter space.
-This diagnostic is more clear for massive, eccentric planets, because the strength of the resonant perturbations scale linearly with both of these quantities.
-
-The results presented here appear to be broadly consistent with \citet{2016ApJ...818..159T}, which used collisionless, massless test particles to model a planetesimal disk perturbed by a planet.
-In their case, a dip feature appeared in the azimuthally averaged surface density profile was seen, although they did use a high enough eccentricity planet in any of their simulations to produce a bump.
-Another thing to note is that the gap morphology seen by \citet{2016ApJ...818..159T} was markedly different for the 2:1 exterior MMR.
-Whether this would alter the radial collision profile for the exterior, rather then the interior 2:1 resonance, is not immediately clear.
-Given that the solid surface density diminishes with distance ($\sim r^{3/2}$ for the MMSN \citep{1981PThPS..70...35H}), exterior resonances may not be quite as useful for this type of measurement.
-
-Our conclusion that the bodies in resonance do not significantly contribute to the radial collision profile (see figure \ref{fig:coll_hist_a}) does appear support the simplifying assumptions made by \citet{2017ApJ...850..103B}, in which dynamically cold, low eccentricity regions of test particles were assumed to trace the regions of second-generation dust production.
-Besides the corotation regions, nonaxisymmetric structure near resonances does not appear to be present in \citet{2017ApJ...850..103B}.
-This makes it difficult to determine whether a simpler model in which test particles 'trace' the collision rate can be used to generate a dust profile.
-
-Resolving these structures is really pushing the capabilities of observatories like ALMA. Mention NG-VLA. Also {\sc Frankenstein} \citep{2020arXiv200507709J}.
-
 \begin{figure*}
@@
     \includegraphics[width=\textwidth]{figures/xy.png}
-    \caption{Non axisymmetric gaps and rings appear near MMRs. More features appear at higher eccentricities. Gap features
-    at $\theta$ = 0 and $\theta = \pi$ follow the giant planet in its orbit. (Update this to show long of peri of Jupiter)\label{fig:xy}}
+    \caption{The positions of the remaining planetesimals at the end of the e1m2 (left), e2m2 (center) and e3m2 (right) simulations. The red dot 
+    indicates the position of the giant planet and the dashed line points in the direction of the planet's longitude of perihelion. Non-axisymmetric gaps 
+    are apparent near the locations of MMRs. At higher eccentricities, more resonances become visible. At the 2:1 MMR, gap features at $\theta$ = 0 
+    and $\theta = \pi$ follow the giant planet in its orbit.\label{fig:xy}}
 \end{center}
@@
     \includegraphics[width=0.5\textwidth]{figures/ae.png}
-    \caption{The MMRs produce spikes in the a-e plane. Between resonances, the nonzero eccentricity is caused by secular
-    forcing by the planet. At larger eccentricities, the higher order resonances become more prominent because of the steeper
-    scaling with $e$.\label{fig:ae}}
+    \caption{The semimajor axes and eccentricities of the remaining planetesimals are shown, with the locations of prominent resonances indicated 
+    by the vertical dashed lines. Libration of the critical angle drives large variations in eccentricity, which produce spikes in the a-e plane. Between 
+    the resonances, the nonzero eccentricity is due to secular forcing by the planet.\label{fig:ae}}
 \end{center}
@@
     \includegraphics[width=\textwidth]{figures/long_ph.png}
-    \caption{The MMRs also induce precession which overpowers the secular forcing. Inside of the resonances, orbits of
-    planetesimals are effectively randomized.\label{fig:long_ph}}
+    \caption{Shown here are the longitudes of pericenter and semimajor axes of the remaining planetesimals. The dashed lines again indicate the 
+    locations of prominent MMRs. Close to the resonances, the critical angle librates and drives fast precession of the longitudes of pericenter of the 
+    bodies. This overpowers the secular forcing by the planet and effectively randomizes the orientations of their orbits.\label{fig:long_ph}}
 \end{center}
 \end{figure*}
+
+\section{Results} \label{sec:results}
+
+All five simulations are evolved for 5,000 years, which is roughly 400 orbits of the perturbing planet. Because the effects of the mean motion 
+resonances are not built into the initial conditions, the simulations must be run long enough for the distribution of orbital elements to reach 
+equilibrium near the resonances before the collision rate is measured. The libration timescale, which describes how long the critical angle (and also 
+the semimajor axis and eccentricity) of a planetesimal in resonance takes to undergo a full oscillation is given by
+
+\begin{equation}\label{eq:lib_time}
+	T_{lib} = \frac{2 \pi}{3 q^{2} C_{r} n e^{\left| 2p + q \right|}},
+\end{equation}
+
+\noindent for small-amplitude librations. For all five sets of initial conditions used, $T_{lib} \sim$ 1,000 - 2,000 years for the 3:1 and 2:1 resonances. 
+For this reason, we allow each simulation to run for 2,000 years before we begin tracking any collision statistics.
+
+\subsection{Varying the Eccentricity}
+
+We begin by examining simulations e1m2, e2m2 and e3m2. The positions of the planetesimals in the x-y plane after 5,000 years of integration is 
+shown in figure \ref{fig:xy}. In all cases, the coordinate system is rotated so that the giant planet lies at $\theta = 0$ and the longitude of perihelion of 
+the planet is shown by the dashed line. Resonances with the perturbing planet are visible via nonaxisymmetric gaps. Upon close inspection of the 
+last few simulation snapshots, these gaps appear to follow the planet in its orbit, rather than aligning themselves with the longitude of perihelion. A 
+similar substructure reveals itself in \citet{2000Icar..143...45R} (see bottom panel of figure 3) and \citet{2016ApJ...818..159T} (figure 3). It is worth 
+noting that \citet{2000Icar..143...45R} started with a completely cold planetesimal disk and a Jupiter mass planet on a circular, coplanar orbit. The 
+presence of these features seems robust to the choice of initial conditions.
+
+The effects of the resonances become much more apparent in semimajor axis-eccentricity space, which is shown in figure \ref{fig:ae}. In all cases, 
+the 3:1, 2:1 and 5:3 resonances are readily visible as 'spikes' in the eccentricity that bend slightly inward (due to the conservation of $E_{J}$). In the 
+e3m2 simulation, features also appear near the 5:2, 7:3 and 5:3 resonances. The absence of these features from the e1m2 simulation can be 
+explained by the fact that the strength of a resonance scales with $e^{q}$ \citep{1994PhyD...77..289M}.
+
+Another important effect of the resonances is visible in figure \ref{fig:long_ph}, which shows the orientation of the longitude of perihelia of 
+planetesimals in the disk. Inside of the resonances, orbits of planetesimals quickly precess and their orientations are effectively randomized. An 
+important point to note is that this strong precession effect quickly disappears beyond the boundaries of the resonance. This turns out to be 
+important to explain the nonaxisymmetric structure seen in figure \ref{fig:xy}, which will be addressed in more detail below.
+
+Next, we examine the statistics of collisions resolved in each of the simulations. The 3D positions and velocities of the two colliding bodies are 
+recorded to a table at the moment of impact. From these quantities, we also derive the Keplerian orbital elements of a collision from these quantities. 
+First, we examine the semimajor axis of the first particle participating in each collision. During a collision, the 'first' particle is defined as the more 
+massive of the two. However, nearly all of the collisions happen between the initial, equal-mass planetesimals. In this case, the distinction is set by 
+the collision search algorithm and is rather arbitrary. In all of the plots where we show collision statistics, we have verified that using the 'first' or 
+'second' collider does not qualitatively change any of the features.
+
+Figure \ref{fig:coll_hist_a} shows the semimajor axis distribution of the resolved collisions. We find that some of the features present in this and 
+subsequent figures are highly sensitive to the number of bins and the location of the bin edges. For this reason, we construct a PDF of the collisions 
+using a Kernel Density Estimate (KDE). We use the {\sc neighbors.KernelDensity} function from the {\sc sklearn} \citep{scikit-learn} package to 
+construct our KDEs. For the kernel, we use a tophat function with a bandwidth of 0.02 AU.
+
+Near some of the resonances, there are noticeable suppressions or enhancements of the local collision rate. This contrasts with the findings of 
+\citet{2000Icar..143...45R}, who simulated a similar setup and found no discernible features near the MMRs. We attribute the differences to  a more 
+conservative timestepping criterion in our simulations. The most prominent features appear as an enhancement to the collision rate near the 2:1 
+MMR and a decrease near the 3:1 MMR. At higher forced eccentricities, features near the 5:2, 7:3 and 5:3 resonances are also visible, due to the 
+steeper sensitivity of higher order resonances to eccentricity \citep{1994PhyD...77..289M}.
+
+We attribute the production of a bump vs a dip at certain resonances to changes in the gravitational focusing factor during two-body encounters. 
+Closer to the star, the planetesimal disk starts off dynamically colder. Here, additional heating from the resonance acts to suppress the gravitational 
+focusing cross section, which reduces the collision rate from the non-perturbed value. Further out in the disk, where the encounter velocity is already 
+higher, the gravitational focusing cross section is already minimized. Any additional heating instead acts to simply increase the encounter rate 
+between bodies, which enhances the collision rate. This explains the relative drop in the collision rate near the 3:1 MMR and the bumps that form 
+near the 2:1 and 5:3 resonance. Although this could potentially serve as a useful diagnostic of the planetesimal size in a disk (because the mutual 
+escape velocity sets how dynamically hot the bodies can get before gravitational focusing is suppressed), a direct measurement of the semimajor 
+axes of the planetesimals is not possible. In addition, as will demonstrate next, collisions due to bodies in resonance end up having an insignificant 
+effect on the final shape of the radial dust distribution.
 
@@
     \caption{In semimajor axis space, prominent features appear near the 3:1 and 2:1 MMRs. Near the 3:1, the collision
-    rate decreases, while it gets enhanced near the 2:1. This is because gravitational focusing is already suppressed
-    near the 2:1. Additional heating by the resonance increases the encounter rate.\label{fig:coll_hist_a}}
+    rate decreases from its unperturbed value, while an enhancement apepars near the 2:1.\label{fig:coll_hist_a}}
 \end{center}
@@
     \includegraphics[width=0.5\textwidth]{figures/coll_hist_r.png}
-    \caption{The features near resonance that appear in cylindrical distance space appear qualitatively different.
-    The orange curve shows collisions with bodies inside the 2:1 and 3:1 MMR excluded. This does not qualitatively
-    change any of the plots, and we infer that the features seen here are produced by bodies outside of resonance.
-    Most interestingly,  the highest eccentricity planet simulation produces bumps, rather than dips near the 2:1 and
-    3:1 MMR.\label{fig:coll_hist_r}}
+    \caption{Here, collisions are instead ordered by cylindrical distance from the star.
+Features near the 3:1 and 2:1 MMRs are still present, but appear qualitatively different than in semimajor axis space.
+At low eccentricities, a dip appears around the center of the resonance.
+At the highest eccentricity, a bump is formed instead.
+In orange, the collision profile is shown with collisions between bodies in resonance removed.
+The bump and dip features remain qualitatively the same, which suggests that they are produced by bodies outside of resonance.\label{fig:coll_hist_r}}
 \end{center}
@@
 
+\subsection{Where Does the Dust End Up?}
+
+To construct a radial dust profile from the collision statistics, we begin by making the assumption that any dust generated by collisions is strongly 
+coupled to the gas. For a dust grain larger than the mean free path of the gas particles, the timescale to damp its eccentricity is given by 
+\citep{1976PThPh..56.1756A}
+
+\begin{equation}\label{eq:t_edamp}
+    t_{e, damp} = \frac{8 s \rho}{3 e C_{D} \rho_{g} v_{th}}.
+\end{equation}
+
+\noindent where $m$, $e$ and $s$ are the mass, eccentricity and radius of the dust grain. $C_{D}$ is a drag coefficient which is of order unity, $
+\rho_{g}$ is the local density of the gas and $v_{th}$ is its thermal speed. At 3 AU, the gaseous component of the solar nebula has a density of $4 
+\times 10^{-10}$ g cm$^{-3}$ and a typical thermal speed of $10^{5}$ cm s$^{-1}$ \citep{1981PThPS..70...35H}. For a 1 mm dust grain with a 
+density of 1 g cm$^{-3}$ and an eccentricity of 0.05, the damping timescale is $4 \times 10^{-3}$ years. This is orders of magnitude smaller than the 
+collision timescale, therefore we conclude that collisionally generated dust grains will immediately couple to the gas.
+
+Operating under this assumption, a map of the relative concentration of second-generation dust can be constructed from the cylindrical 
+distance at which the collisions occur. This is shown in figure \ref{fig:coll_hist_r}. Similar to figure \ref{fig:coll_hist_a}, we use a KDE with a bandwidth 
+of 0.02 AU to assemble the collision locations into a radial distribution. Most strikingly, the bump that was present near the 2:1 resonance is no 
+longer present in cylindrical distance space, although it suddenly appears again in the e3m2 simulation. The dip that is present near the 3:1 MMR 
+also disappears and instead presents as a bump in the e3m2 case. To determine how the resonant bodies actually contribute to the radial collision 
+profile, we excluded collisions that fall between $2.495 < a < 2.505$ AU (near the 3:1 resonance) and between $3.2 < a < 3.35$ AU (near the 2:1 
+resonance), which is shown by the orange curve. Qualitatively, none of the bump or dip features present are changed by making this exclusion. This 
+suggests that the features near resonance seen in semimajor axis space become 'smeared out' in cylindrical distance space due to the large spread 
+in eccentricity and orbital orientation.
+
+This also suggests that the features seen in figure \ref{fig:coll_hist_r} are being produced by bodies outside of resonance. To further understand this, 
+we revisit the nonaxisymmetric structure seen in figure \ref{fig:xy}. In figure \ref{fig:coll_polar_e}, we compare the radial collision profile to the polar 
+structure seen in the e1m2, e2m2 and e3m2 simulations. In the lowest forced eccentricity case, the pileups near the edges of the resonances line up 
+with the boundaries of the dip feature seen in the radial collision profile. The locations of the edges of the resonances are calculated using equations 
+\ref{eq:res_fo} and \ref{eq:res_so}. The pileups are especially prominent for the 2:1 resonance. As discussed previously, the pileups and gaps seen 
+in polar coordinates follow the position of the giant planet in its orbit.
+
+Although the nonaxisymmetric pileup of bodies near the edges of resonances has been seen previously 
+\citep{2000Icar..143...45R, 2016ApJ...818..159T}, we could not find a satisfactory explanation for why it happens and will provide one here. As 
+mentioned previously, the circulation frequency of the critical angle slows as one approaches the edge of the resonance from the outside. Following 
+the pendulum analogy, this is equivalent to reaching the point where the pendulum becomes suspended in the vertical position. When the critical 
+angle stays relatively stationary during an encounter, the net torque will drive the longitude of pericenter towards the point of conjunction 
+\citep{1976ARA&A..14..215P}.  This is the basic mechanism that causes isolated resonances to be stable. Inside of resonance, the critical angles 
+librates about some value and this configuration is maintained. Just outside of resonance, however, the critical angle slowly drifts away, with the drift 
+direction changing sign across the resonance. The net result of this is that bodies near the edge of the resonance experience a torque from that 
+planet that temporarily drives their pericenters toward the current orbital position of the planet. After the encounter ends, differential rotation of the 
+disk slowly destroys the configuration over part of an orbit. This explains why the concentration of planetesimals appears to 'follow' the the planet.
+
 \begin{figure*}
     \includegraphics[width=\textwidth]{figures/coll_polar_e.png}
-    \caption{The features in the previous figure appear to match with the pileups of bodies near the edges of the
-    resonances. The dashed and solid lines show the perihelion and aphelion distances for bodies at the inner
-    and outer edges of the 2:1 and 3:1 resonances. The dip vs bump features seen in the previous figure appear
-    to depend on whether the aphelia of bodies at the inner edge and perihelia of bodies at the outer edge of a
-    resonance cross. When this does not occur, a cavity persists at the center of the resonance, which reduces the
-    collision rate in that region. When the two distances overlap, bodies from both edges of the resonance spend some
-    time in the middle, producing a bump in the collision rate.\label{fig:coll_polar_e}}
+    \caption{The collision profiles in figure \ref{fig:coll_hist_r} are shown alongside the positions of the planetesimals, in polar coordinates. The 
+    synthetic dust emission profiles are shown in orange. The dashed and solid lines show the pericenter and apocenter of bodies at the edge of the 
+    3:1 and 2:1 MMR. In these figures, the longitude of pericenter of the planet lies at $\theta = 0$ and the present position of the planet is indicated 
+    by the vertical line. For the 2:1 resonance, a bump, rather than a dip feature appears when the inner edge or the resonance's apocenter and outer 
+    edge's pericenter distance cross. The collision profile near the 3:1 resonance does not appear to follow this same qualitative behavior.
+    \label{fig:coll_polar_e}}
 \end{figure*}
@@
     \includegraphics[width=\textwidth]{figures/coll_polar_m.png}
-    \caption{Similar to the previous figure, except the eccentricity of the planet is kept constant and the mass is varied.
+    \caption{Similar to figure \ref{fig:coll_polar_e}, except the eccentricity of the planet is kept constant and the mass is varied.
     This has the effect of changing the width of the resonances, without altering the relative apo or peri distances of
-    bodies near the edges.\label{fig:coll_polar_m}}
+    bodies near the edges. Except for the highest mass case, the apocenter and pericenter distances of the inner and outer edges of the 2:1 
+    resonance are too close together to produce much of a dip or a bump feature.\label{fig:coll_polar_m}}
 \end{figure*}
+
+\citet{2016ApJ...818..159T} provides a different explanation for this phenomenon. Instead, the nonaxisymmetric structure is claimed to be a product 
+of the path that a resonant test particle takes in a frame co-rotating with the planet (see figure 8.4 of \citet{2000ssd..book.....M}). This explanation, 
+however, does not hold for a large collection of planetesimals, especially when there is no forced eccentricity. In such a case, the orbits of 
+planetesimals near resonance would be randomly aligned, and the axisymmetric structure should become washed out. In the case with a perturbing 
+planet planet on a circular orbit, this structure is still present (see figure 3 of \citet{2016ApJ...818..159T}).
+
+With no secular forcing, this dynamical phenomena would produce an underdensity in the radial surface density profile near the center of the 
+resonance and an overdensity at each edge in cylindrical distance space. When a forced eccentricity is introduced, the edges of the resonance 
+(indicated by the solid and dashed lines in figure \ref{fig:coll_polar_e}), where the pileups are located, begin to explore a wider range of radii over the 
+course of a single orbit. If the the aphelion distance of the inner edge becomes comparable to the perihelion distance of the outer edge, the 
+overdense regions on each side of the resonance meet and we should expect to see the central dip feature in the collision profile disappear. This is 
+exactly what appears to be happening in the middle panel of figure \ref{fig:coll_polar_e}. As the forced eccentricity is increased further, a region 
+forms at the center of the resonance where planetesimals from both sides of the resonance spend time (although not simultaneously). When this 
+occurs, a bump feature forms in the collision profile near the center of the resonance. This is apparent in the bottom panel of figure 
+\ref{fig:coll_polar_e}.
+
+Although the same phenomenon appears to be happening near the 3:1 MMR, the pileups at the edges of the resonance are not as well defined. We 
+attribute this to the longer synodic period, compared to the 2:1 MMR. In addition, a number of other nearby resonances, including the 7:2 (at 2.25 
+AU), the 10:3 (at 2.33 AU), the 8:3 (at 2.71 AU) and the 5:2 (at 2.82 AU) also likely are contributing to the collision profile in cylindrical distance 
+space near the 3:1. The width of the 3:1 MMR is also much narrower than the 2:1, which means that any dip or bump features produced by it would 
+require much higher resolution observations. For these reasons, we will focus on the 2:1 MMR as the main diagnostic indicator.
+
+\subsection{Observability of the Dust}
+
+Orange curves in figure \ref{fig:coll_polar_e} show the simulated ALMA flux profiles generated with {\sc CASA} \citep{2007ASPC..376..127M}. Have 
+Aaron add in some more text here describing exactly how the profiles were created. Should we add a separate figure to show the flux profiles, or 
+include them in figures 6 and 7 like I've started to do here?
+
+\subsection{Varying the Mass}
+
+The dynamical effects of varying the mass of the planet are somewhat simpler, in that doing so does not affect the forced eccentricity of the 
+planetesimal disk. Instead, only the width of the resonances changes. The width of a first order resonance scales with $m$ (see equation 
+\ref{eq:res_so}), while the leading order terms in the resonant part of the disturbing function, which set the strength of the resonance, also scale as 
+$m$. For the 2:1 MMR, the dynamics near the resonance are equally sensitive to changes in eccentricity and mass.
+
+We show the polar structure of the e2m1, e2m2 and e2m3 simulations in figure \ref{fig:coll_polar_m} alongside the radial collision profile. In all three 
+cases, the eccentricity of the perturbing planet is set to $e_{jup}$. Changes in the apocenter and pericenter distances of the edges of the 
+resonances are entirely due to changes in the libration width here. For the e2m1 and e2m2 simulations, the inner apocenter and outer pericenter 
+distances near the 2:1 MMR are quite similar and no strong features appear in the collision profile near this region. For the e2m3 case, the edges of 
+the resonances are sufficiently far apart to allow a gap near the center of the 2:1 resonance to appear in the collision profile.
+
+\section{Constraining the Mass and Eccentricity of the Planet}\label{sec:constrain}
 
@@
     of the perturbing planet. The color scale indicates the relative strength of the features, while the dashed lines
-    indicate boundaries in parameter space where a dip or a bump will be produced at the resonance.\label{fig:bump_dip_diag}}
+    indicate boundaries in parameter space where a dip or a bump will be produced at the resonance. Combinations of mass and eccentricity that fall 
+    between the dashed lines correspond to an inner apocenter and outer pericenter separation at the edges of the resonance that is smaller than the 
+    resonance width and therefore will not create any significant feature in the collision profile.\label{fig:bump_dip_diag}}
 \end{center}
 \end{figure}
+
+The simple 'bump' vs 'dip' structure that we expect to reveal itself in the dust emission from colliding planetesimals in near-resonance with a giant 
+planet could potentially be used to place constraints on the mass and eccentricity of the planet. Near the 2:1 MMR, the central dip feature is only 
+produced when bodies at the edges of the resonance stay sufficiently separated in cylindrical distance over the course of an orbit. This is achieved 
+when either the resonance width is large and the forced eccentricity is small. Conversely, the bump feature is produced when there is a sufficiently 
+large amount of overlap between the apocenters and pericenters of the inner and outer edges of the resonance, respectively. This is achieved when 
+the resonance is narrow and the forced eccentricity is large.
+
+In figure \ref{fig:bump_dip_diag}, we show the constraints that the presence of a bump or a dip places on the values of $(m_{g}, e_{g})$. A dip is 
+produced by sufficiently low eccentricity and high mass planets, while a bump is produced by a low mass or high eccentricity planet. The parameter 
+choices for the five simulations presented in the previous section are shown by the black dots. Between the two dashed lines, the overlap between 
+the aphelion and perihelion distances of the inner and outer edges of the resonance is smaller than the width of the resonance. In this region, the 
+overdense regions on each side of the resonance spend roughly equal amounts of time at all possible cylindrical distances, and no strong feature 
+appears in the collision profile.
+
+Because the strength of the 2:1 resonance scales with $e_{g}$ and  $m_{g}$, a sufficiently low mass and low eccentricity planet will not induce 
+enough of a perturbation in the planetesimal disk to produce a detectable bump or dip feature. The colored contours in figure \ref{fig:bump_dip_diag} 
+indicate the relative strength of the resonance as these quantities are varied. Although the resonance strength is equally sensitive to changes in 
+mass and eccentricity, the peri - apocenter overlap of the resonance edges is more sensitive to changes in eccentricity. This is also consistent with 
+what was seen in figure \ref{fig:coll_polar_m}, where changing $m_{g}$ by a factor of 4 produced very minimal changes to the resulting dust profile.
+
+In order to actually identify the 2:1 MMR in the dust emission, at least one other resonance must be visible. Assuming the gravitational field in the 
+disk is near-Keplerian, the distance ratios between two features can be used to determine period ratios, which can be used to confirm whether the 
+features seen are indeed resonances. Although the 3:1 MMR does not appear to follow the simple bump vs dip dichotomy described above, its 
+presence should be marginally detectable in all of the cases shown above.
+
+\section{Summary and Conclusions}\label{sec:conclusions}
+
+In this work, we have shown that mean-motion resonances with a perturbing planet produce significant local variations in the collision rate of a 
+planetesimal disk. In contrast to \citet{2000Icar..143...45R}, we find that the more prominent interior MMRs, including the 2:1, 3:1 and 5:3, all 
+produce structure in the collision profile as a function of semimajor axis. Furthermore, we find that a series of distinctly different features appear 
+when collisions are sorted by cylindrical distance from the central star. If enough gas from the protoplanetary disk is still present, dust generated 
+from planetesimals collisions will immediately couple to it and fall onto a circular orbit. In this case, the radial dust emission profile, which can be 
+observed in the sub-mm, directly traces the radial collision rate and therefore the dynamical activity of the planetesimals.
+
+Near the interior 2:1 MMR, we find that a distinct bump or dip feature is generated in the dust profile. The presence of one of these two structures 
+can used to constrain the mass and eccentricity of the perturbing planet. For a high mass, low eccentricity planet, a dip will form in the dust profile 
+because the edges of the resonance, where many collisions occur, stay sufficiently separated. If the planet has a low enough mass (which shrinks 
+the size of the resonance) or is sufficiently eccentric (which decreases the separation between the apocenter and pericenter distances of the edges 
+of the resonance), a bump will instead form. We tested this hypothesis for five different combinations of the planet's mass and eccentricity and found 
+that a distinct bump or dip signature is produced as long as the planet properties are sufficiently far from the dividing line in parameter space. This 
+diagnostic is more useful for massive, eccentric planets, because the strength of the resonant perturbations scale linearly with both of these 
+quantities.
+
+The results presented here appear to be broadly consistent with \citet{2016ApJ...818..159T}, which used collisionless, massless test particles to 
+model a planetesimal disk perturbed by a planet. In their case, a dip feature can be seen in the azimuthally averaged surface density profile, 
+although they did not test a high enough eccentricity planet in any of their simulations to produce a bump. Another thing to note is that the gap 
+morphology seen by \citet{2016ApJ...818..159T} was markedly different for the 2:1 exterior MMR. Whether this would alter the radial collision profile 
+for the exterior, rather than the interior 2:1 resonance, is not immediately clear.  Given that the solid surface density diminishes with distance 
+($\sim r^{-3/2}$ for the MMSN \citep{1981PThPS..70...35H}), exterior resonances may not be quite as useful for this type of measurement.
+
+Compared to using the gap around the planet as a diagnostic \citep{2013ApJ...777L..31D, 2016ApJ...820...29D}, measuring variations in the dust 
+emission near higher order MMRs is much more subtle and requires much higher spatial resolution and sensitivity. As we have shown, the bump vs 
+dip feature near the 2:1 MMR is marginally detectable with ALMA for the nearest protoplanetary disks. Another complicating factor is that the inner 
+$\sim$ 10 AU of most protoplanetary disks are optically thick in the sub-mm. The solution to this problem is to instead observe in the radio, which 
+achieves much poorer resolution. However, future radio facilities like the NG-VLA are expected to achieve sub-AU resolution for nearby planet-
+forming disks \citep{2018ASPC..517..147R}. In the more near-term, techniques like Gaussian process fitting present a promising way to recover 
+substructure at sub-beam resolution \citep{2020arXiv200507709J}.
 

### 2020-05-20 makeFig.py

@@ -697,19 +697,24 @@ def make_xy():
 		return
 
 	# Rotate so that jupiter is at theta =0
+	rad_peri = 100
 	theta_jup_e1 = np.arctan2(pl_e1['pos'][0][1], pl_e1['pos'][0][0])
 	x_e1_rot = x_e1*np.cos(-theta_jup_e1) - y_e1*np.sin(-theta_jup_e1)
 	y_e1_rot = x_e1*np.sin(-theta_jup_e1) + y_e1*np.cos(-theta_jup_e1)
+	x_peri_e1, y_peri_e1 = rad_peri*np.cos(theta_jup_e1), rad_peri*np.sin(theta_jup_e1)
 	theta_jup_e = np.arctan2(pl_e['pos'][0][1], pl_e['pos'][0][0])
 	x_e_rot = x_e*np.cos(-theta_jup_e) - y_e*np.sin(-theta_jup_e)
 	y_e_rot = x_e*np.sin(-theta_jup_e) + y_e*np.cos(-theta_jup_e)
+	x_peri_e, y_peri_e = rad_peri*np.cos(theta_jup_e), rad_peri*np.sin(theta_jup_e)
 	theta_jup_e2 = np.arctan2(pl_e2['pos'][0][1], pl_e2['pos'][0][0])
 	x_e2_rot = x_e2*np.cos(-theta_jup_e2) - y_e2*np.sin(-theta_jup_e2)
 	y_e2_rot = x_e2*np.sin(-theta_jup_e2) + y_e2*np.cos(-theta_jup_e2)
+	x_peri_e2, y_peri_e2 = rad_peri*np.cos(theta_jup_e2), rad_peri*np.sin(theta_jup_e2)
 
 	fig, (ax1, ax2, ax3) = plt.subplots(figsize=(16,5), nrows=1, ncols=3, sharex=True, sharey=True)
 	ax1.scatter(x_e1_rot, y_e1_rot, s=s)
 	ax1.scatter(x_e1_rot[0], y_e1_rot[0], color='r')
+	ax1.plot([0, x_peri_e1], [0, y_peri_e1], linestyle='--')
 	ax1.set_xlabel('X [AU]')
 	ax1.set_ylabel('Y [AU]')
 	ax1.set_title(r'e$_{pl}$ = 1/2 e$_{jup}$')
@@ -717,11 +722,13 @@ def make_xy():
 	ax1.set_ylim(-5.5, 5.5)
[…]

### 2020-05-21 main.tex
Edit text, fix typos, add simulation names to figures

@@
 
-Recent observations of circumstellar disks by ALMA have revealed a rich variety of substructure in the millimeter contiunuum emission. Features 
+Recent observations of circumstellar disks by ALMA have revealed a rich variety of substructure. Features 
 such as gaps and asymmetries 
@@
 structure of the continuum emission in a number of ways. A misaligned giant planet can produce nonaxisymmetric features such as warps 
-\citep{2001A&A...370..447A}. Highly eccentric perturbers can produce even more complicated structures through secular perturbations 
+\citep{2001A&A...370..447A}. Highly eccentric perturbers can produce even more complicated structures through secular interactions 
 \citep{2014MNRAS.443.2541P, 2015MNRAS.448.3679P}. Mean motion resonances (MMRs) have been shown to open gaps as well 
@@
 Collisions between planetesimals are thought to be a significant source of dust for many young circumstellar disks 
-\citep[see][]{2008ARA&A..46..339W}. An expanding debris cloud from a planetesimal collision was recently detected through scattered light in the 
+\citep[see][]{2008ARA&A..46..339W}. An expanding debris cloud from a planetesimal collision was recently detected in the 
 Fomalhut system \citep{2020PNAS..117.9712G}. Although some amount of primordial dust is likely still present during the planet formation process, 
@@
 distinctly observable marker that could be used to infer the presence of the planet. In a followup study, it was found that morphological differences in 
-the dust emission could be used to distinguish between a low and high eccentricity planet \citep{2016ApJ...820...29D}.
+the dust emission could be used to determine whether the planet had a circular or eccentric orbit \citep{2016ApJ...820...29D}.
 
-Although more difficult to spatially resolve, substructure due to mean-motion resonances (MMRs) with a giant planet may hold additional clues which 
+Substructure due to mean-motion resonances (MMRs) with a giant planet may hold additional clues which 
 could be used to constrain the properties of the planet.  The width of a resonance is set by both the mass of the perturbing planet, along with the 
 unperturbed eccentricity of the planetesimals, which is in turn set by the eccentricity of the planet through secular forcing. Therefore, the structure of 
-second generation dust produced near MMRs may hold information about both the mass and eccentricity of the planet.
+second generation dust produced near MMRs encodes information about both the mass and eccentricity of the planet.
 
@@
 of a planetesimal disk under the gravitational influence of an external perturber. In section \ref{sec:sims} we provide an overview of the N-body code 
-that we use and describe the initial conditions that are used for five simulations in which a perturbing giant planet is given is given various masses 
-and eccentricities. Section \ref{sec:results} presents the results of these five simulations and we use the collision statistics to generate synthetic dust 
+used and describe the initial conditions chosen for five simulations in which a perturbing giant planet is given various masses 
+and eccentricities. Section \ref{sec:results} presents the results of these simulations and we use the collision statistics to generate synthetic dust 
 emission profiles that would be detected with observing facilities like ALMA. Next, we show in section \ref{sec:constrain} that a characteristic bump 
@@
 The most direct and widespread effect that a giant perturber will have on a planetesimal disk is through secular forcing of the 
-eccentricities of the planetesimals. This will cause the complex eccentricities of the planetesimals to take on a time independent 
+eccentricities of the planetesimals. This will cause the complex eccentricities of the planetesimals to take on a time-independent 
 forced value, given by \citep{1999ApJ...527..918W} as
@@
 \begin{equation}\label{eq:eforced}
-	z_{f} = \frac{b^{2}_{3/2} (\alpha)}{b^{1}_{3/2} (\alpha)} e_{g} ~ \mathrm{exp} ~ i \omega_{g}.
+	z_{f} = \frac{b^{2}_{3/2} (\alpha)}{b^{1}_{3/2} (\alpha)} e_{g} ~ \mathrm{exp} ~ i \varpi_{g}.
 \end{equation}
@@
 \noindent Here, $\alpha = a_{g} / a$ where $a_{g}$ and $a$ are the semi-major axes of the giant planet and the planetesimal, 
-respectively. $e_{g}$ and $\omega_{g}$ are the eccentricity and longitude of pericenter of the giant and $b^{j}_{s} (\alpha)$ is a 
+respectively. $e_{g}$ and $\varpi_{g}$ are the eccentricity and longitude of pericenter of the giant and $b^{j}_{s} (\alpha)$ is a 
 Laplace coefficient given by \citep{2000ssd..book.....M} as
@@
 
-If we further assume that the two bodies are orbiting in the same plane, the behavior of the bodies near resonance is determined by the
+If we further assume that the two bodies are orbiting in the same plane, the motion of the bodies near resonance is determined by the
 behavior of a critical angle
@@
 \noindent where $\lambda = \varpi + M$ is the mean longitude of a body. For bodies in resonance, the critical angle will librate around an 
-equlibrium value, while this angle will circulate outside of resonance. This behavior is analogous to the motion of a pendulum. Changes in the 
-critical angle are coupled to changes in the mean motion and semimajor axis \citet{2000ssd..book.....M}. An important point to note, which will 
-become important later, is that the circulation frequency approaches zero near the edge of a resonance. The width of a resonance can be 
-defined by determining the largest variation in semimajor axis that permits librational, rather than circulatory motion of the pendulum. For 
-second and higher order resonances, the maximum libration width is given by
+equlibrium value, while this angle will circulate outside of resonance. For small eccentricities, this behavior is analogous to the motion of a 
+pendulum. Variations in the critical angle are coupled to changes in the mean motion and semimajor axis \citet{2000ssd..book.....M}. An important 
+point to note, which will become important later, is that the variation frequency of this angle approaches zero near the edge of a resonance. The 
+width of a resonance can be defined by determining the largest variation in semimajor axis that permits librational, rather than circulatory motion of 
+the $\phi$. For second and higher order resonances, the maximum libration width is given by
 
@@
 
-The net result of this is that MMRs will produce 'spikes' in the semimajor axis - eccentricity distribution of a planetesimal disk. In order to 
+The net result of this is that MMRs will produce spikes in the semimajor axis - eccentricity distribution of a planetesimal disk. In order to 
 preserve the Jacobi energy, equation \ref{eq:tiss} predicts that these spikes will tend to curve away from the perturbing body. This lowers the 
@@
 enhanced surface density will increase the collision rate. At the same time, the large eccentricites will either lower it due to the decreased 
-effectiveness of gravitational focusing, or raise it due to the more vigorous encounter rate, depending on how large the encounter velocity gets 
-compared to the escape velocity of the planetesimals. In addition, the MMRs cause the orbits of planetesimals to precess on relatively short 
+effectiveness of gravitational focusing, or raise it due to the more vigorous encounter rate, depending on the size of the encounter velocity relative to 
+the escape velocity of the planetesimals. In addition, the MMRs cause the orbits of planetesimals to precess on relatively short 
 timescales, which effectively randomizes their longitudes of perihelion. In a secularly forced disk, there will be an interface between aligned 
@@
 In total, five simulations are run. The first is a 'nominal' case, in which the perturbing planet's mass and eccentricity are set to that of Jupiter's. 
-In the other four cases, the mass (eccentricity) is increased or decreased by a factor of two, while the mass (eccentricity) is held at the nominal 
+In the other four cases, the mass (eccentricity) is increased or decreased by a factor of two, while the eccentricity (mass) is held at the nominal 
 value. In all cases, the perturbing giant is placed on a 5.2 AU orbit around a 1 $M_{\odot}$ star. The planetesimal disk extends from 2.2 to 3.8 
-AU, which covers the two most prominent mean motion resonances with the giant planet, the 2:1 at 3.27 AU and the 3:1 at 2.5 AU.The 
+AU, which covers the two most prominent mean motion resonances with the giant planet, the 2:1 at 3.27 AU and the 3:1 at 2.5 AU. The 
 planetesimal disk follows a minimum-mass solar nebula surface density profile \citep{1981PThPS..70...35H}
@@
 distribution to significantly evolve. The eccentricities of the bodies are drawn randomly from a Rayleigh distribution with a mode of $e_{eq}$, 
-while the inclinations are drawn from a similar distribution with a mode of $e_{eq}$/2 \citep{1993MNRAS.263..875I}. The longitude of perihelia 
-$\omega$ and the mean anomalies $M$ of the bodies are drawn from a uniform polar distribution.
+while the inclinations are drawn from a similar distribution with a mode of $e_{eq}$/2 \citep{1993MNRAS.263..875I}. The arguments of perihelion 
+$\omega$, longitude of ascending nodes $\Omega$ and the mean anomalies $M$ of the bodies are drawn uniformly $\in [0, 2 \pi)$.
 
-To account for the effects of secular forcing, the eccentricity vectors of the planetesimals are first decomposed into real and imaginary 
+To account for the effects of secular forcing by the planet, the eccentricity vectors of the planetesimals are first decomposed into real and imaginary 
 components:
@@
 \begin{equation}\label{eq:hk}
-	z = (h, ik) = e \, exp(i \omega)
+	z = (h, ik) = e \, exp(i \varpi)
 \end{equation}
 
-\noindent and a forced component is added to $h$ according to equation \ref{eq:eforced} (where we have set $\omega_{g}$ = 0).
+\noindent and a forced component is added to $h$ according to equation \ref{eq:eforced} (where we have set $\varpi_{g}$ = 0).
 
@@
 the symplectic nature of the integration without being too computationally expensive. Although using $\Delta T$ = 0.01 yr keeps the 
-integration symplectic, we find that a small amount of artificial precession is produced. We reduce the base time step size by an additional 
+integration symplectic, we find that a small amount of artificial precession is produced. This is most noticeable at the inner edge of the
+planetesimal disk. We reduce the base time step size by an additional 
 factor of 4 to the keep longitude of perihelia of planetesimals near the inner edge of the disk from drifting too far over the course of our 
@@
 
-All five simulations are evolved for 5,000 years, which is roughly 400 orbits of the perturbing planet. Because the effects of the mean motion 
-resonances are not built into the initial conditions, the simulations must be run long enough for the distribution of orbital elements to reach 
+All five simulations are evolved for 5,000 years, which is roughly 400 complete orbits of the perturbing planet. Because the effects of the mean 
+motion resonances are not built into the initial conditions, the simulations must be run long enough for the distribution of orbital elements to reach 
 equilibrium near the resonances before the collision rate is measured. The libration timescale, which describes how long the critical angle (and also 
@@
 \noindent for small-amplitude librations. For all five sets of initial conditions used, $T_{lib} \sim$ 1,000 - 2,000 years for the 3:1 and 2:1 resonances. 
-For this reason, we allow each simulation to run for 2,000 years before we begin tracking any collision statistics.
+For this reason, we allow each simulation to run for 2,000 years before we begin recording any collision statistics.
 
@@
 
-We begin by examining simulations e1m2, e2m2 and e3m2. The positions of the planetesimals in the x-y plane after 5,000 years of integration is 
-shown in figure \ref{fig:xy}. In all cases, the coordinate system is rotated so that the giant planet lies at $\theta = 0$ and the longitude of perihelion of 
-the planet is shown by the dashed line. Resonances with the perturbing planet are visible via nonaxisymmetric gaps. Upon close inspection of the 
-last few simulation snapshots, these gaps appear to follow the planet in its orbit, rather than aligning themselves with the longitude of perihelion. A 
-similar substructure reveals itself in \citet{2000Icar..143...45R} (see bottom panel of figure 3) and \citet{2016ApJ...818..159T} (figure 3). It is worth 
-noting that \citet{2000Icar..143...45R} started with a completely cold planetesimal disk and a Jupiter mass planet on a circular, coplanar orbit. The 
-presence of these features seems robust to the choice of initial conditions.
+We begin by examining simulations e1m2, e2m2 and e3m2. The positions of the planetesimals in the x-y plane after 5,000 years of integration are 
+shown in figure \ref{fig:xy}. In all cases, the coordinate system is rotated so that the giant planet lies at $\theta = 0$. The longitude of perihelion of 
+the planet is shown by the dashed line. Resonances with the perturbing planet are visible as nonaxisymmetric gaps. Upon close inspection of a 
+series of simulation snapshots, these gaps appear to follow the planet in its orbit, rather than aligning themselves with the longitude of perihelion. A 
+similar substructure, which is most noticeable near the 2:1 MMR, reveals itself in \citet{2000Icar..143...45R} (see bottom panel of figure 3) and 
+\citet{2016ApJ...818..159T} (figure 3). It is worth noting that \citet{2000Icar..143...45R} started with a completely cold planetesimal disk and a Jupiter 
+mass planet on a circular, coplanar orbit. The presence of these features seems robust to the choice of initial conditions.
 
@@
 Next, we examine the statistics of collisions resolved in each of the simulations. The 3D positions and velocities of the two colliding bodies are 
-recorded to a table at the moment of impact. From these quantities, we also derive the Keplerian orbital elements of a collision from these quantities. 
-First, we examine the semimajor axis of the first particle participating in each collision. During a collision, the 'first' particle is defined as the more 
-massive of the two. However, nearly all of the collisions happen between the initial, equal-mass planetesimals. In this case, the distinction is set by 
-the collision search algorithm and is rather arbitrary. In all of the plots where we show collision statistics, we have verified that using the 'first' or 
-'second' collider does not qualitatively change any of the features.
+recorded to a table at the moment of impact. We derive the Keplerian orbital elements of a collision using these positions and velocities. 
+First, we examine the semimajor axis of the first collider, which is shown in figure \ref{fig:coll_hist_a}. During a collision, the 'first' particle is defined 
+as the more massive of the two. However, nearly all of the collisions happen between the initial, equal-mass planetesimals. In this case, the 
+distinction is set by the collision search algorithm and is rather arbitrary. In all of the plots where we show collision statistics, we have verified that 
+using the 'first' or 'second' collider does not qualitatively change any of the features. We find that some of the features present in figure 
+\ref{fig:coll_hist_a} in this and subsequent figures are highly sensitive to the number of bins and the location of the bin edges. For this reason, we 
+construct a PDF of the collisions using a Kernel Density Estimate (KDE). We use the {\sc neighbors.KernelDensity} function from the {\sc sklearn} 
+\citep{scikit-learn} package to construct our KDEs. For the kernel, we use a tophat function with a bandwidth of 0.02 AU.
 
-Figure \ref{fig:coll_hist_a} shows the semimajor axis distribution of the resolved collisions. We find that some of the features present in this and 
-subsequent figures are highly sensitive to the number of bins and the location of the bin edges. For this reason, we construct a PDF of the collisions 
-using a Kernel Density Estimate (KDE). We use the {\sc neighbors.KernelDensity} function from the {\sc sklearn} \citep{scikit-learn} package to 
-construct our KDEs. For the kernel, we use a tophat function with a bandwidth of 0.02 AU.
-
-Near some of the resonances, there are noticeable suppressions or enhancements of the local collision rate. This contrasts with the findings of 
+Near the stronger resonances, there are noticeable suppressions or enhancements to the local collision rate. This contrasts with the findings of 
 \citet{2000Icar..143...45R}, who simulated a similar setup and found no discernible features near the MMRs. We attribute the differences to a more 
@@
 MMR and a decrease near the 3:1 MMR. At higher forced eccentricities, features near the 5:2, 7:3 and 5:3 resonances are also visible, due to the 
-steeper sensitivity of higher order resonances to eccentricity \citep{1994PhyD...77..289M}.
+steep sensitivity of higher order resonant perturbations to eccentricity \citep{1994PhyD...77..289M}.
 
-We attribute the production of a bump vs a dip at certain resonances to changes in the gravitational focusing factor during two-body encounters. 
+We attribute the production of a bump or a dip at certain resonances to changes in the gravitational focusing factor during two-body encounters. 
 Closer to the star, the planetesimal disk starts off dynamically colder. Here, additional heating from the resonance acts to suppress the gravitational 
-focusing cross section, which reduces the collision rate from the non-perturbed value. Further out in the disk, where the encounter velocity is already 
-higher, the gravitational focusing cross section is already minimized. Any additional heating instead acts to simply increase the encounter rate 
-between bodies, which enhances the collision rate. This explains the relative drop in the collision rate near the 3:1 MMR and the bumps that form 
-near the 2:1 and 5:3 resonance. Although this could potentially serve as a useful diagnostic of the planetesimal size in a disk (because the mutual 
-escape velocity sets how dynamically hot the bodies can get before gravitational focusing is suppressed), a direct measurement of the semimajor 
-axes of the planetesimals is not possible. In addition, as will demonstrate next, collisions due to bodies in resonance end up having an insignificant 
-effect on the final shape of the radial dust distribution.
+focusing cross section, which reduces the collision rate from its non-perturbed value.
+Further out in the disk, where the unperturbed encounter velocity is higher, the gravitational focusing cross section is already minimized.
+Any additional heating instead acts to simply increase the encounter rate between bodies, which enhances the collision rate.
+This explains the relative drop in the collision rate near the 3:1 MMR and the relative increase near the 2:1 and 5:3 resonances.
+Although this could potentially serve as a useful diagnostic of the planetesimal size in a disk (because the mutual escape velocity sets how dynamically hot the bodies can get before gravitational focusing is suppressed), a direct measurement of the semimajor axes of the colliding planetesimals is not possible.
+Furthermore, as will demonstrate next, collisions due to bodies in resonance do not have a significant effect on the final shape of the radial dust distribution.
 
@@
 density of 1 g cm$^{-3}$ and an eccentricity of 0.05, the damping timescale is $4 \times 10^{-3}$ years. This is orders of magnitude smaller than the 
-collision timescale, therefore we conclude that collisionally generated dust grains will immediately couple to the gas.
+orbital timescale, therefore we conclude that collisionally generated dust grains will immediately couple to the gas.
 
@@
 of 0.02 AU to assemble the collision locations into a radial distribution. Most strikingly, the bump that was present near the 2:1 resonance is no 
-longer present in cylindrical distance space, although it suddenly appears again in the e3m2 simulation. The dip that is present near the 3:1 MMR 
-also disappears and instead presents as a bump in the e3m2 case. To determine how the resonant bodies actually contribute to the radial collision 
+longer visible in cylindrical distance space, although it suddenly appears again in the e3m2 simulation. The dip that is visible near the 3:1 MMR 
+also becomes a bump in the highest eccentricity case. To determine how the resonant bodies actually contribute to the radial collision 
 profile, we excluded collisions that fall between $2.495 < a < 2.505$ AU (near the 3:1 resonance) and between $3.2 < a < 3.35$ AU (near the 2:1 
-resonance), which is shown by the orange curve. Qualitatively, none of the bump or dip features present are changed by making this exclusion. This 
-suggests that the features near resonance seen in semimajor axis space become 'smeared out' in cylindrical distance space due to the large spread 
+resonance), which is shown by the orange curve. Qualitatively, none of the bump or dip features present are removed by making this exclusion. This 
+suggests that the features near resonance seen in semimajor axis space become smeared out in cylindrical distance space due to the large spread 
 in eccentricity and orbital orientation.
 
-This also suggests that the features seen in figure \ref{fig:coll_hist_r} are being produced by bodies outside of resonance. To further understand this, 
-we revisit the nonaxisymmetric structure seen in figure \ref{fig:xy}. In figure \ref{fig:coll_polar_e}, we compare the radial collision profile to the polar 
-structure seen in the e1m2, e2m2 and e3m2 simulations. In the lowest forced eccentricity case, the pileups near the edges of the resonances line up 
-with the boundaries of the dip feature seen in the radial collision profile. The locations of the edges of the resonances are calculated using equations 
-\ref{eq:res_fo} and \ref{eq:res_so}. The pileups are especially prominent for the 2:1 resonance. As discussed previously, the pileups and gaps seen 
-in polar coordinates follow the position of the giant planet in its orbit.
+This also suggests that the most prominent bumps and dips seen in figure \ref{fig:coll_hist_r} are being produced by bodies outside of resonance. To 
+further understand this, we consider the nonaxisymmetric structure seen in figure \ref{fig:xy}. In figure \ref{fig:coll_polar_e}, we compare the radial 
+collision profile to the radial structure seen in the e1m2, e2m2 and e3m2 simulations. In the lowest forced eccentricity case, the pileups near the 
+edges of the resonances line up with the boundaries of the dip feature seen in the radial collision profile. The locations of the edges of the 
+resonances are calculated using equations \ref{eq:res_fo} and \ref{eq:res_so}. The pileups are especially prominent for the 2:1 resonance. As 
+discussed previously, the pileups and gaps seen in polar coordinates follow the position of the giant planet in its orbit, which is shown by the vertical 
+line.
 
@@
 \citep{2000Icar..143...45R, 2016ApJ...818..159T}, we could not find a satisfactory explanation for why it happens and will provide one here. As 
-mentioned previously, the circulation frequency of the critical angle slows as one approaches the edge of the resonance from the outside. Following 
-the pendulum analogy, this is equivalent to reaching the point where the pendulum becomes suspended in the vertical position. When the critical 
-angle stays relatively stationary during an encounter, the net torque will drive the longitude of pericenter towards the point of conjunction 
-\citep{1976ARA&A..14..215P}.  This is the basic mechanism that causes isolated resonances to be stable. Inside of resonance, the critical angles 
-librates about some value and this configuration is maintained. Just outside of resonance, however, the critical angle slowly drifts away, with the drift 
-direction changing sign across the resonance. The net result of this is that bodies near the edge of the resonance experience a torque from that 
-planet that temporarily drives their pericenters toward the current orbital position of the planet. After the encounter ends, differential rotation of the 
-disk slowly destroys the configuration over part of an orbit. This explains why the concentration of planetesimals appears to 'follow' the the planet.
+mentioned in section \ref{sec:dynamics}, the circulation frequency of the critical angle slows as one approaches the edge of the resonance from the outside.
+Following the pendulum analogy, this is equivalent to approaching the point where the pendulum becomes suspended in the vertical position.
+When the critical angle stays relatively stationary during an encounter, the net torque will drive the longitude of pericenter towards the point of conjunction \citep{1976ARA&A..14..215P}.
+This is the basic mechanism that causes isolated resonances to be stable.
+Inside of resonance, the critical angles librates about some value and this configuration is maintained.
+Just outside of resonance, however, the critical angle slowly drifts away, with the drift direction changing sign across the resonance.
+The net result of this is that bodies just outside of the resonance experience a torque from that planet that temporarily drives their pericenters toward the current orbital position of the planet.
+After the encounter ends, differential rotation of the disk slowly destroys the configuration over part of an orbit.
+As the planet passes by, adjacent planetesimals near the resonance edges temporarily align themselves in this configuration.
+This explains why the concentration of planetesimals appears to 'follow' the the planet.
 
@@
 planetesimals near resonance would be randomly aligned, and the axisymmetric structure should become washed out. In the case with a perturbing 
-planet planet on a circular orbit, this structure is still present (see figure 3 of \citet{2016ApJ...818..159T}).
+planet planet on a circular orbit, this structure is still present (see figure 3 of \citet{2016ApJ...818..159T}). The only relation between the structure of 
+the gaps in the disk and the path of a resonant particle in the corotating frame is that both phenomena produce the same symmetries, which depend 
+on the resonance being considered.
 
-With no secular forcing, this dynamical phenomena would produce an underdensity in the radial surface density profile near the center of the 
+With no secular forcing, this dynamical phenomena should produce an underdensity in the radial surface density profile near the center of the 
 resonance and an overdensity at each edge in cylindrical distance space. When a forced eccentricity is introduced, the edges of the resonance 
@@
 exactly what appears to be happening in the middle panel of figure \ref{fig:coll_polar_e}. As the forced eccentricity is increased further, a region 
-forms at the center of the resonance where planetesimals from both sides of the resonance spend time (although not simultaneously). When this 
+forms at the center of the resonance where planetesimals on both sides of the resonance spend time (although not simultaneously). When this 
 occurs, a bump feature forms in the collision profile near the center of the resonance. This is apparent in the bottom panel of figure 
@@
 Although the same phenomenon appears to be happening near the 3:1 MMR, the pileups at the edges of the resonance are not as well defined. We 
-attribute this to the longer synodic period, compared to the 2:1 MMR. In addition, a number of other nearby resonances, including the 7:2 (at 2.25 
-AU), the 10:3 (at 2.33 AU), the 8:3 (at 2.71 AU) and the 5:2 (at 2.82 AU) also likely are contributing to the collision profile in cylindrical distance 
+attribute this to the more comlex symmetry, compared to the 2:1 MMR. In addition, a number of other nearby resonances, including the 7:2 (at 
+2.25 AU), the 10:3 (at 2.33 AU), the 8:3 (at 2.71 AU) and the 5:2 (at 2.82 AU) also likely are contributing to the collision profile in cylindrical distance 
 space near the 3:1. The width of the 3:1 MMR is also much narrower than the 2:1, which means that any dip or bump features produced by it would 
@@
 Aaron add in some more text here describing exactly how the profiles were created. Should we add a separate figure to show the flux profiles, or 
-include them in figures 6 and 7 like I've started to do here?
+simply include them as an extra curve in the side panels of figures 6 and 7 like I've started to do here?
 
@@
 cases, the eccentricity of the perturbing planet is set to $e_{jup}$. Changes in the apocenter and pericenter distances of the edges of the 
-resonances are entirely due to changes in the libration width here. For the e2m1 and e2m2 simulations, the inner apocenter and outer pericenter 
+resonances are entirely due to changes in the resonance width. For the e2m1 and e2m2 simulations, the inner apocenter and outer pericenter 
 distances near the 2:1 MMR are quite similar and no strong features appear in the collision profile near this region. For the e2m3 case, the edges of 
-the resonances are sufficiently far apart to allow a gap near the center of the 2:1 resonance to appear in the collision profile.
+the resonances are sufficiently separated to allow a gap near the center of the 2:1 resonance to appear in the collision profile.
 
@@
 
-The simple 'bump' vs 'dip' structure that we expect to reveal itself in the dust emission from colliding planetesimals in near-resonance with a giant 
+The simple bump vs dip structure that we expect to reveal itself in the dust emission from colliding planetesimals in near-resonance with a giant 
 planet could potentially be used to place constraints on the mass and eccentricity of the planet. Near the 2:1 MMR, the central dip feature is only 
 produced when bodies at the edges of the resonance stay sufficiently separated in cylindrical distance over the course of an orbit. This is achieved 
-when either the resonance width is large and the forced eccentricity is small. Conversely, the bump feature is produced when there is a sufficiently 
-large amount of overlap between the apocenters and pericenters of the inner and outer edges of the resonance, respectively. This is achieved when 
-the resonance is narrow and the forced eccentricity is large.
+when either the resonance width is large and the forced eccentricity is small. The bump feature, on the other hand, is produced when there is a 
+sufficiently large amount of overlap between the apocenters and pericenters of the inner and outer edges of the resonance, respectively. This is 
+achieved when the resonance is narrow and the forced eccentricity is large.
 
-In figure \ref{fig:bump_dip_diag}, we show the constraints that the presence of a bump or a dip places on the values of $(m_{g}, e_{g})$. A dip is 
-produced by sufficiently low eccentricity and high mass planets, while a bump is produced by a low mass or high eccentricity planet. The parameter 
+In figure \ref{fig:bump_dip_diag}, we show the constraints that the presence of a bump or a dip places on possible values of $(m_{g}, e_{g})$. A dip 
+is produced by a sufficiently low eccentricity, high mass planet, while a bump is produced by a high eccentricity, low mass planet. The parameter 
 choices for the five simulations presented in the previous section are shown by the black dots. Between the two dashed lines, the overlap between 
 the aphelion and perihelion distances of the inner and outer edges of the resonance is smaller than the width of the resonance. In this region, the 
-overdense regions on each side of the resonance spend roughly equal amounts of time at all possible cylindrical distances, and no strong feature 
-appears in the collision profile.
+overdense regions on each side of the resonance spend roughly equal amounts of time at all possible distances, and no strong feature appears in 
+the collision profile.
 
-Because the strength of the 2:1 resonance scales with $e_{g}$ and  $m_{g}$, a sufficiently low mass and low eccentricity planet will not induce 
+Because the strength of the 2:1 resonance scales with $e_{g}$ and  $m_{g}$, a sufficiently low mass and low eccentricity planet will not create 
 enough of a perturbation in the planetesimal disk to produce a detectable bump or dip feature. The colored contours in figure \ref{fig:bump_dip_diag} 
 indicate the relative strength of the resonance as these quantities are varied. Although the resonance strength is equally sensitive to changes in 
-mass and eccentricity, the peri - apocenter overlap of the resonance edges is more sensitive to changes in eccentricity. This is also consistent with 
-what was seen in figure \ref{fig:coll_polar_m}, where changing $m_{g}$ by a factor of 4 produced very minimal changes to the resulting dust profile.
+mass and eccentricity, the peri - apocenter overlap of the resonance edges is more sensitive to changes in eccentricity. This is because changes to 
+eccentricity affect both the resonance width and the forced eccentricity. As we showed in figure \ref{fig:coll_polar_m}, changing $m_{g}$ by a factor 
+of 4 produced very minimal changes to the resulting dust profile.
 
@@
 produce structure in the collision profile as a function of semimajor axis. Furthermore, we find that a series of distinctly different features appear 
-when collisions are sorted by cylindrical distance from the central star. If enough gas from the protoplanetary disk is still present, dust generated 
-from planetesimals collisions will immediately couple to it and fall onto a circular orbit. In this case, the radial dust emission profile, which can be 
-observed in the sub-mm, directly traces the radial collision rate and therefore the dynamical activity of the planetesimals.
+when collisions are ordered by cylindrical distance from the central star. If enough gas from the protoplanetary disk is still present, dust generated 
+from planetesimal-planetesimal collisions will immediately couple to the gas and fall onto a circular orbit. In this case, the radial dust emission profile, 
+which can be observed at mm wavelengths, directly traces the radial collision rate and therefore the dynamical activity of the planetesimals.
 
-Near the interior 2:1 MMR, we find that a distinct bump or dip feature is generated in the dust profile. The presence of one of these two structures 
-can used to constrain the mass and eccentricity of the perturbing planet. For a high mass, low eccentricity planet, a dip will form in the dust profile 
-because the edges of the resonance, where many collisions occur, stay sufficiently separated. If the planet has a low enough mass (which shrinks 
-the size of the resonance) or is sufficiently eccentric (which decreases the separation between the apocenter and pericenter distances of the edges 
-of the resonance), a bump will instead form. We tested this hypothesis for five different combinations of the planet's mass and eccentricity and found 
-that a distinct bump or dip signature is produced as long as the planet properties are sufficiently far from the dividing line in parameter space. This 
-diagnostic is more useful for massive, eccentric planets, because the strength of the resonant perturbations scale linearly with both of these 
-quantities.
+Near the interior 2:1 MMR, we find that a distinct bump or dip feature is generated in the dust profile, depending on the properties of the perturbing 
+planet. The presence of one of these two structures can used to constrain the mass and eccentricity of the planet. For a high mass, low eccentricity 
+planet, a dip will form in the dust profile because the edges of the resonance, where many collisions occur, stay sufficiently separated. If the planet 
+has a low enough mass (which shrinks the size of the resonance) or is sufficiently eccentric (which decreases the separation between the apocenter 
+and pericenter distances of the edges of the resonance), a bump will instead form. We tested this hypothesis for five different combinations of the 
+planet's mass and eccentricity and found that a distinct bump or dip signature is produced as long as the planet properties are sufficiently far from 
+the dividing line in parameter space. This diagnostic is more useful for massive, eccentric planets, because the strength of the resonant 
+perturbations scale linearly with both of these quantities.
 
-The results presented here appear to be broadly consistent with \citet{2016ApJ...818..159T}, which used collisionless, massless test particles to 
-model a planetesimal disk perturbed by a planet. In their case, a dip feature can be seen in the azimuthally averaged surface density profile, 
-although they did not test a high enough eccentricity planet in any of their simulations to produce a bump. Another thing to note is that the gap 
-morphology seen by \citet{2016ApJ...818..159T} was markedly different for the 2:1 exterior MMR. Whether this would alter the radial collision profile 
-for the exterior, rather than the interior 2:1 resonance, is not immediately clear.  Given that the solid surface density diminishes with distance 
-($\sim r^{-3/2}$ for the MMSN \citep{1981PThPS..70...35H}), exterior resonances may not be quite as useful for this type of measurement.
+The results presented here appear to be broadly consistent with the planetesimal dynamics seen by \citet{2016ApJ...818..159T}. In their case, a dip 
+feature can be seen in the azimuthally averaged surface density profile, although they did not test a high enough eccentricity planet in any of their 
+simulations to produce a bump. Another thing to note is that the gap morphology seen by \citet{2016ApJ...818..159T} was markedly different for the 
+2:1 exterior MMR. Whether this would alter the radial collision profile for the exterior, rather than the interior 2:1 resonance, is not immediately clear.  
+Given that the solid surface density diminishes with distance ($\sim r^{-3/2}$ for the MMSN \citep{1981PThPS..70...35H}), exterior resonances may 
+not be quite as useful for this type of measurement, however.
 
-Compared to using the gap around the planet as a diagnostic \citep{2013ApJ...777L..31D, 2016ApJ...820...29D}, measuring variations in the dust 
-emission near higher order MMRs is much more subtle and requires much higher spatial resolution and sensitivity. As we have shown, the bump vs 
-dip feature near the 2:1 MMR is marginally detectable with ALMA for the nearest protoplanetary disks. Another complicating factor is that the inner 
-$\sim$ 10 AU of most protoplanetary disks are optically thick in the sub-mm. The solution to this problem is to instead observe in the radio, which 
-achieves much poorer resolution. However, future radio facilities like the NG-VLA are expected to achieve sub-AU resolution for nearby planet-
-forming disks \citep{2018ASPC..517..147R}. In the more near-term, techniques like Gaussian process fitting present a promising way to recover 
-substructure at sub-beam resolution \citep{2020arXiv200507709J}.
+Compared to using the corotationg gap opened by the planet as a diagnostic \citep{2013ApJ...777L..31D, 2016ApJ...820...29D}, measuring 
+variations in the dust emission near MMRs is much more subtle and requires much higher spatial resolution and sensitivity. As we have shown, the 
+bump vs dip feature near the 2:1 MMR is marginally detectable with ALMA for the nearest protoplanetary disks. Another complicating factor is that 
+the inner $\sim$ 10 AU of most protoplanetary disks are optically thick in the sub-mm. The solution to this problem is to instead observe at longer 
+wavelengths where the inner disk is optically thin. This comes at the expense of much poorer resolution. However, future radio facilities like the NG-
+VLA are expected to achieve sub-AU resolution for nearby planet-forming disks \citep{2018ASPC..517..147R}. In the more near-term, techniques 
+like Gaussian process fitting present a promising way to recover substructure at sub-beam resolution \citep{2020arXiv200507709J}.
 

### 2020-05-21 makeFig.py

@@ -274,7 +274,7 @@ def make_coll_polar_e():
 	ax00.set_xlabel('Rel. # of Collisions and Flux')
 	ax01.set_xlabel('Azimuth')
 	ax00.set_ylabel('Cylindrical Distance [AU]')
-	ax01.set_title(r'e$_{g}$ = 1/2 e$_{jup}$')
+	ax01.set_title(r'e$_{g}$ = 1/2 e$_{jup}$ (e1m2)')
 
 	# Moderate eccentricity case
 	ecc = ecc_jup
@@ -331,7 +331,7 @@ def make_coll_polar_e():
 	ax10.set_xlabel('Rel. # of Collisions and Flux')
 	ax11.set_xlabel('Azimuth')
 	ax10.set_ylabel('Cylindrical Distance [AU]')
-	ax11.set_title(r'e$_{g}$ = e$_{jup}$')
+	ax11.set_title(r'e$_{g}$ = e$_{jup}$ (e2m2)')
 
 	# High eccentricity case
 	ecc = ecc_jup*2
@@ -385,7 +385,7 @@ def make_coll_polar_e():
 	ax20.set_xlabel('Rel. # of Collisions and Flux')
 	ax21.set_xlabel('Azimuth')
 	ax20.set_ylabel('Cylindrical Distance [AU]')
-	ax21.set_title(r'$e_{g}$ = 2 e$_{jup}$')
+	ax21.set_title(r'$e_{g}$ = 2 e$_{jup}$ (e3m2)')
 
 	plt.savefig(file_str, format=fmt, bbox_inches='tight')
 
@@ -453,7 +453,7 @@ def make_coll_polar_m():
 	ax00.set_xlabel('Rel. # of Collisions and Flux')
 	ax01.set_xlabel('Azimuth')
 	ax00.set_ylabel('Cylindrical Distance [AU]')
-	ax01.set_title(r'M$_{g}$ = 1/2 M$_{jup}$')
+	ax01.set_title(r'M$_{g}$ = 1/2 M$_{jup}$ (e2m1)')
 
 	# Moderate mass case
 	mass = m_jup
@@ -510,7 +510,7 @@ def make_coll_polar_m():
 	ax10.set_xlabel('Rel. # of Collisions and Flux')
 	ax11.set_xlabel('Azimuth')
 	ax10.set_ylabel('Cylindrical Distance [AU]')
[…]

### 2020-06-16 makeFig.py
Add collision PDF data for use with image simulator

@@ -1244,8 +1244,31 @@ def make_wander_res_scale():
 	plt.tight_layout()
 	plt.savefig(file_str, format=fmt, bbox_inches='tight')
 
-make_coll_polar_e()
-make_coll_polar_m()
+def gen_coll_PDF():
+	c = coll_e1
+	coll_bins_r_e1, coll_pdf_r_e1 = kde(c['dist1'])
+
+	c = coll_e
+	coll_bins_r_e, coll_pdf_r_e = kde(c['dist1'])
+
+	c = coll_e2
+	coll_bins_r_e2, coll_pdf_r_e2 = kde(c['dist1'])
+
+	c = coll_m1
+	coll_bins_r_m1, coll_pdf_r_m1 = kde(c['dist1'])
+
+	c = coll_m2
+	coll_bins_r_m2, coll_pdf_r_m2 = kde(c['dist1'])
+
+	np.savetxt('e1m2_coll.txt', [coll_bins_r_e1, coll_pdf_r_e1])
+	np.savetxt('e2m2_coll.txt', [coll_bins_r_e, coll_pdf_r_e])
+	np.savetxt('e3m2_coll.txt', [coll_bins_r_e2, coll_pdf_r_e2])
+	np.savetxt('e2m1_coll.txt', [coll_bins_r_m1, coll_pdf_r_m1])
+	np.savetxt('e2m3_coll.txt', [coll_bins_r_m2, coll_pdf_r_m2])
+
+gen_coll_PDF()
+#make_coll_polar_e()
+#make_coll_polar_m()
 #bump_dip_diag2()
 make_xy()
 make_ae()

### 2020-06-16 main_aaron.tex
Added aaron's working file

--- 2020-05-21 main.tex
@@
 \bibliographystyle{aasjournal}
+
+\newcommand{\ACBc}[1]{\textcolor{red}{#1}}
 
@@
 \citep{2015ApJ...808L...3A, 2016Sci...353.1519P, PhysRevLett.117.251101, 2016ApJ...820L..40A, 2016Natur.535..258C} in the emission provide 
-diagnostics for the physical processes that drive the evolution of the disks. In some cases, these gap features are argued to be an indicator for the 
-presence of a giant planet, either embedded in the disk \citep{2015MNRAS.453L..73D} or orbiting externally. A giant perturber can influence the 
-structure of the continuum emission in a number of ways. A misaligned giant planet can produce nonaxisymmetric features such as warps 
-\citep{2001A&A...370..447A}. Highly eccentric perturbers can produce even more complicated structures through secular interactions 
-\citep{2014MNRAS.443.2541P, 2015MNRAS.448.3679P}. Mean motion resonances (MMRs) have been shown to open gaps as well 
+diagnostics for the physical processes that drive the evolution of the disks.
+In \sout{some cases}\ACBc{many gas-rich systems}, these gap features are argued \sout{to be an indicator for}\ACBc{to indicate} the
+presence of a giant planet, either embedded in the disk \citep{2015MNRAS.453L..73D} or orbiting externally, \ACBc{although the details of gas-dust interactions can have strong effects on the resulting morphologies (Dong).}
+\ACBc{In gas-poor/debris systems,} a giant perturber can \ACBc{also} influence the 
+structure of the \ACBc{dust} continuum emission \sout{ in a number of ways}. \ACBc{For example,} a misaligned giant planet can produce nonaxisymmetric features such as warps 
+\citep{2001A&A...370..447A}, highly eccentric perturbers can produce \sout{even more complicated} structures through secular interactions 
+\citep{2014MNRAS.443.2541P, 2015MNRAS.448.3679P}\ACBc{, and} mean motion resonances (MMRs) \sout{have been shown to open gaps as well }\ACBc{can open gaps}
 \citep{2015ApJ...798...83N, 2016ApJ...818..159T, 2018ApJ...857....3T}.
 
-Collisions between planetesimals are thought to be a significant source of dust for many young circumstellar disks 
-\citep[see][]{2008ARA&A..46..339W}. An expanding debris cloud from a planetesimal collision was recently detected in the 
-Fomalhut system \citep{2020PNAS..117.9712G}. Although some amount of primordial dust is likely still present during the planet formation process, 
+Collisions between planetesimals are thought to be \sout{a significant}\ACBc{the principal} source of dust for \sout{many young circumstellar disks}{debris disks}. 
+\citep[see][]{2008ARA&A..46..339W}.  Although some amount of primordial dust is likely still present during the \sout{planet formation process}\ACBc{early stages of debris disk evolution}, 
 ongoing collisions between small bodies will augment this and could be used to trace the underlying dynamical activity of the planetesimals. 
-\citet{2013ApJ...777L..31D} showed that collisional dust generated near the gap formed by a giant planet in a planetesimal disk should produce a 
+\ACBc{This process was directly detected when the putative object Fomalhaut b was confirmed to be an} expanding debris cloud\ACBc{, most likely} from a planetesimal collision \sout{was recently detected in the
+Fomalhaut system} \citep{2020PNAS..117.9712G}.
+
+\citet{2013ApJ...777L..31D} showed that collisional dust \ACBc{that is} generated near the gap \sout{formed}\ACBc{opened} by a giant planet in a planetesimal disk should produce a 
 distinctly observable marker that could be used to infer the presence of the planet. In a followup study, it was found that morphological differences in 
 the dust emission could be used to determine whether the planet had a circular or eccentric orbit \citep{2016ApJ...820...29D}.
-
-Substructure due to mean-motion resonances (MMRs) with a giant planet may hold additional clues which 
+\ACBc{Moreover,} substructure due to mean-motion resonances (MMRs) with a giant planet may hold additional clues \sout{which}\ACBc{that} 
 could be used to constrain the properties of the planet.  The width of a resonance is set by both the mass of the perturbing planet, along with the 
@@
 explore the collision rate structure of the planetesimal disk in the vicinity of mean motion resonances. In particular, we would like to 
-determine: 1. whether MMRs leave a detectable signature in the collisionally-generated dust. 2. If these signatures can be used to determine or 
+determine \ACBc{(1)} whether MMRs leave a detectable signature in the collisionally-generated dust\ACBc{, and (2) whether} these signatures can be used to determine or 
 constrain the orbital properties of the perturbing planet.
+
+ \ACBc{[Feel free to omit this, particularly because it has a self citation, but I think it is important to highlight that your results could be relevant beyond debris systems]  While the focus here is on the evolution of planetesimal disks in general, with the most direct application being debris systems, we note that the results may be relevant for interpreting structures observed in young, gas-rich disks.
+For example, assuming giant planet formation requires first the presence of planetesimals, then systems such as HL Tau that have purported embedded giant planets, could have localized regions of dust enhancement due to the corresponding planetesimal collisions  \citep{2017ApJ...850..103B}.
+The main difference between such cases and debris disks is that the dust in the former situation couples to gas.
+}
 
@@
 
-\begin{equation}\label{eq:fd_so}
-	f_{d} (\alpha) = \frac{1}{8} \left[ -5(p+q) + 4(p+q)^{2} - 2 \alpha D + 4(p+q) \alpha D + \alpha^{2} D^{2} \right] b^{p+q}_{1/2},
-\end{equation}
+\begin{eqnarray}\label{eq:fd_so}
+	f_{d} (\alpha) &=& \frac{1}{8} \left[ -5(p+q) + 4(p+q)^{2} - 2 \alpha D \right. \\ \nonumber
+	                      & + & \left. 4(p+q) \alpha D + \alpha^{2} D^{2} \right] b^{p+q}_{1/2},
+\end{eqnarray}
 
@@
 factor of 4 to the keep longitude of perihelia of planetesimals near the inner edge of the disk from drifting too far over the course of our 
-integrations.
+integrations. \ACBc{Define too far.}
 
@@
     \includegraphics[width=\textwidth]{figures/xy.png}
-    \caption{The positions of the remaining planetesimals at the end of the e1m2 (left), e2m2 (center) and e3m2 (right) simulations. The red dot 
+    \caption{\ACBc{fix aspect ratino so a circle is a circle.}  The positions of the remaining planetesimals at the end of the e1m2 (left), e2m2 (center) and e3m2 (right) simulations. The red dot 
     indicates the position of the giant planet and the dashed line points in the direction of the planet's longitude of perihelion. Non-axisymmetric gaps 
@@
     \includegraphics[width=0.5\textwidth]{figures/ae.png}
-    \caption{The semimajor axes and eccentricities of the remaining planetesimals are shown, with the locations of prominent resonances indicated 
+    \caption{\ACBc{annotations need to be larger.}  The semimajor axes and eccentricities of the remaining planetesimals are shown, with the locations of prominent resonances indicated 
     by the vertical dashed lines. Libration of the critical angle drives large variations in eccentricity, which produce spikes in the a-e plane. Between 

### 2020-06-17 main_aaron.tex
Updated intro and made comments farther down in the manuscript.  Still working on it.

@@
 
- \ACBc{[Feel free to omit this, particularly because it has a self citation, but I think it is important to highlight that your results could be relevant beyond debris systems]  While the focus here is on the evolution of planetesimal disks in general, with the most direct application being debris systems, we note that the results may be relevant for interpreting structures observed in young, gas-rich disks.
-For example, assuming giant planet formation requires first the presence of planetesimals, then systems such as HL Tau that have purported embedded giant planets, could have localized regions of dust enhancement due to the corresponding planetesimal collisions  \citep{2017ApJ...850..103B}.
-The main difference between such cases and debris disks is that the dust in the former situation couples to gas.
+ \ACBc{[UPDATED to take into account further discussion later in the article.
+Much of the discussion above is on debris discs, so I am trying to reframe the discussion for what follows later in the manuscript.
+Feel free to omit this, particularly because it has a self citation, but I think it is important because the intro is a bit off point otherwise.]  The focus here is on the collisional evolution of planetesimal disks in general, and the results are not intended to be confined to debris disks.
+During planet formation, which occurs in the presence of planetesimals and gas, the coupling between gas and collisionally-produced dust could lead to observable signatures \citep{2017ApJ...850..103B}, as we will explore.
 }
@@
 respectively. $e_{g}$ and $\varpi_{g}$ are the eccentricity and longitude of pericenter of the giant and $b^{j}_{s} (\alpha)$ is a 
-Laplace coefficient given by \citep{2000ssd..book.....M} as
+Laplace coefficient given by \citep{2000ssd..book.....M} as \ACBc{[fixed $cos$ to $\cos$.]}
 
 \begin{equation}\label{eq:lap}
-	b_{s}^{j}(\alpha) = \frac{1}{2 \pi} \int_{0}^{2 \pi} \frac{cos \, j \theta \, d \theta}{\left( 1 - 2 \alpha \, cos \theta + \alpha^2 \right)^{s}}.
+	b_{s}^{j}(\alpha) = \frac{1}{2 \pi} \int_{0}^{2 \pi} \frac{\cos \, j \theta \, d \theta}{\left( 1 - 2 \alpha \, \cos \theta + \alpha^2 \right)^{s}}.
 \end{equation}
@@
 
-In regions where there are commensurabilities between frequencies, secular theory breaks down and bodies are subject to strong 
+In regions where there are commensurabilities between frequencies, \ACBc{Laplace-Langrange} secular theory breaks down and bodies are subject to strong 
 perturbations. For the purposes of this study, we will ignore secular resonances, which generally occur on rather large timescales 
@@
 \noindent where  $p$ and $q$ are integers $>$ 0 and the unprimed and primed quantities correspond to the perturber and the body 
-being perturbed, respectively. If the perturber is much more massive than the other body, the condition for MMR is set  by the semi-major 
+being perturbed, respectively.
+\ACBc{[Might as well state the order and degree of the resonance to fully define the equation.]} If the perturber is much more massive than the other body, the condition for MMR is set  by the semi-major
 axes of the two bodies by
@@
 equlibrium value, while this angle will circulate outside of resonance. For small eccentricities, this behavior is analogous to the motion of a 
-pendulum. Variations in the critical angle are coupled to changes in the mean motion and semimajor axis \citet{2000ssd..book.....M}. An important 
-point to note, which will become important later, is that the variation frequency of this angle approaches zero near the edge of a resonance. The 
+pendulum. Variations in the critical angle are coupled to changes in the mean motion and semimajor axis \citep{2000ssd..book.....M}\ACBc{[fixed citation]}. An important 
+point to note, which \sout{will become important}\ACBc{we will come back to} later, is that the variation frequency of this angle approaches zero near the edge of a resonance. The 
 width of a resonance can be defined by determining the largest variation in semimajor axis that permits librational, rather than circulatory motion of 
@@
 
-The net result of this is that MMRs will produce spikes in the semimajor axis - eccentricity distribution of a planetesimal disk. In order to 
+The net result of this is that MMRs will produce spikes in the semimajor \ACBc{axis-eccentricity} distribution of a planetesimal disk. In order to 
 preserve the Jacobi energy, equation \ref{eq:tiss} predicts that these spikes will tend to curve away from the perturbing body. This lowers the 
@@
 
-In total, five simulations are run. The first is a 'nominal' case, in which the perturbing planet's mass and eccentricity are set to that of Jupiter's. 
+In total, five simulations are run\ACBc{[Reference table!]}. The first is a `nominal' \ACBc{[fixed quotes]} case, in which the perturbing planet's mass and eccentricity are set to that of Jupiter's. 
 In the other four cases, the mass (eccentricity) is increased or decreased by a factor of two, while the eccentricity (mass) is held at the nominal 
-value. In all cases, the perturbing giant is placed on a 5.2 AU orbit around a 1 $M_{\odot}$ star. The planetesimal disk extends from 2.2 to 3.8 
+value.
+In all cases, the perturbing giant is placed on a 5.2 AU orbit around a 1 $M_{\odot}$ star\ACBc{, although the overall dynamics presented here are scalable to different scales [true, right?]}.
+The planetesimal disk extends from 2.2 to 3.8
 AU, which covers the two most prominent mean motion resonances with the giant planet, the 2:1 at 3.27 AU and the 3:1 at 2.5 AU. The 
@@
 \noindent and a forced component is added to $h$ according to equation \ref{eq:eforced} (where we have set $\varpi_{g}$ = 0).
+\ACBc{[question and minor.
+Doesn't the convention place the cosine with k or q (for inclination).
+I tend to recall this because the mnemonic device is that the hard sound goes with the cosine.
+I do not have my standard references on me to verify!
+Feel free to ignore me.]}
 
@@
 
-An additional timescale is set by the dynamical time of the planetesimals ($\sim 1/\sqrt{G \rho}$), which is about 45 minutes. To 
+An additional timescale is set by the dynamical time of the planetesimals ($\sim 1/\sqrt{G \rho}$), which is about 45 minutes. To o i
 resolve the base time step and the dynamical timescale of planetesimals simultaneously, we use a two-tiered time stepping scheme. 
@@
 which the radii of all bodies are inflated by a factor of 2.5. Any bodies with imminent collisions predicted using the inflated radii are 
-placed on a time step that is a factor of 16 smaller than the orbital time step. The purpose of two-tiered scheme is to properly resolve 
+placed on a time step that is a factor of 16 smaller than the orbital time step. The purpose of \ACBc{the} two-tiered scheme is to properly resolve 
 the gravitational interactions between any bodies that undergo a close encounter. This prevents the coarser base time step from 
@@
     \includegraphics[width=\textwidth]{figures/xy.png}
-    \caption{\ACBc{fix aspect ratino so a circle is a circle.}  The positions of the remaining planetesimals at the end of the e1m2 (left), e2m2 (center) and e3m2 (right) simulations. The red dot 
+    \caption{\ACBc{[Is this aspect ratio right?
+I.e., is a circle a circle?]}  The positions of the remaining planetesimals at the end of the e1m2 (left), e2m2 (center) and e3m2 (right) simulations.
+The red dot
     indicates the position of the giant planet and the dashed line points in the direction of the planet's longitude of perihelion. Non-axisymmetric gaps 
@@
 similar substructure, which is most noticeable near the 2:1 MMR, reveals itself in \citet{2000Icar..143...45R} (see bottom panel of figure 3) and 
-\citet{2016ApJ...818..159T} (figure 3). It is worth noting that \citet{2000Icar..143...45R} started with a completely cold planetesimal disk and a Jupiter 
-mass planet on a circular, coplanar orbit. The presence of these features seems robust to the choice of initial conditions.
+\citet{2016ApJ...818..159T} (figure 3).
+\ACBc{This structure was also seen in the \citet{2017ApJ...850..103B} simulations, although it was not reported at the time (see Appendix BLAH).}  It is worth noting that \citet{2000Icar..143...45R} started with a completely cold planetesimal disk and a Jupiter
+mass planet on a circular, coplanar orbit. \ACBc{ \citet{2017ApJ...850..103B} used a similar setup.  Thus, t}he presence of these features seems robust to the choice of initial conditions.
 
@@
     \caption{In semimajor axis space, prominent features appear near the 3:1 and 2:1 MMRs. Near the 3:1, the collision
-    rate decreases from its unperturbed value, while an enhancement apepars near the 2:1.\label{fig:coll_hist_a}}
+    rate decreases from its unperturbed value, while an enhancement apepars near the 2:1.
+\ACBc{[Suggest state bin width and mention density estimator -- basically, many people will just look at the figures, so some of this information is appropriate to repeat.
+]} .\label{fig:coll_hist_a}}
 \end{center}

### 2020-06-19 main_aaron.tex
Included additional edits and a new section on ALMA

@@
 
-Operating under this assumption, a map of the relative concentration of second-generation dust can be constructed from the cylindrical 
+Operating under this assumption\footnote{\ACBc{As discussed in \cite{2017ApJ...850..103B}, the local generation of second-generation dust is only one consideration.
+The dust will also evolve spatially due to drag effects, but can also evolve in size or be re-accreted onto planetesimals.
+For simplicity, we focus on local dust sourcing only while acknowledging that subsequent evolution could affect the morphology.}}, a map of the relative concentration of second-generation dust can be constructed from the cylindrical
 distance at which the collisions occur. This is shown in figure \ref{fig:coll_hist_r}. Similar to figure \ref{fig:coll_hist_a}, we use a KDE with a bandwidth 
@@
 
-This also suggests that the most prominent bumps and dips seen in figure \ref{fig:coll_hist_r} are being produced by bodies outside of resonance. To 
-further understand this, we consider the nonaxisymmetric structure seen in figure \ref{fig:xy}. In figure \ref{fig:coll_polar_e}, we compare the radial 
-collision profile to the radial structure seen in the e1m2, e2m2 and e3m2 simulations. In the lowest forced eccentricity case, the pileups near the 
-edges of the resonances line up with the boundaries of the dip feature seen in the radial collision profile. The locations of the edges of the 
-resonances are calculated using equations \ref{eq:res_fo} and \ref{eq:res_so}. The pileups are especially prominent for the 2:1 resonance. As 
-discussed previously, the pileups and gaps seen in polar coordinates follow the position of the giant planet in its orbit, which is shown by the vertical 
+This also suggests that the \sout{most} prominent bumps and dips seen in figure \ref{fig:coll_hist_r} are \sout{being}\ACBc{mainly} produced by bodies outside of resonance\ACBc{, although the resonant population does make some of the features more pronounced.
+[I think this is more accurate to write.]} To
+further understand this, we consider the nonaxisymmetric structure seen in figure \ref{fig:xy}. \ACBc{We compare} in figure \ref{fig:coll_polar_e}\sout{, we compare} the radial 
+collision profile to the radial structure \sout{seen} in the e1m2, e2m2 and e3m2 simulations. In the lowest forced eccentricity case \ACBc{(e1m2)}, the pileups near the 
+edges of the \sout{resonances}\ACBc{2:1 resonance} line up with the boundaries of the dip feature seen in the radial collision profile \ACBc{[I think this needs to be expanded.
+Perhaps something similar to what follows] }.
+The locations of the edges of the
+resonances are calculated using equations \ref{eq:res_fo} and \ref{eq:res_so}.
+The pileups are \sout{especially prominent for the 2:1 resonance}\ACBc{not as pronounced around the other resonances}.
+As
+discussed previously, the \sout{pileups}\ACBc{planetesimal density enhancements} and gaps seen in polar coordinates follow the position of the giant planet in its orbit, which is shown by the vertical
 line.
+\ACBc{For the e2m2 case, the density enhancements take up a much larger radial width, which smears out the corresponding collisional dust profile.
+In the highest forced eccentricity case (e3m2), the density enhancements occur well within an annulus containing the resonant region, completely altering the radial peak-valley dust morphology.}
 
 Although the nonaxisymmetric pileup of bodies near the edges of resonances has been seen previously 
-\citep{2000Icar..143...45R, 2016ApJ...818..159T}, we could not find a satisfactory explanation for why it happens and will provide one here. As 
+\citep{2000Icar..143...45R, 2016ApJ...818..159T}, we could not find a satisfactory explanation for why it happens\sout{ and will provide one here}\ACBc{, which we will try to provide here [this makes the statement a bit more modest and by extension less confrontational, IMO].}.
+As
 mentioned in section \ref{sec:dynamics}, the circulation frequency of the critical angle slows as one approaches the edge of the resonance from the outside.
@@
 This is the basic mechanism that causes isolated resonances to be stable.
-Inside of resonance, the critical angles librates about some value and this configuration is maintained.
+Inside of resonance, the critical \sout{angles}\ACBc{angle} librates about some value and this configuration is maintained.
 Just outside of resonance, however, the critical angle slowly drifts away, with the drift direction changing sign across the resonance.
@@
 As the planet passes by, adjacent planetesimals near the resonance edges temporarily align themselves in this configuration.
-This explains why the concentration of planetesimals appears to 'follow' the the planet.
+This explains why the concentration of planetesimals appears to \sout{'follow'}\ACBc{`follow'} the \sout{the} planet.
 
@@
     \caption{The collision profiles in figure \ref{fig:coll_hist_r} are shown alongside the positions of the planetesimals, in polar coordinates. The 
-    synthetic dust emission profiles are shown in orange. The dashed and solid lines show the pericenter and apocenter of bodies at the edge of the 
+    synthetic dust emission profiles are shown in orange \ACBc{(only for e2m2)}.
+The dashed and solid lines show the pericenter and apocenter\ACBc{, respectively,} of bodies at \sout{the} \ACBc{each} edge of the
     3:1 and 2:1 MMR. In these figures, the longitude of pericenter of the planet lies at $\theta = 0$ and the present position of the planet is indicated 
@@
 
-\citet{2016ApJ...818..159T} provides a different explanation for this phenomenon. Instead, the nonaxisymmetric structure is claimed to be a product 
-of the path that a resonant test particle takes in a frame co-rotating with the planet (see figure 8.4 of \citet{2000ssd..book.....M}). This explanation, 
+\citet{2016ApJ...818..159T} \sout{provides}\ACBc{provide} a different explanation for this phenomenon\sout{.
+Instead,}\ACBc{, suggesting that} the nonaxisymmetric structure is \sout{claimed to be a}\ACBc{the} product
+of the path that a resonant test particle takes in a frame co-rotating with the planet (see figure 8.4 of \citet{2000ssd..book.....M})\ACBc{[This wording is less confrontational.
+]}.
+This explanation,
 however, does not hold for a large collection of planetesimals, especially when there is no forced eccentricity. In such a case, the orbits of 
-planetesimals near resonance would be randomly aligned, and the axisymmetric structure should become washed out. In the case with a perturbing 
-planet planet on a circular orbit, this structure is still present (see figure 3 of \citet{2016ApJ...818..159T}). The only relation between the structure of 
+planetesimals near resonance would be randomly aligned, and the axisymmetric structure should become washed out. \sout{In the case with a}\ACBc{When the} perturbing 
+planet \sout{planet} \ACBc{is} on a circular orbit, this structure is still present (see figure 3 of \citet{2016ApJ...818..159T}\ACBc{ as well as Appendix BLAH}). 
+The only relation between the structure of 
 the gaps in the disk and the path of a resonant particle in the corotating frame is that both phenomena produce the same symmetries, which depend 
-on the resonance being considered.
+on the \ACBc{given} resonance \sout{being considered}.
 
@@
 resonance and an overdensity at each edge in cylindrical distance space. When a forced eccentricity is introduced, the edges of the resonance 
-(indicated by the solid and dashed lines in figure \ref{fig:coll_polar_e}), where the pileups are located, begin to explore a wider range of radii over the 
+(indicated by the solid and dashed lines in figure \ref{fig:coll_polar_e}), where the pileups are located, \ACBc{[I think this description is confusing.
+The resonant region's edges are given by the density enhancements, but the solid and dashed lines indicated the largest excursions of the resonant region.]}begin to explore a wider range of radii over the
 course of a single orbit. If the the aphelion distance of the inner edge becomes comparable to the perihelion distance of the outer edge, the 
@@
 occurs, a bump feature forms in the collision profile near the center of the resonance. This is apparent in the bottom panel of figure 
-\ref{fig:coll_polar_e}.
+\ref{fig:coll_polar_e}.  \ACBc{[As you can see from my suggested edits, I think this should be *also* discussed above with the first discussion of Figure 6.]}
 
 Although the same phenomenon appears to be happening near the 3:1 MMR, the pileups at the edges of the resonance are not as well defined. We 
-attribute this to the more comlex symmetry, compared to the 2:1 MMR. In addition, a number of other nearby resonances, including the 7:2 (at 
+attribute this to the more complex symmetry, compared to the 2:1 MMR. In addition, a number of other nearby resonances, including the 7:2 (at 
 2.25 AU), the 10:3 (at 2.33 AU), the 8:3 (at 2.71 AU) and the 5:2 (at 2.82 AU) also likely are contributing to the collision profile in cylindrical distance 
 space near the 3:1. The width of the 3:1 MMR is also much narrower than the 2:1, which means that any dip or bump features produced by it would 
-require much higher resolution observations. For these reasons, we will focus on the 2:1 MMR as the main diagnostic indicator.
+require much higher resolution observations.
+For these reasons, we will focus on the 2:1 MMR as the main diagnostic indicator.
+\ACBc{[Armed with the output from my sims, you might be able to comment more on this.]}
 
@@
 
-Orange curves in figure \ref{fig:coll_polar_e} show the simulated ALMA flux profiles generated with {\sc CASA} \citep{2007ASPC..376..127M}. Have 
-Aaron add in some more text here describing exactly how the profiles were created. Should we add a separate figure to show the flux profiles, or 
-simply include them as an extra curve in the side panels of figures 6 and 7 like I've started to do here?
+\ACBc{[You will want to update the previously mentioned orange curves. New text follows]}
+
+While the collisional dust profiles show radial amplitude variations, we still need to assess whether those variations could be observable.  
+To proceed, we create a skymodel for simulated ALMA observations as follows.
+First, we use the radially-averaged collision frequency from simulation e2m2 (Fig.~\ref{fig:coll_hist_r}) as the template for an azimuthally symmetric disk.
+We then scale that profile by a factor of ten, which places ``Jupiter'' at 52 au.  
+This scaling is permitted by the dynamics and makes the disk comparable in size to the many disks that have now been observed by ALMA (maybe reference DSHARP).  
+The observed size scale is then set by envisaging a face-on disk at a distance of 100 pc.
+
+The skymodel intensity (flux per pixel) is produced by interpolating the radial collision frequency onto a 2D Cartesian grid with cell widths of approximately 2 mas. 
+In doing so, we choose to make the intensity proportional to the collision frequency (i.e., the dust) because it is the most straightforward case. 
+Many different parameterizations are possible, depending on optical depth, grain size, disk temperature, etc., but we will avoid such complications here. 
+We normalize the intensity by setting the total disk flux density to be 100 mJy at about 350 GHz.
+
+The simulated observations are performed using the {simobserve} task in {\sc CASA} \citep{2007ASPC..376..127M}.
+The disk is given an $\rm RA = 11^{\rm h} 01^{\rm m} 52^{\rm s}$ and a $\delta = -34^\circ 42\arcmin 17\arcsec$ (i.e., the J2000 coordinates for TW Hydrae) and is ``observed'' through transit on March 20, 2020.
+We observe the disk using configurations 8, 9, and 10 at 350 GHz (cycle 6 antenna file), spending six hr on-source in each configuration\footnote{We have imagined that the TAC likes us.}.  
+The visibilities are corrupted with thermal noise, setting $\rm PWV=1.5$. 
+They are then combined, imaged, and cleaned using the task tclean. Imaging uses Briggs weighting with a robustness parameter of -1.
+
+The results are shown in Figure \ref{fig:alma_sim_obs}.
+The 3:1 and 2:1 resonances can be easily identified in the cleaned image and in the corresponding radial profile.
+Moreover, the features are qualitatively similar to the bright rings and dark gaps seen in actual disk profiles (maybe HL Tau cite).
+[We should make the skymodel available to anyone who wants to use it]
+
+\begin{figure}
+\begin{center}
+    \includegraphics[width=0.5\textwidth]{alma/skymodel_e2m2.png}
+    \includegraphics[width=0.5\textwidth]{alma/xy_e2m2.png}
+    \includegraphics[width=0.5\textwidth]{alma/profile_e2m2.eps}
+    \caption{Simulated ALMA observations.
+Top.
+The skymodel based on the radial collision distribution from the e2m2 simulation.
+The size of the disk has been scaled by a factor of 10 and placed at 100 pc.
+Middle.
+The cleaned image using combined observations in configurations 8, 9, and 10.
+The 3:1 and 2:1 resonance dust gaps are visible.
+Bottom.
+The azimuthally-averaged radial profile based on the cleaned image.
+\label{fig:alma_sim_obs}}
+\end{center}
+\end{figure}
 

### 2020-06-19 alma/genSkyModel.py

@@ -1,0 +1,217 @@
+import math as M
+import pylab as P
+import numpy as NP
+from astropy.io import fits as pyfits
+import scipy.fftpack as fft
+import random as R
+import sys
+import numpy as np
+
+fname="e3m2_coll.txt"
+fileout="skymodel-e3m2.fits"
+SHIFT=0
+
+#this stays the same
+N=2400 # make multiples of 300
+DIST=100
+SCALE=10
+dr=0.0202020202/DIST*SCALE
+dpix=dr/5
+MULTIPLIER=15000000
+#MULTIPLIER=15000
+#MULTIPLIER=150
+normflux = 100 # 10 mJy 
+RA=165.4663
+DEC=-34.70473
+
+nucenter=345e9
+beam=M.pi*0.0278*0.0278/4.
+abbeam=M.sqrt(beam)
+fwhm=0.0278/2
+
+rhodust=2.5
+dustsize=1e-1
+Mdust=0.020 # Mearth
+
+Mearth=2e30/320.
+hplanck=6.626e-27
+c=2.989e10
+kb=1.3807e-16
+au=1.5e13
+
+
+BSCALE  = 1.
+BZERO = 0.
+BMAJ = 0.0278/206265*180/np.pi
+BMIN = 0.0278/206265*180/np.pi
+BPA = 8.402376556396E+01 
+BTYPE='Intensity'
+OBJECT = 'COLLISION.MODEL'
+BUNIT='mJy/pixel'
+EQUINOX =  2000 
+RADESYS = 'FK5 '
+LONPOLE = 180
+LATPOLE = -2.295433409167E+01 
+CTYPE1  = 'RA---SIN'                                                            
+CRVAL1  =    RA
+CDELT1  =  -dpix/3600
+CRPIX1  =  N/2.+1.
+CUNIT1  = 'deg     '                                                            
+CTYPE2  = 'DEC--SIN'                                                            
+CRVAL2  =  DEC
+CDELT2  =   dpix/3600.
+CRPIX2  =   N/2.+1.
+CUNIT2  = 'deg     '  
+
+CTYPE3  = 'FREQ    '                                                            
+CRVAL3  =    3.509375000000E+11                                                 
+CDELT3  =     15.625E6                            
+CRPIX3  =   1.000000000000E+00                                                  
+CUNIT3  = 'Hz      '  
+CTYPE4  = 'STOKES  '                                                            
+CRVAL4  =   1.000000000000E+00                                                  
[…]

### 2020-06-19 alma/makeprofile.py

@@ -1,0 +1,127 @@
+import math as M
+import pylab as P
+import matplotlib as mplt
+import numpy as NP
+from astropy.io import fits as pyfits
+import scipy.fftpack as fft
+import random as R
+import sys
+import numpy as np
+
+
+SKYFITS="skymodel-e1m2.fits" # skymodel for simulated observations
+SIMFITS="e1m2_robustm1.fits"  # simulated observations, cleaned output file
+affix="e1m2"
+
+hdul = pyfits.open(SIMFITS)
+
+NR=160
+dr = 0.5/NR
+
+print(hdul.info)
+
+dra=hdul[0].header["CDELT1"]*3600 # stored as deg, want arcsec
+dde=hdul[0].header["CDELT2"]*3600
+
+bmaj=hdul[0].header["BMAJ"]*3600
+bmin=hdul[0].header["BMIN"]*3600
+bpa=hdul[0].header["BPA"]
+print(bmaj,bmin,bpa)
+
+
+data = np.array(hdul[0].data)
+data = data[0][0]
+
+hdul.close()
+
+hdul = pyfits.open(SKYFITS)
+sky=np.array(hdul[0].data)
+
+dras=hdul[0].header["CDELT1"]*3600
+ddes=hdul[0].header["CDELT2"]*3600
+
+
+NS=int( np.sqrt(sky.size))
+
+
+XS=np.zeros(NS)
+YS=np.zeros(NS)
+
+for i in range(NS):
+   XS[i] = -NS/2*dras + dras*i + 0.5*dras
+   YS[i] = -NS/2*ddes + ddes*i + 0.5*ddes
+
+
+
+hdul.close()
+
+
+mind = np.amin(data)*0.9*0
+maxd = np.amax(data)
+
+levels = np.linspace(0,256)/255*(maxd-mind) + mind
+
+N=int( np.sqrt(data.size))
+
+X=np.zeros(N)
+Y=np.zeros(N)
+
+for i in range(N):
+   X[i] = -N/2*dra + dra*i + 0.5*dra
+   Y[i] = -N/2*dde + dde*i + 0.5*dde
+
+
+profile=np.zeros(NR)
+countr=np.zeros(NR)
+for i in range(N):
+  for j in range(N):
+          x=X[i]
+          y=Y[j]
+          r = np.sqrt(x**2+y**2)
+          ir = int(r/dr)
[…]

### 2020-06-19 alma/script-short.py

@@ -1,0 +1,115 @@
+userProject="sim_e3m2"
+userANT="10"
+
+taskname           = "simobserve"
+project            =  userProject
+skymodel           =  "collision-skymodel-e3m2smth.fits"
+inbright           =  ""
+indirection        =  ""
+incell             =  ""
+incenter           =  ""
+inwidth            =  ""
+complist           =  ""
+compwidth          =  "8GHz"
+setpointings       =  True
+ptgfile            =  "$project.ptg.txt"
+integration        =  "10s"
+direction          =  ""
+mapsize            =  ['', '']
+maptype            =  "ALMA"
+pointingspacing    =  ""
+caldirection       =  ""
+calflux            =  "1Jy"
+obsmode            =  "int"
+refdate            =  "2020/03/20"
+hourangle          =  "transit"
+totaltime          =  "14400s"
+antennalist        =  "antennas/alma.cycle6."+userANT+".cfg"
+sdantlist          =  "aca.tp.cfg"
+sdant              =  0
+outframe           =  "LSRK"
+thermalnoise       =  "tsys-atm"
+user_pwv           =  1.5
+t_ground           =  269.0
+t_sky              =  260.0
+tau0               =  0.1
+seed               =  11111
+leakage            =  0.0
+graphics           =  "both"
+verbose            =  False
+overwrite          =  True
+go()
+
+taskname           = "clean"
+vis                =  userProject+"/"+userProject+".alma.cycle6."+userANT+".noisy.ms"
+imagename          =  userProject+"/dirty_collision"+userANT
+outlierfile        =  ""
+field              =  ""
+spw                =  ""
+selectdata         =  True
+timerange          =  ""
+uvrange            =  ""
+antenna            =  ""
+scan               =  ""
+observation        =  ""
+intent             =  ""
+mode               =  "mfs"
+resmooth           =  False
+gridmode           =  ""
+wprojplanes        =  -1
+facets             =  1
+cfcache            =  "cfcache.dir"
+rotpainc           =  5.0
+painc              =  360.0
+aterm              =  True
+psterm             =  False
+mterm              =  True
+wbawp              =  False
+conjbeams          =  True
+epjtable           =  ""
+interpolation      =  "linear"
+niter              =  0
+gain               =  0.1
+threshold          =  "0.0mJy"
+psfmode            =  "clark"
+imagermode         =  "csclean"
+ftmachine          =  "mosaic"
+mosweight          =  False
+scaletype          =  "SAULT"
[…]

### 2020-06-19 main_aaron.tex
All the way through the paper

@@
 produced when bodies at the edges of the resonance stay sufficiently separated in cylindrical distance over the course of an orbit. This is achieved 
-when either the resonance width is large and the forced eccentricity is small. The bump feature, on the other hand, is produced when there is a 
+when \sout{either} the resonance width is large and the forced eccentricity is small. The bump feature, on the other hand, is produced when there is a 
 sufficiently large amount of overlap between the apocenters and pericenters of the inner and outer edges of the resonance, respectively. This is 
@@
 
+\ACBc{[I would be happy to make one last connection with my 2017 paper, if you are willing.
+One of the main points of that paper was to argue that disks with planet formation should be thought of as partial debris systems, in that some of the morphological dust features could be due to collisional dynamics.
+You have shown that, to within the approximations of the simulations, that this is correct.
+We should not think of disks as either planet-forming with primordial dust or debris disks with second-generation of dust, but a continuum.
+If giant planets are present, then collisional processes must affect the dust distribution.
+]}
+
 Compared to using the corotationg gap opened by the planet as a diagnostic \citep{2013ApJ...777L..31D, 2016ApJ...820...29D}, measuring 

### 2020-06-20 main.tex
Fix up figures, add simulated ALMA stuff

@@
 \section{Introduction} \label{sec:intro}
+
+Text width: \the\textwidth
 
@@
 
+\begin{figure}
+\begin{center}
+    \includegraphics[width=0.5\textwidth]{alma/skymodel_e2m2.png}
+    \includegraphics[width=0.5\textwidth]{alma/xy_e2m2.png}
+    \caption{Simulated ALMA observations.
+Top.
+The skymodel based on the radial collision distribution from the e2m2 simulation.
+The size of the disk has been scaled by a factor of 10 and placed at 100 pc.
+Middle.
+The cleaned image using combined observations in configurations 8, 9, and 10.
+The 3:1 and 2:1 resonance dust gaps are visible.
+\label{fig:alma_sim_obs}}
+\end{center}
+\end{figure}
+
+\begin{figure*}
+    \includegraphics[width=\textwidth]{figures/alma_profiles}
+    \caption{Caption goes here.\label{fig:alma_profiles}}
+\end{figure*}
+
 \subsection{Varying the Mass}
@@
 
+\section{Appendix: Nonaxisymmetric Structure in Boley 2017}\label{sec:boley_plot}
+
+\begin{figure*}
+    \includegraphics[width=\textwidth]{figures/boley_rtheta}
+    \caption{Caption goes here\label{fig:boley_rtheta}}
+\end{figure*}
+
 \end{document}

### 2020-06-20 alma/makeprofile.py

@@ -1,5 +1,5 @@
 import math as M
-import pylab as P
+import matplotlib.pylab as P
 import matplotlib as mplt
 import numpy as NP
 from astropy.io import fits as pyfits
@@ -8,10 +8,13 @@ import random as R
 import sys
 import numpy as np
 
+mplt.rcParams.update({'font.size': 16, 'font.family': 'STIXGeneral', 'mathtext.fontset': 'stix',
+                            'image.cmap': 'viridis', 'xtick.labelsize': 'x-small', 'ytick.labelsize': 'x-small'})
 
-SKYFITS="skymodel-e1m2.fits" # skymodel for simulated observations
-SIMFITS="e1m2_robustm1.fits"  # simulated observations, cleaned output file
-affix="e1m2"
+
+SKYFITS="skymodel-e2m2.fits" # skymodel for simulated observations
+SIMFITS="e2m2_robustm1.fits"  # simulated observations, cleaned output file
+affix="e2m2"
 
 hdul = pyfits.open(SIMFITS)
 
@@ -95,8 +98,8 @@ fig=P.figure()
 ax=fig.add_subplot(111)
 cnt=P.contourf(YS,XS,sky,256,cmap=P.get_cmap("gist_gray_r"))
 ax.set_aspect('equal')
-P.xlabel(r"$\Delta$RA (arcsec)")
-P.ylabel(r"$\Delta\delta$ (arcsec)")
+P.xlabel(r"$\Delta$RA [arcsec]")
+P.ylabel(r"$\Delta\delta$ [arcsec]")
 P.title("Skymodel, scaled "+affix)
 P.xlim([0.5,-0.5])
 P.ylim([-0.5,0.5])
@@ -106,8 +109,8 @@ fig=P.figure()
 ax=fig.add_subplot(111)
 cnt=P.contourf(Y,X,data,levels=levels,cmap=P.get_cmap("gist_gray_r"))
 ax.set_aspect('equal')
-P.xlabel(r"$\Delta$RA (arcsec)")
-P.ylabel(r"$\Delta\delta$ (arcsec)")
+P.xlabel(r"$\Delta$RA [arcsec]")
+P.ylabel(r"$\Delta\delta$ [arcsec]")
 P.title("Cleaned image, scaled "+affix)
 P.xlim([0.5,-0.5])
 P.ylim([-0.5,0.5])
@@ -125,3 +128,4 @@ P.savefig("profile_"+affix+".eps")
 
[…]

### 2020-06-20 makeFig.py

@@ -4,8 +4,8 @@ import matplotlib as mpl
 from matplotlib import cm
 import matplotlib.colors as colors
 
-mpl.rcParams.update({'font.size': 18, 'font.family': 'STIXGeneral', 'mathtext.fontset': 'stix',
-                            'image.cmap': 'viridis'})
+mpl.rcParams.update({'font.size': 16, 'font.family': 'STIXGeneral', 'mathtext.fontset': 'stix',
+                            'image.cmap': 'viridis', 'xtick.labelsize': 'x-small', 'ytick.labelsize': 'x-small'})
 
 import numpy as np
 import pandas as pd
@@ -44,6 +44,13 @@ for idx in range(len(res_p)):
     j2 = -res_p[idx]
     alpha = (-j2/j1)**(2./3.)
     res_dist.append(a_jup*alpha)
+
+# Convert a simulation distance into an angle on the sky for the
+# simulated ALMA images
+def dist_to_ang(dist):
+	# Disk size expanded to increase angular size of observed disk
+	jup_pos_arcsec = ((52*u.AU).to(u.pc)/(100*u.pc)*u.rad).to(u.arcsec).value
+	return dist/a_jup*jup_pos_arcsec
 
 # Build a PDF from a series of data points using a KDE
 from sklearn.neighbors import KernelDensity
@@ -94,14 +101,14 @@ def plot_res(axis, res=-1, vertical=True, show_widths=False, all=False):
 		for idx, val in enumerate(res_ind):
 			if vertical:
 				axis.vlines(res_dist[val], ymin, ymax, linestyles='--', lw=0.5)
-				axis.text(res_dist[val], ymax, res_label[val], verticalalignment='top', fontsize=12)
+				axis.text(res_dist[val], ymax*0.99, res_label[val], verticalalignment='top', fontsize=16)
 				if show_widths:
 					width = res_width_jup(val)
[…]

### 2020-06-20 main.tex
Start implementing aaron's comments

@@
 
-Text width: \the\textwidth
-
-Recent observations of circumstellar disks by ALMA have revealed a rich variety of substructure. Features 
-such as gaps and asymmetries 
+Recent observations of circumstellar disks by ALMA have revealed a rich variety of substructure. Features such as gaps and asymmetries 
 \citep{2015ApJ...808L...3A, 2016Sci...353.1519P, PhysRevLett.117.251101, 2016ApJ...820L..40A, 2016Natur.535..258C} in the emission provide 
-diagnostics for the physical processes that drive the evolution of the disks. In some cases, these gap features are argued to be an indicator for the 
-presence of a giant planet, either embedded in the disk \citep{2015MNRAS.453L..73D} or orbiting externally. A giant perturber can influence the 
-structure of the continuum emission in a number of ways. A misaligned giant planet can produce nonaxisymmetric features such as warps 
-\citep{2001A&A...370..447A}. Highly eccentric perturbers can produce even more complicated structures through secular interactions 
-\citep{2014MNRAS.443.2541P, 2015MNRAS.448.3679P}. Mean motion resonances (MMRs) have been shown to open gaps as well 
+diagnostics for the physical processes that drive the evolution of the disks. In many gas-rich systems, these gap features are argued to indicate the 
+presence of a giant planet, either embedded in the disk \citep{2015MNRAS.453L..73D} or orbiting externally, although the details of gas-dust 
+interactions can have strong effects on the resulting morphologies (Dong).In gas-poor/debris systems, a giant perturber can also influence the 
+structure of the dust continuum emission.
+For example, a misaligned giant planet can produce nonaxisymmetric features such as warps \citep{2001A&A...370..447A}, highly eccentric perturbers can produce structures through secular interactions
+\citep{2014MNRAS.443.2541P, 2015MNRAS.448.3679P}, and mean motion resonances (MMRs) can open gaps
 \citep{2015ApJ...798...83N, 2016ApJ...818..159T, 2018ApJ...857....3T}.
 
-Collisions between planetesimals are thought to be a significant source of dust for many young circumstellar disks 
-\citep[see][]{2008ARA&A..46..339W}. An expanding debris cloud from a planetesimal collision was recently detected in the 
-Fomalhut system \citep{2020PNAS..117.9712G}. Although some amount of primordial dust is likely still present during the planet formation process, 
-ongoing collisions between small bodies will augment this and could be used to trace the underlying dynamical activity of the planetesimals. 
-\citet{2013ApJ...777L..31D} showed that collisional dust generated near the gap formed by a giant planet in a planetesimal disk should produce a 
-distinctly observable marker that could be used to infer the presence of the planet. In a followup study, it was found that morphological differences in 
-the dust emission could be used to determine whether the planet had a circular or eccentric orbit \citep{2016ApJ...820...29D}.
+Collisions between planetesimals are thought to be the principal source of dust for debris disks. \citep[see][]{2008ARA&A..46..339W}.  Although some 
+amount of primordial dust is likely still present during the early stages of debris disk evolution, ongoing collisions between small bodies will augment 
+this and could be used to trace the underlying dynamical activity of the planetesimals. This process was directly detected when the putative object 
+Fomalhaut b was confirmed to be an expanding debris cloud, most likely from a planetesimal collision \citep{2020PNAS..117.9712G}.
 
-Substructure due to mean-motion resonances (MMRs) with a giant planet may hold additional clues which 
-could be used to constrain the properties of the planet.  The width of a resonance is set by both the mass of the perturbing planet, along with the 
-unperturbed eccentricity of the planetesimals, which is in turn set by the eccentricity of the planet through secular forcing. Therefore, the structure of 
-second generation dust produced near MMRs encodes information about both the mass and eccentricity of the planet.
+\citet{2013ApJ...777L..31D} showed that collisional dust that is generated near the gap opened by a giant planet in a planetesimal disk should 
+produce a distinct observable marker that could be used to infer the presence of the planet. In a followup study, it was found that morphological 
+differences in the dust emission could be used to determine whether the planet had a circular or eccentric orbit \citep{2016ApJ...820...29D}.Moreover, 
+substructure due to mean-motion resonances (MMRs) with a giant planet may hold additional clues that could be used to constrain the properties of 
+the planet.  The width of a resonance is set by both the mass of the perturbing planet, along with the unperturbed eccentricity of the planetesimals, 
+which is in turn set by the eccentricity of the planet through secular forcing. Therefore, the structure of second generation dust produced near MMRs 
+encodes information about both the mass and eccentricity of the planet.
 
@@
 
-To further elucidate this subject, we use the tree based N-body code {\sc ChaNGa}
-\citep{2008IEEEpds...ChaNGa, 2015AphCom..2..1} to follow the collisional evolution of a planetesimal disk under the gravitational 
-influence of a Jupiter sized body. Because particle positions are sorted into a tree structure, neighbor finding and collision detection 
-can be done quickly and efficiently. This considerably relaxes the constraints on resolution and integration time. With this toolset, we 
-explore the collision rate structure of the planetesimal disk in the vicinity of mean motion resonances. In particular, we would like to 
-determine: 1. whether MMRs leave a detectable signature in the collisionally-generated dust. 2. If these signatures can be used to determine or 
-constrain the orbital properties of the perturbing planet.
+To further elucidate this subject, we use the tree based N-body code {\sc ChaNGa}\citep{2008IEEEpds...ChaNGa, 2015AphCom..2..1} to follow the 
+collisional evolution of a planetesimal disk under the gravitational influence of a Jupiter sized body. Because particle positions are sorted into a tree 
+structure, neighbor finding and collision detection can be done quickly and efficiently. This considerably relaxes the constraints on resolution and 
+integration time. With this toolset, we explore the collision rate structure of the planetesimal disk in the vicinity of mean motion resonances. In 
+particular, we would like to determine (1) whether MMRs leave a detectable signature in the collisionally-generated dust, and (2) whether these 
+signatures can be used to determine or constrain the orbital properties of the perturbing planet.
 
@@
 \begin{equation}\label{eq:lap}
-	b_{s}^{j}(\alpha) = \frac{1}{2 \pi} \int_{0}^{2 \pi} \frac{cos \, j \theta \, d \theta}{\left( 1 - 2 \alpha \, cos \theta + \alpha^2 \right)^{s}}.
+	b_{s}^{j}(\alpha) = \frac{1}{2 \pi} \int_{0}^{2 \pi} \frac{\cos \, j \theta \, d \theta}{\left( 1 - 2 \alpha \, \cos \theta + \alpha^2 \right)^{s}}.
 \end{equation}
@@
 
-In regions where there are commensurabilities between frequencies, secular theory breaks down and bodies are subject to strong 
-perturbations. For the purposes of this study, we will ignore secular resonances, which generally occur on rather large timescales 
-and will focus on mean motion resonances (MMRs). A MMR occurs  when the orbital period ratio between two bodies is sufficiently 
-close to
+In regions where there are commensurabilities between frequencies, Laplace-Langrange secular theory breaks down and bodies are subject to strong 
+perturbations. For the purposes of this study, we will ignore secular resonances, which generally occur on rather large timescales and will focus on 
+mean motion resonances (MMRs). A MMR occurs  when the orbital period ratio between two bodies is sufficiently close to
 
@@
 
-\noindent where  $p$ and $q$ are integers $>$ 0 and the unprimed and primed quantities correspond to the perturber and the body 
-being perturbed, respectively. If the perturber is much more massive than the other body, the condition for MMR is set  by the semi-major 
-axes of the two bodies by
+\noindent where  $p$ and $q$ are integers $>$ 0 and the unprimed and primed quantities correspond to the perturber and the body being perturbed, respectively.
+In terms of these quantities, $P/P'$ corresponds to a $p+q:p$ resonance If the perturber is much more massive than the other body, the condition for MMR is set  by the semi-major axes of the two bodies by
 
@@
 equlibrium value, while this angle will circulate outside of resonance. For small eccentricities, this behavior is analogous to the motion of a 
-pendulum. Variations in the critical angle are coupled to changes in the mean motion and semimajor axis \citet{2000ssd..book.....M}. An important 
-point to note, which will become important later, is that the variation frequency of this angle approaches zero near the edge of a resonance. The 
+pendulum. Variations in the critical angle are coupled to changes in the mean motion and semimajor axis \citep{2000ssd..book.....M}. An important 
+point to note, which we will come back to later, is that the variation frequency of this angle approaches zero near the edge of a resonance. The 
 width of a resonance can be defined by determining the largest variation in semimajor axis that permits librational, rather than circulatory motion of 
@@
 
+\noindent It should be noted that equation \ref{eq:res_fo} becomes invalid as $e$ approaches zero \citep{2020arXiv200609452M}. The secular forcing 
+in our simulations, however, keeps planetesimals outside of this more complex regime.
+
 Changes in eccentricity are correlated with changes in semimajor axis variations according to the Tisserand relation
@@
 
-The net result of this is that MMRs will produce spikes in the semimajor axis - eccentricity distribution of a planetesimal disk. In order to 
+The net result of this is that MMRs will produce spikes in the semimajor axis-eccentricity distribution of a planetesimal disk. In order to 
 preserve the Jacobi energy, equation \ref{eq:tiss} predicts that these spikes will tend to curve away from the perturbing body. This lowers the 
@@
 
-In total, five simulations are run. The first is a 'nominal' case, in which the perturbing planet's mass and eccentricity are set to that of Jupiter's. 
-In the other four cases, the mass (eccentricity) is increased or decreased by a factor of two, while the eccentricity (mass) is held at the nominal 
-value. In all cases, the perturbing giant is placed on a 5.2 AU orbit around a 1 $M_{\odot}$ star. The planetesimal disk extends from 2.2 to 3.8 
-AU, which covers the two most prominent mean motion resonances with the giant planet, the 2:1 at 3.27 AU and the 3:1 at 2.5 AU. The 
-planetesimal disk follows a minimum-mass solar nebula surface density profile \citep{1981PThPS..70...35H}
+In total, five simulations are run, which are listed in table \ref{tab:sims}. The first is a `nominal' case, in which the perturbing planet's mass and 
+eccentricity are set to that of Jupiter's. In the other four cases, the mass (eccentricity) is increased or decreased by a factor of two, while the 
+eccentricity (mass) is held at the nominal value. In all cases, the perturbing giant is placed on a 5.2 AU orbit around a 1 $M_{\odot}$ star. The 
+planetesimal disk extends from 2.2 to 3.8 AU, which covers the two most prominent mean motion resonances with the giant planet, the 2:1 at 3.27 AU 
+and the 3:1 at 2.5 AU. The planetesimal disk follows a minimum-mass solar nebula surface density profile \citep{1981PThPS..70...35H}
 
@@
 The dynamical effects of secular forcing by the giant planet, along with  the effects of viscous stirring and gas drag on the planetesimals, are 
-built into the initial conditions. This is done by first calculating the equilibirum eccentricity $e_{eq}$ due to viscous stirring and gas drag as a 
+built into the initial conditions. This is done by first calculating the equilibrium eccentricity $e_{eq}$ due to viscous stirring and gas drag as a 
 function of semimajor axis according to equation 12 of \citet{2002ApJ...581..666K}. Although {\sc ChaNGa} does not account for the effects of 
@@
 
-\begin{equation}\label{eq:hk}
-	z = (h, ik) = e \, exp(i \varpi)
+\begin{equation}\label{eq:kh}
+	z = (k, ih) = e \, exp(i \varpi)
 \end{equation}
@@
 integration symplectic, we find that a small amount of artificial precession is produced. This is most noticeable at the inner edge of the
-planetesimal disk. We reduce the base time step size by an additional 
-factor of 4 to the keep longitude of perihelia of planetesimals near the inner edge of the disk from drifting too far over the course of our 
-integrations.
+planetesimal disk.
+We reduce the base time step size by an additional factor of 4 to the prevent the longitude of perihelia of planetesimals at the inner edge of the disk from drifting by more than the intrinsic spread in $\varpi$ due to the free eccentricity over the course of our integrations.
 
@@
 which the radii of all bodies are inflated by a factor of 2.5. Any bodies with imminent collisions predicted using the inflated radii are 
-placed on a time step that is a factor of 16 smaller than the orbital time step. The purpose of two-tiered scheme is to properly resolve 
+placed on a time step that is a factor of 16 smaller than the orbital time step. The purpose of the two-tiered scheme is to properly resolve 
 the gravitational interactions between any bodies that undergo a close encounter. This prevents the coarser base time step from 
@@
 
-\subsection{Varying the Eccentricity}
+\subsection{Varying the Eccentricity} \label{sec:vary_ecc}
 
@@
 similar substructure, which is most noticeable near the 2:1 MMR, reveals itself in \citet{2000Icar..143...45R} (see bottom panel of figure 3) and 
-\citet{2016ApJ...818..159T} (figure 3). It is worth noting that \citet{2000Icar..143...45R} started with a completely cold planetesimal disk and a Jupiter 
-mass planet on a circular, coplanar orbit. The presence of these features seems robust to the choice of initial conditions.
+\citet{2016ApJ...818..159T} (figure 3). This structure is also present in the \citet{2017ApJ...850..103B} simulations, although it was not reported at the 
+time (see Appendix \ref{sec:boley_plot}). It is worth noting that \citet{2000Icar..143...45R} started with a completely cold planetesimal disk and a 
+Jupiter mass planet on a circular, coplanar orbit. \citet{2017ApJ...850..103B} used a similar setup. This, the presence of these features seems robust 
+to the choice of initial conditions.
 
@@
 construct a PDF of the collisions using a Kernel Density Estimate (KDE). We use the {\sc neighbors.KernelDensity} function from the {\sc sklearn} 
-\citep{scikit-learn} package to construct our KDEs. For the kernel, we use a tophat function with a bandwidth of 0.02 AU.
+\citep{scikit-learn} package to construct our KDEs. We use a gaussian kernel with a FWHM of 0.02 AU.
 
@@
     \includegraphics[width=0.5\textwidth]{figures/coll_hist_a.png}
-    \caption{In semimajor axis space, prominent features appear near the 3:1 and 2:1 MMRs. Near the 3:1, the collision
-    rate decreases from its unperturbed value, while an enhancement apepars near the 2:1.\label{fig:coll_hist_a}}
+    \caption{A PDF of the collision rate in each disk as a function of semimajor axis, generated using a KDE with a Gaussian kernel with a FWHM of 0.02 AU.
+In semimajor axis space, prominent features appear near the 3:1 and 2:1 MMRs.
+Near the 3:1, the collision rate decreases from its unperturbed value, while an enhancement apepars near the 2:1.\label{fig:coll_hist_a}}
 \end{center}
@@
 At the highest eccentricity, a bump is formed instead.
-In orange, the collision profile is shown with collisions between bodies in resonance removed.
+The dashed lines shown the collision profile with collisions between bodies in resonance removed.
 The bump and dip features remain qualitatively the same, which suggests that they are produced by bodies outside of resonance.\label{fig:coll_hist_r}}
@@
 
-Operating under this assumption, a map of the relative concentration of second-generation dust can be constructed from the cylindrical 
-distance at which the collisions occur. This is shown in figure \ref{fig:coll_hist_r}. Similar to figure \ref{fig:coll_hist_a}, we use a KDE with a bandwidth 
-of 0.02 AU to assemble the collision locations into a radial distribution. Most strikingly, the bump that was present near the 2:1 resonance is no 
-longer visible in cylindrical distance space, although it suddenly appears again in the e3m2 simulation. The dip that is visible near the 3:1 MMR 
-also becomes a bump in the highest eccentricity case. To determine how the resonant bodies actually contribute to the radial collision 
-profile, we excluded collisions that fall between $2.495 < a < 2.505$ AU (near the 3:1 resonance) and between $3.2 < a < 3.35$ AU (near the 2:1 
-resonance), which is shown by the orange curve. Qualitatively, none of the bump or dip features present are removed by making this exclusion. This 
-suggests that the features near resonance seen in semimajor axis space become smeared out in cylindrical distance space due to the large spread 
-in eccentricity and orbital orientation.
+Operating under this assumption\footnote{As discussed in \cite{2017ApJ...850..103B}, the local generation of second-generation dust is only one 
+consideration.  The dust will also evolve spatially due to drag effects, but can also evolve in size or be re-accreted onto planetesimals. For simplicity, 
+we focus on local dust sourcing only while acknowledging that subsequent evolution could affect the morphology.}, a map of the relative concentration 
+of second-generation dust can be constructed from the cylindrical distance at which the collisions occur. This is shown in figure \ref{fig:coll_hist_r}. 
+Similar to figure \ref{fig:coll_hist_a}, we use a KDE with a bandwidth of 0.02 AU to assemble the collision locations into a radial distribution. Most 
+strikingly, the bump that was present near the 2:1 resonance is no longer visible in cylindrical distance space, although it suddenly appears again in 
+the e3m2 simulation. The dip that is visible near the 3:1 MMR also becomes a bump in the highest eccentricity case. To determine how the resonant 
+bodies actually contribute to the radial collision profile, we excluded collisions that fall between $2.495 < a < 2.505$ AU (near the 3:1 resonance) and 
+between $3.2 < a < 3.35$ AU (near the 2:1 resonance), which is shown by the dashed curve. Qualitatively, none of the bump or dip features present 
+are removed by making this exclusion. This suggests that the features near resonance seen in semimajor axis space become smeared out in 
+cylindrical distance space due to the large spread in eccentricity and orbital orientation.
 
-This also suggests that the most prominent bumps and dips seen in figure \ref{fig:coll_hist_r} are being produced by bodies outside of resonance. To 
-further understand this, we consider the nonaxisymmetric structure seen in figure \ref{fig:xy}. In figure \ref{fig:coll_polar_e}, we compare the radial 
-collision profile to the radial structure seen in the e1m2, e2m2 and e3m2 simulations. In the lowest forced eccentricity case, the pileups near the 
-edges of the resonances line up with the boundaries of the dip feature seen in the radial collision profile. The locations of the edges of the 
-resonances are calculated using equations \ref{eq:res_fo} and \ref{eq:res_so}. The pileups are especially prominent for the 2:1 resonance. As 
-discussed previously, the pileups and gaps seen in polar coordinates follow the position of the giant planet in its orbit, which is shown by the vertical 
-line.
+This also suggests that the prominent bumps and dips seen in figure \ref{fig:coll_hist_r} are mainly produced by bodies outside of resonance, although 
+the resonant population does make some of the features more pronounced. To further understand this, we consider the nonaxisymmetric structure 
+seen in figure \ref{fig:xy}. We compare in figure \ref{fig:coll_polar_e} the radial collision profile to the radial structure seen in the e1m2, e2m2 and 
+e3m2 simulations. In the lowest forced eccentricity case (e1m2), the pileups near the edge of the 2:1 MMR line up with the boundaries of the dip 
+feature seen in the radial collision profile. The locations of the edges of the resonances are calculated using equations \ref{eq:res_fo} and 
+\ref{eq:res_so}. The pileups not as pronounced near the other resonances. As discussed previously, the planetesimal density enhancements and gaps 
+seen in polar coordinates follow the position of the giant planet in its orbit, which is shown by the vertical line. For the e2m2 case, the density 
+enhancements take up a much larger radial width, which smears out the corresponding colli- sional dust profile. In the highest forced eccentricity case 
+(e3m2), the density enhancements occur well within an annulus containing the resonant region, completely al- tering the radial peak-valley dust 
+morphology.
 
 Although the nonaxisymmetric pileup of bodies near the edges of resonances has been seen previously 
-\citep{2000Icar..143...45R, 2016ApJ...818..159T}, we could not find a satisfactory explanation for why it happens and will provide one here. As 
-mentioned in section \ref{sec:dynamics}, the circulation frequency of the critical angle slows as one approaches the edge of the resonance from the outside.
-Following the pendulum analogy, this is equivalent to approaching the point where the pendulum becomes suspended in the vertical position.
-When the critical angle stays relatively stationary during an encounter, the net torque will drive the longitude of pericenter towards the point of conjunction \citep{1976ARA&A..14..215P}.
-This is the basic mechanism that causes isolated resonances to be stable.
-Inside of resonance, the critical angles librates about some value and this configuration is maintained.
-Just outside of resonance, however, the critical angle slowly drifts away, with the drift direction changing sign across the resonance.
-The net result of this is that bodies just outside of the resonance experience a torque from that planet that temporarily drives their pericenters toward the current orbital position of the planet.
-After the encounter ends, differential rotation of the disk slowly destroys the configuration over part of an orbit.
-As the planet passes by, adjacent planetesimals near the resonance edges temporarily align themselves in this configuration.
-This explains why the concentration of planetesimals appears to 'follow' the the planet.
+\citep{2000Icar..143...45R, 2016ApJ...818..159T}, we could not find a satisfactory explanation for why it happens, which we will try to provide here. As 
+mentioned in section \ref{sec:dynamics}, the circulation frequency of the critical angle slows as one approaches the edge of the resonance from the 
+outside. Following the pendulum analogy, this is equivalent to approaching the point where the pendulum becomes suspended in the vertical position. 
+When the critical angle stays relatively stationary during an encounter, the net torque will drive the longitude of pericenter towards the point of 
+conjunction \citep{1976ARA&A..14..215P}.  This is the basic mechanism that causes isolated resonances to be stable. Inside of resonance, the critical 
+angle librates about some value and this configuration is maintained. Just outside of resonance, however, the critical angle slowly drifts away, with the 
+drift direction changing sign across the resonance. The net result of this is that bodies just outside of the resonance experience a torque from that 
+planet that temporarily drives their pericenters toward the current orbital position of the planet. After the encounter ends, differential rotation of the disk 
+slowly destroys the configuration over part of an orbit. As the planet passes by, adjacent planetesimals near the resonance edges temporarily align 
+themselves in this configuration. This explains why the concentration of planetesimals appears to `follow' the planet.
 
@@
     \includegraphics[width=\textwidth]{figures/coll_polar_e.png}
-    \caption{The collision profiles in figure \ref{fig:coll_hist_r} are shown alongside the positions of the planetesimals, in polar coordinates. The 
-    synthetic dust emission profiles are shown in orange. The dashed and solid lines show the pericenter and apocenter of bodies at the edge of the 
-    3:1 and 2:1 MMR. In these figures, the longitude of pericenter of the planet lies at $\theta = 0$ and the present position of the planet is indicated 
-    by the vertical line. For the 2:1 resonance, a bump, rather than a dip feature appears when the inner edge or the resonance's apocenter and outer 
-    edge's pericenter distance cross. The collision profile near the 3:1 resonance does not appear to follow this same qualitative behavior.
+    \caption{The collision profiles in figure \ref{fig:coll_hist_r} are shown alongside the positions of the planetesimals, in polar coordinates.
+The dashed            and solid lines show the pericenter and apocenter, respectively,  of bodies at each edge of the 3:1 and 2:1 MMR.
+In these figures, the longitude of pericenter of the planet lies at $\theta = 0$ and the present position of the planet is indicated by the vertical line.
+For the 2:1 resonance, a bump, rather than a dip feature appears when the inner edge or the resonance's apocenter and outer edge's pericenter distance cross.
+The collision profile near the 3:1 resonance does not appear to follow this same qualitative behavior.
     \label{fig:coll_polar_e}}
@@
 
-\citet{2016ApJ...818..159T} provides a different explanation for this phenomenon. Instead, the nonaxisymmetric structure is claimed to be a product 
+\citet{2016ApJ...818..159T} provide a different explanation for this phenomenon, suggesting that the nonaxisymmetric structure is the product 
 of the path that a resonant test particle takes in a frame co-rotating with the planet (see figure 8.4 of \citet{2000ssd..book.....M}). This explanation, 
 however, does not hold for a large collection of planetesimals, especially when there is no forced eccentricity. In such a case, the orbits of 
-planetesimals near resonance would be randomly aligned, and the axisymmetric structure should become washed out. In the case with a perturbing 
-planet planet on a circular orbit, this structure is still present (see figure 3 of \citet{2016ApJ...818..159T}). The only relation between the structure of 
-the gaps in the disk and the path of a resonant particle in the corotating frame is that both phenomena produce the same symmetries, which depend 
-on the resonance being considered.
+planetesimals near resonance would be randomly aligned, and the axisymmetric structure should become washed out. When the perturbing 
+planet is on a circular orbit, this structure is still present (see figure 3 of \citet{2016ApJ...818..159T} and Appendix \ref{sec:boley_plot}). The only 
+relation between the structure of the gaps in the disk and the path of a resonant particle in the corotating frame is that both phenomena produce the 
+same symmetries, which depend on the given resonance.
 
 With no secular forcing, this dynamical phenomena should produce an underdensity in the radial surface density profile near the center of the 
-resonance and an overdensity at each edge in cylindrical distance space. When a forced eccentricity is introduced, the edges of the resonance 
-(indicated by the solid and dashed lines in figure \ref{fig:coll_polar_e}), where the pileups are located, begin to explore a wider range of radii over the 
-course of a single orbit. If the the aphelion distance of the inner edge becomes comparable to the perihelion distance of the outer edge, the 
-overdense regions on each side of the resonance meet and we should expect to see the central dip feature in the collision profile disappear. This is 
-exactly what appears to be happening in the middle panel of figure \ref{fig:coll_polar_e}. As the forced eccentricity is increased further, a region 
-forms at the center of the resonance where planetesimals on both sides of the resonance spend time (although not simultaneously). When this 
-occurs, a bump feature forms in the collision profile near the center of the resonance. This is apparent in the bottom panel of figure 
+resonance and an overdensity at each edge in cylindrical distance space. When a forced eccentricity is introduced, the radial location of the 
+resonance edges vary over the course of an orbit. The maximum and minimum radial distance that the resonance edges occupy is indicated by the 
+solid and dashed lines in figure \ref{fig:coll_polar_e}. If the the aphelion distance of the inner edge becomes comparable to the perihelion distance of 
+the outer edge, the overdense regions on each side of the resonance meet and we should expect to see the central dip feature in the collision profile 
+disappear. This is exactly what appears to be happening in the middle panel of figure \ref{fig:coll_polar_e}. As the forced eccentricity is increased 
+further, a region forms at the center of the resonance where planetesimals on both sides of the resonance spend time (although not simultaneously). 
+When this occurs, a bump feature forms in the collision profile near the center of the resonance. This is apparent in the bottom panel of figure 
 \ref{fig:coll_polar_e}.
@@
 require much higher resolution observations. For these reasons, we will focus on the 2:1 MMR as the main diagnostic indicator.
-
-\subsection{Observability of the Dust}
-
-Orange curves in figure \ref{fig:coll_polar_e} show the simulated ALMA flux profiles generated with {\sc CASA} \citep{2007ASPC..376..127M}. Have 
-Aaron add in some more text here describing exactly how the profiles were created. Should we add a separate figure to show the flux profiles, or 
-simply include them as an extra curve in the side panels of figures 6 and 7 like I've started to do here?
-
-\begin{figure}
-\begin{center}
-    \includegraphics[width=0.5\textwidth]{alma/skymodel_e2m2.png}
-    \includegraphics[width=0.5\textwidth]{alma/xy_e2m2.png}
-    \caption{Simulated ALMA observations.
-Top.
-The skymodel based on the radial collision distribution from the e2m2 simulation.
-The size of the disk has been scaled by a factor of 10 and placed at 100 pc.
-Middle.
-The cleaned image using combined observations in configurations 8, 9, and 10.
-The 3:1 and 2:1 resonance dust gaps are visible.
-\label{fig:alma_sim_obs}}
-\end{center}
-\end{figure}
-
-\begin{figure*}
-    \includegraphics[width=\textwidth]{figures/alma_profiles}
-    \caption{Caption goes here.\label{fig:alma_profiles}}
-\end{figure*}
 
@@
 the resonances are sufficiently separated to allow a gap near the center of the 2:1 resonance to appear in the collision profile.
+
+\subsection{Observability of the Dust}
+
+While the collisional dust profiles show radial amplitude variations, we still need to assess whether those variations could be observable.  
+To proceed, we create a skymodel for simulated ALMA observations as follows.
+First, we use the radially-averaged collision frequency from simulation e2m2 (Fig.~\ref{fig:coll_hist_r}) as the template for an azimuthally symmetric disk.
+We then scale that profile by a factor of ten, which places ``Jupiter'' at 52 au.  
+This scaling is permitted by the dynamics and makes the disk comparable in size to the many disks that have now been observed by ALMA (maybe reference DSHARP).  
+The observed size scale is then set by envisaging a face-on disk at a distance of 100 pc.
+
+The skymodel intensity (flux per pixel) is produced by interpolating the radial collision frequency onto a 2D Cartesian grid with cell widths of approximately 2 mas. 
+In doing so, we choose to make the intensity proportional to the collision frequency (i.e., the dust) because it is the most straightforward case. 
+Many different parameterizations are possible, depending on optical depth, grain size, disk temperature, etc., but we will avoid such complications here. 
+We normalize the intensity by setting the total disk flux density to be 100 mJy at about 350 GHz.
+
+The simulated observations are performed using the {simobserve} task in {\sc CASA} \citep{2007ASPC..376..127M}.
+The disk is given an $\rm RA = 11^{\rm h} 01^{\rm m} 52^{\rm s}$ and a $\delta = -34^\circ 42\arcmin 17\arcsec$ (i.e., the J2000 coordinates for TW Hydrae) and is ``observed'' through transit on March 20, 2020.
+We observe the disk using configurations 8, 9, and 10 at 350 GHz (cycle 6 antenna file), spending six hr on-source in each configuration\footnote{We have imagined that the TAC likes us.}.  
+The visibilities are corrupted with thermal noise, setting $\rm PWV=1.5$. 
+They are then combined, imaged, and cleaned using the task tclean. Imaging uses Briggs weighting with a robustness parameter of -1.
+
+The results are shown in Figure \ref{fig:alma_sim_obs}.
+The 3:1 and 2:1 resonances can be easily identified in the cleaned image and in the corresponding radial profile.
+Moreover, the features are qualitatively similar to the bright rings and dark gaps seen in actual disk profiles (maybe HL Tau cite).
+[We should make the skymodel available to anyone who wants to use it]
+
+Also mention figure \ref{fig:alma_profiles}.
+
+\begin{figure}
+\begin{center}
+    \includegraphics[width=0.5\textwidth]{alma/skymodel_e2m2.png}
+    \includegraphics[width=0.5\textwidth]{alma/xy_e2m2.png}
+    \caption{Simulated ALMA observations for the nominal (e2m2) case.
+Top.
+The skymodel based on the radial collision distribution from the e2m2 simulation.
+The size of the disk has been scaled by a factor of 10 and placed at 100 pc.
+Middle.
+The cleaned image using combined observations in configurations 8, 9, and 10.
+The 3:1 and 2:1 resonance dust gaps are visible.
+\label{fig:alma_sim_obs}}
+\end{center}
+\end{figure}
+
+\begin{figure*}
+    \includegraphics[width=\textwidth]{figures/alma_profiles.png}
+    \caption{Caption goes here.\label{fig:alma_profiles}}
+\end{figure*}
 
@@
 
+One more connection with Aaron's paper: we have shown that second-generation dust should be present wherever planet formation is happening. 
+Planet forming disks are partial debris systems, with some mix of primordial dust and some produced by recent collisions.
+
 Compared to using the corotationg gap opened by the planet as a diagnostic \citep{2013ApJ...777L..31D, 2016ApJ...820...29D}, measuring 
@@
 
+As mentioned in section \ref{sec:vary_ecc}, the nonaxisymmetric gap structure seen in figure \ref{fig:xy} is present in a number of other studies,
+including \citet{2000Icar..143...45R} and \citet{2016ApJ...818..159T}. One would expect the same dynamics to be at work in the simulation of 
+\citet{2017ApJ...850..103B}, although the structure is not obviously visible in figure 3 of their work.
+
+Here, we present a closer look at the positions of the planetesimals at the end of the \citet{2017ApJ...850..103B} simulation. In figure 
+\ref{fig:boley_rtheta}, we show the planetesimal positions in polar, rather than Cartesian coordinates as originally presented in the paper. Two planets 
+on circular orbits are present here. The first has mass of 17 $M_{\bigoplus}$ and lies at 32.3 AU. The second planet has a mass of 50 $M_{\bigoplus}$ 
+and lies at 68.8 AU. A horseshoe shaped collection of planetesimals is visible to be corotating with each planet. Nonaxisymmetric gaps are also
+visible at the locations of low degree MMRs with the more massive planet, which are denoted with horizontal dashed lines. Moving inward from the 
+location of the more massive planet (indicated by the solid black line), features associated with the 4:3, 3:2 and 2:1 MMRs are visible. Moving 
+outward, features associated with the 3:4 and 2:3 MMRs are also visible (The 1:2 MMR lies exterior to the planetesimal population).
+
+Just as we saw in figure \ref{fig:coll_polar_e}, a gap is present at the same orbital phase as the planet at the 2:1 MMR, along with a second gap on
+the opposite side of the disk. Gaps near the 4:3 and 3:2 MMRs are also present in phase with the planet, although the number and spacing between 
+additional gaps appears to be different for each resonance. In addition, the gap structure associated with the exterior MMRs appears markedly
+different than that of each corresponding interior MMR, which suggests that the structure is related to the symmetry of the path that a planetesimal
+in a frame corotating with the planet takes.
+
 \begin{figure*}

### 2020-06-20 makeFig.py

@@ -834,20 +834,26 @@ def make_coll_hist_r():
 	a211, a212 = 3.2, 3.35
 
 	c = coll_e1
-	res_mask = np.logical_and(~np.logical_and(c['a1'] > a311, c['a1'] < a312), \
-                          ~np.logical_and(c['a1'] > a211, c['a1'] < a212))
+	res_mask = np.logical_and(np.logical_and(~np.logical_and(c['a1'] > a311, c['a1'] < a312), \
+                          ~np.logical_and(c['a1'] > a211, c['a1'] < a212)),
+							np.logical_and(~np.logical_and(c['a2'] > a311, c['a2'] < a312), \
+                          ~np.logical_and(c['a2'] > a211, c['a2'] < a212)))
 	coll_bins_a_e1_ex, coll_pdf_a_e1_ex = kde(c['dist1'][res_mask])
 	e1_norm = len(c[res_mask])/len(coll_e1)
 
 	c = coll_e
-	res_mask = np.logical_and(~np.logical_and(c['a1'] > a311, c['a1'] < a312), \
-                          ~np.logical_and(c['a1'] > a211, c['a1'] < a212))
+	res_mask = np.logical_and(np.logical_and(~np.logical_and(c['a1'] > a311, c['a1'] < a312), \
+                          ~np.logical_and(c['a1'] > a211, c['a1'] < a212)),
+							np.logical_and(~np.logical_and(c['a2'] > a311, c['a2'] < a312), \
+                          ~np.logical_and(c['a2'] > a211, c['a2'] < a212)))
 	coll_bins_a_e_ex, coll_pdf_a_e_ex = kde(c['dist1'][res_mask])
 	e_norm = len(c[res_mask])/len(coll_e)
 
 	c = coll_e2
-	res_mask = np.logical_and(~np.logical_and(c['a1'] > a311, c['a1'] < a312), \
-                          ~np.logical_and(c['a1'] > a211, c['a1'] < a212))
+	res_mask = np.logical_and(np.logical_and(~np.logical_and(c['a1'] > a311, c['a1'] < a312), \
+                          ~np.logical_and(c['a1'] > a211, c['a1'] < a212)),
+							np.logical_and(~np.logical_and(c['a2'] > a311, c['a2'] < a312), \
[…]

### 2020-06-21 main.tex
Finish implementing aaron's edits

@@
 presence of a giant planet, either embedded in the disk \citep{2015MNRAS.453L..73D} or orbiting externally, although the details of gas-dust 
-interactions can have strong effects on the resulting morphologies (Dong).In gas-poor/debris systems, a giant perturber can also influence the 
+interactions can have strong effects on the resulting morphologies (Dong) (Need to ask aaron which paper he meant to reference here).
+In gas-poor/debris systems, a giant perturber can also influence the
 structure of the dust continuum emission.
@@
 \end{equation}
-
-\noindent It should be noted that equation \ref{eq:res_fo} becomes invalid as $e$ approaches zero \citep{2020arXiv200609452M}. The secular forcing 
-in our simulations, however, keeps planetesimals outside of this more complex regime.
 
@@
 
-While the collisional dust profiles show radial amplitude variations, we still need to assess whether those variations could be observable.  
-To proceed, we create a skymodel for simulated ALMA observations as follows.
-First, we use the radially-averaged collision frequency from simulation e2m2 (Fig.~\ref{fig:coll_hist_r}) as the template for an azimuthally symmetric disk.
-We then scale that profile by a factor of ten, which places ``Jupiter'' at 52 au.  
-This scaling is permitted by the dynamics and makes the disk comparable in size to the many disks that have now been observed by ALMA (maybe reference DSHARP).  
-The observed size scale is then set by envisaging a face-on disk at a distance of 100 pc.
+While the collisional dust profiles show radial amplitude variations, we still need to assess whether those variations could be observable. To proceed, 
+we create a sky model for simulated ALMA observations as follows. First, we use the radially-averaged collision profile from each simulation (see fig 
+\ref{fig:coll_polar_e} and \ref{fig:coll_polar_m}) as the template for an azimuthally symmetric disk. We then scale the size of each profile by a factor of 
+ten, which places the perturbing planet at 52 au. This scaling is permitted by the dynamics (both the resonance widths and the forced eccentricities 
+are scale-free) and makes the disk comparable in size to the many disks that have now been observed by ALMA \citep{2018ApJ...869L..42H}. The 
+observed size scale is then set by envisaging a face-on disk at a distance of 100 pc.
 
-The skymodel intensity (flux per pixel) is produced by interpolating the radial collision frequency onto a 2D Cartesian grid with cell widths of approximately 2 mas. 
-In doing so, we choose to make the intensity proportional to the collision frequency (i.e., the dust) because it is the most straightforward case. 
-Many different parameterizations are possible, depending on optical depth, grain size, disk temperature, etc., but we will avoid such complications here. 
-We normalize the intensity by setting the total disk flux density to be 100 mJy at about 350 GHz.
+The sky model intensity (flux per pixel) is produced by interpolating the radial collision frequency onto a 2D Cartesian grid with cell widths of 
+approximately 2 mas. In doing so, we choose to make the intensity proportional to the collision frequency (i.e., the dust) because it is the most 
+straightforward case. Many different parameterizations are possible, depending on optical depth, grain size, disk temperature, etc., but we will avoid 
+such complications here. We normalize the intensity by setting the total disk flux density to be 100 mJy at about 350 GHz.
 
-The simulated observations are performed using the {simobserve} task in {\sc CASA} \citep{2007ASPC..376..127M}.
-The disk is given an $\rm RA = 11^{\rm h} 01^{\rm m} 52^{\rm s}$ and a $\delta = -34^\circ 42\arcmin 17\arcsec$ (i.e., the J2000 coordinates for TW Hydrae) and is ``observed'' through transit on March 20, 2020.
-We observe the disk using configurations 8, 9, and 10 at 350 GHz (cycle 6 antenna file), spending six hr on-source in each configuration\footnote{We have imagined that the TAC likes us.}.  
-The visibilities are corrupted with thermal noise, setting $\rm PWV=1.5$. 
-They are then combined, imaged, and cleaned using the task tclean. Imaging uses Briggs weighting with a robustness parameter of -1.
+The simulated observations are performed using the {simobserve} task in {\sc CASA} \citep{2007ASPC..376..127M}.  The disk is given an 
+$\rm RA = 11^{\rm h} 01^{\rm m} 52^{\rm s}$ and a $\delta = -34^\circ 42\arcmin 17\arcsec$ (i.e., the J2000 coordinates for TW Hydrae) and is 
+``observed'' through transit on March 20, 2020. We observe the disk using configurations 8, 9, and 10 at 350 GHz (cycle 6 antenna file), spending six 
+hours on-source in each configuration\footnote{We have imagined that the TAC really likes us.}.  The visibilities are corrupted with thermal noise, 
+setting $\rm PWV=1.5$. They are then combined, imaged, and cleaned using the task {tclean}. Imaging uses Briggs weighting with a robustness 
+parameter of -1.
 
-The results are shown in Figure \ref{fig:alma_sim_obs}.
-The 3:1 and 2:1 resonances can be easily identified in the cleaned image and in the corresponding radial profile.
-Moreover, the features are qualitatively similar to the bright rings and dark gaps seen in actual disk profiles (maybe HL Tau cite).
-[We should make the skymodel available to anyone who wants to use it]
+The results for the nominal simulation (e2m2) are shown in figure \ref{fig:alma_sim_obs}. The 3:1 and 2:1 resonances can be easily identified in the 
+cleaned image and in the corresponding radial profile.  Moreover, the features are qualitatively similar to the bright rings and dark gaps seen in actual 
+disk profiles \citep{2015ApJ...808L...3A}. [We should make the sky model available to anyone who wants to use it]
 
-Also mention figure \ref{fig:alma_profiles}.
+In figure \ref{fig:alma_profiles}, we show the azumithally-averaged radial profile constructed from the simulated cleaned image from all five 
+simulations. In all cases, a bump or a dip feature is clearly visible at the location of the 3:1 and 2:1 MMRs, indicated by the dashed vertical line. 
+As mentioned previously, the feature at the 2:1 MMR acts as the actual diagnostic indicator, while the 3:1 resonance is mainly useful for 
+determining where the 2:1 MMR is actually located. (Still waiting on Aaron to finish making images for the e2m1 and e2m3 case).
 
@@
     \caption{Simulated ALMA observations for the nominal (e2m2) case.
-Top.
-The skymodel based on the radial collision distribution from the e2m2 simulation.
-The size of the disk has been scaled by a factor of 10 and placed at 100 pc.
-Middle.
-The cleaned image using combined observations in configurations 8, 9, and 10.
-The 3:1 and 2:1 resonance dust gaps are visible.
+Top: The sky model based on the radial collision distribution.
+The size of the disk has been scaled by a factor of 10 and placed at  a distance of 100 pc.
+Bottom: The cleaned image using combined observations in configurations 8, 9, and 10.
+The circle in the bottom left indicates the simulated beam size.
+Gaps in the dust due to the 3:1 and 2:1 resonances are visible.
 \label{fig:alma_sim_obs}}
@@
     \includegraphics[width=\textwidth]{figures/alma_profiles.png}
-    \caption{Caption goes here.\label{fig:alma_profiles}}
+    \caption{The azimuthally-averaged radial profile based on the simulated cleaned images from all five simulations.
+The eccentricty of the perturbing planet increases from left to right, while the mass of the planet increases from bottom to top.
+The vertical dashed lines indicate the locations of the 3:1 and 2:1 resonances.
+As in figure \ref{fig:alma_sim_obs}, the size scale of the disk has been expanded by a factor of 10 and then placed at a distance of 100 pc.\label{fig:alma_profiles}}
 \end{figure*}
@@
 
+In line with \citet{2017ApJ...850..103B}, the results of this work suggest that, in planet forming disks, the observed dust structure should not be 
+interpreted as simply the result of primordial dust that is perturbed by the planets and gas. Instead, some morphological features could be the product 
+of collisional dynamics between larger bodies. Within the confines of the simulations presented here, we have shown that this second-generation dust 
+can give rise to significant features in the dust emission profile. For this reason, we emphasize that planet-forming disks should be thought of as 
+existing along an evolutionary continuum, with the youngest disks being dominated by primordial dust and gas and the most evolved disks being 
+comprised of mainly collisionally generated dust.
+
 The results presented here appear to be broadly consistent with the planetesimal dynamics seen by \citet{2016ApJ...818..159T}. In their case, a dip 
@@
 not be quite as useful for this type of measurement, however.
-
-One more connection with Aaron's paper: we have shown that second-generation dust should be present wherever planet formation is happening. 
-Planet forming disks are partial debris systems, with some mix of primordial dust and some produced by recent collisions.
 
@@
 
-Just as we saw in figure \ref{fig:coll_polar_e}, a gap is present at the same orbital phase as the planet at the 2:1 MMR, along with a second gap on
+Similar to figure \ref{fig:coll_polar_e}, a gap is present at the same orbital phase as the planet at the 2:1 MMR, along with a second gap on
 the opposite side of the disk. Gaps near the 4:3 and 3:2 MMRs are also present in phase with the planet, although the number and spacing between 
@@
     \includegraphics[width=\textwidth]{figures/boley_rtheta}
-    \caption{Caption goes here\label{fig:boley_rtheta}}
+    \caption{Positions of planetesimals at the end of the simulation presented in \citet{2017ApJ...850..103B} in polar coordinates.
+The solid line marks the location of a 50 $M_{\bigoplus}$ planet embedded in the disk.
+The dashed lines mark the locations of first order MMRs.
+A second planet is also present at 32.3 AU, although it is not massive enough to induce any significant structure in the disk near associated resonances.\label{fig:boley_rtheta}}
 \end{figure*}

### 2020-06-21 makeFig.py

@@ -1234,12 +1234,14 @@ def make_boley_rtheta():
 	#axes.axhline(51.3, linestyle='--', lw=1) # 2:1
 
 	# Planet 2
-	axes.axhline(68.8, color='black')
-	axes.axhline(56.8, color='black', linestyle='--', lw=0.5) # 4:3
-	axes.axhline(52.5, color='black', linestyle='--', lw=0.5) # 3:2
-	axes.axhline(43.3, color='black', linestyle='--', lw=0.5) # 2:1
-	axes.axhline(83.3, color='black', linestyle='--', lw=0.5) # 3:4
-	axes.axhline(90.1, color='black', linestyle='--', lw=0.5) # 2:3
+	lw = 2
+	alpha = 0.5
+	axes.axhline(68.8, color='black', lw=lw)
+	axes.axhline(56.8, color='black', linestyle='--', lw=lw, alpha=alpha) # 4:3
+	axes.axhline(52.5, color='black', linestyle='--', lw=lw, alpha=alpha) # 3:2
+	axes.axhline(43.3, color='black', linestyle='--', lw=lw, alpha=alpha) # 2:1
+	axes.axhline(83.3, color='black', linestyle='--', lw=lw, alpha=alpha) # 3:4
+	axes.axhline(90.1, color='black', linestyle='--', lw=lw, alpha=alpha) # 2:3
 
 	plt.savefig(file_str, format=fmt, bbox_inches='tight')
 
@@ -1270,9 +1272,10 @@ def make_alma_profile():
 	    ax.axvline(dist_to_ang(res_dist[2]), linestyle='--')
 	    ax.axvline(dist_to_ang(res_dist[5]), linestyle='--')
 	    ax.set_title(sim_title[idx])
-	    ax.set_xlabel('R [arcsec]')
+	    if idx != 0 and idx != 2:
+	    	ax.set_xlabel('R [arcsec]')
 	    if idx != 2 and idx != 3:
-	    	ax.set_ylabel('Jy/beam')
+	    	ax.set_ylabel('Flux [Jy/beam]')
 	    ax.set_xlim(0.2, 0.4)
 	    ax.set_ylim(-0.001, 0.145)
 	    
@@ -1304,7 +1307,7 @@ def gen_coll_PDF():
 
 #gen_coll_PDF()
 #make_boley_rtheta()
-#make_alma_profile()
+make_alma_profile()
 #make_coll_polar_e()
[…]

### 2020-06-23 alma/makeprofile.py
updated to make new files

@@ -9,9 +9,9 @@ import sys
 import numpy as np
 
 
-SKYFITS="skymodel-e1m2.fits" # skymodel for simulated observations
-SIMFITS="e1m2_robustm1.fits"  # simulated observations, cleaned output file
-affix="e1m2"
+SKYFITS="skymodel-e2m3.fits" # skymodel for simulated observations
+SIMFITS="e2m3_robustm1.fits"  # simulated observations, cleaned output file
+affix="e2m3"
 
 hdul = pyfits.open(SIMFITS)
 

### 2020-06-23 makeFig.py
Fill in missing data in figure 9

@@ -1250,11 +1250,11 @@ def make_alma_profile():
 	if not clobber and os.path.exists(file_str):
 		return
 
-	r1, p1 = [0], [0]
+	r1, p1 = np.loadtxt('alma/e2m1.txt')
 	r2, p2 = np.loadtxt('alma/e1m2.txt')
 	r3, p3 = np.loadtxt('alma/e2m2.txt')
 	r4, p4 = np.loadtxt('alma/e3m2.txt')
-	r5, p5 = [0], [0]
+	r5, p5 = np.loadtxt('alma/e2m3.txt')
 
 	r = [r1, r2, r3, r4, r5]
 	p = [p1, p2, p3, p4, p5]
@@ -1275,7 +1275,7 @@ def make_alma_profile():
 	    if idx != 0 and idx != 2:
 	    	ax.set_xlabel('R [arcsec]')
 	    if idx != 2 and idx != 3:
-	    	ax.set_ylabel('Flux [Jy/beam]')
+	    	ax.set_ylabel('Brightness [Jy/beam]')
 	    ax.set_xlim(0.2, 0.4)
 	    ax.set_ylim(-0.001, 0.145)
 	    

### 2020-06-23 main.tex
Fill in missing data in figure 9
Insert missing Dong et. al citation from introduction

@@
 presence of a giant planet, either embedded in the disk \citep{2015MNRAS.453L..73D} or orbiting externally, although the details of gas-dust 
-interactions can have strong effects on the resulting morphologies (Dong) (Need to ask aaron which paper he meant to reference here).
-In gas-poor/debris systems, a giant perturber can also influence the
-structure of the dust continuum emission.
-For example, a misaligned giant planet can produce nonaxisymmetric features such as warps \citep{2001A&A...370..447A}, highly eccentric perturbers can produce structures through secular interactions
+interactions can have strong effects on the resulting morphologies \citep{2018ApJ...866..110D}. In gas-poor/debris systems, a giant perturber can also influence 
+the structure of the dust continuum emission. For example, a misaligned giant planet can produce nonaxisymmetric features such as warps 
+\citep{2001A&A...370..447A}, highly eccentric perturbers can produce structures through secular interactions 
 \citep{2014MNRAS.443.2541P, 2015MNRAS.448.3679P}, and mean motion resonances (MMRs) can open gaps
@@
 As mentioned previously, the feature at the 2:1 MMR acts as the actual diagnostic indicator, while the 3:1 resonance is mainly useful for 
-determining where the 2:1 MMR is actually located. (Still waiting on Aaron to finish making images for the e2m1 and e2m3 case).
+determining where the 2:1 MMR is actually located.
 

### 2020-06-24 main.tex
Typos and small suggestions.

@@
 presence of a giant planet, either embedded in the disk \citep{2015MNRAS.453L..73D} or orbiting externally, although the details of gas-dust 
-interactions can have strong effects on the resulting morphologies \citep{2018ApJ...866..110D}. In gas-poor/debris systems, a giant perturber can also influence 
+interactions can have strong effects on the resulting morphologies
+\citep{2018ApJ...866..110D}. In gas-poor/debris systems, a giant
+planet perturber can also influence 
 the structure of the dust continuum emission. For example, a misaligned giant planet can produce nonaxisymmetric features such as warps 
@@
 used and describe the initial conditions chosen for five simulations in which a perturbing giant planet is given various masses 
-and eccentricities. Section \ref{sec:results} presents the results of these simulations and we use the collision statistics to generate synthetic dust 
+and eccentricities. Section \ref{sec:results} presents the results of these simulations, and we use the collision statistics to generate synthetic dust 
 emission profiles that would be detected with observing facilities like ALMA. Next, we show in section \ref{sec:constrain} that a characteristic bump 
 or dip feature appears in the dust emission near the interior 2:1 MMR, the presence of which depends on the mass and eccentricity of the perturbing 
-planet. We discuss the potential of using this feature to place and upper or lower on the mass and eccentricity of the planet and conclude in section 
+planet. We discuss the potential of using this feature to place upper
+or lower limits on the mass and eccentricity of the planet and conclude in section 
 \ref{sec:conclusions}.
@@
 
-The most direct and widespread effect that a giant perturber will have on a planetesimal disk is through secular forcing of the 
+The most direct and widespread effect that a giant planet perturber will have on a planetesimal disk is through secular forcing of the 
 eccentricities of the planetesimals. This will cause the complex eccentricities of the planetesimals to take on a time-independent 
@@
 \noindent Here, $\alpha = a_{g} / a$ where $a_{g}$ and $a$ are the semi-major axes of the giant planet and the planetesimal, 
-respectively. $e_{g}$ and $\varpi_{g}$ are the eccentricity and longitude of pericenter of the giant and $b^{j}_{s} (\alpha)$ is a 
+respectively. $e_{g}$ and $\varpi_{g}$ are the eccentricity and
+longitude of pericenter of the giant planet, and $b^{j}_{s} (\alpha)$ is a 
 Laplace coefficient given by \citep{2000ssd..book.....M} as
@@
 
-\noindent where $\lambda = \varpi + M$ is the mean longitude of a body. For bodies in resonance, the critical angle will librate around an 
+\noindent where $\lambda = \varpi + M$ is the mean longitude of a
+body, with $M$ being the mean anomoly. For bodies in resonance, the critical angle will librate around an 
 equlibrium value, while this angle will circulate outside of resonance. For small eccentricities, this behavior is analogous to the motion of a 
@@
 the $\phi$. For second and higher order resonances, the maximum libration width is given by
+% TRQ: there should be a reference (or references) for the equations
+% below.  Perhaps something like "Below we derive the libration widths
+% following Murray & Dermott, chapter XX.
 
@@
 
-\noindent where n, a and e are the mean motion, semimajor axis and eccentricity of the unperturbed body. $C_{r}$ is a constant defined by 
+\noindent where $n$, $a$ and $e$ are the mean motion, semimajor axis and eccentricity of the unperturbed body. $C_{r}$ is a constant defined by 
 $m'/m_{c} n \alpha f_{d}(\alpha)$, where $\alpha$ = $a/a'$ and $f_{d}$ is the resonant part of the disturbing function. For an interior second-order 
@@
 
-In total, five simulations are run, which are listed in table \ref{tab:sims}. The first is a `nominal' case, in which the perturbing planet's mass and 
+In total, five simulations are run, which are listed in table
+\ref{tab:sims}. The first
+% TRQ: second?
+is a ``nominal'' case, in which the perturbing planet's mass and 
 eccentricity are set to that of Jupiter's. In the other four cases, the mass (eccentricity) is increased or decreased by a factor of two, while the 
@@
 the symplectic nature of the integration without being too computationally expensive. Although using $\Delta T$ = 0.01 yr keeps the 
-integration symplectic, we find that a small amount of artificial precession is produced. This is most noticeable at the inner edge of the
+integration symplectic, we find that a small amount of artificial
+precession is produced.
+% TRQ: should we say why?
+This is most noticeable at the inner edge of the
 planetesimal disk.
+% TRQ: so are all particles on a base timestep of 0.0025 yr?
 We reduce the base time step size by an additional factor of 4 to the prevent the longitude of perihelia of planetesimals at the inner edge of the disk from drifting by more than the intrinsic spread in $\varpi$ due to the free eccentricity over the course of our integrations.
@@
 which the radii of all bodies are inflated by a factor of 2.5. Any bodies with imminent collisions predicted using the inflated radii are 
-placed on a time step that is a factor of 16 smaller than the orbital time step. The purpose of the two-tiered scheme is to properly resolve 
+placed on a time step that is a factor of 16 smaller than the orbital
+time step.
+% TRQ: this shorter timestep is still larger than the planetesimal
+% dynamical time; is this a problem?
+The purpose of the two-tiered scheme is to properly resolve 
 the gravitational interactions between any bodies that undergo a close encounter. This prevents the coarser base time step from 
@@
     \caption{The positions of the remaining planetesimals at the end of the e1m2 (left), e2m2 (center) and e3m2 (right) simulations. The red dot 
-    indicates the position of the giant planet and the dashed line points in the direction of the planet's longitude of perihelion. Non-axisymmetric gaps 
+    indicates the position of the giant planet, and the dashed line points in the direction of the planet's longitude of perihelion. Non-axisymmetric gaps 
     are apparent near the locations of MMRs. At higher eccentricities, more resonances become visible. At the 2:1 MMR, gap features at $\theta$ = 0 
@@
 the semimajor axis and eccentricity) of a planetesimal in resonance takes to undergo a full oscillation is given by
-
+% TRQ: again cite book for this.
 \begin{equation}\label{eq:lib_time}
@@
 time (see Appendix \ref{sec:boley_plot}). It is worth noting that \citet{2000Icar..143...45R} started with a completely cold planetesimal disk and a 
-Jupiter mass planet on a circular, coplanar orbit. \citet{2017ApJ...850..103B} used a similar setup. This, the presence of these features seems robust 
+Jupiter mass planet on a circular, coplanar
+orbit. \citet{2017ApJ...850..103B} used a similar setup.
+Thus, the presence of these features seems robust 
 to the choice of initial conditions.
@@
 The effects of the resonances become much more apparent in semimajor axis-eccentricity space, which is shown in figure \ref{fig:ae}. In all cases, 
-the 3:1, 2:1 and 5:3 resonances are readily visible as 'spikes' in the eccentricity that bend slightly inward (due to the conservation of $E_{J}$). In the 
+the 3:1, 2:1 and 5:3 resonances are readily visible as ``spikes'' in the eccentricity that bend slightly inward (due to the conservation of $E_{J}$). In the 
 e3m2 simulation, features also appear near the 5:2, 7:3 and 5:3 resonances. The absence of these features from the e1m2 simulation can be 
@@
 Another important effect of the resonances is visible in figure \ref{fig:long_ph}, which shows the orientation of the longitude of perihelia of 
-planetesimals in the disk. Inside of the resonances, orbits of planetesimals quickly precess and their orientations are effectively randomized. An 
+planetesimals in the disk. Inside of the resonances, orbits of planetesimals quickly precess, and their orientations are effectively randomized. An 
 important point to note is that this strong precession effect quickly disappears beyond the boundaries of the resonance. This turns out to be 
@@
 Next, we examine the statistics of collisions resolved in each of the simulations. The 3D positions and velocities of the two colliding bodies are 
-recorded to a table at the moment of impact. We derive the Keplerian orbital elements of a collision using these positions and velocities. 
-First, we examine the semimajor axis of the first collider, which is shown in figure \ref{fig:coll_hist_a}. During a collision, the 'first' particle is defined 
+recorded in a table at the moment of impact. We derive the Keplerian orbital elements of a collision using these positions and velocities. 
+First, we examine the semimajor axis of the first collider, which is shown in figure \ref{fig:coll_hist_a}. During a collision, the ``first'' particle is defined 
 as the more massive of the two. However, nearly all of the collisions happen between the initial, equal-mass planetesimals. In this case, the 
 distinction is set by the collision search algorithm and is rather arbitrary. In all of the plots where we show collision statistics, we have verified that 
-using the 'first' or 'second' collider does not qualitatively change any of the features. We find that some of the features present in figure 
+using the ``first'' or ``second'' collider does not qualitatively change any of the features. We find that some of the features present in figure 
 \ref{fig:coll_hist_a} in this and subsequent figures are highly sensitive to the number of bins and the location of the bin edges. For this reason, we 
@@
 Closer to the star, the planetesimal disk starts off dynamically colder. Here, additional heating from the resonance acts to suppress the gravitational 
-focusing cross section, which reduces the collision rate from its non-perturbed value.
-Further out in the disk, where the unperturbed encounter velocity is higher, the gravitational focusing cross section is already minimized.
-Any additional heating instead acts to simply increase the encounter rate between bodies, which enhances the collision rate.
-This explains the relative drop in the collision rate near the 3:1 MMR and the relative increase near the 2:1 and 5:3 resonances.
-Although this could potentially serve as a useful diagnostic of the planetesimal size in a disk (because the mutual escape velocity sets how dynamically hot the bodies can get before gravitational focusing is suppressed), a direct measurement of the semimajor axes of the colliding planetesimals is not possible.
-Furthermore, as will demonstrate next, collisions due to bodies in resonance do not have a significant effect on the final shape of the radial dust distribution.
+focusing cross section, which reduces the collision rate from its
+non-perturbed value. Further out in the disk, where the unperturbed
+encounter velocity is higher, the gravitational focusing cross section
+is already minimized. Any additional heating instead acts to simply
+increase the encounter rate between bodies, which enhances the
+collision rate. This explains the relative drop in the collision rate
+near the 3:1 MMR and the relative increase near the 2:1 and 5:3
+resonances. Although this could potentially serve as a useful
+diagnostic of the planetesimal size in a disk (because the mutual
+escape velocity sets how dynamically hot the bodies can get before
+gravitational focusing is suppressed), a direct measurement of the
+semimajor axes of the colliding planetesimals is not
+possible. Furthermore, as we will demonstrate next, collisions due to bodies in resonance do not have a significant effect on the final shape of the radial dust distribution.
 
@@
 In semimajor axis space, prominent features appear near the 3:1 and 2:1 MMRs.
-Near the 3:1, the collision rate decreases from its unperturbed value, while an enhancement apepars near the 2:1.\label{fig:coll_hist_a}}
+Near the 3:1, the collision rate decreases from its unperturbed value, while an enhancement appears near the 2:1.\label{fig:coll_hist_a}}
 \end{center}
@@
 of second-generation dust can be constructed from the cylindrical distance at which the collisions occur. This is shown in figure \ref{fig:coll_hist_r}. 
-Similar to figure \ref{fig:coll_hist_a}, we use a KDE with a bandwidth of 0.02 AU to assemble the collision locations into a radial distribution. Most 
+Similar to figure \ref{fig:coll_hist_a}, we use a KDE with a width of 0.02 AU to assemble the collision locations into a radial distribution. Most 
 strikingly, the bump that was present near the 2:1 resonance is no longer visible in cylindrical distance space, although it suddenly appears again in 
@@
 mentioned in section \ref{sec:dynamics}, the circulation frequency of the critical angle slows as one approaches the edge of the resonance from the 
-outside. Following the pendulum analogy, this is equivalent to approaching the point where the pendulum becomes suspended in the vertical position. 
+outside. Following the pendulum analogy, this is equivalent to
+approaching the point where the pendulum becomes suspended in the
+vertical position
+% TRQ addition
+at top dead center. 
 When the critical angle stays relatively stationary during an encounter, the net torque will drive the longitude of pericenter towards the point of 

### 2020-07-01 main.tex
Comments are indicated by TRQ in the TeX.
Some typos are corrected as well.

@@
 distances near the 2:1 MMR are quite similar and no strong features appear in the collision profile near this region. For the e2m3 case, the edges of 
+%TRQ: I'm not seeing that much of a gap compared to e2m2 and e2m1.
 the resonances are sufficiently separated to allow a gap near the center of the 2:1 resonance to appear in the collision profile.
@@
 hours on-source in each configuration\footnote{We have imagined that the TAC really likes us.}.  The visibilities are corrupted with thermal noise, 
-setting $\rm PWV=1.5$. They are then combined, imaged, and cleaned using the task {tclean}. Imaging uses Briggs weighting with a robustness 
+% TRQ: define PWV
+setting $\rm PWV=1.5$. They are then combined, imaged, and cleaned
+using the task {\tt tclean}. Imaging uses Briggs weighting with a robustness 
 parameter of -1.
@@
 
+%TRQ: fix label on e2m2 plot.
 \begin{figure*}
@@
 
+% TRQ: perhaps mention "2:1" somewhere in the caption.
 \begin{figure}
@@
 produced when bodies at the edges of the resonance stay sufficiently separated in cylindrical distance over the course of an orbit. This is achieved 
-when either the resonance width is large and the forced eccentricity is small. The bump feature, on the other hand, is produced when there is a 
+when either the resonance width is large or the forced eccentricity is small. The bump feature, on the other hand, is produced when there is a 
 sufficiently large amount of overlap between the apocenters and pericenters of the inner and outer edges of the resonance, respectively. This is 
@@
 
+% TRQ: it took me a while to understand the dashed lines.  Is the
+% following correct: the lower dashed line is where the apo/peri of
+% the inner/outer edges of the resonance begin to overlap; the upper
+% dashed line is when the overlap is equal to the width of the
+% resonance?  Perhaps spell this out?
 In figure \ref{fig:bump_dip_diag}, we show the constraints that the presence of a bump or a dip places on possible values of $(m_{g}, e_{g})$. A dip 
@@
 
+% TRQ: perhaps a short definition of "strength" here?
 Because the strength of the 2:1 resonance scales with $e_{g}$ and  $m_{g}$, a sufficiently low mass and low eccentricity planet will not create 
@@
 
+%TRQ: perhaps thinner dashed lines for the MMRs?  It isn't easy to see
+%the gaps in the interior resonances.
 \begin{figure*}

### 2020-07-03 main.tex
Implement Tom's edits

--- 2020-06-24 main.tex
@@
 width of a resonance can be defined by determining the largest variation in semimajor axis that permits librational, rather than circulatory motion of 
-the $\phi$. For second and higher order resonances, the maximum libration width is given by
-% TRQ: there should be a reference (or references) for the equations
-% below.  Perhaps something like "Below we derive the libration widths
-% following Murray & Dermott, chapter XX.
+the $\phi$. For second and higher order resonances, the maximum libration width is given by equation 8.58 in \citet{2000ssd..book.....M} as
 
@@
 
-\noindent where $D b^{j}_{s}$ is the first derivative with respect to $\alpha$ of the Laplace coefficient defined in equation \ref{eq:lap}. This can 
-be written as
+\noindent (see \citet{2000ssd..book.....M} table 8.1) where $D b^{j}_{s}$ is the first derivative with respect to $\alpha$ of the Laplace coefficient defined in equation \ref{eq:lap}.
+This is given by \citet{1961mcm..book.....B} as
 
@@
 
-\noindent and there is an additional contribution to the motion of the critical angle by the pericenter precession rate such that
+\noindent (see \citet{2000ssd..book.....M} table 8.1) and there is an additional contribution to the motion of the critical angle by the pericenter precession rate such that
 
@@
 	\frac{\delta a}{a} = \pm \left(\frac{16}{3} \frac{\left| C_{r} \right|}{n} e \right)^{1/2} \left(  1 + \frac{1}{27 p^2 e^3} \frac{\left| C_{r} \right|}{n} 
-	\right)^{1/2} - \frac{2}{9 p e}  \frac{\left| C_{r} \right|}{n}.
+	\right)^{1/2} - \frac{2}{9 p e}  \frac{\left| C_{r} \right|}{n}
 \end{equation}
+
+\noindent (see \citet{2000ssd..book.....M} equation 8.76).
 
@@
 In total, five simulations are run, which are listed in table
-\ref{tab:sims}. The first
-% TRQ: second?
+\ref{tab:sims}. The second
 is a ``nominal'' case, in which the perturbing planet's mass and 
@@
 For the purposes of the integrator, there are two relevant timescales in this system. The first is the orbital dynamical time $\sqrt{a^3/
-G M_{\odot}}$. All particles are placed on a fixed time step of $\Delta T$ = 0.01 yr. This is roughly 3\% of an orbital dynamical time at 
-the inner edge of the planetesimal disk. From numerical tests with {\sc ChaNGa}, we have found that this time step size preserves 
-the symplectic nature of the integration without being too computationally expensive. Although using $\Delta T$ = 0.01 yr keeps the 
-integration symplectic, we find that a small amount of artificial
-precession is produced.
-% TRQ: should we say why?
-This is most noticeable at the inner edge of the
-planetesimal disk.
-% TRQ: so are all particles on a base timestep of 0.0025 yr?
-We reduce the base time step size by an additional factor of 4 to the prevent the longitude of perihelia of planetesimals at the inner edge of the disk from drifting by more than the intrinsic spread in $\varpi$ due to the free eccentricity over the course of our integrations.
+G M_{\odot}}$. Experimentally, we have found that using a base timestep size with {\sc ChaNGa} of 3\% of an orbital dynamical time
+at the inner edge of the disk keeps the integration symplectic. Although doing so preserves orbital frequencies, the errors associated with
+precession frequencies do not average out to zero. This is especially important given the effects of secular forcing by the planet. To mitigate
+this, we further reduce the base timestep size by a factor of 4 and use $\Delta t$ = 0.0025 yr. Doing so prevents the longitude of perihelia of
+planetesimals at the inner edge of the disk, where this artificial precession is most severe, from drifting by more than the intrinsic spread in $\varpi$ due to the f
+ree eccentricity over the course of our integrations.
 
@@
 resolve the base time step and the dynamical timescale of planetesimals simultaneously, we use a two-tiered time stepping scheme. 
-To start, all bodies are placed on the orbital time step. A first pass of collision detection is then run in 
+To start, all bodies are placed on the base time step. A first pass of collision detection is then run in 
 which the radii of all bodies are inflated by a factor of 2.5. Any bodies with imminent collisions predicted using the inflated radii are 
 placed on a time step that is a factor of 16 smaller than the orbital
-time step.
-% TRQ: this shorter timestep is still larger than the planetesimal
-% dynamical time; is this a problem?
+time step. Although this is still a factor of roughly 7 larger than the dynamical time of a planetesimal, we found no difference in the collision rate
+when using any smaller of a minimum time step size.
 The purpose of the two-tiered scheme is to properly resolve 
@@
 equilibrium near the resonances before the collision rate is measured. The libration timescale, which describes how long the critical angle (and also 
-the semimajor axis and eccentricity) of a planetesimal in resonance takes to undergo a full oscillation is given by
-% TRQ: again cite book for this.
+the semimajor axis and eccentricity) of a planetesimal in resonance takes to undergo a full oscillation is given by (see equation 8.47 in \citet{2000ssd..book.....M})
 \begin{equation}\label{eq:lib_time}
@@
 approaching the point where the pendulum becomes suspended in the
-vertical position
-% TRQ addition
-at top dead center. 
+vertical position at top dead center. 
 When the critical angle stays relatively stationary during an encounter, the net torque will drive the longitude of pericenter towards the point of 
@@
 distances near the 2:1 MMR are quite similar and no strong features appear in the collision profile near this region. For the e2m3 case, the edges of
-the resonances are sufficiently separated to allow a gap near the center of the 2:1 resonance to appear in the collision profile.
+the resonances are sufficiently separated to allow what appears to be the beginning of gap to form near the center of the 2:1 resonance in the collision profile.
 
@@
 hours on-source in each configuration\footnote{We have imagined that the TAC really likes us.}.  The visibilities are corrupted with thermal noise, 
-setting $\rm PWV=1.5$. They are then combined, imaged, and cleaned using the task {tclean}. Imaging uses Briggs weighting with a robustness 
+setting the precipitable water vapor to 1.5 mm. They are then combined, imaged, and cleaned
+using the task {\tt tclean}. Imaging uses Briggs weighting with a robustness 
 parameter of -1.
@@
     \includegraphics[width=0.5\textwidth]{figures/bump_dip_diag.png}
-    \caption{The presence of a dip or bump near the resonances can be used to constrain the mass and eccentricity
+    \caption{The presence of a dip or bump near the 2:1 MMR can be used to constrain the mass and eccentricity
     of the perturbing planet. The color scale indicates the relative strength of the features, while the dashed lines
@@
 
-In figure \ref{fig:bump_dip_diag}, we show the constraints that the presence of a bump or a dip places on possible values of $(m_{g}, e_{g})$. A dip 
-is produced by a sufficiently low eccentricity, high mass planet, while a bump is produced by a high eccentricity, low mass planet. The parameter 
-choices for the five simulations presented in the previous section are shown by the black dots. Between the two dashed lines, the overlap between 
-the aphelion and perihelion distances of the inner and outer edges of the resonance is smaller than the width of the resonance. In this region, the 
-overdense regions on each side of the resonance spend roughly equal amounts of time at all possible distances, and no strong feature appears in 
-the collision profile.
+In figure \ref{fig:bump_dip_diag}, we show the constraints that the presence of a bump or a dip places on possible values of $(m_{g}, e_{g})$. The dashed
+lines indicate regions of parameter space where qualitatively different features in the collision profile are expected to form. Above the upper dashed line, the 
+resonance is wide while the radial excursion distance of planetesimals at the edge of the resonance is small, which gives rise to a dip in the collision profile. 
+Below the lower dashed line, the resonance is narrow, while the radial excursion distance is large, allowing the apocenter and pericenter distances of the edges 
+of the resonance to overlap and produce a bump in the collision profile. Between the dashed lines, the absolute value of separation between the apocenter and 
+pericenter distances of the inner and outer edges of the resonance is less than the resonance width. In this region of parameter space, no significant features in 
+the collision profile near the 2:1 MMR are expected to form.
 
-Because the strength of the 2:1 resonance scales with $e_{g}$ and  $m_{g}$, a sufficiently low mass and low eccentricity planet will not create 
+Because the strength\footnote{More specifically, the strength of the resonant term in the disturbing potential} of the 2:1 resonance scales with $e_{g}$ and  $m_{g}$, a sufficiently low mass and low eccentricity planet will not create
 enough of a perturbation in the planetesimal disk to produce a detectable bump or dip feature. The colored contours in figure \ref{fig:bump_dip_diag} 

### 2020-07-03 main.tex
Fix typos, update appendix label and figure caption

@@
 \noindent where $\lambda = \varpi + M$ is the mean longitude of a
-body, with $M$ being the mean anomoly. For bodies in resonance, the critical angle will librate around an 
+body, with $M$ being the mean anomaly. For bodies in resonance, the critical angle will librate around an 
 equlibrium value, while this angle will circulate outside of resonance. For small eccentricities, this behavior is analogous to the motion of a 
@@
 seen in polar coordinates follow the position of the giant planet in its orbit, which is shown by the vertical line. For the e2m2 case, the density 
-enhancements take up a much larger radial width, which smears out the corresponding colli- sional dust profile. In the highest forced eccentricity case 
+enhancements take up a much larger radial width, which smears out the corresponding collisional dust profile. In the highest forced eccentricity case 
 (e3m2), the density enhancements occur well within an annulus containing the resonant region, completely al- tering the radial peak-valley dust 
@@
 Although the same phenomenon appears to be happening near the 3:1 MMR, the pileups at the edges of the resonance are not as well defined. We 
-attribute this to the more comlex symmetry, compared to the 2:1 MMR. In addition, a number of other nearby resonances, including the 7:2 (at 
+attribute this to the more complex symmetry, compared to the 2:1 MMR. In addition, a number of other nearby resonances, including the 7:2 (at 
 2.25 AU), the 10:3 (at 2.33 AU), the 8:3 (at 2.71 AU) and the 5:2 (at 2.82 AU) also likely are contributing to the collision profile in cylindrical distance 
@@
 indicate the relative strength of the resonance as these quantities are varied. Although the resonance strength is equally sensitive to changes in 
-mass and eccentricity, the peri - apocenter overlap of the resonance edges is more sensitive to changes in eccentricity. This is because changes to 
+mass and eccentricity, the peri-apocenter overlap of the resonance edges is more sensitive to changes in eccentricity. This is because changes to 
 eccentricity affect both the resonance width and the forced eccentricity. As we showed in figure \ref{fig:coll_polar_m}, changing $m_{g}$ by a factor 
@@
 
-Compared to using the corotationg gap opened by the planet as a diagnostic \citep{2013ApJ...777L..31D, 2016ApJ...820...29D}, measuring 
+Compared to using the corotating gap opened by the planet as a diagnostic \citep{2013ApJ...777L..31D, 2016ApJ...820...29D}, measuring 
 variations in the dust emission near MMRs is much more subtle and requires much higher spatial resolution and sensitivity. As we have shown, the 
@@
 
+\setcounter{secnumdepth}{0}
 \section{Appendix: Nonaxisymmetric Structure in Boley 2017}\label{sec:boley_plot}
@@
 \begin{figure*}
-    \includegraphics[width=\textwidth]{figures/boley_rtheta}
+    \includegraphics[width=\textwidth]{figures/boley_rtheta.png}
     \caption{Positions of planetesimals at the end of the simulation presented in \citet{2017ApJ...850..103B} in polar coordinates.
-The solid line marks the location of a 50 $M_{\bigoplus}$ planet embedded in the disk.
-The dashed lines mark the locations of first order MMRs.
+The dashed line marks the location of a 50 $M_{\bigoplus}$ planet embedded in the disk.
+First order MMRs with the planet are indicated with arrows.
 A second planet is also present at 32.3 AU, although it is not massive enough to induce any significant structure in the disk near associated resonances.\label{fig:boley_rtheta}}

### 2020-07-06 main.tex
Minor edits, fix typos and formatting

@@
 production of second-generation dust near prominent mean-motion resonances with the planet using N-body simulations that directly resolve 
-collisions between planetesimals. We find that a distinct over- or under-density in the dust emission is produced at the interior 2:1 mean motion 
+collisions between planetesimals. We find that a distinct over- or under-density in the dust emission is produced at the interior 2:1 mean-motion 
 resonance, depending on the mass and eccentricity of the planet. The presence of one of these two features can be used to place simultaneous 
@@
 produce a distinct observable marker that could be used to infer the presence of the planet. In a followup study, it was found that morphological 
-differences in the dust emission could be used to determine whether the planet had a circular or eccentric orbit \citep{2016ApJ...820...29D}.Moreover, 
+differences in the dust emission could be used to determine whether the planet had a circular or eccentric orbit \citep{2016ApJ...820...29D}. Moreover, 
 substructure due to mean-motion resonances (MMRs) with a giant planet may hold additional clues that could be used to constrain the properties of 
-the planet.  The width of a resonance is set by both the mass of the perturbing planet, along with the unperturbed eccentricity of the planetesimals, 
+the planet.  The width of a resonance is set by both the mass of the perturbing planet and the unperturbed eccentricity of the planetesimals, 
 which is in turn set by the eccentricity of the planet through secular forcing. Therefore, the structure of second generation dust produced near MMRs 
-encodes information about both the mass and eccentricity of the planet.
+may encode information about both the mass and eccentricity of the planet.
 
@@
 To further elucidate this subject, we use the tree based N-body code {\sc ChaNGa}\citep{2008IEEEpds...ChaNGa, 2015AphCom..2..1}  to follow the 
-collisional evolution of a planetesimal disk under the gravitational influence of a Jupiter sized body. Because particle positions are sorted into a tree 
+collisional evolution of a planetesimal disk under the gravitational influence of a Jupiter-sized body. Because particle positions are sorted into a tree 
 structure, neighbor finding and collision detection can be done quickly and efficiently. This considerably relaxes the constraints on resolution and 
-integration time. With this toolset, we explore the collision rate structure of the planetesimal disk in the vicinity of mean motion resonances. In 
+integration time. With this toolset, we explore the collision rate structure of a planetesimal disk in the vicinity of mean-motion resonances with the planet. In 
 particular, we would like to determine (1) whether MMRs leave a detectable signature in the collisionally-generated dust, and (2) whether these 
@@
 used and describe the initial conditions chosen for five simulations in which a perturbing giant planet is given various masses 
-and eccentricities. Section \ref{sec:results} presents the results of these simulations, and we use the collision statistics to generate synthetic dust 
+and eccentricities. Section \ref{sec:results} presents the results of these simulations, and we use the resolved collisions to generate synthetic dust 
 emission profiles that would be detected with observing facilities like ALMA. Next, we show in section \ref{sec:constrain} that a characteristic bump 
 or dip feature appears in the dust emission near the interior 2:1 MMR, the presence of which depends on the mass and eccentricity of the perturbing 
-planet. We discuss the potential of using this feature to place upper
-or lower limits on the mass and eccentricity of the planet and conclude in section 
+planet. We discuss the potential of using this feature to place constraints on the mass and eccentricity of the planet and conclude in section 
 \ref{sec:conclusions}.
@@
 
-The most direct and widespread effect that a giant planet perturber will have on a planetesimal disk is through secular forcing of the 
-eccentricities of the planetesimals. This will cause the complex eccentricities of the planetesimals to take on a time-independent 
+The most direct and widespread effect that a perturbing giant planet will have on a planetesimal disk is through secular forcing of the planetesimals. This will 
+cause the complex eccentricities of the planetesimals to take on a time-independent 
 forced value, given by \citep{1999ApJ...527..918W} as
@@
 
-\noindent Here, $\alpha = a_{g} / a$ where $a_{g}$ and $a$ are the semi-major axes of the giant planet and the planetesimal, 
+\noindent Here, $\alpha = a_{g} / a$ where $a_{g}$ and $a$ are the semi-major axes of the giant planet and a planetesimal, 
 respectively. $e_{g}$ and $\varpi_{g}$ are the eccentricity and
@@
 
-Without any nearby secular or mean motion resonances, equation \ref{eq:eforced} will completely describe the eccentricities and longitude of  
+Without any nearby secular or mean motion-resonances, equation \ref{eq:eforced} will completely describe the eccentricities and longitude of  
 pericenter orientations of the planetesimals. Additional forces due to two-body scattering between planetesimals, along with 
@@
 
-\subsection{Mean Motion Resonances}
+\subsection{Mean-Motion Resonances}
 
@@
 perturbations. For the purposes of this study, we will ignore secular resonances, which generally occur on rather large timescales and will focus on 
-mean motion resonances (MMRs). A MMR occurs  when the orbital period ratio between two bodies is sufficiently close to
+mean-motion resonances. A MMR occurs  when the orbital period ratio between two bodies is sufficiently close to
 
@@
 
-\noindent where  $p$ and $q$ are integers $>$ 0 and the unprimed and primed quantities correspond to the perturber and the body being perturbed, respectively.
-In terms of these quantities, $P/P'$ corresponds to a $p+q:p$ resonance If the perturber is much more massive than the other body, the condition for MMR is set  by the semi-major axes of the two bodies by
+\noindent where  $p$ and $q$ are integers $>$ 0 and the unprimed and primed quantities correspond to the perturber and the body being perturbed, 
+respectively. In terms of these quantities, $P/P'$ corresponds to a $p+q:p$ resonance. If the perturber is much more massive than the other body and all of the 
+bodies lie in a near-Keplerian potential, the condition for MMR is set by
 
@@
 equlibrium value, while this angle will circulate outside of resonance. For small eccentricities, this behavior is analogous to the motion of a 
-pendulum. Variations in the critical angle are coupled to changes in the mean motion and semimajor axis \citep{2000ssd..book.....M}. An important 
-point to note, which we will come back to later, is that the variation frequency of this angle approaches zero near the edge of a resonance. The 
-width of a resonance can be defined by determining the largest variation in semimajor axis that permits librational, rather than circulatory motion of 
-the $\phi$. For second and higher order resonances, the maximum libration width is given by equation 8.58 in \citet{2000ssd..book.....M} as
+pendulum. Furthermore, variations in the critical angle are coupled to changes in the mean motion and semimajor axis \citep{2000ssd..book.....M}. An important 
+point to note, which we will revisit later, is that the variation frequency of this angle approaches zero near the edge of a resonance. The 
+width of a resonance can be defined by determining the largest variation in semimajor axis that permits librational, rather than circulatory motion of $\phi$. For 
+second order and higher MMRs, the maximum libration width is given by equation 8.58 in \citet{2000ssd..book.....M} as
 
@@
 
-For a first order resonance, the associated disturbing function terms are slightly simpler
+For a first-order resonance, the associated disturbing function terms are slightly simpler such that
 
@@
 
-Changes in eccentricity are correlated with changes in semimajor axis variations according to the Tisserand relation
+Changes in eccentricity are correlated with changes in semimajor axis according to the Tisserand relation
 
@@
 surface density of the disk near the locations of resonances, while producing a pileup of bodies on eccentric orbits adjacent to the MMR. The 
-enhanced surface density will increase the collision rate. At the same time, the large eccentricites will either lower it due to the decreased 
-effectiveness of gravitational focusing, or raise it due to the more vigorous encounter rate, depending on the size of the encounter velocity relative to 
+enhanced surface density will increase the collision rate. At the same time, the large eccentricites will either lower the collision rate due to the decreased 
+effectiveness of gravitational focusing, or raise it due to the more vigorous encounter rate, depending on the magnitude of the encounter velocity relative to 
 the escape velocity of the planetesimals. In addition, the MMRs cause the orbits of planetesimals to precess on relatively short 
@@
 eccentricity (mass) is held at the nominal value. In all cases, the perturbing giant is placed on a 5.2 AU orbit around a 1 $M_{\odot}$ star. The 
-planetesimal disk extends from 2.2 to 3.8 AU, which covers the two most prominent mean motion resonances with the giant planet, the 2:1 at 3.27 AU 
+planetesimal disk extends from 2.2 to 3.8 AU, which covers the two most prominent mean-motion resonances with the giant planet, the 2:1 at 3.27 AU 
 and the 3:1 at 2.5 AU. The planetesimal disk follows a minimum-mass solar nebula surface density profile \citep{1981PThPS..70...35H}
@@
 \noindent with $\alpha$ = 3/2 and $\Sigma_{0}$ = 10 g cm$^{-2}$. Planetesimals are given a bulk density of 2 g cm$^{-3}$ and a diameter of 
-300 km. This corresponds to a disk containing roughly 500,000 bodies. Each simulation is evolved for 5,000 years, which is about 400 Jupiter 
-orbits.
+300 km. This corresponds to a disk containing roughly 500,000 bodies. Each simulation is evolved for 5,000 years, which is about 400 orbits 
+of the perturbing planet.
 
@@
 this, we further reduce the base timestep size by a factor of 4 and use $\Delta t$ = 0.0025 yr. Doing so prevents the longitude of perihelia of
-planetesimals at the inner edge of the disk, where this artificial precession is most severe, from drifting by more than the intrinsic spread in $\varpi$ due to the f
-ree eccentricity over the course of our integrations.
+planetesimals at the inner edge of the disk, where this artificial precession is most severe, from drifting by more than the intrinsic spread in $\varpi$ due to the
+free eccentricity over the course of our integrations.
 
 An additional timescale is set by the dynamical time of the planetesimals ($\sim 1/\sqrt{G \rho}$), which is about 45 minutes. To 
-resolve the base time step and the dynamical timescale of planetesimals simultaneously, we use a two-tiered time stepping scheme. 
+resolve the base time step and the dynamical timescale of planetesimals simultaneously, we use a two-tiered time stepping scheme following
+\citep{2015ApJ...806...23L}. 
 To start, all bodies are placed on the base time step. A first pass of collision detection is then run in 
@@
 important point to note is that this strong precession effect quickly disappears beyond the boundaries of the resonance. This turns out to be 
-important to explain the nonaxisymmetric structure seen in figure \ref{fig:xy}, which will be addressed in more detail below.
+key to explaining the nonaxisymmetric structure seen in figure \ref{fig:xy}, which will be addressed in more detail below.
 
 Next, we examine the statistics of collisions resolved in each of the simulations. The 3D positions and velocities of the two colliding bodies are 
-recorded in a table at the moment of impact. We derive the Keplerian orbital elements of a collision using these positions and velocities. 
+recorded to a table at the moment of impact. We derive the Keplerian orbital elements of a collision using these positions and velocities. 
 First, we examine the semimajor axis of the first collider, which is shown in figure \ref{fig:coll_hist_a}. During a collision, the ``first'' particle is defined 
@@
 construct a PDF of the collisions using a Kernel Density Estimate (KDE). We use the {\sc neighbors.KernelDensity} function from the {\sc sklearn} 
-\citep{scikit-learn} package to construct our KDEs. We use a gaussian kernel with a FWHM of 0.02 AU.
+\citep{scikit-learn} package to construct our KDEs, using a gaussian kernel with a FWHM of 0.02 AU.
 
@@
 
-We attribute the production of a bump or a dip at certain resonances to changes in the gravitational focusing factor during two-body encounters. 
+We attribute the production of a bump or a dip at certain semi-major axes to changes in the gravitational focusing factor during two-body encounters. 
 Closer to the star, the planetesimal disk starts off dynamically colder. Here, additional heating from the resonance acts to suppress the gravitational 
@@
 \begin{equation}\label{eq:t_edamp}
-    t_{e, damp} = \frac{8 s \rho}{3 e C_{D} \rho_{g} v_{th}}.
+    t_{e, damp} = \frac{8 s \rho}{3 e C_{D} \rho_{g} v_{th}},
 \end{equation}
@@
 enhancements take up a much larger radial width, which smears out the corresponding collisional dust profile. In the highest forced eccentricity case 
-(e3m2), the density enhancements occur well within an annulus containing the resonant region, completely al- tering the radial peak-valley dust 
+(e3m2), the density enhancements occur well within an annulus containing the resonant region, completely altering the radial peak-valley dust 
 morphology.
@@
 approaching the point where the pendulum becomes suspended in the
-vertical position at top dead center. 
+at top dead center. 
 When the critical angle stays relatively stationary during an encounter, the net torque will drive the longitude of pericenter towards the point of 
 conjunction \citep{1976ARA&A..14..215P}.  This is the basic mechanism that causes isolated resonances to be stable. Inside of resonance, the critical 
-angle librates about some value and this configuration is maintained. Just outside of resonance, however, the critical angle slowly drifts away, with the 
-drift direction changing sign across the resonance. The net result of this is that bodies just outside of the resonance experience a torque from that 
-planet that temporarily drives their pericenters toward the current orbital position of the planet. After the encounter ends, differential rotation of the disk 
+angle librates about an equilibrium value and this configuration is maintained. Just outside of resonance, however, the critical angle slowly drifts away, with the 
+drift direction changing sign across the location of exact resonance. The net result of this is that bodies just outside of the resonance experience a torque from 
+the planet that temporarily drives their pericenters toward the current orbital position of the planet. After the encounter ends, differential rotation of the disk 
 slowly destroys the configuration over part of an orbit. As the planet passes by, adjacent planetesimals near the resonance edges temporarily align 
@@
 planet is on a circular orbit, this structure is still present (see figure 3 of \citet{2016ApJ...818..159T} and Appendix \ref{sec:boley_plot}). The only 
-relation between the structure of the gaps in the disk and the path of a resonant particle in the corotating frame is that both phenomena produce the 
-same symmetries, which depend on the given resonance.
+connection between the structure of the gaps in the disk and the path of a resonant particle in the corotating frame is that both phenomena produce the 
+same symmetries, which depend on the particular MMR.
 
@@
 resonance edges vary over the course of an orbit. The maximum and minimum radial distance that the resonance edges occupy is indicated by the 
-solid and dashed lines in figure \ref{fig:coll_polar_e}. If the the aphelion distance of the inner edge becomes comparable to the perihelion distance of 
+solid and dashed lines in figure \ref{fig:coll_polar_e}. If the the aphelion distance of the inner edge becomes close to the perihelion distance of 
 the outer edge, the overdense regions on each side of the resonance meet and we should expect to see the central dip feature in the collision profile 
@@
 2.25 AU), the 10:3 (at 2.33 AU), the 8:3 (at 2.71 AU) and the 5:2 (at 2.82 AU) also likely are contributing to the collision profile in cylindrical distance 
-space near the 3:1. The width of the 3:1 MMR is also much narrower than the 2:1, which means that any dip or bump features produced by it would 
+space near the 3:1 MMR. The 3:1 MMR is also much narrower than the 2:1, which means that any dip or bump features produced by it would 
 require much higher resolution observations. For these reasons, we will focus on the 2:1 MMR as the main diagnostic indicator.
@@
 While the collisional dust profiles show radial amplitude variations, we still need to assess whether those variations could be observable. To proceed, 
-we create a sky model for simulated ALMA observations as follows. First, we use the radially-averaged collision profile from each simulation (see fig 
+we create a sky model for simulated ALMA observations as follows. First, we use the radially-averaged collision profile from each simulation (see figures 
 \ref{fig:coll_polar_e} and \ref{fig:coll_polar_m}) as the template for an azimuthally symmetric disk. We then scale the size of each profile by a factor of 
@@
 are scale-free) and makes the disk comparable in size to the many disks that have now been observed by ALMA \citep{2018ApJ...869L..42H}. The 
-observed size scale is then set by envisaging a face-on disk at a distance of 100 pc.
+angular size scale is then set by envisaging a face-on disk at a distance of 100 pc.
 
@@
 
-The simulated observations are performed using the {simobserve} task in {\sc CASA} \citep{2007ASPC..376..127M}.  The disk is given an 
+The simulated observations are performed using the {\sc simobserve} task in {\sc CASA} \citep{2007ASPC..376..127M}.  The disk is given an 
 $\rm RA = 11^{\rm h} 01^{\rm m} 52^{\rm s}$ and a $\delta = -34^\circ 42\arcmin 17\arcsec$ (i.e., the J2000 coordinates for TW Hydrae) and is 
@@
 cleaned image and in the corresponding radial profile.  Moreover, the features are qualitatively similar to the bright rings and dark gaps seen in actual 
-disk profiles \citep{2015ApJ...808L...3A}. [We should make the sky model available to anyone who wants to use it]
+disk profiles \citep{2015ApJ...808L...3A}.
+% [We should make the sky model available to anyone who wants to use it]
 
-In figure \ref{fig:alma_profiles}, we show the azumithally-averaged radial profile constructed from the simulated cleaned image from all five 
-simulations. In all cases, a bump or a dip feature is clearly visible at the location of the 3:1 and 2:1 MMRs, indicated by the dashed vertical line. 
-As mentioned previously, the feature at the 2:1 MMR acts as the actual diagnostic indicator, while the 3:1 resonance is mainly useful for 
+In figure \ref{fig:alma_profiles}, we show the azumithally-averaged radial profiles constructed from the simulated cleaned image from all five 
+simulations. In all cases, a bump or a dip feature is clearly visible at the location of the 3:1 and 2:1 MMRs, indicated by the dashed vertical lines. 
+As mentioned previously, the feature at the 2:1 MMR acts as the actual diagnostic indicator, while the 3:1 resonance (along with the gap that would presumably 
+open at the location of the planet) is mainly useful for 
 determining where the 2:1 MMR is actually located.
@@
 
-In figure \ref{fig:bump_dip_diag}, we show the constraints that the presence of a bump or a dip places on possible values of $(m_{g}, e_{g})$. The dashed
+In figure \ref{fig:bump_dip_diag}, we show the constraints that the presence of a bump or a dip or dip at the 2:1 MMR places on possible values of $(m_{g}, e_{g})$. The dashed
 lines indicate regions of parameter space where qualitatively different features in the collision profile are expected to form. Above the upper dashed line, the 
@@
 when collisions are ordered by cylindrical distance from the central star. If enough gas from the protoplanetary disk is still present, dust generated 
-from planetesimal-planetesimal collisions will immediately couple to the gas and fall onto a circular orbit. In this case, the radial dust emission profile, 
-which can be observed at mm wavelengths, directly traces the radial collision rate and therefore the dynamical activity of the planetesimals.
+from planetesimal-planetesimal collisions will immediately fall onto a circular orbit. In this case, the radial dust emission profile, 
+which can be observed at sub-mm wavelengths, directly traces the radial collision rate and therefore the dynamical activity of the planetesimals.
 
@@
 and lies at 68.8 AU. A horseshoe shaped collection of planetesimals is visible to be corotating with each planet. Nonaxisymmetric gaps are also
-visible at the locations of low degree MMRs with the more massive planet, which are denoted with horizontal dashed lines. Moving inward from the 
-location of the more massive planet (indicated by the solid black line), features associated with the 4:3, 3:2 and 2:1 MMRs are visible. Moving 
-outward, features associated with the 3:4 and 2:3 MMRs are also visible (The 1:2 MMR lies exterior to the planetesimal population).
+visible at the locations of first order MMRs with the more massive planet, which are indicated with arrows.
 

### 2020-07-07 makeFig.py
Clean up MMR labels on figures 2 and 3

@@ -29,9 +29,9 @@ simV = u.AU/simT
 path = 'data/'
 
 # Resonances
-res_label = ['7:2', '10:3', '3:1', '8:3', '5:2', '2:1', '5:3']
-res_p = [2, 3, 1, 3, 2, 1, 3]
-res_q = [5, 7, 2, 4, 3, 1, 2]
+res_label = ['7:2', '3:1', '8:3', '5:2', '2:1', '5:3']
+res_p = [2, 1, 3, 2, 1, 3]
+res_q = [5, 2, 4, 3, 1, 2]
 
 mc = 1
 m_jup = 9.54e-4
@@ -231,14 +231,14 @@ def make_coll_polar_e():
 
 	# Low eccentricity case
 	ecc = ecc_jup/2
-	ridx = 2
+	ridx = 1
 	rw_31 = res_width_jup(ridx, ecc_jup=ecc)*2
 	fecc_31 = e_forced(res_dist[ridx], ecc)
 	outer_peri_31 = (res_dist[ridx]+rw_31)*(1+fecc_31)
 	outer_apo_31 = (res_dist[ridx]+rw_31)*(1-fecc_31)
 	inner_peri_31 = (res_dist[ridx]-rw_31)*(1+fecc_31)
 	inner_apo_31 = (res_dist[ridx]-rw_31)*(1-fecc_31)
-	ridx = 5
+	ridx = 4
 	rw_21 = res_width_jup(ridx, ecc_jup=ecc)*2
 	fecc_21 = e_forced(res_dist[ridx], ecc)
 	outer_peri_21 = (res_dist[ridx]+rw_21)*(1+fecc_21)
@@ -285,14 +285,14 @@ def make_coll_polar_e():
 
 	# Moderate eccentricity case
 	ecc = ecc_jup
-	ridx = 2
+	ridx = 1
 	rw_31 = res_width_jup(ridx, ecc_jup=ecc)*2
 	fecc_31 = e_forced(res_dist[ridx], ecc)
 	outer_peri_31 = (res_dist[ridx]+rw_31)*(1+fecc_31)
 	outer_apo_31 = (res_dist[ridx]+rw_31)*(1-fecc_31)
 	inner_peri_31 = (res_dist[ridx]-rw_31)*(1+fecc_31)
 	inner_apo_31 = (res_dist[ridx]-rw_31)*(1-fecc_31)
-	ridx = 5
+	ridx = 4
 	rw_21 = res_width_jup(ridx, ecc_jup=ecc)*2
[…]

### 2020-07-07 main.tex
Add link to simulated ALMA data

@@
 disk profiles \citep{2015ApJ...808L...3A}.
-% [We should make the sky model available to anyone who wants to use it]
 
-In figure \ref{fig:alma_profiles}, we show the azumithally-averaged radial profiles constructed from the simulated cleaned image from all five 
+In figure \ref{fig:alma_profiles}
+\footnote{The simulated brightness profiles, along with the sky models are available at \url{https://github.com/spencerw/planetesimal_coll_paper}}, we show the 
+azumithally-averaged radial profiles constructed from the simulated cleaned image from all five 
 simulations. In all cases, a bump or a dip feature is clearly visible at the location of the 3:1 and 2:1 MMRs, indicated by the dashed vertical lines. 

### 2020-07-07 main.tex
Add acknowledgements section

@@
 
+\section*{Acknowledgements}
+This work was facilitated through the use of advanced computational, storage and networking infrastructure provided by the Hyak supercomputer system at the 
+University of Washington. We acknowledge the people of the Dkhw’Duw’Absh, the Duwamish Tribe, the Muckleshoot Tribe, and other tribes on whose traditional 
+lands we have performed this work.
+
+\textit{Software:} Astropy \citep{2013A&A...558A..33A}, {\sc CASA} \citep{2007ASPC..376..127M}, {\sc ChaNGa} \citep{2008IEEEpds...ChaNGa, 2015AphCom..2..1}, Matplotlib \citep{2007CSE.....9...90H}, NumPy \citep{2011CSE....13b..22V}, Pandas \citep{mckinney-proc-scipy-2010}, {\sc PYNBODY} \citep{2013ascl.soft05002P}, {\sc sklearn} \citep{scikit-learn},
+
 \bibliography{references}

### 2020-07-07 main.tex
Prepare for submission to MNRAS

@@
-\documentclass[twocolumn]{aastex63}
-\usepackage{natbib}
-%\definecolor{orcidlogocol}{HTML}{A6CE39}
-\bibliographystyle{aasjournal}
+\documentclass[fleqn,usenatbib]{mnras}
+\usepackage{newtxtext,newtxmath}
+\usepackage[T1]{fontenc}
+
+\DeclareRobustCommand{\VAN}[3]{#2}
+\let\VANthebibliography\thebibliography
+\def\thebibliography{\DeclareRobustCommand{\VAN}[3]{##3}\VANthebibliography}
+
+\usepackage{graphicx}
+
+\title[Collision rates of planetesimals]{Collision rates of planetesimals near mean-motion resonances}
+
+\author[S. C. Wallace et al.]{
+Spencer C. Wallace$^{1}$\thanks{E-mail: scw7@uw.edu (SCW)},
+Thomas. R. Quinn$^{1}$,
+Aaron C. Boley$^{2}$
+\\
+$^{1}$Astronomy Department, University of Washington, Seattle, WA 98195\\
+$^{2}$Department of Physics and Astronomy, University of British Columbia, Vancouver BC, Canada
+}
+
+% These dates will be filled out by the publisher
+\date{Accepted XXX. Received YYY; in original form ZZZ}
+
+\pubyear{2020}
 
 \begin{document}
-
-\title{COLLISION RATES OF PLANETESIMALS NEAR MEAN-MOTION RESONANCES}
-
-\author{Spencer C. Wallace}
-\affiliation{Astronomy Department, University of Washington, Seattle, WA 98195}
-
-\author{Thomas R. Quinn}
-\affiliation{Astronomy Department, University of Washington, Seattle, WA 98195}
-
-\author{Aaron C. Boley}
-\affiliation{Department of Physics and Astronomy, University of British Columbia, Vancouver BC, Canada}
+\label{firstpage}
+\pagerange{\pageref{firstpage}--\pageref{lastpage}}
+\maketitle
 
 \begin{abstract}
-In circumstellar disks, collisional grinding of planetesimals produces second-generation dust which can be observed through thermal 
+In circumstellar discs, collisional grinding of planetesimals produces second-generation dust which can be observed through thermal 
 emission. While it remains unclear when second-generation dust first becomes a major component of the total dust content, the presence of 
-such dust and potentially the substructure within it can be used to explore a disk's physical conditions. A perturbing planet has been shown to 
-produce nonaxisymmetric structures, as well as gaps in disks, regardless of the origin of the dust. However, small grains will have very 
+such dust and potentially the substructure within it can be used to explore a disc's physical conditions. A perturbing planet has been shown to 
+produce nonaxisymmetric structures, as well as gaps in discs, regardless of the origin of the dust. However, small grains will have very 
 different dynamics compared with planetesimals when in the presence of gas, and as such, the collisional evolution of planetesimals could 
-create dusty disk structures that would not exist otherwise. Previous studies have shown that morphological differences in the collisional dust 
+create dusty disc structures that would not exist otherwise. Previous studies have shown that morphological differences in the collisional dust 
 corotating with a giant planet can be used to determine whether the planet's eccentricity is large or small. Going further, we investigate the 
@@
 
+\begin{keywords}
+planet-disc interactions -- planets and satellites: formation -- submillimetre: planetary systems -- methods: numerical
+\end{keywords}
+
 \section{Introduction} \label{sec:intro}
 
-Recent observations of circumstellar disks by ALMA have revealed a rich variety of substructure. Features such as gaps and asymmetries 
+Recent observations of circumstellar discs by ALMA have revealed a rich variety of substructure. Features such as gaps and asymmetries 
 \citep{2015ApJ...808L...3A, 2016Sci...353.1519P, PhysRevLett.117.251101, 2016ApJ...820L..40A, 2016Natur.535..258C} in the emission provide 
-diagnostics for the physical processes that drive the evolution of the disks. In many gas-rich systems, these gap features are argued to indicate the 
-presence of a giant planet, either embedded in the disk \citep{2015MNRAS.453L..73D} or orbiting externally, although the details of gas-dust 
+diagnostics for the physical processes that drive the evolution of the discs. In many gas-rich systems, these gap features are argued to indicate the 
+presence of a giant planet, either embedded in the disc \citep{2015MNRAS.453L..73D} or orbiting externally, although the details of gas-dust 
 interactions can have strong effects on the resulting morphologies
@@
 
-Collisions between planetesimals are thought to be the principal source of dust for debris disks. \citep[see][]{2008ARA&A..46..339W}.  Although some 
-amount of primordial dust is likely still present during the early stages of debris disk evolution, ongoing collisions between small bodies will augment 
+Collisions between planetesimals are thought to be the principal source of dust for debris discs. \citep[see][]{2008ARA&A..46..339W}.  Although some 
+amount of primordial dust is likely still present during the early stages of debris disc evolution, ongoing collisions between small bodies will augment 
 this and could be used to trace the underlying dynamical activity of the planetesimals. This process was directly detected when the putative object 
@@
 
-\citet{2013ApJ...777L..31D} showed that collisional dust that is generated near the gap opened by a giant planet in a planetesimal disk should 
+\citet{2013ApJ...777L..31D} showed that collisional dust that is generated near the gap opened by a giant planet in a planetesimal disc should 
 produce a distinct observable marker that could be used to infer the presence of the planet. In a followup study, it was found that morphological 
@@
 To further elucidate this subject, we use the tree based N-body code {\sc ChaNGa}\citep{2008IEEEpds...ChaNGa, 2015AphCom..2..1}  to follow the 
-collisional evolution of a planetesimal disk under the gravitational influence of a Jupiter-sized body. Because particle positions are sorted into a tree 
+collisional evolution of a planetesimal disc under the gravitational influence of a Jupiter-sized body. Because particle positions are sorted into a tree 
 structure, neighbor finding and collision detection can be done quickly and efficiently. This considerably relaxes the constraints on resolution and 
-integration time. With this toolset, we explore the collision rate structure of a planetesimal disk in the vicinity of mean-motion resonances with the planet. In 
+integration time. With this toolset, we explore the collision rate structure of a planetesimal disc in the vicinity of mean-motion resonances with the planet. In 
 particular, we would like to determine (1) whether MMRs leave a detectable signature in the collisionally-generated dust, and (2) whether these 
@@
 This work is organized in the following way: In section \ref{sec:dynamics}, we provide an overview of the relevant dynamics that drive the evolution 
-of a planetesimal disk under the gravitational influence of an external perturber. In section \ref{sec:sims} we provide an overview of the N-body code 
+of a planetesimal disc under the gravitational influence of an external perturber. In section \ref{sec:sims} we provide an overview of the N-body code 
 used and describe the initial conditions chosen for five simulations in which a perturbing giant planet is given various masses 
@@
 
-The most direct and widespread effect that a perturbing giant planet will have on a planetesimal disk is through secular forcing of the planetesimals. This will 
+The most direct and widespread effect that a perturbing giant planet will have on a planetesimal disc is through secular forcing of the planetesimals. This will 
 cause the complex eccentricities of the planetesimals to take on a time-independent 
@@
 aerodynamic gas drag will add an additional free component to the complex eccentricity, which will be randomly oriented. The 
-magnitude of the free eccentricity describes how dynamically hot the planetesimal disk is and sets the random encounter speeds of 
-planetesimals. When the dynamical excitation of the disk is driven by gravitational stirring, the magnitude of the free eccentricity can 
+magnitude of the free eccentricity describes how dynamically hot the planetesimal disc is and sets the random encounter speeds of 
+planetesimals. When the dynamical excitation of the disc is driven by gravitational stirring, the magnitude of the free eccentricity can 
 be described by a Rayleigh distribution \citep{1992Icar...96..107I}.
@@
 
-The net result of this is that MMRs will produce spikes in the semimajor axis-eccentricity distribution of a planetesimal disk. In order to 
+The net result of this is that MMRs will produce spikes in the semimajor axis-eccentricity distribution of a planetesimal disc. In order to 
 preserve the Jacobi energy, equation \ref{eq:tiss} predicts that these spikes will tend to curve away from the perturbing body. This lowers the 
-surface density of the disk near the locations of resonances, while producing a pileup of bodies on eccentric orbits adjacent to the MMR. The 
+surface density of the disc near the locations of resonances, while producing a pileup of bodies on eccentric orbits adjacent to the MMR. The 
 enhanced surface density will increase the collision rate. At the same time, the large eccentricites will either lower the collision rate due to the decreased 
@@
 the escape velocity of the planetesimals. In addition, the MMRs cause the orbits of planetesimals to precess on relatively short 
-timescales, which effectively randomizes their longitudes of perihelion. In a secularly forced disk, there will be an interface between aligned 
+timescales, which effectively randomizes their longitudes of perihelion. In a secularly forced disc, there will be an interface between aligned 
 and randomly oriented orbits at the edge of the resonance. Due to the complicated dynamics that are at play in this region, we turn to a direct 
@@
 
-To follow the dynamical and collisional evolution of a planetesimal disk, we use the highly parallel N-body code {\sc ChaNGa} 
+To follow the dynamical and collisional evolution of a planetesimal disc, we use the highly parallel N-body code {\sc ChaNGa} 
 \footnote{A public version of {\sc ChaNGa} can be downloaded from \url{http://www-hpcc.astro.washington.edu/tools/ChaNGa.html}}. 
@@
 
+\begin{figure*}
+\begin{center}
+    \includegraphics[width=\textwidth]{figures/xy.png}
+    \caption{The positions of the remaining planetesimals at the end of the e1m2 (left), e2m2 (center) and e3m2 (right) simulations. The red dot 
+    indicates the position of the giant planet, and the dashed line points in the direction of the planet's longitude of perihelion. Non-axisymmetric gaps 
+    are apparent near the locations of MMRs. At higher eccentricities, more resonances become visible. At the 2:1 MMR, gap features at $\theta$ = 0 
+    and $\theta = \pi$ follow the giant planet in its orbit.\label{fig:xy}}
+\end{center}
+\end{figure*}
+
 \subsection{Initial Conditions}\label{sec:ics}
@@
 eccentricity (mass) is held at the nominal value. In all cases, the perturbing giant is placed on a 5.2 AU orbit around a 1 $M_{\odot}$ star. The 
-planetesimal disk extends from 2.2 to 3.8 AU, which covers the two most prominent mean-motion resonances with the giant planet, the 2:1 at 3.27 AU 
-and the 3:1 at 2.5 AU. The planetesimal disk follows a minimum-mass solar nebula surface density profile \citep{1981PThPS..70...35H}
+planetesimal disc extends from 2.2 to 3.8 AU, which covers the two most prominent mean-motion resonances with the giant planet, the 2:1 at 3.27 AU 
+and the 3:1 at 2.5 AU. The planetesimal disc follows a minimum-mass solar nebula surface density profile \citep{1981PThPS..70...35H}
 
@@
 \noindent with $\alpha$ = 3/2 and $\Sigma_{0}$ = 10 g cm$^{-2}$. Planetesimals are given a bulk density of 2 g cm$^{-3}$ and a diameter of 
-300 km. This corresponds to a disk containing roughly 500,000 bodies. Each simulation is evolved for 5,000 years, which is about 400 orbits 
+300 km. This corresponds to a disc containing roughly 500,000 bodies. Each simulation is evolved for 5,000 years, which is about 400 orbits 
 of the perturbing planet.
@@
 G M_{\odot}}$. Experimentally, we have found that using a base timestep size with {\sc ChaNGa} of 3\% of an orbital dynamical time
-at the inner edge of the disk keeps the integration symplectic. Although doing so preserves orbital frequencies, the errors associated with
+at the inner edge of the disc keeps the integration symplectic. Although doing so preserves orbital frequencies, the errors associated with
 precession frequencies do not average out to zero. This is especially important given the effects of secular forcing by the planet. To mitigate
 this, we further reduce the base timestep size by a factor of 4 and use $\Delta t$ = 0.0025 yr. Doing so prevents the longitude of perihelia of
-planetesimals at the inner edge of the disk, where this artificial precession is most severe, from drifting by more than the intrinsic spread in $\varpi$ due to the
+planetesimals at the inner edge of the disc, where this artificial precession is most severe, from drifting by more than the intrinsic spread in $\varpi$ due to the
 free eccentricity over the course of our integrations.
@@
 reducing the effectiveness of gravitational focusing, while minimizing the additional computational expense.
-
-\begin{figure*}
-\begin{center}
-    \includegraphics[width=\textwidth]{figures/xy.png}
-    \caption{The positions of the remaining planetesimals at the end of the e1m2 (left), e2m2 (center) and e3m2 (right) simulations. The red dot 
-    indicates the position of the giant planet, and the dashed line points in the direction of the planet's longitude of perihelion. Non-axisymmetric gaps 
-    are apparent near the locations of MMRs. At higher eccentricities, more resonances become visible. At the 2:1 MMR, gap features at $\theta$ = 0 
-    and $\theta = \pi$ follow the giant planet in its orbit.\label{fig:xy}}
-\end{center}
-\end{figure*}
 
@@
 \citet{2016ApJ...818..159T} (figure 3). This structure is also present in the \citet{2017ApJ...850..103B} simulations, although it was not reported at the 
-time (see Appendix \ref{sec:boley_plot}). It is worth noting that \citet{2000Icar..143...45R} started with a completely cold planetesimal disk and a 
+time (see Appendix \ref{sec:boley_plot}). It is worth noting that \citet{2000Icar..143...45R} started with a completely cold planetesimal disc and a 
 Jupiter mass planet on a circular, coplanar
@@
 Another important effect of the resonances is visible in figure \ref{fig:long_ph}, which shows the orientation of the longitude of perihelia of 
-planetesimals in the disk. Inside of the resonances, orbits of planetesimals quickly precess, and their orientations are effectively randomized. An 
+planetesimals in the disc. Inside of the resonances, orbits of planetesimals quickly precess, and their orientations are effectively randomized. An 
 important point to note is that this strong precession effect quickly disappears beyond the boundaries of the resonance. This turns out to be 
@@
 We attribute the production of a bump or a dip at certain semi-major axes to changes in the gravitational focusing factor during two-body encounters. 
-Closer to the star, the planetesimal disk starts off dynamically colder. Here, additional heating from the resonance acts to suppress the gravitational 
+Closer to the star, the planetesimal disc starts off dynamically colder. Here, additional heating from the resonance acts to suppress the gravitational 
 focusing cross section, which reduces the collision rate from its
-non-perturbed value. Further out in the disk, where the unperturbed
+non-perturbed value. Further out in the disc, where the unperturbed
 encounter velocity is higher, the gravitational focusing cross section
@@
 resonances. Although this could potentially serve as a useful
-diagnostic of the planetesimal size in a disk (because the mutual
+diagnostic of the planetesimal size in a disc (because the mutual
 escape velocity sets how dynamically hot the bodies can get before
@@
     \includegraphics[width=0.5\textwidth]{figures/coll_hist_a.png}
-    \caption{A PDF of the collision rate in each disk as a function of semimajor axis, generated using a KDE with a Gaussian kernel with a FWHM of 0.02 AU.
+    \caption{A PDF of the collision rate in each disc as a function of semimajor axis, generated using a KDE with a Gaussian kernel with a FWHM of 0.02 AU.
 In semimajor axis space, prominent features appear near the 3:1 and 2:1 MMRs.
@@
 drift direction changing sign across the location of exact resonance. The net result of this is that bodies just outside of the resonance experience a torque from 
-the planet that temporarily drives their pericenters toward the current orbital position of the planet. After the encounter ends, differential rotation of the disk 
+the planet that temporarily drives their pericenters toward the current orbital position of the planet. After the encounter ends, differential rotation of the disc 
 slowly destroys the configuration over part of an orbit. As the planet passes by, adjacent planetesimals near the resonance edges temporarily align 
@@
 planet is on a circular orbit, this structure is still present (see figure 3 of \citet{2016ApJ...818..159T} and Appendix \ref{sec:boley_plot}). The only 
-connection between the structure of the gaps in the disk and the path of a resonant particle in the corotating frame is that both phenomena produce the 
+connection between the structure of the gaps in the disc and the path of a resonant particle in the corotating frame is that both phenomena produce the 
 same symmetries, which depend on the particular MMR.
@@
 The dynamical effects of varying the mass of the planet are somewhat simpler, in that doing so does not affect the forced eccentricity of the 
-planetesimal disk. Instead, only the width of the resonances changes. The width of a first order resonance scales with $m$ (see equation 
+planetesimal disc. Instead, only the width of the resonances changes. The width of a first order resonance scales with $m$ (see equation 
 \ref{eq:res_so}), while the leading order terms in the resonant part of the disturbing function, which set the strength of the resonance, also scale as 
@@
 we create a sky model for simulated ALMA observations as follows. First, we use the radially-averaged collision profile from each simulation (see figures 
-\ref{fig:coll_polar_e} and \ref{fig:coll_polar_m}) as the template for an azimuthally symmetric disk. We then scale the size of each profile by a factor of 
+\ref{fig:coll_polar_e} and \ref{fig:coll_polar_m}) as the template for an azimuthally symmetric disc. We then scale the size of each profile by a factor of 
 ten, which places the perturbing planet at 52 au. This scaling is permitted by the dynamics (both the resonance widths and the forced eccentricities 
-are scale-free) and makes the disk comparable in size to the many disks that have now been observed by ALMA \citep{2018ApJ...869L..42H}. The 
-angular size scale is then set by envisaging a face-on disk at a distance of 100 pc.
+are scale-free) and makes the disc comparable in size to the many discs that have now been observed by ALMA \citep{2018ApJ...869L..42H}. The 
+angular size scale is then set by envisaging a face-on disc at a distance of 100 pc.
 
@@
 approximately 2 mas. In doing so, we choose to make the intensity proportional to the collision frequency (i.e., the dust) because it is the most 
-straightforward case. Many different parameterizations are possible, depending on optical depth, grain size, disk temperature, etc., but we will avoid 
-such complications here. We normalize the intensity by setting the total disk flux density to be 100 mJy at about 350 GHz.
+straightforward case. Many different parameterizations are possible, depending on optical depth, grain size, disc temperature, etc., but we will avoid 
+such complications here. We normalize the intensity by setting the total disc flux density to be 100 mJy at about 350 GHz.
 
-The simulated observations are performed using the {\sc simobserve} task in {\sc CASA} \citep{2007ASPC..376..127M}.  The disk is given an 
+The simulated observations are performed using the {\sc simobserve} task in {\sc CASA} \citep{2007ASPC..376..127M}.  The disc is given an 
 $\rm RA = 11^{\rm h} 01^{\rm m} 52^{\rm s}$ and a $\delta = -34^\circ 42\arcmin 17\arcsec$ (i.e., the J2000 coordinates for TW Hydrae) and is 
-``observed'' through transit on March 20, 2020. We observe the disk using configurations 8, 9, and 10 at 350 GHz (cycle 6 antenna file), spending six 
+``observed'' through transit on March 20, 2020. We observe the disc using configurations 8, 9, and 10 at 350 GHz (cycle 6 antenna file), spending six 
 hours on-source in each configuration\footnote{We have imagined that the TAC really likes us.}.  The visibilities are corrupted with thermal noise, 
@@
 cleaned image and in the corresponding radial profile.  Moreover, the features are qualitatively similar to the bright rings and dark gaps seen in actual 
-disk profiles \citep{2015ApJ...808L...3A}.
+disc profiles \citep{2015ApJ...808L...3A}.
 
@@
 Top: The sky model based on the radial collision distribution.
-The size of the disk has been scaled by a factor of 10 and placed at  a distance of 100 pc.
+The size of the disc has been scaled by a factor of 10 and placed at  a distance of 100 pc.
 Bottom: The cleaned image using combined observations in configurations 8, 9, and 10.
@@
 The vertical dashed lines indicate the locations of the 3:1 and 2:1 resonances.
-As in figure \ref{fig:alma_sim_obs}, the size scale of the disk has been expanded by a factor of 10 and then placed at a distance of 100 pc.\label{fig:alma_profiles}}
+As in figure \ref{fig:alma_sim_obs}, the size scale of the disc has been expanded by a factor of 10 and then placed at a distance of 100 pc.\label{fig:alma_profiles}}
 \end{figure*}
@@
 Because the strength\footnote{More specifically, the strength of the resonant term in the disturbing potential} of the 2:1 resonance scales with $e_{g}$ and  $m_{g}$, a sufficiently low mass and low eccentricity planet will not create
-enough of a perturbation in the planetesimal disk to produce a detectable bump or dip feature. The colored contours in figure \ref{fig:bump_dip_diag} 
+enough of a perturbation in the planetesimal disc to produce a detectable bump or dip feature. The colored contours in figure \ref{fig:bump_dip_diag} 
 indicate the relative strength of the resonance as these quantities are varied. Although the resonance strength is equally sensitive to changes in 
@@
 In order to actually identify the 2:1 MMR in the dust emission, at least one other resonance must be visible. Assuming the gravitational field in the 
-disk is near-Keplerian, the distance ratios between two features can be used to determine period ratios, which can be used to confirm whether the 
+disc is near-Keplerian, the distance ratios between two features can be used to determine period ratios, which can be used to confirm whether the 
 features seen are indeed resonances. Although the 3:1 MMR does not appear to follow the simple bump vs dip dichotomy described above, its 
@@
 In this work, we have shown that mean-motion resonances with a perturbing planet produce significant local variations in the collision rate of a 
-planetesimal disk. In contrast to \citet{2000Icar..143...45R}, we find that the more prominent interior MMRs, including the 2:1, 3:1 and 5:3, all 
+planetesimal disc. In contrast to \citet{2000Icar..143...45R}, we find that the more prominent interior MMRs, including the 2:1, 3:1 and 5:3, all 
 produce structure in the collision profile as a function of semimajor axis. Furthermore, we find that a series of distinctly different features appear 
-when collisions are ordered by cylindrical distance from the central star. If enough gas from the protoplanetary disk is still present, dust generated 
+when collisions are ordered by cylindrical distance from the central star. If enough gas from the protoplanetary disc is still present, dust generated 
 from planetesimal-planetesimal collisions will immediately fall onto a circular orbit. In this case, the radial dust emission profile, 
@@
 
-In line with \citet{2017ApJ...850..103B}, the results of this work suggest that, in planet forming disks, the observed dust structure should not be 
+In line with \citet{2017ApJ...850..103B}, the results of this work suggest that, in planet forming discs, the observed dust structure should not be 
 interpreted as simply the result of primordial dust that is perturbed by the planets and gas. Instead, some morphological features could be the product 
 of collisional dynamics between larger bodies. Within the confines of the simulations presented here, we have shown that this second-generation dust 
-can give rise to significant features in the dust emission profile. For this reason, we emphasize that planet-forming disks should be thought of as 
-existing along an evolutionary continuum, with the youngest disks being dominated by primordial dust and gas and the most evolved disks being 
+can give rise to significant features in the dust emission profile. For this reason, we emphasize that planet-forming discs should be thought of as 
+existing along an evolutionary continuum, with the youngest discs being dominated by primordial dust and gas and the most evolved discs being 
 comprised of mainly collisionally generated dust.
@@
 variations in the dust emission near MMRs is much more subtle and requires much higher spatial resolution and sensitivity. As we have shown, the 
-bump vs dip feature near the 2:1 MMR is marginally detectable with ALMA for the nearest protoplanetary disks. Another complicating factor is that 
-the inner $\sim$ 10 AU of most protoplanetary disks are optically thick in the sub-mm. The solution to this problem is to instead observe at longer 
-wavelengths where the inner disk is optically thin. This comes at the expense of much poorer resolution. However, future radio facilities like the NG-
-VLA are expected to achieve sub-AU resolution for nearby planet-forming disks \citep{2018ASPC..517..147R}. In the more near-term, techniques 
+bump vs dip feature near the 2:1 MMR is marginally detectable with ALMA for the nearest protoplanetary discs. Another complicating factor is that 
+the inner $\sim$ 10 AU of most protoplanetary discs are optically thick in the sub-mm. The solution to this problem is to instead observe at longer 
+wavelengths where the inner disc is optically thin. This comes at the expense of much poorer resolution. However, future radio facilities like the NG-
+VLA are expected to achieve sub-AU resolution for nearby planet-forming discs \citep{2018ASPC..517..147R}. In the more near-term, techniques 
 like Gaussian process fitting present a promising way to recover substructure at sub-beam resolution \citep{2020arXiv200507709J}.
@@
 
+\bibliographystyle{mnras}
 \bibliography{references}
 
-\clearpage
+\appendix
+\section{Nonaxisymmetric Structure in Boley 2017}\label{sec:boley_plot}
 
-\setcounter{secnumdepth}{0}
-\section{Appendix: Nonaxisymmetric Structure in Boley 2017}\label{sec:boley_plot}
+\begin{figure*}
+    \includegraphics[width=\textwidth]{figures/boley_rtheta.png}
+    \caption{Positions of planetesimals at the end of the simulation presented in \citet{2017ApJ...850..103B} in polar coordinates.
+The dashed line marks the location of a 50 $M_{\earth}$ planet embedded in the disc.
+First order MMRs with the planet are indicated with arrows.
+A second planet is also present at 32.3 AU, although it is not massive enough to induce any significant structure in the disc near associated resonances.\label{fig:boley_rtheta}}
+\end{figure*}
 
@@
 \ref{fig:boley_rtheta}, we show the planetesimal positions in polar, rather than Cartesian coordinates as originally presented in the paper. Two planets 
-on circular orbits are present here. The first has mass of 17 $M_{\bigoplus}$ and lies at 32.3 AU. The second planet has a mass of 50 $M_{\bigoplus}$ 
+on circular orbits are present here. The first has mass of 17 $M_{\earth}$ and lies at 32.3 AU. The second planet has a mass of 50 $M_{\earth}$ 
 and lies at 68.8 AU. A horseshoe shaped collection of planetesimals is visible to be corotating with each planet. Nonaxisymmetric gaps are also
@@
 Similar to figure \ref{fig:coll_polar_e}, a gap is present at the same orbital phase as the planet at the 2:1 MMR, along with a second gap on
-the opposite side of the disk. Gaps near the 4:3 and 3:2 MMRs are also present in phase with the planet, although the number and spacing between 
+the opposite side of the disc. Gaps near the 4:3 and 3:2 MMRs are also present in phase with the planet, although the number and spacing between 
 additional gaps appears to be different for each resonance. In addition, the gap structure associated with the exterior MMRs appears markedly
@@
 
-\begin{figure*}
-    \includegraphics[width=\textwidth]{figures/boley_rtheta.png}
-    \caption{Positions of planetesimals at the end of the simulation presented in \citet{2017ApJ...850..103B} in polar coordinates.
-The dashed line marks the location of a 50 $M_{\bigoplus}$ planet embedded in the disk.
-First order MMRs with the planet are indicated with arrows.
-A second planet is also present at 32.3 AU, although it is not massive enough to induce any significant structure in the disk near associated resonances.\label{fig:boley_rtheta}}
-\end{figure*}
-
+\bsp	% typesetting comment
+\label{lastpage}
 \end{document}

### 2020-07-08 main.tex
Move GitHub hyperlink to Data Availabilty section, per new MNRAS requirements

@@
 
-In figure \ref{fig:alma_profiles}
-\footnote{The simulated brightness profiles, along with the sky models are available at \url{https://github.com/spencerw/planetesimal_coll_paper}}, we show the 
+In figure \ref{fig:alma_profiles}, we show the 
 azumithally-averaged radial profiles constructed from the simulated cleaned image from all five 
@@
 
-\textit{Software:} Astropy \citep{2013A&A...558A..33A}, {\sc CASA} \citep{2007ASPC..376..127M}, {\sc ChaNGa} \citep{2008IEEEpds...ChaNGa, 2015AphCom..2..1}, Matplotlib \citep{2007CSE.....9...90H}, NumPy \citep{2011CSE....13b..22V}, Pandas \citep{mckinney-proc-scipy-2010}, {\sc PYNBODY} \citep{2013ascl.soft05002P}, {\sc sklearn} \citep{scikit-learn},
+\textit{Software:} Astropy \citep{2013A&A...558A..33A}, {\sc CASA} \citep{2007ASPC..376..127M}, {\sc ChaNGa} \citep{2008IEEEpds...ChaNGa, 2015AphCom..2..1}, Matplotlib \citep{2007CSE.....9...90H}, NumPy \citep{2011CSE....13b..22V}, Pandas \citep{mckinney-proc-scipy-2010}, {\sc PYNBODY} \citep{2013ascl.soft05002P}, {\sc sklearn} \citep{scikit-learn}
+
+\section*{Data Availability}
+The data presented in this article are available on our GitHub repository, at \url{https://github.com/spencerw/planetesimal_coll_paper}.
 

### 2020-07-09 makeFig.py
Clean up unused functions in makeFig.py

@@ -573,77 +573,6 @@ def bump_dip_diag():
 	file_str = 'figures/bump_dip_diag.' + fmt
 	if not clobber and os.path.exists(file_str):
 		return
-
-	res_idx = 1
-	ngrid = 50
-	e_jup_vals = np.logspace(-3.5, np.log10(0.5), ngrid)
-	m_jup_vals = np.logspace(-1, 1, ngrid)
-
-	is_bump_21 = np.zeros((ngrid, ngrid))
-	for idx in range(ngrid):
-	    for idx1 in range(ngrid):
-	        a_res = res_dist[res_idx]
-	        rw = res_width_jup(res_idx, ecc_jup=e_jup_vals[idx], \
-	                              m_jup=(m_jup_vals[idx1]*u.M_jup).to(u.M_sun).value)*2
-	        fecc = e_forced(a_res, e_jup_vals[idx])
-	        apo_inner = (a_res - rw)*(1 + fecc)
-	        peri_outer = (a_res + rw)*(1 - fecc)
-	        
-	        if (apo_inner - peri_outer)/rw > 0:
-	            is_bump_21[idx][idx1] = 1.0
-	            
-	res_idx = 4
-	e_jup_vals = np.logspace(-3.5, np.log10(0.5), ngrid)
-	m_jup_vals = np.logspace(-1, 1, ngrid)
-
-	is_bump_31 = np.zeros((ngrid, ngrid))
-	for idx in range(ngrid):
-	    for idx1 in range(ngrid):
-	        a_res = res_dist[res_idx]
-	        rw = res_width_jup(res_idx, ecc_jup=e_jup_vals[idx], \
-	                              m_jup=(m_jup_vals[idx1]*u.M_jup).to(u.M_sun).value)*2
-	        fecc = e_forced(a_res, e_jup_vals[idx])
-	        apo_inner = (a_res - rw)*(1 + fecc)
-	        peri_outer = (a_res + rw)*(1 - fecc)
-	        
-	        if (apo_inner - peri_outer)/rw > 0:
-	            is_bump_31[idx][idx1] = 1.0
-
-	fig, axes = plt.subplots(figsize=(5, 5))
[…]

### 2020-07-09 makeFig.py
Add instructions for downloading simulation data

@@ -114,36 +114,35 @@ def plot_res(axis, res=-1, vertical=True, show_widths=False, all=False):
 					axis.hlines(res_dist[val] - width, xmin, xmax, linestyle='-', lw=0.5)
 					axis.hlines(res_dist[val] + width, xmin, xmax, linestyle='-', lw=0.5)
 # Snapshots
-s_c_files = np.array([path + 'hkshiftfullJupCirc/hkshiftfullJupCirc.ic']+ \
-	                  ns.natsorted(gl.glob(path + 'hkshiftfullJupCirc/*.[0-9]*[0-9]')))
-s0_c = pb.load(s_c_files[0])
-s_e_files = np.array([path + 'hkshiftfull/hkshiftfull.ic']+ \
-	                  ns.natsorted(gl.glob(path + 'hkshiftfull/*.[0-9]*[0-9]')))
+s_e_files = np.array([path + 'e2m2/e2m2.ic.800000']+ \
+	                  ns.natsorted(gl.glob(path + 'e2m2/*.[0-9]*[0-9]')))
 s0_e = pb.load(s_e_files[0])
-s_c, s_e = pb.load(s_c_files[-1]), pb.load(s_e_files[-2])
+s_e = pb.load(s_e_files[-2])
 print(s_e_files[-2])
-pl_c, pl_e = ko.orb_params(s_c), ko.orb_params(s_e)
+pl_e = ko.orb_params(s_e)
 
-s_m1_files = np.array([path + 'm1/m1.ic']+ \
-	                  ns.natsorted(gl.glob(path + 'm1/m1_coll.[0-9]*[0-9]')))
+s_m1_files = np.array([path + 'e2m1/e2m1.ic.800000']+ \
+	                  ns.natsorted(gl.glob(path + 'e2m1/e2m1.[0-9]*[0-9]')))
 s0_m1 = pb.load(s_m1_files[0])
-s_m2_files = np.array([path + 'm2/m2.ic']+ \
-	                  ns.natsorted(gl.glob(path + 'm2/m2_coll.[0-9]*[0-9]')))
+s_m2_files = np.array([path + 'e2m3/e2m3.ic.800000']+ \
+	                  ns.natsorted(gl.glob(path + 'e2m3/e2m3.[0-9]*[0-9]')))
 s0_m2 = pb.load(s_m2_files[0])
 s_m1, s_m2 = pb.load(s_m1_files[-1]), pb.load(s_m2_files[-1])
[…]

### 2020-10-26 refereeResponse.txt
Start addressing referee comments

1) It is not clear how collisions were treated. Wallace et al. point to other papers that describe the implementations of the collisional algorithms. Although I agree they should not attempt to describe all details of the code here, it would be of major help to add more text describing how they deal with collisions.
1.1) What is the collisional scaling used?
1.2) What material is assumed for the colliding planetesimals?
1.3) How do you deal with size frequency distribution (collisional cascade) resultant from collisions?
1.4) What is the dust size considered in this work?

I would say all these matter a lot once 300 km planetesimals will likely not be instantaneously pulverized to dust-size when they collide. Thus it is of major importance for the understanding of this work, to know precisely how collisions were treated. If, for instance, authors did not consider any fragmentation, and only tracked collisions to determine where dust would form, I would say this should be put as a caveat.

The reason why I'm asking this to be a caveat is because in this case the authors' results would not necessarily be representing the dust profile, but rather the planetesimal collisional profile, and so the upper limit of dust generation at a given location. This makes a difference regarding the applicability of this work, once the expected real signals from the bumps and dips would be much smaller, and so particularly undetectable. The conclusion's by Wallace et al., potentially based on a local upper limit of dust generation, already points towards an expected faint signal in real observation. Therefore, if the real expected signal end up being even fainter, would this work results be applicable at all, or would them be simply negative results? I am afraid that if the results would be simply negative, they may not be important. I mean, why should we care if we will not be able to easily see those bump/dip features? In this case we would not be able to say anything about the mass and eccentricity of the potential perturbing planet. Therefore, what is the meaning of constraining something that it is unmeasurable?

I would try to help the authors and turn this into a positive light, even if the results turn to be negative. One could eventually say that, once observational capabilities improve, having a constrained measurement would help to quickly interpret images in the future. I don't know how likely is this, but with a proper caveat, it would be acceptable, eventually.

2) I am very concerned by the fact the authors neglected migration on small particles due to aerodynamic drag. 300 km planetesimals will not break down to dust directly (of course some dust will be created during the 300 km planetesimal's collisions, but that would be a very small fraction of mass). The 300 km planetesimals (depending on material) will more likely break into a collection of smaller km-size objects. These smaller size objects will then overpopulate the regions where they were created, thus enhancing collision rates among them. Collisions that continue to happen among these smaller objets will eventually turn them in to a very large swarm of even smaller m- to km-size objects. Ultimately, this last generation of collisionally evolved planetesimals will become dust (then my question about how and if Wallace et al. considered collisional cascade in their simulations).

The problem of neglecting aerodynamic drag becomes then a bigger problem because, as it is very well known, small m- to km-sized objects feel strong headwind and thus can drift very fast Sunwards (e.g. Weidenschilling & Davis 1985; Patterson 1987; Beauge & Ferraz-Mello 1993; Malhotra 1993; Gomes 1995a,b; Jiang & Yeh 2004; Batigyn & Laughlin 2015; Storch & Batygin 2019; Deienno et al. 2020). Therefore, dust created by these large moving swarms could leave a signature that is far different than that when assuming dust would be generated in the location of the 300 km planetesimal collisions (eventually changing, or even destroying, the bump/dip signatures; despite the fact that dust would couple to the gas almost instantaneously, once created). This is why I previously said authors may be tracking the planetesimal collisional profile and the upper limit of dust generation at those locations in their simulations, but not necessarily the dust profile.

I would suggest that the authors investigate and say explicitly in the text what is the expected relation between collisional timescale and drift timescale for m- to km-sized (1 m - 1 km) particles.

They should discuss:
2.1) If drift timescale of 1 m- to 1 km-sized objects is larger than their collision timescale.
In this case, collisions would happen before planetesimals would drift. Then the results should hold true.
2.2) If drift timescale of 1 m- to 1 km-sized objects is smaller than their collision timescale.
In this case, planetesimals would tend to drift faster than they can collisionally evolve. However, if their drift timescale is still larger than 5000 yr (integration time), then maybe this could be a minor issue. But a caveat would still be necessary as the large swarm of small planetesimals would likely continue collisionally evolving elsewhere (far from the mean motion resonances; MMRs, thus potentially changing the bump/dip signatures).
2.3) If drift timescale is smaller than 5000 yr and also smaller than collisional timescale.
In this case, this is a major issue! Planetesimals would quickly fall into the star, leaving minor dust signature, or a continue dust signal throughout their migration path, thus certainly no bumps nor dips would be observed.

Regardless the situation, this should be clearly discussed in the text.

    Measure drift timescale across resonance
    Compare with collision timescale of 1m bodies
        Depends only on surface density of bodies (assume all mass in 1m bodies for simplicity)
        Drift and collision timescales are approx comparable
        Low density planetesimals, less gas or cooler gas all alleviate this

3) Wallace et al. mostly studied collisions that happen around MMRs. Thus, my point 2) above may become a problem for this as well. The pioneering work by Weidenschilling & Davis (1985) suggested small drifting particles could get captured by external MMRs with large planets. However, by that time the authors already pointed out that collisions would likely knock particles out of MMRs. More recently, Deienno et al. (2020) were finally able to confirm the predictions by Weidenschilling & Davis (1985) that collisions prevent small m- to km-sized particles to remain in MMRs (or near them) when gas is still around in the protoplanetary disk. Thus, I would say that, because Wallace et al. is mostly studying collisions within and near MMRs, in a protoplanetary disk (when gas should be around), adding aerodynamic drag on small size particles can be of a major influence, and eventually modifying all conclusions, specially because interior MMRs (those studied in this work) are largely inefficient in capturing any drifting small planetesimal (Weidenschilling & Davis 1985; Beauge & Ferraz-Mello 1993; Malhotra 1993; Gomes 1995a,b).

Summarizing, if interior MMRs can't capture small drifting planetesimals (or even in the case where capture would eventually occur), aerodynamic drag plus collisional evolution would not leave any object in MMRs. Therefore, the bumps and dips observed in this work would eventually not exist.

Not that I want to sound like a broken record, but in my opinion, without considering small planetesimals drifting due to gas drag, the figures presented in this work represent a planetesimal collisional profile, but not necessarily a dust profile. Again, large amounts of dust will not be directly generated by collisions among 300 km planetesimals, but rather by collisions among a larger swarm of m- to km-sized objects. The latter are strongly affected by the gas and don't strongly interact with interior MMRs, unless the planet in migrating Sunwards and capturing them (not the case of the present work).

    So long as the concerns in 2) are satisfied, this is not an issue

4) Wallace et al. performed each simulation for 5000 years. In the introduction, authors claim all works to date are severely limited in simulation time. Well, is 5000 years different than that? Deienno et al. (2020) performed N-body simulations of collisionaly evolving planetesimals (using statistical routines and tracer particles) with N of order O^10+ for 100,000 yr! I understand the codes used and the purpose of the two works were very different, so as the simulation setups. However, I don't understand why 5000 yr is not a severely limited time either. Protoplanetary disks can live much longer than that (Myr timescales). Why 400 orbits is enough? Wouldn't a longer simulation time change all results? I mean, the way it is, I understand that the disk signatures would be those reflecting a 5000 yr evolution, which is basically the observational instant considering how long a disk could live. However, if a 10,000 yr or 100,000 yr evolution would change the dust signatures (especially if considering aerodynamic drag), how applicable are the conclusions in this work? See that 10,000 yr or 100,000 yr are also short periods compared to the disk lifetime. Could you, please, add discussion regarding simulation time, as well as, clearly define what is a short and a long time (and why)? For me 5000 yr is, in principle, too short.

    We were specifically referring to direct N-body simulations (not statistical routines or studies using tracer particles)
    This is the first direct N-body work that resolves the libration timescale of the resonances
    We expect that a much longer integration time will yield the same result, because 5,000 years is longer than all of the relevant timescales relating to dynamics

I'm very concerned about all these 4 points and would like that the authors pay careful attention, as well as, devote a thorough discuss related in the revised text.

The question of applicability:

If I understood the applicability of this work would follow the steps:
1) Once a bump or dip is observed in the dust emission signature of a disk, one would need to assume that this bump or dip reflects the position of the interior 2:1 MMR with a planet.
2) Thus, one would need to look for another dip or bump near what would be the interior 3:1 MMR with that supposed planet.
3) Only then one would be able to guess on the eccentricity and mass of the assumed perturber.

I think this should be clearly said in the conclusions, as well as this idea should be introduced somewhere upfront in the manuscript (maybe in the abstract or introduction). I would not leave to the reader to reach this conclusion. Readers can easily interpret things wrong (especially nowadays where we have so much things to read and we usually read them fast). Did I have the right interpretation or are the author suggesting something different in regards to applicability?

    Exactly. Todo: add a clear outline of this in the conclusions

General points (not in order of importance, but as they appear in the text):

I will use the following nomenclature:
- page 2, left(right) column, third paragraph, line 36 as pg.2 l(r)col. P.3 l.36 (line number reflects the number on the left side of a given page and not the paragraph line.)

1) pg.1 lcol P.1 l.47 - "or orbiting externally" - why not considering the planets orbiting internally too? External MMRs are important and can have a much larger effect in debris disk.

    This is absolutely true. The initial conditions for this work were meant to be compared with simulation B of Richardson et al. 2000, which only focused on the internal MMRs. The phrase 'orbiting externally' was changed to 'orbiting adjacent to'.

2) pg.1 lcol P.1 l.49-51 - "In gas-poor/debris systems, a giant planet perturber can also influence the structure of the dust continuum emission." - Why discussing debris disk if you will only account for the gaseous phase? This confuses the reader.

    The planetesimal dynamics presented in the work are equally applicable to gas rich and gas poor systems. However, the orbital structure of the dust and the constraints it would place on the properties of the giant planet are much less clear. We have reframed this paper draft to make the measurement of the perturbing planet's properties less of a central point and therefore discussing debris disks in the introduction is relevant.

3) pg.1 rcol P.2 l.44-47 - "Dobinson et al. (2013) showed that collisional dust that... to infer the presence of the planet." - In a debris disk or in a gas disk?

    The Dobinson et al. 2013 work modeled the inner gas poor region of a transition disk. The term 'planetesimal disk' in our introdution was changed to 'inner part of a transition disk'.

4) pg.2 lcol P.1 l.44-47 - "Unfortunately, collision detection in an N-body simulation is extremely computationally expensive. So far, studies of planetesimal dynamics near MMRs have involved either collisionless test particles (Boley 2017; Tabeshian &Wiegert 2016, 2018) or severely limited integration times (Richardson et al. 2000). To further elucidate this subject, we use the tree based N-body" - But see Deienno et al. (2020).

    Deienno et al. 2020 makes use of tracer particles, which is not the case with the other studies we cite here. Had we used coarser resolution and taken advantage of tracer particles in this work, the structure seen at the edges of the resonances in figures 6 and 7, which is critical to generating the features seen in the collision profiles, would likely become washed out. The text in the above sentence in the introduction has been changed to clarify that we are only referring to cases where the planetesimals are directly resolved.

5) A general comment - The introduction is confusing. It is clear from the abstract that the work will consider only the gas disk phase of a protoplanetary disk. However, because the introduction discuss a lot of debris disk, it is not clear whether debris disks will be considered. I would suggest focusing the discussion on protoplanetary disk. This way it would be clear authors will work during the gas phase.

    TODO: I think the better thing to do is reframe the abstract. Highlight more about the dynamics, and leave the stuff about gas and the dust structure to the end.

6) Another general comment, now regarding section 2. - A much more relevant dynamics not discussed at all is due to aerodynamic gas-drag on planetesimals (especially the smaller ones). Also, collision rates are not discussed at all !

   TODO: Might be good to add a section discussing gas drag here. Also - I had an analytic derivation of collision rates in an earlier draft - I guess I'll add it back in.

7) Reference - Murray & Dermott (2000) - I think Murray & Dermott (1999) is a better reference (at least more commonly used).
\bibitem[\protect\citeauthoryear{Murray \& Dermott}{1999}]{1999ssd..book.....M} Murray C.~D., Dermott S.~F., 1999, ssd..book

    Never noticed this before! All Murray & Dermott references have been changed to the 1999 version.

8) pg.2 rcol P.1 l.8-9 - "... along with aerodynamic gas drag will..." - Even at this point is still not clear from the text if gas will be considered. Please, clarify the text.3

    Add clarification: although we don't model gas drag here, the ICs need to start in eqilibrium. The viscous stirring time is much longer than any of the other relevant timescales resolved in the simulation, so it is sufficient for us to calculate what <e^2>^{1/2} would be if there were gas around.

9) A general comment with respect to section 2.2 - It looks like there are typos in some of the equations. I would also suggest that, every time that equations from other works are quoted, please, say chapter, page, and eq #. This helps the reader to look after, if a bit more of background is needed. Finally, I don't understand the importance of this section. It ends as: "Due to the complicated dynamics that are at play in this region, we turn to a direct N-body treatment to better understand how the collision rate varies in the vicinity of a MMR.". When I reached this point I asked myself: Will this section be used for something or is it here simply to say that the dynamics are complicated enough to be treated analytically, thus needing numerical analysis? I would suggest to shorten this section. Another suggestion, consider moving it to an appendix (once equations are revised).

    Be sure to add chapter, page number and eq number after all M+D equations. The main purpose of this section is to explain how we calculated resonances widths that were used in the later parts of the paper. Go back through and make sure each of the equations presented is referenced later in the paper. Remove ones that arent

I am not saying equations are wrong, but please, revise all equations to make sure they are correct and consistent, and add explanation when clarification is needed.

10) Equation (5) - should'n this equation have -q instead of -(2p+q) in the third term and -p instead of -q in the second term? See for example Murray & Dermott (1999, chap 8, eq. 8.8), or Beaugé & Ferraz-Mello (1993), or Malhotra (1993), or Gomes (1995)...
From Murray & Dermott (1999, Chap 6 and 8), one of the general forms of the resonant angle can be phi = j1*lamb' + j2*lamb + j4*varpi, where j1 = p+q, j2 = -p and j4 = -q. So why using j2 = -q and j4 = -(2p+q) instead?
The authors should explicitly say, and explain why these choices were made.

    Looks like this was a typo that carried through a few equations. Fortunately, this same mistake was not made when doing any calculations for the paper (all equations used in our analysis are consistent with the referee's convention)

11) Equation (6) - Assuming j4 = 2p+q

    See 10

12) pg.3 lcol P.1 l.11 - "... table 8.1)..." - third row, with j = p+q (in Murray's book).

    To add

13) Equation (9) - Shouldn't this be fd(alfa) = 1/2 [ -2j -alphaD ] b1/2^j (minus, not plus)

    Minus sign missing in front of both terms

14) pg.3 lcol P.2 l.21 - "... table 8.1)..." - first row in Murray's book

    To add

15) pg.3 lcol P.2 l.28 - "... equation 8.76)." - with j2 = p.

    To add

16) pg.3 lcol P.4 l.34-35 - "The net result of this is that MMRs will produce spikes in the semimajor axis-eccentricity distribution of a planetesimal disc." - This is true when migration due to aerodynamic drag is not considered, or for large planetesimals that don't feel strong headwind. Would this still be true for small planetesimals that are drifting inwards? That would largely depend on the relation strength of the resonance vs drifting timescale (resonance crossing time).

    If t_drift >> t_librate, then still holds true. The big question is what is t_librate for sthe small bodies. This is set by their eccentricity.

17) A general note regarding section 3.1 - The code should be described with more details. This is a tree code primarily developed to work on cosmology simulations, thus not commonly applied for astronomical models. What is need to translate a cosmology code to astronomy? What are the differences in potential? I have many questions and a general reader would have them too. In my opinion, simply saying the code works well in half million processors and that it calculates gravitational forces, then redirecting to Jetley et al. (2008) is too superficial. See I am not asking to give all details, as this is an already published code. But having a better description of the portions of the code that are relevant to this work would be important. Also, I think it is crucial that Wallace et al. describe with more details how the code deals with collisions, and all the assumptions made, as well as all the consequences of it. Again, I understand the authors have a full description of the collisional module in Wallace & Quinn (2019), but having a summary of the main relevant features here would not hurt. On the opposite, it would greatly help the reader and the understanding of the work. Besides, including more details would not be a big task, and should also not compromise the length of the work (especially if Sect 2.2 goes mostly to an appendix). Please, I beg for more detail in this section.

    Not sure how to address this? Does the referee mean 'planet formation' when referring to astronomy? Could we just add some citations to other papers that use ChaNGa for planet stuff?

18) pg.3 rcol P.2 l.29-32 - "In the other four cases, the mass (eccentricity) is increased or decreased by a factor of two, while the eccentricity (mass) is held at the nominal value." - This reads awkward. Why not simply say that in other cases mass and/or eccentricity is increased or decreased by a factor of 2?

    We can certainly do this. I wrote this before adding table 1, which makes it clear.

19) pg.3 rcol P.2 l.33 - "... 5.2 AU orbit..." - 1) Why not closer distances? 2) AU -> au (here and elsewhere).

    Maybe we should do more to emphazise that this setup was motivated by a Jupiter - asteroid belt setup. Be sure to change AU to au (this is what the editor asked for in the last MNRAS paper)

20) pg.3 rcol P.2 l.34 - "The planetesimal disc extends from 2.2 to 3.8 AU..." - Why not consider the outer disk too? External resonances can be very strong and capture is more likely there.

    See 19)

21) pg.3 rcol P.2 l.41 - This is a minor comment. I am just curious. Why not using alpha = -1 or -0.9 as it seems more common for protoplanetary disks? -1.5 is an approximation for the Minimum Mass Solar Nebula based on the current solar system planets. Observations of proptoplanetary disks sugggest alpha = -1 or -0.9.

    See 19). Observations sugest alpha = -1 for gas component. Not clear if this is true for the solids (see Chiang + Laughlin 2013). Radial concentration of solids (dust profile steeper than gas) might even be necessary to explain short period terrestrial planets.

22) pg.3 rcol P.2 l.44 - "Each simulation is evolved for 5,000 years" - Could you, please, add discussion regarding simulation time, as well as, define what is a short and long time. For me 5000 yr is, in principle, too short (see my concern #4).

    See our response to concern #4

23) pg.3 rcol P.3 l.44-46 - "The dynamical effects of secular forcing by the giant planet, along with the effects of viscous stirring and gas drag on the planetesimals, are built into the initial conditions." - From the text, It is not clear whether the authors are considering the gas disk phase or not?

    The idea here is that the viscous stirring and gas drag time are longer than the simulation time, so we can get away with ignoring the gas drag on planetesimals. However, we need to make sure the planetesimals start in the right dynamically heated state because the planetesimal formation time is probably longer than the two aformentioned timescales.

24) pg.3 rcol P.3 l.48 - "... and gas drag as a function of semimajor axis..." - Again, is this only used to setup the disk condition, or is this updated during the simulation, once debris are created? Are debris created?

    See 23). Just used to set up the initial conditions

25) pg.3 rcol P.3 l.49-50 - "Although ChaNGa does not account for the effects of gas drag on the planetesimals..." - Please, see my concerns and add discussion.

    This has been addressed in other locations

26) pg.4 lcol P.2 l.49 - "dynamical timescale of planetesimals..." - What do you mean by dynamical timescale of planetesimals? Collisional timescale, drift timescale, what?

    1/sqrt(G*rho_pl), which sets the timescale for gravitational interactions between planetesimals that undergo close encounters

27) pg.4 rcol P.1 l.41 - "... T_lib ~ 1,000 - 2,000 years..." - So the integration time is about a factor of 2-4 T_lib. Is this enough to take conclusions? Please, see my concern and add discussion.

    The 'spikes' in the a-e plane do not evolve over the time that we record collisions, so yes.

28) pg.4 rcol P.2 l.52-53 - "Resonances with the perturbing planet are visible as nonaxisymmetric gaps." - I am afraid that this is only because none of your particles are drifting, which would locally increase the collision rates once small planetesimals fragments that should be drifting away start to (maybe unrealistically) pile up within or near MMR, thus quickly collisionally evolving to dust. I wonder if this would ever happen if gas drag was to play? Please, see my concern and add discussion.

    This is referring specifically to the positions of the planetesimals and not to any observable property. Even if the smaller fragments do drift significantly, the nonaxisymmetric gaps will still be present, although observing full sized planetesimals is next to impossible.

29) pg.4 rcol P.2 l.56-59 - "... in Richardson et al. (2000) (see bottom panel of figure 3) and Tabeshian & Wiegert (2016) (figure 3)." - add figure 3 in those works. Fig 3 in this work does not have bottom panels.

    Is the referee asking me to show fig 3 from these other papers in our paper? Change 'bottom panel of fig 3 in Richardson' to 'fig 3c and 3f in Richardson'

30) Figure 2 - I wonder how (or if) particle drifting due to gas-drag would change this figure? Also, the 8:3 and 7:2 MMRs are irrelevant here! Why not showing 7:3 MMR that is discussed in the main text?

    Is the referee thinking of smaller bodies, or full sized planetesimals here? I wouldnt think that full sized planetsimals are going to drift by any significant amount. Typo in the text here, '7:3' should say '8:3'.

31) Caption of Figure 2 - "Between the resonances, the nonzero eccentricity is due to secular forcing by the planet." - Gas would likely damp them to zero!

    Is this true? What is the timescale for secular forcing?

32) pg.5 rcol P.1 l.15 - "PDF" - Please, define abbreviations before using it.

    Probability density function

33) pg.5 rcol P.2 l.24-27 - "The most prominent features appear as an enhancement to the collision rate near the 2:1 MMR and a decrease near the 3:1 MMR." - I don't see a decrease near 3:1 in figure 4. I see two peaks around 3:1 and one interior to the 2:1.

    I see a decrease near the 3:1 AND two peaks around it! I just didnt mention the peaks because the dip was more noticable.

34) Last paragraph of section 4.1 - "We attribute... radial dust distribution" - I don't understand this argument about gravitational focusing. In my interpretation, what could be happening is that planetesimals that get excited by the MMRs collide at their perihelion distances. This explains why the larger relative # of collisions are close to the MMRs and interior to it.

    I should probably add that extra plot to explain this. Orbital phase at time of collision (perihelion) should show up when looking at semimajor axis.

35) pg.6 lcol P.1 l.33 - "cylindrical distance" - please, define before start using it.

    Define cylindrical distance

36) pg.6 rcol P.2 l.47-54 - "This also suggests... radial collision profile." - I don't know if I agree with authors' conclusions that MMRs are not that important, and that most collisions occur with objects out of resonance. It looks for me that the features seem in Fig 6 (similar to Fig 4) are caused by objects in MMRs colliding at their pericentric and apocentric distances within the eccentric orbits. In my understanding, if authors' arguments are correct, MMRs should basically not matter, and Fig 5 would look similar if no planet was present. If that is the case, how can this work serve to constrain the mass and eccentricity of a perturbing planet?

    Looks like the referee didnt understand what we were getting at here. The collisions are due to bodies right at the edge of resonance, where the circulation frequency blows up. Might help to add in that plot I made showing the difference in the collision profile with and without bodies with semimajor axes inside of resonance.

37) pg.6 rcol P.2 l.38-56 - "As mentioned in section 2, ... appears to 'follow' the planet." - This paragraph is super confuse. I don't understand this. Why not simply say this is caused by the secular forcing in eccentricity? This would save 3 paragraphs in the paper and would be much more clear.

    See 36). The effect is not simply due to the secular forcing, otherwise the gaps in figure 2 would be aligned with the pericenter of the planet.

38) Figs 4 and 5 - Why is the relative # larger than 1? Relative to what?

    Because its a probability density function. Add some discussion in the text of how we normalized them.

39) General note about the figures - Not that I want to be repetitive, but I am afraid that if small planetesimals are allowed to drift the bumps and dips from these figures may change as the small planetesimals would likely collide everywhere in radial distances. This is because internal MMRs are not strong enough to perturb these small fast-drifting planetesimals. In my opinion, without considering small planetesimals drifting due to gas drag, Figs 6 and 7 (especially) represent a planetesimal collisional profile, but not necessarily a dust profile. Please, see my concerns and add discussion.

    Already addressed above

40) pg.10 lcol P.4 l.42-44 - "Many different parameterizations are possible, depending on optical depth, grain size, disc temperature, etc.,..." - But couldn't this change all of your conclusions? Please, see my concerns regarding planetesimal sizes and add discussion.

    Ask aaron about this?

41) Last paragraph of section 5 - "In order to... cases shown above" - This is a big IF, especially if what the authors are measuring here is the planetesimal collisional profile rather than the dust profile, or if the dust profile would be even shallower as a consequence of aerodynamic drag acting on small fragments of collisionally evolved planetesimals.

    Already addressed above

42) pg.12 rcol P.1 l.8-24 - "Near the interior 2:1... both of these quantities." - This is a clear way to set the explanation. Well done! I hope to see more of that in the revised version. I think a lot of the explanations in the main text should be substituted by something clear and concise as this! Make it simple!

    :-)

43) pg.12 rcol P.3 l.45-48 - "Given that the solid surface density diminishes with distance (r^-1.5 for the MMSN (Hayashi 1981)), exterior resonances may not be quite as useful for this type of measurement, however.)" - Not sure I agree. Exterior MMRs can more easily capture inward drifting objects (e.g. Weidenschilling & Davis 1985; Patterson 1987; Beauge & Ferraz-Mello 1993; Malhotra 1993; Gomes 1995; Jiang & Yeh 2004; Batigyn & Laughlin 2015; Storch & Batygin 2019), increasing their local collision rates (Deienno et al. 2020), thus potentially generating very strong dusty features.

    If we're just talking about planetesimals, however, the inner resonances are more useful. Not sure how much we want to get into looking at drifting small bodies

44) pg.12 rcol P.4 l.50-52 - "As we have shown, the bump vs dip feature near the 2:1 MMR is marginally detectable with ALMA for the nearest protoplanetary discs." - Please, see my concern and add discussion.

    Good place to mention caveats brought up by the referee

My apologies for being so long. I do think this work has potential, but it does need substantial clarifications.

### 2020-10-26 main.tex
Start addressing referee comments

@@
 \usepackage[T1]{fontenc}
+\usepackage{ulem}
 
@@
 diagnostics for the physical processes that drive the evolution of the discs. In many gas-rich systems, these gap features are argued to indicate the 
-presence of a giant planet, either embedded in the disc \citep{2015MNRAS.453L..73D} or orbiting externally, although the details of gas-dust 
+presence of a giant planet, either embedded in the disc \citep{2015MNRAS.453L..73D} or orbiting \sout{externally} \textbf{adjacent to it}, although the details of gas-dust 
 interactions can have strong effects on the resulting morphologies
@@
 
-\citet{2013ApJ...777L..31D} showed that collisional dust that is generated near the gap opened by a giant planet in a planetesimal disc should 
+\citet{2013ApJ...777L..31D} showed that collisional dust that is generated near the gap opened by a giant planet in \textbf{the inner regions of} \sout{planetesimal} \textbf{transition} disc should 
 produce a distinct observable marker that could be used to infer the presence of the planet. In a followup study, it was found that morphological 
@@
 \citep{2000Icar..143...45R, 2017ApJ...850..103B}. Unfortunately, collision detection in an N-body simulation is extremely computationally expensive. 
-So far, studies of planetesimal dynamics near MMRs have involved either collisionless test particles 
+So far, studies of planetesimal dynamics near MMRs \textbf{in which the planetesimals are directly resovled} have involved either collisionless test particles 
 \citep{2017ApJ...850..103B, 2016ApJ...818..159T, 2018ApJ...857....3T} or severely limited integration times \citep{2000Icar..143...45R}.
@@
 longitude of pericenter of the giant planet, and $b^{j}_{s} (\alpha)$ is a 
-Laplace coefficient given by \citep{2000ssd..book.....M} as
+Laplace coefficient given by \citep{1999ssd..book.....M} as
 
@@
 equlibrium value, while this angle will circulate outside of resonance. For small eccentricities, this behavior is analogous to the motion of a 
-pendulum. Furthermore, variations in the critical angle are coupled to changes in the mean motion and semimajor axis \citep{2000ssd..book.....M}. An important 
+pendulum. Furthermore, variations in the critical angle are coupled to changes in the mean motion and semimajor axis \citep{1999ssd..book.....M}. An important 
 point to note, which we will revisit later, is that the variation frequency of this angle approaches zero near the edge of a resonance. The 
 width of a resonance can be defined by determining the largest variation in semimajor axis that permits librational, rather than circulatory motion of $\phi$. For 
-second order and higher MMRs, the maximum libration width is given by equation 8.58 in \citet{2000ssd..book.....M} as
+second order and higher MMRs, the maximum libration width is given by equation 8.58 in \citet{1999ssd..book.....M} as
 
@@
 
-\noindent (see \citet{2000ssd..book.....M} table 8.1) where $D b^{j}_{s}$ is the first derivative with respect to $\alpha$ of the Laplace coefficient defined in equation \ref{eq:lap}.
+\noindent (see \citet{1999ssd..book.....M} table 8.1) where $D b^{j}_{s}$ is the first derivative with respect to $\alpha$ of the Laplace coefficient defined in equation \ref{eq:lap}.
 This is given by \citet{1961mcm..book.....B} as
@@
 
-\noindent (see \citet{2000ssd..book.....M} table 8.1) and there is an additional contribution to the motion of the critical angle by the pericenter precession rate such that
+\noindent (see \citet{1999ssd..book.....M} table 8.1) and there is an additional contribution to the motion of the critical angle by the pericenter precession rate such that
 
@@
 
-\noindent (see \citet{2000ssd..book.....M} equation 8.76).
+\noindent (see \citet{1999ssd..book.....M} equation 8.76).
 
@@
 equilibrium near the resonances before the collision rate is measured. The libration timescale, which describes how long the critical angle (and also 
-the semimajor axis and eccentricity) of a planetesimal in resonance takes to undergo a full oscillation is given by (see equation 8.47 in \citet{2000ssd..book.....M})
+the semimajor axis and eccentricity) of a planetesimal in resonance takes to undergo a full oscillation is given by (see equation 8.47 in \citet{1999ssd..book.....M})
 \begin{equation}\label{eq:lib_time}
@@
 \citet{2016ApJ...818..159T} provide a different explanation for this phenomenon, suggesting that the nonaxisymmetric structure is the product 
-of the path that a resonant test particle takes in a frame co-rotating with the planet (see figure 8.4 of \citet{2000ssd..book.....M}). This explanation, 
+of the path that a resonant test particle takes in a frame co-rotating with the planet (see figure 8.4 of \citet{1999ssd..book.....M}). This explanation, 
 however, does not hold for a large collection of planetesimals, especially when there is no forced eccentricity. In such a case, the orbits of 

### 2020-10-28 refereeResponse.txt
More edits according to referee report

@@
 
-    Add clarification: although we don't model gas drag here, the ICs need to start in eqilibrium.
+    TODO: Add clarification: although we don't model gas drag here, the ICs need to start in eqilibrium.
 The viscous stirring time is much longer than any of the other relevant timescales resolved in the simulation, so it is sufficient for us to calculate what <e^2>^{1/2} would be if there were gas around.
@@
 
-    Looks like this was a typo that carried through a few equations.
-Fortunately, this same mistake was not made when doing any calculations for the paper (all equations used in our analysis are consistent with the referee's convention)
+    The argument should indeed by -q, rather than -(2p+q).
+This mistake was carried through when writing up the equations in the paper, although it appears we properly used j4 = -q when doing our analysis and constructing plots.
+(2p+q) has been replaced by q in equations 5 and 6 in the paper.
 
@@
 
-    To add
+    Added
 
@@
 
-    Minus sign missing in front of both terms
+    You are correct. There was a minus sign missing in front of both terms in the paper. This has now been fixed
 
@@
 
-    If t_drift >> t_librate, then still holds true. The big question is what is t_librate for sthe small bodies. This is set by their eccentricity.
+    This section is meant to focus solely on the dynamical effects that the planet has on the full-sized planetesimal population.
+We will save the discussion of what happens to the debris from collisions for a 'caveats' section later in the paper.
 
@@
 
-    Not sure how to address this? Does the referee mean 'planet formation' when referring to astronomy? Could we just add some citations to other papers that use ChaNGa for planet stuff?
+    We provide some references to planet formation simulations done with PKDGRAV, which uses similar methods to ChaNGa.
+An additional paragraph has been added which summarizes some of the details provided about the ChaNGa collision model described in Wallace & Quinn 2019.
 
@@
 
-    We can certainly do this. I wrote this before adding table 1, which makes it clear.
+    This sentence has been simplified.
 
@@
 
-    Maybe we should do more to emphazise that this setup was motivated by a Jupiter - asteroid belt setup. Be sure to change AU to au (this is what the editor asked for in the last MNRAS paper)
+    Another sentence was added to the first paragraph of section 3.2 which explains our choice of parameters more clearly.
+The 'nominal' simulation is meant to be compared directly with simulation B of Richardson et al.
+2000, although we reduce the width of the planetesimal annulus to reduce the number of particles required (while still covering all of the promininent interior MMRs).
+AU has been changed to au everywhere in the paper.
 
@@
 
-    See 19)
+    This is a good point, although exterior MMRs with Jupiter in the solar system are not going to be as interesting due to the close proximity of Saturn (of course, in the general case of a single giant planet, this is not true).
+As discussed above in 19), our work was mainly motivated by the non-result seen by Richardson et al.
+2000.
+Additionally, the number of timesteps required to measure the collision profile for the exterior MMRs increases with semimajor axis when using alpha steeper than -1.
+TODO: Add a discussion at the end of the paper explaining that exterior MMRs are interesting too.
 

### 2020-10-28 main.tex
More edits according to referee report

@@
 create dusty disc structures that would not exist otherwise. Previous studies have shown that morphological differences in the collisional dust 
-corotating with a giant planet can be used to determine whether the planet's eccentricity is large or small. Going further, we investigate the 
-production of second-generation dust near prominent mean-motion resonances with the planet using N-body simulations that directly resolve 
-collisions between planetesimals. We find that a distinct over- or under-density in the dust emission is produced at the interior 2:1 mean-motion 
-resonance, depending on the mass and eccentricity of the planet. The presence of one of these two features can be used to place simultaneous 
-upper or lower limits on the mass and eccentricity of the perturbing body.
+corotating with a giant planet can be used to determine whether the planet's eccentricity is large or small. \textbf{In this work, we use N-body simulations
+that directly resolve collisions between planetesimals to investigate the collision rate profile near mean-motion resonances with the planet. We 
+find that a distinct bump or dip feature is produced in the collision profile, the presence of which depends on the libration width of the resonance, 
+compared with the peri- and apocenter distances of the edges of the resonance. These quantities encode information about the mass and eccentricity 
+of the planet, and therefore these features in the collision profile place constraints on the orbital properties of the planet. Under the simplifying 
+assumption that the resulting dust distribution directly traces the collision profile, we find that a distinct over- or under-density in the dust emission 
+is produced at the interior 2:1 mean-motion resonance, which can be used to constrain the mass and eccentricity of the planet.}
 \end{abstract}
@@
 \begin{equation}\label{eq:phi_crit}
-	\phi = (p + q) \lambda' - q \lambda - (2 p + q) \varpi,
+	\phi = (p + q) \lambda' - p \lambda - q \varpi,
 \end{equation}
@@
 width of a resonance can be defined by determining the largest variation in semimajor axis that permits librational, rather than circulatory motion of $\phi$. For 
-second order and higher MMRs, the maximum libration width is given by equation 8.58 in \citet{1999ssd..book.....M} as
+second order and higher MMRs, the maximum libration width is given by \sout{equation 8.58} in \citet{1999ssd..book.....M} \text{bf}(ch. 8, pg 338, eq. 8.58) as
 
 \begin{equation}\label{eq:res_so}
-	\frac{\delta a}{a} = \pm \left( \frac{16}{3} \frac{\left| C_{r} \right|}{n} e^{\left| 2 p + q \right|} \right)^{1/2},
+	\frac{\delta a}{a} = \pm \left( \frac{16}{3} \frac{\left| C_{r} \right|}{n} e^{\left| q \right|} \right)^{1/2},
 \end{equation}
@@
 
-\noindent (see \citet{1999ssd..book.....M} table 8.1) where $D b^{j}_{s}$ is the first derivative with respect to $\alpha$ of the Laplace coefficient defined in equation \ref{eq:lap}.
+\noindent (see \citet{1999ssd..book.....M} table 8.1\textbf{, third row, with $j = p + q$}) where $D b^{j}_{s}$ is the first derivative with respect to $\alpha$ of the Laplace coefficient defined in equation \ref{eq:lap}.
 This is given by \citet{1961mcm..book.....B} as
@@
 \begin{equation}\label{eq:fd_fo}
-	f_{d}(\alpha) = (p+q) b_{1/2}^{p+q} + \frac{\alpha}{2} D b_{1/2}^{p+q},
+	f_{d}(\alpha) = -(p+q) b_{1/2}^{p+q} - \frac{\alpha}{2} D b_{1/2}^{p+q},
 \end{equation}
 
-\noindent (see \citet{1999ssd..book.....M} table 8.1) and there is an additional contribution to the motion of the critical angle by the pericenter precession rate such that
+\noindent (see \citet{1999ssd..book.....M} table 8.1\textbf{, first row}) and there is an additional contribution to the motion of the critical angle by the pericenter precession rate such that
 
@@
 
-\noindent (see \citet{1999ssd..book.....M} equation 8.76).
+\noindent (see \citet{1999ssd..book.....M} \textbf{ch 8, pg 340,} equation 8.76 \textbf{with $j_{2} = p$}).
 
@@
 This code, which is written in the {\sc CHARM++} parallel programming language, was originally designed for cosmology simulations 
-and has been shown to perform well on up to half a million processors \citep{2015AphCom..2..1}. {\sc ChaNGa} calculates 
-gravitational forces using a modified Barnes-Hut \citep{1986Natur.324..446B} tree with hexadecapole expansions of the moments. 
+and has been shown to perform well on up to half a million processors \citep{2015AphCom..2..1}.
+\textbf{Using similar methods to {\sc PKDGRAV}, which has been used for numerous studies of planet formation (add some references here)}, {\sc ChaNGa} calculates
+gravitational forces using a modified Barnes-Hut \citep{1986Natur.324..446B} tree with hexadecapole expansions of the moments \textbf{and then integrates the equations of motion using a kick-drift-kick leapfrog scheme}.
 All of the simulations we perform use a node opening criterion of $\theta_{BH}$ = 0.7. More information about the code can be found 
-in \citet{2008IEEEpds...ChaNGa}. We have also recently modified {\sc ChaNGa} to handle solid-body collisions. A full description of 
-the collision module implementation can be found in \citet{2019MNRAS.489.2159W}.
+in \citet{2008IEEEpds...ChaNGa}. \sout{We have also recently modified {\sc ChaNGa} to handle solid-body collisions. A full description of 
+the collision module implementation can be found in }\citet{2019MNRAS.489.2159W}.
+
+\textbf{We have recently modified {\sc ChaNGa} to handle solid-body collisions between particles, by assigning them a fixed radius, rather than treating them as tracers of a fluid with a characteristic softening length.
+We provide a brief summary of the collision model here, although a full description is provided in \citet{2019MNRAS.489.2159W}.
+This work is largely based off of the solid-body collision implementation in {\sc PKDGRAV}, which is described in \citet{1994MNRAS.269..493R} and \citet{2000Icar..143...45R}.
+Imminent collisions are found during the drift phase of each time step by extrapolating the positions of bodies forward using the velocity calculated during the first kick.
+For each body, the nearest 64 neighbors are tested for an imminent collision.
+If an imminent collision is detected, the two particles of mass $m_{1}$ and $m_{2}$ are merged together together to form one single larger body with the same density and a mass of $m_{1} + m_{2}$.
+The resulting body is then imparted with the center of mass position and velocity of its two children.
+Because the resolution of a collision can result in another imminent collision, these events must be resolved one at a time, with the soonest collision being resolved first.
+For this reason, another collision search is run each time a collision is resolved, which continues until there are no more imminent collisions during the current time step.}
 
@@
 is a ``nominal'' case, in which the perturbing planet's mass and 
-eccentricity are set to that of Jupiter's. In the other four cases, the mass (eccentricity) is increased or decreased by a factor of two, while the 
-eccentricity (mass) is held at the nominal value. In all cases, the perturbing giant is placed on a 5.2 AU orbit around a 1 $M_{\odot}$ star. The 
-planetesimal disc extends from 2.2 to 3.8 AU, which covers the two most prominent mean-motion resonances with the giant planet, the 2:1 at 3.27 AU 
-and the 3:1 at 2.5 AU. The planetesimal disc follows a minimum-mass solar nebula surface density profile \citep{1981PThPS..70...35H}
+eccentricity are set to that of Jupiter's. In the other four cases, the mass \textbf{or eccentricity is altered} \sout{(eccentricity) is increased or decreased} by a factor of two \sout{, while the 
+eccentricity (mass) is held at} \textbf{from} the nominal value. In all cases, the perturbing giant is placed on a 5.2 au orbit around a 1 $M_{\odot}$ star. The 
+planetesimal disc extends from 2.2 to 3.8 au, which covers the two most prominent mean-motion resonances with the giant planet, the 2:1 at 3.27 au 
+and the 3:1 at 2.5 au. The planetesimal disc follows a minimum-mass solar nebula surface density profile \citep{1981PThPS..70...35H}
 
@@
 \noindent with $\alpha$ = 3/2 and $\Sigma_{0}$ = 10 g cm$^{-2}$. Planetesimals are given a bulk density of 2 g cm$^{-3}$ and a diameter of 
-300 km. This corresponds to a disc containing roughly 500,000 bodies. Each simulation is evolved for 5,000 years, which is about 400 orbits 
+300 km.
+\sout{This corresponds to a disc containing roughly 500,000 bodies.} \textbf{This choice of parameters for the planetesimal disk is meant to follow the setup used in simulation B by \citet{2000Icar..143...45R}.
+One difference from the aformentioned study is that we use a narrower annulus, which reduces the number of particles required from $10^6$ down to roughly 500,000.
+This allows us to use a finer base timestep size, which, as we will discuss in section \ref{sec:results}, appears to be the reason why no features were seen in the collision profile near the resonances by \citet{2000Icar..143...45R}}.
+Each simulation is evolved for 5,000 years, which is about 400 orbits
 of the perturbing planet.
@@
 construct a PDF of the collisions using a Kernel Density Estimate (KDE). We use the {\sc neighbors.KernelDensity} function from the {\sc sklearn} 
-\citep{scikit-learn} package to construct our KDEs, using a gaussian kernel with a FWHM of 0.02 AU.
+\citep{scikit-learn} package to construct our KDEs, using a gaussian kernel with a FWHM of 0.02 au.
 
@@
     \includegraphics[width=0.5\textwidth]{figures/coll_hist_a.png}
-    \caption{A PDF of the collision rate in each disc as a function of semimajor axis, generated using a KDE with a Gaussian kernel with a FWHM of 0.02 AU.
+    \caption{A PDF of the collision rate in each disc as a function of semimajor axis, generated using a KDE with a Gaussian kernel with a FWHM of 0.02 au.
 In semimajor axis space, prominent features appear near the 3:1 and 2:1 MMRs.
@@
 \noindent where $m$, $e$ and $s$ are the mass, eccentricity and radius of the dust grain. $C_{D}$ is a drag coefficient which is of order unity, $
-\rho_{g}$ is the local density of the gas and $v_{th}$ is its thermal speed. At 3 AU, the gaseous component of the solar nebula has a density of $4 
+\rho_{g}$ is the local density of the gas and $v_{th}$ is its thermal speed. At 3 au, the gaseous component of the solar nebula has a density of $4 
 \times 10^{-10}$ g cm$^{-3}$ and a typical thermal speed of $10^{5}$ cm s$^{-1}$ \citep{1981PThPS..70...35H}. For a 1 mm dust grain with a 
@@
 of second-generation dust can be constructed from the cylindrical distance at which the collisions occur. This is shown in figure \ref{fig:coll_hist_r}. 
-Similar to figure \ref{fig:coll_hist_a}, we use a KDE with a width of 0.02 AU to assemble the collision locations into a radial distribution. Most 
+Similar to figure \ref{fig:coll_hist_a}, we use a KDE with a width of 0.02 au to assemble the collision locations into a radial distribution. Most 
 strikingly, the bump that was present near the 2:1 resonance is no longer visible in cylindrical distance space, although it suddenly appears again in 
 the e3m2 simulation. The dip that is visible near the 3:1 MMR also becomes a bump in the highest eccentricity case. To determine how the resonant 
-bodies actually contribute to the radial collision profile, we excluded collisions that fall between $2.495 < a < 2.505$ AU (near the 3:1 resonance) and 
-between $3.2 < a < 3.35$ AU (near the 2:1 resonance), which is shown by the dashed curve. Qualitatively, none of the bump or dip features present 
+bodies actually contribute to the radial collision profile, we excluded collisions that fall between $2.495 < a < 2.505$ au (near the 3:1 resonance) and 
+between $3.2 < a < 3.35$ au (near the 2:1 resonance), which is shown by the dashed curve. Qualitatively, none of the bump or dip features present 
 are removed by making this exclusion. This suggests that the features near resonance seen in semimajor axis space become smeared out in 
@@
 attribute this to the more complex symmetry, compared to the 2:1 MMR. In addition, a number of other nearby resonances, including the 7:2 (at 
-2.25 AU), the 10:3 (at 2.33 AU), the 8:3 (at 2.71 AU) and the 5:2 (at 2.82 AU) also likely are contributing to the collision profile in cylindrical distance 
+2.25 au), the 10:3 (at 2.33 au), the 8:3 (at 2.71 au) and the 5:2 (at 2.82 au) also likely are contributing to the collision profile in cylindrical distance 
 space near the 3:1 MMR. The 3:1 MMR is also much narrower than the 2:1, which means that any dip or bump features produced by it would 
@@
 bump vs dip feature near the 2:1 MMR is marginally detectable with ALMA for the nearest protoplanetary discs. Another complicating factor is that 
-the inner $\sim$ 10 AU of most protoplanetary discs are optically thick in the sub-mm. The solution to this problem is to instead observe at longer 
+the inner $\sim$ 10 au of most protoplanetary discs are optically thick in the sub-mm. The solution to this problem is to instead observe at longer 
 wavelengths where the inner disc is optically thin. This comes at the expense of much poorer resolution. However, future radio facilities like the NG-
@@
 First order MMRs with the planet are indicated with arrows.
-A second planet is also present at 32.3 AU, although it is not massive enough to induce any significant structure in the disc near associated resonances.\label{fig:boley_rtheta}}
+A second planet is also present at 32.3 au, although it is not massive enough to induce any significant structure in the disc near associated resonances.\label{fig:boley_rtheta}}
 \end{figure*}
@@
 \ref{fig:boley_rtheta}, we show the planetesimal positions in polar, rather than Cartesian coordinates as originally presented in the paper. Two planets 
-on circular orbits are present here. The first has mass of 17 $M_{\earth}$ and lies at 32.3 AU. The second planet has a mass of 50 $M_{\earth}$ 
-and lies at 68.8 AU. A horseshoe shaped collection of planetesimals is visible to be corotating with each planet. Nonaxisymmetric gaps are also
+on circular orbits are present here. The first has mass of 17 $M_{\earth}$ and lies at 32.3 au. The second planet has a mass of 50 $M_{\earth}$ 
+and lies at 68.8 au. A horseshoe shaped collection of planetesimals is visible to be corotating with each planet. Nonaxisymmetric gaps are also
 visible at the locations of first order MMRs with the more massive planet, which are indicated with arrows.

### 2020-10-29 refereeResponse.txt
More edits

@@
 This mistake was carried through when writing up the equations in the paper, although it appears we properly used j4 = -q when doing our analysis and constructing plots.
-(2p+q) has been replaced by q in equations 5 and 6 in the paper.
+(2p+q) has been replaced by q in equations 5 and 6 in the paper (also need to fix 14).
 
@@
 
-    This is a good point, although exterior MMRs with Jupiter in the solar system are not going to be as interesting due to the close proximity of Saturn (of course, in the general case of a single giant planet, this is not true).
-As discussed above in 19), our work was mainly motivated by the non-result seen by Richardson et al.
-2000.
+    This is a good point.
+Our work was mainly motivated by the non-result seen by Richardson et al.
+2000, which is why we focus on interior MMRs here.
 Additionally, the number of timesteps required to measure the collision profile for the exterior MMRs increases with semimajor axis when using alpha steeper than -1.
@@
 
-    See 19).
-Observations sugest alpha = -1 for gas component.
-Not clear if this is true for the solids (see Chiang + Laughlin 2013).
-Radial concentration of solids (dust profile steeper than gas) might even be necessary to explain short period terrestrial planets.
+    See 19) and 20).
+While there is certainly evidence that the gaseous component of the outer regions of protoplanetary disks follow alpha = -1, there is little evidence to suggest that this is the case for solids in the inner planet-forming region.
+Although alpha = -1.5 is not motivated by any extrasolar observations, it is compatible with the majority of protoplanetary disk models.
 
@@
 
-    See our response to concern #4
+    See our response to concern #4. Some text has been added to the paper to elaborate on this as well.
 
@@
 
-    The idea here is that the viscous stirring and gas drag time are longer than the simulation time, so we can get away with ignoring the gas drag on planetesimals.
-However, we need to make sure the planetesimals start in the right dynamically heated state because the planetesimal formation time is probably longer than the two aformentioned timescales.
+    We are considering the gas disk phase here, while making the assumption that the effects of for gas drag on the planetesimals is very weak.
+In the initial conditions, we tune dynamical excitation of the planetesimals so that the effects of viscous stirring and gas drag (had we imparted a drag force on the particles in the simulation) are in balance.
+The gravitational stirring time is much longer than 5,000 years, so our planetesimal disk will not suffer from too much dynamical heating because we did not model the gas.
+More text has been added to this section to explain this more clearly.
 
@@
 
-    The 'spikes' in the a-e plane do not evolve over the time that we record collisions, so yes.
+    In our case, the large particle count allows us to look at the 'ensemble average' of the dynamical behavior near resonance.
+Even though individual planetesimals only go through a few librational periods, the phase trajectories that they follow are well populated and allow us to make conclusions about the dynamics without needing a longer baseline to take time averages.
+Had we been following only a few bodies, this would not have been the case.
 

### 2020-10-29 main.tex
More edits

@@
 The dynamical effects of secular forcing by the giant planet, along with  the effects of viscous stirring and gas drag on the planetesimals, are 
-built into the initial conditions. This is done by first calculating the equilibrium eccentricity $e_{eq}$ due to viscous stirring and gas drag as a 
+built into the initial conditions.
+\textbf{Although we do not model the effects of gas drag on the planetesimals, we construct the initial conditions such that these two effects are in balance.
+The viscous stirring timescale of the planetesimal disc is much longer than our chosen integration time, and so the dynamical excitation of the disc (excluding resonances) stays constant, even without modeling damping from gas.}.
+This is done by first calculating the equilibrium eccentricity $e_{eq}$ due to viscous stirring and gas drag as a
 function of semimajor axis according to equation 12 of \citet{2002ApJ...581..666K}. Although {\sc ChaNGa} does not account for the effects of 
@@
 \begin{equation}\label{eq:lib_time}
-	T_{lib} = \frac{2 \pi}{3 q^{2} C_{r} n e^{\left| 2p + q \right|}},
+	T_{lib} = \frac{2 \pi}{3 q^{2} C_{r} n e^{\left| -q \right|}},
 \end{equation}
@@
 \noindent for small-amplitude librations. For all five sets of initial conditions used, $T_{lib} \sim$ 1,000 - 2,000 years for the 3:1 and 2:1 resonances. 
-For this reason, we allow each simulation to run for 2,000 years before we begin recording any collision statistics.
+For this reason, we allow each simulation to run for 2,000 years before we begin recording any collision statistics. \textbf{Although the integration time we use
+is only a tiny fraction of the Myr timescales that a typical protoplanetary disk lives for (citation?), 5,000 years is sufficient to allow all of the relevant dynamics here.
+As discussed above in section \ref{sec:ics}, the initial conditions are constructed so that relevant effects with longer timescales (such as gravitational stirring, gas drag on planetesimals and secular forcing) are already in equilibrium.}
 

### 2020-10-29 refereeResponse.txt
More edits

@@
 
-    See 23). Just used to set up the initial conditions
+    See 23).
+This is just used to set up the initial conditions.
+Both the gravitational stirring and gas drag time for the planetesimals is much longer than the simulation time (because we do not track the creation of smaller debris) and so we can set the initial conditions and then forget about these effects.
 
@@
 
-    This has been addressed in other locations
+    See 23) and 24)
 
@@
 
-    1/sqrt(G*rho_pl), which sets the timescale for gravitational interactions between planetesimals that undergo close encounters
+    This is the timescale for gravitational interactions between planetesimals that undergo close encounters. A sentence has been added to this section to clarify.
 
@@
 Had we been following only a few bodies, this would not have been the case.
+Some additional text has been added to this paragraph to explain this more clearly.
 
@@
 
-    This is referring specifically to the positions of the planetesimals and not to any observable property.
-Even if the smaller fragments do drift significantly, the nonaxisymmetric gaps will still be present, although observing full sized planetesimals is next to impossible.
+    This is referring specifically to the positions of the planetesimals in this figure and not to any observable property.
+Even if the smaller fragments do drift significantly, the nonaxisymmetric gaps in the planetesimals will still be present, although observing full sized planetesimals is next to impossible.
+This sentence has been modified to clarify that we are specifically talking about the structure seen in figure 1.
+A discussion of the referee's concerns about the radial structure of the smaller debris fragments will be added towards the end of the paper.
 
@@
 
-    Is the referee asking me to show fig 3 from these other papers in our paper? Change 'bottom panel of fig 3 in Richardson' to 'fig 3c and 3f in Richardson'
+    The text now specifies the subfigures we are referring to (3c and 3f in Richarson, 3a in Tabeshian & Weigert)
 
@@
 
-    Is the referee thinking of smaller bodies, or full sized planetesimals here?
-I wouldnt think that full sized planetsimals are going to drift by any significant amount.
-Typo in the text here, '7:3' should say '8:3'.
+    The libration timescale and the secular forcing timescale are much shorter than the stopping time due to gas for the planetesimals, so this figure should not look different had we modeled gas drag.
+A typo in the text has been, '7:3' was supposed to say '8:3'.
+TODO: Insert a calculation of the stopping time and secular forcing timescale somewhere.
 
@@
 
-    Is this true? What is the timescale for secular forcing?
+    See 30)
 
@@
 
-    Probability density function
+    PDF stands for probability density function. This is now explained in the text.
 
@@
 
-    I see a decrease near the 3:1 AND two peaks around it! I just didnt mention the peaks because the dip was more noticable.
+    Perhaps we should have been more careful with language here.
+In figure 4, there is a local minimum near the 3:1 MMR.
+There are certainly some additional features surrounding it, although these are partly due to collisions with eccentric bodies in the adjacent (7:2 and 5:2) MMRs.
+The text has been changed to refer to the features at the 3:1 and 2:1 MMRs as local maxima and minima.
 
@@
 
-    I should probably add that extra plot to explain this. Orbital phase at time of collision (perihelion) should show up when looking at semimajor axis.
+    An additional figure has been added to clarify the gravitational focusing explanation.
+TODO: Make figure.
+If the offset in the peak of the collision rate in figure 4 (near the 2:1 MMR, for example) were due to bodies colliding at perihelion, the peak should shift inward as the eccentricity of the planet is increased.
+Between the e1m2 and e3m2 simulations, the mean eccentricity at the 2:1 MMR increases from ~0.03 to ~0.06.
+The perihelion distance of a body at the 2:1 MMR would decrease by about 0.1 AU, which would most certainly be apparent in figure 4.
 
@@
 
-    Define cylindrical distance
+    A sentence has been added to the text to clarify what cylindrical distance means.
 

### 2020-10-29 main.tex
More edits

@@
 
-An additional timescale is set by the dynamical time of the planetesimals ($\sim 1/\sqrt{G \rho}$), which is about 45 minutes. To 
+An additional timescale is set by the dynamical time of the planetesimals ($\sim 1/\sqrt{G \rho}$), which is about 45 minutes.
+\textbf{This timescale must be resolved in order to properly follow close gravitational encounters between these bodies.}.
+To
 resolve the base time step and the dynamical timescale of planetesimals simultaneously, we use a two-tiered time stepping scheme following
@@
 shown in figure \ref{fig:xy}. In all cases, the coordinate system is rotated so that the giant planet lies at $\theta = 0$. The longitude of perihelion of 
-the planet is shown by the dashed line. Resonances with the perturbing planet are visible as nonaxisymmetric gaps. Upon close inspection of a 
+the planet is shown by the dashed line. Resonances with the perturbing planet are visible as nonaxisymmetric gaps \textbf{in this figure}. Upon close inspection of a 
 series of simulation snapshots, these gaps appear to follow the planet in its orbit, rather than aligning themselves with the longitude of perihelion. A 
-similar substructure, which is most noticeable near the 2:1 MMR, reveals itself in \citet{2000Icar..143...45R} (see bottom panel of figure 3) and 
-\citet{2016ApJ...818..159T} (figure 3). This structure is also present in the \citet{2017ApJ...850..103B} simulations, although it was not reported at the 
+similar substructure, which is most noticeable near the 2:1 MMR, reveals itself in \citet{2000Icar..143...45R} (see figure \textbf{3c and 3f}) and 
+\citet{2016ApJ...818..159T} (figure 3\textbf{a}). This structure is also present in the \citet{2017ApJ...850..103B} simulations, although it was not reported at the 
 time (see Appendix \ref{sec:boley_plot}). It is worth noting that \citet{2000Icar..143...45R} started with a completely cold planetesimal disc and a 
@@
 \ref{fig:coll_hist_a} in this and subsequent figures are highly sensitive to the number of bins and the location of the bin edges. For this reason, we 
-construct a PDF of the collisions using a Kernel Density Estimate (KDE). We use the {\sc neighbors.KernelDensity} function from the {\sc sklearn} 
+construct a \textbf{probability density function (PDF)} of the collisions using a Kernel Density Estimate (KDE). We use the {\sc neighbors.KernelDensity} function from the {\sc sklearn} 
 \citep{scikit-learn} package to construct our KDEs, using a gaussian kernel with a FWHM of 0.02 au.
@@
 \citet{2000Icar..143...45R}, who simulated a similar setup and found no discernible features near the MMRs. We attribute the differences to a more 
-conservative timestepping criterion in our simulations. The most prominent features appear as an enhancement to the collision rate near the 2:1 
-MMR and a decrease near the 3:1 MMR. At higher forced eccentricities, features near the 5:2, 7:3 and 5:3 resonances are also visible, due to the 
+conservative timestepping criterion in our simulations. The most prominent features appear as \sout{an enhancement to} \textbf{a local maximum in} the collision rate near the 2:1 
+MMR and a \sout{decrease} \textbf{local minimum} near the 3:1 MMR. At higher forced eccentricities, features near the 5:2, \sout{7}\textbf{8}:3 and 5:3 resonances are also visible, due to the 
 steep sensitivity of higher order resonant perturbations to eccentricity \citep{1994PhyD...77..289M}.
@@
 we focus on local dust sourcing only while acknowledging that subsequent evolution could affect the morphology.}, a map of the relative concentration 
-of second-generation dust can be constructed from the cylindrical distance at which the collisions occur. This is shown in figure \ref{fig:coll_hist_r}. 
+of second-generation dust can be constructed from the cylindrical distance at which the collisions occur.
+\textbf{Here, cylindrical distance is measured as the distance between the central star and the collision in the ($r, \theta$) plane.} This is shown in figure \ref{fig:coll_hist_r}.
 Similar to figure \ref{fig:coll_hist_a}, we use a KDE with a width of 0.02 au to assemble the collision locations into a radial distribution. Most 

### 2020-10-30 refereeResponse.txt
More edits, add figure to clarify gravitational focusing explanation

@@
     An additional figure has been added to clarify the gravitational focusing explanation.
-TODO: Make figure.
+TODO: Update text to go along with figure.
 If the offset in the peak of the collision rate in figure 4 (near the 2:1 MMR, for example) were due to bodies colliding at perihelion, the peak should shift inward as the eccentricity of the planet is increased.
@@
 
-    Looks like the referee didnt understand what we were getting at here.
-The collisions are due to bodies right at the edge of resonance, where the circulation frequency blows up.
-Might help to add in that plot I made showing the difference in the collision profile with and without bodies with semimajor axes inside of resonance.
+    As shown in figure 5, the bump and dip features at the center of the MMRs are still present, even if we ignore particles whose semimajor axis falls within the libration width of the resonances.
+This does not mean, however, that the resonances are not important.
+As we approach the edges of the resonance from the outside, the critical angle approaches a stationary value.
+Where the critical angle is stationary, the pericenter orientations of the planetesimals experience a torque which causes their \varpi to follow the giant planet in its orbit.
+This is what we propose is responsible for the coherent structure seen in the right-hand panels of figures 6 and 7, along with the structure seen in the collision profiles.
+TODO: Expand our explanation in the paper to clarify this.
 
@@
 
-    See 36). The effect is not simply due to the secular forcing, otherwise the gaps in figure 2 would be aligned with the pericenter of the planet.
+    See 36).
+If you look at figures 1, 6 and 7, the nonaxisymmetric gap structure in the disk near the resonances is always aligned with the planet's orbital phase.
+It is also apparent from figure 1 that the gaps are not aligned with the planet's longitude of pericenter, which should be the case if the structure were due to secular forcing in eccentricity.
+Furthermore, bodies in resonance experience strong precession, which randomizes the orientations of their orbits.
+The gap structure cannot be due to the interface between the secularly forced non-resonant part of the disk, and the randomly oriented pericenters of bodies in resonance.
+The latter explanation was described in Tabeshian & Weigery 2016, which we do not find consistent.
 
@@
 
-    Because its a probability density function. Add some discussion in the text of how we normalized them.
+    Figures 4 and 5 are showing the probability density of the collision rates.
+The curves on these plots are normalized such that the area under the curve = 1.
+For the orange curve in figure 5, the normalization factor is scaled by the ratio between the total number of collisions in each sample.
+Some text has been added alongside the discussion of figures 4 and 5 to explain this.
 
@@
 
-    If we're just talking about planetesimals, however, the inner resonances are more useful. Not sure how much we want to get into looking at drifting small bodies
+    Absolutely true if we are going to consider radial drift.
+Given that an expanded discussion of radial drift is now an important part of this paper, we should be more careful not to dismiss the importance of exterior MMRs.
+TODO: How to change the text to address this?
 

### 2020-10-30 main.tex
More edits, add figure to clarify gravitational focusing explanation

@@
 \citep{scikit-learn} package to construct our KDEs, using a gaussian kernel with a FWHM of 0.02 au.
+\textbf{The curves shown in figure \ref{fig:coll_hist_a} are normalized such that the area underneath is normalized to 1.}
 
@@
 We attribute the production of a bump or a dip at certain semi-major axes to changes in the gravitational focusing factor during two-body encounters.
+\textbf{Rewrite this paragraph to reference figure \ref{fig:gf}.}
 Closer to the star, the planetesimal disc starts off dynamically colder. Here, additional heating from the resonance acts to suppress the gravitational 
@@
 \end{figure}
+
+\begin{figure*}
+\begin{center}
+    \includegraphics[width=\textwidth]{figures/gf_plot.png}
+    \caption{\textbf{The collision rate of bodies in the vicinity of the 3:1 (left) and 2:1 (right) MMRs, relative to the minimum value, as a function of the local eccentricity dispersion.
+The pairs of points connected by lines show the values of the perturbed and unperturbed collision rates in the e1m2, e2m2 and e3m2 simulations.}\label{fig:gf}}
+\end{center}
+\end{figure*}
 
@@
 bodies actually contribute to the radial collision profile, we excluded collisions that fall between $2.495 < a < 2.505$ au (near the 3:1 resonance) and 
-between $3.2 < a < 3.35$ au (near the 2:1 resonance), which is shown by the dashed curve. Qualitatively, none of the bump or dip features present 
+between $3.2 < a < 3.35$ au (near the 2:1 resonance), which is shown by the dashed curve.
+\textbf{As in figure \ref{fig:coll_hist_a}, the solid curves are normalized such that the area underneath is equal to 1.
+For the dashed curves, the normalization factor is scaled down according to the total number of collisions in the entire sample and the number of collisions in the subsample which excludes the collisions in resonance.} Qualitatively, none of the bump or dip features present
 are removed by making this exclusion. This suggests that the features near resonance seen in semimajor axis space become smeared out in 

### 2020-10-30 makeFig.py

@@ -997,6 +997,93 @@ def make_alma_profile():
 
 	plt.savefig(file_str, format=fmt, bbox_inches='tight')
 
+def make_gf_plot():
+	file_str = 'figures/gf_plot.' + fmt
+	if not clobber and os.path.exists(file_str):
+		return
+
+	# pl_e1 and pl_e2
+
+	m_pl = pl_e['mass'][1]
+	R_pl = pl_e['eps'][1]*2
+	v_mut_esc = np.sqrt(2*m_pl/R_pl)
+
+	ecc_vals = np.logspace(-2.9, -1.3)
+
+	fig, axes = plt.subplots(figsize=(16,5), ncols=2, sharex=True, sharey=True)
+
+	pl = pl_e1
+	ax = axes[0]
+	vrel_vals_31 = ecc_vals*np.sqrt(1/res_dist[1])
+	cross_31 = (1+v_mut_esc**2/vrel_vals_31**2)*vrel_vals_31
+	ax.plot(ecc_vals, cross_31/np.min(cross_31))
+
+	mask = np.logical_and(pl['a'] > 2.2, pl['a'] < 2.3)
+	e_0_31 = np.std(pl['e'][mask])
+	mask = np.logical_and(pl['a'] > 2.48, pl['a'] < 2.52)
+	de31 = np.std(pl['e'][mask])
+
+	ax.plot([e_0_31, de31], [np.interp(e_0_31, ecc_vals, cross_31/np.min(cross_31)), \
+	              np.interp(de31, ecc_vals, cross_31/np.min(cross_31))], ls='--', marker='o', color='#1f77b4')
+
+	pl = pl_e
+	mask = np.logical_and(pl['a'] > 2.2, pl['a'] < 2.3)
+	e_0_31 = np.std(pl['e'][mask])
+	mask = np.logical_and(pl['a'] > 2.48, pl['a'] < 2.52)
+	de31 = np.std(pl['e'][mask])
+
+	ax.plot([e_0_31, de31], [np.interp(e_0_31, ecc_vals, cross_31/np.min(cross_31)), \
+	              np.interp(de31, ecc_vals, cross_31/np.min(cross_31))], ls='-.', marker='o', color='#1f77b4')
+
+	pl = pl_e2
+	mask = np.logical_and(pl['a'] > 2.2, pl['a'] < 2.3)
+	e_0_31 = np.std(pl['e'][mask])
[…]

### 2020-11-02 main.tex
Rework abstract and end of introduction, outline discussion of relevant timescales in section 2

@@
 that directly resolve collisions between planetesimals to investigate the collision rate profile near mean-motion resonances with the planet. We 
-find that a distinct bump or dip feature is produced in the collision profile, the presence of which depends on the libration width of the resonance, 
-compared with the peri- and apocenter distances of the edges of the resonance. These quantities encode information about the mass and eccentricity 
-of the planet, and therefore these features in the collision profile place constraints on the orbital properties of the planet. Under the simplifying 
-assumption that the resulting dust distribution directly traces the collision profile, we find that a distinct over- or under-density in the dust emission 
-is produced at the interior 2:1 mean-motion resonance, which can be used to constrain the mass and eccentricity of the planet.}
+find that a distinct bump or dip feature is produced in the collision profile, the presence of which depends on the libration width of the resonance and the 
+separation between the peri and apocenter distances of the edges of the resonance. In the collision profile, the presence of one of these two features
+limits possible values for the mass and eccentricity of the planet. Under the simplifying assumption that the radial profile of the dust emission in the disc
+traces the collision profile, we show that a bump or dip feature in the dust emission near the interior 2:1 mean-motion resonance could be used to place constraints
+on the orbital properties of the perturbing planet. So long as radial drift does not play a significant role in the collisional cascade that grinds planetesimals down to
+dust, this feature in the dust emission should be marginally observable in nearby protoplanetary disks with ALMA.}
 \end{abstract}
@@
 
-\citet{2013ApJ...777L..31D} showed that collisional dust that is generated near the gap opened by a giant planet in \textbf{the inner regions of} \sout{planetesimal} \textbf{transition} disc should 
+\citet{2013ApJ...777L..31D} showed that collisional dust that is generated near the gap opened by a giant planet in \textbf{the inner regions of} a \sout{planetesimal} \textbf{transition} disc should 
 produce a distinct observable marker that could be used to infer the presence of the planet. In a followup study, it was found that morphological 
@@
 integration time. With this toolset, we explore the collision rate structure of a planetesimal disc in the vicinity of mean-motion resonances with the planet. In 
-particular, we would like to determine (1) whether MMRs leave a detectable signature in the collisionally-generated dust, and (2) whether these 
+particular, we would like to determine (1) \textbf{What dynamics govern the collision rate profile near MMRs, (2)} whether MMRs leave a detectable signature in the collisionally-generated dust, and \sout{(2)} \textbf{(3)} whether these
 signatures can be used to determine or constrain the orbital properties of the perturbing planet.
@@
 used and describe the initial conditions chosen for five simulations in which a perturbing giant planet is given various masses 
-and eccentricities. Section \ref{sec:results} presents the results of these simulations, and we use the resolved collisions to generate synthetic dust 
-emission profiles that would be detected with observing facilities like ALMA. Next, we show in section \ref{sec:constrain} that a characteristic bump 
+and eccentricities.
+Section \ref{sec:results} presents the results of these simulations \textbf{and we take an in-depth look at the collision rate profiles of the planetesimals near the MMRs.} \sout{, and w} \textbf{In section \ref{sec:constrain}, w}e use the resolved collisions to generate synthetic dust
+emission profiles that would be detected with observing facilities like ALMA \textbf{, under the simplifying assumption that the resulting dust profile traces the collisions of the planetesimals}.
+\sout{Next, we show in section \ref{sec:constrain}} \textbf{Under this assumption, we show} that a characteristic bump
 or dip feature appears in the dust emission near the interior 2:1 MMR, the presence of which depends on the mass and eccentricity of the perturbing 
-planet. We discuss the potential of using this feature to place constraints on the mass and eccentricity of the planet and conclude in section 
+planet.
+If the 2:1 MMR can be identified (presumably by identifying another prominent MMR, such as the 3:1, and measuring the spacing between the two), we discuss the potential of using this feature to place constraints on the mass and eccentricity of the planet\textbf{.
+In addition, we discuss the caveats of connecting the dust and planetesimal collision profiles in such a simple way.} \textbf{Finally, we} conclude in section
 \ref{sec:conclusions}.
@@
 be described by a Rayleigh distribution \citep{1992Icar...96..107I}.
+
+\textbf{Add calculation of secular forcing timescale here}
+
+\subsection{Gas Drag on Planetesimals}
+
+\textbf{Add calculation of gas drag timescale on planetesimals here. Should be much longer than other timescales!}
 
@@
 N-body treatment to better understand how the collision rate varies in the vicinity of a MMR.
+
+\textbf{Move libration timescale here?}
 
@@
 
-All five simulations are evolved for 5,000 years, which is roughly 400 complete orbits of the perturbing planet. Because the effects of the mean 
+\textbf{Consider moving libration timescale to section \ref{sec:dynamics}.} All five simulations are evolved for 5,000 years, which is roughly 400 complete orbits of the perturbing planet.
+Because the effects of the mean
 motion resonances are not built into the initial conditions, the simulations must be run long enough for the distribution of orbital elements to reach 

### 2020-11-12 refereeResponse.txt
Rework abstract and end of introduction, outline discussion of relevant timescales in section 2
Add calculation of secular forcing timescale

@@
 
-    Exactly. Todo: add a clear outline of this in the conclusions
+    This is the correct interpretation. The outline at the end of the introduction now explains this. Todo: add a clear outline of this in the conclusions
 
@@
 While there is certainly evidence that the gaseous component of the outer regions of protoplanetary disks follow alpha = -1, there is little evidence to suggest that this is the case for solids in the inner planet-forming region.
-Although alpha = -1.5 is not motivated by any extrasolar observations, it is compatible with the majority of protoplanetary disk models.
+Although alpha = -1.5 is not motivated by any extrasolar observations, it is compatible with the majority of protoplanetary disk models (see Chiang & Laughlin 2013, also Dai et al.
+2020)
 

### 2020-11-12 main.tex
Add calculation of secular forcing timescale

@@
 
-\textbf{Add calculation of secular forcing timescale here}
+\textbf{The timescale for secular forcing is given by the period at which the free eccentricity cycles in the complex plane.
+The imaginary and real components of the eccentricity of the jth particle are given by \citet{1999ssd..book.....M} (see ch 7, pg 282, equation 7.51)}
+
+\begin{eqnarray}\label{eq:kandh}
+	h_{j} = e_{j1} sin (g_{1} t + \beta_{1}) + e_{j2} sin (g_{2} t + \beta_{2}) \\ \nonumber
+	k_{j} = e_{j1} cos (g_{1} t + \beta_{1}) + e_{j2} cos (g_{2} t + \beta_{2}),
+\end{eqnarray}
+
+\noindent \textbf{where  ($e_{j1}$, $e_{j2}$) and ($g_{1}$ , $g_{2}$) are the corresponding eigenvector components and eigenvalues of the matrix given by \citet{1999ssd..book.....M} (see ch 7, pg 276, equation 7.9 and 7.10, with $\alpha_{12} = \alpha$ and $\bar{\alpha_{12}} = 1$)}
+
+\begin{eqnarray}\label{eq:pert_matrix}
+	A_{jj} = n_{j} \frac{1}{4} \frac{m_{k}}{m_{c} + m_{j}} \alpha b_{3/2}^{(1)} (\alpha) \\ \nonumber
+	A_{jk} = -n_{j} \frac{1}{4} \frac{m_{k}}{m_{c} + m_{j}} \alpha b_{3/2}^{(2)} (\alpha)
+\end{eqnarray}.
+
+\noindent \textbf{Here, $n$ is the mean motion of a body and $m$ is its mass.
+The frequency of the secular forcing is simply the difference of the two eigenvalue frequencies $g_{1} - g_{2}$.
+For the case of a Jupiter mass planet at 5.2 au perturbing a test particle, the timescale for secular forcing is approximately 12,000 years at 3 au.}
 
@@
 width of a resonance can be defined by determining the largest variation in semimajor axis that permits librational, rather than circulatory motion of $\phi$. For 
-second order and higher MMRs, the maximum libration width is given by \sout{equation 8.58} in \citet{1999ssd..book.....M} \text{bf}(ch. 8, pg 338, eq. 8.58) as
+second order and higher MMRs, the maximum libration width is given by \sout{equation 8.58} in \citet{1999ssd..book.....M} \textbf{(ch. 8, pg 338, eq. 8.58} as
 

### 2020-11-12 main.tex
Move libration timescale calculation to section 2, add calculation of gas damping on orbits of planetesimals

@@
 
+\textbf{In mean-motion resonance, the orbital elements of a perturbed body, along with the critical angle described by equation \ref{eq:phi_crit}, will exhibit sinusoidal oscillations.
+In the circular, restricted three-body case, these small amplitude oscillations exhibit a characteristic frequency, given by (see \citet{1999ssd..book.....M} ch 8, pg 332, eq 8.47, with $j_{2} =-p$ and $j_{4} = -q$)}
+
+\begin{equation}\label{eq:lib_time}
+	\omega_{0} = 3 p^{2} C_{r} n e^{\left| -q \right|}.
+\end{equation}
+
+\noindent \textbf{For the most prominent interior mean-motion resonances, including the 2:1 and 3:1, the timescale associated with these oscillations driven by a Jupiter mass planet is  $\sim$ 1,000 - 2,000 years.}
+
 Changes in eccentricity are correlated with changes in semimajor axis according to the Tisserand relation
@@
 
-\textbf{Move libration timescale here?}
+\subsection{Gas Drag on Planetesimals}
+
+\textbf{Over the course of many orbits, the residual gas from the primordial nebula can damp the eccentricities and inclinations of the planetesimals.
+For a planetesimal-sized body, the geometric cross section is much larger than the mean free path of the gas particles and the timescale to damp its eccentricity is given by \citep{1976PThPh..56.1756A}}
+
+\begin{equation}\label{eq:t_edamp}
+    t_{e, damp} = \frac{8 s \rho}{3 e C_{D} \rho_{g} v_{th}},
+\end{equation}
+
+\textbf{\noindent where $m$, $e$ and $s$ are the mass, eccentricity and radius of the planetesimal. $C_{D}$ is a drag coefficient which is of order unity, $
+\rho_{g}$ is the local density of the gas and $v_{th}$ is its thermal speed. At 3 au, the gaseous component of the solar nebula has a density of $4 
+\times 10^{-10}$ g cm$^{-3}$ and a typical thermal speed of $10^{5}$ cm s$^{-1}$ \citep{1981PThPS..70...35H}. For a 100 km body with a 
+density of 2 g cm$^{-3}$ and an eccentricity of 0.1, the damping timescale is on the order of $10^{5}$ years.
+This is much longer than the timescales related to secular forcing and libration near mean-motion resonances, as discussed above, but shorter than the typical protoplanetary disk lifetime and potentially the planetesimal formation timescale.
+For this reason, we do not model the effects of gas drag, although we consider its effects when constructing initial conditions for our simulations, which is discussed next.}
 
@@
 motion resonances are not built into the initial conditions, the simulations must be run long enough for the distribution of orbital elements to reach 
-equilibrium near the resonances before the collision rate is measured. The libration timescale, which describes how long the critical angle (and also 
+equilibrium near the resonances before the collision rate is measured.
+\textbf{TODO: Remove this, discussion of libration timescale has been moved to section \ref{sec:dynamics}}.
+The libration timescale, which describes how long the critical angle (and also
 the semimajor axis and eccentricity) of a planetesimal in resonance takes to undergo a full oscillation is given by (see equation 8.47 in \citet{1999ssd..book.....M})
-\begin{equation}\label{eq:lib_time}
+\begin{equation}\label{eq:lib_time_old}
 	T_{lib} = \frac{2 \pi}{3 q^{2} C_{r} n e^{\left| -q \right|}},
@@
 To construct a radial dust profile from the collision statistics, we begin by making the assumption that any dust generated by collisions is strongly 
-coupled to the gas. For a dust grain larger than the mean free path of the gas particles, the timescale to damp its eccentricity is given by 
+coupled to the gas.
+\textbf{TODO: Shorten this a bit, since we introduce this timescale in section \ref{sec:dynamics}.} For a dust grain larger than the mean free path of the gas particles, the timescale to damp its eccentricity is given by
 \citep{1976PThPh..56.1756A}

### 2020-11-17 main.tex
Finish updating section 2

@@
 
+\textbf{We begin by providing a description of the dynamical effects responsible for shaping the orbital distribution of the planetesimals.
+The purpose of this is twofold: (1) to motivate the initial conditions used for the simulations described in section \ref{sec:ics} and (2) to justify the exclusion of certain physical effects from our simulations.
+Here, we focus solely on the physics relevant for full-sized ($\sim$100 km) planeteismals and leave a discussion of the effects on smaller bodies generated through collisions for section \ref{sec:dust}.}
+
 \subsection{Secular Forcing}\label{sec:sec_force}
@@
 For the case of a Jupiter mass planet at 5.2 au perturbing a test particle, the timescale for secular forcing is approximately 12,000 years at 3 au.}
-
-\subsection{Gas Drag on Planetesimals}
-
-\textbf{Add calculation of gas drag timescale on planetesimals here. Should be much longer than other timescales!}
 
@@
 
-\subsection{Where Does the Dust End Up?}
+\subsection{Where Does the Dust End Up?}\label{sec:dust}
 

### 2020-11-17 main.tex
Edits getting a little messy, get rid of strikethrough and just show changes in bold

@@
 diagnostics for the physical processes that drive the evolution of the discs. In many gas-rich systems, these gap features are argued to indicate the 
-presence of a giant planet, either embedded in the disc \citep{2015MNRAS.453L..73D} or orbiting \sout{externally} \textbf{adjacent to it}, although the details of gas-dust 
+presence of a giant planet, either embedded in the disc \citep{2015MNRAS.453L..73D} or orbiting \textbf{adjacent to it}, although the details of gas-dust 
 interactions can have strong effects on the resulting morphologies
@@
 
-\citet{2013ApJ...777L..31D} showed that collisional dust that is generated near the gap opened by a giant planet in \textbf{the inner regions of} a \sout{planetesimal} \textbf{transition} disc should 
+\citet{2013ApJ...777L..31D} showed that collisional dust that is generated near the gap opened by a giant planet in \textbf{the inner regions of} a \textbf{transition} disc should 
 produce a distinct observable marker that could be used to infer the presence of the planet. In a followup study, it was found that morphological 
@@
 integration time. With this toolset, we explore the collision rate structure of a planetesimal disc in the vicinity of mean-motion resonances with the planet. In 
-particular, we would like to determine (1) \textbf{What dynamics govern the collision rate profile near MMRs, (2)} whether MMRs leave a detectable signature in the collisionally-generated dust, and \sout{(2)} \textbf{(3)} whether these
+particular, we would like to determine (1) \textbf{What dynamics govern the collision rate profile near MMRs, (2)} whether MMRs leave a detectable signature in the collisionally-generated dust, and \textbf{(3)} whether these
 signatures can be used to determine or constrain the orbital properties of the perturbing planet.
@@
 and eccentricities.
-Section \ref{sec:results} presents the results of these simulations \textbf{and we take an in-depth look at the collision rate profiles of the planetesimals near the MMRs.} \sout{, and w} \textbf{In section \ref{sec:constrain}, w}e use the resolved collisions to generate synthetic dust
-emission profiles that would be detected with observing facilities like ALMA \textbf{, under the simplifying assumption that the resulting dust profile traces the collisions of the planetesimals}.
-\sout{Next, we show in section \ref{sec:constrain}} \textbf{Under this assumption, we show} that a characteristic bump
+Section \ref{sec:results} presents the results of these simulations \textbf{and we take an in-depth look at the collision rate profiles of the planetesimals near the MMRs.
+In section \ref{sec:constrain}, w}e use the resolved collisions to generate synthetic dust
+emission profiles that would be detected with observing facilities like ALMA \textbf{, under the simplifying assumption that the resulting dust profile traces the collisions of the planetesimals.
+Under this assumption, we show} that a characteristic bump
 or dip feature appears in the dust emission near the interior 2:1 MMR, the presence of which depends on the mass and eccentricity of the perturbing 
@@
 width of a resonance can be defined by determining the largest variation in semimajor axis that permits librational, rather than circulatory motion of $\phi$. For 
-second order and higher MMRs, the maximum libration width is given by \sout{equation 8.58} in \citet{1999ssd..book.....M} \textbf{(ch. 8, pg 338, eq. 8.58} as
+second order and higher MMRs, the maximum libration width is given by \citet{1999ssd..book.....M} \textbf{(ch. 8, pg 338, eq. 8.58} as
 
@@
 All of the simulations we perform use a node opening criterion of $\theta_{BH}$ = 0.7. More information about the code can be found 
-in \citet{2008IEEEpds...ChaNGa}. \sout{We have also recently modified {\sc ChaNGa} to handle solid-body collisions. A full description of 
-the collision module implementation can be found in }\citet{2019MNRAS.489.2159W}.
+in \citet{2008IEEEpds...ChaNGa}.
 
@@
 is a ``nominal'' case, in which the perturbing planet's mass and 
-eccentricity are set to that of Jupiter's. In the other four cases, the mass \textbf{or eccentricity is altered} \sout{(eccentricity) is increased or decreased} by a factor of two \sout{, while the 
-eccentricity (mass) is held at} \textbf{from} the nominal value. In all cases, the perturbing giant is placed on a 5.2 au orbit around a 1 $M_{\odot}$ star. The 
+eccentricity are set to that of Jupiter's.
+In the other four cases, the mass \textbf{or eccentricity is altered} by a factor of two \textbf{from} the nominal value.
+In all cases, the perturbing giant is placed on a 5.2 au orbit around a 1 $M_{\odot}$ star.
+The
 planetesimal disc extends from 2.2 to 3.8 au, which covers the two most prominent mean-motion resonances with the giant planet, the 2:1 at 3.27 au 
@@
 300 km.
-\sout{This corresponds to a disc containing roughly 500,000 bodies.} \textbf{This choice of parameters for the planetesimal disk is meant to follow the setup used in simulation B by \citet{2000Icar..143...45R}.
+\textbf{This choice of parameters for the planetesimal disk is meant to follow the setup used in simulation B by \citet{2000Icar..143...45R}.
 One difference from the aformentioned study is that we use a narrower annulus, which reduces the number of particles required from $10^6$ down to roughly 500,000.
@@
 \citet{2000Icar..143...45R}, who simulated a similar setup and found no discernible features near the MMRs. We attribute the differences to a more 
-conservative timestepping criterion in our simulations. The most prominent features appear as \sout{an enhancement to} \textbf{a local maximum in} the collision rate near the 2:1 
-MMR and a \sout{decrease} \textbf{local minimum} near the 3:1 MMR. At higher forced eccentricities, features near the 5:2, \sout{7}\textbf{8}:3 and 5:3 resonances are also visible, due to the 
+conservative timestepping criterion in our simulations. The most prominent features appear as \textbf{a local maximum in} the collision rate near the 2:1 
+MMR and a \textbf{local minimum} near the 3:1 MMR. At higher forced eccentricities, features near the 5:2, \textbf{8}:3 and 5:3 resonances are also visible, due to the 
 steep sensitivity of higher order resonant perturbations to eccentricity \citep{1994PhyD...77..289M}.

### 2020-11-17 main.tex
Remove calculation of libration timescale in section 4

@@
 
-\subsection{Mean-Motion Resonances}
+\subsection{Mean-Motion Resonances}\label{sec:mmr}
 
@@
 
-\textbf{Consider moving libration timescale to section \ref{sec:dynamics}.} All five simulations are evolved for 5,000 years, which is roughly 400 complete orbits of the perturbing planet.
-Because the effects of the mean
+All five simulations are evolved for 5,000 years, which is roughly 400 complete orbits of the perturbing planet. Because the effects of the mean 
 motion resonances are not built into the initial conditions, the simulations must be run long enough for the distribution of orbital elements to reach 
 equilibrium near the resonances before the collision rate is measured.
-\textbf{TODO: Remove this, discussion of libration timescale has been moved to section \ref{sec:dynamics}}.
-The libration timescale, which describes how long the critical angle (and also
-the semimajor axis and eccentricity) of a planetesimal in resonance takes to undergo a full oscillation is given by (see equation 8.47 in \citet{1999ssd..book.....M})
-\begin{equation}\label{eq:lib_time_old}
-	T_{lib} = \frac{2 \pi}{3 q^{2} C_{r} n e^{\left| -q \right|}},
-\end{equation}
-
-\noindent for small-amplitude librations. For all five sets of initial conditions used, $T_{lib} \sim$ 1,000 - 2,000 years for the 3:1 and 2:1 resonances. 
-For this reason, we allow each simulation to run for 2,000 years before we begin recording any collision statistics. \textbf{Although the integration time we use
-is only a tiny fraction of the Myr timescales that a typical protoplanetary disk lives for (citation?), 5,000 years is sufficient to allow all of the relevant dynamics here.
-As discussed above in section \ref{sec:ics}, the initial conditions are constructed so that relevant effects with longer timescales (such as gravitational stirring, gas drag on planetesimals and secular forcing) are already in equilibrium.}
+\textbf{To do so, we allow each simulation to run for 2,000 years before we begin recording any collision statistics.
+This is comparable to the libration period (calculated in section \ref{sec:mmr} for the 3:1 and 2:1 resonances.
+Although one might worry that a single libration period may not be enough for the orbital structure due to the resonances to develop, we find that the shape of the semimajor axis-eccentricity distribution of the planetesimals reaches a steady state by this time.
+This is largely due to the fact that there are enough bodies in or near the resonances to allow an ensemble average of phase space, rather a time average.
+Additionally, we find that the time evolution of the collision rate near the resonances maintains a steady state in all five simulations after $\sim$ 2000 years.}
 

### 2020-11-23 main.tex
Add explain of (new) figure 5

@@
 preserve the Jacobi energy, equation \ref{eq:tiss} predicts that these spikes will tend to curve away from the perturbing body. This lowers the 
-surface density of the disc near the locations of resonances, while producing a pileup of bodies on eccentric orbits adjacent to the MMR. The 
+surface density of the disc near the locations of resonances, while producing a pileup of bodies on eccentric orbits adjacent to the MMR.
+\textbf{TODO: split this into a separate section, discussion the safronov collision rate} The
 enhanced surface density will increase the collision rate. At the same time, the large eccentricites will either lower the collision rate due to the decreased 
@@
 
-We attribute the production of a bump or a dip at certain semi-major axes to changes in the gravitational focusing factor during two-body encounters.
-\textbf{Rewrite this paragraph to reference figure \ref{fig:gf}.}
-Closer to the star, the planetesimal disc starts off dynamically colder. Here, additional heating from the resonance acts to suppress the gravitational 
-focusing cross section, which reduces the collision rate from its
-non-perturbed value. Further out in the disc, where the unperturbed
-encounter velocity is higher, the gravitational focusing cross section
-is already minimized. Any additional heating instead acts to simply
-increase the encounter rate between bodies, which enhances the
-collision rate. This explains the relative drop in the collision rate
+\textbf{Although the features in figure \ref{fig:coll_hist_a} near the 3:1 and 2:1 MMRs appear qualitatively different, they can be explained by one single dynamical process.
+As discussed in section (FILL IN LATER), the collision rate between planetesimals depends on both the encounter rate and the strength of gravitational focusing.
+The encounter rate grows as the relative velocity $v$ between the planetesimals increases, while gravitational focusing is most effective for bodies with small relative velocities.
+There is therefore an intermediate value of $v$ for which the average collision rate $\left< \sigma v \right>$ is at a minimum, which we will refer to as  $\left< \sigma v \right>_{0}$.
+The dynamical excitation induced by a mean motion resonance can either increase or decrease the local average collision rate, depending on the size and mass of the planetesimals, along with their unperturbed relative velocites.}
+
+\textbf{In figure \ref{fig:gf}, we show the effect that the 2:1 MMR and 3:1 MMR have on the local average collision rate.
+Each pair of points connected by a line represents the average collision rate before (from the initial condition file) and after (around T = 2,000 yr) the effects of the mean-motion resonances develop.
+In this figure, the relative velocity between bodies is calculated by measuring the eccentricity and inclination dispersion near each resonance and using $v = \sqrt{\left< e^{2} \right> + \left< i^{2} \right>} v_{k}$ \citep{1993ARA&A..31..129L}, where $v_{k}$ is the Keplerian velocity.
+Here, we assume that the eccentricity and inclination dispersions are coupled and use the eccentricity as the independent variable.
+Because both the strength of secular forcing and the effects of the resonant perturbations are different near the 3:1 and 2:1 MMRs, the planetesimal population at each of these locations in the disk experiences a qualitatively different change in the collision rate.
+Near the 3:1 MMR, the unperturbed collision rate is well below the minimum value $\left< \sigma v \right>_{0}$ and the dynamical heating introduced by the resonance acts to suppress the collision rate further.
+Further out in the disk, near the 2:1 MMR, the collision rate starts out much closer to the minimum value and the additional perturbations drive the collision rate upwards.}
+
+\textbf{ This explains the relative drop in the collision rate
 near the 3:1 MMR and the relative increase near the 2:1 and 5:3
-resonances. Although this could potentially serve as a useful
-diagnostic of the planetesimal size in a disc (because the mutual
-escape velocity sets how dynamically hot the bodies can get before
-gravitational focusing is suppressed), a direct measurement of the
+resonances \textbf{seen in figure \ref{fig:coll_hist_a}}. Although this could potentially serve as a useful
+diagnostic of the planetesimal size in a disc (because the\textbf{size and mass of the planetesimals set the eccentricity dispersion at which $\left< \sigma v \right>$ is minimized}), a direct measurement of the
 semimajor axes of the colliding planetesimals is not
-possible. Furthermore, as we will demonstrate next, collisions due to bodies in resonance do not have a significant effect on the final shape of the radial dust distribution.
+possible. Furthermore, as we will demonstrate next, collisions due to bodies in resonance do not have a significant effect on the final shape of the radial dust distribution.}
 

### 2020-11-24 main.tex
Add subsection discussing safronov collision rate

@@
 surface density of the disc near the locations of resonances, while producing a pileup of bodies on eccentric orbits adjacent to the MMR.
-\textbf{TODO: split this into a separate section, discussion the safronov collision rate} The
-enhanced surface density will increase the collision rate. At the same time, the large eccentricites will either lower the collision rate due to the decreased 
-effectiveness of gravitational focusing, or raise it due to the more vigorous encounter rate, depending on the magnitude of the encounter velocity relative to 
-the escape velocity of the planetesimals. In addition, the MMRs cause the orbits of planetesimals to precess on relatively short 
-timescales, which effectively randomizes their longitudes of perihelion. In a secularly forced disc, there will be an interface between aligned 
-and randomly oriented orbits at the edge of the resonance. Due to the complicated dynamics that are at play in this region, we turn to a direct 
-N-body treatment to better understand how the collision rate varies in the vicinity of a MMR.
+
+\subsection{Collisions Between Planetesimals}
+
+\textbf{A simple analytic model of the collision rate of a planetesimal population is given by \citet{1969edo..book.....S} as}
+
+\begin{equation}\label{eq:saf}
+	n \sigma v = n \pi s^{2} \left( 1 + 2 G m / s v^{2} \right) v,
+\end{equation}
+
+\textbf{\noindent where $n$ is the number density of the population, $s$ and $m$ are the radii and masses of the bodies and $v$ is their typical encounter velocity.
+The encounter velocity is often described in terms of the rms eccentricity $\left<e^{2}\right>^{1/2}$ and inclination $\left<i^{2}\right>^{1/2}$ of the population (e.g.
+\citet{1993ARA&A..31..129L}) as}
+
+\begin{equation}\label{eq:eccincvel}
+	v = \sqrt{\left< e^{2} \right> + \left< i^{2} \right>} v_{k},
+\end{equation}
+
+\textbf{\noindent where $v_{k}$ is the local Keplerian velocity.
+The second term in equation \ref{eq:saf} can be thought of as an additional enhancement to the collision cross section due to gravitational focusing.
+When the typical encounter velocity is small compared to the mutual escape velocity of the planetesimals, the collision cross section greatly exceeds the geometric value.
+Another important feature of equation \ref{eq:saf} is that for a fixed value of $n$, the collision rate has a global minimum as a function of $v$.
+For small $v$, gravitational focusing allows for more collisions, while for large $v$ the number of encounters simply becomes so large that the collsion rate again increases, even though gravitational focusing does not operate.
+This point will come up again in section \ref{sec:vary_ecc} when we examine the qualitative changes in the collision rate near mean-motion resonances.}
+
+\textbf{Although equation \ref{eq:saf} works well to describe the collision rate for a homogeneous collection of planetesimals, some problems arise when localized regions of commensurabilities are introduced.
+Namely, the resonances cause the orbits of planetesimals to precess, and an interface between secularly aligned and randomly oriented orbits arises on each side of the resonance.
+Additionally, an interface between dynamically cold and hot planetesimals forms at each side.
+For these reasons, an N-body treatment in which collisions are directly resolved is necessary to understand how the collision rate varies near the MMRs.}
 
@@
 \textbf{Although the features in figure \ref{fig:coll_hist_a} near the 3:1 and 2:1 MMRs appear qualitatively different, they can be explained by one single dynamical process.
-As discussed in section (FILL IN LATER), the collision rate between planetesimals depends on both the encounter rate and the strength of gravitational focusing.
+As discussed in section \ref{sec:saf}, the collision rate between planetesimals depends on both the encounter rate and the strength of gravitational focusing.
 The encounter rate grows as the relative velocity $v$ between the planetesimals increases, while gravitational focusing is most effective for bodies with small relative velocities.
@@
 Each pair of points connected by a line represents the average collision rate before (from the initial condition file) and after (around T = 2,000 yr) the effects of the mean-motion resonances develop.
-In this figure, the relative velocity between bodies is calculated by measuring the eccentricity and inclination dispersion near each resonance and using $v = \sqrt{\left< e^{2} \right> + \left< i^{2} \right>} v_{k}$ \citep{1993ARA&A..31..129L}, where $v_{k}$ is the Keplerian velocity.
-Here, we assume that the eccentricity and inclination dispersions are coupled and use the eccentricity as the independent variable.
+In this figure, the relative velocity between bodies is calculated by measuring the eccentricity and inclination dispersion near each resonance and using equation \ref{eq:eccincvel}.
+Here, we assume that the eccentricity and inclination dispersions are coupled \citep{1993MNRAS.263..875I} and use the eccentricity as the independent variable.
 Because both the strength of secular forcing and the effects of the resonant perturbations are different near the 3:1 and 2:1 MMRs, the planetesimal population at each of these locations in the disk experiences a qualitatively different change in the collision rate.
@@
 
-To construct a radial dust profile from the collision statistics, we begin by making the assumption that any dust generated by collisions is strongly 
+\textbf{TODO: Introduce this a little mroe gently, start off by acknowledging the limitations of this model} To construct a radial dust profile from the collision statistics, we begin by making the assumption that any dust generated by collisions is strongly
 coupled to the gas.
-\textbf{TODO: Shorten this a bit, since we introduce this timescale in section \ref{sec:dynamics}.} For a dust grain larger than the mean free path of the gas particles, the timescale to damp its eccentricity is given by
-\citep{1976PThPh..56.1756A}
-
-\begin{equation}\label{eq:t_edamp}
-    t_{e, damp} = \frac{8 s \rho}{3 e C_{D} \rho_{g} v_{th}},
-\end{equation}
-
-\noindent where $m$, $e$ and $s$ are the mass, eccentricity and radius of the dust grain. $C_{D}$ is a drag coefficient which is of order unity, $
-\rho_{g}$ is the local density of the gas and $v_{th}$ is its thermal speed. At 3 au, the gaseous component of the solar nebula has a density of $4 
+For a dust grain larger than the mean free path of the gas particles, the timescale to damp its eccentricity is given by \textbf{equation \ref{eq:t_edamp}}.
+At 3 au, the gaseous component of the solar nebula has a density of $4
 \times 10^{-10}$ g cm$^{-3}$ and a typical thermal speed of $10^{5}$ cm s$^{-1}$ \citep{1981PThPS..70...35H}. For a 1 mm dust grain with a 

### 2020-11-30 main.tex
Finish calculation of collision + drift timescale for 1m bodies

@@
 
-\subsection{Collisions Between Planetesimals}
+\subsection{Collisions Between Planetesimals}\label{sec:colleq}
 
@@
 Additionally, an interface between dynamically cold and hot planetesimals forms at each side.
+All of these effects cause the number density, collision cross section and encounter velocity to spatially vary in a rather abrupt manner.
 For these reasons, an N-body treatment in which collisions are directly resolved is necessary to understand how the collision rate varies near the MMRs.}
 
-\subsection{Gas Drag on Planetesimals}
+\subsection{Gas Drag on Planetesimals}\label{sec:pl_drag}
 
 \textbf{Over the course of many orbits, the residual gas from the primordial nebula can damp the eccentricities and inclinations of the planetesimals.
-For a planetesimal-sized body, the geometric cross section is much larger than the mean free path of the gas particles and the timescale to damp its eccentricity is given by \citep{1976PThPh..56.1756A}}
+For a planetesimal-sized body, the geometric cross section is much larger than the mean free path of the gas particles and the timescale for gas drag to modify its orbit is given by \citep{1976PThPh..56.1756A}}
 
 \begin{equation}\label{eq:t_edamp}
-    t_{e, damp} = \frac{8 s \rho}{3 e C_{D} \rho_{g} v_{th}},
+    t_{e, damp} = \frac{2 m_{pl}}{C_{D} \pi s_{pl}^{2} \rho_{g} v_{g}},
 \end{equation}
 
-\textbf{\noindent where $m$, $e$ and $s$ are the mass, eccentricity and radius of the planetesimal. $C_{D}$ is a drag coefficient which is of order unity, $
-\rho_{g}$ is the local density of the gas and $v_{th}$ is its thermal speed. At 3 au, the gaseous component of the solar nebula has a density of $4 
-\times 10^{-10}$ g cm$^{-3}$ and a typical thermal speed of $10^{5}$ cm s$^{-1}$ \citep{1981PThPS..70...35H}. For a 100 km body with a 
-density of 2 g cm$^{-3}$ and an eccentricity of 0.1, the damping timescale is on the order of $10^{5}$ years.
+\textbf{\noindent where $m_{pl}$ and $s_{pl}$ are the mass and radius of the planetesimal. $C_{D}$ is a drag coefficient which is of order unity, $
+\rho_{g}$ is the local density of the gas and $v_{g}$ is the headwind velocity of the gas experienced by the planetesimal. At 3 au, the gaseous component of the solar nebula has a density of $4 
+\times 10^{-10}$ g cm$^{-3}$ and the typical headwind experienced by a body on a Keplerian orbit is $\sim 5000$ cm s$^{-1}$ \citep{1981PThPS..70...35H}. For a 100 km body with a 
+density of 2 g cm$^{-3}$ and an eccentricity of 0.1, the stopping timescale is on the order of $10^{6}$ years.
 This is much longer than the timescales related to secular forcing and libration near mean-motion resonances, as discussed above, but shorter than the typical protoplanetary disk lifetime and potentially the planetesimal formation timescale.
@@
 \textbf{Although the features in figure \ref{fig:coll_hist_a} near the 3:1 and 2:1 MMRs appear qualitatively different, they can be explained by one single dynamical process.
-As discussed in section \ref{sec:saf}, the collision rate between planetesimals depends on both the encounter rate and the strength of gravitational focusing.
+As discussed in section \ref{sec:colleq}, the collision rate between planetesimals depends on both the encounter rate and the strength of gravitational focusing.
 The encounter rate grows as the relative velocity $v$ between the planetesimals increases, while gravitational focusing is most effective for bodies with small relative velocities.
@@
 
-\textbf{TODO: Introduce this a little mroe gently, start off by acknowledging the limitations of this model} To construct a radial dust profile from the collision statistics, we begin by making the assumption that any dust generated by collisions is strongly
-coupled to the gas.
-For a dust grain larger than the mean free path of the gas particles, the timescale to damp its eccentricity is given by \textbf{equation \ref{eq:t_edamp}}.
-At 3 au, the gaseous component of the solar nebula has a density of $4
-\times 10^{-10}$ g cm$^{-3}$ and a typical thermal speed of $10^{5}$ cm s$^{-1}$ \citep{1981PThPS..70...35H}. For a 1 mm dust grain with a 
+To construct a radial dust profile from the collision statistics, we begin by making \textbf{two assumptions: 1.
+any dust generated by collisions is strongly coupled to the gas and 2.
+any subsequent spatial evolution of the collisional debris is insignificant.}\textbf{So long as both of these assumptions are true, we can use the locations of planetesimal collisions in the plane of the disk to generate a dust profile for each simulation.}
+
+\textbf{We first provide a justification for assumption (1), which is as follows:} For a dust grain larger than the mean free path of the gas particles, the timescale to damp its eccentricity is given by \citep{1976PThPh..56.1756A}
+
+\begin{equation}\label{eq:t_edamp}
+    t_{e, damp} = \frac{8 s \rho}{3 e C_{D} \rho_{g} v_{th}},
+\end{equation}
+
+\noindent where $m$, $e$ and $s$ are the mass, eccentricity and radius of the dust grain. $C_{D}$ is a drag coefficient which is of order unity, $
+\rho_{g}$ is the local density of the gas and $v_{th}$ is its thermal speed.\textbf{Using the same values for the properties of the solar nebula as we did in section \ref{sec:pl_drag} and assuming} a 1 mm dust grain with a
 density of 1 g cm$^{-3}$ and an eccentricity of 0.05, the damping timescale is $4 \times 10^{-3}$ years. This is orders of magnitude smaller than the 
@@
 
-Operating under this assumption\footnote{As discussed in \cite{2017ApJ...850..103B}, the local generation of second-generation dust is only one 
+\textbf{Assumption (2) is less straightforward to justify and may not be reasonable in all cases.
+Although the spatial redistribution of the full-sized planetesimals and mm-sized dust grains is insignificant, the radial drift forces experienced by intermediate-sized bodies is much greater.
+Collisions between planetesimals do not immediately convert the mass to dust grains.
+Rather, the debris will undergo a collisional cascade process, which gradually grinds the resulting bodies down to smaller and smaller sizes.
+A proper treatment of the collisional cascade process, unfortunately, is quite complicated and is well beyond the scope of this work.
+However, one can safely ignore this process if the peak radial drift timescale is longer than the timescale for collisions between bodies that experience maximal radial drift.}
+
+\textbf{In the inner part of the solar nebula, radial drift is maximized for meter-sized bodies.
+Following our same calculation in \ref{sec:pl_drag} with a 1 m body, we find that an object of this size will drift across the 2:1 MMR on a timescale of $\sim$ 300 years.
+Although we do not model collisions between bodies of this size, an upper limit on the collision timescale for 1 m bodies can be obtained by extrapolating the planetesimal collision rate measured in our simulations down to smaller-sized objects.
+For the e2m2 simulation, we find that 125 collisions occur withing the libration width of the 2:1 MMR during the 3,000 time window that collisions are recorded.
+There are 15,000 total planetesimals within this region, which means that a given planetesimal undergoes a collision every $\sim$ 370,000 years on average.
+If the entire planetesimal population in this region were converted to 1 meter bodies of the same bulk density, the collision timescale would decrease to $\sim$ 1 year.
+The number density of bodies increases by a factor of $10^{15}$, while the geometric collision cross section decreases by a factor of $10^{10}$.
+Additionally, the 1 meter bodies will not experience gravitational focusing like the planetesimals, but this only alters the collision timescale by a factor of order unity.
+From this crude calculation, we conclude that the collision timescale for bodies that experience maximal radial drift is smaller than their drift timescale.
+Therefore, our descision to ignore the spatial redistribution of the collisional debris is not entirely unfounded, although we would like to emphazise that the collision timescale estimated above is strictly a lower limit.}
+
+Operating under \textbf{these assumptions} \footnote{As discussed in \cite{2017ApJ...850..103B}, the local generation of second-generation dust is only one 
 consideration. The dust will also evolve spatially due to drag effects, but can also evolve in size or be re-accreted onto planetesimals. For simplicity, 

### 2020-12-02 main.tex
Add another disclaimer about collisional grinding at the end of section 5

@@
 The dashed lines shown the collision profile with collisions between bodies in resonance removed.
-The bump and dip features remain qualitatively the same, which suggests that they are produced by bodies outside of resonance.\label{fig:coll_hist_r}}
+The bump and dip features remain qualitatively the same, which suggests that they are produced by bodies \textbf{outside of the libration width of the resonance.}\label{fig:coll_hist_r}}
 \end{center}
@@
 
-This also suggests that the prominent bumps and dips seen in figure \ref{fig:coll_hist_r} are mainly produced by bodies outside of resonance, although 
+This also suggests that the prominent bumps and dips seen in figure \ref{fig:coll_hist_r} are mainly produced by bodies outside of \textbf{the libration width of the} resonance, although 
 the resonant population does make some of the features more pronounced. To further understand this, we consider the nonaxisymmetric structure 
@@
 \citet{2016ApJ...818..159T} provide a different explanation for this phenomenon, suggesting that the nonaxisymmetric structure is the product 
-of the path that a resonant test particle takes in a frame co-rotating with the planet (see figure 8.4 of \citet{1999ssd..book.....M}). This explanation, 
+of the path that a resonant test particle takes in a frame co-rotating with the planet (see figure 8.4 of \citet{1999ssd..book.....M}).
+\textbf{In other words, the gap structure is argued to simply be due to the interfaces between the low eccentricity, non-resonant and high eccentricity resonant regions of the disc.} This explanation,
 however, does not hold for a large collection of planetesimals, especially when there is no forced eccentricity. In such a case, the orbits of 
@@
 
+\textbf{We would again like to emphasize that the dust emission profiles in figure \ref{fig:alma_profiles} are constructed upon the assumption that the radial dust structure closely traces the collision profile of the planetesimals.
+This is only the case if the collisional cascade from which the dust grains form happens before radial drift has a chance to move debris away from the resonances.
+Although we showed with a back-of-the-envelope calculation that this is plausible for a typical protoplanetary disk with properties similar to the protosolar nebula, a more thorough treatment of collisional grinding is necessary to be able to interpret the dust emission profiles presented here as anything more than upper limits.}
+
 \section{Summary and Conclusions}\label{sec:conclusions}

### 2020-12-03 refereeResponse.txt
More edits

@@
 
-    This is the correct interpretation. The outline at the end of the introduction now explains this. Todo: add a clear outline of this in the conclusions
+    This is the correct interpretation.
+The paper outline at the end of the introduction now explains this.
+In addition, there is a step-by-step description of this process toward the end of section 6.
 
@@
 
-    The planetesimal dynamics presented in the work are equally applicable to gas rich and gas poor systems.
-However, the orbital structure of the dust and the constraints it would place on the properties of the giant planet are much less clear.
-We have reframed this paper draft to make the measurement of the perturbing planet's properties less of a central point and therefore discussing debris disks in the introduction is relevant.
+	Although the presence of gas is necessary in order to justify a simple, tractable model for connecting the planetesimal collision profile to the dust profile, the dynamics of the planetesimals and the behavior of the collision profile does not depend very strongly on the gas.
+In a debris disk, it is certainly going to be more difficult to make this connection, but the behavior of the planetesimals should be quite similar.
 
@@
 
-    The Dobinson et al. 2013 work modeled the inner gas poor region of a transition disk. The term 'planetesimal disk' in our introdution was changed to 'inner part of a transition disk'.
+    The Dobinson et al.
+2013 work modeled the inner, gas-poor region of a transition disk.
+The term 'planetesimal disk' in our introdution was changed to 'inner part of a transition disk' to make this more clear.
 
@@
 
-    TODO: I think the better thing to do is reframe the abstract. Highlight more about the dynamics, and leave the stuff about gas and the dust structure to the end.
+	We have made edits to the abstract, introduction and conclusion to place more emphasis on the behavior of the planetesimals, which should be similar in both a protoplanetary disk and a debris disk.
+As we show in section 2.4 (newly added), the gas has an incredibly weak effect on the planetesimals.
+As the referee has pointed out, our model for the interaction between the collisional debris and the gas is extremely simple.
+Given that we are placing more focus on the full-sized planetesimals, we do not think it is necessary to focus solely on the gas disk phase.
 
@@
 
-   TODO: Might be good to add a section discussing gas drag here. Also - I had an analytic derivation of collision rates in an earlier draft - I guess I'll add it back in.
+   Two subsections have been added to section 2 which discuss both gas drag on planetsimals and collisions between planetesimals.
 
@@
 
-    TODO: Add clarification: although we don't model gas drag here, the ICs need to start in eqilibrium.
-The viscous stirring time is much longer than any of the other relevant timescales resolved in the simulation, so it is sufficient for us to calculate what <e^2>^{1/2} would be if there were gas around.
+    This is now clarified at the end of section 2.4 (gas drag on planetesimals) and in section 3.2 (initial conditions).
+The idea is that we consider gas drag when building the initial conditions, but do not need directly model its effects during the simulations because the gas drag and viscous stirring timescale is much longer than the simulation timescale.
+We assume that these two effects are in equilibrium, build them into the initial conditions and then can safely forget about them.
 
@@
 
-    Be sure to add chapter, page number and eq number after all M+D equations.
-The main purpose of this section is to explain how we calculated resonances widths that were used in the later parts of the paper.
-Go back through and make sure each of the equations presented is referenced later in the paper.
-Remove ones that arent
+	Chapter, page number and equation number have now been added alongside all equations pulled from Murray and Dermott.
+Although a bit long, the main purpose of this section is to 'show our work' when deriving the secular forcing timescale and libration widths used later in the paper.
+(Should shorten this or move it to an appendix?)
 
@@
     The argument should indeed by -q, rather than -(2p+q).
-This mistake was carried through when writing up the equations in the paper, although it appears we properly used j4 = -q when doing our analysis and constructing plots.
-(2p+q) has been replaced by q in equations 5 and 6 in the paper (also need to fix 14).
+This mistake was carried through when writing up the equations in the paper, although it appears we properly used j4 = -q when doing our analysis and constructing the plots.
+(2p+q) has been replaced by q in equations 5 and 6 in the original draft (equations 7 and 8 in the revised version).
 
@@
 
-    This section is meant to focus solely on the dynamical effects that the planet has on the full-sized planetesimal population.
-We will save the discussion of what happens to the debris from collisions for a 'caveats' section later in the paper.
+    This section is meant to focus solely on the dynamical effects that the planet has on the full-sized planetesimal population, in order to motivate the initial conditions used in the next section, and also to explain the planetesimal collision profiles shown in section 4.1.
+We are purposefully trying to keep discussion of radial drift and collisional debris as a separate, encapsulated part of the paper in the new version.
 
@@
 An additional paragraph has been added which summarizes some of the details provided about the ChaNGa collision model described in Wallace & Quinn 2019.
+TODO: Pull up some PKDGRAV planetesimal studies to reference here.
 
@@
 
-    This sentence has been simplified.
+    Good idea! While this is a little less specific than what we had before, table 1 does a good job of clearing up any ambiguities.
 
@@
 Additionally, the number of timesteps required to measure the collision profile for the exterior MMRs increases with semimajor axis when using alpha steeper than -1.
-TODO: Add a discussion at the end of the paper explaining that exterior MMRs are interesting too.
+We have also added a brief discussion highlighting the importance of studying exterior resonances in the summary and discussion near the end of the paper.
 
@@
     See 19) and 20).
-While there is certainly evidence that the gaseous component of the outer regions of protoplanetary disks follow alpha = -1, there is little evidence to suggest that this is the case for solids in the inner planet-forming region.
+While there is certainly evidence that the gaseous component of the outer regions of protoplanetary disks follow alpha = -1, there is little evidence to confirm that this is the case for solids in the inner planet-forming region.
 Although alpha = -1.5 is not motivated by any extrasolar observations, it is compatible with the majority of protoplanetary disk models (see Chiang & Laughlin 2013, also Dai et al.
-2020)
+2020) and is not uncommonly used in planet formation simulations (TODO: references?)
 
@@
 
-    See our response to concern #4. Some text has been added to the paper to elaborate on this as well.
+    See our response to concern #4. Some text has been added to the paper (at the beginning of section 4) to elaborate on this as well.
 
@@
 
-    We are considering the gas disk phase here, while making the assumption that the effects of for gas drag on the planetesimals is very weak.
-In the initial conditions, we tune dynamical excitation of the planetesimals so that the effects of viscous stirring and gas drag (had we imparted a drag force on the particles in the simulation) are in balance.
-The gravitational stirring time is much longer than 5,000 years, so our planetesimal disk will not suffer from too much dynamical heating because we did not model the gas.
+    See 8).
+We are considering the gas disk phase here, although it shouldn't matter too much in terms of the outcome of the simulations.
 More text has been added to this section to explain this more clearly.
@@
 
-    See 23).
-This is just used to set up the initial conditions.
-Both the gravitational stirring and gas drag time for the planetesimals is much longer than the simulation time (because we do not track the creation of smaller debris) and so we can set the initial conditions and then forget about these effects.
+    See 23). We do not keep track of debris during the simulation. A note has been added to the end of section 3.1 which states this.
 
@@
 
-    In our case, the large particle count allows us to look at the 'ensemble average' of the dynamical behavior near resonance.
-Even though individual planetesimals only go through a few librational periods, the phase trajectories that they follow are well populated and allow us to make conclusions about the dynamics without needing a longer baseline to take time averages.
+    In our case, the large particle count allows us to look at the ensemble average of the dynamical behavior near resonance.
+Even though individual planetesimals only go through a few librational oscillations, the phase trajectories that they follow are well populated with particles.
+This allows us to make conclusions about the dynamics without needing a longer baseline to take time averages.
 Had we been following only a few bodies, this would not have been the case.
@@
 
-    This is referring specifically to the positions of the planetesimals in this figure and not to any observable property.
-Even if the smaller fragments do drift significantly, the nonaxisymmetric gaps in the planetesimals will still be present, although observing full sized planetesimals is next to impossible.
+    This is referring specifically to the positions of the planetesimals in this figure and not to any kind of debris.
+Even if the smaller fragments do drift significantly, the nonaxisymmetric gaps in the planetesimal distribution should still be present.
+Of course, this would be very difficult to observe.
 This sentence has been modified to clarify that we are specifically talking about the structure seen in figure 1.
-A discussion of the referee's concerns about the radial structure of the smaller debris fragments will be added towards the end of the paper.
 
@@
 
-    The libration timescale and the secular forcing timescale are much shorter than the stopping time due to gas for the planetesimals, so this figure should not look different had we modeled gas drag.
-A typo in the text has been, '7:3' was supposed to say '8:3'.
-TODO: Insert a calculation of the stopping time and secular forcing timescale somewhere.
+    As we now derive in section 2, the libration timescale and the secular forcing timescale are much shorter than the stopping time due to gas for the planetesimals, so this figure should not look different had we modeled gas drag.
+A typo in the text has been corrected: '7:3' was supposed to say '8:3'.
 
@@
 
-    PDF stands for probability density function. This is now explained in the text.
+    PDF stands for probability density function. This is now stated in the text.
 
@@
 In figure 4, there is a local minimum near the 3:1 MMR.
-There are certainly some additional features surrounding it, although these are partly due to collisions with eccentric bodies in the adjacent (7:2 and 5:2) MMRs.
+There are certainly some additional features surrounding it, although these are partly due to collisions with bodies on high eccentricity orbits in the adjacent (7:2 and 5:2) MMRs.
 The text has been changed to refer to the features at the 3:1 and 2:1 MMRs as local maxima and minima.
@@
 
-    An additional figure has been added to clarify the gravitational focusing explanation.
-TODO: Update text to go along with figure.
-If the offset in the peak of the collision rate in figure 4 (near the 2:1 MMR, for example) were due to bodies colliding at perihelion, the peak should shift inward as the eccentricity of the planet is increased.
+    An additional figure (fig 5 in the new paper) has been added to clarify the gravitational focusing explanation.
+The basic idea is that both a dynamically cold and a very dynamically hot planetesimal population will exhibit a large collision rate.
+When things are cold, gravitational focusing is highly effective.
+When things are very hot, you get very frequent encounters.
+The collision rate exhibits a minimum value somewhere in between.
+Depending on how dynamically hot the local planetesimal population gets when a resonance heats it up, the collision rate can either increase OR decrease.
+
+    To address the refee's intrepretation: if the offset in the peak of the collision rate in figure 4 (near the 2:1 MMR, for example) were due to bodies colliding at perihelion, the peak should shift inward as the eccentricity of the planet is increased.
 Between the e1m2 and e3m2 simulations, the mean eccentricity at the 2:1 MMR increases from ~0.03 to ~0.06.
@@
 
-    As shown in figure 5, the bump and dip features at the center of the MMRs are still present, even if we ignore particles whose semimajor axis falls within the libration width of the resonances.
-This does not mean, however, that the resonances are not important.
-As we approach the edges of the resonance from the outside, the critical angle approaches a stationary value.
+    As shown in figure 6 (fig 5 in the original version), the bump and dip features at the center of the MMRs are still present, even if we ignore particles whose semimajor axis falls within the libration width of the resonances.
+What this implies is that the EDGES of the resonances are important.
+As we approach a resonance from the outside, the critical angle \phi approaches an unstable equilibirum where it is stationary.
 Where the critical angle is stationary, the pericenter orientations of the planetesimals experience a torque which causes their \varpi to follow the giant planet in its orbit.
@@
 It is also apparent from figure 1 that the gaps are not aligned with the planet's longitude of pericenter, which should be the case if the structure were due to secular forcing in eccentricity.
-Furthermore, bodies in resonance experience strong precession, which randomizes the orientations of their orbits.
-The gap structure cannot be due to the interface between the secularly forced non-resonant part of the disk, and the randomly oriented pericenters of bodies in resonance.
-The latter explanation was described in Tabeshian & Weigery 2016, which we do not find consistent.
+Furthermore, orbits of bodies in resonance experience significant precession, which randomizes their orientations.
+The gap structure cannot be due to the interface between the secularly forced, non-resonant part of the disk, and the randomly oriented orbits of bodies in resonance.
+The latter explanation was given by Tabeshian & Weigert 2016, which, as we point out in our paper, is not adequate.
 
@@
 
-    Already addressed above
+    This is certainly a big if, although we have shown with a back-of-the-envelope calculation in section 4.2 that it could be plausible.
+We have added some additional text to the end of section 5 to remind the reader that the dust profile is built with some shaky assumptions.
 
@@
 
-    Absolutely true if we are going to consider radial drift.
+    This is absolutely true if we are going to consider radial drift.
 Given that an expanded discussion of radial drift is now an important part of this paper, we should be more careful not to dismiss the importance of exterior MMRs.
-TODO: How to change the text to address this?
+Here, we have added a sentence mentioning that exterior MMRs might be pretty important if radial drift is modeled.
 
@@
 
-    Good place to mention caveats brought up by the referee
+    This is addressed in a few other places in the new version of the paper, but we have added a sentence here reminding the reader of the assumption that goes into constucting the dust profile.
 

### 2020-12-03 main.tex
More edits

@@
 planet.
-If the 2:1 MMR can be identified (presumably by identifying another prominent MMR, such as the 3:1, and measuring the spacing between the two), we discuss the potential of using this feature to place constraints on the mass and eccentricity of the planet\textbf{.
+\textbf{If the 2:1 MMR can be identified (most easily by identifying another prominent MMR, such as the 3:1, and measuring the spacing between the two),} we discuss the potential of using this feature to place constraints on the mass and eccentricity of the planet\textbf{.
 In addition, we discuss the caveats of connecting the dust and planetesimal collision profiles in such a simple way.} \textbf{Finally, we} conclude in section
@@
 Because the resolution of a collision can result in another imminent collision, these events must be resolved one at a time, with the soonest collision being resolved first.
-For this reason, another collision search is run each time a collision is resolved, which continues until there are no more imminent collisions during the current time step.}
+For this reason, another collision search is run each time a collision is resolved, which continues until there are no more imminent collisions during the current time step.
+During the course of the simulation, no debris is created by collisions.
+Instead, we use the statistics of the resolved collisions to construct a collisional dust profile, which is discussed in detail in section \ref{sec:dust}.}
 
@@
 This is only the case if the collisional cascade from which the dust grains form happens before radial drift has a chance to move debris away from the resonances.
-Although we showed with a back-of-the-envelope calculation that this is plausible for a typical protoplanetary disk with properties similar to the protosolar nebula, a more thorough treatment of collisional grinding is necessary to be able to interpret the dust emission profiles presented here as anything more than upper limits.}
+Although we showed with a back-of-the-envelope calculation (see section \ref{sec:dust}) that this is plausible for a typical protoplanetary disk with properties similar to the protosolar nebula, a more thorough treatment of collisional grinding is necessary to be able to interpret the dust emission profiles presented here as anything more than upper limits.}
 
@@
 produce structure in the collision profile as a function of semimajor axis. Furthermore, we find that a series of distinctly different features appear 
-when collisions are ordered by cylindrical distance from the central star. If enough gas from the protoplanetary disc is still present, dust generated 
-from planetesimal-planetesimal collisions will immediately fall onto a circular orbit. In this case, the radial dust emission profile, 
-which can be observed at sub-mm wavelengths, directly traces the radial collision rate and therefore the dynamical activity of the planetesimals.
+when collisions are ordered by cylindrical distance from the central star.
+\textbf{The morphology of these features are tied to dynamical behavior of bodies near the edges of the resonances, where the circulation frequency of the critical angle approaches infinity.
+Particularly near the 2:1 MMR, we find that a bump or dip in the collsion profile forms when collisions are ordered by cylindrical distance.
+The presence of one of these two features depends on the peri- and apocenter distances of the edges of the resonance, relative to the libration width.
+Because these quantities depend on the mass and eccentricity of the perturbing planet, these properties of the planet are actually encoded in the collision profile.}
 
-Near the interior 2:1 MMR, we find that a distinct bump or dip feature is generated in the dust profile, depending on the properties of the perturbing 
+Near the interior 2:1 MMR, we find that a distinct bump or dip feature is generated in the collision profile, depending on the properties of the perturbing 
 planet. The presence of one of these two structures can used to constrain the mass and eccentricity of the planet. For a high mass, low eccentricity 
-planet, a dip will form in the dust profile because the edges of the resonance, where many collisions occur, stay sufficiently separated. If the planet 
+planet, a dip will form because the edges of the resonance, where many collisions occur, stay sufficiently separated. If the planet 
 has a low enough mass (which shrinks the size of the resonance) or is sufficiently eccentric (which decreases the separation between the apocenter 
@@
 perturbations scale linearly with both of these quantities.
+
+\textbf{Although the planetesimal collision profile would not be directly observable in a planet-forming disc, the dust from the resulting collisional cascade could potentially be used to trace it.
+So long as the dust grains are well-coupled to the gas and radial drift does not have a significant effect on the morphology of the dust, the bump or dip features seen in the collision profile will also appear in the dust profile.
+Assuming that this is the case, we have generated simulated observations of a protoplanetary disk by ALMA and shown that the bump or dip features seen in the collision profiles should be detectable through the dust emission.
+From a dust emission profile with sufficiently strong radial features, one could constrain the properties of a perturbing planet on an exterior orbit in the following way: (1) identify the locations of two resonances in the disc (2) measure the spacing between them to verify that one of the features is indeed associated with the 2:1 MMR (3) determine whether an under- or overdensity in the radial dust profile exists near this location (4) use the presence of one of these two features to determine the region of the eccentricity-mass plane in which the planet lies.}
 
@@
 2:1 exterior MMR. Whether this would alter the radial collision profile for the exterior, rather than the interior 2:1 resonance, is not immediately clear.  
-Given that the solid surface density diminishes with distance ($\sim r^{-3/2}$ for the MMSN \citep{1981PThPS..70...35H}), exterior resonances may 
-not be quite as useful for this type of measurement, however.
+\textbf{On one hand,} the solid surface density diminishes with distance ($\sim r^{-3/2}$ for the MMSN \citep{1981PThPS..70...35H}), \textbf{which would weaken the signal from locally generated collisional dust.} \textbf{On the other hand, exterior MMRs are quite effective at capturing inward drifting bodies (cite), which could locally enhance the surface density well beyond the MMSN value.
+A full treatment of the collisional cascade process and the radial drift of debris is a subject that we leave for future work.}
 
@@
 variations in the dust emission near MMRs is much more subtle and requires much higher spatial resolution and sensitivity. As we have shown, the 
-bump vs dip feature near the 2:1 MMR is marginally detectable with ALMA for the nearest protoplanetary discs. Another complicating factor is that 
+bump vs dip feature near the 2:1 MMR is marginally detectable with ALMA for the nearest protoplanetary discs\textbf{, so long as the dust profile closely matches the collisional profile of the planetesimals.}.
+Another complicating factor is that
 the inner $\sim$ 10 au of most protoplanetary discs are optically thick in the sub-mm. The solution to this problem is to instead observe at longer 

### 2020-12-08 refereeResponse.txt
More edits, responses to referee in report

@@
+We appreciate the referee's thoughtfulness and perspective and would firstly like to thank them for care and thoroughness that was put into their reviewing of this paper.
+We will address comments from the referee one by one, with the original comment listed first, followed by our response (indented).
+
 1) It is not clear how collisions were treated.
@@
 Although I agree they should not attempt to describe all details of the code here, it would be of major help to add more text describing how they deal with collisions.
+
 1.1) What is the collisional scaling used?
+
+	All collisions result in perferct mergers.
+This is now stated in section 3.1.
+Because we only model where the collisions happen, rather than what the debris looks like, we keep the collision model simple.
+
 1.2) What material is assumed for the colliding planetesimals?
+
+	A 2 g cm^-3 bulk density corresponds to an even mixture of ice and rock. Because all collisions are assumed to result in perfect mergers, this only affects the mass and radius of the bodies.
+
 1.3) How do you deal with size frequency distribution (collisional cascade) resultant from collisions?
+
+	We do not model the evolution of the resulting debris from collisions. More on this below.
+
 1.4) What is the dust size considered in this work?
+
+	We assume that the resulting dust grains are 1mm in size. This is mentioned in section 4.2.
 
@@
 
+	This is an excellent point brought up by the referee and is something that deserves a more careful discussion of in the paper.
+In regards to the applicability of this work: one must first understand where and how the planetsimals collide if there is any hope of nailing down what the resulting dust distribution will look like.
+Going from the collision profile to a dust emission profile deserves an entire paper by itself and we are certainly not doing that analysis justice here.
+
+	In light of this, we think that the best thing to do is to reframe this paper a bit, so that the collisions->dust step is saved until the end, given a little less weight in the abstract, introduction and conclusion, and the concerns brought up by the referee are sufficiently emphasized in the text.
+Most importantly, the reader should be cautioned that the dust profiles we present are upper limits.
+
+	Both the abstract and the summary at the end of the introduction have been reworked to place more emphasis on the planetesimal dynamics and collisions, with the dust profiles and giant planet property constraints as more of an afterthought.
+Sections 2, 3 and 4 of the paper now focus solely on the 300 km planetesimals, save for a few places where we justify our neglect of gas drag during the simulations.
+All discussion of dust production and its observability is now saved for the latter parts of the paper.
+
 2) I am very concerned by the fact the authors neglected migration on small particles due to aerodynamic drag.
@@
 This is why I previously said authors may be tracking the planetesimal collisional profile and the upper limit of dust generation at those locations in their simulations, but not necessarily the dust profile.
+
+	In the original paper, we checked to ensure that the 300 km planetsimals and the < mm-sized dust grains would stay in place, but the referee's concern about the effects of radial drift of intermediate-sized bodies is an important point that was overlooked.
+We handle this by: 1.
+cautioning the reader that the dust emission profiles presented should be interpreted as upper limits 2.
+discussing the concerns brought up by the referee 3.
+Providing a (somewhat crude) calculation of the drift and collision timescale of 1m bodies, where drift should be maximal.
+Point 3 is discussed more below.
 
@@
 
-    Measure drift timescale across resonance
-    Compare with collision timescale of 1m bodies
-        Depends only on surface density of bodies (assume all mass in 1m bodies for simplicity)
-        Drift and collision timescales are approx comparable
-        Low density planetesimals, less gas or cooler gas all alleviate this
+	In section 5, we now provide a calculation of both the drift timescale and collision timescale for 1m bodies near the 2:1 MMR.
+Because we do not model the debris from planetesimal collisions, the collision timescale for the 1m bodies is found by extrapolating the collision rate of the planetesimals to smaller bodies.
+This is done in the following way:
+
+		1. Measure the collision rate (per particle) of the planetesimals from the e2m2 simulation inside the 2:1 MMR
+		2. Assume that the 1m bodies will have dynamical state (eccentricity and inclination dispersion) as the planetesimals
+		3. Assume that all of the mass in solids near the 2:1 MMR is now made up of 1m bodies
+		4.
+Scale the measured planetesimal collision rate by the change in number density and collision cross section (if one were to convert the planetesimal population to smaller bodies) to get the collision timescale for 1m bodies.
+
+	In doing so, we find that the collision timescale for 1m bodies is about 100x smaller than the drift timescale for those bodies across the resonance.
+This suggests that radial drift will not have a large influence on the resulting dust dustribution.
+However, the 1m collision timescale should be interpreted as an lower limit, due to assumptions 2.
+and 3.
+We conclude that it is therefore plausible that radial drift does not play an important role, although a proper treatment of the collisional cascade and drift process is necessary to actually confirm this.
 
@@
 
-    So long as the concerns in 2) are satisfied, this is not an issue
+    See our response to 2)
 

### 2020-12-08 main.tex
More edits, responses to referee in report

@@
 So far, studies of planetesimal dynamics near MMRs \textbf{in which the planetesimals are directly resovled} have involved either collisionless test particles 
-\citep{2017ApJ...850..103B, 2016ApJ...818..159T, 2018ApJ...857....3T} or severely limited integration times \citep{2000Icar..143...45R}.
+\citep{2017ApJ...850..103B, 2016ApJ...818..159T, 2018ApJ...857....3T} or \textbf{integration times that do not fully capture the dynamisc of the resonances} \citep{2000Icar..143...45R, 2013ApJ...777L..31D}.
 
@@
 \rho_{g}$ is the local density of the gas and $v_{g}$ is the headwind velocity of the gas experienced by the planetesimal. At 3 au, the gaseous component of the solar nebula has a density of $4 
-\times 10^{-10}$ g cm$^{-3}$ and the typical headwind experienced by a body on a Keplerian orbit is $\sim 5000$ cm s$^{-1}$ \citep{1981PThPS..70...35H}. For a 100 km body with a 
-density of 2 g cm$^{-3}$ and an eccentricity of 0.1, the stopping timescale is on the order of $10^{6}$ years.
+\times 10^{-10}$ g cm$^{-3}$ and the typical headwind experienced by a body on a Keplerian orbit is $\sim 5,000$ cm s$^{-1}$ \citep{1981PThPS..70...35H}. For a 100 km body with a 
+density of 2 g cm$^{-3}$ \textbf{(assuming a mixture of ice and rock)} and an eccentricity of 0.1, the stopping timescale is on the order of $10^{6}$ years.
 This is much longer than the timescales related to secular forcing and libration near mean-motion resonances, as discussed above, but shorter than the typical protoplanetary disk lifetime and potentially the planetesimal formation timescale.
@@
 and has been shown to perform well on up to half a million processors \citep{2015AphCom..2..1}.
-\textbf{Using similar methods to {\sc PKDGRAV}, which has been used for numerous studies of planet formation (add some references here)}, {\sc ChaNGa} calculates
+\textbf{Using similar methods to {\sc PKDGRAV}, which has been used for numerous studies of planet formation \citep{2000Icar..143...45R, 2005ApJ...625..427L, 2013ApJ...777L..31D, 2015ApJ...806...23L}}, {\sc ChaNGa} calculates
 gravitational forces using a modified Barnes-Hut \citep{1986Natur.324..446B} tree with hexadecapole expansions of the moments \textbf{and then integrates the equations of motion using a kick-drift-kick leapfrog scheme}.
@@
 
-\noindent with $\alpha$ = 3/2 and $\Sigma_{0}$ = 10 g cm$^{-2}$. Planetesimals are given a bulk density of 2 g cm$^{-3}$ and a diameter of 
+\noindent with $\alpha$ = 3/2 and $\Sigma_{0}$ = 10 g cm$^{-2}$. Planetesimals are given a bulk density of 2 g cm$^{-3}$ \textbf{(assume a mixture of ice and rock)} and a diameter of 
 300 km.
@@
 
-\subsection{Where Does the Dust End Up?}\label{sec:dust}
+\section{Where Does the Dust End Up?}\label{sec:dust}
 

### 2020-12-09 refereeResponse.txt
Finish response to referee, edits to new version of paper

@@
 
-    We were specifically referring to direct N-body simulations (not statistical routines or studies using tracer particles)
-    This is the first direct N-body work that resolves the libration timescale of the resonances
-    We expect that a much longer integration time will yield the same result, because 5,000 years is longer than all of the relevant timescales relating to dynamics
+	Other studies which directly resolve planetesimal collisions near MMR (Richarson et al 2000, Dobinson 2013) used an integration time that shorter than the libration timescale of the resonances.
+This is what we mean by 'severely limited'.
+The text in the introduction has been changed to clarify this.
+
+	Regarding other codes that make use of statistical routines or tracer particles (such as Deienno et al.
+2020), the phase space resolution may not be sufficient to fully resolve the dynamics that are happening, particularly near the edges of the resonances.
+
+	Given that gas drag should not have a significant influence on the planetsimals (and it's plausible that the same is true for the collisional debris), we do not expect that a longer integration time should affect our results.
+The integration time we chose (5,000 years) is longer than any of the relevant timescales relating to the dynamics of the planetsimals.
+We now calculate all of the relevant timescales relating to the planetesimals in section 2.
+In addition section 5 contains a discussion of timescales relating to the collisional debris.
 
@@
 An additional paragraph has been added which summarizes some of the details provided about the ChaNGa collision model described in Wallace & Quinn 2019.
-TODO: Pull up some PKDGRAV planetesimal studies to reference here.
 
@@
     See 19) and 20).
-While there is certainly evidence that the gaseous component of the outer regions of protoplanetary disks follow alpha = -1, there is little evidence to confirm that this is the case for solids in the inner planet-forming region.
-Although alpha = -1.5 is not motivated by any extrasolar observations, it is compatible with the majority of protoplanetary disk models (see Chiang & Laughlin 2013, also Dai et al.
-2020) and is not uncommonly used in planet formation simulations (TODO: references?)
+It is true that the MMSN profile is only based off of solar system planets, this has been a standard benchmark in the field for quite a while and is not unreasonable to use.
+Furthermore, there is evidence to suggest that the solid surface density profile close to the star is steeper than alpha = -1 (see Chiang + Laughlin 2013, and Dai, F 2020).
+The region of the protoplanetary disk that we are modeling is not well-constrained by either exoplanet studies or mm and sub-mm observations.
 
@@
 
-    See our response to concern #4. Some text has been added to the paper (at the beginning of section 4) to elaborate on this as well.
+    See our response to concern #4. Some text has been added to the paper (at the beginning of section 4) to elaborate on this.
 
@@
 Where the critical angle is stationary, the pericenter orientations of the planetesimals experience a torque which causes their \varpi to follow the giant planet in its orbit.
-This is what we propose is responsible for the coherent structure seen in the right-hand panels of figures 6 and 7, along with the structure seen in the collision profiles.
-TODO: Expand our explanation in the paper to clarify this.
+This is what we propose is responsible for the coherent structure seen in the right-hand panels of figures 7 and 8 (6 and 7 in the original paper), along with the structure seen in the collision profiles.
+
+    The paragraph referenced now clarifies that we are specifically referring to collisions between bodies inside of the libration width of the resonance.
+An additional sentence has been added at the end of the following paragraph (which provides an explanation for the nonaxisymmetric gaps seen in fig 1) to tie this back to figure 6.
 

### 2020-12-09 main.tex
Finish response to referee, edits to new version of paper

@@
 the planet.  The width of a resonance is set by both the mass of the perturbing planet and the unperturbed eccentricity of the planetesimals, 
-which is in turn set by the eccentricity of the planet through secular forcing. Therefore, the structure of second generation dust produced near MMRs 
+which is in turn set by the eccentricity of the planet through secular forcing.
+Therefore, \textbf{the planetesimal collision profile and potentially} the structure of second generation dust produced near MMRs
 may encode information about both the mass and eccentricity of the planet.
@@
 So far, studies of planetesimal dynamics near MMRs \textbf{in which the planetesimals are directly resovled} have involved either collisionless test particles 
-\citep{2017ApJ...850..103B, 2016ApJ...818..159T, 2018ApJ...857....3T} or \textbf{integration times that do not fully capture the dynamisc of the resonances} \citep{2000Icar..143...45R, 2013ApJ...777L..31D}.
+\citep{2017ApJ...850..103B, 2016ApJ...818..159T, 2018ApJ...857....3T} or \textbf{integration times that do not fully capture the dynamics of the resonances} \citep{2000Icar..143...45R, 2013ApJ...777L..31D}.
 
@@
 In section \ref{sec:constrain}, w}e use the resolved collisions to generate synthetic dust
-emission profiles that would be detected with observing facilities like ALMA \textbf{, under the simplifying assumption that the resulting dust profile traces the collisions of the planetesimals.
+emission profiles that would be detected with observing facilities like ALMA.
+\textbf{This is done by making the simplifying assumption that the dust profile closely matches the collision profile of the planetesimals.
 Under this assumption, we show} that a characteristic bump
@@
 \textbf{If the 2:1 MMR can be identified (most easily by identifying another prominent MMR, such as the 3:1, and measuring the spacing between the two),} we discuss the potential of using this feature to place constraints on the mass and eccentricity of the planet\textbf{.
-In addition, we discuss the caveats of connecting the dust and planetesimal collision profiles in such a simple way.} \textbf{Finally, we} conclude in section
+In addition, we highlight the caveats of connecting the dust and planetesimal collision profiles in such a simple way.} \textbf{Finally, we} conclude in section
 \ref{sec:conclusions}.
@@
 \textbf{The timescale for secular forcing is given by the period at which the free eccentricity cycles in the complex plane.
-The imaginary and real components of the eccentricity of the jth particle are given by \citet{1999ssd..book.....M} (see ch 7, pg 282, equation 7.51)}
+The time-dependent imaginary and real components of the eccentricity of a planetesimal are given by \citet{1999ssd..book.....M} (see ch 7, pg 282, equation 7.51)}
 
 \begin{eqnarray}\label{eq:kandh}
-	h_{j} = e_{j1} sin (g_{1} t + \beta_{1}) + e_{j2} sin (g_{2} t + \beta_{2}) \\ \nonumber
-	k_{j} = e_{j1} cos (g_{1} t + \beta_{1}) + e_{j2} cos (g_{2} t + \beta_{2}),
+	h = e_{1} sin (g_{1} t + \beta_{1}) + e_{2} sin (g_{2} t + \beta_{2}) \\ \nonumber
+	k = e_{1} cos (g_{1} t + \beta_{1}) + e_{2} cos (g_{2} t + \beta_{2}),
 \end{eqnarray}
 
-\noindent \textbf{where  ($e_{j1}$, $e_{j2}$) and ($g_{1}$ , $g_{2}$) are the corresponding eigenvector components and eigenvalues of the matrix given by \citet{1999ssd..book.....M} (see ch 7, pg 276, equation 7.9 and 7.10, with $\alpha_{12} = \alpha$ and $\bar{\alpha_{12}} = 1$)}
+\noindent \textbf{where  ($e_{1}$, $e_{2}$) and ($g_{1}$ , $g_{2}$) are the corresponding eigenvector components and eigenvalues of the matrix given by \citet{1999ssd..book.....M} (see ch 7, pg 276, equation 7.9 and 7.10, with $\alpha_{12} = \alpha$ and $\bar{\alpha_{12}} = 1$)}
 
@@
 The frequency of the secular forcing is simply the difference of the two eigenvalue frequencies $g_{1} - g_{2}$.
-For the case of a Jupiter mass planet at 5.2 au perturbing a test particle, the timescale for secular forcing is approximately 12,000 years at 3 au.}
+For the case of a Jupiter mass planet at 5.2 au perturbing a test particle at 3 au, the timescale for secular forcing is approximately 12,000 years.}
 
@@
 
-\textbf{In mean-motion resonance, the orbital elements of a perturbed body, along with the critical angle described by equation \ref{eq:phi_crit}, will exhibit sinusoidal oscillations.
+\textbf{In mean-motion resonance, the orbital elements of a perturbed body, along with the critical angle described by equation \ref{eq:phi_crit}, will exhibit oscillations.
 In the circular, restricted three-body case, these small amplitude oscillations exhibit a characteristic frequency, given by (see \citet{1999ssd..book.....M} ch 8, pg 332, eq 8.47, with $j_{2} =-p$ and $j_{4} = -q$)}
@@
 
-Changes in eccentricity are correlated with changes in semimajor axis according to the Tisserand relation
+% Not directly relevant for any calculations in the paper, lets leave this out
+%Changes in eccentricity are correlated with changes in semimajor axis according to the Tisserand relation
 
-\begin{equation}\label{eq:tiss}
-	\frac{de}{da} = \frac{a^{3/2} - 1}{2 a^{5/2} e}.
-\end{equation}
+%\begin{equation}\label{eq:tiss}
+%	\frac{de}{da} = \frac{a^{3/2} - 1}{2 a^{5/2} e}.
+%\end{equation}
 
-The net result of this is that MMRs will produce spikes in the semimajor axis-eccentricity distribution of a planetesimal disc. In order to 
-preserve the Jacobi energy, equation \ref{eq:tiss} predicts that these spikes will tend to curve away from the perturbing body. This lowers the 
-surface density of the disc near the locations of resonances, while producing a pileup of bodies on eccentric orbits adjacent to the MMR.
+%The net result of this is that MMRs will produce spikes in the semimajor axis-eccentricity distribution of a planetesimal disc. In order to 
+%preserve the Jacobi energy, equation \ref{eq:tiss} predicts that these spikes will tend to curve away from the perturbing body. This lowers the 
+%surface density of the disc near the locations of resonances, while producing a pileup of bodies on eccentric orbits adjacent to the MMR.
 
@@
 
-\textbf{A simple analytic model of the collision rate of a planetesimal population is given by \citet{1969edo..book.....S} as}
+\textbf{A simple analytic model for the collision rate of a planetesimal population is given by \citet{1969edo..book.....S} as}
 
@@
 
-\textbf{\noindent where $n$ is the number density of the population, $s$ and $m$ are the radii and masses of the bodies and $v$ is their typical encounter velocity.
+\noindent\textbf{where $n$ is the number density of the population, $s$ and $m$ are the radii and masses of the bodies and $v$ is their typical encounter velocity.
 The encounter velocity is often described in terms of the rms eccentricity $\left<e^{2}\right>^{1/2}$ and inclination $\left<i^{2}\right>^{1/2}$ of the population (e.g.
@@
 
-\textbf{\noindent where $v_{k}$ is the local Keplerian velocity.
+\noindent\textbf{where $v_{k}$ is the local Keplerian velocity.
 The second term in equation \ref{eq:saf} can be thought of as an additional enhancement to the collision cross section due to gravitational focusing.
 When the typical encounter velocity is small compared to the mutual escape velocity of the planetesimals, the collision cross section greatly exceeds the geometric value.
-Another important feature of equation \ref{eq:saf} is that for a fixed value of $n$, the collision rate has a global minimum as a function of $v$.
+An important feature of equation \ref{eq:saf} is that for a fixed value of $n$, the collision rate exhibits a global minimum as a function of $v$.
 For small $v$, gravitational focusing allows for more collisions, while for large $v$ the number of encounters simply becomes so large that the collsion rate again increases, even though gravitational focusing does not operate.
@@
 
-\textbf{Over the course of many orbits, the residual gas from the primordial nebula can damp the eccentricities and inclinations of the planetesimals.
+\textbf{Over the course of many orbits, the residual gas from the primordial nebula can damp the eccentricities and inclinations of bodies.
 For a planetesimal-sized body, the geometric cross section is much larger than the mean free path of the gas particles and the timescale for gas drag to modify its orbit is given by \citep{1976PThPh..56.1756A}}
@@
 \begin{equation}\label{eq:t_edamp}
-    t_{e, damp} = \frac{2 m_{pl}}{C_{D} \pi s_{pl}^{2} \rho_{g} v_{g}},
+    t_{e, damp} = \frac{2 m}{C_{D} \pi s^{2} \rho_{g} v_{g}},
 \end{equation}
 
-\textbf{\noindent where $m_{pl}$ and $s_{pl}$ are the mass and radius of the planetesimal. $C_{D}$ is a drag coefficient which is of order unity, $
+\noindent \textbf{where $m$ and $s$ are the mass and radius of the planetesimal. $C_{D}$ is a drag coefficient which is of order unity, $
 \rho_{g}$ is the local density of the gas and $v_{g}$ is the headwind velocity of the gas experienced by the planetesimal. At 3 au, the gaseous component of the solar nebula has a density of $4 
@@
 This is much longer than the timescales related to secular forcing and libration near mean-motion resonances, as discussed above, but shorter than the typical protoplanetary disk lifetime and potentially the planetesimal formation timescale.
-For this reason, we do not model the effects of gas drag, although we consider its effects when constructing initial conditions for our simulations, which is discussed next.}
+For this reason, we do not model the effects of gas drag, although we consider its effects when constructing initial conditions for our simulations, which is discussed in the next section.}
 
@@
 slowly destroys the configuration over part of an orbit. As the planet passes by, adjacent planetesimals near the resonance edges temporarily align 
-themselves in this configuration. This explains why the concentration of planetesimals appears to `follow' the planet.
+themselves in this configuration.
+This explains why the concentration of planetesimals appears to `follow' the planet.
+\textbf{Connecting this back to the radial collision profiles shown in figure \ref{fig:coll_hist_r}, these bodies at the edges of the resonances must be responsible for the bumps and dips morphology seen because excluding collisions between bodies inside of the MMRs does not qualitatively alter the profiles.}
 

### 2020-12-10 main.tex
Final edits

@@
 During the course of the simulation, no debris is created by collisions.
-Instead, we use the statistics of the resolved collisions to construct a collisional dust profile, which is discussed in detail in section \ref{sec:dust}.}
+To model the collisionally generated dust distribution, we use the statistics of the resolved planetesimal collisions to build dust profile.
+This process is discussed in detail in section \ref{sec:dust}.}
 
@@
 
-\noindent with $\alpha$ = 3/2 and $\Sigma_{0}$ = 10 g cm$^{-2}$. Planetesimals are given a bulk density of 2 g cm$^{-3}$ \textbf{(assume a mixture of ice and rock)} and a diameter of 
+\noindent with $\alpha$ = 3/2 and $\Sigma_{0}$ = 10 g cm$^{-2}$. Planetesimals are given a bulk density of 2 g cm$^{-3}$ \textbf{, which corresponds to a mixture of ice and rock,)} and a diameter of 
 300 km.
-\textbf{This choice of parameters for the planetesimal disk is meant to follow the setup used in simulation B by \citet{2000Icar..143...45R}.
+\textbf{This choice of parameters for the planetesimal disk is meant to mimic the setup used in simulation B by \citet{2000Icar..143...45R}.
 One difference from the aformentioned study is that we use a narrower annulus, which reduces the number of particles required from $10^6$ down to roughly 500,000.
 This allows us to use a finer base timestep size, which, as we will discuss in section \ref{sec:results}, appears to be the reason why no features were seen in the collision profile near the resonances by \citet{2000Icar..143...45R}}.
-Each simulation is evolved for 5,000 years, which is about 400 orbits
-of the perturbing planet.
 
@@
 built into the initial conditions.
-\textbf{Although we do not model the effects of gas drag on the planetesimals, we construct the initial conditions such that these two effects are in balance.
+\textbf{Although we do not model the effects of gas drag on the planetesimals during the simulation, we construct the initial conditions such that these two effects are in balance.
 The viscous stirring timescale of the planetesimal disc is much longer than our chosen integration time, and so the dynamical excitation of the disc (excluding resonances) stays constant, even without modeling damping from gas.}.
 This is done by first calculating the equilibrium eccentricity $e_{eq}$ due to viscous stirring and gas drag as a
-function of semimajor axis according to equation 12 of \citet{2002ApJ...581..666K}. Although {\sc ChaNGa} does not account for the effects of 
-gas drag on the planetesimals, the viscous stirring timescale is long compared to our integration time and should not cause the velocity 
+function of semimajor axis according to equation 12 of \citet{2002ApJ...581..666K}.
+\textbf{Both the viscous stirring timescale and the gas drag timescale are} long compared to our integration time and should not cause the velocity
 distribution to significantly evolve. The eccentricities of the bodies are drawn randomly from a Rayleigh distribution with a mode of $e_{eq}$, 
@@
 \textbf{To do so, we allow each simulation to run for 2,000 years before we begin recording any collision statistics.
-This is comparable to the libration period (calculated in section \ref{sec:mmr} for the 3:1 and 2:1 resonances.
-Although one might worry that a single libration period may not be enough for the orbital structure due to the resonances to develop, we find that the shape of the semimajor axis-eccentricity distribution of the planetesimals reaches a steady state by this time.
+This is comparable to the libration period, which was calculated in section \ref{sec:mmr} for the 3:1 and 2:1 resonance).
+Although one might worry that a single libration period may not be long enough for the orbital structure due to the resonances to develop, we find that the shape of the semimajor axis-eccentricity distribution of the planetesimals reaches a steady state by this time.
 This is largely due to the fact that there are enough bodies in or near the resonances to allow an ensemble average of phase space, rather a time average.
-Additionally, we find that the time evolution of the collision rate near the resonances maintains a steady state in all five simulations after $\sim$ 2000 years.}
+As an additional confirmation, we find that the time evolution of the collision rate near the resonances maintains a steady state in all five simulations after $\sim$ 2000 years.}
 
@@
 There is therefore an intermediate value of $v$ for which the average collision rate $\left< \sigma v \right>$ is at a minimum, which we will refer to as  $\left< \sigma v \right>_{0}$.
-The dynamical excitation induced by a mean motion resonance can either increase or decrease the local average collision rate, depending on the size and mass of the planetesimals, along with their unperturbed relative velocites.}
+The dynamical excitation induced by a mean motion resonance can either increase or decrease the local average collision rate, depending on the unperturbed value of  $\left< \sigma v \right>$ relative to  $\left< \sigma v \right>_{0}$.}
 
 \textbf{In figure \ref{fig:gf}, we show the effect that the 2:1 MMR and 3:1 MMR have on the local average collision rate.
-Each pair of points connected by a line represents the average collision rate before (from the initial condition file) and after (around T = 2,000 yr) the effects of the mean-motion resonances develop.
-In this figure, the relative velocity between bodies is calculated by measuring the eccentricity and inclination dispersion near each resonance and using equation \ref{eq:eccincvel}.
-Here, we assume that the eccentricity and inclination dispersions are coupled \citep{1993MNRAS.263..875I} and use the eccentricity as the independent variable.
+Each pair of points connected by a line represents the average collision rate before and after the effects of the mean-motion resonances develop.
+For this figure, the relative velocity between bodies is calculated by measuring the eccentricity and inclination dispersion near each resonance and using equation \ref{eq:eccincvel}.
+Here, we assume that the eccentricity and inclination dispersions are coupled \citep{1993MNRAS.263..875I} and use the eccentricity dispersion as the independent variable.
 Because both the strength of secular forcing and the effects of the resonant perturbations are different near the 3:1 and 2:1 MMRs, the planetesimal population at each of these locations in the disk experiences a qualitatively different change in the collision rate.
 Near the 3:1 MMR, the unperturbed collision rate is well below the minimum value $\left< \sigma v \right>_{0}$ and the dynamical heating introduced by the resonance acts to suppress the collision rate further.
-Further out in the disk, near the 2:1 MMR, the collision rate starts out much closer to the minimum value and the additional perturbations drive the collision rate upwards.}
+Near the 2:1 MMR, the collision rate starts out much closer to the minimum value and the additional perturbations act to drive it higher.}
 
@@
 resonances \textbf{seen in figure \ref{fig:coll_hist_a}}. Although this could potentially serve as a useful
-diagnostic of the planetesimal size in a disc (because the\textbf{size and mass of the planetesimals set the eccentricity dispersion at which $\left< \sigma v \right>$ is minimized}), a direct measurement of the
+diagnostic of the planetesimal size in a disc (the\textbf{size and mass of the planetesimals set the eccentricity dispersion at which $\left< \sigma v \right>$ is minimized}), a direct measurement of the
 semimajor axes of the colliding planetesimals is not
-possible. Furthermore, as we will demonstrate next, collisions due to bodies in resonance do not have a significant effect on the final shape of the radial dust distribution.}
+possible. Furthermore, as we will demonstrate next, collisions due to bodies in resonance do not have a significant effect on the final shape of the radial dust distribution that we predict.}
 
@@
 any dust generated by collisions is strongly coupled to the gas and 2.
-any subsequent spatial evolution of the collisional debris is insignificant.}\textbf{So long as both of these assumptions are true, we can use the locations of planetesimal collisions in the plane of the disk to generate a dust profile for each simulation.}
+any subsequent spatial evolution of the collisional debris is insignificant.} \textbf{So long as both of these assumptions are true, we can use the locations of planetesimal collisions in the plane of the disk to generate a dust profile for each simulation.}
 
@@
 Collisions between planetesimals do not immediately convert the mass to dust grains.
-Rather, the debris will undergo a collisional cascade process, which gradually grinds the resulting bodies down to smaller and smaller sizes.
+Rather, the debris will undergo a collisional cascade process, which gradually grinds the resulting bodies down to smaller sizes.
 A proper treatment of the collisional cascade process, unfortunately, is quite complicated and is well beyond the scope of this work.
-However, one can safely ignore this process if the peak radial drift timescale is longer than the timescale for collisions between bodies that experience maximal radial drift.}
+However, one can safely ignore this process if the peak radial drift timescale is longer than the timescale for collisions between these bodies.}
 
 \textbf{In the inner part of the solar nebula, radial drift is maximized for meter-sized bodies.
-Following our same calculation in \ref{sec:pl_drag} with a 1 m body, we find that an object of this size will drift across the 2:1 MMR on a timescale of $\sim$ 300 years.
-Although we do not model collisions between bodies of this size, an upper limit on the collision timescale for 1 m bodies can be obtained by extrapolating the planetesimal collision rate measured in our simulations down to smaller-sized objects.
-For the e2m2 simulation, we find that 125 collisions occur withing the libration width of the 2:1 MMR during the 3,000 time window that collisions are recorded.
-There are 15,000 total planetesimals within this region, which means that a given planetesimal undergoes a collision every $\sim$ 370,000 years on average.
-If the entire planetesimal population in this region were converted to 1 meter bodies of the same bulk density, the collision timescale would decrease to $\sim$ 1 year.
+Following a similar calculation in \ref{sec:pl_drag} with a 1 m body, we find that an object of this size will drift across the 2:1 MMR on a timescale of $\sim$ 300 years.
+Although we do not model collisions between bodies of this size, a lower limit on the collision timescale for 1 m bodies can be obtained by extrapolating the planetesimal collision rate measured in our simulations down to smaller-sized objects.
+For the e2m2 simulation, we find that 125 collisions occur withing the libration width of the 2:1 MMR from T=2,000 yr to  T=5,000 yr.
+There are a total of 15,000 planetesimals within this region, which means that a single planetesimal undergoes a collision every $\sim$ 370,000 years on average.
+If the entire planetesimal population in this region were converted to 1 meter bodies with the same bulk density, the collision timescale would decrease to $\sim$ 1 year.
 The number density of bodies increases by a factor of $10^{15}$, while the geometric collision cross section decreases by a factor of $10^{10}$.
-Additionally, the 1 meter bodies will not experience gravitational focusing like the planetesimals, but this only alters the collision timescale by a factor of order unity.
 From this crude calculation, we conclude that the collision timescale for bodies that experience maximal radial drift is smaller than their drift timescale.
@@
 consideration. The dust will also evolve spatially due to drag effects, but can also evolve in size or be re-accreted onto planetesimals. For simplicity, 
-we focus on local dust sourcing only while acknowledging that subsequent evolution could affect the morphology.}, a map of the relative concentration 
+we focus on local dust sourcing only while acknowledging that subsequent evolution could \textbf{also} affect the morphology.}, a map of the relative concentration 
 of second-generation dust can be constructed from the cylindrical distance at which the collisions occur.
-\textbf{Here, cylindrical distance is measured as the distance between the central star and the collision in the ($r, \theta$) plane.} This is shown in figure \ref{fig:coll_hist_r}.
+\textbf{Here, cylindrical distance is defined as the separation between the central star and the pointt of collision in the ($r, \theta$) plane.} This is shown in figure \ref{fig:coll_hist_r}.
 Similar to figure \ref{fig:coll_hist_a}, we use a KDE with a width of 0.02 au to assemble the collision locations into a radial distribution. Most 
@@
 of the path that a resonant test particle takes in a frame co-rotating with the planet (see figure 8.4 of \citet{1999ssd..book.....M}).
-\textbf{In other words, the gap structure is argued to simply be due to the interfaces between the low eccentricity, non-resonant and high eccentricity resonant regions of the disc.} This explanation,
+\textbf{In other words, the gap structure is argued to be due to the interfaces between the low eccentricity, non-resonant and high eccentricity resonant regions of the disc.} This explanation,
 however, does not hold for a large collection of planetesimals, especially when there is no forced eccentricity. In such a case, the orbits of 

### 2020-12-11 refereeResponse.txt
Final edits to referee response

@@
-We appreciate the referee's thoughtfulness and perspective and would firstly like to thank them for care and thoroughness that was put into their reviewing of this paper.
-We will address comments from the referee one by one, with the original comment listed first, followed by our response (indented).
+We appreciate the referee's thoughtfulness and perspective and would firstly like to thank them for care and thoroughness that was put into their reviewing.
+We will address comments one by one, with the original comment listed first, followed by our response (indented).
 
@@
 
-	All collisions result in perferct mergers.
-This is now stated in section 3.1.
-Because we only model where the collisions happen, rather than what the debris looks like, we keep the collision model simple.
+	All collisions result in perferct mergers. This is now stated in section 3.1. We do not model the subsequent evolution of any of the debris.
 
@@
 
-	A 2 g cm^-3 bulk density corresponds to an even mixture of ice and rock. Because all collisions are assumed to result in perfect mergers, this only affects the mass and radius of the bodies.
+	A 2 g cm^-3 bulk density corresponds to an even mixture of ice and rock. Because all collisions are assumed to result in perfect mergers, this only affects the mass-radius relation of the bodies.
 
@@
 
-	We do not model the evolution of the resulting debris from collisions. More on this below.
+	This is not modeled in the simulations.
+As the referee points out below, the spatial evolution of bodies between dust and planetesimal sizes might have a significant influence of the final dust distribution.
+We have made sure to highlight this concern throughout the paper, although a back-of-the-envelope calculation in section 5 shows that this might not be terribly important.
 
@@
 In regards to the applicability of this work: one must first understand where and how the planetsimals collide if there is any hope of nailing down what the resulting dust distribution will look like.
-Going from the collision profile to a dust emission profile deserves an entire paper by itself and we are certainly not doing that analysis justice here.
+Going from the planetesimal collision profile to a dust emission profile deserves an entire paper by itself and we are certainly not doing that analysis justice here.
 
-	In light of this, we think that the best thing to do is to reframe this paper a bit, so that the collisions->dust step is saved until the end, given a little less weight in the abstract, introduction and conclusion, and the concerns brought up by the referee are sufficiently emphasized in the text.
-Most importantly, the reader should be cautioned that the dust profiles we present are upper limits.
+	In light of this, we have decided that the best thing to do is to reframe this paper a bit, so that the collisions->dust step is saved until the end, given a little less weight in the abstract, introduction and conclusion, and the concerns brought up by the referee are sufficiently emphasized in the text.
+Most importantly, the reader is now cautioned that the dust profiles we present are upper limits.
 
 	Both the abstract and the summary at the end of the introduction have been reworked to place more emphasis on the planetesimal dynamics and collisions, with the dust profiles and giant planet property constraints as more of an afterthought.
-Sections 2, 3 and 4 of the paper now focus solely on the 300 km planetesimals, save for a few places where we justify our neglect of gas drag during the simulations.
+Sections 2, 3 and 4 of the paper now focus solely on the full-sized planetesimals.
 All discussion of dust production and its observability is now saved for the latter parts of the paper.
@@
 	In section 5, we now provide a calculation of both the drift timescale and collision timescale for 1m bodies near the 2:1 MMR.
-Because we do not model the debris from planetesimal collisions, the collision timescale for the 1m bodies is found by extrapolating the collision rate of the planetesimals to smaller bodies.
+Because we do not model the debris from planetesimal collisions, the collision timescale for the 1m bodies is found by extrapolating the collision rate of the planetesimals down to smaller bodies.
 This is done in the following way:
@@
 		1. Measure the collision rate (per particle) of the planetesimals from the e2m2 simulation inside the 2:1 MMR
-		2. Assume that the 1m bodies will have dynamical state (eccentricity and inclination dispersion) as the planetesimals
-		3. Assume that all of the mass in solids near the 2:1 MMR is now made up of 1m bodies
+		2. Assume that the 1m bodies will have the same dynamical state (eccentricity and inclination dispersion) as the planetesimals
+		3. Assume that all of the mass in solids near the 2:1 MMR now consists of 1m bodies
 		4.
-Scale the measured planetesimal collision rate by the change in number density and collision cross section (if one were to convert the planetesimal population to smaller bodies) to get the collision timescale for 1m bodies.
+Scale the planetesimal collision rate (measured in the simulation) by the change in number density and collision cross section if one were to convert the planetesimal population to smaller bodies to get the collision timescale for 1m bodies.
 
-	In doing so, we find that the collision timescale for 1m bodies is about 100x smaller than the drift timescale for those bodies across the resonance.
+	In doing so, we find that the collision timescale for 1m bodies is about 100x smaller than the drift time for those bodies across the resonance.
 This suggests that radial drift will not have a large influence on the resulting dust dustribution.
@@
 and 3.
-We conclude that it is therefore plausible that radial drift does not play an important role, although a proper treatment of the collisional cascade and drift process is necessary to actually confirm this.
+We conclude that it is therefore plausible that radial drift does not play an important role, although a full, proper treatment of the collisional cascade and drift process is necessary to actually say this with certainty.
 
@@
 
-    See our response to 2)
+    See our response to concern 2)
 
@@
 
-	Given that gas drag should not have a significant influence on the planetsimals (and it's plausible that the same is true for the collisional debris), we do not expect that a longer integration time should affect our results.
+	Given that gas drag does not have a significant influence on the planetsimals (and it's plausible that the same is true for the collisional debris), we do not expect that a longer integration time should affect our results.
 The integration time we chose (5,000 years) is longer than any of the relevant timescales relating to the dynamics of the planetsimals.
 We now calculate all of the relevant timescales relating to the planetesimals in section 2.
+There is now an expanded discussion justifying our choice of integration time at the beginning of section 4.
 In addition section 5 contains a discussion of timescales relating to the collisional debris.
@@
     This is the correct interpretation.
-The paper outline at the end of the introduction now explains this.
-In addition, there is a step-by-step description of this process toward the end of section 6.
+The outline at the end of the introduction now explains this.
+In addition, there is a step-by-step description of this process toward the end of section 7 (section 6 in the original draft).
 
@@
     This is absolutely true.
-The initial conditions for this work were meant to be compared with simulation B of Richardson et al.
+The initial conditions for this work are meant to be compared with simulation B of Richardson et al.
 2000, which only focused on the internal MMRs.
@@
 
-	Although the presence of gas is necessary in order to justify a simple, tractable model for connecting the planetesimal collision profile to the dust profile, the dynamics of the planetesimals and the behavior of the collision profile does not depend very strongly on the gas.
-In a debris disk, it is certainly going to be more difficult to make this connection, but the behavior of the planetesimals should be quite similar.
+	Although the presence of gas is necessary in order to justify a simple, tractable model for connecting the planetesimal collision profile to the dust profile, the dynamics of the planetesimals and the resulting planetesimal collision profile does not depend very strongly on the gas.
+In a debris disk, it is certainly going to be more difficult to model the collisional dust, but the behavior of the planetesimals should be quite similar.
 
@@
 2020 makes use of tracer particles, which is not the case with the other studies we cite here.
-Had we used coarser resolution and taken advantage of tracer particles in this work, the structure seen at the edges of the resonances in figures 6 and 7, which is critical to generating the features seen in the collision profiles, would likely become washed out.
-The text in the above sentence in the introduction has been changed to clarify that we are only referring to cases where the planetesimals are directly resolved.
+Had we used coarser resolution and taken advantage of tracer particles in this work, the structure seen at the edges of the resonances in figures 7 and 8 (figures 6 and 7 in the original paper), which is critical to generating the features seen in the collision profiles, would likely become washed out.
+The text in the above sentence in the introduction has been modified to clarify that we are only referring to cases where the planetesimals are directly resolved.
 
@@
     This is now clarified at the end of section 2.4 (gas drag on planetesimals) and in section 3.2 (initial conditions).
-The idea is that we consider gas drag when building the initial conditions, but do not need directly model its effects during the simulations because the gas drag and viscous stirring timescale is much longer than the simulation timescale.
+The idea is that we consider the effects gas drag when building the initial conditions, but do not need directly model it during the course of the simulations because the gas drag and viscous stirring timescale is quite long.
 We assume that these two effects are in equilibrium, build them into the initial conditions and then can safely forget about them.
@@
 Although a bit long, the main purpose of this section is to 'show our work' when deriving the secular forcing timescale and libration widths used later in the paper.
-(Should shorten this or move it to an appendix?)
 
@@
 2000, which is why we focus on interior MMRs here.
-Additionally, the number of timesteps required to measure the collision profile for the exterior MMRs increases with semimajor axis when using alpha steeper than -1.
-We have also added a brief discussion highlighting the importance of studying exterior resonances in the summary and discussion near the end of the paper.
+We have also added a brief discussion highlighting the importance of studying exterior resonances in future work in the summary and discussion near the end of the paper.
 
@@
     See 19) and 20).
-It is true that the MMSN profile is only based off of solar system planets, this has been a standard benchmark in the field for quite a while and is not unreasonable to use.
+While it is true that the MMSN profile is only based off of solar system planets, this has been a standard benchmark in the field for quite a while and is we do not think it's unreasonable to use.
 Furthermore, there is evidence to suggest that the solid surface density profile close to the star is steeper than alpha = -1 (see Chiang + Laughlin 2013, and Dai, F 2020).
@@
 
-    In our case, the large particle count allows us to look at the ensemble average of the dynamical behavior near resonance.
+    In our case, the large particle count allows us to look at the 'ensemble average' of the dynamical behavior near resonance.
 Even though individual planetesimals only go through a few librational oscillations, the phase trajectories that they follow are well populated with particles.
-This allows us to make conclusions about the dynamics without needing a longer baseline to take time averages.
+This allows us to make conclusions about the dynamics without needing a longer baseline from which to take time averages.
 Had we been following only a few bodies, this would not have been the case.
@@
 
-    As we now derive in section 2, the libration timescale and the secular forcing timescale are much shorter than the stopping time due to gas for the planetesimals, so this figure should not look different had we modeled gas drag.
+    As we now derive in section 2.1, the libration timescale and the secular forcing timescale are much shorter than the stopping time due to gas for the planetesimals, so this figure should not look different had we modeled gas drag in the simulations.
 A typo in the text has been corrected: '7:3' was supposed to say '8:3'.
@@
 When things are cold, gravitational focusing is highly effective.
-When things are very hot, you get very frequent encounters.
-The collision rate exhibits a minimum value somewhere in between.
-Depending on how dynamically hot the local planetesimal population gets when a resonance heats it up, the collision rate can either increase OR decrease.
+When things are very hot, encounters are very frequent and many collsions occur, even though the effective collision cross section is diminished.
+The collision rate exhibits a minimum value at some intermediate value of dynamical excitation.
+Depending on how dynamically hot the local planetesimal population gets when a resonance heats it up, the collision rate can either increase OR decrease from the unperturbed value.
 
-    To address the refee's intrepretation: if the offset in the peak of the collision rate in figure 4 (near the 2:1 MMR, for example) were due to bodies colliding at perihelion, the peak should shift inward as the eccentricity of the planet is increased.
-Between the e1m2 and e3m2 simulations, the mean eccentricity at the 2:1 MMR increases from ~0.03 to ~0.06.
-The perihelion distance of a body at the 2:1 MMR would decrease by about 0.1 AU, which would most certainly be apparent in figure 4.
+    To address the referee's intrepretation: if the offset in the peak of the collision rate in figure 4 (near the 2:1 MMR, for example) were due to bodies colliding at perihelion, the peak should shift inward as the eccentricity of the planet is increased.
+Between the e1m2 and e3m2 simulations, the mean eccentricity at the 2:1 MMR increases from ~0.03 to ~0.06 and so the perihelion distance of a body at the 2:1 MMR would decrease by about 0.1 AU.
+This shift would have apparent in figure 4.
 
@@
     As shown in figure 6 (fig 5 in the original version), the bump and dip features at the center of the MMRs are still present, even if we ignore particles whose semimajor axis falls within the libration width of the resonances.
-What this implies is that the EDGES of the resonances are important.
+What this implies is that the edges of the resonances are important.
 As we approach a resonance from the outside, the critical angle \phi approaches an unstable equilibirum where it is stationary.
-Where the critical angle is stationary, the pericenter orientations of the planetesimals experience a torque which causes their \varpi to follow the giant planet in its orbit.
+Where the critical angle is near-stationary, the pericenter orientations of the planetesimals experience a torque which causes their \varpi to follow the giant planet in its orbit.
 This is what we propose is responsible for the coherent structure seen in the right-hand panels of figures 7 and 8 (6 and 7 in the original paper), along with the structure seen in the collision profiles.
@@
     See 36).
-If you look at figures 1, 6 and 7, the nonaxisymmetric gap structure in the disk near the resonances is always aligned with the planet's orbital phase.
+If you look at figures 1, 7 and 8, (1, 6 and 7 in the original paper) the nonaxisymmetric gap structure in the disk near the resonances is always aligned with the planet's orbital phase.
 It is also apparent from figure 1 that the gaps are not aligned with the planet's longitude of pericenter, which should be the case if the structure were due to secular forcing in eccentricity.
@@
 The gap structure cannot be due to the interface between the secularly forced, non-resonant part of the disk, and the randomly oriented orbits of bodies in resonance.
-The latter explanation was given by Tabeshian & Weigert 2016, which, as we point out in our paper, is not adequate.
+The latter explanation was given by Tabeshian & Weigert 2016, which, as we point out in our paper, does not quite make sense.
 
@@
 
-    Already addressed above
+    See our response to concern 4)
 
@@
 
-    Ask aaron about this?
+    Ask Aaron about this?
 
@@
     This is certainly a big if, although we have shown with a back-of-the-envelope calculation in section 4.2 that it could be plausible.
-We have added some additional text to the end of section 5 to remind the reader that the dust profile is built with some shaky assumptions.
+We have added some additional text to the end of section 5 to remind the reader that the dust profile is built on some not-so-solid assumptions.
 
@@
 My apologies for being so long. I do think this work has potential, but it does need substantial clarifications.
+
+	No need to apologize. We appreciate your thoroughness and care!

### 2021-01-12 main.tex
Start implementing final edits

@@
 \begin{abstract}
-In circumstellar discs, collisional grinding of planetesimals produces second-generation dust which can be observed through thermal 
-emission. While it remains unclear when second-generation dust first becomes a major component of the total dust content, the presence of 
-such dust and potentially the substructure within it can be used to explore a disc's physical conditions. A perturbing planet has been shown to 
-produce nonaxisymmetric structures, as well as gaps in discs, regardless of the origin of the dust. However, small grains will have very 
-different dynamics compared with planetesimals when in the presence of gas, and as such, the collisional evolution of planetesimals could 
-create dusty disc structures that would not exist otherwise. Previous studies have shown that morphological differences in the collisional dust 
-corotating with a giant planet can be used to determine whether the planet's eccentricity is large or small. \textbf{In this work, we use N-body simulations
-that directly resolve collisions between planetesimals to investigate the collision rate profile near mean-motion resonances with the planet. We 
-find that a distinct bump or dip feature is produced in the collision profile, the presence of which depends on the libration width of the resonance and the 
-separation between the peri and apocenter distances of the edges of the resonance. In the collision profile, the presence of one of these two features
-limits possible values for the mass and eccentricity of the planet. Under the simplifying assumption that the radial profile of the dust emission in the disc
+\textbf[In circumstellar discs, collisional grinding of planetesimals produces second-generation dust. While it remains unclear this becomes a major component of the total dust content, 
+the presence of such dust and potentially the substructure within it can be used to explore a disc's physical conditions. A perturbing planet produces nonaxisymmetric structures, as
+well as gaps in discs, regardless of the origin of the dust. The dynamics of planetesimals, however, will be very different than that of small dust grains due to gas interactions. The
+collisional evolution of planetesimals could therefore create dusty disc structures that would not exist otherwise. Previous studies have shown that morphological differences in the
+collisional dust corotating with a giant planet can be used to determine whether the planet's eccentricity is large or small.In this work, we use N-body simulations that directly resolve
+collisions between planetesimals to investigate the collision rate profile near mean-motion resonances. We  find that a distinct bump or dip feature is produced in the collision profile,
+the presence of which depends on the libration width of the resonance and the separation between the peri and apocenter distances of the edges of the resonance. The presence of
+one of these two features limits possible values for the mass and eccentricity of the planet. Under the simplifying assumption that the radial profile of the dust emission in the disc
 traces the collision profile, we show that a bump or dip feature in the dust emission near the interior 2:1 mean-motion resonance could be used to place constraints
 on the orbital properties of the perturbing planet. So long as radial drift does not play a significant role in the collisional cascade that grinds planetesimals down to
-dust, this feature in the dust emission should be marginally observable in nearby protoplanetary disks with ALMA.}
+dust, or if other processes limit the dust to be approximately local, this feature in the dust emission should be marginally observable in nearby protoplanetary disks with ALMA.}
 \end{abstract}
@@
 integration time. With this toolset, we explore the collision rate structure of a planetesimal disc in the vicinity of mean-motion resonances with the planet. In 
-particular, we would like to determine (1) \textbf{What dynamics govern the collision rate profile near MMRs, (2)} whether MMRs leave a detectable signature in the collisionally-generated dust, and \textbf{(3)} whether these
+particular, we would like to determine (1) \textbf{what dynamics govern the collision rate profile near MMRs, (2)} whether MMRs leave a detectable signature in the collisionally-generated dust, and \textbf{(3)} whether these
 signatures can be used to determine or constrain the orbital properties of the perturbing planet.
@@
 
+% TODO: need to introduce matricies here, also mention that we are describing interaction between a planetesimal and jupiter here
+
 \begin{eqnarray}\label{eq:pert_matrix}
 	A_{jj} = n_{j} \frac{1}{4} \frac{m_{k}}{m_{c} + m_{j}} \alpha b_{3/2}^{(1)} (\alpha) \\ \nonumber
-	A_{jk} = -n_{j} \frac{1}{4} \frac{m_{k}}{m_{c} + m_{j}} \alpha b_{3/2}^{(2)} (\alpha)
-\end{eqnarray}.
+	A_{jk} = -n_{j} \frac{1}{4} \frac{m_{k}}{m_{c} + m_{j}} \alpha b_{3/2}^{(2)} (\alpha).
+\end{eqnarray}
 
@@
 We provide a brief summary of the collision model here, although a full description is provided in \citet{2019MNRAS.489.2159W}.
-This work is largely based off of the solid-body collision implementation in {\sc PKDGRAV}, which is described in \citet{1994MNRAS.269..493R} and \citet{2000Icar..143...45R}.
+This work is largely based on the solid-body collision implementation in {\sc PKDGRAV}, which is described in \citet{1994MNRAS.269..493R} and \citet{2000Icar..143...45R}.
 Imminent collisions are found during the drift phase of each time step by extrapolating the positions of bodies forward using the velocity calculated during the first kick.
@@
 
-\noindent with $\alpha$ = 3/2 and $\Sigma_{0}$ = 10 g cm$^{-2}$. Planetesimals are given a bulk density of 2 g cm$^{-3}$ \textbf{, which corresponds to a mixture of ice and rock,)} and a diameter of 
+\noindent with $\alpha$ = 3/2 and $\Sigma_{0}$ = 10 g cm$^{-2}$. Planetesimals are given a bulk density of 2 g cm$^{-3}$ \textbf{, which corresponds to a mixture of ice and rock)} and a diameter of 
 300 km.
@@
 \textbf{Although we do not model the effects of gas drag on the planetesimals during the simulation, we construct the initial conditions such that these two effects are in balance.
-The viscous stirring timescale of the planetesimal disc is much longer than our chosen integration time, and so the dynamical excitation of the disc (excluding resonances) stays constant, even without modeling damping from gas.}.
-This is done by first calculating the equilibrium eccentricity $e_{eq}$ due to viscous stirring and gas drag as a
+The viscous stirring timescale of the planetesimal disc is much longer than our chosen integration time, and so the dynamical excitation of the disc (excluding resonances) stays constant, even without modeling damping from gas.} This is done by first calculating the equilibrium eccentricity $e_{eq}$ due to viscous stirring and gas drag as a
 function of semimajor axis according to equation 12 of \citet{2002ApJ...581..666K}.
@@
 \textbf{To do so, we allow each simulation to run for 2,000 years before we begin recording any collision statistics.
-This is comparable to the libration period, which was calculated in section \ref{sec:mmr} for the 3:1 and 2:1 resonance).
+This is comparable to the libration period, which was calculated in section \ref{sec:mmr} for the 3:1 and 2:1 resonance.
 Although one might worry that a single libration period may not be long enough for the orbital structure due to the resonances to develop, we find that the shape of the semimajor axis-eccentricity distribution of the planetesimals reaches a steady state by this time.
@@
 \citep{scikit-learn} package to construct our KDEs, using a gaussian kernel with a FWHM of 0.02 au.
-\textbf{The curves shown in figure \ref{fig:coll_hist_a} are normalized such that the area underneath is normalized to 1.}
+\textbf{The curves shown in figure \ref{fig:coll_hist_a} are normalized such that the area underneath is equal to 1.}
 
@@
 Because both the strength of secular forcing and the effects of the resonant perturbations are different near the 3:1 and 2:1 MMRs, the planetesimal population at each of these locations in the disk experiences a qualitatively different change in the collision rate.
-Near the 3:1 MMR, the unperturbed collision rate is well below the minimum value $\left< \sigma v \right>_{0}$ and the dynamical heating introduced by the resonance acts to suppress the collision rate further.
-Near the 2:1 MMR, the collision rate starts out much closer to the minimum value and the additional perturbations act to drive it higher.}
+Near the 3:1 MMR, the unperturbed collision rate is well above the minimum value $\left< \sigma v \right>_{0}$ and the dynamical heating introduced by the resonance acts to suppress it further.
+Near the 2:1 MMR, the collision rate starts out much closer to the minimum value and the additional perturbations are strong enough to drive it higher.}
 
@@
 resonances \textbf{seen in figure \ref{fig:coll_hist_a}}. Although this could potentially serve as a useful
-diagnostic of the planetesimal size in a disc (the\textbf{size and mass of the planetesimals set the eccentricity dispersion at which $\left< \sigma v \right>$ is minimized}), a direct measurement of the
+diagnostic of the planetesimal size in a disc (\textbf{because the size and mass of the planetesimals sets the eccentricity dispersion at which $\left< \sigma v \right>$ is minimized}), a direct measurement of the
 semimajor axes of the colliding planetesimals is not
@@
 \end{figure}
+
+% TODO: Stopped here
 

### 2021-01-15 main.tex
Fix up radial drift section, add epstein drag calculation

@@
 \begin{abstract}
-\textbf[In circumstellar discs, collisional grinding of planetesimals produces second-generation dust. While it remains unclear this becomes a major component of the total dust content, 
+\textbf{In circumstellar discs, collisional grinding of planetesimals produces second-generation dust. While it remains unclear this becomes a major component of the total dust content, 
 the presence of such dust and potentially the substructure within it can be used to explore a disc's physical conditions. A perturbing planet produces nonaxisymmetric structures, as
@@
 \textbf{Over the course of many orbits, the residual gas from the primordial nebula can damp the eccentricities and inclinations of bodies.
-For a planetesimal-sized body, the geometric cross section is much larger than the mean free path of the gas particles and the timescale for gas drag to modify its orbit is given by \citep{1976PThPh..56.1756A}}
+For a planetesimal-sized body, the geometric cross section is much larger than the mean free path of the gas particles and the timescale for gas drag to significantly alter its relative velocity is given by \citep{1976PThPh..56.1756A}}
 
-\begin{equation}\label{eq:t_edamp}
-    t_{e, damp} = \frac{2 m}{C_{D} \pi s^{2} \rho_{g} v_{g}},
+\begin{equation}\label{eq:ts_stokes}
+    t_{s} = \frac{2 m}{C_{D} \pi s^{2} \rho_{g} v_{g}},
 \end{equation}
@@
 \times 10^{-10}$ g cm$^{-3}$ and the typical headwind experienced by a body on a Keplerian orbit is $\sim 5,000$ cm s$^{-1}$ \citep{1981PThPS..70...35H}. For a 100 km body with a 
-density of 2 g cm$^{-3}$ \textbf{(assuming a mixture of ice and rock)} and an eccentricity of 0.1, the stopping timescale is on the order of $10^{6}$ years.
+density of 2 g cm$^{-3}$ \textbf{(assuming a mixture of ice and rock)} the stopping timescale is on the order of $10^{6}$ years.
 This is much longer than the timescales related to secular forcing and libration near mean-motion resonances, as discussed above, but shorter than the typical protoplanetary disk lifetime and potentially the planetesimal formation timescale.
@@
     \includegraphics[width=\textwidth]{figures/gf_plot.png}
-    \caption{\textbf{The collision rate of bodies in the vicinity of the 3:1 (left) and 2:1 (right) MMRs, relative to the minimum value, as a function of the local eccentricity dispersion.
-The pairs of points connected by lines show the values of the perturbed and unperturbed collision rates in the e1m2, e2m2 and e3m2 simulations.}\label{fig:gf}}
+    \caption{\textbf{The collision rate (given by equation \ref{eq:saf}) of bodies in the vicinity of the 3:1 (left) and 2:1 (right) MMRs, relative to the minimum value, as a function of the local eccentricity dispersion.
+The pairs of points connected by lines show the values of the perturbed (left-hand points in each subplot) and unperturbed (right-hand points) collision rates in the e1m2, e2m2 and e3m2 simulations.}\label{fig:gf}}
 \end{center}
@@
 
-% TODO: Stopped here
-
 \section{Where Does the Dust End Up?}\label{sec:dust}
 
-To construct a radial dust profile from the collision statistics, we begin by making \textbf{two assumptions: 1.
-any dust generated by collisions is strongly coupled to the gas and 2.
-any subsequent spatial evolution of the collisional debris is insignificant.} \textbf{So long as both of these assumptions are true, we can use the locations of planetesimal collisions in the plane of the disk to generate a dust profile for each simulation.}
+To construct a radial dust profile from the collision statistics, we begin by making \textbf{two assumptions: (1) any dust generated by collisions is strongly coupled to the gas and (2) any subsequent spatial evolution of the collisional debris is insignificant.} \textbf{So long as both of these assumptions are true, we can use the locations of planetesimal collisions in the plane of the disk to generate a dust profile for each simulation.}
 
-\textbf{We first provide a justification for assumption (1), which is as follows:} For a dust grain larger than the mean free path of the gas particles, the timescale to damp its eccentricity is given by \citep{1976PThPh..56.1756A}
+\textbf{We first provide a justification for assumption (1), which is as follows: At 3 AU in the protosolar nebula, the mean free path of a gas particle is $\sim$ 50 cm (assuming a composition of pure hydrogen with a local volume density of $\rho_{g} = 4 \times 10^{-10}$ g cm$^{-3}$).
+This places any dust grains in the Epstein drag regime, with a stopping timescale given by}
 
-\begin{equation}\label{eq:t_edamp}
-    t_{e, damp} = \frac{8 s \rho}{3 e C_{D} \rho_{g} v_{th}},
+\begin{equation}\label{eq:ts_epstein}
+    t_{s} = \frac{\rho s}{\rho_{g} v_{th}},
 \end{equation}
 
-\noindent where $m$, $e$ and $s$ are the mass, eccentricity and radius of the dust grain. $C_{D}$ is a drag coefficient which is of order unity, $
-\rho_{g}$ is the local density of the gas and $v_{th}$ is its thermal speed.\textbf{Using the same values for the properties of the solar nebula as we did in section \ref{sec:pl_drag} and assuming} a 1 mm dust grain with a
-density of 1 g cm$^{-3}$ and an eccentricity of 0.05, the damping timescale is $4 \times 10^{-3}$ years. This is orders of magnitude smaller than the 
+\noindent where $\rho$ is the bulk density of the dust grain, $s$ is its size, and $v_{th}$ is the local thermal velocity of the gas.
+At 3 AU in the protosolar nebula, $v_{th} \sim 10^{5}$ cm s$^{-1}$.
+Assuming a 1 mm dust grain with a $\rho$ = 2 g cm$^{-3}$, the stopping time is $\sim 10^{-4}$ yr.
+This is orders of magnitude smaller than the
 orbital timescale, therefore we conclude that collisionally generated dust grains will immediately couple to the gas.
@@
 Rather, the debris will undergo a collisional cascade process, which gradually grinds the resulting bodies down to smaller sizes.
-A proper treatment of the collisional cascade process, unfortunately, is quite complicated and is well beyond the scope of this work.
+A proper treatment of the collisional cascade process, is quite complicated and is well beyond the scope of this work.
 However, one can safely ignore this process if the peak radial drift timescale is longer than the timescale for collisions between these bodies.}
 
-\textbf{In the inner part of the solar nebula, radial drift is maximized for meter-sized bodies.
+\textbf{Radial drift is maximized for bodies of the size at which St = $t_{s} \Omega$ = 1.
+In the Stokes drag regime at 3 AU, this occurs for bodies of 1 meter in size.
 Following a similar calculation in \ref{sec:pl_drag} with a 1 m body, we find that an object of this size will drift across the 2:1 MMR on a timescale of $\sim$ 300 years.
-Although we do not model collisions between bodies of this size, a lower limit on the collision timescale for 1 m bodies can be obtained by extrapolating the planetesimal collision rate measured in our simulations down to smaller-sized objects.
-For the e2m2 simulation, we find that 125 collisions occur withing the libration width of the 2:1 MMR from T=2,000 yr to  T=5,000 yr.
+Although we do not model collisions between bodies of this size, a lower limit on the collision timescale for these objects can be obtained by extrapolating the planetesimal collision rate measured in our simulations down.
+For the e2m2 simulation, we find that 125 collisions occur within the libration width of the 2:1 MMR from T=2,000 yr to  T=5,000 yr.
 There are a total of 15,000 planetesimals within this region, which means that a single planetesimal undergoes a collision every $\sim$ 370,000 years on average.
-If the entire planetesimal population in this region were converted to 1 meter bodies with the same bulk density, the collision timescale would decrease to $\sim$ 1 year.
-The number density of bodies increases by a factor of $10^{15}$, while the geometric collision cross section decreases by a factor of $10^{10}$.
-From this crude calculation, we conclude that the collision timescale for bodies that experience maximal radial drift is smaller than their drift timescale.
-Therefore, our descision to ignore the spatial redistribution of the collisional debris is not entirely unfounded, although we would like to emphazise that the collision timescale estimated above is strictly a lower limit.}
+If the entire planetesimal population in this region were converted to 1 meter bodies with the same bulk density, the number density of bodies increases by a factor of $10^{15}$, while the geometric collision cross section decreases by a factor of $10^{10}$.
+The collision timescale would therefore decrease to $\sim$ 1 year.
+As shown above, radial drift in the Stokes drag regime is maximized for bodies of 1 meter in size, which is only a factor of two larger than the mean free path of the gas particles.
+It is therefore not entirely clear if the Stokes drag law is appropriate here.
+Because of this, we also repeat the above calculation for bodies that experience Epstein drag.
+With this assumption, we find that radial drift is maximized for a cm-sized body.
+If one were to instead convert all of the collisional debris to objects of this size, the collision timescale decreases by another factor of 100.
+We conclude that the true collision timescale for bodies with maximal radial drift lies somewhere between $10^{-2}$ and 1 year.
+From this crude calculation, it appears plausible that the collision timescale for the fastest inward drifting bodies is smaller than their drift timescale across the 2:1 MMR.
+We argue that it is reasonable and, indeed, best practice to start with such simple assumptions understand the physics before additional complexity is later added.}
 

### 2021-01-25 main.tex
Finish aaron's edits

@@
 
-\textbf{The timescale for secular forcing is given by the period at which the free eccentricity cycles in the complex plane.
-The time-dependent imaginary and real components of the eccentricity of a planetesimal are given by \citet{1999ssd..book.....M} (see ch 7, pg 282, equation 7.51)}
-
-\begin{eqnarray}\label{eq:kandh}
-	h = e_{1} sin (g_{1} t + \beta_{1}) + e_{2} sin (g_{2} t + \beta_{2}) \\ \nonumber
-	k = e_{1} cos (g_{1} t + \beta_{1}) + e_{2} cos (g_{2} t + \beta_{2}),
-\end{eqnarray}
-
-\noindent \textbf{where  ($e_{1}$, $e_{2}$) and ($g_{1}$ , $g_{2}$) are the corresponding eigenvector components and eigenvalues of the matrix given by \citet{1999ssd..book.....M} (see ch 7, pg 276, equation 7.9 and 7.10, with $\alpha_{12} = \alpha$ and $\bar{\alpha_{12}} = 1$)}
-
-% TODO: need to introduce matricies here, also mention that we are describing interaction between a planetesimal and jupiter here
-
-\begin{eqnarray}\label{eq:pert_matrix}
-	A_{jj} = n_{j} \frac{1}{4} \frac{m_{k}}{m_{c} + m_{j}} \alpha b_{3/2}^{(1)} (\alpha) \\ \nonumber
-	A_{jk} = -n_{j} \frac{1}{4} \frac{m_{k}}{m_{c} + m_{j}} \alpha b_{3/2}^{(2)} (\alpha).
-\end{eqnarray}
-
-\noindent \textbf{Here, $n$ is the mean motion of a body and $m$ is its mass.
-The frequency of the secular forcing is simply the difference of the two eigenvalue frequencies $g_{1} - g_{2}$.
-For the case of a Jupiter mass planet at 5.2 au perturbing a test particle at 3 au, the timescale for secular forcing is approximately 12,000 years.}
+\textbf{For the case of a Jupiter mass planet at 5.2 au perturbing a test particle at 3 au, the timescale for secular forcing is approximately 12,000 years. The details of this calculation
+can be found in appendix \ref{sec:sec_forcing_timescale}.}
 
@@
 point to note, which we will revisit later, is that the variation frequency of this angle approaches zero near the edge of a resonance. The 
-width of a resonance can be defined by determining the largest variation in semimajor axis that permits librational, rather than circulatory motion of $\phi$. For 
-second order and higher MMRs, the maximum libration width is given by \citet{1999ssd..book.....M} \textbf{(ch. 8, pg 338, eq. 8.58} as
-
-\begin{equation}\label{eq:res_so}
-	\frac{\delta a}{a} = \pm \left( \frac{16}{3} \frac{\left| C_{r} \right|}{n} e^{\left| q \right|} \right)^{1/2},
-\end{equation}
-
-\noindent where $n$, $a$ and $e$ are the mean motion, semimajor axis and eccentricity of the unperturbed body. $C_{r}$ is a constant defined by 
-$m'/m_{c} n \alpha f_{d}(\alpha)$, where $\alpha$ = $a/a'$ and $f_{d}$ is the resonant part of the disturbing function. For an interior second-order 
-resonance,
-
-\begin{eqnarray}\label{eq:fd_so}
-	f_{d} (\alpha) &=& \frac{1}{8} \left[ -5(p+q) + 4(p+q)^{2} - 2 \alpha D \right. \\ \nonumber
-	                      & + & \left. 4(p+q) \alpha D + \alpha^{2} D^{2} \right] b^{p+q}_{1/2},
-\end{eqnarray}
-
-\noindent (see \citet{1999ssd..book.....M} table 8.1\textbf{, third row, with $j = p + q$}) where $D b^{j}_{s}$ is the first derivative with respect to $\alpha$ of the Laplace coefficient defined in equation \ref{eq:lap}.
-This is given by \citet{1961mcm..book.....B} as
-
-\begin{equation}\label{eq:lap_d}
-	\frac{d b_{s}^{j}}{d \alpha} = s \left( b_{s+1}^{j-1} - 2 \alpha b_{s+1}^{j} + b_{s+1}^{j+1} \right).
-\end{equation}
-
-For a first-order resonance, the associated disturbing function terms are slightly simpler such that
-
-\begin{equation}\label{eq:fd_fo}
-	f_{d}(\alpha) = -(p+q) b_{1/2}^{p+q} - \frac{\alpha}{2} D b_{1/2}^{p+q},
-\end{equation}
-
-\noindent (see \citet{1999ssd..book.....M} table 8.1\textbf{, first row}) and there is an additional contribution to the motion of the critical angle by the pericenter precession rate such that
-
-\begin{equation}\label{eq:res_fo}
-	\frac{\delta a}{a} = \pm \left(\frac{16}{3} \frac{\left| C_{r} \right|}{n} e \right)^{1/2} \left(  1 + \frac{1}{27 p^2 e^3} \frac{\left| C_{r} \right|}{n} 
-	\right)^{1/2} - \frac{2}{9 p e}  \frac{\left| C_{r} \right|}{n}
-\end{equation}
-
-\noindent (see \citet{1999ssd..book.....M} \textbf{ch 8, pg 340,} equation 8.76 \textbf{with $j_{2} = p$}).
-
-\textbf{In mean-motion resonance, the orbital elements of a perturbed body, along with the critical angle described by equation \ref{eq:phi_crit}, will exhibit oscillations.
-In the circular, restricted three-body case, these small amplitude oscillations exhibit a characteristic frequency, given by (see \citet{1999ssd..book.....M} ch 8, pg 332, eq 8.47, with $j_{2} =-p$ and $j_{4} = -q$)}
-
-\begin{equation}\label{eq:lib_time}
-	\omega_{0} = 3 p^{2} C_{r} n e^{\left| -q \right|}.
-\end{equation}
-
-\noindent \textbf{For the most prominent interior mean-motion resonances, including the 2:1 and 3:1, the timescale associated with these oscillations driven by a Jupiter mass planet is  $\sim$ 1,000 - 2,000 years.}
+width of a resonance can be defined by determining the largest variation in semimajor axis that permits librational, rather than circulatory motion of $\phi$. 
+\textbf{Calculations for the widths of first and second order interior MMRs are shown in appendix \ref{sec:libration}, along with a timescale for the libration. For the most prominent interior 
+mean-motion resonances, including the 2:1 and 3:1, the timescale associated with these oscillations driven by a Jupiter mass planet is  $\sim$ 1,000 - 2,000 years.}
 
@@
 straightforward case. Many different parameterizations are possible, depending on optical depth, grain size, disc temperature, etc., but we will avoid 
-such complications here. We normalize the intensity by setting the total disc flux density to be 100 mJy at about 350 GHz.
+such complications here\textbf{, as they would affect the overall brightness profile, but not the presence of any gaps or rings.} We normalize the intensity by
+setting the total disc flux density to be 100 mJy at about 350 GHz.
 
@@
 \textbf{We would again like to emphasize that the dust emission profiles in figure \ref{fig:alma_profiles} are constructed upon the assumption that the radial dust structure closely traces the collision profile of the planetesimals.
-This is only the case if the collisional cascade from which the dust grains form happens before radial drift has a chance to move debris away from the resonances.
-Although we showed with a back-of-the-envelope calculation (see section \ref{sec:dust}) that this is plausible for a typical protoplanetary disk with properties similar to the protosolar nebula, a more thorough treatment of collisional grinding is necessary to be able to interpret the dust emission profiles presented here as anything more than upper limits.}
+For this assumption to be valid, the resulting dust must also remain locally confined, which is can be achieved achieved if the grains are reaccreted onto planetesimals \citep{2015SciA....1E0109J}.
+It is also necessary that the collisional cascade from which the dust grains form plays before radial drift has a chance to move debris away from the resonances.
+Although we showed with a back-of-the-envelope calculation (see section \ref{sec:dust}) that this is plausible for a typical protoplanetary disk with properties similar to the protosolar nebula, a more thorough treatment of collisional grinding and the subsequent evolution of the debris is necessary to be able to interpret the dust emission profiles presented here as anything more than upper limits.}
 
@@
 \appendix
+\section{Timescale for Secular Forcing}\label{sec:sec_forcing_timescale}
+
+\textbf{The timescale for secular forcing is given by the period at which the free eccentricity cycles in the complex plane.
+The time-dependent imaginary and real components of the eccentricity of a planetesimal are given by \citet{1999ssd..book.....M} (see ch 7, pg 282, equation 7.51)}
+
+\begin{eqnarray}\label{eq:kandh}
+	h = e_{1} sin (g_{1} t + \beta_{1}) + e_{2} sin (g_{2} t + \beta_{2}) \\ \nonumber
+	k = e_{1} cos (g_{1} t + \beta_{1}) + e_{2} cos (g_{2} t + \beta_{2}),
+\end{eqnarray}
+
+\noindent \textbf{where  ($e_{1}$, $e_{2}$) and ($g_{1}$ , $g_{2}$) are the corresponding eigenvector components and eigenvalues of a matrix, which describes the secular interaction between two bodies, given by \citet{1999ssd..book.....M} (see ch 7, pg 276, equation 7.9 and 7.10, with $\alpha_{12} = \alpha$ and $\bar{\alpha_{12}} = 1$)}
+
+\begin{eqnarray}\label{eq:pert_matrix}
+	A_{jj} = n_{j} \frac{1}{4} \frac{m_{k}}{m_{c} + m_{j}} \alpha b_{3/2}^{(1)} (\alpha) \\ \nonumber
+	A_{jk} = -n_{j} \frac{1}{4} \frac{m_{k}}{m_{c} + m_{j}} \alpha b_{3/2}^{(2)} (\alpha).
+\end{eqnarray}
+
+\noindent \textbf{Here, $n$ is the mean motion of a body and $m$ is its mass.
+In the case of a massless test particle being perturbed by a giant planet, $m_{0} = m_{g}$ and $m_{2} = 0$.
+The frequency of the secular forcing is simply the difference of the two eigenvalue frequencies $g_{1} - g_{2}$.}
+
+\section{Libration in Mean Motion Resonance}\label{sec:libration}
+
+For second order and higher MMRs, the maximum libration width is given by \citet{1999ssd..book.....M} \textbf{(ch. 8, pg 338, eq. 8.58} as
+
+\begin{equation}\label{eq:res_so}
+	\frac{\delta a}{a} = \pm \left( \frac{16}{3} \frac{\left| C_{r} \right|}{n} e^{\left| q \right|} \right)^{1/2},
+\end{equation}
+
+\noindent where $n$, $a$ and $e$ are the mean motion, semimajor axis and eccentricity of the unperturbed body. $C_{r}$ is a constant defined by 
+$m'/m_{c} n \alpha f_{d}(\alpha)$, where $\alpha$ = $a/a'$ and $f_{d}$ is the resonant part of the disturbing function. For an interior second-order 
+resonance,
+
+\begin{eqnarray}\label{eq:fd_so}
+	f_{d} (\alpha) &=& \frac{1}{8} \left[ -5(p+q) + 4(p+q)^{2} - 2 \alpha D \right. \\ \nonumber
+	                      & + & \left. 4(p+q) \alpha D + \alpha^{2} D^{2} \right] b^{p+q}_{1/2},
+\end{eqnarray}
+
+\noindent (see \citet{1999ssd..book.....M} table 8.1\textbf{, third row, with $j = p + q$}) where $D b^{j}_{s}$ is the first derivative with respect to $\alpha$ of the Laplace coefficient defined in equation \ref{eq:lap}.
+This is given by \citet{1961mcm..book.....B} as
+
+\begin{equation}\label{eq:lap_d}
+	\frac{d b_{s}^{j}}{d \alpha} = s \left( b_{s+1}^{j-1} - 2 \alpha b_{s+1}^{j} + b_{s+1}^{j+1} \right).
+\end{equation}
+
+For a first-order resonance, the associated disturbing function terms are slightly simpler such that
+
+\begin{equation}\label{eq:fd_fo}
+	f_{d}(\alpha) = -(p+q) b_{1/2}^{p+q} - \frac{\alpha}{2} D b_{1/2}^{p+q},
+\end{equation}
+
+\noindent (see \citet{1999ssd..book.....M} table 8.1\textbf{, first row}) and there is an additional contribution to the motion of the critical angle by the pericenter precession rate such that
+
+\begin{equation}\label{eq:res_fo}
+	\frac{\delta a}{a} = \pm \left(\frac{16}{3} \frac{\left| C_{r} \right|}{n} e \right)^{1/2} \left(  1 + \frac{1}{27 p^2 e^3} \frac{\left| C_{r} \right|}{n} 
+	\right)^{1/2} - \frac{2}{9 p e}  \frac{\left| C_{r} \right|}{n}
+\end{equation}
+
+\noindent (see \citet{1999ssd..book.....M} \textbf{ch 8, pg 340,} equation 8.76 \textbf{with $j_{2} = p$}).
+
+\textbf{In mean-motion resonance, the orbital elements of a perturbed body, along with the critical angle described by equation \ref{eq:phi_crit}, will exhibit oscillations.
+In the circular, restricted three-body case, these small amplitude oscillations exhibit a characteristic frequency, given by (see \citet{1999ssd..book.....M} ch 8, pg 332, eq 8.47, with $j_{2} =-p$ and $j_{4} = -q$)}
+
+\begin{equation}\label{eq:lib_time}
+	\omega_{0} = 3 p^{2} C_{r} n e^{\left| -q \right|}.
+\end{equation}
+
 \section{Nonaxisymmetric Structure in Boley 2017}\label{sec:boley_plot}

### 2021-01-25 makeFig.py
Fix title on brightness profile plot

@@ -977,7 +977,7 @@ def make_alma_profile():
 	spec = fig.add_gridspec(ncols=3, nrows=3)
 
 	spec_idx = [[0, 1], [1, 0], [1, 1], [1, 2], [2, 1]]
-	sim_title = ['e2m3', 'e1m2', 'e2m2', 'e2m3', 'e2m1']
+	sim_title = ['e2m3', 'e1m2', 'e2m2', 'e3m2', 'e2m1']
 	for idx in range(len(spec_idx)):
 	    i, j = spec_idx[idx][0], spec_idx[idx][1]
 	    ax = fig.add_subplot(spec[i, j])

### 2021-01-25 refereeResponse.txt
Move figures backward in text a little

@@
-We appreciate the referee's thoughtfulness and perspective and would firstly like to thank them for care and thoroughness that was put into their reviewing.
-We will address comments one by one, with the original comment listed first, followed by our response (indented).
+We appreciate the referee's thorough and careful comments. We will address concerns with the manuscript one by one, with the original comment listed first, followed by our response (indented).
 
@@
 
+	A more detailed discussion of the collision model has been added to the end of section 3.1. Most importantly, it is now explicitly stated that we only model the planetesimal-planetesimal collisions.
+
 1.1) What is the collisional scaling used?
 
-	All collisions result in perferct mergers. This is now stated in section 3.1. We do not model the subsequent evolution of any of the debris.
+	All collisions result in perferct mergers (although the subsequent growth of the planetesimals does not matter much, as no bodies in any of the simulations happen to undergo more than a single collision).
+This is now stated in section 3.1.
+We do not model the subsequent evolution of any of the debris.
 
@@
 
-	A 2 g cm^-3 bulk density corresponds to an even mixture of ice and rock. Because all collisions are assumed to result in perfect mergers, this only affects the mass-radius relation of the bodies.
+	A 2 g cm^-3 bulk density corresponds to an even mixture of ice and rock. Because of our simple collision model, this only affects the mass-radius relation of the bodies.
 
@@
 
-	This is not modeled in the simulations.
+	We assume that there is a direct correspondence between the local collision rate and the amount of dust present.
 As the referee points out below, the spatial evolution of bodies between dust and planetesimal sizes might have a significant influence of the final dust distribution.
-We have made sure to highlight this concern throughout the paper, although a back-of-the-envelope calculation in section 5 shows that this might not be terribly important.
+We have made sure to highlight this concern throughout the paper, and provide a somewhat crude calculation in section 5 which suggests that this assumption is not terribly unreasonable.
 
@@
 
-	We assume that the resulting dust grains are 1mm in size. This is mentioned in section 4.2.
+	We assume that the resulting dust grains are 1mm in size. This is mentioned in section 5 (section 4.2 in the original draft).
 
@@
 In regards to the applicability of this work: one must first understand where and how the planetsimals collide if there is any hope of nailing down what the resulting dust distribution will look like.
-Going from the planetesimal collision profile to a dust emission profile deserves an entire paper by itself and we are certainly not doing that analysis justice here.
+Going from the planetesimal collision profile to a dust emission profile deserves an entire paper by itself and we certainly do not do that analysis justice here.
 
@@
 
-	In the original paper, we checked to ensure that the 300 km planetsimals and the < mm-sized dust grains would stay in place, but the referee's concern about the effects of radial drift of intermediate-sized bodies is an important point that was overlooked.
+	In the original paper, we checked to ensure that the 300 km planetsimals and the mm-sized (and smaller) dust grains would stay in place, but the referee's concern about the effects of radial drift of intermediate-sized bodies is an important point that was overlooked.
 We handle this by: 1.
@@
 		4.
-Scale the planetesimal collision rate (measured in the simulation) by the change in number density and collision cross section if one were to convert the planetesimal population to smaller bodies to get the collision timescale for 1m bodies.
+Scale the planetesimal collision rate (measured in the simulation) by the factor by which the number density and collision cross section would change if one were to convert the planetesimal population to smaller bodies.
+In this way, we get and estimate for the collision timescale for 1m bodies.
 
-	In doing so, we find that the collision timescale for 1m bodies is about 100x smaller than the drift time for those bodies across the resonance.
+	In doing so, we estimate that the collision timescale for 1m bodies is up to 100x-1000x smaller than the drift time for those bodies across the resonance.
 This suggests that radial drift will not have a large influence on the resulting dust dustribution.
 However, the 1m collision timescale should be interpreted as an lower limit, due to assumptions 2.
-and 3.
-We conclude that it is therefore plausible that radial drift does not play an important role, although a full, proper treatment of the collisional cascade and drift process is necessary to actually say this with certainty.
+and 3 listed above.
+We conclude that it is *plausible* that radial drift does not play an important role, although a full, proper treatment of the collisional cascade and drift process is necessary to say this with certainty.
 
@@
 
-    See our response to concern 2)
+    See our response to concern 2). The referee is absolutely correct that the connection we have made between the planetesimal collision profile and the dust profile is rather tenuous.
 
@@
 
-	Other studies which directly resolve planetesimal collisions near MMR (Richarson et al 2000, Dobinson 2013) used an integration time that shorter than the libration timescale of the resonances.
+	Other studies which directly resolve planetesimal collisions near MMR with N-body methods (Richarson et al 2000, Dobinson 2013) used an integration time that shorter than the libration timescale of the resonances.
 This is what we mean by 'severely limited'.
@@
 
-	Regarding other codes that make use of statistical routines or tracer particles (such as Deienno et al.
-2020), the phase space resolution may not be sufficient to fully resolve the dynamics that are happening, particularly near the edges of the resonances.
+	Regarding other codes that make use of tracer particles (such as Deienno et al.
+2020), one would worry that the phase space resolution may not be sufficient to fully resolve the dynamics that are happening, particularly near the edges of the resonances.
+It is doubtful that statistical routines would capture this either, unless it was explicitly built in to the code.
 
 	Given that gas drag does not have a significant influence on the planetsimals (and it's plausible that the same is true for the collisional debris), we do not expect that a longer integration time should affect our results.
-The integration time we chose (5,000 years) is longer than any of the relevant timescales relating to the dynamics of the planetsimals.
-We now calculate all of the relevant timescales relating to the planetesimals in section 2.
-There is now an expanded discussion justifying our choice of integration time at the beginning of section 4.
-In addition section 5 contains a discussion of timescales relating to the collisional debris.
+The integration time we have chosen (5,000 years) is longer than any of the relevant timescales relating to the dynamics of the planetsimals.
+We now present a calculation all of the relevant timescales relating to the dynamics of the planetesimals in section 2.
+We have also added an expanded discussion justifying our choice of integration time to the beginning of section 4.
+In addition, section 5 contains a discussion of timescales relating to the debris from the collisional cascade process.
 
@@
     This is the correct interpretation.
-The outline at the end of the introduction now explains this.
+The outline at the end of the introduction now lays this out.
 In addition, there is a step-by-step description of this process toward the end of section 7 (section 6 in the original draft).
@@
 The phrase 'orbiting externally' was changed to 'orbiting adjacent to'.
+The reason we did not explore exterior MMRs in this work is because doing so is more computationally expensive.
+(Many more orbits required for collisions to occur)
 
@@
 	Although the presence of gas is necessary in order to justify a simple, tractable model for connecting the planetesimal collision profile to the dust profile, the dynamics of the planetesimals and the resulting planetesimal collision profile does not depend very strongly on the gas.
-In a debris disk, it is certainly going to be more difficult to model the collisional dust, but the behavior of the planetesimals should be quite similar.
+In a debris disk, we can't connect the planetesimal collision profile and the dust profile in such a simple way, but the behavior of the planetesimals should be quite similar.
 
@@
 2020 makes use of tracer particles, which is not the case with the other studies we cite here.
-Had we used coarser resolution and taken advantage of tracer particles in this work, the structure seen at the edges of the resonances in figures 7 and 8 (figures 6 and 7 in the original paper), which is critical to generating the features seen in the collision profiles, would likely become washed out.
-The text in the above sentence in the introduction has been modified to clarify that we are only referring to cases where the planetesimals are directly resolved.
+Had we used coarser resolution and taken advantage of tracer particles in this work, the structure seen at the edges of the resonances in figures 7 and 8 (figures 6 and 7 in the original paper), which is critical to generating the features seen in the collision profiles, is unlikely to have been resolved.
+The text in the above sentence in the introduction has been modified to clarify that we are only referring to cases where the planetesimals are directly modeled.
 
@@
 	We have made edits to the abstract, introduction and conclusion to place more emphasis on the behavior of the planetesimals, which should be similar in both a protoplanetary disk and a debris disk.
-As we show in section 2.4 (newly added), the gas has an incredibly weak effect on the planetesimals.
-As the referee has pointed out, our model for the interaction between the collisional debris and the gas is extremely simple.
-Given that we are placing more focus on the full-sized planetesimals, we do not think it is necessary to focus solely on the gas disk phase.
+As we show in section 2.4 (newly added), the gas has an incredibly weak effect on the planetesimals and their resulting motion and collisions should be similar in both a gas-rich and gas-poor system.
 
@@
 
-   Two subsections have been added to section 2 which discuss both gas drag on planetsimals and collisions between planetesimals.
+   Good point! Two additional subsections have been added to section 2, which discuss both gas drag on planetsimals and collisions between planetesimals.
 
@@
     This is now clarified at the end of section 2.4 (gas drag on planetesimals) and in section 3.2 (initial conditions).
-The idea is that we consider the effects gas drag when building the initial conditions, but do not need directly model it during the course of the simulations because the gas drag and viscous stirring timescale is quite long.
-We assume that these two effects are in equilibrium, build them into the initial conditions and then can safely forget about them.
+The idea is that we consider the effects gas drag when building the initial conditions, but do not need directly model it during the course of the simulations because the gas drag and gravitational stirring timescales (which counteract each other) are quite long.
+We assume that these two effects are in equilibrium, build them into the initial conditions (through the eccentricity and inclination dispersions) and then can safely forget about them.
 
@@
 	Chapter, page number and equation number have now been added alongside all equations pulled from Murray and Dermott.
-Although a bit long, the main purpose of this section is to 'show our work' when deriving the secular forcing timescale and libration widths used later in the paper.
+This section has been repurposed a bit, and some of the more detailed parts have been moved to the appendix.
+The main purpose of this section is now to present calculations for the timescales of dynamical effects (secular forcing, libration in MMR, aerodynamic gas drag) that act on the full-sized planetesimals.
+Note that all of the discussion and calculations of the dynamics of the collisional debris is saved for section 5.
+Most of the detailed references to Murray and Dermott have been moved to the appendix, as this is probably an unnecessary amount of detail for the typical reader.
 
@@
 This mistake was carried through when writing up the equations in the paper, although it appears we properly used j4 = -q when doing our analysis and constructing the plots.
-(2p+q) has been replaced by q in equations 5 and 6 in the original draft (equations 7 and 8 in the revised version).
+(2p+q) has been replaced by q in equations 5 and 6 in the original draft (equations 5 and B1 in the revised version).
 
@@
 
-    You are correct. There was a minus sign missing in front of both terms in the paper. This has now been fixed
+    You are correct. There was a minus sign missing in front of both terms in the paper. This has now been fixed.
 
@@
     This section is meant to focus solely on the dynamical effects that the planet has on the full-sized planetesimal population, in order to motivate the initial conditions used in the next section, and also to explain the planetesimal collision profiles shown in section 4.1.
-We are purposefully trying to keep discussion of radial drift and collisional debris as a separate, encapsulated part of the paper in the new version.
+We are purposefully trying to keep discussion of radial drift and collisional debris as a separate, encapsulated part of the paper (section 5) in the new version.
 
@@
 
-    Good idea! While this is a little less specific than what we had before, table 1 does a good job of clearing up any ambiguities.
+    Agreed, the referee's suggestion is much clearer.
 
@@
     See 19) and 20).
-While it is true that the MMSN profile is only based off of solar system planets, this has been a standard benchmark in the field for quite a while and is we do not think it's unreasonable to use.
+alpha = -1,5 has been a standard benchmark in the field for quite a while and is we do not think it's unreasonable to use.
 Furthermore, there is evidence to suggest that the solid surface density profile close to the star is steeper than alpha = -1 (see Chiang + Laughlin 2013, and Dai, F 2020).
@@
     See 8).
-We are considering the gas disk phase here, although it shouldn't matter too much in terms of the outcome of the simulations.
+We are considering the gas disk phase here.
+This shouldn't matter too much in terms of the motion and collisions of the planetesimals, although the presence of the gas is very important to construct the dust profiles.
 More text has been added to this section to explain this more clearly.
@@
 
-    This is referring specifically to the positions of the planetesimals in this figure and not to any kind of debris.
+    This is referring to the positions of the planetesimals in this figure, and not to any kind of debris.
 Even if the smaller fragments do drift significantly, the nonaxisymmetric gaps in the planetesimal distribution should still be present.
-Of course, this would be very difficult to observe.
+Of course, this would wash out all of the interesting features in the dust emission profile.
 This sentence has been modified to clarify that we are specifically talking about the structure seen in figure 1.
@@
 
-    As we now derive in section 2.1, the libration timescale and the secular forcing timescale are much shorter than the stopping time due to gas for the planetesimals, so this figure should not look different had we modeled gas drag in the simulations.
+    As we now calculate in section 2.1, the libration timescale and the secular forcing timescale are much shorter than the stopping time due to gas for the planetesimals, so this figure should not look different had we modeled gas drag in the simulations.
 A typo in the text has been corrected: '7:3' was supposed to say '8:3'.
@@
 What this implies is that the edges of the resonances are important.
-As we approach a resonance from the outside, the critical angle \phi approaches an unstable equilibirum where it is stationary.
+As we approach a resonance from the outside, the critical angle \phi becomes near-stationary (using the pendulum analogy, this corresponds to a bob in the vertical, upside-down position).
 Where the critical angle is near-stationary, the pericenter orientations of the planetesimals experience a torque which causes their \varpi to follow the giant planet in its orbit.
@@
 It is also apparent from figure 1 that the gaps are not aligned with the planet's longitude of pericenter, which should be the case if the structure were due to secular forcing in eccentricity.
-Furthermore, orbits of bodies in resonance experience significant precession, which randomizes their orientations.
-The gap structure cannot be due to the interface between the secularly forced, non-resonant part of the disk, and the randomly oriented orbits of bodies in resonance.
-The latter explanation was given by Tabeshian & Weigert 2016, which, as we point out in our paper, does not quite make sense.
+An explanation similar to the referee's was given by Tabeshian & Weigert 2016, which, as we point out, does not explain why the gaps are misaligned from the planet's longitude of pericenter.
 
@@
 
-    Figures 4 and 5 are showing the probability density of the collision rates.
-The curves on these plots are normalized such that the area under the curve = 1.
+    These are showing the probability density of the collision rates as a function of semimajor axis (fig 4) and distance from the star (fig 5).
+The curves on these plots are normalized such that the area underneath = 1.
 For the orange curve in figure 5, the normalization factor is scaled by the ratio between the total number of collisions in each sample.
@@
 
-    Ask Aaron about this?
+    To clarify, these parameters will alter the overall brightness profile of the dust, but should not affect the features due to the resonances.
+Some additional text has been added to this section to explain this.
 
@@
 
-    This is certainly a big if, although we have shown with a back-of-the-envelope calculation in section 4.2 that it could be plausible.
-We have added some additional text to the end of section 5 to remind the reader that the dust profile is built on some not-so-solid assumptions.
+    This is certainly a big 'if', although we have shown with a back-of-the-envelope calculation in section 5 that the connection between the collision profile and the dust profile is not completely unreasonable.
+We have added some additional text to the end of section 5 to remind the reader that the dust profile is built on somewhat tenuous assumptions.
 
@@
 Given that an expanded discussion of radial drift is now an important part of this paper, we should be more careful not to dismiss the importance of exterior MMRs.
-Here, we have added a sentence mentioning that exterior MMRs might be pretty important if radial drift is modeled.
+Here, we have added a sentence mentioning that exterior MMRs might be important if radial drift is modeled.
 
@@
 
-	No need to apologize. We appreciate your thoroughness and care!
+	No need to apologize. Thank you very much for being so thorough!
+
+	References used in response:
+
+	- Chiang, E. & Laughlin, G., 2013, MNRAS, 431, 3444C
+	- Dai, F. et al., 2020, AJ, 159, 247D

### 2021-01-25 main.tex
Move figures backward in text a little

@@
 
+\begin{figure*}
+\begin{center}
+    \includegraphics[width=\textwidth]{figures/xy.png}
+    \caption{The positions of the remaining planetesimals at the end of the e1m2 (left), e2m2 (center) and e3m2 (right) simulations. The red dot 
+    indicates the position of the giant planet, and the dashed line points in the direction of the planet's longitude of perihelion. Non-axisymmetric gaps 
+    are apparent near the locations of MMRs. At higher eccentricities, more resonances become visible. At the 2:1 MMR, gap features at $\theta$ = 0 
+    and $\theta = \pi$ follow the giant planet in its orbit.\label{fig:xy}}
+\end{center}
+\end{figure*}
+
 \section{Simulations} \label{sec:sims}
@@
 
-\begin{figure*}
-\begin{center}
-    \includegraphics[width=\textwidth]{figures/xy.png}
-    \caption{The positions of the remaining planetesimals at the end of the e1m2 (left), e2m2 (center) and e3m2 (right) simulations. The red dot 
-    indicates the position of the giant planet, and the dashed line points in the direction of the planet's longitude of perihelion. Non-axisymmetric gaps 
-    are apparent near the locations of MMRs. At higher eccentricities, more resonances become visible. At the 2:1 MMR, gap features at $\theta$ = 0 
-    and $\theta = \pi$ follow the giant planet in its orbit.\label{fig:xy}}
-\end{center}
-\end{figure*}
-
 \subsection{Initial Conditions}\label{sec:ics}
@@
 
-\noindent with $\alpha$ = 3/2 and $\Sigma_{0}$ = 10 g cm$^{-2}$. Planetesimals are given a bulk density of 2 g cm$^{-3}$ \textbf{, which corresponds to a mixture of ice and rock)} and a diameter of 
+\noindent with $\alpha$ = 3/2 and $\Sigma_{0}$ = 10 g cm$^{-2}$.
+Planetesimals are given a bulk density of 2 g cm$^{-3}$ \textbf{, which corresponds to a mixture of ice and rock,} and \textbf{are given a} diameter of
 300 km.
@@
 
-\textbf{We first provide a justification for assumption (1), which is as follows: At 3 AU in the protosolar nebula, the mean free path of a gas particle is $\sim$ 50 cm (assuming a composition of pure hydrogen with a local volume density of $\rho_{g} = 4 \times 10^{-10}$ g cm$^{-3}$).
+\textbf{We first provide a justification for assumption (1), which is as follows: At 3 au in the protosolar nebula, the mean free path of a gas particle is $\sim$ 50 cm (assuming a composition of pure hydrogen with a local volume density of $\rho_{g} = 4 \times 10^{-10}$ g cm$^{-3}$).
 This places any dust grains in the Epstein drag regime, with a stopping timescale given by}
@@
 \noindent where $\rho$ is the bulk density of the dust grain, $s$ is its size, and $v_{th}$ is the local thermal velocity of the gas.
-At 3 AU in the protosolar nebula, $v_{th} \sim 10^{5}$ cm s$^{-1}$.
+At 3 au in the protosolar nebula, $v_{th} \sim 10^{5}$ cm s$^{-1}$.
 Assuming a 1 mm dust grain with a $\rho$ = 2 g cm$^{-3}$, the stopping time is $\sim 10^{-4}$ yr.
@@
 \textbf{Radial drift is maximized for bodies of the size at which St = $t_{s} \Omega$ = 1.
-In the Stokes drag regime at 3 AU, this occurs for bodies of 1 meter in size.
+In the Stokes drag regime at 3 au, this occurs for bodies of 1 meter in size.
 Following a similar calculation in \ref{sec:pl_drag} with a 1 m body, we find that an object of this size will drift across the 2:1 MMR on a timescale of $\sim$ 300 years.
@@
 wavelengths where the inner disc is optically thin. This comes at the expense of much poorer resolution. However, future radio facilities like the NG-
-VLA are expected to achieve sub-AU resolution for nearby planet-forming discs \citep{2018ASPC..517..147R}. In the more near-term, techniques 
+VLA are expected to achieve sub-au resolution for nearby planet-forming discs \citep{2018ASPC..517..147R}. In the more near-term, techniques 
 like Gaussian process fitting present a promising way to recover substructure at sub-beam resolution \citep{2020arXiv200507709J}.

### 2021-01-26 main.tex
Once more through the paper

@@
 collisional evolution of planetesimals could therefore create dusty disc structures that would not exist otherwise. Previous studies have shown that morphological differences in the
-collisional dust corotating with a giant planet can be used to determine whether the planet's eccentricity is large or small.In this work, we use N-body simulations that directly resolve
+collisional dust corotating with a giant planet can be used to determine whether the planet's eccentricity is large or small. In this work, we use N-body simulations that directly resolve
 collisions between planetesimals to investigate the collision rate profile near mean-motion resonances. We  find that a distinct bump or dip feature is produced in the collision profile,
-the presence of which depends on the libration width of the resonance and the separation between the peri and apocenter distances of the edges of the resonance. The presence of
+the presence of which depends on the libration width of the resonance and the separation between the peri- and apocenter distances of the edges of the resonance. The presence of
 one of these two features limits possible values for the mass and eccentricity of the planet. Under the simplifying assumption that the radial profile of the dust emission in the disc
-traces the collision profile, we show that a bump or dip feature in the dust emission near the interior 2:1 mean-motion resonance could be used to place constraints
+traces the planetesimal collision profile, we show that the presence of a bump or dip feature in the dust emission near the interior 2:1 mean-motion resonance can be used to place constraints
 on the orbital properties of the perturbing planet. So long as radial drift does not play a significant role in the collisional cascade that grinds planetesimals down to
@@
 
-Collisions between planetesimals are thought to be the principal source of dust for debris discs. \citep[see][]{2008ARA&A..46..339W}.  Although some 
+Collisions between planetesimals are thought to be the principal source of dust for debris discs \citep[see][]{2008ARA&A..46..339W}.  Although some 
 amount of primordial dust is likely still present during the early stages of debris disc evolution, ongoing collisions between small bodies will augment 
@@
 structure, neighbor finding and collision detection can be done quickly and efficiently. This considerably relaxes the constraints on resolution and 
-integration time. With this toolset, we explore the collision rate structure of a planetesimal disc in the vicinity of mean-motion resonances with the planet. In 
+integration time. With this toolset, we explore the collision rate structure of a planetesimal disc in the vicinity of mean-motion resonances with a planet. In 
 particular, we would like to determine (1) \textbf{what dynamics govern the collision rate profile near MMRs, (2)} whether MMRs leave a detectable signature in the collisionally-generated dust, and \textbf{(3)} whether these
@@
 Section \ref{sec:results} presents the results of these simulations \textbf{and we take an in-depth look at the collision rate profiles of the planetesimals near the MMRs.
+In section \ref{sec:dust},  we extrapolate the collision rate down to smaller bodies and motivate a direct correspondence between the planetesimal collision profile and the resulting dust profile.
 In section \ref{sec:constrain}, w}e use the resolved collisions to generate synthetic dust
-emission profiles that would be detected with observing facilities like ALMA.
-\textbf{This is done by making the simplifying assumption that the dust profile closely matches the collision profile of the planetesimals.
-Under this assumption, we show} that a characteristic bump
+emission profiles that would be detected with observing facilities like ALMA. \textbf{Under our simplifying assumptions, we show} that a characteristic bump 
 or dip feature appears in the dust emission near the interior 2:1 MMR, the presence of which depends on the mass and eccentricity of the perturbing 
 planet.
-\textbf{If the 2:1 MMR can be identified (most easily by identifying another prominent MMR, such as the 3:1, and measuring the spacing between the two),} we discuss the potential of using this feature to place constraints on the mass and eccentricity of the planet\textbf{.
+\textbf{If the 2:1 MMR can be identified (presumably, by identifying another prominent MMR, such as the 3:1, and measuring the spacing between the two),} we discuss the potential for using this feature to place constraints on the mass and eccentricity of the planet\textbf{.
 In addition, we highlight the caveats of connecting the dust and planetesimal collision profiles in such a simple way.} \textbf{Finally, we} conclude in section
@@
 The purpose of this is twofold: (1) to motivate the initial conditions used for the simulations described in section \ref{sec:ics} and (2) to justify the exclusion of certain physical effects from our simulations.
-Here, we focus solely on the physics relevant for full-sized ($\sim$100 km) planeteismals and leave a discussion of the effects on smaller bodies generated through collisions for section \ref{sec:dust}.}
+Here, we focus solely on the physics relevant for full-sized ($\sim$100 km) planeteismals and save a discussion of the effects on smaller bodies generated through collisions for section \ref{sec:dust}.}
 
@@
 longitude of pericenter of the giant planet, and $b^{j}_{s} (\alpha)$ is a 
-Laplace coefficient given by \citep{1999ssd..book.....M} as
+Laplace coefficient given by \citep{1999ssd..book.....M} \textbf{(ch. 6, pg. 237, eq. 6.67)} as
 
 \begin{equation}\label{eq:lap}
-	b_{s}^{j}(\alpha) = \frac{1}{2 \pi} \int_{0}^{2 \pi} \frac{\cos \, j \theta \, d \theta}{\left( 1 - 2 \alpha \, \cos \theta + \alpha^2 \right)^{s}}.
+	b_{s}^{j}(\alpha) = \frac{1}{\pi} \int_{0}^{2 \pi} \frac{\cos \, j \psi \, d \psi}{\left( 1 - 2 \alpha \, \cos \psi + \alpha^2 \right)^{s}}.
 \end{equation}
@@
 An important feature of equation \ref{eq:saf} is that for a fixed value of $n$, the collision rate exhibits a global minimum as a function of $v$.
-For small $v$, gravitational focusing allows for more collisions, while for large $v$ the number of encounters simply becomes so large that the collsion rate again increases, even though gravitational focusing does not operate.
-This point will come up again in section \ref{sec:vary_ecc} when we examine the qualitative changes in the collision rate near mean-motion resonances.}
+For small $v$, gravitational focusing facilitates more collisions, while for large $v$ the encounter rate simply becomes so great that the collision rate again increases, even though gravitational focusing is mostly supressed.
+This point will become relevant in section \ref{sec:vary_ecc} when we examine the qualitative changes in the collision rate near mean-motion resonances.}
 
-\textbf{Although equation \ref{eq:saf} works well to describe the collision rate for a homogeneous collection of planetesimals, some problems arise when localized regions of commensurabilities are introduced.
-Namely, the resonances cause the orbits of planetesimals to precess, and an interface between secularly aligned and randomly oriented orbits arises on each side of the resonance.
-Additionally, an interface between dynamically cold and hot planetesimals forms at each side.
-All of these effects cause the number density, collision cross section and encounter velocity to spatially vary in a rather abrupt manner.
-For these reasons, an N-body treatment in which collisions are directly resolved is necessary to understand how the collision rate varies near the MMRs.}
+\textbf{Although equation \ref{eq:saf} works well to describe the collision rate for a homogeneous collection of planetesimals, some problems arise when regions of commensurabilities are introduced.
+Namely, the resonances cause the orbits of planetesimals to precess, and an interface between secularly aligned and randomly oriented orbits arise on each side of the resonance.
+Additionally, an interface between dynamically cold and hot planetesimals develop.
+These two effects cause the number density, collision cross section and encounter velocity to rather abruptly vary across the boundaries of the resonance.
+For this reason, an N-body treatment in which collisions are directly resolved is necessary to understand how the collision rate varies near the MMRs.}
 
@@
 \textbf{Over the course of many orbits, the residual gas from the primordial nebula can damp the eccentricities and inclinations of bodies.
-For a planetesimal-sized body, the geometric cross section is much larger than the mean free path of the gas particles and the timescale for gas drag to significantly alter its relative velocity is given by \citep{1976PThPh..56.1756A}}
+For a planetesimal-sized body, gas drag operates in the Stokes regime and the timescale for aerodynamic forces to significantly alter its relative velocity is given by \citep{1976PThPh..56.1756A}}
 
@@
 \times 10^{-10}$ g cm$^{-3}$ and the typical headwind experienced by a body on a Keplerian orbit is $\sim 5,000$ cm s$^{-1}$ \citep{1981PThPS..70...35H}. For a 100 km body with a 
-density of 2 g cm$^{-3}$ \textbf{(assuming a mixture of ice and rock)} the stopping timescale is on the order of $10^{6}$ years.
-This is much longer than the timescales related to secular forcing and libration near mean-motion resonances, as discussed above, but shorter than the typical protoplanetary disk lifetime and potentially the planetesimal formation timescale.
-For this reason, we do not model the effects of gas drag, although we consider its effects when constructing initial conditions for our simulations, which is discussed in the next section.}
+density of 2 g cm$^{-3}$ \textbf{(assuming a mixture of ice and rock)} the stopping timescale is on the order of 1 Myr.
+This is much longer than the timescales associated with secular forcing and libration due to mean-motion resonances, as discussed above, but shorter than the typical protoplanetary disk lifetime and potentially shorter the planetesimal formation timescale.
+For this reason, we do not model the effects of gas drag in the simulations, although we consider its effects when constructing initial conditions, which is discussed in the next section.}
 
@@
 \textbf{Using similar methods to {\sc PKDGRAV}, which has been used for numerous studies of planet formation \citep{2000Icar..143...45R, 2005ApJ...625..427L, 2013ApJ...777L..31D, 2015ApJ...806...23L}}, {\sc ChaNGa} calculates
-gravitational forces using a modified Barnes-Hut \citep{1986Natur.324..446B} tree with hexadecapole expansions of the moments \textbf{and then integrates the equations of motion using a kick-drift-kick leapfrog scheme}.
+gravitational forces using a modified Barnes-Hut \citep{1986Natur.324..446B} tree with hexadecapole expansions of the moments \textbf{and integrates the equations of motion using a kick-drift-kick leapfrog scheme}.
 All of the simulations we perform use a node opening criterion of $\theta_{BH}$ = 0.7. More information about the code can be found 
@@
 We provide a brief summary of the collision model here, although a full description is provided in \citet{2019MNRAS.489.2159W}.
-This work is largely based on the solid-body collision implementation in {\sc PKDGRAV}, which is described in \citet{1994MNRAS.269..493R} and \citet{2000Icar..143...45R}.
+This work is largely based on the solid-body collision implementation in {\sc PKDGRAV}, which is detailed in \citet{1994MNRAS.269..493R} and \citet{2000Icar..143...45R}.
 Imminent collisions are found during the drift phase of each time step by extrapolating the positions of bodies forward using the velocity calculated during the first kick.
@@
 The resulting body is then imparted with the center of mass position and velocity of its two children.
-Because the resolution of a collision can result in another imminent collision, these events must be resolved one at a time, with the soonest collision being resolved first.
+Because the resolution of a collision can result in another imminent collision, these events must be handled one at a time, with the soonest collision being resolved first.
 For this reason, another collision search is run each time a collision is resolved, which continues until there are no more imminent collisions during the current time step.
@@
 300 km.
-\textbf{This choice of parameters for the planetesimal disk is meant to mimic the setup used in simulation B by \citet{2000Icar..143...45R}.
+\textbf{This choice of parameters is meant to mimic the setup used in simulation B from \citet{2000Icar..143...45R}.
 One difference from the aformentioned study is that we use a narrower annulus, which reduces the number of particles required from $10^6$ down to roughly 500,000.
@@
 
-The dynamical effects of secular forcing by the giant planet, along with  the effects of viscous stirring and gas drag on the planetesimals, are 
+\textbf{Another difference from \citet{2000Icar..143...45R} is that} the dynamical effects of secular forcing by the giant planet, along with the effects of viscous stirring and gas drag on the planetesimals, are
 built into the initial conditions.
-\textbf{Although we do not model the effects of gas drag on the planetesimals during the simulation, we construct the initial conditions such that these two effects are in balance.
-The viscous stirring timescale of the planetesimal disc is much longer than our chosen integration time, and so the dynamical excitation of the disc (excluding resonances) stays constant, even without modeling damping from gas.} This is done by first calculating the equilibrium eccentricity $e_{eq}$ due to viscous stirring and gas drag as a
-function of semimajor axis according to equation 12 of \citet{2002ApJ...581..666K}.
-\textbf{Both the viscous stirring timescale and the gas drag timescale are} long compared to our integration time and should not cause the velocity
-distribution to significantly evolve. The eccentricities of the bodies are drawn randomly from a Rayleigh distribution with a mode of $e_{eq}$, 
+\textbf{Although we do not model the effects of gas drag on the planetesimals during the simulation, we construct the initial conditions such that the effects of gas drag and viscous stirring are in balance.
+The viscous stirring timescale of the planetesimal disc is much longer than our chosen integration time, and so the dynamical excitation of the disc (excluding resonances) stays constant, even without the inclusion of damping forces from the gas.} This is done by first calculating the equilibrium eccentricity $e_{eq}$ due to viscous stirring and gas drag as a
+function of semimajor axis according to equation 12 of \citet{2002ApJ...581..666K}. The eccentricities of the bodies are drawn randomly from a Rayleigh distribution with a mode of $e_{eq}$, 
 while the inclinations are drawn from a similar distribution with a mode of $e_{eq}$/2 \citep{1993MNRAS.263..875I}. The arguments of perihelion 
@@
 For the purposes of the integrator, there are two relevant timescales in this system. The first is the orbital dynamical time $\sqrt{a^3/
-G M_{\odot}}$. Experimentally, we have found that using a base timestep size with {\sc ChaNGa} of 3\% of an orbital dynamical time
+G M_{\odot}}$. \textbf{Through experimentation}, we have found that using a base timestep size with {\sc ChaNGa} of 3\% of an orbital dynamical time
 at the inner edge of the disc keeps the integration symplectic. Although doing so preserves orbital frequencies, the errors associated with
@@
 An additional timescale is set by the dynamical time of the planetesimals ($\sim 1/\sqrt{G \rho}$), which is about 45 minutes.
-\textbf{This timescale must be resolved in order to properly follow close gravitational encounters between these bodies.}.
+\textbf{This timescale must be resolved in order to properly follow close gravitational encounters between these bodies}.
 To
-resolve the base time step and the dynamical timescale of planetesimals simultaneously, we use a two-tiered time stepping scheme following
+resolve the base time step and the dynamical timescale of planetesimals simultaneously, we use a two-tiered time stepping scheme, following
 \citep{2015ApJ...806...23L}. 
@@
 Although one might worry that a single libration period may not be long enough for the orbital structure due to the resonances to develop, we find that the shape of the semimajor axis-eccentricity distribution of the planetesimals reaches a steady state by this time.
-This is largely due to the fact that there are enough bodies in or near the resonances to allow an ensemble average of phase space, rather a time average.
+This is largely due to the fact that there are enough bodies in or near the resonances to allow an ensemble average of phase space, rather than a time average.
 As an additional confirmation, we find that the time evolution of the collision rate near the resonances maintains a steady state in all five simulations after $\sim$ 2000 years.}
@@
 \citet{2016ApJ...818..159T} (figure 3\textbf{a}). This structure is also present in the \citet{2017ApJ...850..103B} simulations, although it was not reported at the 
-time (see Appendix \ref{sec:boley_plot}). It is worth noting that \citet{2000Icar..143...45R} started with a completely cold planetesimal disc and a 
-Jupiter mass planet on a circular, coplanar
-orbit. \citet{2017ApJ...850..103B} used a similar setup.
-Thus, the presence of these features seems robust 
-to the choice of initial conditions.
+time (see Appendix \ref{sec:boley_plot}).
+\textbf{It is worth noting that both \citet{2000Icar..143...45R} and \citet{2017ApJ...850..103B} started with a completely cold planetesimal disc.} Thus, the presence of these features seems robust to the choice of initial conditions.
 
 The effects of the resonances become much more apparent in semimajor axis-eccentricity space, which is shown in figure \ref{fig:ae}. In all cases, 
-the 3:1, 2:1 and 5:3 resonances are readily visible as ``spikes'' in the eccentricity that bend slightly inward (due to the conservation of $E_{J}$). In the 
-e3m2 simulation, features also appear near the 5:2, 7:3 and 5:3 resonances. The absence of these features from the e1m2 simulation can be 
+the 3:1, 2:1 and 5:3 resonances are readily visible as ``spikes'' in the eccentricity that bend slightly inward (due to the conservation of \textbf{the Jacobi energy}). In the 
+e3m2 simulation, features also appear near the 5:2, 7:3 and 5:3 resonances. The absence of these \textbf{finer} features from the e1m2 simulation can be 
 explained by the fact that the strength of a resonance scales with $e^{q}$ \citep{1994PhyD...77..289M}.
@@
 \citet{2000Icar..143...45R}, who simulated a similar setup and found no discernible features near the MMRs. We attribute the differences to a more 
-conservative timestepping criterion in our simulations. The most prominent features appear as \textbf{a local maximum in} the collision rate near the 2:1 
+conservative timestepping criterion in our simulations\textbf{, along with the inclusion of secular perturbations in our initial conditions}.
+The most prominent features appear as \textbf{a local maximum in} the collision rate near the 2:1
 MMR and a \textbf{local minimum} near the 3:1 MMR. At higher forced eccentricities, features near the 5:2, \textbf{8}:3 and 5:3 resonances are also visible, due to the 
@@
 Each pair of points connected by a line represents the average collision rate before and after the effects of the mean-motion resonances develop.
-For this figure, the relative velocity between bodies is calculated by measuring the eccentricity and inclination dispersion near each resonance and using equation \ref{eq:eccincvel}.
-Here, we assume that the eccentricity and inclination dispersions are coupled \citep{1993MNRAS.263..875I} and use the eccentricity dispersion as the independent variable.
+Here, the relative velocity between bodies is calculated by measuring the eccentricity and inclination dispersion near each resonance and using equation \ref{eq:eccincvel}.
+We assume that the eccentricity and inclination dispersions are coupled \citep{1993MNRAS.263..875I} and use the eccentricity dispersion as an independent variable.
 Because both the strength of secular forcing and the effects of the resonant perturbations are different near the 3:1 and 2:1 MMRs, the planetesimal population at each of these locations in the disk experiences a qualitatively different change in the collision rate.
 Near the 3:1 MMR, the unperturbed collision rate is well above the minimum value $\left< \sigma v \right>_{0}$ and the dynamical heating introduced by the resonance acts to suppress it further.
-Near the 2:1 MMR, the collision rate starts out much closer to the minimum value and the additional perturbations are strong enough to drive it higher.}
+Near the 2:1 MMR, the collision rate starts out much closer to the minimum value and the additional perturbations instead act to drive it higher.}
 
@@
 In semimajor axis space, prominent features appear near the 3:1 and 2:1 MMRs.
-Near the 3:1, the collision rate decreases from its unperturbed value, while an enhancement appears near the 2:1.\label{fig:coll_hist_a}}
+Near the 3:1, the collision rate \textbf{exhibits a local minimum}, while an enhancement appears near the 2:1.\label{fig:coll_hist_a}}
 \end{center}
@@
     \caption{\textbf{The collision rate (given by equation \ref{eq:saf}) of bodies in the vicinity of the 3:1 (left) and 2:1 (right) MMRs, relative to the minimum value, as a function of the local eccentricity dispersion.
-The pairs of points connected by lines show the values of the perturbed (left-hand points in each subplot) and unperturbed (right-hand points) collision rates in the e1m2, e2m2 and e3m2 simulations.}\label{fig:gf}}
+The pairs of points connected by lines show the values of the perturbed (left-hand points in each subplot) and unperturbed (right-hand points) collision rates in the e1m2, e2m2 and e3m2 simulations.
+The unpertburbed collision rate, along with the amount of dynamical heating that the planetesimal population experiences determines whether the MMR acts to suppress or enhance the collision rate.}\label{fig:gf}}
 \end{center}
@@
 
-To construct a radial dust profile from the collision statistics, we begin by making \textbf{two assumptions: (1) any dust generated by collisions is strongly coupled to the gas and (2) any subsequent spatial evolution of the collisional debris is insignificant.} \textbf{So long as both of these assumptions are true, we can use the locations of planetesimal collisions in the plane of the disk to generate a dust profile for each simulation.}
+To construct a radial dust profile from the collision statistics, we begin by making \textbf{two assumptions: (1) any dust generated by collisions is strongly coupled to the gas and (2) any subsequent spatial evolution of the collisional debris is insignificant.} \textbf{So long as both of these assumptions are true, we can use the radial locations of planetesimal collisions in the plane of the disk to generate a dust profile for each simulation.}
 
@@
 If the entire planetesimal population in this region were converted to 1 meter bodies with the same bulk density, the number density of bodies increases by a factor of $10^{15}$, while the geometric collision cross section decreases by a factor of $10^{10}$.
-The collision timescale would therefore decrease to $\sim$ 1 year.
+The collision timescale would therefore decrease to $\sim$ 1 year, which is 2 orders of magnitude smaller than the drift timescale.
 As shown above, radial drift in the Stokes drag regime is maximized for bodies of 1 meter in size, which is only a factor of two larger than the mean free path of the gas particles.
@@
 Because of this, we also repeat the above calculation for bodies that experience Epstein drag.
-With this assumption, we find that radial drift is maximized for a cm-sized body.
-If one were to instead convert all of the collisional debris to objects of this size, the collision timescale decreases by another factor of 100.
-We conclude that the true collision timescale for bodies with maximal radial drift lies somewhere between $10^{-2}$ and 1 year.
-From this crude calculation, it appears plausible that the collision timescale for the fastest inward drifting bodies is smaller than their drift timescale across the 2:1 MMR.
-We argue that it is reasonable and, indeed, best practice to start with such simple assumptions understand the physics before additional complexity is later added.}
+With this assumption, we find that radial drift is maximized for a cm-sized body and both the radial drift and collision timescale for bodies of that size decrease by a factor of 10 relative to the Stokes values.
+In both cases, collisions between maximally drifting bodies occur on a timescale two orders of magnitude shorter than the drift timescale.
+We therefore argue that it is reasonable and, indeed, best practice to start with such simple assumptions understand the physics before additional complexity is later added.
+We caution, however, that the collision timescale estimates provided here should be interpreted as lower limits.}
 
@@
 of second-generation dust can be constructed from the cylindrical distance at which the collisions occur.
-\textbf{Here, cylindrical distance is defined as the separation between the central star and the pointt of collision in the ($r, \theta$) plane.} This is shown in figure \ref{fig:coll_hist_r}.
+\textbf{Here, cylindrical distance is defined as the separation between the central star and the location of collision in the ($r, \theta$) plane.} This is shown in figure \ref{fig:coll_hist_r}.
 Similar to figure \ref{fig:coll_hist_a}, we use a KDE with a width of 0.02 au to assemble the collision locations into a radial distribution. Most 
 strikingly, the bump that was present near the 2:1 resonance is no longer visible in cylindrical distance space, although it suddenly appears again in 
-the e3m2 simulation. The dip that is visible near the 3:1 MMR also becomes a bump in the highest eccentricity case. To determine how the resonant 
+the e3m2 simulation. The \textbf{local minimum} that is visible near the 3:1 MMR also becomes a \textbf{local maximum} in the highest eccentricity case. To determine how the resonant 
 bodies actually contribute to the radial collision profile, we excluded collisions that fall between $2.495 < a < 2.505$ au (near the 3:1 resonance) and 
@@
 \textbf{As in figure \ref{fig:coll_hist_a}, the solid curves are normalized such that the area underneath is equal to 1.
-For the dashed curves, the normalization factor is scaled down according to the total number of collisions in the entire sample and the number of collisions in the subsample which excludes the collisions in resonance.} Qualitatively, none of the bump or dip features present
+For the dashed curves, the normalization factor is scaled according to the number of collisions in the entire sample, compared to the number of collisions in the subsample, which excludes the collisions in resonance.} Qualitatively, none of the bump or dip features present
 are removed by making this exclusion. This suggests that the features near resonance seen in semimajor axis space become smeared out in 
@@
 the resonant population does make some of the features more pronounced. To further understand this, we consider the nonaxisymmetric structure 
-seen in figure \ref{fig:xy}. We compare in figure \ref{fig:coll_polar_e} the radial collision profile to the radial structure seen in the e1m2, e2m2 and 
+seen in figure \ref{fig:xy}. In figure \ref{fig:coll_polar_e}, we compare the radial collision profiles to the radial structure seen in the e1m2, e2m2 and 
 e3m2 simulations. In the lowest forced eccentricity case (e1m2), the pileups near the edge of the 2:1 MMR line up with the boundaries of the dip 
@@
 the planet that temporarily drives their pericenters toward the current orbital position of the planet. After the encounter ends, differential rotation of the disc 
-slowly destroys the configuration over part of an orbit. As the planet passes by, adjacent planetesimals near the resonance edges temporarily align 
+slowly undoes the configuration. As the planet again passes by, adjacent planetesimals near the resonance edges temporarily align 
 themselves in this configuration.
@@
 of the path that a resonant test particle takes in a frame co-rotating with the planet (see figure 8.4 of \citet{1999ssd..book.....M}).
-\textbf{In other words, the gap structure is argued to be due to the interfaces between the low eccentricity, non-resonant and high eccentricity resonant regions of the disc.} This explanation,
+\textbf{In other words, the gap structure is argued to be due to the interfaces between the low eccentricity, non-resonant and high eccentricity, resonant regions of the disc.} This explanation,
 however, does not hold for a large collection of planetesimals, especially when there is no forced eccentricity. In such a case, the orbits of 
-planetesimals near resonance would be randomly aligned, and the axisymmetric structure should become washed out. When the perturbing 
+planetesimals near resonance would be randomly aligned, and the axisymmetric structure should become washed out. Furthermore, when the perturbing 
 planet is on a circular orbit, this structure is still present (see figure 3 of \citet{2016ApJ...818..159T} and Appendix \ref{sec:boley_plot}). The only 
 connection between the structure of the gaps in the disc and the path of a resonant particle in the corotating frame is that both phenomena produce the 
-same symmetries, which depend on the particular MMR.
+same symmetries, which depend on the particular MMR considered.
 
@@
 setting the precipitable water vapor to 1.5 mm. They are then combined, imaged, and cleaned
-using the task {\tt tclean}. Imaging uses Briggs weighting with a robustness 
-parameter of -1.
+using the task {\tt tclean}. Imaging uses Briggs weighting with a robustness parameter of -1.
 
@@
     \includegraphics[width=0.5\textwidth]{alma/xy_e2m2.png}
-    \caption{Simulated ALMA observations for the nominal (e2m2) case.
+    \caption{Simulated ALMA observations for the nominal (e2m2) case\textbf{, operating under the assumption that the dust profile closely traces the planetesimal collision profile}.
 Top: The sky model based on the radial collision distribution.
@@
     \caption{The azimuthally-averaged radial profile based on the simulated cleaned images from all five simulations.
-The eccentricty of the perturbing planet increases from left to right, while the mass of the planet increases from bottom to top.
+The eccentricity of the perturbing planet increases from left to right, while the mass of the planet increases from bottom to top.
 The vertical dashed lines indicate the locations of the 3:1 and 2:1 resonances.
@@
     \includegraphics[width=0.5\textwidth]{figures/bump_dip_diag.png}
-    \caption{The presence of a dip or bump near the 2:1 MMR can be used to constrain the mass and eccentricity
+    \caption{The presence of a dip or bump \textbf{in the collision profile (and therefore the dust profile)} near the 2:1 MMR can be used to constrain the mass and eccentricity
     of the perturbing planet. The color scale indicates the relative strength of the features, while the dashed lines
@@
 \textbf{We would again like to emphasize that the dust emission profiles in figure \ref{fig:alma_profiles} are constructed upon the assumption that the radial dust structure closely traces the collision profile of the planetesimals.
-For this assumption to be valid, the resulting dust must also remain locally confined, which is can be achieved achieved if the grains are reaccreted onto planetesimals \citep{2015SciA....1E0109J}.
+For this assumption to be valid, the resulting dust must remain locally confined, which is can be achieved achieved if the grains are reaccreted onto planetesimals \citep{2015SciA....1E0109J}.
 It is also necessary that the collisional cascade from which the dust grains form plays before radial drift has a chance to move debris away from the resonances.
@@
 \textbf{The morphology of these features are tied to dynamical behavior of bodies near the edges of the resonances, where the circulation frequency of the critical angle approaches infinity.
-Particularly near the 2:1 MMR, we find that a bump or dip in the collsion profile forms when collisions are ordered by cylindrical distance.
+Particularly near the 2:1 MMR, we find that a bump or dip in the collision profile forms when collisions are ordered by cylindrical distance.
 The presence of one of these two features depends on the peri- and apocenter distances of the edges of the resonance, relative to the libration width.
@@
 So long as the dust grains are well-coupled to the gas and radial drift does not have a significant effect on the morphology of the dust, the bump or dip features seen in the collision profile will also appear in the dust profile.
-Assuming that this is the case, we have generated simulated observations of a protoplanetary disk by ALMA and shown that the bump or dip features seen in the collision profiles should be detectable through the dust emission.
-From a dust emission profile with sufficiently strong radial features, one could constrain the properties of a perturbing planet on an exterior orbit in the following way: (1) identify the locations of two resonances in the disc (2) measure the spacing between them to verify that one of the features is indeed associated with the 2:1 MMR (3) determine whether an under- or overdensity in the radial dust profile exists near this location (4) use the presence of one of these two features to determine the region of the eccentricity-mass plane in which the planet lies.}
+Assuming that this is the case, we have generated simulated observations of a protoplanetary disk with ALMA and showed that the bump or dip features seen in the collision profiles should be detectable through the dust emission.
+From a dust emission profile with sufficiently strong radial features, one could constrain the properties of a perturbing planet on an exterior orbit in the following way: (1) identify the locations of two MMRs in the disc (2) measure the spacing between them to verify that one of the features is indeed associated with the 2:1 MMR (3) determine whether an under- or overdensity in the radial dust profile exists near this location (4) use the presence of one of these two features to determine the region of the eccentricity-mass plane in which the planet lies.}
 
@@
 2:1 exterior MMR. Whether this would alter the radial collision profile for the exterior, rather than the interior 2:1 resonance, is not immediately clear.  
-\textbf{On one hand,} the solid surface density diminishes with distance ($\sim r^{-3/2}$ for the MMSN \citep{1981PThPS..70...35H}), \textbf{which would weaken the signal from locally generated collisional dust.} \textbf{On the other hand, exterior MMRs are quite effective at capturing inward drifting bodies (cite), which could locally enhance the surface density well beyond the MMSN value.
+\textbf{On one hand,} the solid surface density diminishes with distance ($\sim r^{-3/2}$ for the MMSN \citep{1981PThPS..70...35H}), \textbf{which would weaken the signal from locally generated collisional dust.} \textbf{On the other hand, exterior MMRs are quite effective at capturing inward drifting bodies \citep{1985Icar...62...16W}, which could locally enhance the surface density well beyond the MMSN value.
 A full treatment of the collisional cascade process and the radial drift of debris is a subject that we leave for future work.}
@@
 variations in the dust emission near MMRs is much more subtle and requires much higher spatial resolution and sensitivity. As we have shown, the 
-bump vs dip feature near the 2:1 MMR is marginally detectable with ALMA for the nearest protoplanetary discs\textbf{, so long as the dust profile closely matches the collisional profile of the planetesimals.}.
+bump vs dip feature near the 2:1 MMR is marginally detectable with ALMA for the nearest protoplanetary discs\textbf{, so long as the dust profile closely matches the collisional profile of the planetesimals}.
 Another complicating factor is that
@@
 
-\textbf{The timescale for secular forcing is given by the period at which the free eccentricity cycles in the complex plane.
-The time-dependent imaginary and real components of the eccentricity of a planetesimal are given by \citet{1999ssd..book.....M} (see ch 7, pg 282, equation 7.51)}
+\textbf{The timescale for secular forcing is given by the period at which the free eccentricity of a body cycles in the complex plane.
+The time-dependent imaginary and real components of the eccentricity of a planetesimal are given by \citet{1999ssd..book.....M} (see ch.
+7, pg.
+282, eq.
+7.51)}
 
@@
 
-\noindent \textbf{where  ($e_{1}$, $e_{2}$) and ($g_{1}$ , $g_{2}$) are the corresponding eigenvector components and eigenvalues of a matrix, which describes the secular interaction between two bodies, given by \citet{1999ssd..book.....M} (see ch 7, pg 276, equation 7.9 and 7.10, with $\alpha_{12} = \alpha$ and $\bar{\alpha_{12}} = 1$)}
+\noindent \textbf{where  ($e_{1}$, $e_{2}$) and ($g_{1}$ , $g_{2}$) are the corresponding eigenvector components and eigenvalues of a matrix, which describes the secular interaction between two bodies, given by \citet{1999ssd..book.....M} (see ch.
+7, pg.
+276, eq.
+7.9 and 7.10, with $\alpha_{12} = \alpha$ and $\bar{\alpha_{12}} = 1$)}
 
@@
 \noindent \textbf{Here, $n$ is the mean motion of a body and $m$ is its mass.
-In the case of a massless test particle being perturbed by a giant planet, $m_{0} = m_{g}$ and $m_{2} = 0$.
+In the case of a massless test particle being perturbed by a giant planet, $m_{1} = m_{g}$ and $m_{2} = 0$.
 The frequency of the secular forcing is simply the difference of the two eigenvalue frequencies $g_{1} - g_{2}$.}
@@
 
-For second order and higher MMRs, the maximum libration width is given by \citet{1999ssd..book.....M} \textbf{(ch. 8, pg 338, eq. 8.58} as
+For second order and higher MMRs, the maximum libration width is given by \citet{1999ssd..book.....M} \textbf{(ch. 8, pg. 338, eq. 8.58)} as
 
@@
 
-\noindent (see \citet{1999ssd..book.....M} \textbf{ch 8, pg 340,} equation 8.76 \textbf{with $j_{2} = p$}).
+\noindent (see \citet{1999ssd..book.....M} \textbf{ch. 8, pg. 340,} eq. 8.76 \textbf{with $j_{2} = p$}).
 
 \textbf{In mean-motion resonance, the orbital elements of a perturbed body, along with the critical angle described by equation \ref{eq:phi_crit}, will exhibit oscillations.
-In the circular, restricted three-body case, these small amplitude oscillations exhibit a characteristic frequency, given by (see \citet{1999ssd..book.....M} ch 8, pg 332, eq 8.47, with $j_{2} =-p$ and $j_{4} = -q$)}
+In the circular, restricted three-body case, these small amplitude oscillations exhibit a characteristic frequency, given by (see \citet{1999ssd..book.....M} ch.
+8, pg.
+332, eq.
+8.47, with $j_{2} =-p$ and $j_{4} = -q$)}
 

### 2021-01-26 main.tex
Clean up newlines and indentation in tex file

@@
 one of these two features limits possible values for the mass and eccentricity of the planet. Under the simplifying assumption that the radial profile of the dust emission in the disc
-traces the planetesimal collision profile, we show that the presence of a bump or dip feature in the dust emission near the interior 2:1 mean-motion resonance can be used to place constraints
-on the orbital properties of the perturbing planet. So long as radial drift does not play a significant role in the collisional cascade that grinds planetesimals down to
-dust, or if other processes limit the dust to be approximately local, this feature in the dust emission should be marginally observable in nearby protoplanetary disks with ALMA.}
+traces the planetesimal collision profile, we show that the presence of a bump or dip feature in the dust emission near the interior 2:1 mean-motion resonance can be used to place 
+constraints on the orbital properties of the perturbing planet. So long as radial drift does not play a significant role in the collisional cascade that grinds planetesimals down to dust, or if 
+other processes limit the dust to be approximately local, this feature in the dust emission should be marginally observable in nearby protoplanetary disks with ALMA.}
 \end{abstract}
@@
 the planet.  The width of a resonance is set by both the mass of the perturbing planet and the unperturbed eccentricity of the planetesimals, 
-which is in turn set by the eccentricity of the planet through secular forcing.
-Therefore, \textbf{the planetesimal collision profile and potentially} the structure of second generation dust produced near MMRs
-may encode information about both the mass and eccentricity of the planet.
+which is in turn set by the eccentricity of the planet through secular forcing. Therefore, \textbf{the planetesimal collision profile and potentially} the structure of second generation 
+dust produced near MMRs may encode information about both the mass and eccentricity of the planet.
 
@@
 So far, studies of planetesimal dynamics near MMRs \textbf{in which the planetesimals are directly resovled} have involved either collisionless test particles 
-\citep{2017ApJ...850..103B, 2016ApJ...818..159T, 2018ApJ...857....3T} or \textbf{integration times that do not fully capture the dynamics of the resonances} \citep{2000Icar..143...45R, 2013ApJ...777L..31D}.
+\citep{2017ApJ...850..103B, 2016ApJ...818..159T, 2018ApJ...857....3T} or \textbf{integration times that do not fully capture the dynamics of the resonances} 
+\citep{2000Icar..143...45R, 2013ApJ...777L..31D}.
 
@@
 integration time. With this toolset, we explore the collision rate structure of a planetesimal disc in the vicinity of mean-motion resonances with a planet. In 
-particular, we would like to determine (1) \textbf{what dynamics govern the collision rate profile near MMRs, (2)} whether MMRs leave a detectable signature in the collisionally-generated dust, and \textbf{(3)} whether these
-signatures can be used to determine or constrain the orbital properties of the perturbing planet.
+particular, we would like to determine (1) \textbf{what dynamics govern the collision rate profile near MMRs, (2)} whether MMRs leave a detectable signature in the
+collisionally-generated dust, and \textbf{(3)} whether these signatures can be used to determine or constrain the orbital properties of the perturbing planet.
 
@@
 of a planetesimal disc under the gravitational influence of an external perturber. In section \ref{sec:sims} we provide an overview of the N-body code 
-used and describe the initial conditions chosen for five simulations in which a perturbing giant planet is given various masses 
-and eccentricities.
-Section \ref{sec:results} presents the results of these simulations \textbf{and we take an in-depth look at the collision rate profiles of the planetesimals near the MMRs.
-In section \ref{sec:dust},  we extrapolate the collision rate down to smaller bodies and motivate a direct correspondence between the planetesimal collision profile and the resulting dust profile.
-In section \ref{sec:constrain}, w}e use the resolved collisions to generate synthetic dust
+used and describe the initial conditions chosen for five simulations in which a perturbing giant planet is given various masses  and eccentricities. Section
+\ref{sec:results} presents the results of these simulations \textbf{and we take an in-depth look at the collision rate profiles of the planetesimals near the MMRs. 
+In section \ref{sec:dust},  we extrapolate the collision rate down to smaller bodies and motivate a direct correspondence between the planetesimal collision profile
+and the resulting dust profile. In section \ref{sec:constrain}, w}e use the resolved collisions to generate synthetic dust 
 emission profiles that would be detected with observing facilities like ALMA. \textbf{Under our simplifying assumptions, we show} that a characteristic bump 
 or dip feature appears in the dust emission near the interior 2:1 MMR, the presence of which depends on the mass and eccentricity of the perturbing 
-planet.
-\textbf{If the 2:1 MMR can be identified (presumably, by identifying another prominent MMR, such as the 3:1, and measuring the spacing between the two),} we discuss the potential for using this feature to place constraints on the mass and eccentricity of the planet\textbf{.
-In addition, we highlight the caveats of connecting the dust and planetesimal collision profiles in such a simple way.} \textbf{Finally, we} conclude in section
-\ref{sec:conclusions}.
+planet. \textbf{If the 2:1 MMR can be identified (presumably, by identifying another prominent MMR, such as the 3:1, and measuring the spacing between the two),} we discuss the 
+potential for using this feature to place constraints on the mass and eccentricity of the planet\textbf{. In addition, we highlight the caveats of connecting the dust and planetesimal collision 
+profiles in such a simple way.} \textbf{Finally, we} conclude in section \ref{sec:conclusions}.
 
@@
 
-\textbf{We begin by providing a description of the dynamical effects responsible for shaping the orbital distribution of the planetesimals.
-The purpose of this is twofold: (1) to motivate the initial conditions used for the simulations described in section \ref{sec:ics} and (2) to justify the exclusion of certain physical effects from our simulations.
-Here, we focus solely on the physics relevant for full-sized ($\sim$100 km) planeteismals and save a discussion of the effects on smaller bodies generated through collisions for section \ref{sec:dust}.}
+\textbf{We begin by providing a description of the dynamical effects responsible for shaping the orbital distribution of the planetesimals. The purpose of this is twofold: (1) to motivate
+the initial conditions used for the simulations described in section \ref{sec:ics} and (2) to justify the exclusion of certain physical effects from our simulations. Here, we focus solely on the 
+physics relevant for full-sized ($\sim$100 km) planeteismals and save a discussion of the effects on smaller bodies generated through collisions for section \ref{sec:dust}.}
 
@@
 
-\noindent\textbf{where $v_{k}$ is the local Keplerian velocity.
-The second term in equation \ref{eq:saf} can be thought of as an additional enhancement to the collision cross section due to gravitational focusing.
-When the typical encounter velocity is small compared to the mutual escape velocity of the planetesimals, the collision cross section greatly exceeds the geometric value.
-An important feature of equation \ref{eq:saf} is that for a fixed value of $n$, the collision rate exhibits a global minimum as a function of $v$.
-For small $v$, gravitational focusing facilitates more collisions, while for large $v$ the encounter rate simply becomes so great that the collision rate again increases, even though gravitational focusing is mostly supressed.
+\noindent\textbf{where $v_{k}$ is the local Keplerian velocity. The second term in equation \ref{eq:saf} can be thought of as an additional enhancement to the collision cross section due to 
+gravitational focusing. When the typical encounter velocity is small compared to the mutual escape velocity of the planetesimals, the collision cross section greatly exceeds the geometric 
+value. An important feature of equation \ref{eq:saf} is that for a fixed value of $n$, the collision rate exhibits a global minimum as a function of $v$. For small $v$, gravitational focusing 
+facilitates more collisions, while for large $v$ the encounter rate simply becomes so great that the collision rate again increases, even though gravitational focusing is mostly surpressed. 
 This point will become relevant in section \ref{sec:vary_ecc} when we examine the qualitative changes in the collision rate near mean-motion resonances.}
 
-\textbf{Although equation \ref{eq:saf} works well to describe the collision rate for a homogeneous collection of planetesimals, some problems arise when regions of commensurabilities are introduced.
-Namely, the resonances cause the orbits of planetesimals to precess, and an interface between secularly aligned and randomly oriented orbits arise on each side of the resonance.
-Additionally, an interface between dynamically cold and hot planetesimals develop.
-These two effects cause the number density, collision cross section and encounter velocity to rather abruptly vary across the boundaries of the resonance.
-For this reason, an N-body treatment in which collisions are directly resolved is necessary to understand how the collision rate varies near the MMRs.}
+\textbf{Although equation \ref{eq:saf} works well to describe the collision rate for a homogeneous collection of planetesimals, some problems arise when regions of commensurabilities are 
+introduced. Namely, the resonances cause the orbits of planetesimals to precess, and an interface between secularly aligned and randomly oriented orbits arise on each side of the 
+resonance. Additionally, an interface between dynamically cold and hot planetesimals develop. These two effects cause the number density, collision cross section and encounter velocity 
+to rather abruptly vary across the boundaries of the resonance. For this reason, an N-body treatment in which collisions are directly resolved is necessary to understand how the collision 
+rate varies near the MMRs.}
 
@@
 
-\textbf{Over the course of many orbits, the residual gas from the primordial nebula can damp the eccentricities and inclinations of bodies.
-For a planetesimal-sized body, gas drag operates in the Stokes regime and the timescale for aerodynamic forces to significantly alter its relative velocity is given by \citep{1976PThPh..56.1756A}}
+\textbf{Over the course of many orbits, the residual gas from the primordial nebula can damp the eccentricities and inclinations of bodies. For a planetesimal-sized body, gas drag operates 
+in the Stokes regime and the timescale for aerodynamic forces to significantly alter its relative velocity is given by \citep{1976PThPh..56.1756A}}
 
@@
 \noindent \textbf{where $m$ and $s$ are the mass and radius of the planetesimal. $C_{D}$ is a drag coefficient which is of order unity, $
-\rho_{g}$ is the local density of the gas and $v_{g}$ is the headwind velocity of the gas experienced by the planetesimal. At 3 au, the gaseous component of the solar nebula has a density of $4 
-\times 10^{-10}$ g cm$^{-3}$ and the typical headwind experienced by a body on a Keplerian orbit is $\sim 5,000$ cm s$^{-1}$ \citep{1981PThPS..70...35H}. For a 100 km body with a 
-density of 2 g cm$^{-3}$ \textbf{(assuming a mixture of ice and rock)} the stopping timescale is on the order of 1 Myr.
-This is much longer than the timescales associated with secular forcing and libration due to mean-motion resonances, as discussed above, but shorter than the typical protoplanetary disk lifetime and potentially shorter the planetesimal formation timescale.
-For this reason, we do not model the effects of gas drag in the simulations, although we consider its effects when constructing initial conditions, which is discussed in the next section.}
+\rho_{g}$ is the local density of the gas and $v_{g}$ is the headwind velocity of the gas experienced by the planetesimal. At 3 au, the gaseous component of the solar nebula has a
+density of $4 \times 10^{-10}$ g cm$^{-3}$ and the typical headwind experienced by a body on a Keplerian orbit is $\sim 5,000$ cm s$^{-1}$ \citep{1981PThPS..70...35H}. For a 100 km 
+body with a density of 2 g cm$^{-3}$ \textbf{(assuming a mixture of ice and rock)} the stopping timescale is on the order of 1 Myr. This is much longer than the timescales associated with 
+secular forcing and libration due to mean-motion resonances, as discussed above, but shorter than the typical protoplanetary disk lifetime and potentially shorter the planetesimal 
+formation timescale. For this reason, we do not model the effects of gas drag in the simulations, although we consider its effects when constructing initial conditions, which is discussed in 
+the next section.}
 
@@
 This code, which is written in the {\sc CHARM++} parallel programming language, was originally designed for cosmology simulations 
-and has been shown to perform well on up to half a million processors \citep{2015AphCom..2..1}.
-\textbf{Using similar methods to {\sc PKDGRAV}, which has been used for numerous studies of planet formation \citep{2000Icar..143...45R, 2005ApJ...625..427L, 2013ApJ...777L..31D, 2015ApJ...806...23L}}, {\sc ChaNGa} calculates
-gravitational forces using a modified Barnes-Hut \citep{1986Natur.324..446B} tree with hexadecapole expansions of the moments \textbf{and integrates the equations of motion using a kick-drift-kick leapfrog scheme}.
-All of the simulations we perform use a node opening criterion of $\theta_{BH}$ = 0.7. More information about the code can be found 
-in \citet{2008IEEEpds...ChaNGa}.
+and has been shown to perform well on up to half a million processors \citep{2015AphCom..2..1}. \textbf{Using similar methods to {\sc PKDGRAV}, which has been used for numerous 
+studies of planet formation \citep{2000Icar..143...45R, 2005ApJ...625..427L, 2013ApJ...777L..31D, 2015ApJ...806...23L}}, {\sc ChaNGa} calculates 
+gravitational forces using a modified Barnes-Hut \citep{1986Natur.324..446B} tree with hexadecapole expansions of the moments \textbf{and integrates the equations of motion using a 
+kick-drift-kick leapfrog scheme}. All of the simulations we perform use a node opening criterion of $\theta_{BH}$ = 0.7. More information about the code can be found in 
+\citet{2008IEEEpds...ChaNGa}.
 
-\textbf{We have recently modified {\sc ChaNGa} to handle solid-body collisions between particles, by assigning them a fixed radius, rather than treating them as tracers of a fluid with a characteristic softening length.
-We provide a brief summary of the collision model here, although a full description is provided in \citet{2019MNRAS.489.2159W}.
-This work is largely based on the solid-body collision implementation in {\sc PKDGRAV}, which is detailed in \citet{1994MNRAS.269..493R} and \citet{2000Icar..143...45R}.
-Imminent collisions are found during the drift phase of each time step by extrapolating the positions of bodies forward using the velocity calculated during the first kick.
-For each body, the nearest 64 neighbors are tested for an imminent collision.
-If an imminent collision is detected, the two particles of mass $m_{1}$ and $m_{2}$ are merged together together to form one single larger body with the same density and a mass of $m_{1} + m_{2}$.
-The resulting body is then imparted with the center of mass position and velocity of its two children.
-Because the resolution of a collision can result in another imminent collision, these events must be handled one at a time, with the soonest collision being resolved first.
-For this reason, another collision search is run each time a collision is resolved, which continues until there are no more imminent collisions during the current time step.
-During the course of the simulation, no debris is created by collisions.
-To model the collisionally generated dust distribution, we use the statistics of the resolved planetesimal collisions to build dust profile.
-This process is discussed in detail in section \ref{sec:dust}.}
+\textbf{We have recently modified {\sc ChaNGa} to handle solid-body collisions between particles, by assigning them a fixed radius, rather than treating them as tracers of a fluid with a 
+characteristic softening length. We provide a brief summary of the collision model here, although a full description is provided in \citet{2019MNRAS.489.2159W}. This work is largely based 
+on the solid-body collision implementation in {\sc PKDGRAV}, which is detailed in \citet{1994MNRAS.269..493R} and \citet{2000Icar..143...45R}. Imminent collisions are found during the 
+drift phase of each time step by extrapolating the positions of bodies forward using the velocity calculated during the first kick. For each body, the nearest 64 neighbors are tested for an 
+imminent collision. If an imminent collision is detected, the two particles of mass $m_{1}$ and $m_{2}$ are merged together together to form one single larger body with the same density 
+and a mass of $m_{1} + m_{2}$. The resulting body is then imparted with the center of mass position and velocity of its two children. Because the resolution of a collision can result in 
+another imminent collision, these events must be handled one at a time, with the soonest collision being resolved first. For this reason, another collision search is run each time a collision 
+is resolved, which continues until there are no more imminent collisions during the current time step. During the course of the simulation, no debris is created by collisions. To model the 
+collisionally generated dust distribution, we use the statistics of the resolved planetesimal collisions to build dust profile. This process is discussed in detail in section \ref{sec:dust}.}
 
@@
 
-In total, five simulations are run, which are listed in table
-\ref{tab:sims}. The second
-is a ``nominal'' case, in which the perturbing planet's mass and 
-eccentricity are set to that of Jupiter's.
-In the other four cases, the mass \textbf{or eccentricity is altered} by a factor of two \textbf{from} the nominal value.
-In all cases, the perturbing giant is placed on a 5.2 au orbit around a 1 $M_{\odot}$ star.
-The
-planetesimal disc extends from 2.2 to 3.8 au, which covers the two most prominent mean-motion resonances with the giant planet, the 2:1 at 3.27 au 
-and the 3:1 at 2.5 au. The planetesimal disc follows a minimum-mass solar nebula surface density profile \citep{1981PThPS..70...35H}
+In total, five simulations are run, which are listed in table \ref{tab:sims}. The second is a ``nominal'' case, in which the perturbing planet's mass and eccentricity are set to that of Jupiter's. 
+In the other four cases, the mass \textbf{or eccentricity is altered} by a factor of two \textbf{from} the nominal value. In all cases, the perturbing giant is placed on a 5.2 au orbit around a 1 
+$M_{\odot}$ star. The planetesimal disc extends from 2.2 to 3.8 au, which covers the two most prominent mean-motion resonances with the giant planet, the 2:1 at 3.27 au and the 3:1 at 
+2.5 au. The planetesimal disc follows a minimum-mass solar nebula surface density profile \citep{1981PThPS..70...35H}
 
@@
 
-\noindent with $\alpha$ = 3/2 and $\Sigma_{0}$ = 10 g cm$^{-2}$.
-Planetesimals are given a bulk density of 2 g cm$^{-3}$ \textbf{, which corresponds to a mixture of ice and rock,} and \textbf{are given a} diameter of
-300 km.
-\textbf{This choice of parameters is meant to mimic the setup used in simulation B from \citet{2000Icar..143...45R}.
-One difference from the aformentioned study is that we use a narrower annulus, which reduces the number of particles required from $10^6$ down to roughly 500,000.
-This allows us to use a finer base timestep size, which, as we will discuss in section \ref{sec:results}, appears to be the reason why no features were seen in the collision profile near the resonances by \citet{2000Icar..143...45R}}.
+\noindent with $\alpha$ = 3/2 and $\Sigma_{0}$ = 10 g cm$^{-2}$. Planetesimals are given a bulk density of 2 g cm$^{-3}$ \textbf{, which corresponds to a mixture of ice and rock,} and 
+\textbf{are given a} diameter of 300 km. \textbf{This choice of parameters is meant to mimic the setup used in simulation B from \citet{2000Icar..143...45R}. One difference from the 
+aformentioned study is that we use a narrower annulus, which reduces the number of particles required from $10^6$ down to roughly 500,000. This allows us to use a finer base timestep 
+size, which, as we will discuss in section \ref{sec:results}, appears to be the reason why no features were seen in the collision profile near the resonances by \citet{2000Icar..143...45R}}.
 
-\textbf{Another difference from \citet{2000Icar..143...45R} is that} the dynamical effects of secular forcing by the giant planet, along with the effects of viscous stirring and gas drag on the planetesimals, are
-built into the initial conditions.
-\textbf{Although we do not model the effects of gas drag on the planetesimals during the simulation, we construct the initial conditions such that the effects of gas drag and viscous stirring are in balance.
-The viscous stirring timescale of the planetesimal disc is much longer than our chosen integration time, and so the dynamical excitation of the disc (excluding resonances) stays constant, even without the inclusion of damping forces from the gas.} This is done by first calculating the equilibrium eccentricity $e_{eq}$ due to viscous stirring and gas drag as a
-function of semimajor axis according to equation 12 of \citet{2002ApJ...581..666K}. The eccentricities of the bodies are drawn randomly from a Rayleigh distribution with a mode of $e_{eq}$, 
-while the inclinations are drawn from a similar distribution with a mode of $e_{eq}$/2 \citep{1993MNRAS.263..875I}. The arguments of perihelion 
-$\omega$, longitude of ascending nodes $\Omega$ and the mean anomalies $M$ of the bodies are drawn uniformly $\in [0, 2 \pi)$.
+\textbf{Another difference from \citet{2000Icar..143...45R} is that} the dynamical effects of secular forcing by the giant planet, along with the effects of viscous stirring and gas drag on the 
+planetesimals, are built into the initial conditions. \textbf{Although we do not model the effects of gas drag on the planetesimals during the simulation, we construct the initial conditions 
+such that the effects of gas drag and viscous stirring are in balance. The viscous stirring timescale of the planetesimal disc is much longer than our chosen integration time, and so the 
+dynamical excitation of the disc (excluding resonances) stays constant, even without the inclusion of damping forces from the gas.} This is done by first calculating the equilibrium 
+eccentricity $e_{eq}$ due to viscous stirring and gas drag as a function of semimajor axis according to equation 12 of \citet{2002ApJ...581..666K}. The eccentricities of the bodies are 
+drawn randomly from a Rayleigh distribution with a mode of $e_{eq}$, while the inclinations are drawn from a similar distribution with a mode of $e_{eq}$/2 \citep{1993MNRAS.263..875I}. 
+The arguments of perihelion $\omega$, longitude of ascending nodes $\Omega$ and the mean anomalies $M$ of the bodies are drawn uniformly $\in [0, 2 \pi)$.
 
@@
 
-An additional timescale is set by the dynamical time of the planetesimals ($\sim 1/\sqrt{G \rho}$), which is about 45 minutes.
-\textbf{This timescale must be resolved in order to properly follow close gravitational encounters between these bodies}.
-To
-resolve the base time step and the dynamical timescale of planetesimals simultaneously, we use a two-tiered time stepping scheme, following
-\citep{2015ApJ...806...23L}. 
-To start, all bodies are placed on the base time step. A first pass of collision detection is then run in 
-which the radii of all bodies are inflated by a factor of 2.5. Any bodies with imminent collisions predicted using the inflated radii are 
-placed on a time step that is a factor of 16 smaller than the orbital
-time step. Although this is still a factor of roughly 7 larger than the dynamical time of a planetesimal, we found no difference in the collision rate
-when using any smaller of a minimum time step size.
-The purpose of the two-tiered scheme is to properly resolve 
-the gravitational interactions between any bodies that undergo a close encounter. This prevents the coarser base time step from 
+An additional timescale is set by the dynamical time of the planetesimals ($\sim 1/\sqrt{G \rho}$), which is about 45 minutes. \textbf{This timescale must be resolved in order to properly 
+follow close gravitational encounters between these bodies}. To resolve the base time step and the dynamical timescale of planetesimals simultaneously, we use a two-tiered time 
+stepping scheme, following\citep{2015ApJ...806...23L}. To start, all bodies are placed on the base time step. A first pass of collision detection is then run in which the radii of all bodies are 
+inflated by a factor of 2.5. Any bodies with imminent collisions predicted using the inflated radii are placed on a time step that is a factor of 16 smaller than the orbital time step. Although 
+this is still a factor of roughly 7 larger than the dynamical time of a planetesimal, we found no difference in the collision rate when using any smaller of a minimum time step size.The 
+purpose of the two-tiered scheme is to properly resolve the gravitational interactions between any bodies that undergo a close encounter. This prevents the coarser base time step from 
 reducing the effectiveness of gravitational focusing, while minimizing the additional computational expense.
@@
 motion resonances are not built into the initial conditions, the simulations must be run long enough for the distribution of orbital elements to reach 
-equilibrium near the resonances before the collision rate is measured.
-\textbf{To do so, we allow each simulation to run for 2,000 years before we begin recording any collision statistics.
-This is comparable to the libration period, which was calculated in section \ref{sec:mmr} for the 3:1 and 2:1 resonance.
-Although one might worry that a single libration period may not be long enough for the orbital structure due to the resonances to develop, we find that the shape of the semimajor axis-eccentricity distribution of the planetesimals reaches a steady state by this time.
-This is largely due to the fact that there are enough bodies in or near the resonances to allow an ensemble average of phase space, rather than a time average.
-As an additional confirmation, we find that the time evolution of the collision rate near the resonances maintains a steady state in all five simulations after $\sim$ 2000 years.}
+equilibrium near the resonances before the collision rate is measured. \textbf{To do so, we allow each simulation to run for 2,000 years before we begin recording any collision statistics. 
+This is comparable to the libration period, which was calculated in section \ref{sec:mmr} for the 3:1 and 2:1 resonance. Although one might worry that a single libration period may not be 
+long enough for the orbital structure due to the resonances to develop, we find that the shape of the semimajor axis-eccentricity distribution of the planetesimals reaches a steady state by 
+this time. This is largely due to the fact that there are enough bodies in or near the resonances to allow an ensemble average of phase space, rather than a time average. As an additional 
+confirmation, we find that the time evolution of the collision rate near the resonances maintains a steady state in all five simulations after $\sim$ 2000 years.}
 
@@
 \citet{2016ApJ...818..159T} (figure 3\textbf{a}). This structure is also present in the \citet{2017ApJ...850..103B} simulations, although it was not reported at the 
-time (see Appendix \ref{sec:boley_plot}).
-\textbf{It is worth noting that both \citet{2000Icar..143...45R} and \citet{2017ApJ...850..103B} started with a completely cold planetesimal disc.} Thus, the presence of these features seems robust to the choice of initial conditions.
+time (see Appendix \ref{sec:boley_plot}). \textbf{It is worth noting that both \citet{2000Icar..143...45R} and \citet{2017ApJ...850..103B} started with a completely cold planetesimal disc.} 
+Thus, the presence of these features seems robust to the choice of initial conditions.
 
@@
 construct a \textbf{probability density function (PDF)} of the collisions using a Kernel Density Estimate (KDE). We use the {\sc neighbors.KernelDensity} function from the {\sc sklearn} 
-\citep{scikit-learn} package to construct our KDEs, using a gaussian kernel with a FWHM of 0.02 au.
-\textbf{The curves shown in figure \ref{fig:coll_hist_a} are normalized such that the area underneath is equal to 1.}
+\citep{scikit-learn} package to construct our KDEs, using a gaussian kernel with a FWHM of 0.02 au. \textbf{The curves shown in figure \ref{fig:coll_hist_a} are normalized such that the 
+area underneath is equal to 1.}
 
@@
 \citet{2000Icar..143...45R}, who simulated a similar setup and found no discernible features near the MMRs. We attribute the differences to a more 
-conservative timestepping criterion in our simulations\textbf{, along with the inclusion of secular perturbations in our initial conditions}.
-The most prominent features appear as \textbf{a local maximum in} the collision rate near the 2:1
-MMR and a \textbf{local minimum} near the 3:1 MMR. At higher forced eccentricities, features near the 5:2, \textbf{8}:3 and 5:3 resonances are also visible, due to the 
-steep sensitivity of higher order resonant perturbations to eccentricity \citep{1994PhyD...77..289M}.
+conservative timestepping criterion in our simulations\textbf{, along with the inclusion of secular perturbations in our initial conditions}. The most prominent features appear as \textbf{a 
+local maximum in} the collision rate near the 2:1 MMR and a \textbf{local minimum} near the 3:1 MMR. At higher forced eccentricities, features near the 5:2, \textbf{8}:3 and 5:3 
+resonances are also visible, due to the steep sensitivity of higher order resonant perturbations to eccentricity \citep{1994PhyD...77..289M}.
 
-\textbf{Although the features in figure \ref{fig:coll_hist_a} near the 3:1 and 2:1 MMRs appear qualitatively different, they can be explained by one single dynamical process.
-As discussed in section \ref{sec:colleq}, the collision rate between planetesimals depends on both the encounter rate and the strength of gravitational focusing.
-The encounter rate grows as the relative velocity $v$ between the planetesimals increases, while gravitational focusing is most effective for bodies with small relative velocities.
-There is therefore an intermediate value of $v$ for which the average collision rate $\left< \sigma v \right>$ is at a minimum, which we will refer to as  $\left< \sigma v \right>_{0}$.
-The dynamical excitation induced by a mean motion resonance can either increase or decrease the local average collision rate, depending on the unperturbed value of  $\left< \sigma v \right>$ relative to  $\left< \sigma v \right>_{0}$.}
+\textbf{Although the features in figure \ref{fig:coll_hist_a} near the 3:1 and 2:1 MMRs appear qualitatively different, they can be explained by one single dynamical process. As discussed in 
+section \ref{sec:colleq}, the collision rate between planetesimals depends on both the encounter rate and the strength of gravitational focusing. The encounter rate grows as the relative 
+velocity $v$ between the planetesimals increases, while gravitational focusing is most effective for bodies with small relative velocities. There is therefore an intermediate value of $v$ for 
+which the average collision rate $\left< \sigma v \right>$ is at a minimum, which we will refer to as  $\left< \sigma v \right>_{0}$. The dynamical excitation induced by a mean motion 
+resonance can either increase or decrease the local average collision rate, depending on the unperturbed value of  $\left< \sigma v \right>$ relative to  $\left< \sigma v \right>_{0}$.}
 
-\textbf{In figure \ref{fig:gf}, we show the effect that the 2:1 MMR and 3:1 MMR have on the local average collision rate.
-Each pair of points connected by a line represents the average collision rate before and after the effects of the mean-motion resonances develop.
-Here, the relative velocity between bodies is calculated by measuring the eccentricity and inclination dispersion near each resonance and using equation \ref{eq:eccincvel}.
-We assume that the eccentricity and inclination dispersions are coupled \citep{1993MNRAS.263..875I} and use the eccentricity dispersion as an independent variable.
-Because both the strength of secular forcing and the effects of the resonant perturbations are different near the 3:1 and 2:1 MMRs, the planetesimal population at each of these locations in the disk experiences a qualitatively different change in the collision rate.
-Near the 3:1 MMR, the unperturbed collision rate is well above the minimum value $\left< \sigma v \right>_{0}$ and the dynamical heating introduced by the resonance acts to suppress it further.
-Near the 2:1 MMR, the collision rate starts out much closer to the minimum value and the additional perturbations instead act to drive it higher.}
+\textbf{In figure \ref{fig:gf}, we show the effect that the 2:1 MMR and 3:1 MMR have on the local average collision rate. Each pair of points connected by a line represents the average 
+collision rate before and after the effects of the mean-motion resonances develop. Here, the relative velocity between bodies is calculated by measuring the eccentricity and inclination 
+dispersion near each resonance and using equation \ref{eq:eccincvel}. We assume that the eccentricity and inclination dispersions are coupled \citep{1993MNRAS.263..875I} and use the 
+eccentricity dispersion as an independent variable. Because both the strength of secular forcing and the effects of the resonant perturbations are different near the 3:1 and 2:1 MMRs, the 
+planetesimal population at each of these locations in the disk experiences a qualitatively different change in the collision rate. Near the 3:1 MMR, the unperturbed collision rate is well 
+above the minimum value $\left< \sigma v \right>_{0}$ and the dynamical heating introduced by the resonance acts to suppress it further. Near the 2:1 MMR, the collision rate starts out 
+much closer to the minimum value and the additional perturbations instead act to drive it higher.}
 
-\textbf{ This explains the relative drop in the collision rate
-near the 3:1 MMR and the relative increase near the 2:1 and 5:3
-resonances \textbf{seen in figure \ref{fig:coll_hist_a}}. Although this could potentially serve as a useful
-diagnostic of the planetesimal size in a disc (\textbf{because the size and mass of the planetesimals sets the eccentricity dispersion at which $\left< \sigma v \right>$ is minimized}), a direct measurement of the
-semimajor axes of the colliding planetesimals is not
-possible. Furthermore, as we will demonstrate next, collisions due to bodies in resonance do not have a significant effect on the final shape of the radial dust distribution that we predict.}
+\textbf{ This explains the relative drop in the collision rate near the 3:1 MMR and the relative increase near the 2:1 and 5:3 resonances \textbf{seen in figure \ref{fig:coll_hist_a}}. Although 
+this could potentially serve as a useful diagnostic of the planetesimal size in a disc (\textbf{because the size and mass of the planetesimals sets the eccentricity dispersion at which 
+$\left< \sigma v \right>$ is minimized}), a direct measurement of the semimajor axes of the colliding planetesimals is not possible. Furthermore, as we will demonstrate next, collisions due 
+to bodies in resonance do not have a significant effect on the final shape of the radial dust distribution that we predict.}
 
@@
     \includegraphics[width=0.5\textwidth]{figures/coll_hist_a.png}
-    \caption{A PDF of the collision rate in each disc as a function of semimajor axis, generated using a KDE with a Gaussian kernel with a FWHM of 0.02 au.
-In semimajor axis space, prominent features appear near the 3:1 and 2:1 MMRs.
-Near the 3:1, the collision rate \textbf{exhibits a local minimum}, while an enhancement appears near the 2:1.\label{fig:coll_hist_a}}
+    \caption{A PDF of the collision rate in each disc as a function of semimajor axis, generated using a KDE with a Gaussian kernel with a FWHM of 0.02 au. In semimajor axis space, 
+    prominent features appear near the 3:1 and 2:1 MMRs. Near the 3:1, the collision rate \textbf{exhibits a local minimum}, while an enhancement appears near the 
+    2:1.\label{fig:coll_hist_a}}
 \end{center}
@@
     \includegraphics[width=\textwidth]{figures/gf_plot.png}
-    \caption{\textbf{The collision rate (given by equation \ref{eq:saf}) of bodies in the vicinity of the 3:1 (left) and 2:1 (right) MMRs, relative to the minimum value, as a function of the local eccentricity dispersion.
-The pairs of points connected by lines show the values of the perturbed (left-hand points in each subplot) and unperturbed (right-hand points) collision rates in the e1m2, e2m2 and e3m2 simulations.
-The unpertburbed collision rate, along with the amount of dynamical heating that the planetesimal population experiences determines whether the MMR acts to suppress or enhance the collision rate.}\label{fig:gf}}
+    \caption{\textbf{The collision rate (given by equation \ref{eq:saf}) of bodies in the vicinity of the 3:1 (left) and 2:1 (right) MMRs, relative to the minimum value, as a function of the local 
+    eccentricity dispersion. The pairs of points connected by lines show the values of the perturbed (left-hand points in each subplot) and unperturbed (right-hand points) collision rates in 
+    the e1m2, e2m2 and e3m2 simulations. The unpertburbed collision rate, along with the amount of dynamical heating that the planetesimal population experiences determines whether 
+    the MMR acts to suppress or enhance the collision rate.}\label{fig:gf}}
 \end{center}
@@
     \includegraphics[width=0.5\textwidth]{figures/coll_hist_r.png}
-    \caption{Here, collisions are instead ordered by cylindrical distance from the star.
-Features near the 3:1 and 2:1 MMRs are still present, but appear qualitatively different than in semimajor axis space.
-At low eccentricities, a dip appears around the center of the resonance.
-At the highest eccentricity, a bump is formed instead.
-The dashed lines shown the collision profile with collisions between bodies in resonance removed.
-The bump and dip features remain qualitatively the same, which suggests that they are produced by bodies \textbf{outside of the libration width of the resonance.}\label{fig:coll_hist_r}}
+    \caption{Here, collisions are instead ordered by cylindrical distance from the star. Features near the 3:1 and 2:1 MMRs are still present, but appear qualitatively different than in 
+    semimajor axis space. At low eccentricities, a dip appears around the center of the resonance. At the highest eccentricity, a bump is formed instead. The dashed lines shown the 
+    collision profile with collisions between bodies in resonance removed. The bump and dip features remain qualitatively the same, which suggests that they are produced by bodies 
+    \textbf{outside of the libration width of the resonance.}\label{fig:coll_hist_r}}
 \end{center}
@@
 
-To construct a radial dust profile from the collision statistics, we begin by making \textbf{two assumptions: (1) any dust generated by collisions is strongly coupled to the gas and (2) any subsequent spatial evolution of the collisional debris is insignificant.} \textbf{So long as both of these assumptions are true, we can use the radial locations of planetesimal collisions in the plane of the disk to generate a dust profile for each simulation.}
+To construct a radial dust profile from the collision statistics, we begin by making \textbf{two assumptions: (1) any dust generated by collisions is strongly coupled to the gas and (2) any 
+subsequent spatial evolution of the collisional debris is insignificant.} \textbf{So long as both of these assumptions are true, we can use the radial locations of planetesimal collisions in the 
+plane of the disk to generate a dust profile for each simulation.}
 
-\textbf{We first provide a justification for assumption (1), which is as follows: At 3 au in the protosolar nebula, the mean free path of a gas particle is $\sim$ 50 cm (assuming a composition of pure hydrogen with a local volume density of $\rho_{g} = 4 \times 10^{-10}$ g cm$^{-3}$).
-This places any dust grains in the Epstein drag regime, with a stopping timescale given by}
+\textbf{We first provide a justification for assumption (1), which is as follows: At 3 au in the protosolar nebula, the mean free path of a gas particle is $\sim$ 50 cm (assuming a composition 
+of pure hydrogen with a local volume density of $\rho_{g} = 4 \times 10^{-10}$ g cm$^{-3}$). This places any dust grains in the Epstein drag regime, with a stopping timescale given by}
 
@@
 
-\noindent where $\rho$ is the bulk density of the dust grain, $s$ is its size, and $v_{th}$ is the local thermal velocity of the gas.
-At 3 au in the protosolar nebula, $v_{th} \sim 10^{5}$ cm s$^{-1}$.
-Assuming a 1 mm dust grain with a $\rho$ = 2 g cm$^{-3}$, the stopping time is $\sim 10^{-4}$ yr.
-This is orders of magnitude smaller than the
+\noindent where $\rho$ is the bulk density of the dust grain, $s$ is its size, and $v_{th}$ is the local thermal velocity of the gas. At 3 au in the protosolar nebula, $v_{th} \sim 10^{5}$ cm 
+s$^{-1}$. Assuming a 1 mm dust grain with a $\rho$ = 2 g cm$^{-3}$, the stopping time is $\sim 10^{-4}$ yr.  This is orders of magnitude smaller than the 
 orbital timescale, therefore we conclude that collisionally generated dust grains will immediately couple to the gas.
 
-\textbf{Assumption (2) is less straightforward to justify and may not be reasonable in all cases.
-Although the spatial redistribution of the full-sized planetesimals and mm-sized dust grains is insignificant, the radial drift forces experienced by intermediate-sized bodies is much greater.
-Collisions between planetesimals do not immediately convert the mass to dust grains.
-Rather, the debris will undergo a collisional cascade process, which gradually grinds the resulting bodies down to smaller sizes.
-A proper treatment of the collisional cascade process, is quite complicated and is well beyond the scope of this work.
-However, one can safely ignore this process if the peak radial drift timescale is longer than the timescale for collisions between these bodies.}
+\textbf{Assumption (2) is less straightforward to justify and may not be reasonable in all cases. Although the spatial redistribution of the full-sized planetesimals and mm-sized dust grains 
+is insignificant, the radial drift forces experienced by intermediate-sized bodies is much greater. Collisions between planetesimals do not immediately convert the mass to dust grains. 
+Rather, the debris will undergo a collisional cascade process, which gradually grinds the resulting bodies down to smaller sizes. A proper treatment of the collisional cascade process, is 
+quite complicated and is well beyond the scope of this work. However, one can safely ignore this process if the peak radial drift timescale is longer than the timescale for collisions 
+between these bodies.}
 
-\textbf{Radial drift is maximized for bodies of the size at which St = $t_{s} \Omega$ = 1.
-In the Stokes drag regime at 3 au, this occurs for bodies of 1 meter in size.
-Following a similar calculation in \ref{sec:pl_drag} with a 1 m body, we find that an object of this size will drift across the 2:1 MMR on a timescale of $\sim$ 300 years.
-Although we do not model collisions between bodies of this size, a lower limit on the collision timescale for these objects can be obtained by extrapolating the planetesimal collision rate measured in our simulations down.
-For the e2m2 simulation, we find that 125 collisions occur within the libration width of the 2:1 MMR from T=2,000 yr to  T=5,000 yr.
-There are a total of 15,000 planetesimals within this region, which means that a single planetesimal undergoes a collision every $\sim$ 370,000 years on average.
-If the entire planetesimal population in this region were converted to 1 meter bodies with the same bulk density, the number density of bodies increases by a factor of $10^{15}$, while the geometric collision cross section decreases by a factor of $10^{10}$.
-The collision timescale would therefore decrease to $\sim$ 1 year, which is 2 orders of magnitude smaller than the drift timescale.
-As shown above, radial drift in the Stokes drag regime is maximized for bodies of 1 meter in size, which is only a factor of two larger than the mean free path of the gas particles.
-It is therefore not entirely clear if the Stokes drag law is appropriate here.
-Because of this, we also repeat the above calculation for bodies that experience Epstein drag.
-With this assumption, we find that radial drift is maximized for a cm-sized body and both the radial drift and collision timescale for bodies of that size decrease by a factor of 10 relative to the Stokes values.
-In both cases, collisions between maximally drifting bodies occur on a timescale two orders of magnitude shorter than the drift timescale.
-We therefore argue that it is reasonable and, indeed, best practice to start with such simple assumptions understand the physics before additional complexity is later added.
-We caution, however, that the collision timescale estimates provided here should be interpreted as lower limits.}
+\textbf{Radial drift is maximized for bodies of the size at which St = $t_{s} \Omega$ = 1. In the Stokes drag regime at 3 au, this occurs for bodies of 1 meter in size. Following a similar 
+calculation in \ref{sec:pl_drag} with a 1 m body, we find that an object of this size will drift across the 2:1 MMR on a timescale of $\sim$ 300 years. Although we do not model collisions 
+between bodies of this size, a lower limit on the collision timescale for these objects can be obtained by extrapolating the planetesimal collision rate measured in our simulations down. For 
+the e2m2 simulation, we find that 125 collisions occur within the libration width of the 2:1 MMR from T=2,000 yr to  T=5,000 yr. There are a total of 15,000 planetesimals within this region, 
+which means that a single planetesimal undergoes a collision every $\sim$ 370,000 years on average. If the entire planetesimal population in this region were converted to 1 meter bodies 
+with the same bulk density, the number density of bodies increases by a factor of $10^{15}$, while the geometric collision cross section decreases by a factor of $10^{10}$. The collision 
+timescale would therefore decrease to $\sim$ 1 year, which is 2 orders of magnitude smaller than the drift timescale. As shown above, radial drift in the Stokes drag regime is maximized 
+for bodies of 1 meter in size, which is only a factor of two larger than the mean free path of the gas particles. It is therefore not entirely clear if the Stokes drag law is appropriate here. 
+Because of this, we also repeat the above calculation for bodies that experience Epstein drag. With this assumption, we find that radial drift is maximized for a cm-sized body and both the 
+radial drift and collision timescale for bodies of that size decrease by a factor of 10 relative to the Stokes values. In both cases, collisions between maximally drifting bodies occur on a 
+timescale two orders of magnitude shorter than the drift timescale. We therefore argue that it is reasonable and, indeed, best practice to start with such simple assumptions understand the 
+physics before additional complexity is later added. We caution, however, that the collision timescale estimates provided here should be interpreted as lower limits.}
 
@@
 we focus on local dust sourcing only while acknowledging that subsequent evolution could \textbf{also} affect the morphology.}, a map of the relative concentration 
-of second-generation dust can be constructed from the cylindrical distance at which the collisions occur.
-\textbf{Here, cylindrical distance is defined as the separation between the central star and the location of collision in the ($r, \theta$) plane.} This is shown in figure \ref{fig:coll_hist_r}.
+of second-generation dust can be constructed from the cylindrical distance at which the collisions occur. \textbf{Here, cylindrical distance is defined as the separation between the central 
+star and the location of collision in the ($r, \theta$) plane.} This is shown in figure \ref{fig:coll_hist_r}. 
 Similar to figure \ref{fig:coll_hist_a}, we use a KDE with a width of 0.02 au to assemble the collision locations into a radial distribution. Most 
@@
 bodies actually contribute to the radial collision profile, we excluded collisions that fall between $2.495 < a < 2.505$ au (near the 3:1 resonance) and 
-between $3.2 < a < 3.35$ au (near the 2:1 resonance), which is shown by the dashed curve.
-\textbf{As in figure \ref{fig:coll_hist_a}, the solid curves are normalized such that the area underneath is equal to 1.
-For the dashed curves, the normalization factor is scaled according to the number of collisions in the entire sample, compared to the number of collisions in the subsample, which excludes the collisions in resonance.} Qualitatively, none of the bump or dip features present
+between $3.2 < a < 3.35$ au (near the 2:1 resonance), which is shown by the dashed curve. \textbf{As in figure \ref{fig:coll_hist_a}, the solid curves are normalized such that the area 
+underneath is equal to 1. For the dashed curves, the normalization factor is scaled according to the number of collisions in the entire sample, compared to the number of collisions in the 
+subsample, which excludes the collisions in resonance.} Qualitatively, none of the bump or dip features present 
 are removed by making this exclusion. This suggests that the features near resonance seen in semimajor axis space become smeared out in 
@@
 slowly undoes the configuration. As the planet again passes by, adjacent planetesimals near the resonance edges temporarily align 
-themselves in this configuration.
-This explains why the concentration of planetesimals appears to `follow' the planet.
-\textbf{Connecting this back to the radial collision profiles shown in figure \ref{fig:coll_hist_r}, these bodies at the edges of the resonances must be responsible for the bumps and dips morphology seen because excluding collisions between bodies inside of the MMRs does not qualitatively alter the profiles.}
+themselves in this configuration. This explains why the concentration of planetesimals appears to `follow' the planet. \textbf{Connecting this back to the radial collision profiles shown in 
+figure \ref{fig:coll_hist_r}, these bodies at the edges of the resonances must be responsible for the bumps and dips morphology seen because excluding collisions between bodies inside 
+of the MMRs does not qualitatively alter the profiles.}
 
@@
     \includegraphics[width=\textwidth]{figures/coll_polar_e.png}
-    \caption{The collision profiles in figure \ref{fig:coll_hist_r} are shown alongside the positions of the planetesimals, in polar coordinates.
-The dashed and solid lines show the pericenter and apocenter, respectively,  of bodies at each edge of the 3:1 and 2:1 MMR.
-In these figures, the longitude of pericenter of the planet lies at $\theta = 0$ and the present position of the planet is indicated by the vertical line.
-For the 2:1 resonance, a bump, rather than a dip feature appears when the inner edge or the resonance's apocenter and outer edge's pericenter distance cross.
-The collision profile near the 3:1 resonance does not appear to follow this same qualitative behavior.
+    \caption{The collision profiles in figure \ref{fig:coll_hist_r} are shown alongside the positions of the planetesimals, in polar coordinates. The dashed and solid lines show the pericenter 
+    and apocenter, respectively,  of bodies at each edge of the 3:1 and 2:1 MMR. In these figures, the longitude of pericenter of the planet lies at $\theta = 0$ and the present position of the 
+    planet is indicated by the vertical line. For the 2:1 resonance, a bump, rather than a dip feature appears when the inner edge or the resonance's apocenter and outer edge's pericenter 
+    distance cross. The collision profile near the 3:1 resonance does not appear to follow this same qualitative behavior.
     \label{fig:coll_polar_e}}
@@
 \citet{2016ApJ...818..159T} provide a different explanation for this phenomenon, suggesting that the nonaxisymmetric structure is the product 
-of the path that a resonant test particle takes in a frame co-rotating with the planet (see figure 8.4 of \citet{1999ssd..book.....M}).
-\textbf{In other words, the gap structure is argued to be due to the interfaces between the low eccentricity, non-resonant and high eccentricity, resonant regions of the disc.} This explanation,
+of the path that a resonant test particle takes in a frame co-rotating with the planet (see figure 8.4 of \citet{1999ssd..book.....M}). \textbf{In other words, the gap structure is argued to be 
+due to the interfaces between the low eccentricity, non-resonant and high eccentricity, resonant regions of the disc.} This explanation, 
 however, does not hold for a large collection of planetesimals, especially when there is no forced eccentricity. In such a case, the orbits of 
@@
     \includegraphics[width=0.5\textwidth]{alma/xy_e2m2.png}
-    \caption{Simulated ALMA observations for the nominal (e2m2) case\textbf{, operating under the assumption that the dust profile closely traces the planetesimal collision profile}.
-Top: The sky model based on the radial collision distribution.
-The size of the disc has been scaled by a factor of 10 and placed at  a distance of 100 pc.
-Bottom: The cleaned image using combined observations in configurations 8, 9, and 10.
-The circle in the bottom left indicates the simulated beam size.
-Gaps in the dust due to the 3:1 and 2:1 resonances are visible.
+    \caption{Simulated ALMA observations for the nominal (e2m2) case\textbf{, operating under the assumption that the dust profile closely traces the planetesimal collision profile}.  Top: 
+    The sky model based on the radial collision distribution. The size of the disc has been scaled by a factor of 10 and placed at  a distance of 100 pc. Bottom: The cleaned image using 
+    combined observations in configurations 8, 9, and 10. The circle in the bottom left indicates the simulated beam size. Gaps in the dust due to the 3:1 and 2:1 resonances are visible. 
     \label{fig:alma_sim_obs}}
@@
     \includegraphics[width=\textwidth]{figures/alma_profiles.png}
-    \caption{The azimuthally-averaged radial profile based on the simulated cleaned images from all five simulations.
-The eccentricity of the perturbing planet increases from left to right, while the mass of the planet increases from bottom to top.
-The vertical dashed lines indicate the locations of the 3:1 and 2:1 resonances.
-As in figure \ref{fig:alma_sim_obs}, the size scale of the disc has been expanded by a factor of 10 and then placed at a distance of 100 pc.\label{fig:alma_profiles}}
+    \caption{The azimuthally-averaged radial profile based on the simulated cleaned images from all five simulations. The eccentricity of the perturbing planet increases from left to right, 
+    while the mass of the planet increases from bottom to top. The vertical dashed lines indicate the locations of the 3:1 and 2:1 resonances. As in figure \ref{fig:alma_sim_obs}, the size 
+    scale of the disc has been expanded by a factor of 10 and then placed at a distance of 100 pc.\label{fig:alma_profiles}}
 \end{figure*}
@@
 
-Because the strength\footnote{More specifically, the strength of the resonant term in the disturbing potential} of the 2:1 resonance scales with $e_{g}$ and  $m_{g}$, a sufficiently low mass and low eccentricity planet will not create
-enough of a perturbation in the planetesimal disc to produce a detectable bump or dip feature. The colored contours in figure \ref{fig:bump_dip_diag} 
-indicate the relative strength of the resonance as these quantities are varied. Although the resonance strength is equally sensitive to changes in 
-mass and eccentricity, the peri-apocenter overlap of the resonance edges is more sensitive to changes in eccentricity. This is because changes to 
-eccentricity affect both the resonance width and the forced eccentricity. As we showed in figure \ref{fig:coll_polar_m}, changing $m_{g}$ by a factor 
-of 4 produced very minimal changes to the resulting dust profile.
+Because the strength\footnote{More specifically, the strength of the resonant term in the disturbing potential} of the 2:1 resonance scales with $e_{g}$ and  $m_{g}$, a sufficiently low 
+mass and low eccentricity planet will not create enough of a perturbation in the planetesimal disc to produce a detectable bump or dip feature. The colored contours in figure 
+\ref{fig:bump_dip_diag} indicate the relative strength of the resonance as these quantities are varied. Although the resonance strength is equally sensitive to changes in mass and 
+eccentricity, the peri-apocenter overlap of the resonance edges is more sensitive to changes in eccentricity. This is because changes to eccentricity affect both the resonance width and 
+the forced eccentricity. As we showed in figure \ref{fig:coll_polar_m}, changing $m_{g}$ by a factor of 4 produced very minimal changes to the resulting dust profile.
 
@@
 
-\textbf{We would again like to emphasize that the dust emission profiles in figure \ref{fig:alma_profiles} are constructed upon the assumption that the radial dust structure closely traces the collision profile of the planetesimals.
-For this assumption to be valid, the resulting dust must remain locally confined, which is can be achieved achieved if the grains are reaccreted onto planetesimals \citep{2015SciA....1E0109J}.
-It is also necessary that the collisional cascade from which the dust grains form plays before radial drift has a chance to move debris away from the resonances.
-Although we showed with a back-of-the-envelope calculation (see section \ref{sec:dust}) that this is plausible for a typical protoplanetary disk with properties similar to the protosolar nebula, a more thorough treatment of collisional grinding and the subsequent evolution of the debris is necessary to be able to interpret the dust emission profiles presented here as anything more than upper limits.}
+\textbf{We would again like to emphasize that the dust emission profiles in figure \ref{fig:alma_profiles} are constructed upon the assumption that the radial dust structure closely traces the 
+collision profile of the planetesimals. For this assumption to be valid, the resulting dust must remain locally confined, which is can be achieved achieved if the grains are reaccreted onto 
+planetesimals \citep{2015SciA....1E0109J}. It is also necessary that the collisional cascade from which the dust grains form plays before radial drift has a chance to move debris away 
+from the resonances. Although we showed with a back-of-the-envelope calculation (see section \ref{sec:dust}) that this is plausible for a typical protoplanetary disk with properties similar 
+to the protosolar nebula, a more thorough treatment of collisional grinding and the subsequent evolution of the debris is necessary to be able to interpret the dust emission profiles 
+presented here as anything more than upper limits.}
 
@@
 produce structure in the collision profile as a function of semimajor axis. Furthermore, we find that a series of distinctly different features appear 
-when collisions are ordered by cylindrical distance from the central star.
-\textbf{The morphology of these features are tied to dynamical behavior of bodies near the edges of the resonances, where the circulation frequency of the critical angle approaches infinity.
-Particularly near the 2:1 MMR, we find that a bump or dip in the collision profile forms when collisions are ordered by cylindrical distance.
-The presence of one of these two features depends on the peri- and apocenter distances of the edges of the resonance, relative to the libration width.
+when collisions are ordered by cylindrical distance from the central star. \textbf{The morphology of these features are tied to dynamical behavior of bodies near the edges of the 
+resonances, where the circulation frequency of the critical angle approaches infinity. Particularly near the 2:1 MMR, we find that a bump or dip in the collision profile forms when collisions 
+are ordered by cylindrical distance. The presence of one of these two features depends on the peri- and apocenter distances of the edges of the resonance, relative to the libration width. 
 Because these quantities depend on the mass and eccentricity of the perturbing planet, these properties of the planet are actually encoded in the collision profile.}
@@
 
-\textbf{Although the planetesimal collision profile would not be directly observable in a planet-forming disc, the dust from the resulting collisional cascade could potentially be used to trace it.
-So long as the dust grains are well-coupled to the gas and radial drift does not have a significant effect on the morphology of the dust, the bump or dip features seen in the collision profile will also appear in the dust profile.
-Assuming that this is the case, we have generated simulated observations of a protoplanetary disk with ALMA and showed that the bump or dip features seen in the collision profiles should be detectable through the dust emission.
-From a dust emission profile with sufficiently strong radial features, one could constrain the properties of a perturbing planet on an exterior orbit in the following way: (1) identify the locations of two MMRs in the disc (2) measure the spacing between them to verify that one of the features is indeed associated with the 2:1 MMR (3) determine whether an under- or overdensity in the radial dust profile exists near this location (4) use the presence of one of these two features to determine the region of the eccentricity-mass plane in which the planet lies.}
+\textbf{Although the planetesimal collision profile would not be directly observable in a planet-forming disc, the dust from the resulting collisional cascade could potentially be used to trace 
+it. So long as the dust grains are well-coupled to the gas and radial drift does not have a significant effect on the morphology of the dust, the bump or dip features seen in the collision 
+profile will also appear in the dust profile. Assuming that this is the case, we have generated simulated observations of a protoplanetary disk with ALMA and showed that the bump or dip 
+features seen in the collision profiles should be detectable through the dust emission. From a dust emission profile with sufficiently strong radial features, one could constrain the 
+properties of a perturbing planet on an exterior orbit in the following way: (1) identify the locations of two MMRs in the disc (2) measure the spacing between them to verify that one of the 
+features is indeed associated with the 2:1 MMR (3) determine whether an under- or overdensity in the radial dust profile exists near this location (4) use the presence of one of these two 
+features to determine the region of the eccentricity-mass plane in which the planet lies.}
 
@@
 2:1 exterior MMR. Whether this would alter the radial collision profile for the exterior, rather than the interior 2:1 resonance, is not immediately clear.  
-\textbf{On one hand,} the solid surface density diminishes with distance ($\sim r^{-3/2}$ for the MMSN \citep{1981PThPS..70...35H}), \textbf{which would weaken the signal from locally generated collisional dust.} \textbf{On the other hand, exterior MMRs are quite effective at capturing inward drifting bodies \citep{1985Icar...62...16W}, which could locally enhance the surface density well beyond the MMSN value.
-A full treatment of the collisional cascade process and the radial drift of debris is a subject that we leave for future work.}
+\textbf{On one hand,} the solid surface density diminishes with distance ($\sim r^{-3/2}$ for the MMSN \citep{1981PThPS..70...35H}), \textbf{which would weaken the signal from locally 
+generated collisional dust.} \textbf{On the other hand, exterior MMRs are quite effective at capturing inward drifting bodies \citep{1985Icar...62...16W}, which could locally enhance the 
+surface density well beyond the MMSN value. A full treatment of the collisional cascade process and the radial drift of debris is a subject that we leave for future work.}
 
@@
 variations in the dust emission near MMRs is much more subtle and requires much higher spatial resolution and sensitivity. As we have shown, the 
-bump vs dip feature near the 2:1 MMR is marginally detectable with ALMA for the nearest protoplanetary discs\textbf{, so long as the dust profile closely matches the collisional profile of the planetesimals}.
-Another complicating factor is that
+bump vs dip feature near the 2:1 MMR is marginally detectable with ALMA for the nearest protoplanetary discs\textbf{, so long as the dust profile closely matches the collisional profile of 
+the planetesimals}. Another complicating factor is that 
 the inner $\sim$ 10 au of most protoplanetary discs are optically thick in the sub-mm. The solution to this problem is to instead observe at longer 
@@
 
-\textit{Software:} Astropy \citep{2013A&A...558A..33A}, {\sc CASA} \citep{2007ASPC..376..127M}, {\sc ChaNGa} \citep{2008IEEEpds...ChaNGa, 2015AphCom..2..1}, Matplotlib \citep{2007CSE.....9...90H}, NumPy \citep{2011CSE....13b..22V}, Pandas \citep{mckinney-proc-scipy-2010}, {\sc PYNBODY} \citep{2013ascl.soft05002P}, {\sc sklearn} \citep{scikit-learn}
+\textit{Software:} Astropy \citep{2013A&A...558A..33A}, {\sc CASA} \citep{2007ASPC..376..127M}, {\sc ChaNGa} \citep{2008IEEEpds...ChaNGa, 2015AphCom..2..1}, Matplotlib 
+\citep{2007CSE.....9...90H}, NumPy \citep{2011CSE....13b..22V}, Pandas \citep{mckinney-proc-scipy-2010}, {\sc PYNBODY} \citep{2013ascl.soft05002P}, {\sc sklearn} \citep{scikit-learn}
 
@@
 
-\textbf{The timescale for secular forcing is given by the period at which the free eccentricity of a body cycles in the complex plane.
-The time-dependent imaginary and real components of the eccentricity of a planetesimal are given by \citet{1999ssd..book.....M} (see ch.
-7, pg.
-282, eq.
-7.51)}
+\textbf{The timescale for secular forcing is given by the period at which the free eccentricity of a body cycles in the complex plane. The time-dependent imaginary and real components of 
+the eccentricity of a planetesimal are given by \citet{1999ssd..book.....M} (see ch. 7, pg. 282, eq. 7.51)}
 
@@
 
-\noindent \textbf{where  ($e_{1}$, $e_{2}$) and ($g_{1}$ , $g_{2}$) are the corresponding eigenvector components and eigenvalues of a matrix, which describes the secular interaction between two bodies, given by \citet{1999ssd..book.....M} (see ch.
-7, pg.
-276, eq.
-7.9 and 7.10, with $\alpha_{12} = \alpha$ and $\bar{\alpha_{12}} = 1$)}
+\noindent \textbf{where  ($e_{1}$, $e_{2}$) and ($g_{1}$ , $g_{2}$) are the corresponding eigenvector components and eigenvalues of a matrix, which describes the secular interaction 
+between two bodies, given by \citet{1999ssd..book.....M} (see ch. 7, pg. 276, eq. 7.9 and 7.10, with $\alpha_{12} = \alpha$ and $\bar{\alpha_{12}} = 1$)}
 
@@
 
-\noindent \textbf{Here, $n$ is the mean motion of a body and $m$ is its mass.
-In the case of a massless test particle being perturbed by a giant planet, $m_{1} = m_{g}$ and $m_{2} = 0$.
+\noindent \textbf{Here, $n$ is the mean motion of a body and $m$ is its mass. In the case of a massless test particle being perturbed by a giant planet, $m_{1} = m_{g}$ and $m_{2} = 0$. 
 The frequency of the secular forcing is simply the difference of the two eigenvalue frequencies $g_{1} - g_{2}$.}
@@
 
-\noindent (see \citet{1999ssd..book.....M} table 8.1\textbf{, third row, with $j = p + q$}) where $D b^{j}_{s}$ is the first derivative with respect to $\alpha$ of the Laplace coefficient defined in equation \ref{eq:lap}.
-This is given by \citet{1961mcm..book.....B} as
+\noindent (see \citet{1999ssd..book.....M} table 8.1\textbf{, third row, with $j = p + q$}) where $D b^{j}_{s}$ is the first derivative with respect to $\alpha$ of the Laplace coefficient defined in 
+equation \ref{eq:lap}. This is given by \citet{1961mcm..book.....B} as
 
@@
 
-\textbf{In mean-motion resonance, the orbital elements of a perturbed body, along with the critical angle described by equation \ref{eq:phi_crit}, will exhibit oscillations.
-In the circular, restricted three-body case, these small amplitude oscillations exhibit a characteristic frequency, given by (see \citet{1999ssd..book.....M} ch.
-8, pg.
-332, eq.
-8.47, with $j_{2} =-p$ and $j_{4} = -q$)}
+\textbf{In mean-motion resonance, the orbital elements of a perturbed body, along with the critical angle described by equation \ref{eq:phi_crit}, will exhibit oscillations. In the circular, 
+restricted three-body case, these small amplitude oscillations exhibit a characteristic frequency, given by (see \citet{1999ssd..book.....M} ch. 8, pg. 332, eq. 8.47, with $j_{2} =-p$ and 
+$j_{4} = -q$)}
 
@@
     \includegraphics[width=\textwidth]{figures/boley_rtheta.png}
-    \caption{Positions of planetesimals at the end of the simulation presented in \citet{2017ApJ...850..103B} in polar coordinates.
-The dashed line marks the location of a 50 $M_{\earth}$ planet embedded in the disc.
-First order MMRs with the planet are indicated with arrows.
-A second planet is also present at 32.3 au, although it is not massive enough to induce any significant structure in the disc near associated resonances.\label{fig:boley_rtheta}}
+    \caption{Positions of planetesimals at the end of the simulation presented in \citet{2017ApJ...850..103B} in polar coordinates. The dashed line marks the location of a 50 $M_{\earth}$ 
+    planet embedded in the disc. First order MMRs with the planet are indicated with arrows. A second planet is also present at 32.3 au, although it is not massive enough to induce any 
+    significant structure in the disc near associated resonances.\label{fig:boley_rtheta}}
 \end{figure*}

### 2021-01-27 refereeResponse.txt
Minor typos.  One issue about defining "St".

@@
 	We assume that there is a direct correspondence between the local collision rate and the amount of dust present.
-As the referee points out below, the spatial evolution of bodies between dust and planetesimal sizes might have a significant influence of the final dust distribution.
+As the referee points out below, the spatial evolution of bodies between dust and planetesimal sizes might have a significant influence on the final dust distribution.
 We have made sure to highlight this concern throughout the paper, and provide a somewhat crude calculation in section 5 which suggests that this assumption is not terribly unreasonable.
@@
 
-	Other studies which directly resolve planetesimal collisions near MMR with N-body methods (Richarson et al 2000, Dobinson 2013) used an integration time that shorter than the libration timescale of the resonances.
+	Other studies which directly resolve planetesimal collisions near MMR with N-body methods (Richarson et al 2000, Dobinson 2013) used an integration time that is shorter than the libration timescale of the resonances.
 This is what we mean by 'severely limited'.
@@
 The reason we did not explore exterior MMRs in this work is because doing so is more computationally expensive.
-(Many more orbits required for collisions to occur)
+(Many more orbits are required for collisions to occur)
 
@@
     This is now clarified at the end of section 2.4 (gas drag on planetesimals) and in section 3.2 (initial conditions).
-The idea is that we consider the effects gas drag when building the initial conditions, but do not need directly model it during the course of the simulations because the gas drag and gravitational stirring timescales (which counteract each other) are quite long.
+The idea is that we consider the effects gas drag when building the initial conditions, but do not need to directly model it during the course of the simulations because the gas drag and gravitational stirring timescales (which counteract each other) are quite long.
 We assume that these two effects are in equilibrium, build them into the initial conditions (through the eccentricity and inclination dispersions) and then can safely forget about them.
@@
     See 19) and 20).
-alpha = -1,5 has been a standard benchmark in the field for quite a while and is we do not think it's unreasonable to use.
+alpha = -1.5 has been a standard benchmark in the field for quite a while and we do not think it's unreasonable to use.
 Furthermore, there is evidence to suggest that the solid surface density profile close to the star is steeper than alpha = -1 (see Chiang + Laughlin 2013, and Dai, F 2020).

### 2021-01-27 main.tex
Minor typos.  One issue about defining "St".

@@
 \begin{abstract}
-\textbf{In circumstellar discs, collisional grinding of planetesimals produces second-generation dust. While it remains unclear this becomes a major component of the total dust content, 
+\textbf{In circumstellar discs, collisional grinding of planetesimals
+  produces second-generation dust. While it remains unclear whether this becomes a major component of the total dust content, 
 the presence of such dust and potentially the substructure within it can be used to explore a disc's physical conditions. A perturbing planet produces nonaxisymmetric structures, as
@@
 \citep{2000Icar..143...45R, 2017ApJ...850..103B}. Unfortunately, collision detection in an N-body simulation is extremely computationally expensive. 
-So far, studies of planetesimal dynamics near MMRs \textbf{in which the planetesimals are directly resovled} have involved either collisionless test particles 
+So far, studies of planetesimal dynamics near MMRs \textbf{in which the planetesimals are directly resolved} have involved either collisionless test particles 
 \citep{2017ApJ...850..103B, 2016ApJ...818..159T, 2018ApJ...857....3T} or \textbf{integration times that do not fully capture the dynamics of the resonances} 
@@
 imminent collision. If an imminent collision is detected, the two particles of mass $m_{1}$ and $m_{2}$ are merged together together to form one single larger body with the same density 
-and a mass of $m_{1} + m_{2}$. The resulting body is then imparted with the center of mass position and velocity of its two children. Because the resolution of a collision can result in 
+and a mass of $m_{1} + m_{2}$. The resulting body is then imparted
+with the center of mass position and velocity of the two
+colliders. Because the resolution of a collision can result in 
 another imminent collision, these events must be handled one at a time, with the soonest collision being resolved first. For this reason, another collision search is run each time a collision 
 is resolved, which continues until there are no more imminent collisions during the current time step. During the course of the simulation, no debris is created by collisions. To model the 
-collisionally generated dust distribution, we use the statistics of the resolved planetesimal collisions to build dust profile. This process is discussed in detail in section \ref{sec:dust}.}
+collisionally generated dust distribution, we use the statistics of
+the resolved planetesimal collisions to build a dust profile. This process is discussed in detail in section \ref{sec:dust}.}
 
@@
     eccentricity dispersion. The pairs of points connected by lines show the values of the perturbed (left-hand points in each subplot) and unperturbed (right-hand points) collision rates in 
-    the e1m2, e2m2 and e3m2 simulations. The unpertburbed collision rate, along with the amount of dynamical heating that the planetesimal population experiences determines whether 
+    the e1m2, e2m2 and e3m2 simulations. The unperturbed collision rate, along with the amount of dynamical heating that the planetesimal population experiences determines whether 
     the MMR acts to suppress or enhance the collision rate.}\label{fig:gf}}
@@
 s$^{-1}$. Assuming a 1 mm dust grain with a $\rho$ = 2 g cm$^{-3}$, the stopping time is $\sim 10^{-4}$ yr.  This is orders of magnitude smaller than the 
-orbital timescale, therefore we conclude that collisionally generated dust grains will immediately couple to the gas.
+orbital timescale; therefore, we conclude that collisionally generated dust grains will immediately couple to the gas.
 
@@
 is insignificant, the radial drift forces experienced by intermediate-sized bodies is much greater. Collisions between planetesimals do not immediately convert the mass to dust grains. 
-Rather, the debris will undergo a collisional cascade process, which gradually grinds the resulting bodies down to smaller sizes. A proper treatment of the collisional cascade process, is 
+Rather, the debris will undergo a collisional cascade process, which
+gradually grinds the resulting bodies down to smaller sizes. A proper
+treatment of the collisional cascade process is 
 quite complicated and is well beyond the scope of this work. However, one can safely ignore this process if the peak radial drift timescale is longer than the timescale for collisions 
@@
 
-\textbf{Radial drift is maximized for bodies of the size at which St = $t_{s} \Omega$ = 1. In the Stokes drag regime at 3 au, this occurs for bodies of 1 meter in size. Following a similar 
+%TRQ: do you need "St" here?
+I don't think it's used elsewhere in the paper.St $\equiv t_{s} \Omega$ = 1.
+In the Stokes drag regime at 3 au, this occurs for bodies of 1 meter in size.
+Following a similar
 calculation in \ref{sec:pl_drag} with a 1 m body, we find that an object of this size will drift across the 2:1 MMR on a timescale of $\sim$ 300 years. Although we do not model collisions 
@@
 \textbf{We would again like to emphasize that the dust emission profiles in figure \ref{fig:alma_profiles} are constructed upon the assumption that the radial dust structure closely traces the 
-collision profile of the planetesimals. For this assumption to be valid, the resulting dust must remain locally confined, which is can be achieved achieved if the grains are reaccreted onto 
+collision profile of the planetesimals. For this assumption to be valid, the resulting dust must remain locally confined, which can be achieved if the grains are reaccreted onto 
 planetesimals \citep{2015SciA....1E0109J}. It is also necessary that the collisional cascade from which the dust grains form plays before radial drift has a chance to move debris away 

### 2021-01-29 main.tex
Get rid of direct mention of St

@@
 
-%TRQ: do you need "St" here?
-I don't think it's used elsewhere in the paper.St $\equiv t_{s} \Omega$ = 1.
-In the Stokes drag regime at 3 au, this occurs for bodies of 1 meter in size.
-Following a similar
+\textbf{This occurs for bodies of the size at which $t_{s} \Omega$ = 1. In the Stokes drag regime at 3 au, this occurs for bodies of 1 meter in size. Following a similar 
 calculation in \ref{sec:pl_drag} with a 1 m body, we find that an object of this size will drift across the 2:1 MMR on a timescale of $\sim$ 300 years. Although we do not model collisions 

### 2021-01-29 main.tex
Shorten abstract to meet 250 word limit:

@@
 \begin{abstract}
-\textbf{In circumstellar discs, collisional grinding of planetesimals
-  produces second-generation dust. While it remains unclear whether this becomes a major component of the total dust content, 
-the presence of such dust and potentially the substructure within it can be used to explore a disc's physical conditions. A perturbing planet produces nonaxisymmetric structures, as
-well as gaps in discs, regardless of the origin of the dust. The dynamics of planetesimals, however, will be very different than that of small dust grains due to gas interactions. The
-collisional evolution of planetesimals could therefore create dusty disc structures that would not exist otherwise. Previous studies have shown that morphological differences in the
-collisional dust corotating with a giant planet can be used to determine whether the planet's eccentricity is large or small. In this work, we use N-body simulations that directly resolve
-collisions between planetesimals to investigate the collision rate profile near mean-motion resonances. We  find that a distinct bump or dip feature is produced in the collision profile,
-the presence of which depends on the libration width of the resonance and the separation between the peri- and apocenter distances of the edges of the resonance. The presence of
-one of these two features limits possible values for the mass and eccentricity of the planet. Under the simplifying assumption that the radial profile of the dust emission in the disc
-traces the planetesimal collision profile, we show that the presence of a bump or dip feature in the dust emission near the interior 2:1 mean-motion resonance can be used to place 
-constraints on the orbital properties of the perturbing planet. So long as radial drift does not play a significant role in the collisional cascade that grinds planetesimals down to dust, or if 
-other processes limit the dust to be approximately local, this feature in the dust emission should be marginally observable in nearby protoplanetary disks with ALMA.}
+\textbf{In circumstellar discs, collisional grinding of planetesimals produces second-generation dust.
+While it remains unclear whether this ever becomes a major component of the total dust content, the presence of such dust, and potentially the substructure within, it can be used to explore a disc's physical conditions.
+A perturbing planet produces nonaxisymmetric structures and gaps in the dust, regardless of its origin.
+The dynamics of planetesimals, however, will be very different than that of small dust grains due to weaker gas interactions.
+Therefore, planetesimal collisions could create dusty disc structures that would not exist otherwise.
+In this work, we use N-body simulations to investigate the collision rate profile of planetesimals near mean-motion resonances.
+We find that a distinct bump or dip feature is produced in the collision profile, the presence of which depends on the libration width of the resonance and the separation between the peri- and apocenter distances of the edges of the resonance.
+The presence of one of these two features depends on the mass and eccentricity of the planet.
+Assuming that the radial dust emission traces the planetesimal collision profile, the presence of a bump or dip feature in the dust emission at the 2:1 mean-motion resonance can constrain the orbital properties of the perturbing planet.
+This assumption is valid, so long as radial drift does not play a significant role during the collisional cascade process.
+Under this assumption, these features in the dust emission should be marginally observable in nearby protoplanetary disks with ALMA.}
 \end{abstract}

### 2021-02-23 main.tex
Remove boldface edit marks

@@
 \begin{abstract}
-\textbf{In circumstellar discs, collisional grinding of planetesimals produces second-generation dust.
+In circumstellar discs, collisional grinding of planetesimals produces second-generation dust.
 While it remains unclear whether this ever becomes a major component of the total dust content, the presence of such dust, and potentially the substructure within, it can be used to explore a disc's physical conditions.
@@
 This assumption is valid, so long as radial drift does not play a significant role during the collisional cascade process.
-Under this assumption, these features in the dust emission should be marginally observable in nearby protoplanetary disks with ALMA.}
+Under this assumption, these features in the dust emission should be marginally observable in nearby protoplanetary disks with ALMA.
 \end{abstract}
@@
 diagnostics for the physical processes that drive the evolution of the discs. In many gas-rich systems, these gap features are argued to indicate the 
-presence of a giant planet, either embedded in the disc \citep{2015MNRAS.453L..73D} or orbiting \textbf{adjacent to it}, although the details of gas-dust 
+presence of a giant planet, either embedded in the disc \citep{2015MNRAS.453L..73D} or orbiting adjacent to it, although the details of gas-dust 
 interactions can have strong effects on the resulting morphologies
@@
 
-\citet{2013ApJ...777L..31D} showed that collisional dust that is generated near the gap opened by a giant planet in \textbf{the inner regions of} a \textbf{transition} disc should 
+\citet{2013ApJ...777L..31D} showed that collisional dust that is generated near the gap opened by a giant planet in the inner regions of a transition disc should 
 produce a distinct observable marker that could be used to infer the presence of the planet. In a followup study, it was found that morphological 
@@
 the planet.  The width of a resonance is set by both the mass of the perturbing planet and the unperturbed eccentricity of the planetesimals, 
-which is in turn set by the eccentricity of the planet through secular forcing. Therefore, \textbf{the planetesimal collision profile and potentially} the structure of second generation 
+which is in turn set by the eccentricity of the planet through secular forcing. Therefore, the planetesimal collision profile and potentially the structure of second generation 
 dust produced near MMRs may encode information about both the mass and eccentricity of the planet.
@@
 \citep{2000Icar..143...45R, 2017ApJ...850..103B}. Unfortunately, collision detection in an N-body simulation is extremely computationally expensive. 
-So far, studies of planetesimal dynamics near MMRs \textbf{in which the planetesimals are directly resolved} have involved either collisionless test particles 
-\citep{2017ApJ...850..103B, 2016ApJ...818..159T, 2018ApJ...857....3T} or \textbf{integration times that do not fully capture the dynamics of the resonances} 
+So far, studies of planetesimal dynamics near MMRs in which the planetesimals are directly resolved have involved either collisionless test particles 
+\citep{2017ApJ...850..103B, 2016ApJ...818..159T, 2018ApJ...857....3T} or integration times that do not fully capture the dynamics of the resonances 
 \citep{2000Icar..143...45R, 2013ApJ...777L..31D}.
@@
 integration time. With this toolset, we explore the collision rate structure of a planetesimal disc in the vicinity of mean-motion resonances with a planet. In 
-particular, we would like to determine (1) \textbf{what dynamics govern the collision rate profile near MMRs, (2)} whether MMRs leave a detectable signature in the
-collisionally-generated dust, and \textbf{(3)} whether these signatures can be used to determine or constrain the orbital properties of the perturbing planet.
+particular, we would like to determine (1) what dynamics govern the collision rate profile near MMRs, (2) whether MMRs leave a detectable signature in the
+collisionally-generated dust, and (3) whether these signatures can be used to determine or constrain the orbital properties of the perturbing planet.
 
@@
 used and describe the initial conditions chosen for five simulations in which a perturbing giant planet is given various masses  and eccentricities. Section
-\ref{sec:results} presents the results of these simulations \textbf{and we take an in-depth look at the collision rate profiles of the planetesimals near the MMRs. 
+\ref{sec:results} presents the results of these simulations and we take an in-depth look at the collision rate profiles of the planetesimals near the MMRs. 
 In section \ref{sec:dust},  we extrapolate the collision rate down to smaller bodies and motivate a direct correspondence between the planetesimal collision profile
-and the resulting dust profile. In section \ref{sec:constrain}, w}e use the resolved collisions to generate synthetic dust 
-emission profiles that would be detected with observing facilities like ALMA. \textbf{Under our simplifying assumptions, we show} that a characteristic bump 
+and the resulting dust profile. In section \ref{sec:constrain}, we use the resolved collisions to generate synthetic dust 
+emission profiles that would be detected with observing facilities like ALMA. Under our simplifying assumptions, we show that a characteristic bump 
 or dip feature appears in the dust emission near the interior 2:1 MMR, the presence of which depends on the mass and eccentricity of the perturbing 
-planet. \textbf{If the 2:1 MMR can be identified (presumably, by identifying another prominent MMR, such as the 3:1, and measuring the spacing between the two),} we discuss the 
-potential for using this feature to place constraints on the mass and eccentricity of the planet\textbf{. In addition, we highlight the caveats of connecting the dust and planetesimal collision 
-profiles in such a simple way.} \textbf{Finally, we} conclude in section \ref{sec:conclusions}.
+planet. If the 2:1 MMR can be identified (presumably, by identifying another prominent MMR, such as the 3:1, and measuring the spacing between the two), we discuss the 
+potential for using this feature to place constraints on the mass and eccentricity of the planet. In addition, we highlight the caveats of connecting the dust and planetesimal collision 
+profiles in such a simple way. Finally, we conclude in section \ref{sec:conclusions}.
 
@@
 
-\textbf{We begin by providing a description of the dynamical effects responsible for shaping the orbital distribution of the planetesimals. The purpose of this is twofold: (1) to motivate
+We begin by providing a description of the dynamical effects responsible for shaping the orbital distribution of the planetesimals. The purpose of this is twofold: (1) to motivate
 the initial conditions used for the simulations described in section \ref{sec:ics} and (2) to justify the exclusion of certain physical effects from our simulations. Here, we focus solely on the 
-physics relevant for full-sized ($\sim$100 km) planeteismals and save a discussion of the effects on smaller bodies generated through collisions for section \ref{sec:dust}.}
+physics relevant for full-sized ($\sim$100 km) planeteismals and save a discussion of the effects on smaller bodies generated through collisions for section \ref{sec:dust}.
 
@@
 longitude of pericenter of the giant planet, and $b^{j}_{s} (\alpha)$ is a 
-Laplace coefficient given by \citep{1999ssd..book.....M} \textbf{(ch. 6, pg. 237, eq. 6.67)} as
+Laplace coefficient given by \citep{1999ssd..book.....M} (ch. 6, pg. 237, eq. 6.67) as
 
@@
 
-\textbf{For the case of a Jupiter mass planet at 5.2 au perturbing a test particle at 3 au, the timescale for secular forcing is approximately 12,000 years. The details of this calculation
-can be found in appendix \ref{sec:sec_forcing_timescale}.}
+For the case of a Jupiter mass planet at 5.2 au perturbing a test particle at 3 au, the timescale for secular forcing is approximately 12,000 years. The details of this calculation
+can be found in appendix \ref{sec:sec_forcing_timescale}.
 
@@
 width of a resonance can be defined by determining the largest variation in semimajor axis that permits librational, rather than circulatory motion of $\phi$. 
-\textbf{Calculations for the widths of first and second order interior MMRs are shown in appendix \ref{sec:libration}, along with a timescale for the libration. For the most prominent interior 
-mean-motion resonances, including the 2:1 and 3:1, the timescale associated with these oscillations driven by a Jupiter mass planet is  $\sim$ 1,000 - 2,000 years.}
+Calculations for the widths of first and second order interior MMRs are shown in appendix \ref{sec:libration}, along with a timescale for the libration. For the most prominent interior 
+mean-motion resonances, including the 2:1 and 3:1, the timescale associated with these oscillations driven by a Jupiter mass planet is  $\sim$ 1,000 - 2,000 years.
 
@@
 
-\textbf{A simple analytic model for the collision rate of a planetesimal population is given by \citet{1969edo..book.....S} as}
+A simple analytic model for the collision rate of a planetesimal population is given by \citet{1969edo..book.....S} as
 
@@
 
-\noindent\textbf{where $n$ is the number density of the population, $s$ and $m$ are the radii and masses of the bodies and $v$ is their typical encounter velocity.
+\noindent where $n$ is the number density of the population, $s$ and $m$ are the radii and masses of the bodies and $v$ is their typical encounter velocity.
 The encounter velocity is often described in terms of the rms eccentricity $\left<e^{2}\right>^{1/2}$ and inclination $\left<i^{2}\right>^{1/2}$ of the population (e.g.
-\citet{1993ARA&A..31..129L}) as}
+\citet{1993ARA&A..31..129L}) as
 
@@
 
-\noindent\textbf{where $v_{k}$ is the local Keplerian velocity. The second term in equation \ref{eq:saf} can be thought of as an additional enhancement to the collision cross section due to 
+\noindent where $v_{k}$ is the local Keplerian velocity. The second term in equation \ref{eq:saf} can be thought of as an additional enhancement to the collision cross section due to 
 gravitational focusing. When the typical encounter velocity is small compared to the mutual escape velocity of the planetesimals, the collision cross section greatly exceeds the geometric 
 value. An important feature of equation \ref{eq:saf} is that for a fixed value of $n$, the collision rate exhibits a global minimum as a function of $v$. For small $v$, gravitational focusing 
-facilitates more collisions, while for large $v$ the encounter rate simply becomes so great that the collision rate again increases, even though gravitational focusing is mostly surpressed. 
-This point will become relevant in section \ref{sec:vary_ecc} when we examine the qualitative changes in the collision rate near mean-motion resonances.}
+facilitates more collisions, while for large $v$ the encounter rate simply becomes so great that the collision rate again increases, even though gravitational focusing is mostly suppressed. 
+This point will become relevant in section \ref{sec:vary_ecc} when we examine the qualitative changes in the collision rate near mean-motion resonances.
 
-\textbf{Although equation \ref{eq:saf} works well to describe the collision rate for a homogeneous collection of planetesimals, some problems arise when regions of commensurabilities are 
+Although equation \ref{eq:saf} works well to describe the collision rate for a homogeneous collection of planetesimals, some problems arise when regions of commensurabilities are 
 introduced. Namely, the resonances cause the orbits of planetesimals to precess, and an interface between secularly aligned and randomly oriented orbits arise on each side of the 
@@
 to rather abruptly vary across the boundaries of the resonance. For this reason, an N-body treatment in which collisions are directly resolved is necessary to understand how the collision 
-rate varies near the MMRs.}
+rate varies near the MMRs.
 
@@
 
-\textbf{Over the course of many orbits, the residual gas from the primordial nebula can damp the eccentricities and inclinations of bodies. For a planetesimal-sized body, gas drag operates 
-in the Stokes regime and the timescale for aerodynamic forces to significantly alter its relative velocity is given by \citep{1976PThPh..56.1756A}}
+Over the course of many orbits, the residual gas from the primordial nebula can damp the eccentricities and inclinations of bodies. For a planetesimal-sized body, gas drag operates 
+in the Stokes regime and the timescale for aerodynamic forces to significantly alter its relative velocity is given by \citep{1976PThPh..56.1756A}
 
@@
 
-\noindent \textbf{where $m$ and $s$ are the mass and radius of the planetesimal. $C_{D}$ is a drag coefficient which is of order unity, $
+\noindent where $m$ and $s$ are the mass and radius of the planetesimal. $C_{D}$ is a drag coefficient which is of order unity, $
 \rho_{g}$ is the local density of the gas and $v_{g}$ is the headwind velocity of the gas experienced by the planetesimal. At 3 au, the gaseous component of the solar nebula has a
 density of $4 \times 10^{-10}$ g cm$^{-3}$ and the typical headwind experienced by a body on a Keplerian orbit is $\sim 5,000$ cm s$^{-1}$ \citep{1981PThPS..70...35H}. For a 100 km 
-body with a density of 2 g cm$^{-3}$ \textbf{(assuming a mixture of ice and rock)} the stopping timescale is on the order of 1 Myr. This is much longer than the timescales associated with 
+body with a density of 2 g cm$^{-3}$ (assuming a mixture of ice and rock) the stopping timescale is on the order of 1 Myr. This is much longer than the timescales associated with 
 secular forcing and libration due to mean-motion resonances, as discussed above, but shorter than the typical protoplanetary disk lifetime and potentially shorter the planetesimal 
 formation timescale. For this reason, we do not model the effects of gas drag in the simulations, although we consider its effects when constructing initial conditions, which is discussed in 
-the next section.}
+the next section.
 
@@
 This code, which is written in the {\sc CHARM++} parallel programming language, was originally designed for cosmology simulations 
-and has been shown to perform well on up to half a million processors \citep{2015AphCom..2..1}. \textbf{Using similar methods to {\sc PKDGRAV}, which has been used for numerous 
-studies of planet formation \citep{2000Icar..143...45R, 2005ApJ...625..427L, 2013ApJ...777L..31D, 2015ApJ...806...23L}}, {\sc ChaNGa} calculates 
-gravitational forces using a modified Barnes-Hut \citep{1986Natur.324..446B} tree with hexadecapole expansions of the moments \textbf{and integrates the equations of motion using a 
-kick-drift-kick leapfrog scheme}. All of the simulations we perform use a node opening criterion of $\theta_{BH}$ = 0.7. More information about the code can be found in 
+and has been shown to perform well on up to half a million processors \citep{2015AphCom..2..1}. Using similar methods to {\sc PKDGRAV}, which has been used for numerous 
+studies of planet formation \citep{2000Icar..143...45R, 2005ApJ...625..427L, 2013ApJ...777L..31D, 2015ApJ...806...23L}, {\sc ChaNGa} calculates 
+gravitational forces using a modified Barnes-Hut \citep{1986Natur.324..446B} tree with hexadecapole expansions of the moments and integrates the equations of motion using a 
+kick-drift-kick leapfrog scheme. All of the simulations we perform use a node opening criterion of $\theta_{BH}$ = 0.7. More information about the code can be found in 
 \citet{2008IEEEpds...ChaNGa}.
 
-\textbf{We have recently modified {\sc ChaNGa} to handle solid-body collisions between particles, by assigning them a fixed radius, rather than treating them as tracers of a fluid with a 
+We have recently modified {\sc ChaNGa} to handle solid-body collisions between particles, by assigning them a fixed radius, rather than treating them as tracers of a fluid with a 
 characteristic softening length. We provide a brief summary of the collision model here, although a full description is provided in \citet{2019MNRAS.489.2159W}. This work is largely based 
@@
 collisionally generated dust distribution, we use the statistics of
-the resolved planetesimal collisions to build a dust profile. This process is discussed in detail in section \ref{sec:dust}.}
+the resolved planetesimal collisions to build a dust profile. This process is discussed in detail in section \ref{sec:dust}.
 
@@
 In total, five simulations are run, which are listed in table \ref{tab:sims}. The second is a ``nominal'' case, in which the perturbing planet's mass and eccentricity are set to that of Jupiter's. 
-In the other four cases, the mass \textbf{or eccentricity is altered} by a factor of two \textbf{from} the nominal value. In all cases, the perturbing giant is placed on a 5.2 au orbit around a 1 
+In the other four cases, the mass or eccentricity is altered by a factor of two from the nominal value. In all cases, the perturbing giant is placed on a 5.2 au orbit around a 1 
 $M_{\odot}$ star. The planetesimal disc extends from 2.2 to 3.8 au, which covers the two most prominent mean-motion resonances with the giant planet, the 2:1 at 3.27 au and the 3:1 at 
@@
 
-\noindent with $\alpha$ = 3/2 and $\Sigma_{0}$ = 10 g cm$^{-2}$. Planetesimals are given a bulk density of 2 g cm$^{-3}$ \textbf{, which corresponds to a mixture of ice and rock,} and 
-\textbf{are given a} diameter of 300 km. \textbf{This choice of parameters is meant to mimic the setup used in simulation B from \citet{2000Icar..143...45R}. One difference from the 
+\noindent with $\alpha$ = 3/2 and $\Sigma_{0}$ = 10 g cm$^{-2}$. Planetesimals are given a bulk density of 2 g cm$^{-3}$, which corresponds to a mixture of ice and rock, and 
+are given a diameter of 300 km. This choice of parameters is meant to mimic the setup used in simulation B from \citet{2000Icar..143...45R}. One difference from the 
 aformentioned study is that we use a narrower annulus, which reduces the number of particles required from $10^6$ down to roughly 500,000. This allows us to use a finer base timestep 
-size, which, as we will discuss in section \ref{sec:results}, appears to be the reason why no features were seen in the collision profile near the resonances by \citet{2000Icar..143...45R}}.
+size, which, as we will discuss in section \ref{sec:results}, appears to be the reason why no features were seen in the collision profile near the resonances by \citet{2000Icar..143...45R}.
 
-\textbf{Another difference from \citet{2000Icar..143...45R} is that} the dynamical effects of secular forcing by the giant planet, along with the effects of viscous stirring and gas drag on the 
-planetesimals, are built into the initial conditions. \textbf{Although we do not model the effects of gas drag on the planetesimals during the simulation, we construct the initial conditions 
+Another difference from \citet{2000Icar..143...45R} is that the dynamical effects of secular forcing by the giant planet, along with the effects of viscous stirring and gas drag on the 
+planetesimals, are built into the initial conditions. Although we do not model the effects of gas drag on the planetesimals during the simulation, we construct the initial conditions 
 such that the effects of gas drag and viscous stirring are in balance. The viscous stirring timescale of the planetesimal disc is much longer than our chosen integration time, and so the 
-dynamical excitation of the disc (excluding resonances) stays constant, even without the inclusion of damping forces from the gas.} This is done by first calculating the equilibrium 
+dynamical excitation of the disc (excluding resonances) stays constant, even without the inclusion of damping forces from the gas. This is done by first calculating the equilibrium 
 eccentricity $e_{eq}$ due to viscous stirring and gas drag as a function of semimajor axis according to equation 12 of \citet{2002ApJ...581..666K}. The eccentricities of the bodies are 
@@
 For the purposes of the integrator, there are two relevant timescales in this system. The first is the orbital dynamical time $\sqrt{a^3/
-G M_{\odot}}$. \textbf{Through experimentation}, we have found that using a base timestep size with {\sc ChaNGa} of 3\% of an orbital dynamical time
+G M_{\odot}}$. Through experimentation, we have found that using a base timestep size with {\sc ChaNGa} of 3\% of an orbital dynamical time
 at the inner edge of the disc keeps the integration symplectic. Although doing so preserves orbital frequencies, the errors associated with
@@
 
-An additional timescale is set by the dynamical time of the planetesimals ($\sim 1/\sqrt{G \rho}$), which is about 45 minutes. \textbf{This timescale must be resolved in order to properly 
-follow close gravitational encounters between these bodies}. To resolve the base time step and the dynamical timescale of planetesimals simultaneously, we use a two-tiered time 
+An additional timescale is set by the dynamical time of the planetesimals ($\sim 1/\sqrt{G \rho}$), which is about 45 minutes. This timescale must be resolved in order to properly 
+follow close gravitational encounters between these bodies. To resolve the base time step and the dynamical timescale of planetesimals simultaneously, we use a two-tiered time 
 stepping scheme, following\citep{2015ApJ...806...23L}. To start, all bodies are placed on the base time step. A first pass of collision detection is then run in which the radii of all bodies are 
@@
 motion resonances are not built into the initial conditions, the simulations must be run long enough for the distribution of orbital elements to reach 
-equilibrium near the resonances before the collision rate is measured. \textbf{To do so, we allow each simulation to run for 2,000 years before we begin recording any collision statistics. 
+equilibrium near the resonances before the collision rate is measured. To do so, we allow each simulation to run for 2,000 years before we begin recording any collision statistics. 
 This is comparable to the libration period, which was calculated in section \ref{sec:mmr} for the 3:1 and 2:1 resonance. Although one might worry that a single libration period may not be 
@@
 this time. This is largely due to the fact that there are enough bodies in or near the resonances to allow an ensemble average of phase space, rather than a time average. As an additional 
-confirmation, we find that the time evolution of the collision rate near the resonances maintains a steady state in all five simulations after $\sim$ 2000 years.}
+confirmation, we find that the time evolution of the collision rate near the resonances maintains a steady state in all five simulations after $\sim$ 2000 years.
 
@@
 shown in figure \ref{fig:xy}. In all cases, the coordinate system is rotated so that the giant planet lies at $\theta = 0$. The longitude of perihelion of 
-the planet is shown by the dashed line. Resonances with the perturbing planet are visible as nonaxisymmetric gaps \textbf{in this figure}. Upon close inspection of a 
+the planet is shown by the dashed line. Resonances with the perturbing planet are visible as nonaxisymmetric gaps in this figure. Upon close inspection of a 
 series of simulation snapshots, these gaps appear to follow the planet in its orbit, rather than aligning themselves with the longitude of perihelion. A 
-similar substructure, which is most noticeable near the 2:1 MMR, reveals itself in \citet{2000Icar..143...45R} (see figure \textbf{3c and 3f}) and 
-\citet{2016ApJ...818..159T} (figure 3\textbf{a}). This structure is also present in the \citet{2017ApJ...850..103B} simulations, although it was not reported at the 
-time (see Appendix \ref{sec:boley_plot}). \textbf{It is worth noting that both \citet{2000Icar..143...45R} and \citet{2017ApJ...850..103B} started with a completely cold planetesimal disc.} 
+similar substructure, which is most noticeable near the 2:1 MMR, reveals itself in \citet{2000Icar..143...45R} (see figure 3c and 3f) and 
+\citet{2016ApJ...818..159T} (figure 3a). This structure is also present in the \citet{2017ApJ...850..103B} simulations, although it was not reported at the 
+time (see Appendix \ref{sec:boley_plot}). It is worth noting that both \citet{2000Icar..143...45R} and \citet{2017ApJ...850..103B} started with a completely cold planetesimal disc. 
 Thus, the presence of these features seems robust to the choice of initial conditions.
@@
 The effects of the resonances become much more apparent in semimajor axis-eccentricity space, which is shown in figure \ref{fig:ae}. In all cases, 
-the 3:1, 2:1 and 5:3 resonances are readily visible as ``spikes'' in the eccentricity that bend slightly inward (due to the conservation of \textbf{the Jacobi energy}). In the 
-e3m2 simulation, features also appear near the 5:2, 7:3 and 5:3 resonances. The absence of these \textbf{finer} features from the e1m2 simulation can be 
+the 3:1, 2:1 and 5:3 resonances are readily visible as ``spikes'' in the eccentricity that bend slightly inward (due to the conservation of the Jacobi energy). In the 
+e3m2 simulation, features also appear near the 5:2, 7:3 and 5:3 resonances. The absence of these finer features from the e1m2 simulation can be 
 explained by the fact that the strength of a resonance scales with $e^{q}$ \citep{1994PhyD...77..289M}.
@@
 \ref{fig:coll_hist_a} in this and subsequent figures are highly sensitive to the number of bins and the location of the bin edges. For this reason, we 
-construct a \textbf{probability density function (PDF)} of the collisions using a Kernel Density Estimate (KDE). We use the {\sc neighbors.KernelDensity} function from the {\sc sklearn} 
-\citep{scikit-learn} package to construct our KDEs, using a gaussian kernel with a FWHM of 0.02 au. \textbf{The curves shown in figure \ref{fig:coll_hist_a} are normalized such that the 
-area underneath is equal to 1.}
+construct a probability density function (PDF) of the collisions using a Kernel Density Estimate (KDE). We use the {\sc neighbors.KernelDensity} function from the {\sc sklearn} 
+\citep{scikit-learn} package to construct our KDEs, using a gaussian kernel with a FWHM of 0.02 au. The curves shown in figure \ref{fig:coll_hist_a} are normalized such that the 
+area underneath is equal to 1.
 
@@
 \citet{2000Icar..143...45R}, who simulated a similar setup and found no discernible features near the MMRs. We attribute the differences to a more 
-conservative timestepping criterion in our simulations\textbf{, along with the inclusion of secular perturbations in our initial conditions}. The most prominent features appear as \textbf{a 
-local maximum in} the collision rate near the 2:1 MMR and a \textbf{local minimum} near the 3:1 MMR. At higher forced eccentricities, features near the 5:2, \textbf{8}:3 and 5:3 
+conservative timestepping criterion in our simulations, along with the inclusion of secular perturbations in our initial conditions. The most prominent features appear as a 
+local maximum in the collision rate near the 2:1 MMR and a local minimum near the 3:1 MMR. At higher forced eccentricities, features near the 5:2, 8:3 and 5:3 
 resonances are also visible, due to the steep sensitivity of higher order resonant perturbations to eccentricity \citep{1994PhyD...77..289M}.
 
-\textbf{Although the features in figure \ref{fig:coll_hist_a} near the 3:1 and 2:1 MMRs appear qualitatively different, they can be explained by one single dynamical process. As discussed in 
+Although the features in figure \ref{fig:coll_hist_a} near the 3:1 and 2:1 MMRs appear qualitatively different, they can be explained by one single dynamical process. As discussed in 
 section \ref{sec:colleq}, the collision rate between planetesimals depends on both the encounter rate and the strength of gravitational focusing. The encounter rate grows as the relative 
@@
 which the average collision rate $\left< \sigma v \right>$ is at a minimum, which we will refer to as  $\left< \sigma v \right>_{0}$. The dynamical excitation induced by a mean motion 
-resonance can either increase or decrease the local average collision rate, depending on the unperturbed value of  $\left< \sigma v \right>$ relative to  $\left< \sigma v \right>_{0}$.}
+resonance can either increase or decrease the local average collision rate, depending on the unperturbed value of  $\left< \sigma v \right>$ relative to  $\left< \sigma v \right>_{0}$.
 
-\textbf{In figure \ref{fig:gf}, we show the effect that the 2:1 MMR and 3:1 MMR have on the local average collision rate. Each pair of points connected by a line represents the average 
+In figure \ref{fig:gf}, we show the effect that the 2:1 MMR and 3:1 MMR have on the local average collision rate. Each pair of points connected by a line represents the average 
 collision rate before and after the effects of the mean-motion resonances develop. Here, the relative velocity between bodies is calculated by measuring the eccentricity and inclination 
@@
 above the minimum value $\left< \sigma v \right>_{0}$ and the dynamical heating introduced by the resonance acts to suppress it further. Near the 2:1 MMR, the collision rate starts out 
-much closer to the minimum value and the additional perturbations instead act to drive it higher.}
+much closer to the minimum value and the additional perturbations instead act to drive it higher.
 
-\textbf{ This explains the relative drop in the collision rate near the 3:1 MMR and the relative increase near the 2:1 and 5:3 resonances \textbf{seen in figure \ref{fig:coll_hist_a}}. Although 
-this could potentially serve as a useful diagnostic of the planetesimal size in a disc (\textbf{because the size and mass of the planetesimals sets the eccentricity dispersion at which 
-$\left< \sigma v \right>$ is minimized}), a direct measurement of the semimajor axes of the colliding planetesimals is not possible. Furthermore, as we will demonstrate next, collisions due 
-to bodies in resonance do not have a significant effect on the final shape of the radial dust distribution that we predict.}
+This explains the relative drop in the collision rate near the 3:1 MMR and the relative increase near the 2:1 and 5:3 resonances seen in figure \ref{fig:coll_hist_a}. Although 
+this could potentially serve as a useful diagnostic of the planetesimal size in a disc (because the size and mass of the planetesimals sets the eccentricity dispersion at which 
+$\left< \sigma v \right>$ is minimized), a direct measurement of the semimajor axes of the colliding planetesimals is not possible. Furthermore, as we will demonstrate next, collisions due 
+to bodies in resonance do not have a significant effect on the final shape of the radial dust distribution that we predict.
 
@@
     \caption{A PDF of the collision rate in each disc as a function of semimajor axis, generated using a KDE with a Gaussian kernel with a FWHM of 0.02 au. In semimajor axis space, 
-    prominent features appear near the 3:1 and 2:1 MMRs. Near the 3:1, the collision rate \textbf{exhibits a local minimum}, while an enhancement appears near the 
+    prominent features appear near the 3:1 and 2:1 MMRs. Near the 3:1, the collision rate exhibits a local minimum, while an enhancement appears near the 
     2:1.\label{fig:coll_hist_a}}
@@
     \includegraphics[width=\textwidth]{figures/gf_plot.png}
-    \caption{\textbf{The collision rate (given by equation \ref{eq:saf}) of bodies in the vicinity of the 3:1 (left) and 2:1 (right) MMRs, relative to the minimum value, as a function of the local 
+    \caption{The collision rate (given by equation \ref{eq:saf}) of bodies in the vicinity of the 3:1 (left) and 2:1 (right) MMRs, relative to the minimum value, as a function of the local 
     eccentricity dispersion. The pairs of points connected by lines show the values of the perturbed (left-hand points in each subplot) and unperturbed (right-hand points) collision rates in 
     the e1m2, e2m2 and e3m2 simulations. The unperturbed collision rate, along with the amount of dynamical heating that the planetesimal population experiences determines whether 
-    the MMR acts to suppress or enhance the collision rate.}\label{fig:gf}}
+    the MMR acts to suppress or enhance the collision rate.\label{fig:gf}}
 \end{center}
@@
     collision profile with collisions between bodies in resonance removed. The bump and dip features remain qualitatively the same, which suggests that they are produced by bodies 
-    \textbf{outside of the libration width of the resonance.}\label{fig:coll_hist_r}}
+    outside of the libration width of the resonance.\label{fig:coll_hist_r}}
 \end{center}
@@
 
-To construct a radial dust profile from the collision statistics, we begin by making \textbf{two assumptions: (1) any dust generated by collisions is strongly coupled to the gas and (2) any 
-subsequent spatial evolution of the collisional debris is insignificant.} \textbf{So long as both of these assumptions are true, we can use the radial locations of planetesimal collisions in the 
-plane of the disk to generate a dust profile for each simulation.}
+To construct a radial dust profile from the collision statistics, we begin by making two assumptions: (1) any dust generated by collisions is strongly coupled to the gas and (2) any 
+subsequent spatial evolution of the collisional debris is insignificant. So long as both of these assumptions are true, we can use the radial locations of planetesimal collisions in the 
+plane of the disk to generate a dust profile for each simulation.
 
-\textbf{We first provide a justification for assumption (1), which is as follows: At 3 au in the protosolar nebula, the mean free path of a gas particle is $\sim$ 50 cm (assuming a composition 
-of pure hydrogen with a local volume density of $\rho_{g} = 4 \times 10^{-10}$ g cm$^{-3}$). This places any dust grains in the Epstein drag regime, with a stopping timescale given by}
+We first provide a justification for assumption (1), which is as follows: At 3 au in the protosolar nebula, the mean free path of a gas particle is $\sim$ 50 cm (assuming a composition 
+of pure hydrogen with a local volume density of $\rho_{g} = 4 \times 10^{-10}$ g cm$^{-3}$). This places any dust grains in the Epstein drag regime, with a stopping timescale given by
 
@@
 
-\textbf{Assumption (2) is less straightforward to justify and may not be reasonable in all cases. Although the spatial redistribution of the full-sized planetesimals and mm-sized dust grains 
+Assumption (2) is less straightforward to justify and may not be reasonable in all cases. Although the spatial redistribution of the full-sized planetesimals and mm-sized dust grains 
 is insignificant, the radial drift forces experienced by intermediate-sized bodies is much greater. Collisions between planetesimals do not immediately convert the mass to dust grains. 
@@
 quite complicated and is well beyond the scope of this work. However, one can safely ignore this process if the peak radial drift timescale is longer than the timescale for collisions 
-between these bodies.}
+between these bodies.
 
-\textbf{This occurs for bodies of the size at which $t_{s} \Omega$ = 1. In the Stokes drag regime at 3 au, this occurs for bodies of 1 meter in size. Following a similar 
+This occurs for bodies of the size at which $t_{s} \Omega$ = 1. In the Stokes drag regime at 3 au, this occurs for bodies of 1 meter in size. Following a similar 
 calculation in \ref{sec:pl_drag} with a 1 m body, we find that an object of this size will drift across the 2:1 MMR on a timescale of $\sim$ 300 years. Although we do not model collisions 
@@
 timescale two orders of magnitude shorter than the drift timescale. We therefore argue that it is reasonable and, indeed, best practice to start with such simple assumptions understand the 
-physics before additional complexity is later added. We caution, however, that the collision timescale estimates provided here should be interpreted as lower limits.}
+physics before additional complexity is later added. We caution, however, that the collision timescale estimates provided here should be interpreted as lower limits.
 
-Operating under \textbf{these assumptions} \footnote{As discussed in \cite{2017ApJ...850..103B}, the local generation of second-generation dust is only one 
+Operating under these assumptions \footnote{As discussed in \cite{2017ApJ...850..103B}, the local generation of second-generation dust is only one 
 consideration. The dust will also evolve spatially due to drag effects, but can also evolve in size or be re-accreted onto planetesimals. For simplicity, 
 we focus on local dust sourcing only while acknowledging that subsequent evolution could \textbf{also} affect the morphology.}, a map of the relative concentration 
-of second-generation dust can be constructed from the cylindrical distance at which the collisions occur. \textbf{Here, cylindrical distance is defined as the separation between the central 
-star and the location of collision in the ($r, \theta$) plane.} This is shown in figure \ref{fig:coll_hist_r}. 
+of second-generation dust can be constructed from the cylindrical distance at which the collisions occur. Here, cylindrical distance is defined as the separation between the central 
+star and the location of collision in the ($r, \theta$) plane. This is shown in figure \ref{fig:coll_hist_r}. 
 Similar to figure \ref{fig:coll_hist_a}, we use a KDE with a width of 0.02 au to assemble the collision locations into a radial distribution. Most 
 strikingly, the bump that was present near the 2:1 resonance is no longer visible in cylindrical distance space, although it suddenly appears again in 
-the e3m2 simulation. The \textbf{local minimum} that is visible near the 3:1 MMR also becomes a \textbf{local maximum} in the highest eccentricity case. To determine how the resonant 
+the e3m2 simulation. The local minimum that is visible near the 3:1 MMR also becomes a local maximum in the highest eccentricity case. To determine how the resonant 
 bodies actually contribute to the radial collision profile, we excluded collisions that fall between $2.495 < a < 2.505$ au (near the 3:1 resonance) and 
-between $3.2 < a < 3.35$ au (near the 2:1 resonance), which is shown by the dashed curve. \textbf{As in figure \ref{fig:coll_hist_a}, the solid curves are normalized such that the area 
+between $3.2 < a < 3.35$ au (near the 2:1 resonance), which is shown by the dashed curve. As in figure \ref{fig:coll_hist_a}, the solid curves are normalized such that the area 
 underneath is equal to 1. For the dashed curves, the normalization factor is scaled according to the number of collisions in the entire sample, compared to the number of collisions in the 
-subsample, which excludes the collisions in resonance.} Qualitatively, none of the bump or dip features present 
+subsample, which excludes the collisions in resonance. Qualitatively, none of the bump or dip features present 
 are removed by making this exclusion. This suggests that the features near resonance seen in semimajor axis space become smeared out in 
@@
 
-This also suggests that the prominent bumps and dips seen in figure \ref{fig:coll_hist_r} are mainly produced by bodies outside of \textbf{the libration width of the} resonance, although 
+This also suggests that the prominent bumps and dips seen in figure \ref{fig:coll_hist_r} are mainly produced by bodies outside of the libration width of the resonance, although 
 the resonant population does make some of the features more pronounced. To further understand this, we consider the nonaxisymmetric structure 
@@
 slowly undoes the configuration. As the planet again passes by, adjacent planetesimals near the resonance edges temporarily align 
-themselves in this configuration. This explains why the concentration of planetesimals appears to `follow' the planet. \textbf{Connecting this back to the radial collision profiles shown in 
+themselves in this configuration. This explains why the concentration of planetesimals appears to `follow' the planet. Connecting this back to the radial collision profiles shown in 
 figure \ref{fig:coll_hist_r}, these bodies at the edges of the resonances must be responsible for the bumps and dips morphology seen because excluding collisions between bodies inside 
-of the MMRs does not qualitatively alter the profiles.}
+of the MMRs does not qualitatively alter the profiles.
 
@@
 \citet{2016ApJ...818..159T} provide a different explanation for this phenomenon, suggesting that the nonaxisymmetric structure is the product 
-of the path that a resonant test particle takes in a frame co-rotating with the planet (see figure 8.4 of \citet{1999ssd..book.....M}). \textbf{In other words, the gap structure is argued to be 
-due to the interfaces between the low eccentricity, non-resonant and high eccentricity, resonant regions of the disc.} This explanation, 
+of the path that a resonant test particle takes in a frame co-rotating with the planet (see figure 8.4 of \citet{1999ssd..book.....M}). In other words, the gap structure is argued to be 
+due to the interfaces between the low eccentricity, non-resonant and high eccentricity, resonant regions of the disc. This explanation, 
 however, does not hold for a large collection of planetesimals, especially when there is no forced eccentricity. In such a case, the orbits of 
@@
 straightforward case. Many different parameterizations are possible, depending on optical depth, grain size, disc temperature, etc., but we will avoid 
-such complications here\textbf{, as they would affect the overall brightness profile, but not the presence of any gaps or rings.} We normalize the intensity by
+such complications here, as they would affect the overall brightness profile, but not the presence of any gaps or rings. We normalize the intensity by
 setting the total disc flux density to be 100 mJy at about 350 GHz.
@@
     \includegraphics[width=0.5\textwidth]{alma/xy_e2m2.png}
-    \caption{Simulated ALMA observations for the nominal (e2m2) case\textbf{, operating under the assumption that the dust profile closely traces the planetesimal collision profile}.  Top: 
+    \caption{Simulated ALMA observations for the nominal (e2m2) case, operating under the assumption that the dust profile closely traces the planetesimal collision profile.  Top: 
     The sky model based on the radial collision distribution. The size of the disc has been scaled by a factor of 10 and placed at  a distance of 100 pc. Bottom: The cleaned image using 
@@
     \includegraphics[width=0.5\textwidth]{figures/bump_dip_diag.png}
-    \caption{The presence of a dip or bump \textbf{in the collision profile (and therefore the dust profile)} near the 2:1 MMR can be used to constrain the mass and eccentricity
+    \caption{The presence of a dip or bump in the collision profile (and therefore the dust profile) near the 2:1 MMR can be used to constrain the mass and eccentricity
     of the perturbing planet. The color scale indicates the relative strength of the features, while the dashed lines
@@
 
-\textbf{We would again like to emphasize that the dust emission profiles in figure \ref{fig:alma_profiles} are constructed upon the assumption that the radial dust structure closely traces the 
+We would again like to emphasize that the dust emission profiles in figure \ref{fig:alma_profiles} are constructed upon the assumption that the radial dust structure closely traces the 
 collision profile of the planetesimals. For this assumption to be valid, the resulting dust must remain locally confined, which can be achieved if the grains are reaccreted onto 
@@
 to the protosolar nebula, a more thorough treatment of collisional grinding and the subsequent evolution of the debris is necessary to be able to interpret the dust emission profiles 
-presented here as anything more than upper limits.}
+presented here as anything more than upper limits.
 
@@
 produce structure in the collision profile as a function of semimajor axis. Furthermore, we find that a series of distinctly different features appear 
-when collisions are ordered by cylindrical distance from the central star. \textbf{The morphology of these features are tied to dynamical behavior of bodies near the edges of the 
+when collisions are ordered by cylindrical distance from the central star. The morphology of these features are tied to dynamical behavior of bodies near the edges of the 
 resonances, where the circulation frequency of the critical angle approaches infinity. Particularly near the 2:1 MMR, we find that a bump or dip in the collision profile forms when collisions 
 are ordered by cylindrical distance. The presence of one of these two features depends on the peri- and apocenter distances of the edges of the resonance, relative to the libration width. 
-Because these quantities depend on the mass and eccentricity of the perturbing planet, these properties of the planet are actually encoded in the collision profile.}
+Because these quantities depend on the mass and eccentricity of the perturbing planet, these properties of the planet are actually encoded in the collision profile.
 
@@
 
-\textbf{Although the planetesimal collision profile would not be directly observable in a planet-forming disc, the dust from the resulting collisional cascade could potentially be used to trace 
+Although the planetesimal collision profile would not be directly observable in a planet-forming disc, the dust from the resulting collisional cascade could potentially be used to trace 
 it. So long as the dust grains are well-coupled to the gas and radial drift does not have a significant effect on the morphology of the dust, the bump or dip features seen in the collision 
@@
 features is indeed associated with the 2:1 MMR (3) determine whether an under- or overdensity in the radial dust profile exists near this location (4) use the presence of one of these two 
-features to determine the region of the eccentricity-mass plane in which the planet lies.}
+features to determine the region of the eccentricity-mass plane in which the planet lies.
 
@@
 2:1 exterior MMR. Whether this would alter the radial collision profile for the exterior, rather than the interior 2:1 resonance, is not immediately clear.  
-\textbf{On one hand,} the solid surface density diminishes with distance ($\sim r^{-3/2}$ for the MMSN \citep{1981PThPS..70...35H}), \textbf{which would weaken the signal from locally 
-generated collisional dust.} \textbf{On the other hand, exterior MMRs are quite effective at capturing inward drifting bodies \citep{1985Icar...62...16W}, which could locally enhance the 
-surface density well beyond the MMSN value. A full treatment of the collisional cascade process and the radial drift of debris is a subject that we leave for future work.}
+On one hand, the solid surface density diminishes with distance ($\sim r^{-3/2}$ for the MMSN \citep{1981PThPS..70...35H}), which would weaken the signal from locally 
+generated collisional dust. On the other hand, exterior MMRs are quite effective at capturing inward drifting bodies \citep{1985Icar...62...16W}, which could locally enhance the 
+surface density well beyond the MMSN value. A full treatment of the collisional cascade process and the radial drift of debris is a subject that we leave for future work.
 
@@
 variations in the dust emission near MMRs is much more subtle and requires much higher spatial resolution and sensitivity. As we have shown, the 
-bump vs dip feature near the 2:1 MMR is marginally detectable with ALMA for the nearest protoplanetary discs\textbf{, so long as the dust profile closely matches the collisional profile of 
-the planetesimals}. Another complicating factor is that 
+bump vs dip feature near the 2:1 MMR is marginally detectable with ALMA for the nearest protoplanetary discs, so long as the dust profile closely matches the collisional profile of 
+the planetesimals. Another complicating factor is that 
 the inner $\sim$ 10 au of most protoplanetary discs are optically thick in the sub-mm. The solution to this problem is to instead observe at longer 
@@
 
-\textbf{The timescale for secular forcing is given by the period at which the free eccentricity of a body cycles in the complex plane. The time-dependent imaginary and real components of 
-the eccentricity of a planetesimal are given by \citet{1999ssd..book.....M} (see ch. 7, pg. 282, eq. 7.51)}
+The timescale for secular forcing is given by the period at which the free eccentricity of a body cycles in the complex plane. The time-dependent imaginary and real components of 
+the eccentricity of a planetesimal are given by \citet{1999ssd..book.....M} (see ch. 7, pg. 282, eq. 7.51)
 
@@
 
-\noindent \textbf{where  ($e_{1}$, $e_{2}$) and ($g_{1}$ , $g_{2}$) are the corresponding eigenvector components and eigenvalues of a matrix, which describes the secular interaction 
-between two bodies, given by \citet{1999ssd..book.....M} (see ch. 7, pg. 276, eq. 7.9 and 7.10, with $\alpha_{12} = \alpha$ and $\bar{\alpha_{12}} = 1$)}
+\noindent where  ($e_{1}$, $e_{2}$) and ($g_{1}$ , $g_{2}$) are the corresponding eigenvector components and eigenvalues of a matrix, which describes the secular interaction 
+between two bodies, given by \citet{1999ssd..book.....M} (see ch. 7, pg. 276, eq. 7.9 and 7.10, with $\alpha_{12} = \alpha$ and $\bar{\alpha_{12}} = 1$)
 
@@
 
-\noindent \textbf{Here, $n$ is the mean motion of a body and $m$ is its mass. In the case of a massless test particle being perturbed by a giant planet, $m_{1} = m_{g}$ and $m_{2} = 0$. 
-The frequency of the secular forcing is simply the difference of the two eigenvalue frequencies $g_{1} - g_{2}$.}
+\noindent Here, $n$ is the mean motion of a body and $m$ is its mass. In the case of a massless test particle being perturbed by a giant planet, $m_{1} = m_{g}$ and $m_{2} = 0$. 
+The frequency of the secular forcing is simply the difference of the two eigenvalue frequencies $g_{1} - g_{2}$.
 
@@
 
-For second order and higher MMRs, the maximum libration width is given by \citet{1999ssd..book.....M} \textbf{(ch. 8, pg. 338, eq. 8.58)} as
+For second order and higher MMRs, the maximum libration width is given by \citet{1999ssd..book.....M} (ch. 8, pg. 338, eq. 8.58) as
 
@@
 
-\noindent (see \citet{1999ssd..book.....M} table 8.1\textbf{, third row, with $j = p + q$}) where $D b^{j}_{s}$ is the first derivative with respect to $\alpha$ of the Laplace coefficient defined in 
+\noindent (see \citet{1999ssd..book.....M} table 8.1, third row, with $j = p + q$) where $D b^{j}_{s}$ is the first derivative with respect to $\alpha$ of the Laplace coefficient defined in 
 equation \ref{eq:lap}. This is given by \citet{1961mcm..book.....B} as
@@
 
-\noindent (see \citet{1999ssd..book.....M} table 8.1\textbf{, first row}) and there is an additional contribution to the motion of the critical angle by the pericenter precession rate such that
+\noindent (see \citet{1999ssd..book.....M} table 8., first row) and there is an additional contribution to the motion of the critical angle by the pericenter precession rate such that
 
@@
 
-\noindent (see \citet{1999ssd..book.....M} \textbf{ch. 8, pg. 340,} eq. 8.76 \textbf{with $j_{2} = p$}).
+\noindent (see \citet{1999ssd..book.....M} ch. 8, pg. 340, eq. 8.76, with $j_{2} = p$).
 
-\textbf{In mean-motion resonance, the orbital elements of a perturbed body, along with the critical angle described by equation \ref{eq:phi_crit}, will exhibit oscillations. In the circular, 
+In mean-motion resonance, the orbital elements of a perturbed body, along with the critical angle described by equation \ref{eq:phi_crit}, will exhibit oscillations. In the circular, 
 restricted three-body case, these small amplitude oscillations exhibit a characteristic frequency, given by (see \citet{1999ssd..book.....M} ch. 8, pg. 332, eq. 8.47, with $j_{2} =-p$ and 
-$j_{4} = -q$)}
+$j_{4} = -q$)
 

### 2021-02-23 refereeResponse2.txt
Final edits before acceptance to journal

1) In page 7 is said — "We assume that the eccentricity and inclination dispersions are coupled (Ida et al. 1993) and use the eccentricity dispersion as an independent variable.” — It is strange to think on the eccentricity as an independent parameter once it is coupled with the inclination. Maybe change it to “free parameter”?

    "independent variable" has been changed to "free parameter" here.

2) The explanation for the changes in <\sigma v> in the caption of Figure 5 seems incorrect. Actually, their are correct, but what the authors call lef-hand points should be right-hand points and vice-versa. The correct explanation (relation left- right-points) is given in the main text (page 7 - lines 20—25; “… Near the 3:1… drive it higher). Please, review it.

    Fixed

3) Page 7 — “However, one can safely ignore this process if the peak radial drift timescale is longer than the timescale for collisions between these bodies.” — I think safely is too strong! Please, consider changing to “can safely” or “may”.

    "can safely" has been changed to "may be able to".

4) Wallace et al. assume values for \Sigma_0 and \rho_0 in the minimum solar nebular that are not conventional. I understand they are comparing their model with Richardson et al. (2000), and thus, they are using the same values from that work. But, please, consider given the reader a more physical explanation. For example:

4.1) In section 2.4 the authors use 4e-10 g/cm^3 for minimum solar nebula density at 3 au. It is rather confusing why this value was chosen. The density of the nebula in Hayashi (1981) is given by \rho_r = \rho_0*[r^(-2.75)] — eq 2.7 assuming z=0 (mid-plane) and \rho_0 = 1.4e-9 g/cm^3. At 3 au this will result \rho(r=3au) ~ 2.86e-11 g/cm^3 and not 4e-10 g/cm^3. Are the authors considering a different gas temperature profile (what is the flaring relation — did I miss that in the text)? Please, consider reviewing this value or explaining why not using the value from quoted reference. The same value is used in section 5 to explain the fate of the dust.

   The referee is correct that we should have used \rho(r=3au) ~ 2.86e-11 g/cm^3. The value in the paper draft comes from
   a mistake in our calculations, where we accidentally scaled \rho_0 as a surface density, rather than as a volume density.
   It appears that this mistake was only made when calculating a value for \rho(r=3au) to display in the paper and does not appear in any of our analysis code. Therefore, the gas drag timescale in section 2.4, the mean free path in section 5, and the radial drift timescales in section 5 remain the same.

4.2) In section 3.2 it is once again not clear how Wallace et al have chosen the minimum nebula value for \Simga_0. In Hayashi (1981) the surface density is defined as \Sigma_0 = 7.1 g/cm^2 for rock bodies only, 30 g/cm^2 for rock+ice bodies, and 1700 g/cm^2 for gas. Where does \Sigma_0 = 10  g/cm^2 comes from? Please, consider explaining this.

  Following other papers (which cite Hayashi 1981 and then use \Sigma_0 = 10 g/cm^2), we have now changed the sentence before equation 9 to read "The planetesimal disk loosely follows a minimum-mass solar nebula profile"

5) I would once again call the attention for quoting figures from other works. Instead of “(see figure 3c and 3f)” use (see figure 3c and 3f from their work), or (see their figures 3c and 3f). It sounds like a useless change, but I caught myself once again like, wait, what, are there panels 3(a, b, c, d, e, and f) in this work? Same for (figure 3 a). All this is in section 4.1.

  "see figure" has been changed to "see their figure(s)"

### 2021-02-23 main.tex
Final edits before acceptance to journal

@@
 \rho_{g}$ is the local density of the gas and $v_{g}$ is the headwind velocity of the gas experienced by the planetesimal. At 3 au, the gaseous component of the solar nebula has a
-density of $4 \times 10^{-10}$ g cm$^{-3}$ and the typical headwind experienced by a body on a Keplerian orbit is $\sim 5,000$ cm s$^{-1}$ \citep{1981PThPS..70...35H}. For a 100 km 
-body with a density of 2 g cm$^{-3}$ (assuming a mixture of ice and rock) the stopping timescale is on the order of 1 Myr. This is much longer than the timescales associated with 
+density of $3 \times 10^{-11}$ g cm$^{-3}$ and the typical headwind experienced by a body on a Keplerian orbit is $\sim 5,000$ cm s$^{-1}$ \citep{1981PThPS..70...35H}. For a 100 km 
+body with a density of 2 g cm$^{-3}$ (assuming a mixture of ice and rock) the stopping timescale is about 1 Myr. This is much longer than the timescales associated with 
 secular forcing and libration due to mean-motion resonances, as discussed above, but shorter than the typical protoplanetary disk lifetime and potentially shorter the planetesimal 
@@
 $M_{\odot}$ star. The planetesimal disc extends from 2.2 to 3.8 au, which covers the two most prominent mean-motion resonances with the giant planet, the 2:1 at 3.27 au and the 3:1 at 
-2.5 au. The planetesimal disc follows a minimum-mass solar nebula surface density profile \citep{1981PThPS..70...35H}
+2.5 au. The planetesimal disc loosely follows a minimum-mass solar nebula surface density profile \citep{1981PThPS..70...35H}
 
@@
 series of simulation snapshots, these gaps appear to follow the planet in its orbit, rather than aligning themselves with the longitude of perihelion. A 
-similar substructure, which is most noticeable near the 2:1 MMR, reveals itself in \citet{2000Icar..143...45R} (see figure 3c and 3f) and 
-\citet{2016ApJ...818..159T} (figure 3a). This structure is also present in the \citet{2017ApJ...850..103B} simulations, although it was not reported at the 
+similar substructure, which is most noticeable near the 2:1 MMR, reveals itself in \citet{2000Icar..143...45R} (see their figures 3c and 3f) and 
+\citet{2016ApJ...818..159T} (see their figure 3a). This structure is also present in the \citet{2017ApJ...850..103B} simulations, although it was not reported at the 
 time (see Appendix \ref{sec:boley_plot}). It is worth noting that both \citet{2000Icar..143...45R} and \citet{2017ApJ...850..103B} started with a completely cold planetesimal disc. 
@@
 dispersion near each resonance and using equation \ref{eq:eccincvel}. We assume that the eccentricity and inclination dispersions are coupled \citep{1993MNRAS.263..875I} and use the 
-eccentricity dispersion as an independent variable. Because both the strength of secular forcing and the effects of the resonant perturbations are different near the 3:1 and 2:1 MMRs, the 
+eccentricity dispersion as a free parameter. Because both the strength of secular forcing and the effects of the resonant perturbations are different near the 3:1 and 2:1 MMRs, the 
 planetesimal population at each of these locations in the disk experiences a qualitatively different change in the collision rate. Near the 3:1 MMR, the unperturbed collision rate is well 
@@
     \caption{The collision rate (given by equation \ref{eq:saf}) of bodies in the vicinity of the 3:1 (left) and 2:1 (right) MMRs, relative to the minimum value, as a function of the local 
-    eccentricity dispersion. The pairs of points connected by lines show the values of the perturbed (left-hand points in each subplot) and unperturbed (right-hand points) collision rates in 
+    eccentricity dispersion.
+The pairs of points connected by lines show the values of the unperturbed (left-hand points in each subplot) and perturbed (right-hand points in each subplot) collision rates in
     the e1m2, e2m2 and e3m2 simulations. The unperturbed collision rate, along with the amount of dynamical heating that the planetesimal population experiences determines whether 
@@
 We first provide a justification for assumption (1), which is as follows: At 3 au in the protosolar nebula, the mean free path of a gas particle is $\sim$ 50 cm (assuming a composition 
-of pure hydrogen with a local volume density of $\rho_{g} = 4 \times 10^{-10}$ g cm$^{-3}$). This places any dust grains in the Epstein drag regime, with a stopping timescale given by
+of pure hydrogen with a local volume density of $\rho_{g} = 3 \times 10^{-11}$ g cm$^{-3}$). This places any dust grains in the Epstein drag regime, with a stopping timescale given by
 
@@
 treatment of the collisional cascade process is 
-quite complicated and is well beyond the scope of this work. However, one can safely ignore this process if the peak radial drift timescale is longer than the timescale for collisions 
+quite complicated and is well beyond the scope of this work. However, one may be able to ignore this process if the peak radial drift timescale is longer than the timescale for collisions 
 between these bodies.

### 2021-02-24 main.tex
Fix space around changa citation, prevent footnote text from splitting between pages

@@
 \def\thebibliography{\DeclareRobustCommand{\VAN}[3]{##3}\VANthebibliography}
+
+% Prevent footnotes from breaking across multiple pages
+\interfootnotelinepenalty=10000
 
@@
 
-To further elucidate this subject, we use the tree based N-body code {\sc ChaNGa}\citep{2008IEEEpds...ChaNGa, 2015AphCom..2..1}  to follow the 
+To further elucidate this subject, we use the tree based N-body code {\sc ChaNGa} \citep{2008IEEEpds...ChaNGa, 2015AphCom..2..1} to follow the 
 collisional evolution of a planetesimal disc under the gravitational influence of a Jupiter-sized body. Because particle positions are sorted into a tree 
